### 2015-08-04 LensingPaper_draft_v1.01.tex
Started git repository for Lensing paper.

% mn2esample.tex
%
% v2.1 released 22nd May 2002 (G. Hutton)
%
% The mnsample.tex file has been amended to highlight
% the proper use of LaTeX2e code with the class file
% and using natbib cross-referencing. These changes
% do not reflect the original paper by A. V. Raveendran.
%
% Previous versions of this sample document were
% compatible with the LaTeX 2.09 style file mn.sty
% v1.2 released 5th September 1994 (M. Reed)
% v1.1 released 18th July 1994
% v1.0 released 28th January 1994

\documentclass[useAMS,usenatbib]{mn2e}

% If your system does not have the AMS fonts version 2.0 installed, then
% remove the useAMS option.
%
% useAMS allows you to obtain upright Greek characters.
% e.g. \umu, \upi etc.  See the section on "Upright Greek characters" in
% this guide for further information.
%
% If you are using AMS 2.0 fonts, bold math letters/symbols are available
% at a larger range of sizes for NFSS release 1 and 2 (using \boldmath or
% preferably \bmath).
%
% The usenatbib command allows the use of Patrick Daly's natbib.sty for
% cross-referencing.
%
% If you wish to typeset the paper in Times font (if you do not have the
% PostScript Type 1 Computer Modern fonts you will need to do this to get
% smoother fonts in a PDF file) then uncomment the next line
% \usepackage{Times}

%%%%% AUTHORS - PLACE YOUR OWN MACROS HERE %%%%%

%_____GENERAL PACKAGES_____
\usepackage{amsmath}	%for \text{} in math mode
\usepackage{amssymb}	%for symbols

%_____FIGURES_____
\usepackage{graphicx}	%for including images
\usepackage{float}	%for [Hhtb] etc of figures
\usepackage{grffile}    %for using underscores in figure filenames
\usepackage{subcaption} %for having sub-captions in figures with multiple panels
\usepackage{placeins} %for \FloatBarrier, which forces all figures to be printed before continuing

%_____SYMBOLS_____
\usepackage{ mathrsfs } %for slanted letters in math mode

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title[A spiral galaxy's mass distribution uncovered]{A spiral galaxy's mass distribution uncovered through lensing and dynamics}
\author[W. Trick, G. van de Ven and A. Dutton]{W. Trick$^{1}$\thanks{E-mail:
trick@mpia.de}, G. van de Ven$^{1}$ and A. Dutton$^{1}$\\
$^{1}$Max-Planck-Institute for Astronomy, K\"{o}nigstuhl 17, 69117 Heidelberg, Germany}
\begin{document}

\date{Accepted ????. Received ????; in original form ????}

\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2014}

\maketitle

\label{firstpage}

\begin{abstract}
[TO DO]
\end{abstract}

\begin{keywords}
blabla -- blabla: bla.
\end{keywords}

\section{Introduction}

[TO DO]

\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/first_glimpse_450.ps}
  \caption{J1331 in F450W ("blue")}
  \label{fig:???}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/first_glimpse_814.ps}
  \caption{J1331 in F814W ("red")}
  \label{fig:???}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_imgpos.ps}
  \caption{The lensing images}
  \label{fig:lens_just_imgpos}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/stellar_kinematics_data.ps}
  \caption{Stellar Kinematics by \citet{SWELLSV}}
  \label{fig:???}
\end{subfigure}
\caption{Hubble Space telescope (HST) images and stellar kinematics of the galaxy SDSS J1331+3638 (J1331), which has a large counter-rotating core and whose bulge acts as a strong lens for a bluish background source. \emph{Panel (a) and (b):} HST images of J1331 by \citet{SWELLSI} in two filters, F450W in panel (a) and F814W in panel (b). The galaxy's coordinates on the sky are right ascension $\alpha$ = 202.91800$^\circ$ and declination $\delta$ = 36.46999$^\circ$ (epoch J2000). Image orientation and scaling are indicated in panel (a); the scaling transformation from arcseconds to the physical size of the galaxy in kpc uses the galaxy's redshift $z_d = 0.113$ \citep{SWELLSIII}. The black solid line in panel (a) shows the orientation of the major-axis. The line has a length of 10 arcsec and indicates the region within which we carry out the Jeans modelling. (NOT ALL THE TIME.???????) \emph{Panel (c):} The central region of J1331 in F450W, surface brightness subtracted. An IRAF ellipse ???? fit to the F450W surface brightness in panel (a) was subtracted from the image. The (smoothed) residuals within the white square in panel (a) are shown in panel (c). Four bright blobs (A,B,C and D) become visible, which are arranged in a typical strong lensing configuration around the center of the galaxy (G). \emph{Panel (d):} Stellar Kinematics along the galaxy's major axis as measured by \citet{SWELLSV}, line-of-sight rotation velocity $v_\text{rot}$, line-of-sight velocity dispersion $\sigma$ and the rms-velocity $v_\text{rms} = \sqrt{v_\text{rot}^2 + \sigma^2}$. The dotted line in panel (b) indicates the galaxy's effective half-light radius (in the F814W filter), $R_\text{eff} = 2.6" = 5.2$ kpc. The $v_\text{rot}$ curve reveals that J1331 is counter-rotating within $R_\text{eff}$. TO DO: Add (x,y) axis in figure b).???????}
\label{fig:specialJ1331}
\end{figure*}

\clearpage

\section{Data}

[TO DO]

\section{Surface Photometry with Multi-Gaussian Expansion} \label{kap:MGE}

\subsection{Multi-Gaussian Expansion Formalism}

[TO DO]

\subsection{MGE Photometry for J1331}

[TO DO]

\begin{figure}
\begin{minipage}[c]{\linewidth}
\centering
\includegraphics[width=0.8\textwidth]{fig/1331F814Wsci_MGE_M.ps}
\caption{??? MGE as used in the dynamical modelling ??? [TO DO: nice caption]}
\label{fig:???}
\end{minipage}
\begin{minipage}[c]{\linewidth}
\centering
\includegraphics[width=0.8\textwidth]{fig/1331F814W_MGE_disk_L.ps}
\caption{??? [TO DO: caption]}
\label{fig:???}
\end{minipage}
\end{figure}

\begin{table*}
\centering
\begin{minipage}[t]{40mm}
\caption{PSF F814W MGE ??????}
\begin{tabular}{ccc}
\hline
$k$ & $G_k$ & $\sigma_k$ [arcsec] \\\hline
1 & 0.184 & 0.038\\
2 & 0.485 & 0.085\\
3 & 0.222 & 0.169\\
4 & 0.109 & 0.487\\\hline
\end{tabular}
\label{tab:PSFMGEF814W}
\end{minipage}
\hspace{10mm}
\begin{minipage}[t]{100mm}
\caption{F814W MGE???}
\begin{tabular}{cccccc}
\hline
 & total luminosity  & surface density & \multicolumn{2}{c}{Gaussian dispersion} & axis ratio\\
$k$  & $L_k$ [counts] & $I_{0,k}$ [$L_\odot$/pc$^2$] & $\sigma_k$ [arcsec] & $\sigma_k$ [kpc] & $q'_k$\\\hline
1  &     9425.96 &      20768.  &  0.051   & 0.103  & 1.00\\
2  &    13173.0 &        3161.2 &  0.178   & 0.358  & 0.76\\
3  &    40235.0 &        1588.2 &  0.503   & 1.008  & 0.58\\
4  &    67755.2 &         502.25&  1.180   & 2.368  & 0.56\\
5  &    203677. &         136.51&  3.891   & 7.805  & 0.57\\\hline
\end{tabular}
\label{tab:MGEF814W}
\end{minipage}
\end{table*}

\begin{table}
\centering
\begin{minipage}{140mm}
\caption{Galaxy Parameters of J1331}
\begin{tabular}{lllrl}
\hline
redshift                  & $z_d$ & 0.113 & \citep{SWELLSIII}\\
angular diameter distance & $D_d$ [Mpc] & 414 & \\
scaling                   & 1 kpc / 1 arcsec & 2.006 & \\
position angle            & $\phi$ [degrees] & wrt what???\\
average axis ratio & $q'$ & 0.598\\
average ellipticity & $\epsilon = 1 - q'$ & 0.402 & \\
apparent F814W magnitude & $m_\text{F814W}$ [mag] & 15.77 & \\
total F814W luminosity & $L_\text{tot,F814W}$ [$10^{10} L_\odot$] & 5.6 & \\
effective half-light radius & $R_\text{eff}$ [arcsec] & 2.6 & \\
& $R_\text{eff}$ [pc]& 5.2 & \\
\hline
\end{tabular}
\end{minipage}
\end{table}

\clearpage

\section{Gravitational Lensing}

\subsection{Formalism and Model}

\subsubsection{Stron Gravitational Lensing Formalism}

A gravitational lens is a mass distribution, whose gravitational potential $\Phi$ acts as a lens for light coming from a source positioned somewhere on a plane behind the lens. The angular diameter distance from the observer to the lens is $D_d$, to the source plane it is $D_s$ and the distance between the lens and source plane is $D_{ds}$. The deflection potential of the lens is its potential, projected along the line of sight $z$ and rescaled to
\begin{equation}
\psi(\vec{\theta}) := \frac{D_{ds}}{D_d D_s} \frac{2}{c^2} \int \Phi(\vec{r}=D_d \vec{\theta},z) {\ \mathrm d} z, \label{eq:psidef}
\end{equation}
where $\vec{\theta}$ is a 2-dimensional vector on the plane of the sky. The light from the source at $\vec{\beta} = (\xi,\eta)$ is deflected according to the lens equation
\begin{equation}
\vec{\beta} = \vec{\theta}_i - \left.\vec{\nabla}_\theta \psi(\vec{\theta})\right|_{\vec{\theta}_i} \label{eq:lenseqpot}
\end{equation}
into an image $\vec{\theta}_i = (x_i,y_i)$. The gradient of the deflection potential $\vec{\nabla}_\theta \psi(\vec{\theta})$ is equal to the angle by which the light is deflected multiplied by $D_{ds}/D_{s}$.
\\The total time delay of an deflected light path through $\vec{\theta}$ with respect to the unperturbed light path is given by 
\begin{equation}
\Delta t(\vec{\theta}) = \frac{(1+z_d)}{c} \frac{D_d D_s}{D_{ds}} \left[ \frac 12 (\vec{\theta} - \vec{\beta})^2 - \psi(\vec{\theta})\right], \label{eq:timedelay}
\end{equation}
\citep{BartGravLens}. According to Fermat's principle the image positions will be observed at the extrema of $\Delta t(\vec{\theta})$.
\\The inverse magnification tensor
\begin{equation}
\mathscr{M}^{-1} \equiv \frac{\partial \vec{\beta}}{\partial \vec{\theta}} \overset{(\ref{eq:lenseqpot})}{=} \left(\delta_{ij} - \frac{\partial^2 \psi}{\partial \theta_i \partial \theta_j} \right)\label{eq:magnificationtensor}
\end{equation}
describes how the source position changes with image position. It also describes the distortion of the image shape for an extended source and its magnification due to lensing according to
$$\mu \equiv \frac{\text{image area}}{\text{source area}} = \det \mathscr{M}.$$
Lines in the image plane for which the magnification becomes infinite, i.e. $\det \mathscr{M}^{-1} = 0$, are called \emph{critical curves}. The corresponding lines in the source plane are called \emph{caustics}. The position of the source with respect to the caustic detemines the number of images and their configuration and shape with respect to each other.
\\The \emph{Einstein mass} $M_\text{ein}$ and \emph{Einstein radius} $R_\text{ein}$ are defined via the relation
\begin{equation*}
M_\text{ein} \equiv M_\text{proj}(<R_\text{ein}) \overset{!}{=} \pi \Sigma_\text{crit} R_\text{ein}^2,
\end{equation*}
where $\Sigma_\text{crit} \equiv \frac{c^2}{4\pi G} \frac{D_s}{D_d D_{ds}}$ is the critical density and $M_\text{proj}(<R_\text{ein})$ is the mass projected along the line-of-sight within $R_\text{ein}$. $M_\text{ein}$ is similar to the projected mass within the critical curve $M_\text{crit}$.

\subsubsection{Lens Model} %???\label{sec:lensmodel}

Following \citet{EvansWitt} we assume a scale-free model
\begin{equation*}
\psi(R',\theta) = R^{'\alpha} F(\theta) \label{eq:scalefreemodel}
\end{equation*}
for the lensing potential, consisting of an angular part $F(\theta)$ and a power-law radial part, with $(R',\theta)$ being polar coordinates on the plane of the sky. The case $\alpha = 1$ corresponds to a flat rotation curve. We expand $F(\theta)$ into a Fourier series,
\begin{equation}
F(\theta) = \frac{a_0}{2} + \sum_{k=1}^{\infty} \left(a_k \cos(k\theta) + b_k \sin (k\theta) \right). \label{eq:Fourieransatz}
\end{equation}
For this scale-free lens model the lens equation (\ref{eq:lenseqpot}) becomes
\begin{equation}
\begin{pmatrix} \xi \\ \eta \end{pmatrix} = \begin{pmatrix} R'_i \cos \theta_i - R_i^{'\alpha-1} \left(\alpha \cos \theta_i F(\theta_i) - \sin \theta_i F'(\theta_i) \right) \\ R'_i \sin \theta_i - R_i^{'\alpha-1} \left(\alpha \sin \theta_i F(\theta_i + \cos \theta_i F'(\theta_i) \right)\end{pmatrix}\label{eq:Fourierlenseq}
\end{equation}
\citep{EvansWitt}, where $F'(\theta) = \partial F(\theta) / \partial \theta$. When we fix the slope $\alpha$, then the lens equation is a purely linear problem and can be solved numerically for the source position $(\xi,\eta)$ and the Fourier parameters $(a_k,b_k)$ given one observed image at position $(x_i=R'_i \cos \theta_i,y_i=R'_i \sin \theta_i)$.

\subsection{Procedure}

\subsubsection{Image Positions}

We determine the positions of the lensing images by first subtracting a smooth model for the galaxy's surface brightness from the original image. As models we use MGE fits (cf. \S\ref{kap:MGE}) and IRAF ellipse fits (???) to the galaxy in each the F450W and F814W filter. (For example the MGE we use for F814W is the MGE given in tab. \ref{tab:MGEF814W} convolved with the PSF in tab. \ref{tab:PSFMGEF814W}.) The lensing images become then visible in the residuals (see fig. \ref{fig:lens_just_imgpos}). Because the lensing images are extended, we use the position of the brightest pixel in each of the images. We also use the F814W-MGE subtracted residuals from \citet{SWELLSIII}. The lensing positions as determined from the latter are given in tab. \ref{tab:lenspos}. The scatter of lensing positions as determined from subtracting different surface brightness models from the galaxy in different filters gives an error of $\pm 1$ pixel on the image positions.

\begin{table}
\centering
\begin{minipage}{70mm}
\begin{tabular}{r|rrrr|c}
\hline
  & A & B & C & D & G\\\hline
$x_i$ [pixel] & 12.1 & -8.5 & 21.7 & -3.3 & 0.5 $\pm \sqrt{2}$ \\
$y_i$ [pixel] & 16.6 & -10.4 & -0.5 & 19.2 & 0.5 $\pm \sqrt{2}$ \\
\hline
\end{tabular}
\caption{Positions of the lensing images (A-D) and the galaxy center (G) in fig. \ref{fig:lens_just_imgpos}. The image positions were determined from the lens subtracted image for J1331 in figure 4 of \citet{SWELLSIII}, rotated to the $(x,y)$ coordinate system in fig. \ref{fig:lens_just_imgpos}. The pixel scale is 1 pixel = 0.05 arcsec and the error of each image position is $\pm$ 1 pixel. \textit{SMALL PROBLEM: Somehow I used $\sqrt(2)$ pixel as the error on the galaxy center in the Monte Carlo sampling code instead of the 0.5 pixel I claim here. Should I change this table and the error bars in the figures to match this bug????}}
\label{tab:lenspos}
\end{minipage}
\end{table}

\subsubsection{Fitting}

As described in \S\ref{sec:lensmodel} our lensing model has the following free parameters: the source position $(\xi,\eta)$, and the radial slope $\alpha$ and Fourier parameters $(a_k,b_k)$ of the lens mass distribution in eq. (\ref{eq:scalefreemodel}) and (\ref{eq:Fourieransatz}). We want to find the lensing model which minimizes for all four images the distance between the observed image positions $\vec{\theta}_{oi}$ and those predicted by the lensing model $\vec{\theta}_{pi}$. Because we want to avoid solving the lens equation (cf. eq. (\ref{eq:lenseqpot}) and (\ref{eq:Fourierlenseq})) for $\theta_{pi}$, we follow \citet{1991ApJ...373..354K} and cast the calculation back to the source plane using the magnification tensor in eq. (\ref{eq:magnificationtensor}):
\begin{eqnarray*}
\chi^2_\text{lens} &=& \sum_{i=1}^{4} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right) \left( \vec{\theta}_{pi} - \vec{\theta}_{oi} \right)\right|^2\\
&\simeq& \sum_{i=1}^{N} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right)  \left.\mathscr{M}\right|_{\vec{\theta}=\vec{\theta}_{oi}} \left( \begin{matrix} \xi - \tilde{\xi}_i \\ \eta - \tilde{\eta}_i \end{matrix} \right) \right|^2,
\end{eqnarray*}
where $(\Delta_x,\Delta_y)$ are the measurement errors of the image positions $\vec{\theta}_{oi}$. $\left.\mathscr{M}\right|_{\vec{\theta}=\vec{\theta}_{oi}}$ is the magnification tensor and $(\tilde{\xi}_i,\tilde{\eta}_i)$ the source position according to the lens equation evaluated at $\vec{\theta}_{oi}$. Following \citet{GlennEC} we add a term
\begin{equation*}
\chi^2_\text{shape} = \lambda \sum_{k \geq 3} \frac{\left(a_k^2 +b_k^2 \right)}{a_0^2} 
\end{equation*}
which forces the shape of the mass distribution to be close to an ellipse. The total $\chi^2$ to minimize is therefore
\begin{equation*}
\chi^2 = \chi^2_\text{lens} + \chi^2_\text{shape}
\end{equation*}
We set $a_1 = b_1 = 0$, which corresponds to the choice of origin; in this case the center of the galaxy.
\\To be able to constrain the slope $\alpha$, we would have needed flux ratios for the images as in \citet{GlennEC}. But the extended quality of the images and the uncertainty in surface brightness subtraction makes flux determination too unreliable and we do not include them in the fitting. Even though the constraint from just the image position fit on $\alpha$ is very weak, we were however able to show that the image positions in tab. \ref{tab:lenspos} minimize $\chi^2$ at $\alpha=1$ and also our other image position sets from different models and filters are consistent with a flat rotation curve. In the following we therefore set $\alpha=1$.

\subsection{Results}

\subsubsection{Best Fit Lens Model}

The best fit lens model for the image positions in tab. \ref{tab:lenspos} is given in the first column of tab. \ref{tab:bestfitlensmodel}. Fig. \ref{fig:lensbestfiteinsteincurves} shows the corresponding critical curve, caustic and Einstein radius, and the best fit source position. In this case, where $\alpha=1$, the critical curve is also an equidensity contour of the galaxy model. Fig. \ref{fig:lensbestfittimedelay} overplots the smoothed residuals from the F814W image subtracted by the IRAF ellipse fit to the surface brightness with the contours of the best fit model's time delay surface. This demonstrates that, although we did not include any information about the shape of the lensing images in the fit, it is consistent with the predicted distortion for an extended source by the best fit lens model.
\\To estimate how the uncertainties in the determination of the image positions and galaxy center affect the results, we Monte Carlo sample random positions from a two-dimensional Normal distribution centered at the positions in tab. \ref{tab:lenspos} and a standard deviation corresponding to the measurement error of 1 pixel. A Gaussian fit to the resulting distributions of best fit values leads to the constraints on the shape parameters and Einstein quantities in the second column in tab. \ref{tab:bestfitlensmodel}. We therefore constrain the Einstein radius to within 2\%, $R_\text{ein} = (0.91 \pm 0.02)$ arcsec and the projected mass within the critical curve with a relative error of 4\%, $M_\text{crit} =(7.9\pm0.3)\cdot 10^{10} M_\odot$. Our measurement of $R_\text{ein}$ is consistent with that from \citet{SWELLSIII}, $R_\text{ein,SWELLS} = (0.96 \pm 0.04)$ arcsec. The relative difference between our critical mass and that of \citet{SWELLSIII}, $M_\text{crit,SWELLS} =(8.86\pm0.61)\cdot 10^{10} M_\odot$, is 13\%.

\begin{table*}
\centering
\caption{??? in tab. \ref{tab:lenspos}, for $\alpha = 1$}
\begin{tabular}{llrrclr}
\hline
 &  & \multicolumn{1}{c}{lens model for} &\multicolumn{4}{c}{lens model from Monte Carlo sampling  } \\
 &  & \multicolumn{1}{c}{peak image positions}  & \multicolumn{4}{c}{of image positions }  \\ \hline
Einstein Radius      & $R_\text{ein}$ [arcsec]             & $0.907$ & $0.91$  & $\pm$ & $     0.02$ & ($2\%$)\\
Einstein Mass        & $M_\text{ein}$ [$10^{10} M_\odot$]  & $7.72$  & $7.8 $  & $\pm$ & $      0.3$ & ($4\%$) \\
Critical Mass        & $M_\text{crit}$ [$10^{10} M_\odot$] & $7.87$  & $7.9$   & $\pm$ & $      0.3$ & ($4\%$)\\
Source Position      & $\xi$ [arcsec]                      & $0.095$ & $0.09 $ & $\pm$ & $     0.03$ & ($28\%$)\\
                     & $\eta$ [arcsec]                     & $0.107$ & $0.10 $ & $\pm$ & $     0.03$ & ($27\%$)\\
Fourier Coefficients & $a_0$                               & $1.814$ & $1.82 $ & $\pm$ & $   0.04$ & (2\%)\\
                     & $a_2$                               & $0.012$ & $ 0.011 $ & $\pm$ & $    0.004$ & (35\%)\\
                     & $b_2$                               & $-0.057$ & $-0.06 $  & $\pm$ & $  0.01$ & (25\%)\\
                     & $a_3$                               & $-0.0001$& $0.0000 $ & $\pm$ & $   0.0006$ & \\
                     & $b_3$                               & $-0.0002$&$0.000 $   & $\pm$ & $  0.001$ & \\\hline
\end{tabular}  
\label{tab:bestfitlensmodel} 
\end{table*}

\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_einstein.ps}
  \caption{??? Critical curves, Einstein radius, caustics, source position for best fit model. ??? [TO DO: nice caption]}
  \label{fig:lensbestfiteinsteincurves}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_timedelay.ps}
  \caption{??? Time delay surface ??? [TO DO: nice caption]}
  \label{fig:lensbestfittimedelay}
\end{subfigure}
\caption{???}
\label{fig:???}
\end{figure*}

\subsubsection{Comparison with Light Distribution}

Fig. \ref{fig:lenscomparemass} shows the surface mass distribution as predicted by the best fit model in tab. \ref{tab:bestfitlensmodel}. We introduce random noise according to the uncertainties in the Fourier shape parameters to create a mock observation that visualizes the effect of the measurement errors. To be able to compare the predicted mass distribution to the observed light distribution we transform the surface brightness into a mass density: We first integrate the MGE in tab. \ref{tab:MGEF814W} to get the total luminosity within the Einstein radius and the predicted mass-to-light ratio as $\Upsilon_\text{I,ein} = M_\text{ein} / L_\text{I,ein}$. Fig. \ref{fig:lenscomparelight} shows then the observed surface brightness in the F814W filter multiplied by $\Upsilon_\text{I,ein}$.  Fig. \ref{fig:lenscompareboth} finally compares equidensity contours at the same values of both the predicted lens mass distribution and the observed surface brightness times $\Upsilon_\text{I,ein}$. We note the following three facts: 1.The mass predicted from lensing and the observed light distribution are oriented in the same direction. 2. Within the Einstein radius mass and light distribution have the same shape, while further out the mass distribution is more roundish. 3. The light distribution drops faster than the mass with increasing radius. This could indicate that the stellar component of the galaxy is superimposed by a more roundish dark matter component.

\begin{table}
\centering
\caption{???}
\begin{tabular}{cc}
\hline
Total I-band luminosity within $R_\text{ein}$ & Mass-to-light ratio within $R_\text{ein}$\\
 $L_\text{I,ein}$ [$10^{10} L_\odot$] & $\Upsilon_\text{I,ein} = M_\text{ein} / L_\text{I,ein}$ [$\Upsilon_\odot$]\\\hline
1.40 & 5.56\\\hline
\end{tabular}  
\label{tab:einsteinML} 
\end{table}

\begin{figure*}
\centering
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_surface_brightness.ps}
  \caption{???}
  \label{fig:lenscomparelight}
\end{subfigure}%
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_surface_density.ps}
  \caption{???}
  \label{fig:lenscomparemass}
\end{subfigure}
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/paper_lensmass_brightness_compare.ps}
  \caption{???}
  \label{fig:lenscompareboth}
\end{subfigure}
\caption{??? Preliminary crappy caption: Left: OBSERVED surface bightness multiplied with M/L in Einstein radius (overplotted in red). Middle: BEST FIT MODEL for mass distribution from lensing (including "wriggles" due to uncertainties in image positions). Contours are at the same levels. Right: Same contours, to directly show the difference in shape. ??? [TO DO: nice caption]}
\label{fig:???}
\end{figure*}

\clearpage

\section{Dynamical Modelling}

\subsection{Jeans Axisymmetric Modelling (JAM)}

[TO DO]

\subsection{JAM based on Surface Brightness}

\subsubsection{... with "Mass-follows-Light" and Velocity Anisotropy}

[TO DO]

\begin{figure*}
\centering
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[height=6cm]{fig/jam_A2_vrms.ps}
  \caption{??? Preliminary crappy caption: Failed try to fit a mass-follows-light model to the central regions of the galaxy. "Best fit" velocity anisotropy $\beta = -1/2$ is pegged at lower limit. ??? [TO DO: nice caption]}
  \label{fig:???}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[height=6cm]{fig/lensing_JAM_comparision.ps}
  \caption{??? Preliminary crappy caption: Observed vrms is overplotted (not fitted) with best fit lens mass models for $\alpha = 1$ (red) and $\alpha = 1.1$ (green).??? [TO DO: nice caption]}
  \label{fig:???}
\end{minipage}
\end{figure*}

\subsubsection{... with Increasing Mass-to-Light Ratio Gradient}

[TO DO]

\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[height=6cm]{fig/jam_G_vrms.ps}
  \caption{???}
  \label{fig:???}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[height=6cm]{fig/jam_G_enclMass.ps}
  \caption{???}
  \label{fig:???}
\end{subfigure}
\caption{??? Using the surface brightness MGE for the dynamical modelling: each Gaussian got it's own M/L such that the overall M/L is increasing with radius. This is the best fit model. The enclosed mass is overplotted with Einstein mass with 4\% error (overplotted, not fitted). ??? [TO DO: nice caption]}
\label{fig:???}
\end{figure*}

\subsubsection{... with the Lens Mass Model}

[TO DO]

\clearpage

\subsection{JAM with a NFW Dark Matter Halo}

\subsubsection{Sampling with a Markov Monte Carlo Chain}

[TO DO]

\begin{figure*}
\centering
\includegraphics[width=0.9\linewidth]{fig/B4_contour_plot_short.ps}
\caption{??? Preliminary crappy caption: Result of the MCMC sampling of the parameter space for a model with NFW halo and constant velocity anisotropy. Green and blue shows the priors. Grey diamonds are the models shown in next figure. ??? [TO DO: nice caption]}
\label{fig:???}
\end{figure*}

\begin{figure*}
\centering
\begin{subfigure}{\textwidth}
  \centering
  \includegraphics[width=0.8\linewidth]{fig/B4_rms_error_curves.ps}
  \caption{???}
  \label{fig:???}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_vcirc.ps}
  \caption{????????}
  \label{fig:???}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_projmass.ps}
  \caption{???}
  \label{fig:???}
\end{subfigure}
\caption{??? Preliminary crappy caption: 12 samples from the parameter pdf found with the MCMC above for the model with NFW halo and constant velocity anisotropy. Big red dot shows the Einstein mass with a 10\% error (used in fit). ??? [TO DO: nice caption]}
\label{fig:???}
\end{figure*}

\subsubsection{Predicting the Rotation Curve at larger Radii}

[TO DO]

\begin{figure*}
\centering
\includegraphics[width=0.7\linewidth]{fig/B4_rms_rot_curves_best_model.ps}
\caption{??? Preliminary crappy caption: Model: NFW halo and constant velocity anisotropy, using the the mean / peak values of the MCMC result in the above pdf for the model parameters. Fitting one more free parameter to the rotation curve in the inner regions, predicting the rotation curve and dispersion at larger radii. Green dots are gas kinematics. ??? [TO DO: nice caption]}
\label{fig:???}
\end{figure*}

\section{Discussion and Conclusion}

\subsection{Does J1331 have a Merger History?}

[TO DO]

\subsection{Summary}

[TO DO]

%---------------------------------------------------------------------------
\bibliographystyle{mn2e}
\bibliography{literaturelist}
%---------------------------------------------------------------------------

\label{lastpage}

\end{document}

### 2015-08-04 LensingPaper_draft_v1.01.tex
Restructured paper and wrote a first (too long) version of abstract.

@@
-% mn2esample.tex
-%
-% v2.1 released 22nd May 2002 (G. Hutton)
-%
-% The mnsample.tex file has been amended to highlight
-% the proper use of LaTeX2e code with the class file
-% and using natbib cross-referencing. These changes
-% do not reflect the original paper by A. V. Raveendran.
-%
-% Previous versions of this sample document were
-% compatible with the LaTeX 2.09 style file mn.sty
-% v1.2 released 5th September 1994 (M. Reed)
-% v1.1 released 18th July 1994
-% v1.0 released 28th January 1994
-
 \documentclass[useAMS,usenatbib]{mn2e}
-
-% If your system does not have the AMS fonts version 2.0 installed, then
-% remove the useAMS option.
-%
-% useAMS allows you to obtain upright Greek characters.
-% e.g. \umu, \upi etc.  See the section on "Upright Greek characters" in
-% this guide for further information.
-%
-% If you are using AMS 2.0 fonts, bold math letters/symbols are available
-% at a larger range of sizes for NFSS release 1 and 2 (using \boldmath or
-% preferably \bmath).
-%
-% The usenatbib command allows the use of Patrick Daly's natbib.sty for
-% cross-referencing.
-%
-% If you wish to typeset the paper in Times font (if you do not have the
-% PostScript Type 1 Computer Modern fonts you will need to do this to get
-% smoother fonts in a PDF file) then uncomment the next line
-% \usepackage{Times}
-
-%%%%% AUTHORS - PLACE YOUR OWN MACROS HERE %%%%%
 
@@
 \usepackage{ mathrsfs } %for slanted letters in math mode
+
+%_____FORMAT_____
+\setcounter{secnumdepth}{2}	%depth of section numbering
 
@@
 
+%--------------------------------------------
+%Abstract
 \begin{abstract}
-[TO DO]
+\include{docs/abstract_v1.01}
 \end{abstract}
+%--------------------------------------------
 
@@
 
-\section{Introduction}
+%--------------------------------------------
+%Introduction
+\include{docs/introduction_v1.01}
+%--------------------------------------------
 
-[TO DO]
+%------------------------
+\include{docs/data_v1.01}
+%------------------------
 
-\begin{figure*}
-\centering
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[width=.9\linewidth]{fig/first_glimpse_450.ps}
-  \caption{J1331 in F450W ("blue")}
-  \label{fig:???}
-\end{subfigure}%
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[width=.9\linewidth]{fig/first_glimpse_814.ps}
-  \caption{J1331 in F814W ("red")}
-  \label{fig:???}
-\end{subfigure}
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[width=.9\linewidth]{fig/lens_imgpos.ps}
-  \caption{The lensing images}
-  \label{fig:lens_just_imgpos}
-\end{subfigure}%
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[width=.9\linewidth]{fig/stellar_kinematics_data.ps}
-  \caption{Stellar Kinematics by \citet{SWELLSV}}
-  \label{fig:???}
-\end{subfigure}
-\caption{Hubble Space telescope (HST) images and stellar kinematics of the galaxy SDSS J1331+3638 (J1331), which has a large counter-rotating core and whose bulge acts as a strong lens for a bluish background source.
-\emph{Panel (a) and (b):} HST images of J1331 by \citet{SWELLSI} in two filters, F450W in panel (a) and F814W in panel (b).
-The galaxy's coordinates on the sky are right ascension $\alpha$ = 202.91800$^\circ$ and declination $\delta$ = 36.46999$^\circ$ (epoch J2000).
-Image orientation and scaling are indicated in panel (a); the scaling transformation from arcseconds to the physical size of the galaxy in kpc uses the galaxy's redshift $z_d = 0.113$ \citep{SWELLSIII}.
-The black solid line in panel (a) shows the orientation of the major-axis.
-The line has a length of 10 arcsec and indicates the region within which we carry out the Jeans modelling.
-(NOT ALL THE TIME.???????) \emph{Panel (c):} The central region of J1331 in F450W, surface brightness subtracted.
-An IRAF ellipse ????
-fit to the F450W surface brightness in panel (a) was subtracted from the image.
-The (smoothed) residuals within the white square in panel (a) are shown in panel (c).
-Four bright blobs (A,B,C and D) become visible, which are arranged in a typical strong lensing configuration around the center of the galaxy (G).
-\emph{Panel (d):} Stellar Kinematics along the galaxy's major axis as measured by \citet{SWELLSV}, line-of-sight rotation velocity $v_\text{rot}$, line-of-sight velocity dispersion $\sigma$ and the rms-velocity $v_\text{rms} = \sqrt{v_\text{rot}^2 + \sigma^2}$.
-The dotted line in panel (b) indicates the galaxy's effective half-light radius (in the F814W filter), $R_\text{eff} = 2.6" = 5.2$ kpc.
-The $v_\text{rot}$ curve reveals that J1331 is counter-rotating within $R_\text{eff}$.
-TO DO: Add (x,y) axis in figure b).???????}
-\label{fig:specialJ1331}
-\end{figure*}
+%------------------------
+\section{Modelling}
+\include{docs/model_MGE_v1.01}
+\include{docs/model_lensing_v1.01}
+\include{docs/model_fitting_v1.01}
+\include{docs/model_JAM_v1.01}
+%------------------------
 
-\clearpage
+%------------------------
+\section{Results}
+\include{docs/results_photometry_v1.01}
+\include{docs/results_lensing_v1.01}
+\include{docs/results_JAMwithSB_v1.01}
+\include{docs/results_JAMwithNFW_v1.01}
+%------------------------
 
-\section{Data}
-
-[TO DO]
-
-\section{Surface Photometry with Multi-Gaussian Expansion} \label{kap:MGE}
-
-\subsection{Multi-Gaussian Expansion Formalism}
-
-[TO DO]
-
-\subsection{MGE Photometry for J1331}
-
-[TO DO]
-
-\begin{figure}
-\begin{minipage}[c]{\linewidth}
-\centering
-\includegraphics[width=0.8\textwidth]{fig/1331F814Wsci_MGE_M.ps}
-\caption{??? MGE as used in the dynamical modelling ??? [TO DO: nice caption]}
-\label{fig:???}
-\end{minipage}
-\begin{minipage}[c]{\linewidth}
-\centering
-\includegraphics[width=0.8\textwidth]{fig/1331F814W_MGE_disk_L.ps}
-\caption{??? [TO DO: caption]}
-\label{fig:???}
-\end{minipage}
-\end{figure}
-
-\begin{table*}
-\centering
-\begin{minipage}[t]{40mm}
-\caption{PSF F814W MGE ??????}
-\begin{tabular}{ccc}
-\hline
-$k$ & $G_k$ & $\sigma_k$ [arcsec] \\\hline
-1 & 0.184 & 0.038\\
-2 & 0.485 & 0.085\\
-3 & 0.222 & 0.169\\
-4 & 0.109 & 0.487\\\hline
-\end{tabular}
-\label{tab:PSFMGEF814W}
-\end{minipage}
-\hspace{10mm}
-\begin{minipage}[t]{100mm}
-\caption{F814W MGE???}
-\begin{tabular}{cccccc}
-\hline
- & total luminosity  & surface density & \multicolumn{2}{c}{Gaussian dispersion} & axis ratio\\
-$k$  & $L_k$ [counts] & $I_{0,k}$ [$L_\odot$/pc$^2$] & $\sigma_k$ [arcsec] & $\sigma_k$ [kpc] & $q'_k$\\\hline
-1  &     9425.96 &      20768.  &  0.051   & 0.103  & 1.00\\
-2  &    13173.0 &        3161.2 &  0.178   & 0.358  & 0.76\\
-3  &    40235.0 &        1588.2 &  0.503   & 1.008  & 0.58\\
-4  &    67755.2 &         502.25&  1.180   & 2.368  & 0.56\\
-5  &    203677. &         136.51&  3.891   & 7.805  & 0.57\\\hline
-\end{tabular}
-\label{tab:MGEF814W}
-\end{minipage}
-\end{table*}
-
-\begin{table}
-\centering
-\begin{minipage}{140mm}
-\caption{Galaxy Parameters of J1331}
-\begin{tabular}{lllrl}
-\hline
-redshift                  & $z_d$ & 0.113 & \citep{SWELLSIII}\\
-angular diameter distance & $D_d$ [Mpc] & 414 & \\
-scaling                   & 1 kpc / 1 arcsec & 2.006 & \\
-position angle            & $\phi$ [degrees] & wrt what???\\
-average axis ratio & $q'$ & 0.598\\
-average ellipticity & $\epsilon = 1 - q'$ & 0.402 & \\
-apparent F814W magnitude & $m_\text{F814W}$ [mag] & 15.77 & \\
-total F814W luminosity & $L_\text{tot,F814W}$ [$10^{10} L_\odot$] & 5.6 & \\
-effective half-light radius & $R_\text{eff}$ [arcsec] & 2.6 & \\
-& $R_\text{eff}$ [pc]& 5.2 & \\
-\hline
-\end{tabular}
-\end{minipage}
-\end{table}
-
-\clearpage
-
-\section{Gravitational Lensing}
-
-\subsection{Formalism and Model}
-
-\subsubsection{Stron Gravitational Lensing Formalism}
-
-A gravitational lens is a mass distribution, whose gravitational potential $\Phi$ acts as a lens for light coming from a source positioned somewhere on a plane behind the lens.
-The angular diameter distance from the observer to the lens is $D_d$, to the source plane it is $D_s$ and the distance between the lens and source plane is $D_{ds}$.
-The deflection potential of the lens is its potential, projected along the line of sight $z$ and rescaled to
-\begin{equation}
-\psi(\vec{\theta}) := \frac{D_{ds}}{D_d D_s} \frac{2}{c^2} \int \Phi(\vec{r}=D_d \vec{\theta},z) {\ \mathrm d} z, \label{eq:psidef}
-\end{equation}
-where $\vec{\theta}$ is a 2-dimensional vector on the plane of the sky. The light from the source at $\vec{\beta} = (\xi,\eta)$ is deflected according to the lens equation
-\begin{equation}
-\vec{\beta} = \vec{\theta}_i - \left.\vec{\nabla}_\theta \psi(\vec{\theta})\right|_{\vec{\theta}_i} \label{eq:lenseqpot}
-\end{equation}
-into an image $\vec{\theta}_i = (x_i,y_i)$.
-The gradient of the deflection potential $\vec{\nabla}_\theta \psi(\vec{\theta})$ is equal to the angle by which the light is deflected multiplied by $D_{ds}/D_{s}$.
-\\The total time delay of an deflected light path through $\vec{\theta}$ with respect to the unperturbed light path is given by 
-\begin{equation}
-\Delta t(\vec{\theta}) = \frac{(1+z_d)}{c} \frac{D_d D_s}{D_{ds}} \left[ \frac 12 (\vec{\theta} - \vec{\beta})^2 - \psi(\vec{\theta})\right], \label{eq:timedelay}
-\end{equation}
-\citep{BartGravLens}. According to Fermat's principle the image positions will be observed at the extrema of $\Delta t(\vec{\theta})$.
-\\The inverse magnification tensor
-\begin{equation}
-\mathscr{M}^{-1} \equiv \frac{\partial \vec{\beta}}{\partial \vec{\theta}} \overset{(\ref{eq:lenseqpot})}{=} \left(\delta_{ij} - \frac{\partial^2 \psi}{\partial \theta_i \partial \theta_j} \right)\label{eq:magnificationtensor}
-\end{equation}
-describes how the source position changes with image position. It also describes the distortion of the image shape for an extended source and its magnification due to lensing according to
-$$\mu \equiv \frac{\text{image area}}{\text{source area}} = \det \mathscr{M}.$$
-Lines in the image plane for which the magnification becomes infinite, i.e.
-$\det \mathscr{M}^{-1} = 0$, are called \emph{critical curves}.
-The corresponding lines in the source plane are called \emph{caustics}.
-The position of the source with respect to the caustic detemines the number of images and their configuration and shape with respect to each other.
-\\The \emph{Einstein mass} $M_\text{ein}$ and \emph{Einstein radius} $R_\text{ein}$ are defined via the relation
-\begin{equation*}
-M_\text{ein} \equiv M_\text{proj}(<R_\text{ein}) \overset{!}{=} \pi \Sigma_\text{crit} R_\text{ein}^2,
-\end{equation*}
-where $\Sigma_\text{crit} \equiv \frac{c^2}{4\pi G} \frac{D_s}{D_d D_{ds}}$ is the critical density and $M_\text{proj}(<R_\text{ein})$ is the mass projected along the line-of-sight within $R_\text{ein}$.
-$M_\text{ein}$ is similar to the projected mass within the critical curve $M_\text{crit}$.
-
-\subsubsection{Lens Model} %???\label{sec:lensmodel}
-
-Following \citet{EvansWitt} we assume a scale-free model
-\begin{equation*}
-\psi(R',\theta) = R^{'\alpha} F(\theta) \label{eq:scalefreemodel}
-\end{equation*}
-for the lensing potential, consisting of an angular part $F(\theta)$ and a power-law radial part, with $(R',\theta)$ being polar coordinates on the plane of the sky.
-The case $\alpha = 1$ corresponds to a flat rotation curve.
-We expand $F(\theta)$ into a Fourier series,
-\begin{equation}
-F(\theta) = \frac{a_0}{2} + \sum_{k=1}^{\infty} \left(a_k \cos(k\theta) + b_k \sin (k\theta) \right). \label{eq:Fourieransatz}
-\end{equation}
-For this scale-free lens model the lens equation (\ref{eq:lenseqpot}) becomes
-\begin{equation}
-\begin{pmatrix} \xi \\ \eta \end{pmatrix} = \begin{pmatrix} R'_i \cos \theta_i - R_i^{'\alpha-1} \left(\alpha \cos \theta_i F(\theta_i) - \sin \theta_i F'(\theta_i) \right) \\ R'_i \sin \theta_i - R_i^{'\alpha-1} \left(\alpha \sin \theta_i F(\theta_i + \cos \theta_i F'(\theta_i) \right)\end{pmatrix}\label{eq:Fourierlenseq}
-\end{equation}
-\citep{EvansWitt}, where $F'(\theta) = \partial F(\theta) / \partial \theta$.
-When we fix the slope $\alpha$, then the lens equation is a purely linear problem and can be solved numerically for the source position $(\xi,\eta)$ and the Fourier parameters $(a_k,b_k)$ given one observed image at position $(x_i=R'_i \cos \theta_i,y_i=R'_i \sin \theta_i)$.
-
-\subsection{Procedure}
-
-\subsubsection{Image Positions}
-
-We determine the positions of the lensing images by first subtracting a smooth model for the galaxy's surface brightness from the original image.
-As models we use MGE fits (cf.
-\S\ref{kap:MGE}) and IRAF ellipse fits (???) to the galaxy in each the F450W and F814W filter.
-(For example the MGE we use for F814W is the MGE given in tab.
-\ref{tab:MGEF814W} convolved with the PSF in tab.
-\ref{tab:PSFMGEF814W}.) The lensing images become then visible in the residuals (see fig.
-\ref{fig:lens_just_imgpos}).
-Because the lensing images are extended, we use the position of the brightest pixel in each of the images.
-We also use the F814W-MGE subtracted residuals from \citet{SWELLSIII}.
-The lensing positions as determined from the latter are given in tab.
-\ref{tab:lenspos}.
-The scatter of lensing positions as determined from subtracting different surface brightness models from the galaxy in different filters gives an error of $\pm 1$ pixel on the image positions.
-
-\begin{table}
-\centering
-\begin{minipage}{70mm}
-\begin{tabular}{r|rrrr|c}
-\hline
-  & A & B & C & D & G\\\hline
-$x_i$ [pixel] & 12.1 & -8.5 & 21.7 & -3.3 & 0.5 $\pm \sqrt{2}$ \\
-$y_i$ [pixel] & 16.6 & -10.4 & -0.5 & 19.2 & 0.5 $\pm \sqrt{2}$ \\
-\hline
-\end{tabular}
-\caption{Positions of the lensing images (A-D) and the galaxy center (G) in fig.
-\ref{fig:lens_just_imgpos}.
-The image positions were determined from the lens subtracted image for J1331 in figure 4 of \citet{SWELLSIII}, rotated to the $(x,y)$ coordinate system in fig.
-\ref{fig:lens_just_imgpos}.
-The pixel scale is 1 pixel = 0.05 arcsec and the error of each image position is $\pm$ 1 pixel.
-\textit{SMALL PROBLEM: Somehow I used $\sqrt(2)$ pixel as the error on the galaxy center in the Monte Carlo sampling code instead of the 0.5 pixel I claim here.
-Should I change this table and the error bars in the figures to match this bug????}}
-\label{tab:lenspos}
-\end{minipage}
-\end{table}
-
-\subsubsection{Fitting}
-
-As described in \S\ref{sec:lensmodel} our lensing model has the following free parameters: the source position $(\xi,\eta)$, and the radial slope $\alpha$ and Fourier parameters $(a_k,b_k)$ of the lens mass distribution in eq.
-(\ref{eq:scalefreemodel}) and (\ref{eq:Fourieransatz}).
-We want to find the lensing model which minimizes for all four images the distance between the observed image positions $\vec{\theta}_{oi}$ and those predicted by the lensing model $\vec{\theta}_{pi}$.
-Because we want to avoid solving the lens equation (cf.
-eq.
-(\ref{eq:lenseqpot}) and (\ref{eq:Fourierlenseq})) for $\theta_{pi}$, we follow \citet{1991ApJ...373..354K} and cast the calculation back to the source plane using the magnification tensor in eq.
-(\ref{eq:magnificationtensor}):
-\begin{eqnarray*}
-\chi^2_\text{lens} &=& \sum_{i=1}^{4} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right) \left( \vec{\theta}_{pi} - \vec{\theta}_{oi} \right)\right|^2\\
-&\simeq& \sum_{i=1}^{N} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right)  \left.\mathscr{M}\right|_{\vec{\theta}=\vec{\theta}_{oi}} \left( \begin{matrix} \xi - \tilde{\xi}_i \\ \eta - \tilde{\eta}_i \end{matrix} \right) \right|^2,
-\end{eqnarray*}
-where $(\Delta_x,\Delta_y)$ are the measurement errors of the image positions $\vec{\theta}_{oi}$.
-$\left.\mathscr{M}\right|_{\vec{\theta}=\vec{\theta}_{oi}}$ is the magnification tensor and $(\tilde{\xi}_i,\tilde{\eta}_i)$ the source position according to the lens equation evaluated at $\vec{\theta}_{oi}$.
-Following \citet{GlennEC} we add a term
-\begin{equation*}
-\chi^2_\text{shape} = \lambda \sum_{k \geq 3} \frac{\left(a_k^2 +b_k^2 \right)}{a_0^2} 
-\end{equation*}
-which forces the shape of the mass distribution to be close to an ellipse. The total $\chi^2$ to minimize is therefore
-\begin{equation*}
-\chi^2 = \chi^2_\text{lens} + \chi^2_\text{shape}
-\end{equation*}
-We set $a_1 = b_1 = 0$, which corresponds to the choice of origin; in this case the center of the galaxy.
-\\To be able to constrain the slope $\alpha$, we would have needed flux ratios for the images as in \citet{GlennEC}.
-But the extended quality of the images and the uncertainty in surface brightness subtraction makes flux determination too unreliable and we do not include them in the fitting.
-Even though the constraint from just the image position fit on $\alpha$ is very weak, we were however able to show that the image positions in tab.
-\ref{tab:lenspos} minimize $\chi^2$ at $\alpha=1$ and also our other image position sets from different models and filters are consistent with a flat rotation curve.
-In the following we therefore set $\alpha=1$.
-
-\subsection{Results}
-
-\subsubsection{Best Fit Lens Model}
-
-The best fit lens model for the image positions in tab.
-\ref{tab:lenspos} is given in the first column of tab.
-\ref{tab:bestfitlensmodel}.
-Fig.
-\ref{fig:lensbestfiteinsteincurves} shows the corresponding critical curve, caustic and Einstein radius, and the best fit source position.
-In this case, where $\alpha=1$, the critical curve is also an equidensity contour of the galaxy model.
-Fig.
-\ref{fig:lensbestfittimedelay} overplots the smoothed residuals from the F814W image subtracted by the IRAF ellipse fit to the surface brightness with the contours of the best fit model's time delay surface.
-This demonstrates that, although we did not include any information about the shape of the lensing images in the fit, it is consistent with the predicted distortion for an extended source by the best fit lens model.
-\\To estimate how the uncertainties in the determination of the image positions and galaxy center affect the results, we Monte Carlo sample random positions from a two-dimensional Normal distribution centered at the positions in tab.
-\ref{tab:lenspos} and a standard deviation corresponding to the measurement error of 1 pixel.
-A Gaussian fit to the resulting distributions of best fit values leads to the constraints on the shape parameters and Einstein quantities in the second column in tab.
-\ref{tab:bestfitlensmodel}.
-We therefore constrain the Einstein radius to within 2\%, $R_\text{ein} = (0.91 \pm 0.02)$ arcsec and the projected mass within the critical curve with a relative error of 4\%, $M_\text{crit} =(7.9\pm0.3)\cdot 10^{10} M_\odot$.
-Our measurement of $R_\text{ein}$ is consistent with that from \citet{SWELLSIII}, $R_\text{ein,SWELLS} = (0.96 \pm 0.04)$ arcsec.
-The relative difference between our critical mass and that of \citet{SWELLSIII}, $M_\text{crit,SWELLS} =(8.86\pm0.61)\cdot 10^{10} M_\odot$, is 13\%.
-
-\begin{table*}
-\centering
-\caption{??? in tab. \ref{tab:lenspos}, for $\alpha = 1$}
-\begin{tabular}{llrrclr}
-\hline
- &  & \multicolumn{1}{c}{lens model for} &\multicolumn{4}{c}{lens model from Monte Carlo sampling  } \\
- &  & \multicolumn{1}{c}{peak image positions}  & \multicolumn{4}{c}{of image positions }  \\ \hline
-Einstein Radius      & $R_\text{ein}$ [arcsec]             & $0.907$ & $0.91$  & $\pm$ & $     0.02$ & ($2\%$)\\
-Einstein Mass        & $M_\text{ein}$ [$10^{10} M_\odot$]  & $7.72$  & $7.8 $  & $\pm$ & $      0.3$ & ($4\%$) \\
-Critical Mass        & $M_\text{crit}$ [$10^{10} M_\odot$] & $7.87$  & $7.9$   & $\pm$ & $      0.3$ & ($4\%$)\\
-Source Position      & $\xi$ [arcsec]                      & $0.095$ & $0.09 $ & $\pm$ & $     0.03$ & ($28\%$)\\
-                     & $\eta$ [arcsec]                     & $0.107$ & $0.10 $ & $\pm$ & $     0.03$ & ($27\%$)\\
-Fourier Coefficients & $a_0$                               & $1.814$ & $1.82 $ & $\pm$ & $   0.04$ & (2\%)\\
-                     & $a_2$                               & $0.012$ & $ 0.011 $ & $\pm$ & $    0.004$ & (35\%)\\
-                     & $b_2$                               & $-0.057$ & $-0.06 $  & $\pm$ & $  0.01$ & (25\%)\\
-                     & $a_3$                               & $-0.0001$& $0.0000 $ & $\pm$ & $   0.0006$ & \\
-                     & $b_3$                               & $-0.0002$&$0.000 $   & $\pm$ & $  0.001$ & \\\hline
-\end{tabular}  
-\label{tab:bestfitlensmodel} 
-\end{table*}
-
-\begin{figure*}
-\centering
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[width=.9\linewidth]{fig/lens_einstein.ps}
-  \caption{??? Critical curves, Einstein radius, caustics, source position for best fit model. ??? [TO DO: nice caption]}
-  \label{fig:lensbestfiteinsteincurves}
-\end{subfigure}%
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[width=.9\linewidth]{fig/lens_timedelay.ps}
-  \caption{??? Time delay surface ??? [TO DO: nice caption]}
-  \label{fig:lensbestfittimedelay}
-\end{subfigure}
-\caption{???}
-\label{fig:???}
-\end{figure*}
-
-\subsubsection{Comparison with Light Distribution}
-
-Fig.
-\ref{fig:lenscomparemass} shows the surface mass distribution as predicted by the best fit model in tab.
-\ref{tab:bestfitlensmodel}.
-We introduce random noise according to the uncertainties in the Fourier shape parameters to create a mock observation that visualizes the effect of the measurement errors.
-To be able to compare the predicted mass distribution to the observed light distribution we transform the surface brightness into a mass density: We first integrate the MGE in tab.
-\ref{tab:MGEF814W} to get the total luminosity within the Einstein radius and the predicted mass-to-light ratio as $\Upsilon_\text{I,ein} = M_\text{ein} / L_\text{I,ein}$.
-Fig.
-\ref{fig:lenscomparelight} shows then the observed surface brightness in the F814W filter multiplied by $\Upsilon_\text{I,ein}$.
-Fig.
-\ref{fig:lenscompareboth} finally compares equidensity contours at the same values of both the predicted lens mass distribution and the observed surface brightness times $\Upsilon_\text{I,ein}$.
-We note the following three facts: 1.The mass predicted from lensing and the observed light distribution are oriented in the same direction.
-2.
-Within the Einstein radius mass and light distribution have the same shape, while further out the mass distribution is more roundish.
-3.
-The light distribution drops faster than the mass with increasing radius.
-This could indicate that the stellar component of the galaxy is superimposed by a more roundish dark matter component.
-
-\begin{table}
-\centering
-\caption{???}
-\begin{tabular}{cc}
-\hline
-Total I-band luminosity within $R_\text{ein}$ & Mass-to-light ratio within $R_\text{ein}$\\
- $L_\text{I,ein}$ [$10^{10} L_\odot$] & $\Upsilon_\text{I,ein} = M_\text{ein} / L_\text{I,ein}$ [$\Upsilon_\odot$]\\\hline
-1.40 & 5.56\\\hline
-\end{tabular}  
-\label{tab:einsteinML} 
-\end{table}
-
-\begin{figure*}
-\centering
-\begin{subfigure}{.3\textwidth}
-  \centering
-  \includegraphics[width=.9\linewidth]{fig/lens_surface_brightness.ps}
-  \caption{???}
-  \label{fig:lenscomparelight}
-\end{subfigure}%
-\begin{subfigure}{.3\textwidth}
-  \centering
-  \includegraphics[width=.9\linewidth]{fig/lens_surface_density.ps}
-  \caption{???}
-  \label{fig:lenscomparemass}
-\end{subfigure}
-\begin{subfigure}{.3\textwidth}
-  \centering
-  \includegraphics[width=.9\linewidth]{fig/paper_lensmass_brightness_compare.ps}
-  \caption{???}
-  \label{fig:lenscompareboth}
-\end{subfigure}
-\caption{???
-Preliminary crappy caption: Left: OBSERVED surface bightness multiplied with M/L in Einstein radius (overplotted in red).
-Middle: BEST FIT MODEL for mass distribution from lensing (including "wriggles" due to uncertainties in image positions).
-Contours are at the same levels.
-Right: Same contours, to directly show the difference in shape.
-???
-[TO DO: nice caption]}
-\label{fig:???}
-\end{figure*}
-
-\clearpage
-
-\section{Dynamical Modelling}
-
-\subsection{Jeans Axisymmetric Modelling (JAM)}
-
-[TO DO]
-
-\subsection{JAM based on Surface Brightness}
-
-\subsubsection{... with "Mass-follows-Light" and Velocity Anisotropy}
-
-[TO DO]
-
-\begin{figure*}
-\centering
-\begin{minipage}{.5\textwidth}
-  \centering
-  \includegraphics[height=6cm]{fig/jam_A2_vrms.ps}
-  \caption{???
-Preliminary crappy caption: Failed try to fit a mass-follows-light model to the central regions of the galaxy.
-"Best fit" velocity anisotropy $\beta = -1/2$ is pegged at lower limit.
-???
-[TO DO: nice caption]}
-  \label{fig:???}
-\end{minipage}%
-\begin{minipage}{.5\textwidth}
-  \centering
-  \includegraphics[height=6cm]{fig/lensing_JAM_comparision.ps}
-  \caption{??? Preliminary crappy caption: Observed vrms is overplotted (not fitted) with best fit lens mass models for $\alpha = 1$ (red) and $\alpha = 1.1$ (green).??? [TO DO: nice caption]}
-  \label{fig:???}
-\end{minipage}
-\end{figure*}
-
-\subsubsection{... with Increasing Mass-to-Light Ratio Gradient}
-
-[TO DO]
-
-\begin{figure*}
-\centering
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[height=6cm]{fig/jam_G_vrms.ps}
-  \caption{???}
-  \label{fig:???}
-\end{subfigure}%
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[height=6cm]{fig/jam_G_enclMass.ps}
-  \caption{???}
-  \label{fig:???}
-\end{subfigure}
-\caption{???
-Using the surface brightness MGE for the dynamical modelling: each Gaussian got it's own M/L such that the overall M/L is increasing with radius.
-This is the best fit model.
-The enclosed mass is overplotted with Einstein mass with 4\% error (overplotted, not fitted).
-???
-[TO DO: nice caption]}
-\label{fig:???}
-\end{figure*}
-
-\subsubsection{... with the Lens Mass Model}
-
-[TO DO]
-
-\clearpage
-
-\subsection{JAM with a NFW Dark Matter Halo}
-
-\subsubsection{Sampling with a Markov Monte Carlo Chain}
-
-[TO DO]
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.9\linewidth]{fig/B4_contour_plot_short.ps}
-\caption{???
-Preliminary crappy caption: Result of the MCMC sampling of the parameter space for a model with NFW halo and constant velocity anisotropy.
-Green and blue shows the priors.
-Grey diamonds are the models shown in next figure.
-???
-[TO DO: nice caption]}
-\label{fig:???}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\begin{subfigure}{\textwidth}
-  \centering
-  \includegraphics[width=0.8\linewidth]{fig/B4_rms_error_curves.ps}
-  \caption{???}
-  \label{fig:???}
-\end{subfigure}
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_vcirc.ps}
-  \caption{????????}
-  \label{fig:???}
-\end{subfigure}%
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_projmass.ps}
-  \caption{???}
-  \label{fig:???}
-\end{subfigure}
-\caption{???
-Preliminary crappy caption: 12 samples from the parameter pdf found with the MCMC above for the model with NFW halo and constant velocity anisotropy.
-Big red dot shows the Einstein mass with a 10\% error (used in fit).
-???
-[TO DO: nice caption]}
-\label{fig:???}
-\end{figure*}
-
-\subsubsection{Predicting the Rotation Curve at larger Radii}
-
-[TO DO]
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.7\linewidth]{fig/B4_rms_rot_curves_best_model.ps}
-\caption{???
-Preliminary crappy caption: Model: NFW halo and constant velocity anisotropy, using the the mean / peak values of the MCMC result in the above pdf for the model parameters.
-Fitting one more free parameter to the rotation curve in the inner regions, predicting the rotation curve and dispersion at larger radii.
-Green dots are gas kinematics.
-???
-[TO DO: nice caption]}
-\label{fig:???}
-\end{figure*}
-
+%------------------------
 \section{Discussion and Conclusion}
-
-\subsection{Does J1331 have a Merger History?}
-
-[TO DO]
-
-\subsection{Summary}
-
-[TO DO]
+\include{docs/discussion_merger_v1.01}
+\include{docs/summary_v1.01}
+%------------------------
 

### 2015-08-04 docs/abstract_v1.01.tex
Restructured paper and wrote a first (too long) version of abstract.

We analyse the stellar and dark matter distribution in the spiral galaxy SDSS J1331+3638 (J1331) by means of two independent methods: gravitational lensing and dynamical Jeans modelling. Hubble Space Telescope (HST) imaging by \citet{SWELLSI} reveals, that J1331's bulge is superimposed by a quadruplet of extended lensing images. By fitting a gravitational potential model to the image positions, we constrain the mass inside the Einstein radius ($R_\text{ein}=0.91\pm0.02$ arcsec) to within 4\% ($M_\text{ein} = (7.8\pm0.3) \cdot 10^{10} M_\odot$). From Multi-Gaussian Expansions (MGE) of J1331's surface brightness distribution we find that J1331 has an apparent I-band magnitude of $m_I \simeq 15.8$ mag, a total luminosity of $L_{I,tot} \simeq 5.6 \cdot 10^{10}L_{I,\odot}$ and an effective radius of $R_\text{eff} \simeq 2.6$ arcsec = 5.6 kpc.

According to the long-slit major axis stellar kinematics from \citet{SWELLSV}, J1331 has a counter-rotating stellar core inside $\sim 2$ arcsec. We model the observed stellar kinematics in J1331's central regions by finding MGE models for the surface brightness, stellar and dark matter distribution that solve the axisymmetric Jeans equations. We test galaxy models for (A) mass-follows-light with velocity anisotropy, (B) an increasing mass-to-light ration gradient, (C) the best fit lens model, and (D) including an NFW dark matter halo. We show that, because model (A) fails to reproduce the observed kinematics, J1331 requires a steep total mass-to-light ratio gradient in the center. Model (B) predicts independently the same total mass inside the Einstein radius as the lens model, and vice versa model (C) gives an independent prediction of the observed kinematics in the galaxy center. We constrain the NFW halo of J1331 in model (D) to have a virial velocity $v_{200} \simeq 240 \pm 40$ km/s and a concentration of $c_{200} \simeq 8 \pm 2$ in case of a moderate tangential velocity anisotropy of $\beta_z \simeq −0.4 \pm 0.1$. The NFW halo models can successfully reproduce the signatures of J1331's counter-rotating stellar core and predict J1331's rotation curve at larger radii. However, all these models were more massive than expected from the gas rotation curve at larger radii, and failed to reproduce the steep drop in measured velocity dispersion at [TO DO: WHAT RADIUS???]. This could indicate a non-trivial re-distribution of matter due a possible minor merger event in J1331's past.

### 2015-08-04 docs/data_v1.01.tex
Restructured paper and wrote a first (too long) version of abstract.

\section{Data}

[TO DO]

\begin{itemize}
\item Hubble Space teleskope (HST) imaging by \cite{SWELLSI} in two filters (F450W amd F814W)
\item I filter: for surface brightness distribution of J1331's bulge for Jeans modelling
\item ??? filter: to identify bluish lensing images
\end{itemize}

### 2015-08-04 docs/discussion_merger_v1.01.tex
Restructured paper and wrote a first (too long) version of abstract.

\subsection{Does J1331 have a Merger History?}

[TO DO]

### 2015-08-04 docs/introduction_v1.01.tex
Restructured paper and wrote a first (too long) version of abstract.

\section{Introduction}

[TO DO]

\paragraph{Characteristics of J1331: Lensing}
\begin{itemize}
\item at redshift $z_d\simeq0.113$ [TO DO: REF]
\item large reddish bulge
\item superimposed by quadruplet of extended bluish images at a redshift of $z_s\simeq0.254$ [TO DO: REF]
\item lensed object might be a star-forming blob of a background galaxy.
\end{itemize}

\paragraph{Data used}
\begin{itemize}
\item Hubble Space Telescope (HST) imaging by \cite{SWELLSI}
\end{itemize}

[TO DO]

%============================================================================

\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/first_glimpse_450.ps}
  \caption{J1331 in F450W ("blue")}
  \label{fig:???}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/first_glimpse_814.ps}
  \caption{J1331 in F814W ("red")}
  \label{fig:???}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_imgpos.ps}
  \caption{The lensing images}
  \label{fig:lens_just_imgpos}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/stellar_kinematics_data.ps}
  \caption{Stellar Kinematics by \citet{SWELLSV}}
  \label{fig:???}
\end{subfigure}
\caption{Hubble Space telescope (HST) images and stellar kinematics of the galaxy SDSS J1331+3638 (J1331), which has a large counter-rotating core and whose bulge acts as a strong lens for a bluish background source. \emph{Panel (a) and (b):} HST images of J1331 by \citet{SWELLSI} in two filters, F450W in panel (a) and F814W in panel (b). The galaxy's coordinates on the sky are right ascension $\alpha$ = 202.91800$^\circ$ and declination $\delta$ = 36.46999$^\circ$ (epoch J2000). Image orientation and scaling are indicated in panel (a); the scaling transformation from arcseconds to the physical size of the galaxy in kpc uses the galaxy's redshift $z_d = 0.113$ \citep{SWELLSIII}. The black solid line in panel (a) shows the orientation of the major-axis. The line has a length of 10 arcsec and indicates the region within which we carry out the Jeans modelling. (NOT ALL THE TIME.???????) \emph{Panel (c):} The central region of J1331 in F450W, surface brightness subtracted. An IRAF ellipse ???? fit to the F450W surface brightness in panel (a) was subtracted from the image. The (smoothed) residuals within the white square in panel (a) are shown in panel (c). Four bright blobs (A,B,C and D) become visible, which are arranged in a typical strong lensing configuration around the center of the galaxy (G). \emph{Panel (d):} Stellar Kinematics along the galaxy's major axis as measured by \citet{SWELLSV}, line-of-sight rotation velocity $v_\text{rot}$, line-of-sight velocity dispersion $\sigma$ and the rms-velocity $v_\text{rms} = \sqrt{v_\text{rot}^2 + \sigma^2}$. The dotted line in panel (b) indicates the galaxy's effective half-light radius (in the F814W filter), $R_\text{eff} = 2.6" = 5.2$ kpc. The $v_\text{rot}$ curve reveals that J1331 is counter-rotating within $R_\text{eff}$. TO DO: Add (x,y) axis in figure b).???????}
\label{fig:specialJ1331}
\end{figure*}

\clearpage

### 2015-08-04 docs/model_JAM_v1.01.tex
Restructured paper and wrote a first (too long) version of abstract.

\subsection{Jeans Axisymmetric Modelling (JAM)}

[TO DO]

### 2015-08-04 docs/model_MGE_v1.01.tex
Restructured paper and wrote a first (too long) version of abstract.

\subsection{Multi-Gaussian Expansion Formalism}

[TO DO]

### 2015-08-04 docs/model_fitting_v1.01.tex
Restructured paper and wrote a first (too long) version of abstract.

\subsection{Fitting the Lens Model to the Image Positions}

\paragraph{Image Positions.} We determine the positions of the lensing images by first subtracting a smooth model for the galaxy's surface brightness from the original image. As models we use MGE fits (cf. \S\ref{kap:MGE}) and IRAF ellipse fits (???) to the galaxy in each the F450W and F814W filter. (For example the MGE we use for F814W is the MGE given in tab. \ref{tab:MGEF814W} convolved with the PSF in tab. \ref{tab:PSFMGEF814W}.) The lensing images become then visible in the residuals (see fig. \ref{fig:lens_just_imgpos}). Because the lensing images are extended, we use the position of the brightest pixel in each of the images. We also use the F814W-MGE subtracted residuals from \citet{SWELLSIII}. The lensing positions as determined from the latter are given in tab. \ref{tab:lenspos}. The scatter of lensing positions as determined from subtracting different surface brightness models from the galaxy in different filters gives an error of $\pm 1$ pixel on the image positions.

\begin{table}
\centering
\begin{minipage}{70mm}
\begin{tabular}{r|rrrr|c}
\hline
  & A & B & C & D & G\\\hline
$x_i$ [pixel] & 12.1 & -8.5 & 21.7 & -3.3 & 0.5 $\pm \sqrt{2}$ \\
$y_i$ [pixel] & 16.6 & -10.4 & -0.5 & 19.2 & 0.5 $\pm \sqrt{2}$ \\
\hline
\end{tabular}
\caption{Positions of the lensing images (A-D) and the galaxy center (G) in fig. \ref{fig:lens_just_imgpos}. The image positions were determined from the lens subtracted image for J1331 in figure 4 of \citet{SWELLSIII}, rotated to the $(x,y)$ coordinate system in fig. \ref{fig:lens_just_imgpos}. The pixel scale is 1 pixel = 0.05 arcsec and the error of each image position is $\pm$ 1 pixel. \textit{SMALL PROBLEM: Somehow I used $\sqrt(2)$ pixel as the error on the galaxy center in the Monte Carlo sampling code instead of the 0.5 pixel I claim here. Should I change this table and the error bars in the figures to match this bug????}}
\label{tab:lenspos}
\end{minipage}
\end{table}

\paragraph{Fitting.} As described in \S\ref{sec:lensmodel} our lensing model has the following free parameters: the source position $(\xi,\eta)$, and the radial slope $\alpha$ and Fourier parameters $(a_k,b_k)$ of the lens mass distribution in eq. (\ref{eq:scalefreemodel}) and (\ref{eq:Fourieransatz}). We want to find the lensing model which minimizes for all four images the distance between the observed image positions $\vec{\theta}_{oi}$ and those predicted by the lensing model $\vec{\theta}_{pi}$. Because we want to avoid solving the lens equation (cf. eq. (\ref{eq:lenseqpot}) and (\ref{eq:Fourierlenseq})) for $\theta_{pi}$, we follow \citet{1991ApJ...373..354K} and cast the calculation back to the source plane using the magnification tensor in eq. (\ref{eq:magnificationtensor}):
\begin{eqnarray*}
\chi^2_\text{lens} &=& \sum_{i=1}^{4} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right) \left( \vec{\theta}_{pi} - \vec{\theta}_{oi} \right)\right|^2\\
&\simeq& \sum_{i=1}^{N} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right)  \left.\mathscr{M}\right|_{\vec{\theta}=\vec{\theta}_{oi}} \left( \begin{matrix} \xi - \tilde{\xi}_i \\ \eta - \tilde{\eta}_i \end{matrix} \right) \right|^2,
\end{eqnarray*}
where $(\Delta_x,\Delta_y)$ are the measurement errors of the image positions $\vec{\theta}_{oi}$. $\left.\mathscr{M}\right|_{\vec{\theta}=\vec{\theta}_{oi}}$ is the magnification tensor and $(\tilde{\xi}_i,\tilde{\eta}_i)$ the source position according to the lens equation evaluated at $\vec{\theta}_{oi}$. Following \citet{GlennEC} we add a term
\begin{equation*}
\chi^2_\text{shape} = \lambda \sum_{k \geq 3} \frac{\left(a_k^2 +b_k^2 \right)}{a_0^2} 
\end{equation*}
which forces the shape of the mass distribution to be close to an ellipse. The total $\chi^2$ to minimize is therefore
\begin{equation*}
\chi^2 = \chi^2_\text{lens} + \chi^2_\text{shape}
\end{equation*}
We set $a_1 = b_1 = 0$, which corresponds to the choice of origin; in this case the center of the galaxy.
\\To be able to constrain the slope $\alpha$, we would have needed flux ratios for the images as in \citet{GlennEC}. But the extended quality of the images and the uncertainty in surface brightness subtraction makes flux determination too unreliable and we do not include them in the fitting. Even though the constraint from just the image position fit on $\alpha$ is very weak, we were however able to show that the image positions in tab. \ref{tab:lenspos} minimize $\chi^2$ at $\alpha=1$ and also our other image position sets from different models and filters are consistent with a flat rotation curve. In the following we therefore set $\alpha=1$.

### 2015-08-04 docs/model_lensing_v1.01.tex
Restructured paper and wrote a first (too long) version of abstract.

\subsection{Strong Gravitational Lensing Formalism and Lens Model}

\paragraph{Lensing Formalism.} A gravitational lens is a mass distribution, whose gravitational potential $\Phi$ acts as a lens for light coming from a source positioned somewhere on a plane behind the lens. The angular diameter distance from the observer to the lens is $D_d$, to the source plane it is $D_s$ and the distance between the lens and source plane is $D_{ds}$. The deflection potential of the lens is its potential, projected along the line of sight $z$ and rescaled to
\begin{equation}
\psi(\vec{\theta}) := \frac{D_{ds}}{D_d D_s} \frac{2}{c^2} \int \Phi(\vec{r}=D_d \vec{\theta},z) {\ \mathrm d} z, \label{eq:psidef}
\end{equation}
where $\vec{\theta}$ is a 2-dimensional vector on the plane of the sky. The light from the source at $\vec{\beta} = (\xi,\eta)$ is deflected according to the lens equation
\begin{equation}
\vec{\beta} = \vec{\theta}_i - \left.\vec{\nabla}_\theta \psi(\vec{\theta})\right|_{\vec{\theta}_i} \label{eq:lenseqpot}
\end{equation}
into an image $\vec{\theta}_i = (x_i,y_i)$. The gradient of the deflection potential $\vec{\nabla}_\theta \psi(\vec{\theta})$ is equal to the angle by which the light is deflected multiplied by $D_{ds}/D_{s}$.
\\The total time delay of an deflected light path through $\vec{\theta}$ with respect to the unperturbed light path is given by 
\begin{equation}
\Delta t(\vec{\theta}) = \frac{(1+z_d)}{c} \frac{D_d D_s}{D_{ds}} \left[ \frac 12 (\vec{\theta} - \vec{\beta})^2 - \psi(\vec{\theta})\right], \label{eq:timedelay}
\end{equation}
\citep{BartGravLens}. According to Fermat's principle the image positions will be observed at the extrema of $\Delta t(\vec{\theta})$.
\\The inverse magnification tensor
\begin{equation}
\mathscr{M}^{-1} \equiv \frac{\partial \vec{\beta}}{\partial \vec{\theta}} \overset{(\ref{eq:lenseqpot})}{=} \left(\delta_{ij} - \frac{\partial^2 \psi}{\partial \theta_i \partial \theta_j} \right)\label{eq:magnificationtensor}
\end{equation}
describes how the source position changes with image position. It also describes the distortion of the image shape for an extended source and its magnification due to lensing according to
$$\mu \equiv \frac{\text{image area}}{\text{source area}} = \det \mathscr{M}.$$
Lines in the image plane for which the magnification becomes infinite, i.e. $\det \mathscr{M}^{-1} = 0$, are called \emph{critical curves}. The corresponding lines in the source plane are called \emph{caustics}. The position of the source with respect to the caustic detemines the number of images and their configuration and shape with respect to each other.
\\The \emph{Einstein mass} $M_\text{ein}$ and \emph{Einstein radius} $R_\text{ein}$ are defined via the relation
\begin{equation*}
M_\text{ein} \equiv M_\text{proj}(<R_\text{ein}) \overset{!}{=} \pi \Sigma_\text{crit} R_\text{ein}^2,
\end{equation*}
where $\Sigma_\text{crit} \equiv \frac{c^2}{4\pi G} \frac{D_s}{D_d D_{ds}}$ is the critical density and $M_\text{proj}(<R_\text{ein})$ is the mass projected along the line-of-sight within $R_\text{ein}$. $M_\text{ein}$ is similar to the projected mass within the critical curve $M_\text{crit}$.

\paragraph{Lens Model.} Following \citet{EvansWitt} we assume a scale-free model
\begin{equation*}
\psi(R',\theta) = R^{'\alpha} F(\theta) \label{eq:scalefreemodel}
\end{equation*}
for the lensing potential, consisting of an angular part $F(\theta)$ and a power-law radial part, with $(R',\theta)$ being polar coordinates on the plane of the sky. The case $\alpha = 1$ corresponds to a flat rotation curve. We expand $F(\theta)$ into a Fourier series,
\begin{equation}
F(\theta) = \frac{a_0}{2} + \sum_{k=1}^{\infty} \left(a_k \cos(k\theta) + b_k \sin (k\theta) \right). \label{eq:Fourieransatz}
\end{equation}
For this scale-free lens model the lens equation (\ref{eq:lenseqpot}) becomes
\begin{equation}
\begin{pmatrix} \xi \\ \eta \end{pmatrix} = \begin{pmatrix} R'_i \cos \theta_i - R_i^{'\alpha-1} \left(\alpha \cos \theta_i F(\theta_i) - \sin \theta_i F'(\theta_i) \right) \\ R'_i \sin \theta_i - R_i^{'\alpha-1} \left(\alpha \sin \theta_i F(\theta_i + \cos \theta_i F'(\theta_i) \right)\end{pmatrix}\label{eq:Fourierlenseq}
\end{equation}
\citep{EvansWitt}, where $F'(\theta) = \partial F(\theta) / \partial \theta$. When we fix the slope $\alpha$, then the lens equation is a purely linear problem and can be solved numerically for the source position $(\xi,\eta)$ and the Fourier parameters $(a_k,b_k)$ given one observed image at position $(x_i=R'_i \cos \theta_i,y_i=R'_i \sin \theta_i)$.

### 2015-08-04 docs/results_JAMwithNFW_v1.01.tex
Restructured paper and wrote a first (too long) version of abstract.

\subsection{JAM with a NFW Dark Matter Halo}

\subsubsection{Sampling with a Markov Monte Carlo Chain}

[TO DO]

\begin{figure*}
\centering
\includegraphics[width=0.9\linewidth]{fig/B4_contour_plot_short.ps}
\caption{??? Preliminary crappy caption: Result of the MCMC sampling of the parameter space for a model with NFW halo and constant velocity anisotropy. Green and blue shows the priors. Grey diamonds are the models shown in next figure. ??? [TO DO: nice caption]}
\label{fig:???}
\end{figure*}

\begin{figure*}
\centering
\begin{subfigure}{\textwidth}
  \centering
  \includegraphics[width=0.8\linewidth]{fig/B4_rms_error_curves.ps}
  \caption{???}
  \label{fig:???}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_vcirc.ps}
  \caption{????????}
  \label{fig:???}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_projmass.ps}
  \caption{???}
  \label{fig:???}
\end{subfigure}
\caption{??? Preliminary crappy caption: 12 samples from the parameter pdf found with the MCMC above for the model with NFW halo and constant velocity anisotropy. Big red dot shows the Einstein mass with a 10\% error (used in fit). ??? [TO DO: nice caption]}
\label{fig:???}
\end{figure*}

\subsubsection{Predicting the Rotation Curve at larger Radii}

[TO DO]

\begin{figure*}
\centering
\includegraphics[width=0.7\linewidth]{fig/B4_rms_rot_curves_best_model.ps}
\caption{??? Preliminary crappy caption: Model: NFW halo and constant velocity anisotropy, using the the mean / peak values of the MCMC result in the above pdf for the model parameters. Fitting one more free parameter to the rotation curve in the inner regions, predicting the rotation curve and dispersion at larger radii. Green dots are gas kinematics. ??? [TO DO: nice caption]}
\label{fig:???}
\end{figure*}

### 2015-08-04 docs/results_JAMwithSB_v1.01.tex
Restructured paper and wrote a first (too long) version of abstract.

\subsection{JAM based on Surface Brightness}

\subsubsection{... with "Mass-follows-Light" and Velocity Anisotropy}

[TO DO]

\begin{figure*}
\centering
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[height=6cm]{fig/jam_A2_vrms.ps}
  \caption{??? Preliminary crappy caption: Failed try to fit a mass-follows-light model to the central regions of the galaxy. "Best fit" velocity anisotropy $\beta = -1/2$ is pegged at lower limit. ??? [TO DO: nice caption]}
  \label{fig:???}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[height=6cm]{fig/lensing_JAM_comparision.ps}
  \caption{??? Preliminary crappy caption: Observed vrms is overplotted (not fitted) with best fit lens mass models for $\alpha = 1$ (red) and $\alpha = 1.1$ (green).??? [TO DO: nice caption]}
  \label{fig:???}
\end{minipage}
\end{figure*}

\subsubsection{... with Increasing Mass-to-Light Ratio Gradient}

[TO DO]

\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[height=6cm]{fig/jam_G_vrms.ps}
  \caption{???}
  \label{fig:???}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[height=6cm]{fig/jam_G_enclMass.ps}
  \caption{???}
  \label{fig:???}
\end{subfigure}
\caption{??? Using the surface brightness MGE for the dynamical modelling: each Gaussian got it's own M/L such that the overall M/L is increasing with radius. This is the best fit model. The enclosed mass is overplotted with Einstein mass with 4\% error (overplotted, not fitted). ??? [TO DO: nice caption]}
\label{fig:???}
\end{figure*}

\subsubsection{... with the Lens Mass Model}

[TO DO]

### 2015-08-04 docs/results_lensing_v1.01.tex
Restructured paper and wrote a first (too long) version of abstract.

\subsection{Mass distribution from Lensing}

\paragraph{Best fit lens model.} The best fit lens model for the image positions in tab. \ref{tab:lenspos} is given in the first column of tab. \ref{tab:bestfitlensmodel}. Fig. \ref{fig:lensbestfiteinsteincurves} shows the corresponding critical curve, caustic and Einstein radius, and the best fit source position. In this case, where $\alpha=1$, the critical curve is also an equidensity contour of the galaxy model. Fig. \ref{fig:lensbestfittimedelay} overplots the smoothed residuals from the F814W image subtracted by the IRAF ellipse fit to the surface brightness with the contours of the best fit model's time delay surface. This demonstrates that, although we did not include any information about the shape of the lensing images in the fit, it is consistent with the predicted distortion for an extended source by the best fit lens model.
\\To estimate how the uncertainties in the determination of the image positions and galaxy center affect the results, we Monte Carlo sample random positions from a two-dimensional Normal distribution centered at the positions in tab. \ref{tab:lenspos} and a standard deviation corresponding to the measurement error of 1 pixel. A Gaussian fit to the resulting distributions of best fit values leads to the constraints on the shape parameters and Einstein quantities in the second column in tab. \ref{tab:bestfitlensmodel}. We therefore constrain the Einstein radius to within 2\%, $R_\text{ein} = (0.91 \pm 0.02)$ arcsec and the projected mass within the critical curve with a relative error of 4\%, $M_\text{crit} =(7.9\pm0.3)\cdot 10^{10} M_\odot$. Our measurement of $R_\text{ein}$ is consistent with that from \citet{SWELLSIII}, $R_\text{ein,SWELLS} = (0.96 \pm 0.04)$ arcsec. The relative difference between our critical mass and that of \citet{SWELLSIII}, $M_\text{crit,SWELLS} =(8.86\pm0.61)\cdot 10^{10} M_\odot$, is 13\%.

%========================================================================================

\begin{table*}
\centering
\caption{??? in tab. \ref{tab:lenspos}, for $\alpha = 1$}
\begin{tabular}{llrrclr}
\hline
 &  & \multicolumn{1}{c}{lens model for} &\multicolumn{4}{c}{lens model from Monte Carlo sampling  } \\
 &  & \multicolumn{1}{c}{peak image positions}  & \multicolumn{4}{c}{of image positions }  \\ \hline
Einstein Radius      & $R_\text{ein}$ [arcsec]             & $0.907$ & $0.91$  & $\pm$ & $     0.02$ & ($2\%$)\\
Einstein Mass        & $M_\text{ein}$ [$10^{10} M_\odot$]  & $7.72$  & $7.8 $  & $\pm$ & $      0.3$ & ($4\%$) \\
Critical Mass        & $M_\text{crit}$ [$10^{10} M_\odot$] & $7.87$  & $7.9$   & $\pm$ & $      0.3$ & ($4\%$)\\
Source Position      & $\xi$ [arcsec]                      & $0.095$ & $0.09 $ & $\pm$ & $     0.03$ & ($28\%$)\\
                     & $\eta$ [arcsec]                     & $0.107$ & $0.10 $ & $\pm$ & $     0.03$ & ($27\%$)\\
Fourier Coefficients & $a_0$                               & $1.814$ & $1.82 $ & $\pm$ & $   0.04$ & (2\%)\\
                     & $a_2$                               & $0.012$ & $ 0.011 $ & $\pm$ & $    0.004$ & (35\%)\\
                     & $b_2$                               & $-0.057$ & $-0.06 $  & $\pm$ & $  0.01$ & (25\%)\\
                     & $a_3$                               & $-0.0001$& $0.0000 $ & $\pm$ & $   0.0006$ & \\
                     & $b_3$                               & $-0.0002$&$0.000 $   & $\pm$ & $  0.001$ & \\\hline
\end{tabular}  
\label{tab:bestfitlensmodel} 
\end{table*}

%========================================================================================

\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_einstein.ps}
  \caption{??? Critical curves, Einstein radius, caustics, source position for best fit model. ??? [TO DO: nice caption]}
  \label{fig:lensbestfiteinsteincurves}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_timedelay.ps}
  \caption{??? Time delay surface ??? [TO DO: nice caption]}
  \label{fig:lensbestfittimedelay}
\end{subfigure}
\caption{???}
\label{fig:???}
\end{figure*}

%========================================================================================

\paragraph{Comparison with Light Distribution.} Fig. \ref{fig:lenscomparemass} shows the surface mass distribution as predicted by the best fit model in tab. \ref{tab:bestfitlensmodel}. We introduce random noise according to the uncertainties in the Fourier shape parameters to create a mock observation that visualizes the effect of the measurement errors. To be able to compare the predicted mass distribution to the observed light distribution we transform the surface brightness into a mass density: We first integrate the MGE in tab. \ref{tab:MGEF814W} to get the total luminosity within the Einstein radius and the predicted mass-to-light ratio as $\Upsilon_\text{I,ein} = M_\text{ein} / L_\text{I,ein}$. Fig. \ref{fig:lenscomparelight} shows then the observed surface brightness in the F814W filter multiplied by $\Upsilon_\text{I,ein}$.  Fig. \ref{fig:lenscompareboth} finally compares equidensity contours at the same values of both the predicted lens mass distribution and the observed surface brightness times $\Upsilon_\text{I,ein}$. We note the following three facts: 1.The mass predicted from lensing and the observed light distribution are oriented in the same direction. 2. Within the Einstein radius mass and light distribution have the same shape, while further out the mass distribution is more roundish. 3. The light distribution drops faster than the mass with increasing radius. This could indicate that the stellar component of the galaxy is superimposed by a more roundish dark matter component.

\paragraph{[TO DO: Stuff to mention]}
\begin{itemize}
\item best fit lens total mass distribution of J1331 has the same position angle and a similar elliptical shape as the surfache brightness distributon, but is slightly rounder, and could be consistent with a flat rotation curve.
\end{itemize}

%========================================================================================

\begin{table}
\centering
\caption{???}
\begin{tabular}{cc}
\hline
Total I-band luminosity within $R_\text{ein}$ & Mass-to-light ratio within $R_\text{ein}$\\
 $L_\text{I,ein}$ [$10^{10} L_\odot$] & $\Upsilon_\text{I,ein} = M_\text{ein} / L_\text{I,ein}$ [$\Upsilon_\odot$]\\\hline
1.40 & 5.56\\\hline
\end{tabular}  
\label{tab:einsteinML} 
\end{table}

%========================================================================================

\begin{figure*}
\centering
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_surface_brightness.ps}
  \caption{???}
  \label{fig:lenscomparelight}
\end{subfigure}%
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_surface_density.ps}
  \caption{???}
  \label{fig:lenscomparemass}
\end{subfigure}
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/paper_lensmass_brightness_compare.ps}
  \caption{???}
  \label{fig:lenscompareboth}
\end{subfigure}
\caption{??? Preliminary crappy caption: Left: OBSERVED surface bightness multiplied with M/L in Einstein radius (overplotted in red). Middle: BEST FIT MODEL for mass distribution from lensing (including "wriggles" due to uncertainties in image positions). Contours are at the same levels. Right: Same contours, to directly show the difference in shape. ??? [TO DO: nice caption]}
\label{fig:???}
\end{figure*}

### 2015-08-04 docs/results_photometry_v1.01.tex
Restructured paper and wrote a first (too long) version of abstract.

\subsection{Surface Photometry for J1331 with MGE}

[TO DO]

\paragraph{[TO DO: Stuff to mention]}
\begin{itemize}
\item fit sof MGE to J1331s surface brightness within $\sim$ 2 half-light radii, and to an Iraf Ellipse model for J1331's outer regions, make it possible to easily deconvolve the hst images with its PSF.
\item the deporjecten if the galaxy under the assumption of oblate axusymmetry and an estimated inclination of $\sim70^\circ$ can be performed analytically.
\end{itemize}

%============================================================================

\begin{figure}
\begin{minipage}[c]{\linewidth}
\centering
\includegraphics[width=0.8\textwidth]{fig/1331F814Wsci_MGE_M.ps}
\caption{??? MGE as used in the dynamical modelling ??? [TO DO: nice caption]}
\label{fig:???}
\end{minipage}
\begin{minipage}[c]{\linewidth}
\centering
\includegraphics[width=0.8\textwidth]{fig/1331F814W_MGE_disk_L.ps}
\caption{??? [TO DO: caption]}
\label{fig:???}
\end{minipage}
\end{figure}

%============================================================================

\begin{table*}
\centering
\begin{minipage}[t]{40mm}
\caption{PSF F814W MGE ??????}
\begin{tabular}{ccc}
\hline
$k$ & $G_k$ & $\sigma_k$ [arcsec] \\\hline
1 & 0.184 & 0.038\\
2 & 0.485 & 0.085\\
3 & 0.222 & 0.169\\
4 & 0.109 & 0.487\\\hline
\end{tabular}
\label{tab:PSFMGEF814W}
\end{minipage}
\hspace{10mm}
\begin{minipage}[t]{100mm}
\caption{F814W MGE???}
\begin{tabular}{cccccc}
\hline
 & total luminosity  & surface density & \multicolumn{2}{c}{Gaussian dispersion} & axis ratio\\
$k$  & $L_k$ [counts] & $I_{0,k}$ [$L_\odot$/pc$^2$] & $\sigma_k$ [arcsec] & $\sigma_k$ [kpc] & $q'_k$\\\hline
1  &     9425.96 &      20768.  &  0.051   & 0.103  & 1.00\\
2  &    13173.0 &        3161.2 &  0.178   & 0.358  & 0.76\\
3  &    40235.0 &        1588.2 &  0.503   & 1.008  & 0.58\\
4  &    67755.2 &         502.25&  1.180   & 2.368  & 0.56\\
5  &    203677. &         136.51&  3.891   & 7.805  & 0.57\\\hline
\end{tabular}
\label{tab:MGEF814W}
\end{minipage}
\end{table*}

%============================================================================

\begin{table}
\centering
\begin{minipage}{140mm}
\caption{Galaxy Parameters of J1331}
\begin{tabular}{lllrl}
\hline
redshift                  & $z_d$ & 0.113 & \citep{SWELLSIII}\\
angular diameter distance & $D_d$ [Mpc] & 414 & \\
scaling                   & 1 kpc / 1 arcsec & 2.006 & \\
position angle            & $\phi$ [degrees] & wrt what???\\
average axis ratio & $q'$ & 0.598\\
average ellipticity & $\epsilon = 1 - q'$ & 0.402 & \\
apparent F814W magnitude & $m_\text{F814W}$ [mag] & 15.77 & \\
total F814W luminosity & $L_\text{tot,F814W}$ [$10^{10} L_\odot$] & 5.6 & \\
effective half-light radius & $R_\text{eff}$ [arcsec] & 2.6 & \\
& $R_\text{eff}$ [pc]& 5.2 & \\
\hline
\end{tabular}
\end{minipage}
\end{table}

### 2015-08-05 docs/introduction_v1.01.tex
Made notes for the introduction.

@@
 
-\paragraph{Characteristics of J1331: Lensing}
+\paragraph{Dark matter general}
 \begin{itemize}
+\item The flat rotation curves of galaxies were the first indication, that galaxies could reside in large and massive, more or less spherical halos made of invisible dark matter $\longrightarrow$ stellar movements in solar neighbourhood \citep{1932BAN.....6..249O}, $H\alpha$ rotation curves of external galaxies \citep{1978ApJ...225L.107R}
+\item Standard model of cosmology, based on the by the Planck Mission, predicts $\sim32\%$ of the universes content is in the form of matter and $\sim 85\%$ of the total matter is non-baryonic dark matter.
+\end{itemize}
+
+\paragraph{Lensing to measure mass}
+\begin{itemize}
+\item Completely independent method to measure mass of galaxies is gravitational lensing
+\item massive galaxies can act as gravitational lenses, deflect light of background sources, gives rise to multiple images
+\item By 2010 over 200 strong gravitational galaxy lenses had been discovered \citep{2010ARA&A..48...87T} and the number is still rising
+\item On galaxy scales strong gravitational lensing is sensitive to the total projected matter amount inside approximately $\sim 1$ arcsec.
+\end{itemize}
+
+\paragraph{Dynamical modelling to measure mass}
+\begin{itemize}
+\item Gas rotation curves are useful to measure matter distribution at large radii
+\item gas on circular orbits $\longrightarrow$ directly circular velocity curve and mass profile. 
+\item But: gas has dissipative nature, concentrated to mid-plane $\longrightarrow$ sensitive to disturbances by e.g. bars, spiral arms
+\item stars are dissipationless, present almost everywhere in the galaxy $\longrightarrow$ very good tracers of the underlying gravitational potential $\longrightarrow$  but much more complex motions: bulk rotation around principal axis, plus random motion components in all coordinate directions $\longrightarrow$ velocity anisotropy $\longrightarrow$ degeneracy with matter distribution
+\item modelling: account for stellar rotation, dispersion and velocity anisotropy
+\item e.g. solution of the Jeans equations for an assumed velocity anisotropy, e.g. \citet{Cap08}
+\item dynamical modelling of stellar kinematics also at smaller radii $\longrightarrow$ complement lensing investigation of the matter distribution in the center of galaxies
+\item Other modelling methods: Schwarzschild's orbital superposition approach \citep{schwarzschild}
+\end{itemize}
+
+\paragraph{Dark Matter Halos}
+\begin{itemize}
+\item Cosmological cold dark matter N-body simulations suggest that dark matter halos take a cuspy shape, following a NFW profile \citep{NFW96}
+\item central dark matter density cusps are not observed in dark matter dominated galaxies (dwarfs); if they exist in more massive galaxies depends strongly on stellar mass-to-light ratio.
+Overall, observations suggest cored dark matter halos $\longrightarrow$ core-cusp problem, might be due to a yet unknown interaction between dark matter and baryons
+\end{itemize}
+
+\paragraph{SWELLS Survey}
+\begin{itemize}
+\item [TO DO]
+\end{itemize}
+
+\paragraph{Characteristics of J1331}
+\begin{itemize}
+\item SDSS J1331+3638 (J1331)
+\item approximate hubble type Sb
+\item first discovered by Sloan digital sky survey (SDSS) [TO DO: REF]
 \item at redshift $z_d\simeq0.113$ [TO DO: REF]
-\item large reddish bulge
-\item superimposed by quadruplet of extended bluish images at a redshift of $z_s\simeq0.254$ [TO DO: REF]
+\item \citet{SWELLSI} identified it as a strong lens
+\item large reddish bulge and bluish spiral arms, see panel (a) and (b) in figure 1
+\item superimposed by quadruplet of extended bluish images at a redshift of $z_s\simeq0.254$ [TO DO: REF], see panel (c) in figure 1
 \item lensed object might be a star-forming blob of a background galaxy.
+\item Lensing properties first analysed by \citet{SWELLSIII}
+\item rather edge-on $\longrightarrow$ possible to measure rotation curves.
+\citet{SWELLSV} measured the gas and stellar rotation curves along the major axis.
+Fitted galaxy model to gas kinematics at large radii, and lensing result
+\item large counter-rotating core, see panel (d) in figure 1
+\item possible minor merger in the past
+\end{itemize}
+
+\paragraph{Goal of this work}
+\begin{itemize}
+\item constraining the matter distribution in a galaxy, disentangling stellar and dark matter component at smaller radii
+\item using two independent methods, lensing and dynamics
+\item testing, if Jeans modelling works also in the presence of counter-rotating cores
+\item focus on the smaller radii, as \citet{SWELLSV} was focusing on outer regions
+\item complementing the work by [SWELLS paper on lensing and lensing/dynamcis TO DO: find] by an in depth analysis
+\item ideal case: investigating how a minor merger modifies the mass distribution of a galaxy
 \end{itemize}
@@
 \begin{itemize}
-\item Hubble Space Telescope (HST) imaging by \cite{SWELLSI}
+\item Hubble Space Telescope (HST) imaging by \cite{SWELLSI}, see panels (a) and (b) in Figure 1
+\item  \citet{SWELLSV} measured the gas and stellar rotation curves along the major axis. see panels (b) and (d) in Figure 1
+\end{itemize}
+
+\paragraph{Methods}
+\begin{itemize}
+\item similar analysis of J1331 as \citet{GlennEC} has done with the Einstein cross
+\item lensing: fitting scale-free galaxy model to image positions \citep{EvansWitt}
+\item photometry: MGE expansion of surface brightness in the F814W filter (deconvolution with PSF), apparent magnitude, total luminosity, effective radius
+\item Jeans modelling: jeans axisymmetric modelling (JAM) by \citet{Cap08} to fit model predictions for the second velocity moments to the stellar kinematics data
 \end{itemize}

### 2015-08-05 docs/introduction_v1.01.tex
Started writing sections on MGE photometry.

@@
 \item \citet{SWELLSI} identified it as a strong lens
-\item large reddish bulge and bluish spiral arms, see panel (a) and (b) in figure 1
-\item superimposed by quadruplet of extended bluish images at a redshift of $z_s\simeq0.254$ [TO DO: REF], see panel (c) in figure 1
+\item large reddish bulge and bluish spiral arms, see Fig. \ref{fig:F450W} and \ref{fig:F814W}
+\item superimposed by quadruplet of extended bluish images at a redshift of $z_s\simeq0.254$ [TO DO: REF], see Fig. \ref{fig:lens_just_imgpos}
 \item lensed object might be a star-forming blob of a background galaxy.
@@
 Fitted galaxy model to gas kinematics at large radii, and lensing result
-\item large counter-rotating core, see panel (d) in figure 1
+\item large counter-rotating core, see Fig. \ref{fig:kinematics}
 \item possible minor merger in the past
@@
 \begin{itemize}
-\item Hubble Space Telescope (HST) imaging by \cite{SWELLSI}, see panels (a) and (b) in Figure 1
-\item  \citet{SWELLSV} measured the gas and stellar rotation curves along the major axis. see panels (b) and (d) in Figure 1
+\item Hubble Space Telescope (HST)/WFPC2/WFC3 imaging by \cite{SWELLSI}, see Fig. \ref{fig:F450W} and \ref{fig:F814W}
+\item  \citet{SWELLSV} measured the gas and stellar rotation curves along the major axis. see Fig. \ref{fig:F814W} and \ref{fig:kinematics}
 \end{itemize}
@@
   \caption{J1331 in F450W ("blue")}
-  \label{fig:???}
+  \label{fig:F450W}
 \end{subfigure}%
@@
   \caption{J1331 in F814W ("red")}
-  \label{fig:???}
+  \label{fig:F814W}
 \end{subfigure}
@@
   \caption{Stellar Kinematics by \citet{SWELLSV}}
-  \label{fig:???}
+  \label{fig:kinematics}
 \end{subfigure}
 \caption{Hubble Space telescope (HST) images and stellar kinematics of the galaxy SDSS J1331+3638 (J1331), which has a large counter-rotating core and whose bulge acts as a strong lens for a bluish background source.
-\emph{Panel (a) and (b):} HST images of J1331 by \citet{SWELLSI} in two filters, F450W in panel (a) and F814W in panel (b).
+\emph{Panel (a) and (b):} HST/WFPC2/WFC3 images of J1331 by \citet{SWELLSI} in two filters, F450W in panel (a) and F814W in panel (b).
 The galaxy's coordinates on the sky are right ascension $\alpha$ = 202.91800$^\circ$ and declination $\delta$ = 36.46999$^\circ$ (epoch J2000).
-Image orientation and scaling are indicated in panel (a); the scaling transformation from arcseconds to the physical size of the galaxy in kpc uses the galaxy's redshift $z_d = 0.113$ \citep{SWELLSIII}.
+Image orientation and scaling are indicated in panel (a); the scaling transformation from arcseconds to the physical size of the galaxy in kpc uses the galaxy's redshift $z_d = 0.113$ \citep{SWELLSIII} (i.e.
+assumes an angular diameter distance of 414 Mpc).
+The color scaling of these two images is the same.
 The black solid line in panel (a) shows the orientation of the major-axis.
 The line has a length of 10 arcsec and indicates the region within which we carry out the Jeans modelling.
-(NOT ALL THE TIME.???????) \emph{Panel (c):} The central region of J1331 in F450W, surface brightness subtracted.
+[TO DO: NOT ALL THE TIME.???????] \emph{Panel (c):} The central region of J1331 in F450W, surface brightness subtracted.
 An IRAF ellipse ????
@@
 The $v_\text{rot}$ curve reveals that J1331 is counter-rotating within $R_\text{eff}$.
-TO DO: Add (x,y) axis in figure b).???????}
+[TO DO: Add (x,y) axis in figure b).???????]}
 \label{fig:specialJ1331}

### 2015-08-05 docs/model_MGE_v1.01.tex
Started writing sections on MGE photometry.

@@
 
+Multi-Gaussian Expansions (MGE) are used to parametrize the observed surface brightness or projected total mass of a galaxy as a sum of $N$ two-dimensional, elliptical Gaussians \citep{1991ApJ...366..599B,1992A&A...253..366M,1994A&A...285..723E,1999MNRAS.303..495E}.
+This work makes use of the algorithm and code\footnote{Michele Cappellari's IDL code package for fitting MGEs to images is available online at \url{http://www-astro.physics.ox.ac.uk/~mxc/software}.
+The version from June 2012 was used in this work.} by \citet{Cap02}.
+We assume all Gaussians to have the same center and position angle $\phi$, i.e.
+orientation of w.r.t.
+the $y'$-axis of the coordinate system with polar coordinates $(R',\theta')$ [TO DO: CHECK].
+Then the surface brightness can be written as
+\begin{eqnarray}
+I(R',\theta') &=& \sum_{i=1}^{N} I_{0,i} \exp\left[ - \frac{1}{2\sigma_i^2} \left(x^{'2} + \frac{y^{'2}}{q_i^{'2}}\right)\right]\label{eq:MGEgeneral}\\
+\text{with } I_{0,i} &=& \frac{L_i}{2\pi \sigma_i^2 q'_i}\nonumber\\%\label{eq:centralItotalL}\\
+\text{and } x'_i &=& R' \cos(\theta' - \phi)\nonumber\\
+y'_i &=& R' \sin(\theta' - \phi),\nonumber
+\end{eqnarray}
+where $I_{0,i}$ is the central surface brightness of each Gaussian, $L_i$ its total luminosity, $\sigma_i$ its dispersion along the major axis and $q'_i$ the axis ratio between the elliptical Gaussians major and minor axis.
+\\We can also expand the telescopes point-spread function (PSF) as a sum of circular Gaussians,
+\begin{equation}
+\text{PSF}(x,y) = \sum_j \frac{G_j}{2 \pi \delta_j^2} \exp\left[- \frac{1}{2 \delta_j^2} \left(x^2 + y^2 \right)\right], \label{eq:PSFgeneral}
+\end{equation}
+where $\sum_j G_j = 1$ and $\delta_j$ are in this case the dispersions of the circular PSF Gaussians.
+In this case the observed surface brightness distribution is a convolution of the intrinsic surface brightness in Eq.
+(\ref{eq:MGEgeneral}) with the PSF in Eq.
+(\ref{eq:PSFgeneral}): $(I \ast \text{PSF}) (x',y')$ is then again a sum of Gaussians and can be directly fitted to an image of the galaxy in question.
+
 [TO DO]
+
+\paragraph{Other stuff to mention}
+\begin{itemize}
+\item [TO DO] analytic deprojection into 3D Gaussians
+\end{itemize}

### 2015-08-05 docs/results_photometry_v1.01.tex
Started writing sections on MGE photometry.

@@
-\subsection{Surface Photometry for J1331 with MGE}
+\subsection{Surface Photometry for J1331 with MGEs}
+
+To derive J1331's surface brightness distribution, we use the HST image in the infrared F814W filter, shown in Fig.
+\ref{fig:F814W}.
+In infrared J1331's central old and smooth stellar component is more extended than in the F450W filter in Fig.
+\ref{fig:F450W}, which is more sensitive to young clumpy star-forming regions.
+In infrared the bulge is also much brighter than the bluish lens images and the imaging is less prone to extinction.
+The F814W image is therefore best suited for fitting a MGE.
+
+\paragraph{PSF for the HST/F814W filter.} We find a radial profile for the HST/F814W filter PSF from circular annuli within a synthetic PSF image from [TO DO: Where did we get this image from???], ignoring diffraction spikes.
+The one-dimensional MGE fit of Eq.
+(\ref{eq:PSFgeneral}) to this radial profile is performed using the code by [TO DO: REF and footnote to code].
+The MGE parameters of the normalized PSF model are given in Tab.
+\ref{tab:PSFMGEF814W}.
 
@@
 \begin{minipage}[t]{40mm}
-\caption{PSF F814W MGE ??????}
+\caption{F814W PSF MGE: Parameters of the circular four-Gaussian MGE in Eq. (\ref{eq:PSFgeneral} fitted to the radial profile of the synthetic HST/F814W PSF image by [TO DO].}
 \begin{tabular}{ccc}
 \hline
-$k$ & $G_k$ & $\sigma_k$ [arcsec] \\\hline
+$k$ & $G_k$ & $\delta_k$ [arcsec] \\\hline
 1 & 0.184 & 0.038\\

### 2015-08-06 docs/results_photometry_v1.01.tex
Wrote sections on MGE fitting results.

@@
 
-To derive J1331's surface brightness distribution, we use the HST image in the infrared F814W filter, shown in Fig.
+In \S ???
+we derived a mass model for J1331 from Lensing.
+In this section set up a model for the galaxy's intrinsic light distribution in terms of an MGE, which we will then compare to the mass distribution.
+The light model will also be the basis of the dynamical Jeans modelling in \S ???.
+\\To derive J1331's surface brightness distribution, we use the HST image in the infrared F814W filter, shown in Fig.
 \ref{fig:F814W}.
@@
 
+\paragraph{MGE for the inner regions.} We fit a MGE to the smooth central region within radius $\sim 5$ arcsec of the HST/WFPC2/WF3/F814W image of J1331 in Fig.
+\ref{fig:F814W}.
+Bright objects  close to the galaxy, blobs possibly belonging to the background galaxy and parts of the foreground spiral arm were masked during the fit.
+J1331's galaxy center, position angle and average apparent ellipticity (see table \ref{tab:galaxyparameters}) are found from the images weighted first and second moment.
+The MGE fit, as performed by the code \cite{Cap02}, splits the image in annuli with the given ellipticity and position angle and sectors of $5^\circ$ width and fits an 5-Gaussian MGE of the form in Eq.
+(\ref{eq:MGEgeneral}) convolved with the PSF MGE in table \ref{tab:PSFMGEF814W} to it.
+The best fit MGE (PSF convolved) is compared to the data in Fig.
+\ref{fig:MGEinnerRegions} and the corresponding parameters of the intrinsic surface brightness distribution are given in table \ref{tab:MGEF814W}.
+The fit is a very good representation of the light distribution in the inner 5 arcsec, but underestimates the light distribution outside of this.
+
+\paragraph{MGE for the outer regions.} To get an handle on the light distribution also in the outer parts of J1331, where spiral arms dominate, we first fit a IRAF ELLIPSE [TO DO: How to reference???] model to the F814W image (masking the brightest blobs in the spiral arms and outer regions).
+Only then we fit a 7-Gaussian MGE to the smooth ellipse model.
+The MGE does not perfectly reproduce the flattness of the ellipse model at every radius, but considering the spiral arm dominated outer regions of J1331, it is good enough for an approximate handling of the overall light distribution.
+
+\paragraph{Transformation into physical units.} To transform the MGE in units of counts into physical units, we apply a simplified version of the procedure described in \citet{Holtzman}.
+\\The scaling of the drizzled HST/WFC3 images is  $S = 0.05$ arcsec/pixel and the total exposure time $T = 1600$ sec.
+The total F814W luminosity in counts of each Gaussian of the MGE has a central flux in counts per pixel of
+\begin{equation*}
+C_0\text{[counts/pixel]} = \frac{L[counts]}{2\pi \sigma[\text{pixel}]^2 q}.
+\end{equation*}
+This is then transformed into an I-band surface brightness via
+\begin{equation*}
+\mu_I \simeq -2.5 \log_{10}\left( \frac{C_0\text{[counts/pixel]}}{T \cdot S^2}\right) + Z + C + A_I,
+\end{equation*}
+where $Z\simeq21.62$ is a the zero-point from \citet{Holtzman}  (updated according to \citet{Dolphin,DolphinNew}) for the photometric system of the HST/WFPC2 camera and the F814W filter plus a correction for the difference in gain of calibration and observation.
+$C= 0.1$ corrects for the finite aperture of the WFPC2.
+And $A_I =0.015$ mag  is the extinction in the I-band tpwards J1331, according to the NASA/IPAC Extragalactic Database [TO DO: proper reference].
+The correction between the F814W filter and the I-band of the UBVRI photometric system is  small \citep{Holtzman} and we neglect it therefore.
+
 [TO DO]
@@
 \item fit sof MGE to J1331s surface brightness within $\sim$ 2 half-light radii, and to an Iraf Ellipse model for J1331's outer regions, make it possible to easily deconvolve the hst images with its PSF.
-\item the deporjecten if the galaxy under the assumption of oblate axusymmetry and an estimated inclination of $\sim70^\circ$ can be performed analytically.
+\item the deporjecten if the galaxy under the assumption of oblate axisymmetry and an estimated inclination of $\sim70^\circ$ can be performed analytically.
 \end{itemize}
@@
 \includegraphics[width=0.8\textwidth]{fig/1331F814Wsci_MGE_M.ps}
-\caption{??? MGE as used in the dynamical modelling ??? [TO DO: nice caption]}
-\label{fig:???}
+\caption{MGE for J1331's inner regions: Comparison of contours with constant F814W surface brightness of J1331's central region (orange lines) with the corresponding iso-brightness contours of the best fit MGE in table \ref{tab:MGEF814W}, convolved with the PSF in table \ref{tab:MGEF814W}, (gray lines).
+The MGE model is a good representation of the galaxy's light distribution within $\sim 5$ arcsec.
+Image scaling and orientation are indicated in the figure.
+The black line has a length of 10 arcsec and it's orientation corresponds to the galaxy's position angle as found in table \ref{tab:galaxyparameters}.
+For comparison the Einstein radius as found in table ???
+is indicated as red dashed line.
+This MGE is used in the dynamical Jeans modelling in \S ???.
+[TO DO: explain how this MGE is used in dynamical modelling]}
+\label{fig:MGEinnerRegions}
 \end{minipage}
@@
 \includegraphics[width=0.8\textwidth]{fig/1331F814W_MGE_disk_L.ps}
-\caption{??? [TO DO: caption]}
-\label{fig:???}
+\caption{MGE for J1331's outer regions: Comparison of contours with constant surface brightness of the smooth IRAF ELLIPSE model for J1331 in the F814W filter (yellow) with a corresponding best fit MGE (gray lines).
+The green box corresponds to the image section shown in Fig.
+\ref{{fig:MGEinnerRegions}, with the Einstein radius as dashed red line.
+[TO DO: caption]}
+\label{fig:MGEouterRegions}
 \end{minipage}
@@
 \begin{minipage}[t]{100mm}
-\caption{F814W MGE???}
+\caption{J1331's F814W MGE: Parameters of the best fit MGE to the F814W surface brightness of J1331 in Fig.
+\ref{fig:F814W}.
+The fit is best inside an radius of 5 arcsec.
+The galaxy center and position angle, which gives the orientation of the MGE with respect to the original image, are given in table \ref{tab:galaxyparameters}.
+This MGE is used in the dynamical modelling in \S ???.}
 \begin{tabular}{cccccc}
@@
 \end{tabular}
+\label{tab:galaxyparameters}
 \end{minipage}

### 2015-08-10 docs/abstract_v1.01.tex
Made notes for the introduction.
Wrote more stuff.

@@
 By fitting a gravitational potential model to the image positions, we constrain the mass inside the Einstein radius ($R_\text{ein}=0.91\pm0.02$ arcsec) to within 4\% ($M_\text{ein} = (7.8\pm0.3) \cdot 10^{10} M_\odot$).
-From Multi-Gaussian Expansions (MGE) of J1331's surface brightness distribution we find that J1331 has an apparent I-band magnitude of $m_I \simeq 15.8$ mag, a total luminosity of $L_{I,tot} \simeq 5.6 \cdot 10^{10}L_{I,\odot}$ and an effective radius of $R_\text{eff} \simeq 2.6$ arcsec = 5.6 kpc.
+From Multi-Gaussian Expansions (MGE) of J1331's surface brightness distribution we find that J1331 has a total I-band luminosity of $L_{I,tot} \simeq 5.6 \cdot 10^{10}L_{I,\odot}$ and an effective radius of $R_\text{eff} \simeq 2.6$ arcsec = 5.6 kpc.
+[TO DO: I guess, apparent magnitude is not very interesting.]
 
@@
 This could indicate a non-trivial re-distribution of matter due a possible minor merger event in J1331's past.
+
+[TO DO: something about mass to light ratios????]

### 2015-08-10 docs/results_lensing_v1.01.tex
Wrote more stuff.

@@
 \subsection{Mass distribution from Lensing}
+
+\paragraph{Image Positions.} We determine the positions of the lensing images by first subtracting a smooth model for the galaxy's surface brightness from the original image.
+As models we use MGE fits (cf.
+\S\ref{kap:MGE}) and IRAF ellipse fits (???) to the galaxy in each the F450W and F814W filter.
+(For example the MGE we use for F814W is the MGE given in tab.
+\ref{tab:MGEF814W} convolved with the PSF in tab.
+\ref{tab:PSFMGEF814W}.) The lensing images become then visible in the residuals (see fig.
+\ref{fig:lens_just_imgpos}).
+Because the lensing images are extended, we use the position of the brightest pixel in each of the images.
+We also use the F814W-MGE subtracted residuals from \citet{SWELLSIII}.
+The lensing positions as determined from the latter are given in tab.
+\ref{tab:lenspos}.
+The scatter of lensing positions as determined from subtracting different surface brightness models from the galaxy in different filters gives an error of $\pm 1$ pixel on the image positions.
+
+\begin{table}
+\centering
+\begin{minipage}{70mm}
+\begin{tabular}{r|rrrr|c}
+\hline
+  & A & B & C & D & G\\\hline
+$x_i$ [pixel] & 12.1 & -8.5 & 21.7 & -3.3 & 0.5 $\pm \sqrt{2}$ \\
+$y_i$ [pixel] & 16.6 & -10.4 & -0.5 & 19.2 & 0.5 $\pm \sqrt{2}$ \\
+\hline
+\end{tabular}
+\caption{Positions of the lensing images (A-D) and the galaxy center (G) in fig.
+\ref{fig:lens_just_imgpos}.
+The image positions were determined from the lens subtracted image for J1331 in figure 4 of \citet{SWELLSIII}, rotated to the $(x,y)$ coordinate system in fig.
+\ref{fig:lens_just_imgpos}.
+The pixel scale is 1 pixel = 0.05 arcsec and the error of each image position is $\pm$ 1 pixel.
+\textit{SMALL PROBLEM: Somehow I used $\sqrt(2)$ pixel as the error on the galaxy center in the Monte Carlo sampling code instead of the 0.5 pixel I claim here.
+Should I change this table and the error bars in the figures to match this bug????}}
+\label{tab:lenspos}
+\end{minipage}
+\end{table}
 
@@
 We introduce random noise according to the uncertainties in the Fourier shape parameters to create a mock observation that visualizes the effect of the measurement errors.
-To be able to compare the predicted mass distribution to the observed light distribution we transform the surface brightness into a mass density: We first integrate the MGE in tab.
+From the mock image's second moment we find an average axis ratio for the lens mass model of $q_\text{lens} \simeq 0.695$, which is consistent with the one found by \citet{SWELLSIII}, $q_\text{lens,SWELLSIII} = 0.67 \pm 0.09$, while the light's average axis ratio in Table \ref{tab:galaxyparameters} is $q' = 0.598$.
+\\To be able to compare the predicted mass distribution to the observed light distribution, we transform the surface brightness into a mass density: We first integrate the MGE in tab.
 \ref{tab:MGEF814W} to get the total luminosity within the Einstein radius and the predicted mass-to-light ratio as $\Upsilon_\text{I,ein} = M_\text{ein} / L_\text{I,ein}$.
@@
 \ref{fig:lenscompareboth} finally compares equidensity contours at the same values of both the predicted lens mass distribution and the observed surface brightness times $\Upsilon_\text{I,ein}$.
-We note the following three facts: 1.The mass predicted from lensing and the observed light distribution are oriented in the same direction.
+\\Figure \ref{fig:lenslightcompareALL} leads to the following three findings: 1.The mass predicted from lensing and the observed light distribution are oriented in the same direction.
 2.
-Within the Einstein radius mass and light distribution have the same shape, while further out the mass distribution is more roundish.
+Within the Einstein radius, mass and light distribution have the same shape, while further out the mass distribution is more roundish.
 3.
 The light distribution drops faster than the mass with increasing radius.
-This could indicate that the stellar component of the galaxy is superimposed by a more roundish dark matter component.
+\\Reasons for the difference in observed light and measured mass distribution could be, e.g.
+an apparent change of shape due to dust extinction, a strongly changing $\Upsilon_*$, or the stellar component of the galaxy could be superimposed by a more roundish dark matter component.
 
@@
 [TO DO: nice caption]}
-\label{fig:???}
+\label{fig:lenslightcompareALL}
 \end{figure*}

### 2015-08-10 docs/results_photometry_v1.01.tex
Wrote more stuff.

@@
 \subsection{Surface Photometry for J1331 with MGEs}
+
+%============================================================================
+
+\begin{figure}
+\centering
+\includegraphics[width=0.8\columnwidth]{fig/1331F814Wsci_MGE_M.ps}
+\caption{MGE for J1331's inner regions: Comparison of contours with constant F814W surface brightness of J1331's central region (orange lines) with the corresponding iso-brightness contours of the best fit MGE in table \ref{tab:MGEF814W}, convolved with the PSF in table \ref{tab:MGEF814W}, (gray lines).
+The MGE model is a good representation of the galaxy's light distribution within $\sim 5$ arcsec.
+Image scaling and orientation are indicated in the figure.
+The black line has a length of 10 arcsec and it's orientation corresponds to the galaxy's position angle as found in table \ref{tab:galaxyparameters}.
+For comparison the Einstein radius as found in table ???
+is indicated as red dashed line.
+This MGE is used in the dynamical Jeans modelling in \S ???.
+[TO DO: explain how this MGE is used in dynamical modelling]}
+\label{fig:MGEinnerRegions}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.8\columnwidth]{fig/1331F814W_MGE_disk_L.ps}
+\caption{MGE for J1331's outer regions: Comparison of contours with constant surface brightness of the smooth IRAF ELLIPSE model for J1331 in the F814W filter (yellow) with a corresponding best fit MGE (gray lines).
+The green box corresponds to the image section shown in Fig.
+\ref{fig:MGEinnerRegions}, with the Einstein radius as dashed red line.
+[TO DO: caption]}
+\label{fig:MGEouterRegions}
+\end{figure}
+
+%============================================================================
+
+\begin{table}
+\centering
+\caption{F814W PSF MGE: Parameters of the circular four-Gaussian MGE in Eq. (\ref{eq:PSFgeneral} fitted to the radial profile of the synthetic HST/F814W PSF image by [TO DO].}
+\begin{tabular}{ccc}
+\hline
+$k$ & $G_k$ & $\delta_k$ [arcsec] \\\hline
+1 & 0.184 & 0.038\\
+2 & 0.485 & 0.085\\
+3 & 0.222 & 0.169\\
+4 & 0.109 & 0.487\\\hline
+\end{tabular}
+\label{tab:PSFMGEF814W}
+\end{table}
+
+\begin{table*}
+\centering
+\caption{J1331's F814W MGE: Parameters of the best fit MGE to the F814W surface brightness of J1331 in Fig.
+\ref{fig:F814W}.
+The fit is best inside an radius of 5 arcsec.
+The galaxy center and position angle, which gives the orientation of the MGE with respect to the original image, are given in table \ref{tab:galaxyparameters}.
+This MGE is used in the dynamical modelling in \S ???.
+The first column gives the total F814W luminosity of the Gaussian in Eq.
+(\ref{eq:centralItotalL}) in units of counts.
+The second column is the corresponding I-band peak surface brightness in Eq.
+(\ref{eq:MGEgeneral}) in units of a luminosity surface density, calculated from the first column following the procedure described in \S ???.
+The third and fourth column give the dispersion and the last column the axis ratio of the Gaussian in Eq.
+(\ref{eq:MGEgeneral}).}
+\begin{tabular}{cccccc}
+\hline
+ & total luminosity  & surface density & \multicolumn{2}{c}{Gaussian dispersion} & axis ratio\\
+$k$  & $L_k$ [counts] & $I_{0,k}$ [$L_\odot$/pc$^2$] & $\sigma_k$ [arcsec] & $\sigma_k$ [kpc] & $q'_k$\\\hline
+1  &     9425.96 &      20768.  &  0.051   & 0.103  & 1.00\\
+2  &    13173.0 &        3161.2 &  0.178   & 0.358  & 0.76\\
+3  &    40235.0 &        1588.2 &  0.503   & 1.008  & 0.58\\
+4  &    67755.2 &         502.25&  1.180   & 2.368  & 0.56\\
+5  &    203677. &         136.51&  3.891   & 7.805  & 0.57\\\hline
+\end{tabular}
+\label{tab:MGEF814W}
+\end{table*}
+
+%============================================================================
+
+\begin{table*}
+\centering
+\caption{Galaxy Parameters of J1331}
+\begin{tabular}{lllrl}
+\hline
+redshift                  & $z_d$ & 0.113 & \citep{SWELLSIII}\\
+angular diameter distance & $D_d$ [Mpc] & 414 & \\
+scaling                   & 1 kpc / 1 arcsec & 2.006 & \\
+position angle            & $\phi$ [degrees] & wrt what???\\
+average axis ratio & $q'$ & 0.598\\
+average ellipticity & $\epsilon = 1 - q'$ & 0.402 & \\
+apparent I-band magnitude & $m_\text{I}$ [mag] & 15.77 & \\
+total I-band luminosity & $L_\text{tot,I}$ [$10^{10} L_\odot$] & 5.6 & \\
+effective half-light radius & $R_\text{eff}$ [arcsec] & 2.6 & \\
+& $R_\text{eff}$ [pc]& 5.2 & \\
+\hline
+\end{tabular}
+\label{tab:galaxyparameters}
+\end{table*}
+
+%============================================================================
 
@@
 
-\paragraph{Transformation into physical units.} To transform the MGE in units of counts into physical units, we apply a simplified version of the procedure described in \citet{Holtzman}.
+\paragraph{Transformation into physical units.} To transform the MGE in units of counts into physical units, we apply a simplified version of the procedure described in \citet{Holtzman}, analogous to [TO DO: Cappellari Read me file???]
 \\The scaling of the drizzled HST/WFC3 images is  $S = 0.05$ arcsec/pixel and the total exposure time $T = 1600$ sec.
-The total F814W luminosity in counts of each Gaussian of the MGE has a central flux in counts per pixel of
+The total F814W luminosity in counts of each Gaussian of the MGE has a central surface brightness in counts per pixel of
 \begin{equation*}
-C_0\text{[counts/pixel]} = \frac{L[counts]}{2\pi \sigma[\text{pixel}]^2 q}.
+C_0\text{[counts/pixel]} = \frac{L[\text{counts}]}{2\pi \sigma[\text{pixel}]^2 q}.
 \end{equation*}
 This is then transformed into an I-band surface brightness via
-\begin{equation*}
-\mu_I \simeq -2.5 \log_{10}\left( \frac{C_0\text{[counts/pixel]}}{T \cdot S^2}\right) + Z + C + A_I,
-\end{equation*}
-where $Z\simeq21.62$ is a the zero-point from \citet{Holtzman}  (updated according to \citet{Dolphin,DolphinNew}) for the photometric system of the HST/WFPC2 camera and the F814W filter plus a correction for the difference in gain of calibration and observation.
+\begin{equation}
+\mu_I \simeq -2.5 \log_{10}\left( \frac{C_0\text{[counts/pixel]}}{T[\text{sec}] \cdot S[\text{arcsec/pixel}]^2}\right) + Z + C + A_I, \label{eq:muI_}
+\end{equation}
+where $Z\simeq21.62$ is a the zero-point from \citet{Holtzman}  (updated according to \citet{Dolphin,DolphinNew}) for the photometric system of the HST/WFPC2 camera and the F814W filter plus a correction for the difference in gain between calibration and observation.
 $C= 0.1$ corrects for the finite aperture of the WFPC2.
 And $A_I =0.015$ mag  is the extinction in the I-band tpwards J1331, according to the NASA/IPAC Extragalactic Database [TO DO: proper reference].
-The correction between the F814W filter and the I-band of the UBVRI photometric system is  small \citep{Holtzman} and we neglect it therefore.
+The color-dependent correction between the F814W filter and the I-band of the UBVRI photometric system is  small \citep{Holtzman} and we neglect it therefore.
+The last step is to transform the surface brightness $\mu_i$ in mag to the I-band surface density of the Gaussian in $L_\odot$/pc$^2$ as
+\begin{eqnarray*}
+I_0[L_\odot \text{pc}^{-2}] = \left( 64800/\pi\right)^2 \left(1+z \right)^4 10^{0.4\left(M_{\odot,I}-\mu_I \right)},
+\end{eqnarray*}
+where the term with $z$ accounts for redshift dimming and $M_{\odot,I}=4.08$ mag is the sun's absolute I-band magnitude \citep{1998gaas.book.....B}.
+The luminosity $L_k$[counts] and the corresponding surface brightness density $I \equiv I_{0,k}[L_\odot \text{pc}^{-2}]$ of each Gaussian are given in Table \ref{fig:MGEinnerRegions}.
+[TO DO: I'm really confused about this.
+Check, that everything is correct and the naming of quantities, e.g.
+with or without subscripts of 0, is fine???] [TO DO: Maybe shift to appendix???]
 
-[TO DO]
+\paragraph{Inclination.} [TO DO: Do we need this for the dynamical modelling???? Is described on p. 56]
+
+\paragraph{Total luminosity and effective radius.} J1331's total I-band luminosity is easily determined by summing up the luminosity contributions of all the Gaussians of the MGE for the outer regions (shown as gray lines in Fig.
+\ref{fig:MGEouterRegions}).
+We find $L_\text{tot,I} \simeq 5.6 \cdot 10^{10} L_\odot$.
+This corresponds to an apparent magnitude of $m_I = 15.77$ mag.
+We determine the circularized effective radius $R_\text{eff}$ of J1331 from the definition $L(<R_\text{eff}) \equiv \frac 12 L_\text{tot}$ and the growth curve $L(<R)$ from the MGE model of the outer regions [TO DO: Maybe I need a table anyway???], where $R$ is the projected radius on the sky [TO DO: Or is it $R'$???].
+We find the effective radius to be $R_\text{eff} \simeq 2.6 \text{arcsec} \hat{=} 5.2 \text{kpc}$.
+All values are summarized in Table \ref{tab:galaxyparameters}.
 
@@
 \begin{itemize}
-\item fit sof MGE to J1331s surface brightness within $\sim$ 2 half-light radii, and to an Iraf Ellipse model for J1331's outer regions, make it possible to easily deconvolve the hst images with its PSF.
 \item the deporjecten if the galaxy under the assumption of oblate axisymmetry and an estimated inclination of $\sim70^\circ$ can be performed analytically.
 \end{itemize}
-
-%============================================================================
-
-\begin{figure}
-\begin{minipage}[c]{\linewidth}
-\centering
-\includegraphics[width=0.8\textwidth]{fig/1331F814Wsci_MGE_M.ps}
-\caption{MGE for J1331's inner regions: Comparison of contours with constant F814W surface brightness of J1331's central region (orange lines) with the corresponding iso-brightness contours of the best fit MGE in table \ref{tab:MGEF814W}, convolved with the PSF in table \ref{tab:MGEF814W}, (gray lines).
-The MGE model is a good representation of the galaxy's light distribution within $\sim 5$ arcsec.
-Image scaling and orientation are indicated in the figure.
-The black line has a length of 10 arcsec and it's orientation corresponds to the galaxy's position angle as found in table \ref{tab:galaxyparameters}.
-For comparison the Einstein radius as found in table ???
-is indicated as red dashed line.
-This MGE is used in the dynamical Jeans modelling in \S ???.
-[TO DO: explain how this MGE is used in dynamical modelling]}
-\label{fig:MGEinnerRegions}
-\end{minipage}
-\begin{minipage}[c]{\linewidth}
-\centering
-\includegraphics[width=0.8\textwidth]{fig/1331F814W_MGE_disk_L.ps}
-\caption{MGE for J1331's outer regions: Comparison of contours with constant surface brightness of the smooth IRAF ELLIPSE model for J1331 in the F814W filter (yellow) with a corresponding best fit MGE (gray lines).
-The green box corresponds to the image section shown in Fig.
-\ref{{fig:MGEinnerRegions}, with the Einstein radius as dashed red line.
-[TO DO: caption]}
-\label{fig:MGEouterRegions}
-\end{minipage}
-\end{figure}
-
-%============================================================================
-
-\begin{table*}
-\centering
-\begin{minipage}[t]{40mm}
-\caption{F814W PSF MGE: Parameters of the circular four-Gaussian MGE in Eq. (\ref{eq:PSFgeneral} fitted to the radial profile of the synthetic HST/F814W PSF image by [TO DO].}
-\begin{tabular}{ccc}
-\hline
-$k$ & $G_k$ & $\delta_k$ [arcsec] \\\hline
-1 & 0.184 & 0.038\\
-2 & 0.485 & 0.085\\
-3 & 0.222 & 0.169\\
-4 & 0.109 & 0.487\\\hline
-\end{tabular}
-\label{tab:PSFMGEF814W}
-\end{minipage}
-\hspace{10mm}
-\begin{minipage}[t]{100mm}
-\caption{J1331's F814W MGE: Parameters of the best fit MGE to the F814W surface brightness of J1331 in Fig.
-\ref{fig:F814W}.
-The fit is best inside an radius of 5 arcsec.
-The galaxy center and position angle, which gives the orientation of the MGE with respect to the original image, are given in table \ref{tab:galaxyparameters}.
-This MGE is used in the dynamical modelling in \S ???.}
-\begin{tabular}{cccccc}
-\hline
- & total luminosity  & surface density & \multicolumn{2}{c}{Gaussian dispersion} & axis ratio\\
-$k$  & $L_k$ [counts] & $I_{0,k}$ [$L_\odot$/pc$^2$] & $\sigma_k$ [arcsec] & $\sigma_k$ [kpc] & $q'_k$\\\hline
-1  &     9425.96 &      20768.  &  0.051   & 0.103  & 1.00\\
-2  &    13173.0 &        3161.2 &  0.178   & 0.358  & 0.76\\
-3  &    40235.0 &        1588.2 &  0.503   & 1.008  & 0.58\\
-4  &    67755.2 &         502.25&  1.180   & 2.368  & 0.56\\
-5  &    203677. &         136.51&  3.891   & 7.805  & 0.57\\\hline
-\end{tabular}
-\label{tab:MGEF814W}
-\end{minipage}
-\end{table*}
-
-%============================================================================
-
-\begin{table}
-\centering
-\begin{minipage}{140mm}
-\caption{Galaxy Parameters of J1331}
-\begin{tabular}{lllrl}
-\hline
-redshift                  & $z_d$ & 0.113 & \citep{SWELLSIII}\\
-angular diameter distance & $D_d$ [Mpc] & 414 & \\
-scaling                   & 1 kpc / 1 arcsec & 2.006 & \\
-position angle            & $\phi$ [degrees] & wrt what???\\
-average axis ratio & $q'$ & 0.598\\
-average ellipticity & $\epsilon = 1 - q'$ & 0.402 & \\
-apparent F814W magnitude & $m_\text{F814W}$ [mag] & 15.77 & \\
-total F814W luminosity & $L_\text{tot,F814W}$ [$10^{10} L_\odot$] & 5.6 & \\
-effective half-light radius & $R_\text{eff}$ [arcsec] & 2.6 & \\
-& $R_\text{eff}$ [pc]& 5.2 & \\
-\hline
-\end{tabular}
-\label{tab:galaxyparameters}
-\end{minipage}
-\end{table}

### 2015-08-11 docs/abstract_v1.01.tex
Small change in abstract.

--- 2015-08-04 docs/abstract_v1.01.tex
@@
 According to the long-slit major axis stellar kinematics from \citet{SWELLSV}, J1331 has a counter-rotating stellar core inside $\sim 2$ arcsec.
-We model the observed stellar kinematics in J1331's central regions by finding MGE models for the surface brightness, stellar and dark matter distribution that solve the axisymmetric Jeans equations.
-We test galaxy models for (A) mass-follows-light with velocity anisotropy, (B) an increasing mass-to-light ration gradient, (C) the best fit lens model, and (D) including an NFW dark matter halo.
-We show that, because model (A) fails to reproduce the observed kinematics, J1331 requires a steep total mass-to-light ratio gradient in the center.
-Model (B) predicts independently the same total mass inside the Einstein radius as the lens model, and vice versa model (C) gives an independent prediction of the observed kinematics in the galaxy center.
-We constrain the NFW halo of J1331 in model (D) to have a virial velocity $v_{200} \simeq 240 \pm 40$ km/s and a concentration of $c_{200} \simeq 8 \pm 2$ in case of a moderate tangential velocity anisotropy of $\beta_z \simeq −0.4 \pm 0.1$.
+We model the observed stellar kinematics in J1331's central regions by finding MGE models for the stellar and dark matter distribution that solve the axisymmetric Jeans equations.
+We find that J1331 requires a steep total mass-to-light ratio gradient in the center to reproduce the observed stellar kinematics.
+The best fit dynamical model predicts a total mass inside the Einstein radius consistent with the lens model, and vice versa the lens model gives an successful prediction for the observed kinematics in the galaxy center.
+For a dynamical model including a NFW dark matter halo,  we constrain the halo to have virial velocity $v_{200} \simeq 240 \pm 40$ km/s and a concentration of $c_{200} \simeq 8 \pm 2$ in case of a moderate tangential velocity anisotropy of $\beta_z \simeq −0.4 \pm 0.1$.
 The NFW halo models can successfully reproduce the signatures of J1331's counter-rotating stellar core and predict J1331's rotation curve at larger radii.

### 2015-08-11 docs/model_JAM_v1.01.tex

@@
 
+Jeans axisymmetric models (JAM) assume galaxies (1a) to be collisionless, i.e.
+the collisionless Boltzmann equation for the distribution function $f(\vect{x},\vect{v},t)$ has to be satisfied ($\frac{\diff f(\vect{x},\vect{v},t}{\diff t} = 0$), (1b) in a steady state ($\frac{\partial}{\partial t} = 0$), (1c) axisymmetric (best described in cylindrical coordinates $(R,z,\phi)$ and $\frac{\partial}{\partial \phi} = 0$) and (2) to have their velocity ellipsoid aligned with the cylindrical coordinate system.
+From this follow the Jeans equations as the vector-valued first moment of the Boltzmann equation, i.e.
+\begin{equation*}
 [TO DO]
+\end{equation*}
+[TO DO]

### 2015-08-11 docs/model_lensing_v1.01.tex

@@
 When we fix the slope $\alpha$, then the lens equation is a purely linear problem and can be solved numerically for the source position $(\xi,\eta)$ and the Fourier parameters $(a_k,b_k)$ given one observed image at position $(x_i=R'_i \cos \theta_i,y_i=R'_i \sin \theta_i)$.
+
+\paragraph{Model fitting.} As described above our lensing model has the following free parameters: the source position $(\xi,\eta)$, and the radial slope $\alpha$ and Fourier parameters $(a_k,b_k)$ of the lens mass distribution in eq.
+(\ref{eq:scalefreemodel}) and (\ref{eq:Fourieransatz}).
+We want to find the lensing model which minimizes for all four images the distance between the observed image positions $\vec{\theta}_{oi}$ and those predicted by the lensing model $\vec{\theta}_{pi}$.
+Because we want to avoid solving the lens equation (cf.
+eq.
+(\ref{eq:lenseqpot}) and (\ref{eq:Fourierlenseq})) for $\theta_{pi}$, we follow \citet{1991ApJ...373..354K} and cast the calculation back to the source plane using the magnification tensor in eq.
+(\ref{eq:magnificationtensor}):
+\begin{eqnarray*}
+\chi^2_\text{lens} &=& \sum_{i=1}^{4} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right) \left( \vec{\theta}_{pi} - \vec{\theta}_{oi} \right)\right|^2\\
+&\simeq& \sum_{i=1}^{N} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right)  \left.\mathscr{M}\right|_{\vec{\theta}=\vec{\theta}_{oi}} \left( \begin{matrix} \xi - \tilde{\xi}_i \\ \eta - \tilde{\eta}_i \end{matrix} \right) \right|^2,
+\end{eqnarray*}
+where $(\Delta_x,\Delta_y)$ are the measurement errors of the image positions $\vec{\theta}_{oi}$.
+$\left.\mathscr{M}\right|_{\vec{\theta}=\vec{\theta}_{oi}}$ is the magnification tensor and $(\tilde{\xi}_i,\tilde{\eta}_i)$ the source position according to the lens equation evaluated at $\vec{\theta}_{oi}$.
+Following \citet{GlennEC} we add a term
+\begin{equation*}
+\chi^2_\text{shape} = \lambda \sum_{k \geq 3} \frac{\left(a_k^2 +b_k^2 \right)}{a_0^2} 
+\end{equation*}
+which forces the shape of the mass distribution to be close to an ellipse. The total $\chi^2$ to minimize is therefore
+\begin{equation*}
+\chi^2 = \chi^2_\text{lens} + \chi^2_\text{shape}
+\end{equation*}
+We set $a_1 = b_1 = 0$, which corresponds to the choice of origin; in this case the center of the galaxy.
+\\To be able to constrain the slope $\alpha$, we would have needed flux ratios for the images as in \citet{GlennEC}.
+But the extended quality of the images and the uncertainty in surface brightness subtraction makes flux determination too unreliable and we do not include them in the fitting.
+Even though the constraint from just the image position fit on $\alpha$ is very weak, we were however able to show that the image positions in tab.
+\ref{tab:lenspos} minimize $\chi^2$ at $\alpha=1$ and also our other image position sets from different models and filters are consistent with a flat rotation curve.
+In the following we therefore set $\alpha=1$.

### 2015-08-11 docs/model_JAM_v1.01.tex
Started writing section on JAM.

--- 2015-08-04 docs/model_JAM_v1.01.tex
@@
 
-[TO DO]
+Jeans axisymmetric models (JAM) assume galaxies (a) to be collisionless, i.e.
+the collisionless Boltzmann equation for the distribution function $f(\vect{x},\vect{v},t)$ has to be satisfied ($\frac{\diff f(\vect{x},\vect{v},t}{\diff t} = 0$), (b) in a steady state ($\frac{\partial}{\partial t} = 0$), (c) axisymmetric (best described in cylindrical coordinates $(R,z,\phi)$ and $\frac{\partial}{\partial \phi} = 0$).
+From this follow the axisymmetric Jeans equations as the vector-valued first moment of the Boltzmann equation, i.e.
+\begin{equation*}
+\int \frac{\diff f}{\diff t} \Diff3 v = 0.
+\end{equation*}
+To be able to solve the Jeans equations, additional assumptions about the velocity ellipsoid tensor $\langle v_i v_j\rangle$ have to be made.
+We follow \citet{Cap08} and assume firstly, that the galaxy's velocity ellipsoid is aligned with the cylindrical coordinate system, i.e.
+$\langle v_i v_j\rangle = 0$ for $i\neq j$.
+Secondly, we assume a constant ratio between the radial and vertical 2nd velocity moments, $\beta_z \equiv 1 - \langle v_z^2 \rangle / \langle v_R^2\rangle$.
+This reduces the Jeans equations to two equations for $\langle v_z^2 \rangle$ and $\langle v_\phi^2 \rangle$, that can be solved by means of one integration,
+\begin{eqnarray*}
+n \langle v_z^2 \rangle (R,z) &=& \int_0^\infty n \frac{\partial \Phi}{\partial z} \diff z\\
+n \langle v_\phi^2 \rangle (R,z) &=& R \frac{\partial}{\partial R} \left( \frac{n \langle v_z^2 \rangle}{1-\beta_z} \right) + \frac{n \langle v_z^2 \rangle}{1 - \beta_z} + R n \frac{\partial \Phi}{\partial R},
+\end{eqnarray*}
+where $n(\vect{x}) = \int f(\vect{x},\vect{v}) \diff3 v$ is the number density of tracers and $\Phi(\vect{x})$ the galaxy's gravitational potential, generated by the mass density $\rho(\vect{x})$ via Poisson's equation.
+\\The JAM modelling approach by \citet{Cap08} makes use of expressing the tracer density and the mass density as MGEs (see also [TO DO: REF: Emsellem et al.
+19994]).
+The density of stellar tracers is assumed to be proportional to the observed and deprojected brightness distribution $\nu(R,z)$ in Eq.
+(\ref{eq:deprojMGE}).
+The mass density consists of several sets of MGEs: One MGE, that is usually taken to be $\nu(R,z)$ multiplied by a constant stellar mass-to-light ratio $\Upsilon_*$, describes the distribution of stellar mass in the galaxy.
+To mimick gradients of stellar mass-to-light ratio, each Gaussian could be assigned its own $\Upsilon_{*,i}$.
+To add a Navarro-Frenck-White (NFW) [TO DO: REF] dark matter halo component, a MGE generated from a fit to a NFW profile can be added to the stellar component.
+[TO DO: continue on p.
+74]
+
+\paragraph{Data comparison.} As data we use stellar line-of-sight rotation velocities $v_\text{rot} \equiv \langle v_\text{los} \rangle$ [TO DO: consistent, los or rot] and velocity dispersions $\sigma$ as described in \S\ref{sec:data}.
+The JAM models give us a prediction for the second line-of-sight velocity moment $v_\text{los}$.
+The root mean square (rms) line-of-sight velocity $v_\text{rms}$ allows a data-model comparison by relating theses velocities according to
+\begin{equation*}
+v_\text{rms}^2 = \langle v_\text{los}^2 \rangle = v_\text{rot}^2 + \sigma^2.
+\end{equation*}

### 2015-08-11 docs/model_MGE_v1.01.tex
Started writing section on JAM.

@@
 I(R',\theta') &=& \sum_{i=1}^{N} I_{0,i} \exp\left[ - \frac{1}{2\sigma_i^2} \left(x^{'2} + \frac{y^{'2}}{q_i^{'2}}\right)\right]\label{eq:MGEgeneral}\\
-\text{with } I_{0,i} &=& \frac{L_i}{2\pi \sigma_i^2 q'_i}\nonumber\\%\label{eq:centralItotalL}\\
+\text{with } I_{0,i} &=& \frac{L_i}{2\pi \sigma_i^2 q'_i}\label{eq:centralItotalL}\\
 \text{and } x'_i &=& R' \cos(\theta' - \phi)\nonumber\\
@@
 
-[TO DO]
-
-\paragraph{Other stuff to mention}
-\begin{itemize}
-\item [TO DO] analytic deprojection into 3D Gaussians
-\end{itemize}
+$I(R',\theta')$ describes the intrinsic, to 2D projected light distribution or surface density of the galaxy.
+Under the assumption that the galaxy is oblate and axisymmetric, and given the inclination angle $i$ of the galaxy with respect to the observer, MGEs allow an analytic deprojection of the 2D MGE to get a 3D light distribution or density $\nu(R,z)$ for the galaxy,
+\begin{equation}
+\nu(R,z) = \sum_i \nu_{0,i} \exp \left[-\frac{1}{2\sigma_i}\left(R^2 + \frac{z^2}{q_i^2} \right) \right]. \label{eq:deprojMGE}
+\end{equation}
+The flattening of each axisymmetric 3D Gaussian $q$ and its central density $\nu_{0,i}$ follow from the observed 2D axis ratio $q'_i$ and surface density $I_{0,i}$ as
+\begin{eqnarray*}
+q_i^2 &=& \frac{q_i'^2 - \cos^2 i}{\sin^2 i}\\
+\nu_{0,i} &=& \frac{q_i' I_{0,i}}{q_i \sqrt{2 \pi \sigma_i^2}}.
+\end{eqnarray*}

### 2015-08-11 docs/results_photometry_v1.01.tex
Started writing section on JAM.

@@
 
-\paragraph{Inclination.} [TO DO: Do we need this for the dynamical modelling???? Is described on p. 56]
+\paragraph{Inclination.} To estimate the inclination of J1331 with respect to the observer, we use the observed axis ratio of the flattest ellipse in the Iraf Ellipse [TO DO] model for J1331, which is $q'=0.42$.
+This is similar to the disk axis ratio of $q' = 0.40$ found by \citet{SWELLSI} [TO DO: CHECK].
+If a typical thickness of an oblate disk was around $q_0 \sim 0.2$ [TO DO: REF: Holmberg 1985], the inclination would follow from $\cos^2 i = \frac{q'^2 - q_0^2}{1 - q_0^2}$ and a correction of $+3^\circ$ [TO DO: REF: Tully 1988].
+Our estimate for the inclination is therefore $i \approx 70^\circ$.
 

### 2015-08-11 docs/data_v1.01.tex
Wrote sections on MGE fitting results.
Added stuff to data section.

@@
-\section{Data}
+\section{Data} \label{sec:data}
 
@@
 \item ??? filter: to identify bluish lensing images
+\item drizzled image
 \end{itemize}
+
+\paragraph{Stellar Kinematics.} We use the stellar kinematics for J1331 measured by [TO DO: REF: Dutton 2013].
+They obtained long-slit spectra along J1331's major-axis with the Low Resolution Imaging Spectrograph (LRIS) on the Keck I 10m telescope.
+The width of the slot was 1 arcsec and the seeing Conditions had a FWHM of $\sim 1.1$ arcsec.
+Spectra for spatial bins of different widths along the major axis were extracted.
+Analogously to [TO DO: REF: Dutton 2011] they measured line-of-sight rotation velocities ($v_\text{rot}$) and stellar velocity dispersion ($\sigma$) by fitting Gaussian line profiles to emission lines in these spectra.
+Gas kinematics were extracted from fits to H$\alpha$ and NII lines, as tracers for inonized gas.
+\\The stellar kinematics, $v_\text{rot}$, $\sigma$ and $v_\text{rms}^2=v_\text{rot}^2 + \sigma^2$ are [TO DO]

### 2015-08-13 docs/data_v1.01.tex
Started writing data section.

@@
 Gas kinematics were extracted from fits to H$\alpha$ and NII lines, as tracers for inonized gas.
-\\The stellar kinematics, $v_\text{rot}$, $\sigma$ and $v_\text{rms}^2=v_\text{rot}^2 + \sigma^2$ are [TO DO]
+\\The stellar kinematics, $v_\text{rot}$, $\sigma$ and $v_\text{rms}^2=v_\text{rot}^2 + \sigma^2$ are shown in Figure \ref{fig:kinematics}.
+The rotation curve reveals a counter-rotating core within 2 arcsec $\simeq$ 4 kpc.
+Outside of $\sim 3.5 arcsec$ there is a steep drop in the dispersion, which is exptected at the boundary between the pressure supported bulge and the rotationally supported disk, which appears around this radius in the F450W filter in Figure \ref{fig:F450W}.
+However, in the brighter F814W filter in Figure \ref{fig:F814W}  the large reddish bulge extends out to $\sim$5 arcsec.
+\\Inside of $\sim 4$ arcsec, the data appears to be symmetric, outside of this the assumption of axisymmetry seems not to be valid anymore, considering the data.
+We add -2.3 km/s to the $v_\text{rot}$ to ensure $v_\text{rot}(R=0) \sim 0$ as a possible correction term for a systematic misjudgement of the systemic velocity.
+We also symmetrize the data within 4 arcsec and asign a minimum error of $\delta v_\text{rms} > 5$ km/s to the $v_\text{rms}$ data.
+In the JAM modelling, which is based on the assumption of axisymmetry, only kinematics within $\sim 2.5$ and 4 arcsec are used.
+Another reason to restrict to modelling on the bulge region is that our MGE in Table \ref{tab:MGEF814W} is only a good representation of J1331's F814W light distribution inside $\sim 5$ arcsec.

### 2015-08-13 docs/model_JAM_v1.01.tex
Started writing data section.

@@
 \end{equation*}
+The model in Eq.
+[TO DO] predicts the intrinsic $\langle v_\text{los}^2 \rangle$ at a given position on the sky, which have then to be modified to model the mode of observation, to be comparable to the measurements.
+The measured $v_\text{rms}$ is a light-weighted mean for a pixel along the long-slit of the spectrograph, with height $L_y = 1$ arcsec [TO DO: REF: Dutton 2013] and a certain given extent in along the major axis, $L_x$, i.e.
+for a rectangular aperture
+\begin{equation*}
+\text{AP}(x,y) = \left\{ \begin{array}{ll} 1 & \text{for } -\frac{L_x}{2} \leq x \leq + \frac{L_x}{2} \text{ and } - \frac{L_y}{2} \leq y \leq + \frac{L_y}{2}  \\ 0 & \text{otherwise} \end{array} \right.
+.
+\end{equation*}
+The light arriving at the spectrograph itself was subject to seeing, i.e. a Gaussian 
+\begin{equation*}
+\text{PSF}(x,y)=\mathscr{N}(0,FWHM/2\sqrt{2\ln2})
+\end{equation*}
+with FWHM=1.1 arcsec  [TO DO: REF: Dutton 2013]. The model predictions have therefore to be convolved with the convolution kernel
+\begin{eqnarray*}
+K(x,y) &=& (\text{PSF} \ast \text{AP})(x,y) \\
+&=& \frac{1}{4} \prod_{u \in \{x,y\}} \left[ \text{erf}\left( \frac{L_u/2 - u}{\sqrt{2}\sigma_\text{seeing}}\right) + \text{erf} \left( \frac{L_u/2 + u}{\sqrt{2} \sigma_\text{seeing}} \right) \right]
+\end{eqnarray*}
+and weighted by the surface brightness $I(x,y)$ [TO DO: primed x and y or not????]
+\begin{eqnarray*}
+I_\text{obs} &=& I \ast K\\
+\langle v_\text{los}^2 \rangle |_\text{obs} &=& \frac{(I \langle v_\text{los}^2\rangle) \ast K}{I_\text{obs}}.
+\end{eqnarray*}
+If provided with with the convolution kernel, the JAM code by [TO DO: REF: Cappellari 2008] [TO DO: reference code] performs the convolution numerically.
+We set $L_x = 0.21$ arcsec as the width of the model pixel, and get a prediction for the actual measurements in bins of width 0.63, 1.26 and 1.89 arcsec [TO DO: REF: Dutton 2013] as light-weighted mean from each 3, 6 and 9 model pixels.

### 2015-08-13 docs/results_JAMwithSB_v1.01.tex
Started writing data section.
Started writing section on JAM modelling with surface brightness MGE. Updated plot on model G enclosed mass.

@@
 
-\subsubsection{... with "Mass-follows-Light" and Velocity Anisotropy}
+\paragraph{...
+with the Lens Mass Model.} Our first JAM model uses the mass distribution which we found from lensing constraints in \S\ref{sec:results_lensing} to generate an independent prediction for the $v_\text{rms}$ curve following the procedure in \S\ref{sec:model_JAM}.
+In addition to the flat rotation curve model with $\alpha = 1$ in Table \ref{tab:bestfitlensmodel}, we also investigate a lens model, which was found as a best fit to the lensing images when assuming a [TO DO: rising or droppint???] rotation curve slope of $\alpha=1.1$.
+The predictions are compared with the data in Figure \ref{fig:JAM_modelL}.
+The agreement between the lensing prediction and the observed kinematics within $R' \sim 3$ arcsec is striking, especially around the Einstein radius.
+The $\alpha = 1$ model fits the wings nicely, while the $\alpha = 1.1$ model recreates almost exactly the observed central dip.
+The sharp drop in $v_\text{rms}$ around $R' \sim 3$ arcsec [TO DO: make sure all projected Rs are $R'$] cannot be reproduced, however.
+But outside of the Einstein radius our lensing models are only extrapolations and the true constraint is around the Einstein radius.
+
+%==================================================================
+
+\begin{figure}
+  \centering
+  \includegraphics[height=6cm]{fig/lensing_JAM_comparision.ps}
+  \caption{Comparison (not a fit!) of the symmetrized stellar $v_\text{rms}$ data of J1331 (blue dots) with JAM models generated from mass distributions which were independently derived from lensing constraints in \S\ref{sec:results_lensing}.
+The red solid line corresponds to the lens model for a flat rotation curve ($\alpha = 1$) in Table \ref{tab:bestfitlensmodel}; the green line is a best fit lens model found analogously from the image positions, but for a fixed rotation curve slope of $\alpha = 1.1$.
+For the JAM modelling a best fit MGE to the lens mass models were used, as well as the observed surface brightness MGE in Table \ref{tab:MGEF814W}, assuming velocity isotropy $\beta_z = 0$ and an inclination of $i = 70^\circ$.The red and black dotted lines are the Einstein radius and the effective half-light radius, respectively.}
+  \label{fig:JAM_modelL}
+\end{figure}
+
+%==================================================================
+
+\paragraph{...
+with "Mass-follows-Light" and Velocity Anisotropy.} Our second JAM model is a mass-follows-light model, which are often used in dynamical JAM modelling (e.g.
+\citet{GlennEC,Cap06}), where the mass distribution ins generated by multiplying the light distribution in Table \ref{tab:MGEF814W} by a constant total mass-to-light ratio  $\Upsilon_{I,\text{tot}}^\text{dyn}$.
+This assumes that the dark matter is always a constant fraction of the total matter distribution everywhere.
+This simplified model sometimes gives good representations of the inner parts of galaxies, where the stellar component dominates.
+In addition to the free fit parameter  $\Upsilon_{I,\text{tot}}^\text{dyn}$, we also allow for a overall constant but non-zero velocity anisotropy $\beta_z$.
+The best fit is found by minimizing $\chi^2$ between the $v_\text{rms}$ data and model prediction and is demonstrated in Figure \ref{fig:JAM_modelA2}.
+For $\beta_z$ we impose the fitting limits $\beta_z \in [-0.5,+0.5]$.
+While the outer parts of galaxies often show radially biased velocity anisotropy up to $\sim 0.5$ (from dynamical modelling of observed elliptical galaxies (e.g.
+\citet{Kronawitter2000}) and cosmological simulations (e.g.
+\citet{2004MNRAS.352..535D,2001ApJ...557..533F}), the centers of galaxies are near-isotropic or have  negative velocity anisotropy \citep{2003ApJ...583...92G}.
+Only in extreme models (e.g.
+around in-spiralling supermassive black holes \citep{1997NewA....2..533Q}) velocity anisotropies as low as $\sim -1$ have been found.
+A lower limit of $\beta_z \geq -0.5$ is a realistic assumption for J1331, for which we do not expect extreme dynamical conditions.
+The best fit in Figure \ref{fig:JAM_modelA2} however strives to very negative velocity anisotropies to be able to get the deep central dip in the  $v_\text{rms}$ curve.
+But $\beta_z = -0.5$ is not even a remotely agreeable fit and lower anisotropies are not to be expected and realistic.
+We also tested radial profiles for $\beta_z(R)$ of the form proposed by \citet{BaesVanHese}, which was however equally unable to reproduce the data.
+We conclude, that this is due to the well-known degeneracy between anisotropy and mass profile [TO DO: REF] and the mass-follows-light model is \emph{not} a good representation of the mass distribution in J1331's inner regions.
+
+%==================================================================
+
+\begin{figure}
+  \centering
+  \includegraphics[height=6cm]{fig/jam_A2_vrms.ps}
+  \caption{Comparison of the symmetrized $v_\text{rms}$ data of J1331 (blue dots) with a best fit dynamical JAM model (solid red line) assuming mass-follows-light and with two free parameters: $\Upsilon_{I,\text{tot}}^\text{dyn}$, the total I-band mass-to-light ratio found from dynamics, which converts the observed surface brightness in Table \ref{tab:MGEF814W} into a mass distribution, and the velocity anisotropy parameter $\beta_z$.
+The "best" fit is $\Upsilon_{I,*}^\text{dyn} = 4.8 \pm 0.1$ and $\beta_z = -0.5$, where the latter is however pegged at the lower limit of the allowed value range.
+This is obviously not a good model.}
+  \label{fig:JAM_modelA2}
+\end{figure}
+
+%==================================================================
+
+\paragraph{...
+with Increasing Mass-to-Light Ratio Gradient.} In \S\ref{sec:results_lensing} we found from the lensing, that the light distribution might drop faster with radius than the mass distribution.
+This would correspond to a radially increasing total mass-to-light ratio.
+As velocity anisotropy alone cannot explain the observed kinematics in a simple a mass-follows-light model, we now allow for an increasing mass-to-light ratio gradient in the JAM modelling to generate a mass model from the light distribution in Table \ref{tab:MGEF814W}.
+We do this by assigning each of the five Gaussians in the MGE its own mass-to-light ratio and replace the total luminosity in Eq.
+(\ref{eq:centralItotalL}) $L_i$ with the Gaussians total Mass $M_i = \Upsilon_{i} L_i$.
+We treat the five $\Upsilon_i$ as free parameters and only require that $\Upsilon_{j} \geq \Upsilon_i$ when the corresponding $\sigma_j \geq \sigma_i$ to ensure an overall mass-to-light ratio that is increasing with radius.
+[TO DO: Discuss Figure]
 
@@
 
-\begin{figure*}
-\centering
-\begin{minipage}{.5\textwidth}
-  \centering
-  \includegraphics[height=6cm]{fig/jam_A2_vrms.ps}
-  \caption{???
-Preliminary crappy caption: Failed try to fit a mass-follows-light model to the central regions of the galaxy.
-"Best fit" velocity anisotropy $\beta = -1/2$ is pegged at lower limit.
-???
-[TO DO: nice caption]}
-  \label{fig:???}
-\end{minipage}%
-\begin{minipage}{.5\textwidth}
-  \centering
-  \includegraphics[height=6cm]{fig/lensing_JAM_comparision.ps}
-  \caption{??? Preliminary crappy caption: Observed vrms is overplotted (not fitted) with best fit lens mass models for $\alpha = 1$ (red) and $\alpha = 1.1$ (green).??? [TO DO: nice caption]}
-  \label{fig:???}
-\end{minipage}
-\end{figure*}
-
-\subsubsection{... with Increasing Mass-to-Light Ratio Gradient}
-
-[TO DO]
+%==================================================================
 
@@
 
-\subsubsection{... with the Lens Mass Model}
-
-[TO DO]
+%==================================================================

### 2015-08-14 docs/results_JAMwithSB_v1.01.tex
Small changes.

@@
 \paragraph{...
-with Increasing Mass-to-Light Ratio Gradient.} In \S\ref{sec:results_lensing} we found from the lensing, that the light distribution might drop faster with radius than the mass distribution.
+with Increasing Mass-to-Light Ratio.} In \S\ref{sec:results_lensing} we found from the lensing, that the light distribution might drop faster with radius than the mass distribution.
 This would correspond to a radially increasing total mass-to-light ratio.
-As velocity anisotropy alone cannot explain the observed kinematics in a simple a mass-follows-light model, we now allow for an increasing mass-to-light ratio gradient in the JAM modelling to generate a mass model from the light distribution in Table \ref{tab:MGEF814W}.
+As velocity anisotropy alone cannot explain the observed kinematics in a simple a mass-follows-light model, we now allow for an mass-to-light ratio gradient in the JAM modelling to generate a mass model from the light distribution in Table \ref{tab:MGEF814W}.
 We do this by assigning each of the five Gaussians in the MGE its own mass-to-light ratio and replace the total luminosity in Eq.
@@
   \includegraphics[height=6cm]{fig/jam_G_vrms.ps}
-  \caption{???}
-  \label{fig:???}
+  \caption{Comparison between the stellar $v_\text{rms}$ data (blue points) and the best fit JAM model using an increasing }
+  \label{fig:JAM_modelG}
 \end{subfigure}%
@@
   \includegraphics[height=6cm]{fig/jam_G_enclMass.ps}
-  \caption{???}
+  \caption{??? [TO DO: Make figure wider. Include legend.???] [TO DO: Why does this plot look different than the others???]}
   \label{fig:???}
 \end{subfigure}
-\caption{???
+\caption{JAM model found by using an increasing mass-to-light ratio to generate a mass model from the light distribution in Table \ref{tab:MGEF814W}.
+[TO DO]???
 Using the surface brightness MGE for the dynamical modelling: each Gaussian got it's own M/L such that the overall M/L is increasing with radius.

### 2015-08-17 docs/results_JAMwithNFW_v1.01.tex
started writing section on NFW modelling.

@@
 
-\subsubsection{Sampling with a Markov Monte Carlo Chain}
+\paragraph{Including a NFW halo.} The dynamical modelling attempts in the previous sections suggest that J1331's inner regions have a slightly more roundish and at large radii more massive mass distribution than expected from the distribution of stars alone.
+A dark matter halo in addition to the stellar component could explain these findings.
+We therefore proceed by modelling the mass distribution with a) a stellar component, which we get from the light MGE in Table [TO DO: REF????] times a constant stellar mass-to-light ratio $\Upsilon_*$), and b) a spherical NFW dark matter component [TO DO: Navarro 1995 or 1996???], which is implemented in the JAM modelling as a fit of a 10-Gaussian MGE to the classical NFW profile
+\begin{equation*}
+\rho_\text{NFW}(r) \propto 1 / \frac{r}{R_\text{s,NFW}} \left( 1 + \frac{r}{R_\text{s,NFW}} \right)^2.
+\end{equation*}
+The NFW halo has two free parameters, the scale length $R_\text{s,NFW}$ and a parameter describing the total mass of the halo.
+We use $v_\text{200}$, which is the circular velocity at the radius $r_\text{200}$ within which the mean density of the halo is 200 times the cosmological [TO DO: how to express this] critical density, i.e.
+\begin{eqnarray*}
+M_\text{200} &=& M(<r_{200})\\
+\frac{M_{200}}{ \frac 43 \pi r_{200}^3} &=& 200 \rho_\text{crit}(z=0) \\
+v_\text{200} &=& \sqrt{\frac{GM_{200}}{r_\text{200}}}
+\end{eqnarray*}
+with $\rho_\text{crit}(z=0)=1.43 \cdot 10^{-7} M_\odot / \text{pc}^3$ in the WMAP5 cosmology by [TO DO: REF: Dunkley et al. 2009].
+
+\paragraph{Priors.} [TO DO: REF: Dutton et al. 2010] give a relation for halo vs. stellar mass for late-type galaxies. For an Chabrier IMF stellar population they found
+\begin{equation*}
+y = y_0 \left( \frac{x}{x_0} \right)^\alpha \left[ \frac 12 + \frac 12 \left(\frac{x}{x_0} \right)^\gamma \right]^{(\beta - \alpha)/\gamma},
+\end{equation*}
+where $x= m_*$ [$M_\odot h^{-2}$] is the stellar mass, $y = \frac{\langle M_{200}\rangle}{m_*}$ and $\langle M_{200}\rangle$ [$M_\odot h^{-2}$] is the mean halo mass.
+The parameters for the mean and $2\sigma$ error curves for this relation are$\alpha = -0.5\pm0.15$, $\beta = 0$, $\gamma = 1.0$, $\log_{10} x_0 = 10.4$, $\log_{10} {y_0}_{-0.24}^{+0.28}$ [TO DO: REF: Dutton et al.
+2010].
+Using the stellar mass estimate for J1331 from \citet{SWELLSI} $m_* = (1.06 \pm 0.25) \cdot 10^{11} M_\odot$ for the Chabrier IMF estimate [TO DO: introduce somewhere], we find ${v_{200}} = (202_{-33}^{+44})_{-13}^{+12}$.
+The first of the two quoted errors is due to the $2\sigma$ scatter in the relation by [TO DO: REF: Dutton et al.
+2010].
+The second error is the propagated error due to the uncertainty in the stellar mass.
+We use this rough estimate for J1331's [TO DO: Continue on page 98]
 

### 2015-08-17 docs/results_JAMwithSB_v1.01.tex
started writing section on NFW modelling.

@@
 We treat the five $\Upsilon_i$ as free parameters and only require that $\Upsilon_{j} \geq \Upsilon_i$ when the corresponding $\sigma_j \geq \sigma_i$ to ensure an overall mass-to-light ratio that is increasing with radius.
-[TO DO: Discuss Figure]
-
-[TO DO]
+\\Figure \ref{fig:enclMass_modelG} shows the (local projected) mass-to-light ratio gradient generated by the best fit to the dynamics data, which rises from $\Upsilon_\text{tot} = 2.53$ in the center and approaches a value of $\Upsilon_\text{tot}$ outside of the fitted region at $R'\gtrsim 3$ arcsec of $\Upsilon_\text{tot} = 7.60)$.
+The central mass-to-light ratio corresponds to the Chabrier IMF stellar mass-to-light ratio found by [TO DO: REF: TREU ET AL 2011] $\Upsilon_{i,*}^\text{Chab} = 2.5 \pm 0.6$ [TO DO: introduce and explain????].
+The strong rise  of$\Upsilon_\text{tot}(R')$ cannot be explained by an increase in the stellar $\Upsilon_*$ alone [TO DO: Really???
+Maybe it would have dropped again in the blue disk, if I had allowed for it????], so we deduce that we might need  contribution of dark matter halo in J1331.
+\\Fig.
+\ref{fig:JAM_modelG} shows that the best fit model greatly reproduces the central dip in the $v_\text{rms}$ curve, even though it has slight problems fitting the drop around $R' \sim 4$ arcsec.
+The latter might be because we only allowed the $\Upsilon_\text{tot}(R')$ to rise.
+A slight drop could be expected when the reddish bulge turns into the bluish disk and the contribution of the stellar component becomes less due to a lower $\Upsilon_{*}$ for younger and bluer populations.
+\\In Fig.
+\ref{fig:enclMass_modelG} we overplot the enclosed mass profile with the Einstein mass $M_\text{ein} = (7.77 \pm 0.33) \cdot 10^{10} M_\odot$ at the Einstein radius found from lensing in Table [TO DO: REF].
+The agreement between the Einstein mass and the independently found $M(<R_\text{ein}) = 7.49 \cdot 10^{10} M_\odot$ from dynamical modelling is striking.
 
@@
   \includegraphics[height=6cm]{fig/jam_G_vrms.ps}
-  \caption{Comparison between the stellar $v_\text{rms}$ data (blue points) and the best fit JAM model using an increasing }
+  \caption{Comparison of $v_\text{rms}$ data and best fit model.}
   \label{fig:JAM_modelG}
@@
   \includegraphics[height=6cm]{fig/jam_G_enclMass.ps}
-  \caption{??? [TO DO: Make figure wider. Include legend.???] [TO DO: Why does this plot look different than the others???]}
-  \label{fig:???}
+  \caption{Enclosed mass and mass-to-light ratio profile.
+[TO DO: Make figure wider.
+Include legend.???] [TO DO: weird  ticks on right axis???] [TO DO: Why does this plot look different than the others???]}
+  \label{fig:enclMass_modelG}
 \end{subfigure}
-\caption{JAM model found by using an increasing mass-to-light ratio to generate a mass model from the light distribution in Table \ref{tab:MGEF814W}.
-[TO DO]???
-Using the surface brightness MGE for the dynamical modelling: each Gaussian got it's own M/L such that the overall M/L is increasing with radius.
-This is the best fit model.
-The enclosed mass is overplotted with Einstein mass with 4\% error (overplotted, not fitted).
-???
-[TO DO: nice caption]}
-\label{fig:???}
+\caption{JAM model found by fitting an increasing total mass-to-light ratio $\Upsilon_\text{tot}$ profile used to generate a mass model from the light distribution.
+This is done by assigning a different mass-to-light ratio to each Gaussian in the MGE in Table \ref{tab:MGEF814W}.
+\emph{Panel (a):} Comparison between the stellar $v_\text{rms}$ data (blue points) and the best fit model (green line).
+\emph{Panel (b):} Enclosed mass inside the projected radius $R'$ on the sky (green line, left axis) and mass-to-light profile $\Upsilon(R')$ along the major axis [TO DO: CHECK???] (blue line, right axis) of the best fit model.
+The enclosed mass curve is overplotted with the independent finding for the Einstein mass $\pm 4 \%$ in Table [TO DO: TABLE REFERENCE???] (red dot) at the Einstein radius (red dotted line).
+The best fit mass-to-light ratios of the first four Gaussians are plotted against each Gaussians $\sigma$ (yellow stars).
+The two Gaussians with the largest $\sigma$ (the fifth is not shown) have the same best fit mass-to-light ratio.
+Overplotted is also the effective half-light ratio $R_\text{eff}$ (black dotted line).}
+\label{fig:modelG}
 \end{figure*}

### 2015-08-18 docs/results_JAMwithNFW_v1.01.tex
More on modelling with NFW.

@@
 \end{eqnarray*}
-with $\rho_\text{crit}(z=0)=1.43 \cdot 10^{-7} M_\odot / \text{pc}^3$ in the WMAP5 cosmology by [TO DO: REF: Dunkley et al. 2009].
+with $\rho_\text{crit}(z=0)=1.43 \cdot 10^{-7} M_\odot / \text{pc}^3$ in the WMAP5 cosmology by [TO DO: REF: Dunkley et al.
+2009].
+How much the mass is concentrated in the center of the NFW halo is given by the concentration of the NFW halo defined by $c_{200}\equiv r_{200} / R_{s,NFW}$.
+[TO DO: so toll ist das mit der Radiusbenennung noch nicht.????].
+There is a close relation between the concentration and halo mass in simulations [TO DO: REF: Navarro et al.
+1996].
+[TO DO: REF: Maccio et al 2008] found this relation for the WMAP5 cosmology [TO DO: REF: Dunkley 2009] to be
+\begin{equation}
+\langle \log c_{200} \rangle (M_{200}) = 0.830 - 0.098 \log \left(h \frac{M_{200}}{10^{12} M_\odot} \right) \label{eq:Maccio08}
+\end{equation}
+(their equation 10), with a Gaussian scatter of $\sigma_{\log c_{200}} = 0.105$ (their table A2).
 
-\paragraph{Priors.} [TO DO: REF: Dutton et al. 2010] give a relation for halo vs. stellar mass for late-type galaxies. For an Chabrier IMF stellar population they found
+\paragraph{Modelling and Priors.} The full set of fit parameters is $(\Upsilon_{I,*},R_\text{S,NFW},v_{200},\beta)$ [TO DO: $\beta$ or $\beta_0$???] [TO DO: Einheitlich $\Upsilon_{I,*}$????], where $\beta$ is the constant velocity anisotropy parameter (see [TO DO: REFERENCE TO SECTION???]).
+We will investigate this parameter space with a MCMC [TO DO: REFERENCE EMCEE???] and use priors for the halo parameters to guide the fit to a realistic NFW halo shape.
+\\{[TO DO: REF: Dutton et al. 2010]} give a relation for halo vs. stellar mass for late-type galaxies. For an Chabrier IMF stellar population they found
 \begin{equation*}
@@
 The second error is the propagated error due to the uncertainty in the stellar mass.
-We use this rough estimate for J1331's [TO DO: Continue on page 98]
+We use this as a rough estimate for the halo of J1331 and as Gaussian prior on $v_{200}$,
+\begin{equation*}
+p(v_{200}) = \mathscr{N}(200 \text{km/s} ,40 \text{km/s}).
+\end{equation*}
+\\We also use the concentration vs. halo mass relation by [TO DO: REF: Maccio 2008] in Eq. (\ref{eq:Maccio08}) as a prior on the concentration, i.e.
+\begin{equation*}
+p(\log c_{200} \mid v_{200}) = \mathscr{N}\left(\langle \log c_{200} \rangle (M_{200}) \mid 0.105 \right).
+\end{equation*}
+\\For the velocity anisotropy parameter $\beta$ we will again employ a uniform prior 
+\begin{equation*}
+p(\beta) = \mathscr{U}(-0.5,+0.5)
+\end{equation*}
+to exclude very unrealistic anisotropies. The full prior used is then
+\begin{equation*}
+p(\Upsilon_{I,*},R_\text{S,NFW},v_{200},\beta) = \frac{1}{\ln\left( 10 R_{s,NFW}\right)} p(\log c_{200} \mid v_{200}) \cdot p(v_{200}) \cdot p(\beta), 
+\end{equation*}
+where the factor $1/\ln\left( 10 R_{s,NFW}\right)$ is the Jacobian of the transformation from the halo parameters $(v_{200},\log c_{200})$ [TO DO: introduce concentration] to $(v_{200},R_{s,NFW})$.
 

### 2015-08-19 docs/results_JAMwithNFW_v1.01.tex
Even more stuff on modelling with NFW halo.

@@
 A dark matter halo in addition to the stellar component could explain these findings.
-We therefore proceed by modelling the mass distribution with a) a stellar component, which we get from the light MGE in Table [TO DO: REF????] times a constant stellar mass-to-light ratio $\Upsilon_*$), and b) a spherical NFW dark matter component [TO DO: Navarro 1995 or 1996???], which is implemented in the JAM modelling as a fit of a 10-Gaussian MGE to the classical NFW profile
+We therefore proceed by modelling the mass distribution with a) a stellar component, which we get from the light MGE in Table \ref{tab:MGEF814W} times a constant stellar mass-to-light ratio $\Upsilon_*$), and b) a spherical NFW dark matter component \citep{Navarro+1995c,NFW96}.
+In the JAM modelling we use a 10-Gaussian MGE fit to the classical NFW profile
 \begin{equation*}
@@
 \end{eqnarray*}
-with $\rho_\text{crit}(z=0)=1.43 \cdot 10^{-7} M_\odot / \text{pc}^3$ in the WMAP5 cosmology by [TO DO: REF: Dunkley et al.
-2009].
+with $\rho_\text{crit}(z=0)=1.43 \cdot 10^{-7} M_\odot / \text{pc}^3$ in the WMAP5 cosmology by \citet{WMAP5cosm}.
 How much the mass is concentrated in the center of the NFW halo is given by the concentration of the NFW halo defined by $c_{200}\equiv r_{200} / R_{s,NFW}$.
 [TO DO: so toll ist das mit der Radiusbenennung noch nicht.????].
-There is a close relation between the concentration and halo mass in simulations [TO DO: REF: Navarro et al.
-1996].
-[TO DO: REF: Maccio et al 2008] found this relation for the WMAP5 cosmology [TO DO: REF: Dunkley 2009] to be
+There is a close relation between the concentration and halo mass in simulations \citep{NFW96}.
+\citet{Maccio08} found this relation for the WMAP5 cosmology \citep{WMAP5cosm} to be
 \begin{equation}
@@
 
-\paragraph{Modelling and Priors.} The full set of fit parameters is $(\Upsilon_{I,*},R_\text{S,NFW},v_{200},\beta)$ [TO DO: $\beta$ or $\beta_0$???] [TO DO: Einheitlich $\Upsilon_{I,*}$????], where $\beta$ is the constant velocity anisotropy parameter (see [TO DO: REFERENCE TO SECTION???]).
-We will investigate this parameter space with a MCMC [TO DO: REFERENCE EMCEE???] and use priors for the halo parameters to guide the fit to a realistic NFW halo shape.
-\\{[TO DO: REF: Dutton et al. 2010]} give a relation for halo vs. stellar mass for late-type galaxies. For an Chabrier IMF stellar population they found
+\paragraph{Modelling.} The full set of fit parameters is $(\Upsilon_{I,*},R_\text{S,NFW},v_{200},\beta)$ [TO DO: $\beta$ or $\beta_0$???] [TO DO: Einheitlich $\Upsilon_{I,*}$????], where $\beta$ is the constant velocity anisotropy parameter (see \S\ref{sec:model_JAM}).
+We will investigate this parameter space with a MCMC \citep{emcee} and use priors for the halo parameters to guide the fit to a realistic NFW halo shape.
+\\\citet{Dutton10} give a relation for halo vs. stellar mass for late-type galaxies. For an Chabrier IMF stellar population they found
 \begin{equation*}
@@
 where $x= m_*$ [$M_\odot h^{-2}$] is the stellar mass, $y = \frac{\langle M_{200}\rangle}{m_*}$ and $\langle M_{200}\rangle$ [$M_\odot h^{-2}$] is the mean halo mass.
-The parameters for the mean and $2\sigma$ error curves for this relation are$\alpha = -0.5\pm0.15$, $\beta = 0$, $\gamma = 1.0$, $\log_{10} x_0 = 10.4$, $\log_{10} {y_0}_{-0.24}^{+0.28}$ [TO DO: REF: Dutton et al.
-2010].
+The parameters for the mean and $2\sigma$ error curves for this relation are$\alpha = -0.5\pm0.15$, $\beta = 0$, $\gamma = 1.0$, $\log_{10} x_0 = 10.4$, $\log_{10} {y_0}_{-0.24}^{+0.28}$ \citet{Dutton10}.
 Using the stellar mass estimate for J1331 from \citet{SWELLSI} $m_* = (1.06 \pm 0.25) \cdot 10^{11} M_\odot$ for the Chabrier IMF estimate [TO DO: introduce somewhere], we find ${v_{200}} = (202_{-33}^{+44})_{-13}^{+12}$.
-The first of the two quoted errors is due to the $2\sigma$ scatter in the relation by [TO DO: REF: Dutton et al.
-2010].
+The first of the two quoted errors is due to the $2\sigma$ scatter in the relation by \citet{Dutton10}.
 The second error is the propagated error due to the uncertainty in the stellar mass.
@@
 \end{equation*}
-\\We also use the concentration vs. halo mass relation by [TO DO: REF: Maccio 2008] in Eq. (\ref{eq:Maccio08}) as a prior on the concentration, i.e.
+\\We also use the concentration vs. halo mass relation by \citet{Maccio08} in Eq. (\ref{eq:Maccio08}) as a prior on the concentration, i.e.
 \begin{equation*}
@@
 where the factor $1/\ln\left( 10 R_{s,NFW}\right)$ is the Jacobian of the transformation from the halo parameters $(v_{200},\log c_{200})$ [TO DO: introduce concentration] to $(v_{200},R_{s,NFW})$.
+\\We restrict the $v_\text{rms}$ fit to a region $R' \lesssim 3.5$ arcsec, approximately within the effective half-light radius $R_\text{eff} = 2.6$ arcsec  [TO DO: make sure R' everywhere ???].
+We also include the Einstein mass $M(<R_\text{ein}$ with a 10\% error as an additional constraint in the fit.
 
-[TO DO]
+\paragraph{Result.} Figure \ref{fig:modelB4_triangle} shows the posterior probability distribution of the fit sampled with an MCMC.
+Overplotted are also the priors used to constrain the NFW halo.
+The best fit parameters are summarized in Table \ref{tab:modelB4_bestfit}.
+We find that the best fit NFW halo strives to be more massive and with a higher concentration than  proposed by the prior.
+At the same time the model prefers again very negative velocity anisotropies; the sample with the highest probability is pegged at the lower limit of the prior.
+Both, the concentrated halo and the low anisotropy are needed to reproduce the central dip of the $v_\text{rms}$ curve.
 
@@
 \includegraphics[width=0.9\linewidth]{fig/B4_contour_plot_short.ps}
-\caption{???
-Preliminary crappy caption: Result of the MCMC sampling of the parameter space for a model with NFW halo and constant velocity anisotropy.
-Green and blue shows the priors.
-Grey diamonds are the models shown in next figure.
-???
-[TO DO: nice caption]}
-\label{fig:???}
+\caption{Posterior probability distribution sampled with MCMC (red dots and histograms) for a JAM model with NFW halo, parametrized by $R_\text{s,NFW}$ and $v_\text{200}$, a stellar mass distribution generated from the I-band MGE in Table \ref{tab:MGEF814W} and a constant stellar mass-to-light ratio $\Upsilon_{I,*}$, and constant velocity anisotropy $\beta_z$.
+Shown are also the priors used for J1331's NFW halo, $\mathscr{N}(200 \text{km/s},40 \text{km/s})$ (green) and the concentration vs.
+halo mass relation by \citet{Maccio08} from Eq.
+(\ref{eq:Maccio08}) in terms of $v_{200}$ vs.
+$R_\text{s,NFW}$ with $1\sigma$ scatter (blue).
+The MCMC samples are color coded according to their probability (darker red for higher probability); the sample point with the highest probability is marked by a black diamond.
+The black cross is the mean of the distribution and the ellipses are derived from the covariance of matrix of the sample set and correspond approximately to $1\sigma$ (black solid ellipse) and $2\sigma$ (black dotted ellipse).
+The histograms of the marginalized 1D distributions are overplotted by the mean (black solid lines) and $1\sigma$ error (black dashed lines), whose values are also quoted in the figure and in Table \ref{tab:modelB4_bestfit}.
+The grey diamonds mark a random sub-selection of 12 samples; the corresponding models are shown in Figure \ref{fig:modelB4_models}.}
+\label{fig:modelB4_triangle}
 \end{figure*}
+
+\begin{table}
+\centering
+\begin{tabular}{llrcl}
+\hline
+stellar I-band mass-to-light ratio & $\Upsilon_{I,*}$ & 4.2 & $\pm$ & 0.2\\
+velocity anisotropy & $\beta_z$ & -0.4 & $\pm$ & 0.1 \\
+NFW halo scale length & $R_\text{s,NFW}$ [kpc] & 40 & $\pm$ & 20\\
+NFW halo virial velocity & $v_{200}$ [km/s] & 240 & $\pm$ & 40\\
+NFW halo concentration & $c_{200}$ & 8 & $\pm$ & 2 \\
+NFW halo mass & $M_{200}$ [$10^{12} M_\odot$] & 5 & $\pm$ & 2\\
+\hline
+\end{tabular}
+\caption{Summary of the best fit parameters of the JAM model with NFW halo from the MCMC exploration in Figure \ref{fig:modelB4_triangle}.
+The halo mass and concentration are calculated from the the best fit $R_\text{s,NFW}$ and $v_{200}$.}
+\label{tab:modelB4_bestfit}
+\end{table}
 
@@
   \includegraphics[width=0.8\linewidth]{fig/B4_rms_error_curves.ps}
-  \caption{???}
-  \label{fig:???}
+  \caption{Comparison of the $v_\text{rms}$ data with the best fit JAM models.}
+  \label{fig:modelB4_vrms}
 \end{subfigure}
-\begin{subfigure}{.5\textwidth}
+\begin{subfigure}{.48\textwidth}
   \centering
   \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_vcirc.ps}
-  \caption{????????}
-  \label{fig:???}
+  \caption{Circular velocity curve.}
+  \label{fig:modelB4_vcirc}
 \end{subfigure}%
-\begin{subfigure}{.5\textwidth}
+\hspace{.02\textwidth}
+\begin{subfigure}{.48\textwidth}
   \centering
   \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_projmass.ps}
-  \caption{???}
-  \label{fig:???}
+  \caption{Enclosed mass profile.}
+  \label{fig:modelB4_enclMass}
 \end{subfigure}
-\caption{???
-Preliminary crappy caption: 12 samples from the parameter pdf found with the MCMC above for the model with NFW halo and constant velocity anisotropy.
-Big red dot shows the Einstein mass with a 10\% error (used in fit).
-???
-[TO DO: nice caption]}
-\label{fig:???}
+\caption{Best fit JAM model including a NFW halo and velocity anisotropy with parameters given in Table \ref{tab:modelB4_bestfit}.
+The 12 lines shown correspond to the 12 models randomly drawn from the posterior probability distribution and marked as grey diamonds in Figure \ref{fig:modelB4_triangle}.
+Overplotted are the Einstein radius (red dotted line) and the effective half-light radius (black dotted line).
+The blue dashed line marks the radius within which the data and model were fitted.
+\emph{Panel a)} shows the comparison of the symmetrized $v_\text{rms}$ data (solid blue points) with the best fit JAM models including a NFW halo (red solid lines).
+Also shown is the non-symmetrized data at larger radii (open blue dots) and an extrapolation of the best fit models, using the same model parameters but the I-band surface brightness MGE for the outer regions of J1331 derived from the Ellipse model (red dashed lines).
+\emph{Panel b)} shows the circular velocity curve of the total mass (green), and separately the contribution of the stellar mass (yellow, again generated from the MGE in Table \ref{tab:F814WMGE}) and dark matter (grey).
+\emph{Panel c)} shows the corresponding enclosed mass profile.
+Overplotted is also the Einstein mass at the Einstein radius with a 10\% error, which was used in the fit as an additional constraint.[TO DO: radius benennungen sind irgendwie verrutscht]}
+\label{fig:modelB4_models}
 \end{figure*}

### 2015-08-20 docs/model_JAM_v1.01.tex
Started writing section on JAM modelling with surface brightness MGE. Updated plot on model G enclosed mass.
Wrote section on rotation curve recovery.

@@
-\subsection{Jeans Axisymmetric Modelling (JAM)}
+\subsection{Jeans Axisymmetric Modelling (JAM)} \label{sec:model_JAM}
 
@@
 where $n(\vect{x}) = \int f(\vect{x},\vect{v}) \diff3 v$ is the number density of tracers and $\Phi(\vect{x})$ the galaxy's gravitational potential, generated by the mass density $\rho(\vect{x})$ via Poisson's equation.
-\\The JAM modelling approach by \citet{Cap08} makes use of expressing the tracer density and the mass density as MGEs (see also [TO DO: REF: Emsellem et al.
-19994]).
+\\The JAM modelling approach by \citet{Cap08} makes use of expressing the tracer density and the mass density as MGEs (see also \citet{1994A&A...285..723E}).
 The density of stellar tracers is assumed to be proportional to the observed and deprojected brightness distribution $\nu(R,z)$ in Eq.
@@
 To mimick gradients of stellar mass-to-light ratio, each Gaussian could be assigned its own $\Upsilon_{*,i}$.
-To add a Navarro-Frenck-White (NFW) [TO DO: REF] dark matter halo component, a MGE generated from a fit to a NFW profile can be added to the stellar component.
+To add a Navarro-Frenck-White (NFW) \citep{Navarro+1995c,NFW96} dark matter halo component, a MGE generated from a fit to a NFW profile can be added to the stellar component.
 [TO DO: continue on p.
@@
 [TO DO] predicts the intrinsic $\langle v_\text{los}^2 \rangle$ at a given position on the sky, which have then to be modified to model the mode of observation, to be comparable to the measurements.
-The measured $v_\text{rms}$ is a light-weighted mean for a pixel along the long-slit of the spectrograph, with height $L_y = 1$ arcsec [TO DO: REF: Dutton 2013] and a certain given extent in along the major axis, $L_x$, i.e.
+The measured $v_\text{rms}$ is a light-weighted mean for a pixel along the long-slit of the spectrograph, with height $L_y = 1$ arcsec \citep{SWELLSV} and a certain given extent in along the major axis, $L_x$, i.e.
 for a rectangular aperture
@@
 \end{equation*}
-with FWHM=1.1 arcsec  [TO DO: REF: Dutton 2013]. The model predictions have therefore to be convolved with the convolution kernel
+with FWHM=1.1 arcsec  \citep{SWELLSV}. The model predictions have therefore to be convolved with the convolution kernel
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-If provided with with the convolution kernel, the JAM code by [TO DO: REF: Cappellari 2008] [TO DO: reference code] performs the convolution numerically.
-We set $L_x = 0.21$ arcsec as the width of the model pixel, and get a prediction for the actual measurements in bins of width 0.63, 1.26 and 1.89 arcsec [TO DO: REF: Dutton 2013] as light-weighted mean from each 3, 6 and 9 model pixels.
+If provided with with the convolution kernel, the JAM code by \citet{Cap08} [TO DO: reference code] performs the convolution numerically.
+We set $L_x = 0.21$ arcsec as the width of the model pixel, and get a prediction for the actual measurements in bins of width 0.63, 1.26 and 1.89 arcsec \citep{SWELLSV} as light-weighted mean from each 3, 6 and 9 model pixels.
+
+\paragraph{Rotation curve.} The intrinsic rotation curve is the first velocity moment $\langle v_\phi\rangle = \sqrt{\langle v_\phi^2 \rangle - \sigma_\phi^2}$.
+The observed rotation curve is the projection of the light-weighted contributions to $\langle v_\phi\rangle$ along the line-of-sight(\cite{Cap08}),
+\begin{equation*}
+I \langle v_\text{los}\rangle = \int_{-\infty}^{+\infty} \nu \langle v_\phi\rangle \cos \phi \sin i \diff z'.
+\end{equation*}
+The first velocity moments cannot be uniquely determined from the Jeans equations, which give only a prediction for the second velocity moments.
+Further assumptions are needed to separate the second velocity moments into ordered and random motion.
+\citet{Cap08} assumes that in a steady state there is no streaming velocity in $R$ direction, i.e.
+$\langle v_R \rangle = 0$ and therefore $\sigma_R^2 = \langle v_R^2 \rangle$.
+Then \citet{Cap08} relates the dispersions in $R$ and $\phi$ direction such that
+$$\langle v_\phi\rangle = \sqrt{\langle v_\phi^2 \rangle - \sigma_\phi^2} \equiv \kappa \sqrt{\langle v_\phi^2 \rangle - \langle v_R^2 \rangle},$$
+and the $\kappa$ parameter quantifies the rotation: $\kappa = 0$ means no rotation at all and $|\kappa| = 1$ describes a velocity dispersion ellipsoid that is a circle in the $R$-$\phi$ plane \citep{Cap08}.
+The sign of $\kappa$ determines the rotation direction.
+We can assign a constant $\kappa_k$ to every Gaussian in the MGE formalism and
+\begin{equation*}
+\nu \langle v_\phi\rangle = \left[\nu \sum_{k} \kappa_k^2 \left( [\nu\langle v_\phi^2 \rangle]_k - [\nu\langle v_R^2 \rangle]_k\right) \right]^{1/2}
+\end{equation*} 
+is then the light-weighted circular velocity curve, given the second velocity moments found from the Jeans equations.
+\\To model the counter-rotating core of J1331 with one free parameter for, we employ the condition that the overall $\kappa(R)$ profile should smoothly and relatively steeply transition from $\kappa(R) = -\kappa' < 0$ at small $R$ [TO DO: Check, ich glaube das hier ist das intrinsische R in Zylinder-Coordinaten] trough $\kappa(R_0) \equiv 0$ and increase to $\kappa(R) = \kappa' > 0$ at large $R$.
+Our imposed profile is
+\begin{equation}
+\kappa(R) = \kappa' \frac{R^2 - R_0^2}{R^2 + R_0^2}. \label{eq:kappa_profile}
+\end{equation}
+We find $\kappa'$ by matching the model $\langle v_\text{los} \rangle$ with the symmetrized $v_\text{rot}$ data, where for a given $\kappa'$ the $\kappa_k$ are found from fitting the MGE generated profile $\kappa(R) = \sum_k \kappa_k \nu_k(r)/\sum_k \nu_k(r)$ to Eq.
+(\ref{eq:kappa_profile}).
+The observed zero point is at $R'_0\approx 2$ arcsec.
+In the deprojected galactic plane the radius of zero rotation would be at a $R_0 \gtrsim 2$ arcsec, and we choose it to be at 2.2 arcsec.

### 2015-08-20 docs/results_JAMwithNFW_v1.01.tex
Wrote section on rotation curve recovery.

@@
 Both, the concentrated halo and the low anisotropy are needed to reproduce the central dip of the $v_\text{rms}$ curve.
+[TO DO: Rewrite.
+Not very good.]
+The first panel in Figure \ref{fig:modelB4_vrot} shows the mean best fit values from Table \ref{tab:modelB4_bestfit}.
 
@@
 
-\subsubsection{Predicting the Rotation Curve at larger Radii}
-
-[TO DO]
+\paragraph{Rotation curve.} Following the procedure in \S\ref{sec:model_JAM} we find the rotation curve from the best fit mean model in Table \ref{tab:modelB4_bestfit} by fitting the rotation parameter $\kappa'$ to the symmetrized $v_\text{rot}$ data within $R' = 3.5$ arcsec.
+The best fit with $\kappa' = 0.76$ is shown in the second panel of Figure \ref{fig:modelB4_vrot}.
+The third panel gives the dispersion that was calculated simply by $\sigma = \sqrt{v_\text{rms}^2 - v_\text{rot}^2}$.
+Our assumptions for $\kappa(R)$ nicely reproduce a $v_\text{rot}$ model with counter-rotating core.
+Although we fitted $v_\text{rot}$ only to the inner regions, the extrapolation to large radii fits the data also very well.
+While the dispersion $\sigma$ in the center fits by construction quite good, there is a huge discrepancy at large radii.
+The predicted dispersion is much larger than the data; we would expect the disk rotationally supported and therefore have a low velocity dispersion; especially dispersions as high as $\sim 200 km/s$ are more likely to be observed in the pressure supported bulges of galaxies.
+There \emph{might} be something unexpeted with the $\sigma$ measurements around $\sim 5$ arcsec, but at large radii the the best fit model NFW halo is simply too massive.
 
@@
 \includegraphics[width=0.7\linewidth]{fig/B4_rms_rot_curves_best_model.ps}
-\caption{???
-Preliminary crappy caption: Model: NFW halo and constant velocity anisotropy, using the the mean / peak values of the MCMC result in the above pdf for the model parameters.
-Fitting one more free parameter to the rotation curve in the inner regions, predicting the rotation curve and dispersion at larger radii.
-Green dots are gas kinematics.
-???
-[TO DO: nice caption]}
-\label{fig:???}
+\caption{Generating the rotation curve from the JAM model with NFW halo and constant velocity anisotropy with the mean parameters in Table \ref{tab:modelB4_bestfit} and with the best fit rotation parameter $\kappa' = 0.76$ in Eq.
+(\ref{eq:kappa_profile}) (red solid lines).
+The second velocity moment in the first panel and the first velocity moment in the second panel with the additional fit parameter $\kappa'$ were fitted to the symmetrized data (solid blue points).
+The velocity dispersion is simply $\sigma = \sqrt{v_\text{rms}^2 - v_\text{rot}^2}$.
+At larger radii we compare the unsymmetrized data (open blue dots), the gas kinematics from \citet{SWELLSV} (green diamonds) and a JAM model using the same model parameters but the light distribution MGE generated from the Ellipse model in Figure [TO DO: REF FIGURE] as a prediction for the outer regions of J1331 (red dashed lines).
+The central regions are very well reproduced and we can also greatly predict the rotation curve at larger radii.
+Only at larger radii the $v_\text{rms}$ and $v_\text{rot}$ overestimate the measurements, probably due to a too massive NFW halo.}
+\label{fig:modelB4_vrot}
 \end{figure*}

### 2015-08-25 docs/introduction_v1.01.tex
Started writing data section.
Added short section on cored logarithmic halo.

@@
 \item [TO DO]
+\item \citet{SWELLSI} give measurements for the apparent AB magnitudes for the HST/WFPC2 I-band/F814W filter for disk and bulge, as well as stellar masses for stellar population models for a Chabrier [TO DO: REF] and Salpeter [TO DO: REF] initial mass function (IMF).
 \end{itemize}
@@
 The color scaling of these two images is the same.
-The black solid line in panel (a) shows the orientation of the major-axis.
+The black solid line in panel (b) shows the orientation of the major-axis.
 The line has a length of 10 arcsec and indicates the region within which we carry out the Jeans modelling.

### 2015-08-25 docs/results_JAMwithNFW_v1.01.tex
Added short section on cored logarithmic halo.

@@
 Not very good.]
+
 The first panel in Figure \ref{fig:modelB4_vrot} shows the mean best fit values from Table \ref{tab:modelB4_bestfit}.
+
+We also fitted a model with a cored logarithmic dark matter halo.
+The cored halo models are in general slightly less massive than the NFW halo and therefore fitt the outer regions of J1331 better.
+However, the density profile of the cored halo as well as the I-band light distribution within the plane drop as $\rho(r) \propto r^{-2}$, there is a strong degeneracy between the stellar mass and the dark matter.
+Overall we were not able to give tight constraints on the cored logarithmic halo.
 

### 2015-09-01 docs/data_v1.01.tex
Revistied most of the lensing section.

@@
 \end{itemize}
+
+\paragraph{HST imaging.} [TO DO] Follow up high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) was performed \citep{SWELLSI}).
+The WF3 CCD chip pf WFPC2.
+The images we are using are a combination of four exposures with each an exposure of 400s and were drizzled to a pixel scale of 1 pixel = 0.05 arcsec.
+Filters F450W and F814W.
+Redshifts Lens image redshift $z_s = 0.254$  \citep{SWELLSIII} This galaxy is at a redshift of $z_d = 0.113$ (\cite{SWELLSIII}).
+Angular diameter distance according to [TO DO: REF: Dunkley] is 414 Mpc, which translates into a scaling of 1 arcsec $\hat{=}$ 2.01 kpc for J1331.
 

### 2015-09-01 docs/discussion_ML_v1.01.tex
Revistied most of the lensing section.

\subsection{Stellar mass-to-light ratios}

[TO DO] [TO DO: Also compare with results from Treu et al.]

\paragraph{Collection of thoughts}
\begin{itemize}
\item [TO DO: Start on page 62]
\end{itemize}

\begin{table}
\centering
\begin{tabular}{cccccc}
\hline\hline
& & \multicolumn{2}{c}{Chabrier IMF} & \multicolumn{2}{c}{Salpeter IMF}\\
      &  $L$ [$10^{10}L_{\odot}$]                & $M_*$ [$10^{10}M_\odot$]               & $\Upsilon_*^\text{chab}$ & $M_*$ [$10^{10}M_\odot$] & $\Upsilon_*^\text{sal}$ \\\hline
bulge &   $3.10 \pm 0.15 $  & $7.8 \pm 1.8$ & $2.5 \pm 0.6$ & $14.5 \pm 3.7 $ & $4.7 \pm 1.2$ \\
disk  &   $2.35 \pm 0.11 $  & $2.9 \pm 0.7$ & $1.2 \pm 0.3$ & $5.2 \pm 1.1$ & $2.2 \pm 0.5$ \\
total &   $5.45 \pm 0.19$ & $10.6 \pm 1.9$& & $19.7 \pm 3.9$&\\\hline
\end{tabular}
\caption{Total I-band luminosity, stellar mass and mass-to-light ratio, calculated from the I-band AB magnitudes and stellar masses found for J133's bulge and disk by \citet{SWELLS} (their table 2) for comparison with this work. The transformation from AB magnitudes to the Johnson-Cousins I-Band used the relation $I[\text{mag}] = I[\text{ABmag}] - 0.309$ from [TO DO: REF: Frei and Gunn 1994] (their table 2). For the conversion from apparent magnitude to total luminosity the redshift $z=0.113$ [TO DO: REF: Brewer] was turned into a luminosity distance using the cosmology by [TO DO: REF: Dunkley]. }
\label{tab:previousresults}
\end{table}

### 2015-09-01 docs/introduction_v1.01.tex
Revistied most of the lensing section.

@@
 \item [TO DO]
+\item Sloan WFC Edge-on Late-type Lens Survey (SWELLS) WFC = Wide field camera \citep{SWELLSI,SWELLSII,SWELLSIII,SWELLSIV,SWELLSV,SWELLSVI}
 \item \citet{SWELLSI} give measurements for the apparent AB magnitudes for the HST/WFPC2 I-band/F814W filter for disk and bulge, as well as stellar masses for stellar population models for a Chabrier [TO DO: REF] and Salpeter [TO DO: REF] initial mass function (IMF).
+\item dedicated to find spiral galaxy strong lenses, to combine lensing and dznamical modelling to break degeneracies inherent in both methods.
+\item picked galaxies in SDSS whose spectra had to different redshifts within 3 arcsec, which makes it likely to capture strong lenses with typical Einstein radii of 1 arcsec.
+Sufficiently inclined galaxies were picked by eye.
+Follow up high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) was performed \citep{SWELLSI}).
 \end{itemize}
@@
 \item SDSS J1331+3638 (J1331)
-\item approximate hubble type Sb
+\item approximate hubble type Sb, Spiral galaxy almost edge-on
 \item first discovered by Sloan digital sky survey (SDSS) [TO DO: REF]
-\item at redshift $z_d\simeq0.113$ [TO DO: REF]
 \item \citet{SWELLSI} identified it as a strong lens
+\item Its coordinates on the sky are right ascension = 202.91800$^\circ$ and a declination = 36.46999$^\circ$ (epoch J2000). 
+\item This galaxy is at a redshift of $z_d = 0.113$ (\cite{SWELLSIII}).
 \item large reddish bulge and bluish spiral arms, see Fig. \ref{fig:F450W} and \ref{fig:F814W}
-\item superimposed by quadruplet of extended bluish images at a redshift of $z_s\simeq0.254$ [TO DO: REF], see Fig. \ref{fig:lens_just_imgpos}
+\item superimposed by quadruplet of extended bluish images at a redshift of $z_s\simeq0.254$ [TO DO: REF], see Fig.
+\ref{fig:lens_just_imgpos}, approximately at a distance of 1 arcsec from the galaxy center (which is a typical Einstein radius).
+\item Lens image redshift $z_s = 0.254$  \citep{SWELLSIII}
 \item lensed object might be a star-forming blob of a background galaxy.
@@
 \item possible minor merger in the past
+\item background object: possibly bright star forming region in the spiral arms of background galaxy 
 \end{itemize}

### 2015-09-01 docs/model_lensing_v1.02.tex
Revistied most of the lensing section.

--- 2015-08-11 docs/model_lensing_v1.01.tex
@@
-\subsection{Strong Gravitational Lensing Formalism and Lens Model}
+\subsection{Strong Gravitational Lensing Formalism and Lens Model} \label{sec:lensing_theo}
 
@@
 \end{equation}
-where $\vec{\theta}$ is a 2-dimensional vector on the plane of the sky. The light from the source at $\vec{\beta} = (\xi,\eta)$ is deflected according to the lens equation
+where $\vec{\theta}$ is a 2-dimensional vector on the plane of the sky.
+The light from the source at $\vec{\beta} = (\xi,\eta)$\footnote{$\xi$ and $\eta$ are cartesian coordinates on the plane of the sky.} is deflected according to the lens equation
 \begin{equation}
@@
 \paragraph{Lens Model.} Following \citet{EvansWitt} we assume a scale-free model
-\begin{equation*}
+\begin{equation}
 \psi(R',\theta) = R^{'\alpha} F(\theta) \label{eq:scalefreemodel}
-\end{equation*}
+\end{equation}
 for the lensing potential, consisting of an angular part $F(\theta)$ and a power-law radial part, with $(R',\theta)$ being polar coordinates on the plane of the sky.
@@
 (\ref{eq:lenseqpot}) and (\ref{eq:Fourierlenseq})) for $\theta_{pi}$, we follow \citet{1991ApJ...373..354K} and cast the calculation back to the source plane using the magnification tensor in eq.
-(\ref{eq:magnificationtensor}):
+(\ref{eq:magnificationtensor}) to approximate $\vect{\theta} \simeq (\partial \vect{\theta} / \partial \vect{\beta}) \vect{\beta} = \mathscr{M} \vect{\beta} $ and the $\chi^2_\text{lens}$ that the fit wants to minimize becomes
 \begin{eqnarray*}
@@
 where $(\Delta_x,\Delta_y)$ are the measurement errors of the image positions $\vec{\theta}_{oi}$.
-$\left.\mathscr{M}\right|_{\vec{\theta}=\vec{\theta}_{oi}}$ is the magnification tensor and $(\tilde{\xi}_i,\tilde{\eta}_i)$ the source position according to the lens equation evaluated at $\vec{\theta}_{oi}$.
+$\left.\mathscr{M}\right|_{\vec{\theta}=\vec{\theta}_{oi}}$ is the magnification tensor and $(\tilde{\xi}_i,\tilde{\eta}_i)$ the source position according to the lens equation, both evaluated at $\vec{\theta}_{oi}$.
 Following \citet{GlennEC} we add a term
@@
 \\To be able to constrain the slope $\alpha$, we would have needed flux ratios for the images as in \citet{GlennEC}.
-But the extended quality of the images and the uncertainty in surface brightness subtraction makes flux determination too unreliable and we do not include them in the fitting.
-Even though the constraint from just the image position fit on $\alpha$ is very weak, we were however able to show that the image positions in tab.
-\ref{tab:lenspos} minimize $\chi^2$ at $\alpha=1$ and also our other image position sets from different models and filters are consistent with a flat rotation curve.
-In the following we therefore set $\alpha=1$.
+But the extended quality of the images, possible dust obscuration and surface brightness fluctuations due to microlensing events, as well as the uncertainty in surface brightness subtraction make flux determination too unreliable and we do not include them in the fitting.
+
+[TO DO: eq. to Equation, fig. to Figure, \S to Section, vec to vect, cf to see, tab. to Table]

### 2015-09-01 docs/results_lensing_v1.02.tex
Revistied most of the lensing section.

--- 2015-08-10 docs/results_lensing_v1.01.tex
@@
-\subsection{Mass distribution from Lensing}
+\subsection{Mass distribution from Lensing} \label{sec:results_lensing}
 
 \paragraph{Image Positions.} We determine the positions of the lensing images by first subtracting a smooth model for the galaxy's surface brightness from the original image.
-As models we use MGE fits (cf.
-\S\ref{kap:MGE}) and IRAF ellipse fits (???) to the galaxy in each the F450W and F814W filter.
+As models we use MGE fits and IRAF ellipse fits  (see Sections \ref{sec:MGE_theo} and \ref{sec:MGE_results})  to the galaxy in each the F450W and F814W filter.
 (For example the MGE we use for F814W is the MGE given in tab.
@@
 \ref{tab:PSFMGEF814W}.) The lensing images become then visible in the residuals (see fig.
-\ref{fig:lens_just_imgpos}).
+\ref{fig:lens_just_imgpos}), in which we smooth out noise smaller than the PSF.
 Because the lensing images are extended, we use the position of the brightest pixel in each of the images.
-We also use the F814W-MGE subtracted residuals from \citet{SWELLSIII}.
+We also use the F450W-MGE subtracted residuals from \citet{SWELLSIII}.
 The lensing positions as determined from the latter are given in tab.
@@
 The scatter of lensing positions as determined from subtracting different surface brightness models from the galaxy in different filters gives an error of $\pm 1$ pixel on the image positions.
+We find slightly different positions for the peak of the surface brightness in the different filters and apply correspondingly an error of one diagonal pixel to the brightness peak in the F450W image which we use as center of the galaxy.
+\\Eight image position coordinates allow us to fit a lens mass model with only $<8$ free parameters. We therefore do not fit Fourier components $(a_k,b_k)$ with $k > 3$.
+\\Even though the constraints from the image positions on $\alpha$ is very weak, we were however able to show that the image positions in tab.
+\ref{tab:lenspos} are consistent with a model with flat rotation curve.
+In the following we therefore set $\alpha=1$.
 
@@
 \ref{fig:lensbestfiteinsteincurves} shows the corresponding critical curve, caustic and Einstein radius, and the best fit source position.
-In this case, where $\alpha=1$, the critical curve is also an equidensity contour of the galaxy model.
+In this case, where $\alpha=1$, the critical curve is also an equidensity contour of the galaxy model \citep{EvansWitt}, which appears to have an elliptical mass distribution.
+This cricital curve is called \emph{tangential}, because of the tangential orientation of the images close to it.
+The source is located close to a cusp of the diamond-shaped caustic: a lensing configuration for which we indeed expect four images.
+This is a good indication that indeed all four images are indeed lensing images of the same object.
 Fig.
-\ref{fig:lensbestfittimedelay} overplots the smoothed residuals from the F814W image subtracted by the IRAF ellipse fit to the surface brightness with the contours of the best fit model's time delay surface.
+\ref{fig:lensbestfittimedelay} overplots the smoothed residuals from the F450W image subtracted by the IRAF ellipse fit to the surface brightness with the contours of the best fit model's time delay surface.
 This demonstrates that, although we did not include any information about the shape of the lensing images in the fit, it is consistent with the predicted distortion for an extended source by the best fit lens model.
 \\To estimate how the uncertainties in the determination of the image positions and galaxy center affect the results, we Monte Carlo sample random positions from a two-dimensional Normal distribution centered at the positions in tab.
-\ref{tab:lenspos} and a standard deviation corresponding to the measurement error of 1 pixel.
+\ref{tab:lenspos} and a standard deviation corresponding to the measurement error.
 A Gaussian fit to the resulting distributions of best fit values leads to the constraints on the shape parameters and Einstein quantities in the second column in tab.
@@
 We therefore constrain the Einstein radius to within 2\%, $R_\text{ein} = (0.91 \pm 0.02)$ arcsec and the projected mass within the critical curve with a relative error of 4\%, $M_\text{crit} =(7.9\pm0.3)\cdot 10^{10} M_\odot$.
-Our measurement of $R_\text{ein}$ is consistent with that from \citet{SWELLSIII}, $R_\text{ein,SWELLS} = (0.96 \pm 0.04)$ arcsec.
+Our measurement of $R_\text{ein}$ is consistent with that from \citet{SWELLSIII}, $R_\text{ein,SWELLS} = (0.96 \pm 0.04)$ arcsec (which used a singular isothermal ellipsoid as lens mass model and the intermediate-axis convention of the critical curve as the Einstein radius).
 The relative difference between our critical mass and that of \citet{SWELLSIII}, $M_\text{crit,SWELLS} =(8.86\pm0.61)\cdot 10^{10} M_\odot$, is 13\%.
@@
   \includegraphics[width=.9\linewidth]{fig/lens_einstein.ps}
-  \caption{??? Critical curves, Einstein radius, caustics, source position for best fit model. ??? [TO DO: nice caption]}
+  \caption{Best fit critical curve, Einstein radius, caustic, source position.}
   \label{fig:lensbestfiteinsteincurves}
@@
   \includegraphics[width=.9\linewidth]{fig/lens_timedelay.ps}
-  \caption{??? Time delay surface ??? [TO DO: nice caption]}
+  \caption{Time delay surface.}
   \label{fig:lensbestfittimedelay}
 \end{subfigure}
-\caption{???}
+\caption{Best fit lens model in Table \ref{tab:bestfitlensmodel} found from the image positions.
+In the background we show the central region of J1331 in the F450W filter, subtracted by an Iraf Ellipse model of the F450W surface brightness and smoothed by boxcar smoothing of the order of the PSF size.
+The four bluish lensing images are clearly visible and we mark the brightness peaks in Table \ref{tab:lenspos} as well as the galaxy center (G) as red dots.
+The Einstein radius of the best fit lens model is shown as a red dotted circle.
+\emph{Panel (a)} Besides the image positions and Einstein radius, the critical curve (red solid line) is shown in the lens plane.
+The caustic (green solid line) corresponding to the critical curve and best fit source position (green dot), which are both located in the source plane, are shown as well.
+For $\alpha=1$ (which we assumed for our lens model) the critical curve is a contour of constant surface density of the mass model.
+\emph{Panel (b)} The yellow lines show (arbitrary) contours of the time delay surface given by Equation \ref{eq:timedelay} of the best fit lens model.
+Not only the position of the extrema, but also their shape is consistent with the observed, extended images, even though we did not use information about the image shape in the analysis.
+The other two right blobs (north east of A, south east of B) might be star forming regions of the background galaxy as well.
+[TO DO: Add A, B, C, D in the figure to make clear which image is which.]}
 \label{fig:???}

### 2015-09-02 docs/discussion_ML_v1.01.tex
Started writing the discussion section on stellar mass-to-light ratios.

@@
+We've presented different dynamical models of the central region of J1331, some of them capturing the observed kinematics well, but none of them work both at small and large radii.
+In the following we will discuss possible reasons for these deviations by also comparing our results to previous work.
+
 \subsection{Stellar mass-to-light ratios}
+
+Further knowledge of the stellar populations within J1331 and their initial mass functions (IMF) would be useful.
+In particular a sophisticated guess for the \emph{stellar} mass-to-light ratio in J1331's bulge could be compared to our very reliable measurement of the \emph{total} mass-to-light ratio inside the Einstein radius (see Table [TO DO: REF]) to support or contradict the presence of a lot of dark matter in the bulge.
+Traditional choices for the IMF are the bottom-heavy IMF by \citet{Salpeter1955}
+$$\xi(m) \propto m^{-x}, x=2.35$$
+and the IMFs by \citet{2002Sci...295...82K} and \citet{Chabrier2003}, which are in agreement with each other and predict less low-mass stars.
+\\\citet{Ferreras} found a relation between the central stellar velocity dispersion $\sigma_0$ in early-type galaxies and the IMF slope.
+A higher $\sigma_0$ suggests a more bottom-heavy IMF.
+For an unimodal (Salpeter-like) IMF and a $\sigma_0 \propto 200 $ km/s for J1331 (see Figure \ref{fig:kinematics}) they predict $x \approx 2.33$ (see Figure 4 in \citet{Ferreras}), which is close to the standard Salpeter slope.
+These findings are supported by \citet{2014MNRAS.438.1483S}, who found for SDSS galaxies also a relation between unimodal (single power-law) IMF slope and stellar velocity dispersion.
+Their Table 2 lists $x(\sigma_*=190 \pm 20 \text{ km s}^{-1}) = 2.08 \pm 2.08$ and $x(\sigma_*= 230 \pm 20 \text{ km s}^{-1}) = 2.33 \pm 0.4$.
+When assuming a bi-modal (Kroupa-equivalent-like) IMF, \citet{Ferreras} predict $x \approx 2.85$ (see Figure 4 in \citet{Ferreras}) for J1331's central velocity dispersion.
+This is more bottom-heavy than the standard \citet{2002Sci...295...82K} IMF.
+Overall the central velocity dispersion suggests a rather bottom-heavy IMF J1331's bulge and therefore large stellar mass-to-light ratio.
+\\ \citet{SWELLSI} estimated J1331's stellar bulge mass given a Salpeter IMF and measured the I-band AB magnitude of the bulge.
+Transformed to a stellar I-band mass-to-light ratio (see Table \ref{tab:previousresults}) this would correspond to $\Upsilon_\text{I,*}^\text{Salpeter} = 4.7 \pm 1.2$.
+\\We compare our findings of the stellar mass-to-light ratios with the study by \cite{SWELLSV}: \cite{SWELLSV} found that the bulge of J1331 has an IMF more bottom-heavy than the Salpeter IMF from fitting a NFW halo to (1) the Einstein mass and (2) gas kinematics at larger radii $\gtrsim 8$ arcsec.
+We fitted the stellar kinematics within $\sim 3.5$ arcsec and the Einstein mass with a NFW halo and found $\Upsilon^\text{dyn}_{*,I} = 4.2 \pm 0.2$ (see Table [TO DO ???]).
+\cite{SWELLSV}  found systematically lower NFW halos ($v_\text{circ}(5\text{arcsec}) \sim 120 \text{km s}^{-1}$ according to their Figure 2) than we did ($v_\text{circ}(5\text{arcsec}) \sim 200 \text{km s}^{-1}$, see Figure [TO DO ???]).
+[TO DO: Continue writing notes into text]
+\begin{itemize}
+\item We found an Einstein mass-to-light ratio of $\Upsilon_\text{I,tot,Ein} = 5.6$ (see Table [TO DO ???]).
+In case of a lower mass NFW halo, the largest contribution to this mass-to-light ratio would then be stellar mass.
+And the corresponding IMF would be more bottom heavy than Salpeter as well, like what \citet{SWELLSV} found.
+\item The light distribution multiplied with $\Upsilon_\text{I,tot,Ein}$ looks very similar to \cite{SWELLSV} [TO DO: Look details up in their paper and my work
+\item In the JAM model based on the surface brightness alone with the increasing mass-to-light ratio, we found a total mass-to-light ratio in the center of J1331 of  $\Upsilon_\text{I,tot}(R\sim0) = 2.53$.
+This is very close to the stellar mass-to-light ratio we got from \citet{SWELLSI} estimates of the bulge's stellar mass using the \citet{Chabrier2003} IMF $\Upsilon_\text{I,*}^\text{Chabrier} = 2.5 \pm 0.6$, i.e.
+less bottom-heavy (more blue) population.
+\item The central dip of the stellar kinematics cannot be explained alone by a strong contribution of dark matter, because the best fit NFW halos are too massive to explain the kinematics at larger radii.
+\item The central dip can also not be explained alone by tangential [TO DO: check???] velocity anisotropy in the center and a lower contribution by dark matter.
+\item The above discussion motivates the following speculation: In the absence of a strong dark matter contribution in the center, the overall stellar-mass-to-light ratio within the Einstein radius indicates a bottom-heavy Salpeter-like IMF, consistent with estimates from the velocity dispersion.
+At the same time the central dip can then be only explained, if there was an increase in stellar mass-to-light ratio with radius \textit{within} the bulge.
+\emph{If} there was a stellar population in the very center with an IMF close to the \citet{Chabrier2003} IMF, surrounded by a more bottom-heavy population, the central stellar kinematics would be well explained and be fully consistent with the lensing results, as found in Figure \ref{fig:modelG} and the surrounding text.
+It is not expected that the bluish disk of J1331 has a $\Upsilon_{*,I}$ as high as the reddish bulge.
+The kinematics at larger radii would then be much better recovered by lower mass dark matter halo as found by \citet{SWELLSV}.
+\item Standard JAM modelling approaches seem not to work for J1331.
+A JAM model for J1331 would need to allow for stellar mass-to-light ratio gradients within the galaxy, velocity anisotropy and a dark matter halo.
+Because of degeneracies between stellar and dark mass, and matter distribution and anisotropy profile, such a dynamical model would not lead to very tight constraints on the model parameters.
+Further priors are needed.
+\item Detailed stellar population analyses of the spectra taken along J1331's major axis could possibly support or contradict the suspicion of the existence of stellar mass-to-light ratio gradients in J1331.
+\end{itemize}
+
+[TO DO: Rewrite the paper such, that it's main message is, that there is a strong indication of increasing stellar mass-to-light ratio in the center of the galaxy, i.e.
+a bluish core, because neither velocity anisotropy, neither a strong dark matter contribution alone can explain all dynamical signatures.
+"Evidence from Lensing and Dynamics for a bluish core in the center of J1331" as a possible alternative title???
+Eher nicht...]
 

### 2015-09-02 docs/results_JAMwithSB_v1.01.tex
Started writing the discussion section on stellar mass-to-light ratios.

@@
 [TO DO: Make figure wider.
-Include legend.???] [TO DO: weird  ticks on right axis???] [TO DO: Why does this plot look different than the others???]}
+Include legend.???] [TO DO: weird  ticks on right axis???] [TO DO: Why does this plot look different than the others???] [TO DO: Switch the two y-axes.
+It's better to have ML on the left side, to read up the central ML.]}
   \label{fig:enclMass_modelG}

### 2015-09-02 docs/results_lensing_v1.02.tex
Started writing the discussion section on stellar mass-to-light ratios.

@@
  &  & \multicolumn{1}{c}{peak image positions}  & \multicolumn{4}{c}{of image positions }  \\ \hline
-Einstein Radius      & $R_\text{ein}$ [arcsec]             & $0.907$ & $0.91$  & $\pm$ & $     0.02$ & ($2\%$)\\
-Einstein Mass        & $M_\text{ein}$ [$10^{10} M_\odot$]  & $7.72$  & $7.8 $  & $\pm$ & $      0.3$ & ($4\%$) \\
-Critical Mass        & $M_\text{crit}$ [$10^{10} M_\odot$] & $7.87$  & $7.9$   & $\pm$ & $      0.3$ & ($4\%$)\\
-Source Position      & $\xi$ [arcsec]                      & $0.095$ & $0.09 $ & $\pm$ & $     0.03$ & ($28\%$)\\
+Einstein radius      & $R_\text{ein}$ [arcsec]             & $0.907$ & $0.91$  & $\pm$ & $     0.02$ & ($2\%$)\\
+Einstein mass        & $M_\text{ein}$ [$10^{10} M_\odot$]  & $7.72$  & $7.8 $  & $\pm$ & $      0.3$ & ($4\%$) \\
+Total mass-to-light ratio & $\Upsilon_\text{I,tot,Ein}$ & & $\sim 5.6$ & & \\
+Critical mass        & $M_\text{crit}$ [$10^{10} M_\odot$] & $7.87$  & $7.9$   & $\pm$ & $      0.3$ & ($4\%$)\\
+Source position      & $\xi$ [arcsec]                      & $0.095$ & $0.09 $ & $\pm$ & $     0.03$ & ($28\%$)\\
                      & $\eta$ [arcsec]                     & $0.107$ & $0.10 $ & $\pm$ & $     0.03$ & ($27\%$)\\
-Fourier Coefficients & $a_0$                               & $1.814$ & $1.82 $ & $\pm$ & $   0.04$ & (2\%)\\
+Fourier coefficients & $a_0$                               & $1.814$ & $1.82 $ & $\pm$ & $   0.04$ & (2\%)\\
                      & $a_2$                               & $0.012$ & $ 0.011 $ & $\pm$ & $    0.004$ & (35\%)\\
@@
 \end{figure*}
+
+[TO DO: Include in discussion the Einstein-Mass-to-light ratio and reference to table. Needed for later.]

### 2015-09-03 docs/discussion_ML_v1.01.tex
Finished section on JAM theory.

@@
 Further knowledge of the stellar populations within J1331 and their initial mass functions (IMF) would be useful.
-In particular a sophisticated guess for the \emph{stellar} mass-to-light ratio in J1331's bulge could be compared to our very reliable measurement of the \emph{total} mass-to-light ratio inside the Einstein radius (see Table [TO DO: REF]) to support or contradict the presence of a lot of dark matter in the bulge.
-Traditional choices for the IMF are the bottom-heavy IMF by \citet{Salpeter1955}
-$$\xi(m) \propto m^{-x}, x=2.35$$
-and the IMFs by \citet{2002Sci...295...82K} and \citet{Chabrier2003}, which are in agreement with each other and predict less low-mass stars.
+In particular a sophisticated guess for the \emph{stellar} mass-to-light ratio in J1331's bulge could be compared to our very reliable measurement of the \emph{total} mass-to-light ratio inside the Einstein radius (see Table \ref{tab:bestfitlensmodel}) to support or contradict the presence of a lot of dark matter in the bulge.
+Traditional choices for the IMF are the bottom-heavy IMF by \citet{Salpeter1955},
+$$\xi(m) \propto m^{-x}, x=2.35,$$
+(where $\xi(m) \diff m$ is the number of stars with mass $m$ in $[m,m+\diff m]$) and the IMFs by \citet{2002Sci...295...82K} and \citet{Chabrier2003}, which are in agreement with each other and predict less low-mass stars.
 \\\citet{Ferreras} found a relation between the central stellar velocity dispersion $\sigma_0$ in early-type galaxies and the IMF slope.
@@
 \\We compare our findings of the stellar mass-to-light ratios with the study by \cite{SWELLSV}: \cite{SWELLSV} found that the bulge of J1331 has an IMF more bottom-heavy than the Salpeter IMF from fitting a NFW halo to (1) the Einstein mass and (2) gas kinematics at larger radii $\gtrsim 8$ arcsec.
-We fitted the stellar kinematics within $\sim 3.5$ arcsec and the Einstein mass with a NFW halo and found $\Upsilon^\text{dyn}_{*,I} = 4.2 \pm 0.2$ (see Table [TO DO ???]).
-\cite{SWELLSV}  found systematically lower NFW halos ($v_\text{circ}(5\text{arcsec}) \sim 120 \text{km s}^{-1}$ according to their Figure 2) than we did ($v_\text{circ}(5\text{arcsec}) \sim 200 \text{km s}^{-1}$, see Figure [TO DO ???]).
+We fitted the stellar kinematics within $\sim 3.5$ arcsec and the Einstein mass with a NFW halo and found $\Upsilon^\text{dyn}_{*,I} = 4.2 \pm 0.2$ (see Table \ref{tab:modelB4_bestfit}).
+\cite{SWELLSV}  found systematically lower NFW halos ($v_\text{circ}(5\text{arcsec}) \sim 120 \text{km s}^{-1}$ according to their Figure 2) than we did ($v_\text{circ}(5\text{arcsec}) \sim 200 \text{km s}^{-1}$, see Figure \ref{fig:kinematics}).
 [TO DO: Continue writing notes into text]
 \begin{itemize}
-\item We found an Einstein mass-to-light ratio of $\Upsilon_\text{I,tot,Ein} = 5.6$ (see Table [TO DO ???]).
+\item We found an Einstein mass-to-light ratio of $\Upsilon_\text{I,tot,Ein} = 5.6$ (see Table \ref{tab:bestfitlensmodel}).
 In case of a lower mass NFW halo, the largest contribution to this mass-to-light ratio would then be stellar mass.
 And the corresponding IMF would be more bottom heavy than Salpeter as well, like what \citet{SWELLSV} found.
-\item The light distribution multiplied with $\Upsilon_\text{I,tot,Ein}$ looks very similar to \cite{SWELLSV} [TO DO: Look details up in their paper and my work
+\item The light distribution multiplied with $\Upsilon_\text{I,tot,Ein}$ looks very similar to \cite{SWELLSV} [TO DO: Look details up in their paper and my work]
 \item In the JAM model based on the surface brightness alone with the increasing mass-to-light ratio, we found a total mass-to-light ratio in the center of J1331 of  $\Upsilon_\text{I,tot}(R\sim0) = 2.53$.
@@
 \caption{Total I-band luminosity, stellar mass and mass-to-light ratio, calculated from the I-band AB magnitudes and stellar masses found for J133's bulge and disk by \citet{SWELLS} (their table 2) for comparison with this work.
-The transformation from AB magnitudes to the Johnson-Cousins I-Band used the relation $I[\text{mag}] = I[\text{ABmag}] - 0.309$ from [TO DO: REF: Frei and Gunn 1994] (their table 2).
-For the conversion from apparent magnitude to total luminosity the redshift $z=0.113$ [TO DO: REF: Brewer] was turned into a luminosity distance using the cosmology by [TO DO: REF: Dunkley].
+The transformation from AB magnitudes to the Johnson-Cousins I-Band used the relation $I[\text{mag}] = I[\text{ABmag}] - 0.309$ from \citet{FG1994} (their table 2).
+For the conversion from apparent magnitude to total luminosity the redshift $z=0.113$ \citet{SWELLSIII} was turned into a luminosity distance using the cosmology by \ref{WMAP5cosm}.
 }

### 2015-09-03 docs/model_JAM_v1.01.tex
Finished section on JAM theory.

@@
 $\langle v_i v_j\rangle = 0$ for $i\neq j$.
-Secondly, we assume a constant ratio between the radial and vertical 2nd velocity moments, $\beta_z \equiv 1 - \langle v_z^2 \rangle / \langle v_R^2\rangle$.
+Secondly, we assume a constant ratio between the radial and vertical 2nd velocity moments,
+\begin{equation}
+\beta_z \equiv 1 - \langle v_z^2 \rangle / \langle v_R^2\rangle. \label{eq:bz}
+\end{equation}
 This reduces the Jeans equations to two equations for $\langle v_z^2 \rangle$ and $\langle v_\phi^2 \rangle$, that can be solved by means of one integration,
-\begin{eqnarray*}
-n \langle v_z^2 \rangle (R,z) &=& \int_0^\infty n \frac{\partial \Phi}{\partial z} \diff z\\
-n \langle v_\phi^2 \rangle (R,z) &=& R \frac{\partial}{\partial R} \left( \frac{n \langle v_z^2 \rangle}{1-\beta_z} \right) + \frac{n \langle v_z^2 \rangle}{1 - \beta_z} + R n \frac{\partial \Phi}{\partial R},
-\end{eqnarray*}
-where $n(\vect{x}) = \int f(\vect{x},\vect{v}) \diff3 v$ is the number density of tracers and $\Phi(\vect{x})$ the galaxy's gravitational potential, generated by the mass density $\rho(\vect{x})$ via Poisson's equation.
+\begin{eqnarray}
+n \langle v_z^2 \rangle (R,z) &=& \int_0^\infty n \frac{\partial \Phi}{\partial z} \diff z \label{eq:Jeans1}\\
+n \langle v_\phi^2 \rangle (R,z) &=& R \frac{\partial}{\partial R} \left( \frac{n \langle v_z^2 \rangle}{1-\beta_z} \right) + \frac{n \langle v_z^2 \rangle}{1 - \beta_z} + R n \frac{\partial \Phi}{\partial R},\label{eq:Jeans2}
+\end{eqnarray}
+where $n(\vect{x}) = \int f(\vect{x},\vect{v}) \Diff3 v$ is the number density of tracers and $\Phi(\vect{x})$ the galaxy's gravitational potential, generated by the mass density $\rho(\vect{x})$ via Poisson's equation.
 \\The JAM modelling approach by \citet{Cap08} makes use of expressing the tracer density and the mass density as MGEs (see also \citet{1994A&A...285..723E}).
@@
 (\ref{eq:deprojMGE}).
-The mass density consists of several sets of MGEs: One MGE, that is usually taken to be $\nu(R,z)$ multiplied by a constant stellar mass-to-light ratio $\Upsilon_*$, describes the distribution of stellar mass in the galaxy.
-To mimick gradients of stellar mass-to-light ratio, each Gaussian could be assigned its own $\Upsilon_{*,i}$.
-To add a Navarro-Frenck-White (NFW) \citep{Navarro+1995c,NFW96} dark matter halo component, a MGE generated from a fit to a NFW profile can be added to the stellar component.
-[TO DO: continue on p.
-74]
+The mass density $\rho(R,z)$ consists of several sets of MGEs: One MGE, that is usually taken to be $\nu(R,z)$ multiplied by a constant stellar mass-to-light ratio $\Upsilon_*$, describes the distribution of stellar mass in the galaxy.
+(To mimick gradients of mass-to-light ratio, each Gaussian could be assigned its own $\Upsilon_{*,i}$.) To add a Navarro-Frenck-White (NFW) \citep{Navarro+1995c,NFW96} dark matter halo component, a MGE generated from a fit to a NFW profile can be added to the stellar component.
+[TO DO: Maybe remove detailed description of the mass MGE here, if it is described in detail somewhere else.] The gravitational potential is generated from the mass MGE by integrating the Poisson equation \citep{1994A&A...285..723E}.
+Equations \ref{eq:Jeans1} and \ref{eq:Jeans2} together with \ref{eq:bz} provide the velocity dispersion tensor $\langle v_i v_j \rangle = \langle v_i^2 \rangle$ (with $i,j \in \{ R,\phi, z\}$).
+It is then rotated by the inclination angle $i$ to the coordinate system of the observer ($(x',y')$ being the plane of the sky and $z'$ the line-of-sight, where $x'$ is alinged with the galaxy's major axis).
+Taking a light-weighted projection along the line-of-sight gives a model prediction for the line-of-sight velocity second moment, which is comparable to actual spectroscopic measurements of the second velocity moment.
+Details of the derivation using the MGE formalism are given in \citet{Cap08} and repeated in \citet{GlennEC}, we therefore just quote the result by \citet{Cap08} (their Equation 28) for the line-of-sight second velocity moment prediction from the Jeans equations,
+\begin{eqnarray}
+&&\left(I \langle v_\text{los}^2\rangle\right)(x',y')\\
+&&= 4 \pi^{3/2} G \int_0^1 \sum_{k=1}^N \sum_{j=1}^M \nu_{0,k} \ q_j \ \rho_{0,j} \ u^2\nonumber\\
+&& \times \frac{\sigma_k^2 \ q^{2}_k \left( \cos^2 i + \frac{\sin^2 i}{1-\beta_{z,k}}\right) + \mathscr{D} \  {x'}^{2} \sin^2 i}{(1-\mathscr{C}u^2) \sqrt{(\mathscr{A} + \mathscr{B} \cos^2 i) \left[1-(1-q^{2}_j) u^2 \right]}}\label{eq:explicitLOSvelCap}\\
+&& \times \exp\left\{- \mathscr{A} \left[{x'}^{2} + \frac{(\mathscr{A}+\mathscr{B}) \ {y'}^{2}}{\mathscr{A}+\mathscr{B}\cos^2 i}\right] \right\} \diff u, \\
+\end{eqnarray}
+with $N$ Gaussians describing the tracer distribution and $M$ Gaussians describing the mass distribution, $\rho_{0,j}$ being the $j$-th mass density Gaussian evaluated at $(R=0,z=0)$ and
+\begin{eqnarray*}
+\mathscr{A} &=& \frac 12 \left(\frac{u^2}{\sigma_j^2} + \frac{1}{\sigma_k^2} \right)\nonumber\\
+\mathscr{B} &=& \frac 12 \left\{\frac{1-q^{2}_k}{\sigma_k^2 q^{2}_k} + \frac{(1-q^{2}_j)u^4}{\sigma_j^2 \left[1-(1-{q}_j^{2})u^2 \right]} \right\}\nonumber\\
+\mathscr{C} &=& 1- q^{2}_j - \frac{\sigma_k^2 q^{2}_k}{\sigma^2_j}\nonumber\\
+\mathscr{D} &=& 1 - \frac{q^{2}_k}{1-\beta_{z,k}} - \left[ \left(1-\frac{1}{1-\beta_{k,z}}\right)\mathscr{C} + \frac{1-q^{2}_j}{1-\beta_{z,k}}\right] u^2.\nonumber
+\end{eqnarray*}
+The JAM modelling code by \citet{Cap08} evaluates numerically Equation \ref{eq:explicitLOSvelCap} for a given luminous tracer and mass distribution MGE and a given inclination.
+
+[TO DO: make primed and unprimed coordinate systems clear.]
 

### 2015-09-03 docs/model_MGE_v1.01.tex
Revistied most of the lensing section.
Finished section on JAM theory.

@@
-\subsection{Multi-Gaussian Expansion Formalism}
+\subsection{Multi-Gaussian Expansion Formalism} \label{sec:MGE_theo}
 
@@
 \end{equation}
-The flattening of each axisymmetric 3D Gaussian $q$ and its central density $\nu_{0,i}$ follow from the observed 2D axis ratio $q'_i$ and surface density $I_{0,i}$ as
+The flattening of each axisymmetric 3D Gaussian $q_i$ and its central density $\nu_{0,i}$ follow from the observed 2D axis ratio $q'_i$ and surface density $I_{0,i}$ as
 \begin{eqnarray*}

### 2015-09-04 docs/discussion_ML_v1.01.tex
Finished section on mass / light comparison.

@@
 
-\subsection{Stellar mass-to-light ratios}
+\subsection{Stellar mass-to-light ratios} \label{sec:MLdiscussion}
 
 Further knowledge of the stellar populations within J1331 and their initial mass functions (IMF) would be useful.
-In particular a sophisticated guess for the \emph{stellar} mass-to-light ratio in J1331's bulge could be compared to our very reliable measurement of the \emph{total} mass-to-light ratio inside the Einstein radius (see Table \ref{tab:bestfitlensmodel}) to support or contradict the presence of a lot of dark matter in the bulge.
+In particular a sophisticated guess for the \emph{stellar} mass-to-light ratio in J1331's bulge could be compared to our very reliable measurement of the \emph{total} mass-to-light ratio inside the Einstein radius (see Table \ref{tab:einsteinML} ) to support or contradict the presence of a lot of dark matter in the bulge.
 Traditional choices for the IMF are the bottom-heavy IMF by \citet{Salpeter1955},
@@
 \\We compare our findings of the stellar mass-to-light ratios with the study by \cite{SWELLSV}: \cite{SWELLSV} found that the bulge of J1331 has an IMF more bottom-heavy than the Salpeter IMF from fitting a NFW halo to (1) the Einstein mass and (2) gas kinematics at larger radii $\gtrsim 8$ arcsec.
-We fitted the stellar kinematics within $\sim 3.5$ arcsec and the Einstein mass with a NFW halo and found $\Upsilon^\text{dyn}_{*,I} = 4.2 \pm 0.2$ (see Table \ref{tab:modelB4_bestfit}).
+We fitted the stellar kinematics within $\sim 3.5$ arcsec and the Einstein mass with a NFW halo and found $\Upsilon_\text{I,*}^\text{dyn} = 4.2 \pm 0.2$ (see Table \ref{tab:modelB4_bestfit}).
 \cite{SWELLSV}  found systematically lower NFW halos ($v_\text{circ}(5\text{arcsec}) \sim 120 \text{km s}^{-1}$ according to their Figure 2) than we did ($v_\text{circ}(5\text{arcsec}) \sim 200 \text{km s}^{-1}$, see Figure \ref{fig:kinematics}).
@@
 \begin{itemize}
-\item We found an Einstein mass-to-light ratio of $\Upsilon_\text{I,tot,Ein} = 5.6$ (see Table \ref{tab:bestfitlensmodel}).
+\item We found an Einstein mass-to-light ratio of $\Upsilon_\text{I,tot}^\text{ein} = 5.6$ (see Table \ref{tab:einsteinML}).
 In case of a lower mass NFW halo, the largest contribution to this mass-to-light ratio would then be stellar mass.
 And the corresponding IMF would be more bottom heavy than Salpeter as well, like what \citet{SWELLSV} found.
-\item The light distribution multiplied with $\Upsilon_\text{I,tot,Ein}$ looks very similar to \cite{SWELLSV} [TO DO: Look details up in their paper and my work]
+\item The circular velocity curve $v_\text{circ}(R) = \left.
+sqrt{R \frac{\partial \Phi}{\partial R}} \right|_{z=0}$ \citet{SWELLSV} find for J1331 peaks at $v_\text{circ}(R\sim0.9 \text{arcsec}) \sim 350 \text{km s}^{-1}$ (from lensing constraints only) and at $v_\text{circ}(R\sim0.9 \text{arcsec}) \sim 370 \text{km s}^{-1}$ (when including a dark matter halo and gas kinematics in the fit).
+We find a very similar circular velocity curve (at least at small radii) for a mass-follows-light model with constant $\Upsilon_\text{I,tot}^\text{ein} = 5.6$, which peaks at $v_\text{circ}(R\sim0.9 \text{arcsec}) \sim 360 \text{km s}^{-1}$.
 \item In the JAM model based on the surface brightness alone with the increasing mass-to-light ratio, we found a total mass-to-light ratio in the center of J1331 of  $\Upsilon_\text{I,tot}(R\sim0) = 2.53$.
@@
 \emph{If} there was a stellar population in the very center with an IMF close to the \citet{Chabrier2003} IMF, surrounded by a more bottom-heavy population, the central stellar kinematics would be well explained and be fully consistent with the lensing results, as found in Figure \ref{fig:modelG} and the surrounding text.
-It is not expected that the bluish disk of J1331 has a $\Upsilon_{*,I}$ as high as the reddish bulge.
+It is not expected that the bluish disk of J1331 has a $\Upsilon_\text{I,*}$ as high as the reddish bulge.
 The kinematics at larger radii would then be much better recovered by lower mass dark matter halo as found by \citet{SWELLSV}.
@@
 \item Detailed stellar population analyses of the spectra taken along J1331's major axis could possibly support or contradict the suspicion of the existence of stellar mass-to-light ratio gradients in J1331.
+\item According to Figure 5c [TO DO: REF] the lensing result might not predict a mass to light ratio gradient inside Rein, but then again the mass slope $alpha=1$ was only weakly constrained.
 \end{itemize}
@@
 [TO DO] [TO DO: Also compare with results from Treu et al.]
+
+[TO DO: Einheitlich: $Upsilon_{I,*}^{comment}$, $\Upsilon_\text{I,tot}^\text{ein}$]
 
@@
 & & \multicolumn{2}{c}{Chabrier IMF} & \multicolumn{2}{c}{Salpeter IMF}\\
-      &  $L$ [$10^{10}L_{\odot}$]                & $M_*$ [$10^{10}M_\odot$]               & $\Upsilon_*^\text{chab}$ & $M_*$ [$10^{10}M_\odot$] & $\Upsilon_*^\text{sal}$ \\\hline
+      &  $L$ [$10^{10}L_{\odot}$]                & $M_*$ [$10^{10}M_\odot$]               & $\Upsilon_\text{I,*}^\text{chab}$ & $M_*$ [$10^{10}M_\odot$] & $\Upsilon_\text{I,*}^\text{Salpeter}$ \\\hline
 bulge &   $3.10 \pm 0.15 $  & $7.8 \pm 1.8$ & $2.5 \pm 0.6$ & $14.5 \pm 3.7 $ & $4.7 \pm 1.2$ \\

### 2015-09-04 docs/results_JAMwithSB_v1.01.tex
Finished section on mass / light comparison.

@@
 This simplified model sometimes gives good representations of the inner parts of galaxies, where the stellar component dominates.
-In addition to the free fit parameter  $\Upsilon_{I,\text{tot}}^\text{dyn}$, we also allow for a overall constant but non-zero velocity anisotropy $\beta_z$.
+Testing this model for J1331 is also motivated by our findings from lensing in Section \ref{sec:results_lensing}, where around the Einstein radius total and luminous mass seem to have a similar distribution.
+\\In addition to the free fit parameter  $\Upsilon_{I,\text{tot}}^\text{dyn}$, we also allow for a overall constant but non-zero velocity anisotropy $\beta_z$.
 The best fit is found by minimizing $\chi^2$ between the $v_\text{rms}$ data and model prediction and is demonstrated in Figure \ref{fig:JAM_modelA2}.

### 2015-09-04 docs/results_lensing_v1.02.tex
Finished section on mass / light comparison.

--- 2015-09-01 docs/results_lensing_v1.02.tex
@@
 As models we use MGE fits and IRAF ellipse fits  (see Sections \ref{sec:MGE_theo} and \ref{sec:MGE_results})  to the galaxy in each the F450W and F814W filter.
-(For example the MGE we use for F814W is the MGE given in tab.
-\ref{tab:MGEF814W} convolved with the PSF in tab.
-\ref{tab:PSFMGEF814W}.) The lensing images become then visible in the residuals (see fig.
-\ref{fig:lens_just_imgpos}), in which we smooth out noise smaller than the PSF.
+(For example the MGE we use for F814W is the MGE given in Table \ref{tab:MGEF814W} convolved with the PSF in Table \ref{tab:PSFMGEF814W}.) The lensing images become then visible in the residuals (see Figure \ref{fig:lens_just_imgpos}), in which we smooth out noise smaller than the PSF.
 Because the lensing images are extended, we use the position of the brightest pixel in each of the images.
 We also use the F450W-MGE subtracted residuals from \citet{SWELLSIII}.
-The lensing positions as determined from the latter are given in tab.
-\ref{tab:lenspos}.
+The lensing positions as determined from the latter are given in Table \ref{tab:lenspos}.
 The scatter of lensing positions as determined from subtracting different surface brightness models from the galaxy in different filters gives an error of $\pm 1$ pixel on the image positions.
@@
 \\Eight image position coordinates allow us to fit a lens mass model with only $<8$ free parameters. We therefore do not fit Fourier components $(a_k,b_k)$ with $k > 3$.
-\\Even though the constraints from the image positions on $\alpha$ is very weak, we were however able to show that the image positions in tab.
-\ref{tab:lenspos} are consistent with a model with flat rotation curve.
+\\Even though the constraints from the image positions on $\alpha$ is very weak, we were however able to show that the image positions in Table \ref{tab:lenspos} are consistent with a model with flat rotation curve.
 In the following we therefore set $\alpha=1$.
@@
 \end{tabular}
-\caption{Positions of the lensing images (A-D) and the galaxy center (G) in fig.
-\ref{fig:lens_just_imgpos}.
-The image positions were determined from the lens subtracted image for J1331 in figure 4 of \citet{SWELLSIII}, rotated to the $(x,y)$ coordinate system in fig.
-\ref{fig:lens_just_imgpos}.
+\caption{Positions of the lensing images (A-D) and the galaxy center (G) in Figure \ref{fig:lens_just_imgpos}.
+The image positions were determined from the lens subtracted image for J1331 in Figure 4 of \citet{SWELLSIII}, rotated to the $(x,y)$ coordinate system in Figure \ref{fig:lens_just_imgpos}.
 The pixel scale is 1 pixel = 0.05 arcsec and the error of each image position is $\pm$ 1 pixel.
@@
 
-\paragraph{Best fit lens model.} The best fit lens model for the image positions in tab.
-\ref{tab:lenspos} is given in the first column of tab.
-\ref{tab:bestfitlensmodel}.
-Fig.
-\ref{fig:lensbestfiteinsteincurves} shows the corresponding critical curve, caustic and Einstein radius, and the best fit source position.
+\paragraph{Best fit lens model.} The best fit lens model for the image positions in Table \ref{tab:lenspos} is given in the first column of Table \ref{tab:bestfitlensmodel}.
+Figure \ref{fig:lensbestfiteinsteincurves} shows the corresponding critical curve, caustic and Einstein radius, and the best fit source position.
 In this case, where $\alpha=1$, the critical curve is also an equidensity contour of the galaxy model \citep{EvansWitt}, which appears to have an elliptical mass distribution.
@@
 This is a good indication that indeed all four images are indeed lensing images of the same object.
-Fig.
-\ref{fig:lensbestfittimedelay} overplots the smoothed residuals from the F450W image subtracted by the IRAF ellipse fit to the surface brightness with the contours of the best fit model's time delay surface.
+Figure \ref{fig:lensbestfittimedelay} overplots the smoothed residuals from the F450W image subtracted by the IRAF ellipse fit to the surface brightness with the contours of the best fit model's time delay surface.
 This demonstrates that, although we did not include any information about the shape of the lensing images in the fit, it is consistent with the predicted distortion for an extended source by the best fit lens model.
-\\To estimate how the uncertainties in the determination of the image positions and galaxy center affect the results, we Monte Carlo sample random positions from a two-dimensional Normal distribution centered at the positions in tab.
-\ref{tab:lenspos} and a standard deviation corresponding to the measurement error.
-A Gaussian fit to the resulting distributions of best fit values leads to the constraints on the shape parameters and Einstein quantities in the second column in tab.
-\ref{tab:bestfitlensmodel}.
+\\To estimate how the uncertainties in the determination of the image positions and galaxy center affect the results, we Monte Carlo sample random positions from a two-dimensional Normal distribution centered at the positions in Table \ref{tab:lenspos} and a standard deviation corresponding to the measurement error.
+A Gaussian fit to the resulting distributions of best fit values leads to the constraints on the shape parameters and Einstein quantities in the second column in Table \ref{tab:bestfitlensmodel}.
 We therefore constrain the Einstein radius to within 2\%, $R_\text{ein} = (0.91 \pm 0.02)$ arcsec and the projected mass within the critical curve with a relative error of 4\%, $M_\text{crit} =(7.9\pm0.3)\cdot 10^{10} M_\odot$.
@@
 \centering
-\caption{??? in tab. \ref{tab:lenspos}, for $\alpha = 1$}
+\caption{[TO DO: Caption] ??? in Table \ref{tab:lenspos}, for $\alpha = 1$}
 \begin{tabular}{llrrclr}
@@
  &  & \multicolumn{1}{c}{peak image positions}  & \multicolumn{4}{c}{of image positions }  \\ \hline
-Einstein Radius      & $R_\text{ein}$ [arcsec]             & $0.907$ & $0.91$  & $\pm$ & $     0.02$ & ($2\%$)\\
-Einstein Mass        & $M_\text{ein}$ [$10^{10} M_\odot$]  & $7.72$  & $7.8 $  & $\pm$ & $      0.3$ & ($4\%$) \\
-Critical Mass        & $M_\text{crit}$ [$10^{10} M_\odot$] & $7.87$  & $7.9$   & $\pm$ & $      0.3$ & ($4\%$)\\
-Source Position      & $\xi$ [arcsec]                      & $0.095$ & $0.09 $ & $\pm$ & $     0.03$ & ($28\%$)\\
+Einstein radius      & $R_\text{ein}$ [arcsec]             & $0.907$ & $0.91$  & $\pm$ & $     0.02$ & ($2\%$)\\
+Einstein mass        & $M_\text{ein}$ [$10^{10} M_\odot$]  & $7.72$  & $7.8 $  & $\pm$ & $      0.3$ & ($4\%$) \\
+Critical mass        & $M_\text{crit}$ [$10^{10} M_\odot$] & $7.87$  & $7.9$   & $\pm$ & $      0.3$ & ($4\%$)\\
+Source position      & $\xi$ [arcsec]                      & $0.095$ & $0.09 $ & $\pm$ & $     0.03$ & ($28\%$)\\
                      & $\eta$ [arcsec]                     & $0.107$ & $0.10 $ & $\pm$ & $     0.03$ & ($27\%$)\\
-Fourier Coefficients & $a_0$                               & $1.814$ & $1.82 $ & $\pm$ & $   0.04$ & (2\%)\\
+Fourier coefficients & $a_0$                               & $1.814$ & $1.82 $ & $\pm$ & $   0.04$ & (2\%)\\
                      & $a_2$                               & $0.012$ & $ 0.011 $ & $\pm$ & $    0.004$ & (35\%)\\
@@
 
-\paragraph{Comparison with Light Distribution.} Fig.
-\ref{fig:lenscomparemass} shows the surface mass distribution as predicted by the best fit model in tab.
-\ref{tab:bestfitlensmodel}.
-We introduce random noise according to the uncertainties in the Fourier shape parameters to create a mock observation that visualizes the effect of the measurement errors.
+\paragraph{Comparison with Light Distribution.} The surface mass distribution as predicted by the best fit model in Table \ref{tab:bestfitlensmodel} is shown in Figure \ref{fig:lenscomparemass}.
+We introduced random noise according to the uncertainties in the Fourier shape parameters to create a mock observation that visualizes the effect of the measurement errors.
 From the mock image's second moment we find an average axis ratio for the lens mass model of $q_\text{lens} \simeq 0.695$, which is consistent with the one found by \citet{SWELLSIII}, $q_\text{lens,SWELLSIII} = 0.67 \pm 0.09$, while the light's average axis ratio in Table \ref{tab:galaxyparameters} is $q' = 0.598$.
-\\To be able to compare the predicted mass distribution to the observed light distribution, we transform the surface brightness into a mass density: We first integrate the MGE in tab.
-\ref{tab:MGEF814W} to get the total luminosity within the Einstein radius and the predicted mass-to-light ratio as $\Upsilon_\text{I,ein} = M_\text{ein} / L_\text{I,ein}$.
-Fig.
-\ref{fig:lenscomparelight} shows then the observed surface brightness in the F814W filter multiplied by $\Upsilon_\text{I,ein}$.
-Fig.
-\ref{fig:lenscompareboth} finally compares equidensity contours at the same values of both the predicted lens mass distribution and the observed surface brightness times $\Upsilon_\text{I,ein}$.
-\\Figure \ref{fig:lenslightcompareALL} leads to the following three findings: 1.The mass predicted from lensing and the observed light distribution are oriented in the same direction.
-2.
-Within the Einstein radius, mass and light distribution have the same shape, while further out the mass distribution is more roundish.
-3.
-The light distribution drops faster than the mass with increasing radius.
-\\Reasons for the difference in observed light and measured mass distribution could be, e.g.
-an apparent change of shape due to dust extinction, a strongly changing $\Upsilon_*$, or the stellar component of the galaxy could be superimposed by a more roundish dark matter component.
-
-\paragraph{[TO DO: Stuff to mention]}
-\begin{itemize}
-\item best fit lens total mass distribution of J1331 has the same position angle and a similar elliptical shape as the surfache brightness distributon, but is slightly rounder, and could be consistent with a flat rotation curve.
-\end{itemize}
+\\To estimate the total mass-to-light ratio within the Einstein radius $\Upsilon_\text{I,tot}^\text{ein} = M_\text{ein} / L_\text{I,ein}$, we first integrate the MGE in Table \ref{tab:MGEF814W} to get the total luminosity within the Einstein radius $L_\text{I,ein}$.
+$L_\text{I,ein}$ and $\Upsilon_\text{I,tot}^\text{ein}$ are given in Table \ref{tab:einsteinML}.
+$\Upsilon_\text{I,tot}^\text{ein} \sim 5.6$ is consistent or slightly larger than the stellar mass-to-light ratio assuming a Salpeter Initial Mass Function $\Upsilon_\text{I,*}^\text{Salpeter} = 4.7 \pm 1.2$ according to \citet{SWELLSI} and Table \ref{tab:previousresults} (see also discussion in Section \ref{sec:MLdiscussion}).
+We use $\Upsilon_\text{I,tot}^\text{ein}$ to transform the observed surface brightness in the F814W filter into a surface mass density to compare it to the lensing mass distribution (Figure \ref{fig:lenscomparelight}).
+Figure \ref{fig:lenscompareboth} then compares equidensity contours at the same values of both the predicted lens mass distribution and the observed surface brightness times $\Upsilon_\text{I,tot}^\text{ein}$.
+\\Figure \ref{fig:lenslightcompareALL} leads to the following three findings: (1)The mass predicted from lensing and the observed light distribution are oriented in the same direction (i.e.
+have the same position angle).
+(2) Within and around the Einstein radius, mass and light distribution have a similar elliptical shape, while further out the mass distribution is slightly rounder.
+(3) The light distribution drops faster than the mass with increasing radius.
+Astrophysical reasons for the differences in observed light and measured mass distribution could be, e.g.
+an apparent change of shape due to dust extinction, a strongly changing $\Upsilon_{I,*}$, or the stellar component of the galaxy could be superimposed by a more roundish dark matter component.
+We have to note however that the mass distribution is only constraint around the Einstein radius and otherwise an extrapolation.
 
@@
 \centering
-\caption{???}
+\caption{Total I-band (F814W) luminosity inside the Einstein radius $R_\text{ein}$, found from integrating the MGE in Table \ref{tab:MGEF814W} and corresponding total mass-to-light ratio $\Upsilon_\text{I,tot}^\text{ein}$ using the Einstein mass $M_\text{ein}$.
+$R_\text{ein}$ and $M_\text{ein}$ are given in Table \ref{tab:bestfitlensmodel}.}
 \begin{tabular}{cc}
@@
 Total I-band luminosity within $R_\text{ein}$ & Mass-to-light ratio within $R_\text{ein}$\\
- $L_\text{I,ein}$ [$10^{10} L_\odot$] & $\Upsilon_\text{I,ein} = M_\text{ein} / L_\text{I,ein}$ [$\Upsilon_\odot$]\\\hline
+ $L_\text{I,ein}$ [$10^{10} L_\odot$] & $\Upsilon_\text{I,tot}^\text{ein} = M_\text{ein} / L_\text{I,ein}$ [$\Upsilon_{\text{I},\odot}$]\\\hline
 1.40 & 5.56\\\hline
@@
   \includegraphics[width=.9\linewidth]{fig/lens_surface_brightness.ps}
-  \caption{???}
+  \caption{Observed light distribution. [TO DO: use $\Upsilon_\text{I,tot}^\text{ein}$ on colorbar]}
   \label{fig:lenscomparelight}
@@
   \includegraphics[width=.9\linewidth]{fig/lens_surface_density.ps}
-  \caption{???}
+  \caption{Predicted mass distribution.}
   \label{fig:lenscomparemass}
@@
   \includegraphics[width=.9\linewidth]{fig/paper_lensmass_brightness_compare.ps}
-  \caption{???}
+  \caption{Comparison of mass and light.}
   \label{fig:lenscompareboth}
 \end{subfigure}
-\caption{???
-Preliminary crappy caption: Left: OBSERVED surface bightness multiplied with M/L in Einstein radius (overplotted in red).
-Middle: BEST FIT MODEL for mass distribution from lensing (including "wriggles" due to uncertainties in image positions).
-Contours are at the same levels.
-Right: Same contours, to directly show the difference in shape.
-???
-[TO DO: nice caption]}
+\caption{Comparison of the observed F814W/I-band surface brightness distribution (Panel (a) and orange contours) and predicted mass distribution from lensing constraints (Panel (b) and pink contours).
+To allow for a qualitative comparison of the contours in Panel (c), the light distribution was turned into a mass distribution by multiplication with the total mass-to-light ratio inside the Einstein radius $\Upsilon_\text{I,tot}^\text{ein}$ in Table \ref{tab:einsteinML}.
+The Einstein radius is overplotted as red dotted circle.
+The uncertainties in the mass model in the second column of Table \ref{tab:bestfitlensmodel} were translated into random Monte Carlo noise in the mass contours.
+The smooth black contours correspond to the best fit model in the first column of Table \ref{tab:bestfitlensmodel}.
+The background in Panel (c) shows again the surface brightness subtracted center of the galaxy to make the lensing images visible.}
 \label{fig:lenslightcompareALL}

### 2015-09-07 docs/data_v1.01.tex
Finished Data section.

--- 2015-08-13 docs/data_v1.01.tex
@@
 
-[TO DO]
+For our lensing and dynamics analysis of J1331 we use on the one hand Hubble Space Telescope (HST) imaging by \cite{SWELLSI} in two filters (F450W and F814W), and on the other hand line-of-sight stellar kinematics along J1331's major axis by \citet{SWELLSV}.
 
-\begin{itemize}
-\item Hubble Space teleskope (HST) imaging by \cite{SWELLSI} in two filters (F450W amd F814W)
-\item I filter: for surface brightness distribution of J1331's bulge for Jeans modelling
-\item ??? filter: to identify bluish lensing images
-\item drizzled image
-\end{itemize}
+\paragraph{Redshift.} [TO DO: WHO???] found from SDSS spectra that J1331 has two redshifts inside 1 arcsec: The smaller one, $z_d = 0.113$, is the redshift of J1331 itself, the larger one, $z_s = 0.254$, is the redshift of the lensed background source \citep{SWELLSIII}.
+According to its redshift and the WMAP5 [TO DO: CHECK] cosmology \citep{WMAP5cosm}, J1331 has an angular diameter distance of 414 Mpc, which translates into a transverse scaling of 1 arcsec $\hat{=}$ 2.01 kpc.
 
-\paragraph{Stellar Kinematics.} We use the stellar kinematics for J1331 measured by [TO DO: REF: Dutton 2013].
+\paragraph{HST imaging.} We use the follow-up HST imaging, with which \citet{SWELLSI} confirmed that J1331 is indeed a strong gravitational lens [TO DO: REALLY???].
+They performed high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) and its WF3 CCD chip.
+The images we are using are a combination of four exposures with each an exposure of 400s and were drizzled to a pixel scale of 1 pixel = 0.05 arcsec.
+In particular we use the images in the filters F450W, to identify the positions of the bluish lensing images, and F814W to create a surface brightness MGE model of the reddish bulge (I-band), used in the JAM dynamical modelling.
+
+\paragraph{Stellar kinematics.} For the dynamical modelling we also use the stellar kinematics for J1331 measured by \citet{SWELLSV}.
 They obtained long-slit spectra along J1331's major-axis with the Low Resolution Imaging Spectrograph (LRIS) on the Keck I 10m telescope.
@@
 Spectra for spatial bins of different widths along the major axis were extracted.
-Analogously to [TO DO: REF: Dutton 2011] they measured line-of-sight rotation velocities ($v_\text{rot}$) and stellar velocity dispersion ($\sigma$) by fitting Gaussian line profiles to emission lines in these spectra.
+Analogously to \citet{SWELLSII} they measured line-of-sight rotation velocities ($v_\text{rot}$) and stellar velocity dispersion ($\sigma$) by fitting Gaussian line profiles to emission lines in these spectra.
 Gas kinematics were extracted from fits to H$\alpha$ and NII lines, as tracers for inonized gas.
@@
 In the JAM modelling, which is based on the assumption of axisymmetry, only kinematics within $\sim 2.5$ and 4 arcsec are used.
-Another reason to restrict to modelling on the bulge region is that our MGE in Table \ref{tab:MGEF814W} is only a good representation of J1331's F814W light distribution inside $\sim 5$ arcsec.
+Another reason to restrict to modelling on the bulge region is that our MGE in Table \ref{tab:MGEF814W} is only a good representation of J1331's F814W light distribution inside $\sim 5$ arcsec.\\
+
+[TO DO: How to deal with the typo in J1331s name????]

### 2015-09-07 docs/discussion_ML_v1.02.tex
(Forgot to add new discussion file...)

--- 2015-09-04 docs/discussion_ML_v1.01.tex
@@
 
-\subsection{Stellar mass-to-light ratios} \label{sec:MLdiscussion}
+\subsection{On J1331's Stellar Mass-to-Light Ratio} \label{sec:MLdiscussion}
 
@@
 In particular a sophisticated guess for the \emph{stellar} mass-to-light ratio in J1331's bulge could be compared to our very reliable measurement of the \emph{total} mass-to-light ratio inside the Einstein radius (see Table \ref{tab:einsteinML} ) to support or contradict the presence of a lot of dark matter in the bulge.
+\\
+
 Traditional choices for the IMF are the bottom-heavy IMF by \citet{Salpeter1955},
@@
 (where $\xi(m) \diff m$ is the number of stars with mass $m$ in $[m,m+\diff m]$) and the IMFs by \citet{2002Sci...295...82K} and \citet{Chabrier2003}, which are in agreement with each other and predict less low-mass stars.
-\\\citet{Ferreras} found a relation between the central stellar velocity dispersion $\sigma_0$ in early-type galaxies and the IMF slope.
+\\
+
+\citet{Ferreras} found a relation between the central stellar velocity dispersion $\sigma_0$ in early-type galaxies and the IMF slope.
 A higher $\sigma_0$ suggests a more bottom-heavy IMF.
@@
 This is more bottom-heavy than the standard \citet{2002Sci...295...82K} IMF.
-Overall the central velocity dispersion suggests a rather bottom-heavy IMF J1331's bulge and therefore large stellar mass-to-light ratio.
-\\ \citet{SWELLSI} estimated J1331's stellar bulge mass given a Salpeter IMF and measured the I-band AB magnitude of the bulge.
-Transformed to a stellar I-band mass-to-light ratio (see Table \ref{tab:previousresults}) this would correspond to $\Upsilon_\text{I,*}^\text{Salpeter} = 4.7 \pm 1.2$.
-\\We compare our findings of the stellar mass-to-light ratios with the study by \cite{SWELLSV}: \cite{SWELLSV} found that the bulge of J1331 has an IMF more bottom-heavy than the Salpeter IMF from fitting a NFW halo to (1) the Einstein mass and (2) gas kinematics at larger radii $\gtrsim 8$ arcsec.
-We fitted the stellar kinematics within $\sim 3.5$ arcsec and the Einstein mass with a NFW halo and found $\Upsilon_\text{I,*}^\text{dyn} = 4.2 \pm 0.2$ (see Table \ref{tab:modelB4_bestfit}).
+Overall the central velocity dispersion suggests a rather bottom-heavy IMF J1331's bulge and therefore large stellar mass-to-light ratio.\\
+
+\citet{SWELLSI} estimated J1331's stellar bulge mass given a Salpeter IMF and measured the I-band AB magnitude of the bulge.
+Transformed to a stellar I-band mass-to-light ratio (see Table \ref{tab:previousresults}) this would correspond to $\Upsilon_\text{I,*}^\text{Salpeter} = 4.7 \pm 1.2$.\\
+
+We compare our findings of the stellar mass-to-light ratios with the study by \cite{SWELLSV}: \cite{SWELLSV} found that the bulge of J1331 has an IMF more bottom-heavy than the Salpeter IMF from fitting a NFW halo to (1) the Einstein mass and (2) gas kinematics at larger radii $\gtrsim 8$ arcsec.
+In Section \ref{sec:results_JAM_NFW} we fitted the stellar kinematics within $\sim 3.5$ arcsec and the Einstein mass with a NFW halo and the best fit $\Upsilon_\text{I,*}^\text{dyn} = 4.2 \pm 0.2$ (see Table \ref{tab:modelB4_bestfit}) indicates a less bottom-heavy IMF than the Salpeter IMF.
 \cite{SWELLSV}  found systematically lower NFW halos ($v_\text{circ}(5\text{arcsec}) \sim 120 \text{km s}^{-1}$ according to their Figure 2) than we did ($v_\text{circ}(5\text{arcsec}) \sim 200 \text{km s}^{-1}$, see Figure \ref{fig:kinematics}).
-[TO DO: Continue writing notes into text]
-\begin{itemize}
-\item We found an Einstein mass-to-light ratio of $\Upsilon_\text{I,tot}^\text{ein} = 5.6$ (see Table \ref{tab:einsteinML}).
-In case of a lower mass NFW halo, the largest contribution to this mass-to-light ratio would then be stellar mass.
-And the corresponding IMF would be more bottom heavy than Salpeter as well, like what \citet{SWELLSV} found.
-\item The circular velocity curve $v_\text{circ}(R) = \left.
+We note however, that our results would be much closer to those by \citet{SWELLSV}, if we only used the lensing results at small radii as they did: The total mass-to-light ratio of $\Upsilon_\text{I,tot}^\text{ein} = 5.6$ inside the Einstein radius (see Table \ref{tab:einsteinML}).
+In case of a lower mass dark matter halo, the largest contribution to this mass-to-light ratio would then be stellar mass.
+And the corresponding IMF would be more bottom-heavy than Salpeter,  like what \citet{SWELLSV} found.
+The circular velocity curve $v_\text{circ}(R) = \left.
 sqrt{R \frac{\partial \Phi}{\partial R}} \right|_{z=0}$ \citet{SWELLSV} find for J1331 peaks at $v_\text{circ}(R\sim0.9 \text{arcsec}) \sim 350 \text{km s}^{-1}$ (from lensing constraints only) and at $v_\text{circ}(R\sim0.9 \text{arcsec}) \sim 370 \text{km s}^{-1}$ (when including a dark matter halo and gas kinematics in the fit).
-We find a very similar circular velocity curve (at least at small radii) for a mass-follows-light model with constant $\Upsilon_\text{I,tot}^\text{ein} = 5.6$, which peaks at $v_\text{circ}(R\sim0.9 \text{arcsec}) \sim 360 \text{km s}^{-1}$.
-\item In the JAM model based on the surface brightness alone with the increasing mass-to-light ratio, we found a total mass-to-light ratio in the center of J1331 of  $\Upsilon_\text{I,tot}(R\sim0) = 2.53$.
-This is very close to the stellar mass-to-light ratio we got from \citet{SWELLSI} estimates of the bulge's stellar mass using the \citet{Chabrier2003} IMF $\Upsilon_\text{I,*}^\text{Chabrier} = 2.5 \pm 0.6$, i.e.
-less bottom-heavy (more blue) population.
-\item The central dip of the stellar kinematics cannot be explained alone by a strong contribution of dark matter, because the best fit NFW halos are too massive to explain the kinematics at larger radii.
-\item The central dip can also not be explained alone by tangential [TO DO: check???] velocity anisotropy in the center and a lower contribution by dark matter.
-\item The above discussion motivates the following speculation: In the absence of a strong dark matter contribution in the center, the overall stellar-mass-to-light ratio within the Einstein radius indicates a bottom-heavy Salpeter-like IMF, consistent with estimates from the velocity dispersion.
+We get a very similar circular velocity curve (at least at small radii) for a mass-follows-light model with constant $\Upsilon_\text{I,tot}^\text{ein} = 5.6$, which peaks at $v_\text{circ}(R\sim0.9 \text{arcsec}) \sim 360 \text{km s}^{-1}$.
+From this comparison follows, that the model by \citet{SWELLS} corresponds approximately to a mass-follows-light model in the inner regions of J1331.
+In Section \ref{sec:results_JAM_SB} however we showed, that this is \emph{not} a good model for J1331 and won't be able to reproduce the central stellar $v_\text{rms}$ dip.
+On the other hand, because our NFW JAM models fail to predict the stellar kinematics at large radii, the true halo parameters are more likely closer to the findings by \citet{SWELLSV}.\\
+
+All of this leaves the central dip unexplained: It cannot be due to tangential velocity anisotropy in the center alone (see Section \ref{sec:results_JAM_SB}, Figure \ref{fig:JAM_modelA2}).
+It also cannot be explained by a strong contribution of dark matter inside the bulge together with a moderate tagential velocity anisotropy, because the corresponding dark matter halos would still be too massive to fit the data in the outer regions (see Section \ref{sec:results_JAM_NFW}, Figure \ref{fig:modelB4_vrms}]).
+
+An alternative JAM model was introduced in Section \ref{sec:results_JAM_SB}, where we used the surface brightness distribution without a halo component but together with an increasing mass-to-light ratio.
+We found that such a model would be perfectly consistent with the lensing results and predict a total mass-to-light ratio in the center of J1331 of  $\Upsilon_\text{I,tot}(R\sim0) = 2.53$.
+This is very close to the stellar mass-to-light ratio we got from \citet{SWELLSI} estimates of the bulge's stellar mass using the Chabrier IMF $\Upsilon_\text{I,*}^\text{Chabrier} = 2.5 \pm 0.6$, i.e.
+less bottom-heavy (more bluish) population.\\
+
+The above discussion motivates the following speculation: In the absence of a strong dark matter contribution in the center, the overall stellar-mass-to-light ratio within the Einstein radius indicates a bottom-heavy IMF close to the Salpeter IMF, consistent with estimates from the velocity dispersion.
 At the same time the central dip can then be only explained, if there was an increase in stellar mass-to-light ratio with radius \textit{within} the bulge.
-\emph{If} there was a stellar population in the very center with an IMF close to the \citet{Chabrier2003} IMF, surrounded by a more bottom-heavy population, the central stellar kinematics would be well explained and be fully consistent with the lensing results, as found in Figure \ref{fig:modelG} and the surrounding text.
-It is not expected that the bluish disk of J1331 has a $\Upsilon_\text{I,*}$ as high as the reddish bulge.
-The kinematics at larger radii would then be much better recovered by lower mass dark matter halo as found by \citet{SWELLSV}.
-\item Standard JAM modelling approaches seem not to work for J1331.
+\emph{If} there was a central stellar population with an IMF close to the \citet{Chabrier2003} IMF, surrounded by a more bottom-heavy population, the central stellar kinematics would be well explained and be fully consistent with the lensing results.
+(According to Figure \ref{fig:lenscompareboth} the lensing result might not predict a mass to light ratio gradient inside $R_\text{ein}$, but then again the mass slope $alpha=1$ was only weakly constrained.) It is not expected that the bluish disk of J1331 has a $\Upsilon_\text{I,*}$ as high as the reddish bulge.
+The kinematics at larger radii would then also be much better recovered by lower mass dark matter halo as found by \citet{SWELLSV}.
+\\
+
+Standard JAM modelling approaches seem not to work for J1331.
 A JAM model for J1331 would need to allow for stellar mass-to-light ratio gradients within the galaxy, velocity anisotropy and a dark matter halo.
@@
 Further priors are needed.
-\item Detailed stellar population analyses of the spectra taken along J1331's major axis could possibly support or contradict the suspicion of the existence of stellar mass-to-light ratio gradients in J1331.
-\item According to Figure 5c [TO DO: REF] the lensing result might not predict a mass to light ratio gradient inside Rein, but then again the mass slope $alpha=1$ was only weakly constrained.
-\end{itemize}
+Detailed stellar population analyses of the spectra taken along J1331's major axis could possibly support or contradict the suspicion of the existence of stellar mass-to-light ratio gradients in J1331.
 
@@
 
-[TO DO] [TO DO: Also compare with results from Treu et al.]
-
 [TO DO: Einheitlich: $Upsilon_{I,*}^{comment}$, $\Upsilon_\text{I,tot}^\text{ein}$]
 
-\paragraph{Collection of thoughts}
-\begin{itemize}
-\item [TO DO: Start on page 62]
-\end{itemize}
-
-\begin{table}
+\begin{table*}
 \centering
@@
 \label{tab:previousresults}
-\end{table}
+\end{table*}

### 2015-09-07 docs/abstract_v1.02.tex
Small changes in Abstract.

--- 2015-08-11 docs/abstract_v1.01.tex
@@
 We analyse the stellar and dark matter distribution in the spiral galaxy SDSS J1331+3638 (J1331) by means of two independent methods: gravitational lensing and dynamical Jeans modelling.
-Hubble Space Telescope (HST) imaging by \citet{SWELLSI} reveals, that J1331's bulge is superimposed by a quadruplet of extended lensing images.
-By fitting a gravitational potential model to the image positions, we constrain the mass inside the Einstein radius ($R_\text{ein}=0.91\pm0.02$ arcsec) to within 4\% ($M_\text{ein} = (7.8\pm0.3) \cdot 10^{10} M_\odot$).
-From Multi-Gaussian Expansions (MGE) of J1331's surface brightness distribution we find that J1331 has an apparent I-band magnitude of $m_I \simeq 15.8$ mag, a total luminosity of $L_{I,tot} \simeq 5.6 \cdot 10^{10}L_{I,\odot}$ and an effective radius of $R_\text{eff} \simeq 2.6$ arcsec = 5.6 kpc.
+Hubble Space Telescope (HST) imaging by \citet{SWELLSI} show, that J1331's bulge is superimposed by a quadruplet of extended lensing images.
+By fitting a gravitational potential model to the image positions, we tightly constrain the mass inside the Einstein radius ($R_\text{ein}=0.91\pm0.02$ arcsec) to within 4\% ($M_\text{ein} = (7.8\pm0.3) \cdot 10^{10} M_\odot$).
 
 According to the long-slit major axis stellar kinematics from \citet{SWELLSV}, J1331 has a counter-rotating stellar core inside $\sim 2$ arcsec.
-We model the observed stellar kinematics in J1331's central regions by finding MGE models for the stellar and dark matter distribution that solve the axisymmetric Jeans equations.
+We model the observed stellar kinematics in J1331's central regions by finding Multi-Gaussian Expansion (MGE) models for the stellar and dark matter distribution that solve the axisymmetric Jeans equations.
 We find that J1331 requires a steep total mass-to-light ratio gradient in the center to reproduce the observed stellar kinematics.
@@
 The NFW halo models can successfully reproduce the signatures of J1331's counter-rotating stellar core and predict J1331's rotation curve at larger radii.
-However, all these models were more massive than expected from the gas rotation curve at larger radii, and failed to reproduce the steep drop in measured velocity dispersion at [TO DO: WHAT RADIUS???].
-This could indicate a non-trivial re-distribution of matter due a possible minor merger event in J1331's past.
+However, all these models were more massive than expected from the gas rotation curve and stellar velocity dispersion at larger radii.
+We speculate that this could indicate a non-trivial re-distribution of matter due a possible minor merger event in J1331's past, e.g.
+a stellar core in J1331's very center with a \citet{Chabrier2003} initial mass function (IMF), surrounded by a extended stellar bulge population with a super \citet{Salpeter1955} IMF.

### 2015-09-08 docs/discussion_ML_v1.02.tex
Started writing discussion of possible minor merger.

@@
 All of this leaves the central dip unexplained: It cannot be due to tangential velocity anisotropy in the center alone (see Section \ref{sec:results_JAM_SB}, Figure \ref{fig:JAM_modelA2}).
-It also cannot be explained by a strong contribution of dark matter inside the bulge together with a moderate tagential velocity anisotropy, because the corresponding dark matter halos would still be too massive to fit the data in the outer regions (see Section \ref{sec:results_JAM_NFW}, Figure \ref{fig:modelB4_vrms}]).
+It also cannot be explained by a strong contribution of dark matter inside the bulge together with a moderate tagential velocity anisotropy, because the corresponding dark matter halos would still be too massive to fit the data in the outer regions (see Section \ref{sec:results_JAM_NFW}, Figure \ref{fig:modelB4_vrms}]).\\
 
@@
 
+Another feature in the stellar kinematics, that none of our JAM models was able to reproduce in the slightest and which we therefore excluded in the modelling, was the dip in $v_\text{rms}$ around $\sim 6$ arcsec, which occurs around the transition from bulge to disk (see Figure [TO DO: 1b]).\\
+
 The above discussion motivates the following speculation: In the absence of a strong dark matter contribution in the center, the overall stellar-mass-to-light ratio within the Einstein radius indicates a bottom-heavy IMF close to the Salpeter IMF, consistent with estimates from the velocity dispersion.
@@
 \emph{If} there was a central stellar population with an IMF close to the \citet{Chabrier2003} IMF, surrounded by a more bottom-heavy population, the central stellar kinematics would be well explained and be fully consistent with the lensing results.
-(According to Figure \ref{fig:lenscompareboth} the lensing result might not predict a mass to light ratio gradient inside $R_\text{ein}$, but then again the mass slope $alpha=1$ was only weakly constrained.) It is not expected that the bluish disk of J1331 has a $\Upsilon_\text{I,*}$ as high as the reddish bulge.
-The kinematics at larger radii would then also be much better recovered by lower mass dark matter halo as found by \citet{SWELLSV}.
-\\
-
-Standard JAM modelling approaches seem not to work for J1331.
-A JAM model for J1331 would need to allow for stellar mass-to-light ratio gradients within the galaxy, velocity anisotropy and a dark matter halo.
-Because of degeneracies between stellar and dark mass, and matter distribution and anisotropy profile, such a dynamical model would not lead to very tight constraints on the model parameters.
-Further priors are needed.
-Detailed stellar population analyses of the spectra taken along J1331's major axis could possibly support or contradict the suspicion of the existence of stellar mass-to-light ratio gradients in J1331.
+(According to Figure \ref{fig:lenscompareboth} the lensing result might not predict a mass to light ratio gradient inside $R_\text{ein}$, but then again the mass slope $alpha=1$ was only weakly constrained.) The disk of J1331 has a lower $\Upsilon_\text{I,*}$ than the bulge (see Table \ref{tab:previousresults} according to \citet{SWELLSI}).
+Such a drop in $\Upsilon_\text{I,*}$ at the transition region from bulge to disk around $\sim 5$ arcsec could lead to the observed drop in $v_\text{rms}$, while an increasing contribution of a lower mass dark matter halo at larger radii as found by \citet{SWELLSV}, would recover the kinematics in the out regions of J1331's disk.\\
 

### 2015-09-08 docs/discussion_merger_v1.01.tex
Started writing discussion of possible minor merger.

@@
 
-[TO DO]
+\paragraph{TO DO: Stuff to mention}
+\begin{itemize}
+\item J1331 has a counter-rotating stellar component.
+\item suggests that there was a process where two components with angular momenta oriented in opposite directions were involved
+\item 1. scenario: accretion of gas on retrograde orbits and subsequent star formation
+\item --> counter-rotating component is younger than the rest of the galaxy
+\item argument against: To form enough stars such taht the net rotation of the large and massive core is retrograde, a very large amount of gas would have had to be accreted - which is not very likeliy [TO DO" REF: KLEINEBERG 2011]
+\item 2. scenarios: Major mergers of similarly massive galaxies
+\item argument against: major merger products are often quiescent, elliptical galaxies [TO DO: REF: TOOMRE TOOMRE 1972]
+\item 3. sencaro: minor merger
+\item --> dissipationless accretion of a satellite on retrograde orbit [TO DO: REF: KORMENDY 1984] with dense core to survive and spiral to core due to tidal friction
+\item --> counter-rotating component would be younger, as star formation in low-mass satellite galaxies occurs later [TO DO: REF]
+\item if the counter-rotating component is younger needs to be tested by detailed stellar population analysis
+\item Minor merger effects in elliptical galaxies have been studied e.g. by [TO DO:REF: BALCELLS AND QUINN 1990]
+\item large bulges of sporals or ellipticals are reddest in the center and become bluer further out
+\item Satellite nucleus settling in the core of the larger galaxy could caus a reverse color gradient
+\item Normally this gradient is only weak, but there are exceptions [TO DO: CAROLLO 1997].
+\item A second effect of the minor merger could be a misalignement of the photometric and kinematic major axis
+\end{itemize}
+
+\subsection{Future Work}
+
+Standard JAM modelling approaches seem not to work for J1331.
+A JAM model for J1331 would need to allow for stellar mass-to-light ratio gradients within the galaxy, velocity anisotropy and a dark matter halo.
+Because of degeneracies between stellar and dark mass, and matter distribution and anisotropy profile, such a dynamical model would not lead to very tight constraints on the model parameters.
+Further priors are needed.
+Detailed stellar population analyses of the spectra taken along J1331's major axis could possibly support or contradict the suspicion of the existence of stellar mass-to-light ratio gradients in J1331.
+
+\paragraph{Model Failures}
+\begin{itemize}
+\item Assumption of axisymmetry is not true anymore
+\item [TO DO: more]
+\end{itemize}

### 2015-09-08 docs/model_JAM_v1.01.tex
Started writing discussion of possible minor merger.

@@
 \\The JAM modelling approach by \citet{Cap08} makes use of expressing the tracer density and the mass density as MGEs (see also \citet{1994A&A...285..723E}).
-The density of stellar tracers is assumed to be proportional to the observed and deprojected brightness distribution $\nu(R,z)$ in Eq.
-(\ref{eq:deprojMGE}).
+The density of stellar tracers is assumed to be proportional to the observed and deprojected brightness distribution $\nu(R,z)$ in Equation \ref{eq:deprojMGE}.
 The mass density $\rho(R,z)$ consists of several sets of MGEs: One MGE, that is usually taken to be $\nu(R,z)$ multiplied by a constant stellar mass-to-light ratio $\Upsilon_*$, describes the distribution of stellar mass in the galaxy.
@@
 \begin{eqnarray}
-&&\left(I \langle v_\text{los}^2\rangle\right)(x',y')\\
+&&\left(I \langle v_\text{los}^2\rangle\right)(x',y')\nonumber\\
 &&= 4 \pi^{3/2} G \int_0^1 \sum_{k=1}^N \sum_{j=1}^M \nu_{0,k} \ q_j \ \rho_{0,j} \ u^2\nonumber\\
-&& \times \frac{\sigma_k^2 \ q^{2}_k \left( \cos^2 i + \frac{\sin^2 i}{1-\beta_{z,k}}\right) + \mathscr{D} \  {x'}^{2} \sin^2 i}{(1-\mathscr{C}u^2) \sqrt{(\mathscr{A} + \mathscr{B} \cos^2 i) \left[1-(1-q^{2}_j) u^2 \right]}}\label{eq:explicitLOSvelCap}\\
-&& \times \exp\left\{- \mathscr{A} \left[{x'}^{2} + \frac{(\mathscr{A}+\mathscr{B}) \ {y'}^{2}}{\mathscr{A}+\mathscr{B}\cos^2 i}\right] \right\} \diff u, \\
+&& \times \frac{\sigma_k^2 \ q^{2}_k \left( \cos^2 i + \frac{\sin^2 i}{1-\beta_{z,k}}\right) + \mathscr{D} \  {x'}^{2} \sin^2 i}{(1-\mathscr{C}u^2) \sqrt{(\mathscr{A} + \mathscr{B} \cos^2 i) \left[1-(1-q^{2}_j) u^2 \right]}}\nonumber\\
+&& \times \exp\left\{- \mathscr{A} \left[{x'}^{2} + \frac{(\mathscr{A}+\mathscr{B}) \ {y'}^{2}}{\mathscr{A}+\mathscr{B}\cos^2 i}\right] \right\} \diff u, \label{eq:explicitLOSvelCap}
 \end{eqnarray}
@@
 
-\paragraph{Data comparison.} As data we use stellar line-of-sight rotation velocities $v_\text{rot} \equiv \langle v_\text{los} \rangle$ [TO DO: consistent, los or rot] and velocity dispersions $\sigma$ as described in \S\ref{sec:data}.
-The JAM models give us a prediction for the second line-of-sight velocity moment $v_\text{los}$.
+\paragraph{Data comparison.} As data we use stellar line-of-sight rotation velocities $v_\text{rot} \equiv \langle v_\text{los} \rangle$ [TO DO: consistent, los or rot] and velocity dispersions $\sigma$ as described in Section \ref{sec:data}.
+The JAM models give us a prediction for the second line-of-sight velocity moment $\langle v_\text{los}^2 \rangle$.
 The root mean square (rms) line-of-sight velocity $v_\text{rms}$ allows a data-model comparison by relating theses velocities according to
@@
 \end{equation*}
-The model in Eq.
-[TO DO] predicts the intrinsic $\langle v_\text{los}^2 \rangle$ at a given position on the sky, which have then to be modified to model the mode of observation, to be comparable to the measurements.
-The measured $v_\text{rms}$ is a light-weighted mean for a pixel along the long-slit of the spectrograph, with height $L_y = 1$ arcsec \citep{SWELLSV} and a certain given extent in along the major axis, $L_x$, i.e.
+The model in Equation \ref{eq:explicitLOSvelCap} predicts the intrinsic $\langle v_\text{los}^2 \rangle$ at a given position on the sky, which have then to be modified according to the mode of observation, to be comparable to the measurements.
+The measured $v_\text{rms}$ is a light-weighted mean for a pixel along the long-slit of the spectrograph, with height $L_y = 1$ arcsec \citep{SWELLSV} and a certain given extent in along the galaxy's major axis, $L_x$, i.e.
 for a rectangular aperture
 \begin{equation*}
-\text{AP}(x,y) = \left\{ \begin{array}{ll} 1 & \text{for } -\frac{L_x}{2} \leq x \leq + \frac{L_x}{2} \text{ and } - \frac{L_y}{2} \leq y \leq + \frac{L_y}{2}  \\ 0 & \text{otherwise} \end{array} \right.
-.
+\text{AP}(x,y) = \left\{ \begin{array}{ll} 1 & \text{for } -\frac{L_x}{2} \leq x \leq + \frac{L_x}{2}\\
+& \text{and } - \frac{L_y}{2} \leq y \leq + \frac{L_y}{2}  \\ 0 & \text{otherwise.} \end{array} \right.
 \end{equation*}
-The light arriving at the spectrograph itself was subject to seeing, i.e. a Gaussian 
+The light arriving at the spectrograph itself was subject to seeing, i.e. a Gaussian with Full Width Half Maximum (FWHM) of1.1 arcsec \citep{SWELLSV}
 \begin{equation*}
-\text{PSF}(x,y)=\mathscr{N}(0,FWHM/2\sqrt{2\ln2})
+\text{PSF}(x,y)=\mathscr{N}(0,\text{FWHM}/2\sqrt{2\ln2}).
 \end{equation*}
-with FWHM=1.1 arcsec  \citep{SWELLSV}. The model predictions have therefore to be convolved with the convolution kernel
+The model predictions have therefore to be convolved with the convolution kernel
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-If provided with with the convolution kernel, the JAM code by \citet{Cap08} [TO DO: reference code] performs the convolution numerically.
+If provided with the convolution kernel, the JAM code by \citet{Cap08} [TO DO: reference code] performs the convolution numerically.
 We set $L_x = 0.21$ arcsec as the width of the model pixel, and get a prediction for the actual measurements in bins of width 0.63, 1.26 and 1.89 arcsec \citep{SWELLSV} as light-weighted mean from each 3, 6 and 9 model pixels.
@@
 \end{equation}
-We find $\kappa'$ by matching the model $\langle v_\text{los} \rangle$ with the symmetrized $v_\text{rot}$ data, where for a given $\kappa'$ the $\kappa_k$ are found from fitting the MGE generated profile $\kappa(R) = \sum_k \kappa_k \nu_k(r)/\sum_k \nu_k(r)$ to Eq.
-(\ref{eq:kappa_profile}).
+We find $\kappa'$ by matching the model $\langle v_\text{los} \rangle$ with the symmetrized $v_\text{rot}$ data, where for a given $\kappa'$ the $\kappa_k$ are found from fitting the MGE generated profile $\kappa(R) = \sum_k \kappa_k \nu_k(r)/\sum_k \nu_k(r)$ to Equation \ref{eq:kappa_profile}.
 The observed zero point is at $R'_0\approx 2$ arcsec.

### 2015-09-08 docs/results_JAMwithNFW_v1.01.tex
Finished discussion on stellar mass-to-light ratios.
Started writing discussion of possible minor merger.

@@
-\subsection{JAM with a NFW Dark Matter Halo}
+\subsection{JAM with a NFW Dark Matter Halo} \label{sec:results_JAM_NFW}
 
@@
 to exclude very unrealistic anisotropies. The full prior used is then
-\begin{equation*}
-p(\Upsilon_{I,*},R_\text{S,NFW},v_{200},\beta) = \frac{1}{\ln\left( 10 R_{s,NFW}\right)} p(\log c_{200} \mid v_{200}) \cdot p(v_{200}) \cdot p(\beta), 
-\end{equation*}
+\begin{eqnarray*}
+&&p(\Upsilon_{I,*},R_\text{S,NFW},v_{200},\beta) \\
+&&= \frac{1}{\ln\left( 10 R_{s,NFW}\right)} p(\log c_{200} \mid v_{200}) \cdot p(v_{200}) \cdot p(\beta), 
+\end{eqnarray*}
 where the factor $1/\ln\left( 10 R_{s,NFW}\right)$ is the Jacobian of the transformation from the halo parameters $(v_{200},\log c_{200})$ [TO DO: introduce concentration] to $(v_{200},R_{s,NFW})$.
@@
 We also include the Einstein mass $M(<R_\text{ein}$ with a 10\% error as an additional constraint in the fit.
+[TO DO: Didn't include the results from the Moster 2010 relation, because they where quite close to the Dutton 2010 relation anyway.
+Or should I?]
 
@@
 Overplotted are also the priors used to constrain the NFW halo.
-The best fit parameters are summarized in Table \ref{tab:modelB4_bestfit}.
-We find that the best fit NFW halo strives to be more massive and with a higher concentration than  proposed by the prior.
-At the same time the model prefers again very negative velocity anisotropies; the sample with the highest probability is pegged at the lower limit of the prior.
+The mean parameters are summarized in Table \ref{tab:modelB4_bestfit}.
+We find that the best fit NFW halo strives to be more massive and with a higher concentration (due to a smaller $R_\text{s,NFW}$) than  proposed by the prior.
+At the same time the model prefers again very negative velocity anisotropies: The sample with the highest probability is pegged at the lower limit of the unifrom prior.
 Both, the concentrated halo and the low anisotropy are needed to reproduce the central dip of the $v_\text{rms}$ curve.
-[TO DO: Rewrite.
-Not very good.]
-
-The first panel in Figure \ref{fig:modelB4_vrot} shows the mean best fit values from Table \ref{tab:modelB4_bestfit}.
+There are slight covariances between $\Upsilon_{I,*}$,  $R_\text{s,NFW}$ and $\beta_z$: The smaller the dark matter contribution in the center (i.e.
+the larger $\Upsilon_{I,*}$ [TO DO: make sure, mass-to-light ratio is everywhere named properly]), the less concentrated is the halo (i.e.
+the larger $R_\text{s,NFW}$), the more velocity anisotropy is needed to reproduce the central dip.
+As the effect of $v_{200}$ is mostly at larger radii, this parameter doesn't show any covariances - but is also mostly constrained by the prior.
+The $v_\text{rms}$ curve corresponding to the mean best fit values from Table \ref{tab:modelB4_bestfit} is shown in the first panel of Figure \ref{fig:modelB4_vrot}.
+Figure \ref{fig:modelB4_models} illustrates the range of parameters fitting the data according to the full posterior probability function.
+The model fits the $v_\text{rms}$ data in the inner regions quite well (Figure \ref{fig:modelB4_vrms}) and is also consistent with the Einstein mass (see Figure \ref{fig:modelB4_enclMass}).
+The extrapolation of the model to larger radii however overestimates the data, does not exhibit a drop around $\sim 6$ arcsec at all and seems to be therefore overall too massive.\\
 
 We also fitted a model with a cored logarithmic dark matter halo.
-The cored halo models are in general slightly less massive than the NFW halo and therefore fitt the outer regions of J1331 better.
+The cored halo models are in general slightly less massive than the NFW halo and therefore fit the outer regions of J1331 better.
 However, the density profile of the cored halo as well as the I-band light distribution within the plane drop as $\rho(r) \propto r^{-2}$, there is a strong degeneracy between the stellar mass and the dark matter.
@@
 
-\begin{table}
+\begin{table*}
 \centering
@@
 \label{tab:modelB4_bestfit}
-\end{table}
+\end{table*}
 

### 2015-09-09 docs/introduction_v1.02.tex
Finished introduction (references still missing).

\section{Introduction}

%Intro
Gravitational lensing and dynamical modelling provide independent constraints on the mass distribution of galaxies. Combining them allows for valuable cross-checking opportunities to resolve degeneracies inherent in both methods. It can also help to disentangle the stellar and dark matter content of galaxies, of which the latter is still shrouded by many open questions.\\

%Dark Matter
The flat rotation curves of galaxies (deduced from e.g. the stellar movements in the solar neighbourhood \citep{1932BAN.....6..249O} and $H\alpha$ rotation curves in external galaxies \citep{1978ApJ...225L.107R}) were the first indication that galaxies might reside in massive, almost spherical halos made of invisible ``dark'' matter. The standard model of cosmology, based on results by the Planck Mission [TO DO: REF], predicts that $\sim 85\%$ of the universe's total matter content is in the form of non-baryonic cold dark matter. Simulations suggest that this kind of dark matter forms cuspy halos following a Navarro-Frenck-White (NFW) profile \citep{NFW96}. However, central dark matter density cusps are not observed in dark matter dominated dwarf galaxies [TO DO: REF]. If they exist in more massive galaxies depends strongly on stellar mass-to-light ratio [TO DO: REF]. Overall, observations suggest cored dark matter halos. This discrepancy, known as the core-cusp problem, might be due to a yet unknown interaction between dark matter and baryons [TO DO: REF].\\

Determining the overall mass distribution in massive galaxies and separating the dark from the stellar mass components is therefore a crucial step in better understanding the structure of galaxies and nature or dark matter.\\

%Lensing
Strong gravitational lensing is an independent method to tightly constrain the projected total mass of galaxies inside $\sim 1$ arcsec [TO DO: REF]. Massive galaxies can act as gravitational lenses and deflect the light of background sources, giving rise to multiple distorted images of the source [TO DO: REF]. By 2010 over 200 strong gravitational galaxy lenses had been discovered \citep{2010ARA&A..48...87T} and the number is still rising.\\

%Dynamical modelling
The mass profile at larger galactocentric radii can be probed by gas rotation curves that directly measure the galaxy's circlar velocity profile [TO DO: REF]. However, due to its dissipative nature, gas motions are very sensitive to disturbances by e.g. spiral arms and bars [TO DO: REF].\\
Very good and dissipationless dynamical tracers for the underlying gravitational potential are the stars. Their motions are complex, a bulk rotation around one principal axis combined with random motions in all coordinate directions, full dynamical modelling of rotation, dispersion and velocity anisotropies is needed to deduce the matter distribution. An example is axisymmetric Jeans modelling, which solves the Jeans equations for an assumed mass distribution and velocity anisotropy under the assumption of axisymmetry (e.g. \citealt{Cap08}). Degeneracies between stellar and dark matter and velocity anisotropy have to be resolved using additional assumptions.\\
Another dynamical modelling method often applied to external galaxies is e.g. Schwarzschild's orbital superposition approach \citep{schwarzschild}.\\
Because stars are present almost everywhere in the galaxy, stellar dynamical modelling can complement mass constraints from lensing at small and gas motions at large radii.\\

The Sloan WFC Edge-on Late-type Lens Survey (SWELLS, WFC = Wide field camera) \citep{SWELLSI,SWELLSII,SWELLSIII,SWELLSIV,SWELLSV,SWELLSVI} is dedicated to find and investigate spiral galaxies, seen almost edge-on so rotation curves can be easily measured, that are also strong gravitational lenses. By combining lensing and dynamical modelling degeneracies inherent in both methods can be broken. SWELLS picked galaxies in SDSS whose spectra had two different redshifts within 3 arcsec, which makes it likely to capture strong lenses with typical Einstein radii of 1 arcsec. Sufficiently inclined galaxies were picked by eye. Follow up high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) was performed to confirm their lensing status \citep{SWELLSI}.\\

%Characteristics of J1331
One of the SWELLS galaxies is SDSS J1331+3638, to which we refer as J1331 in the remainder of this work. It is a spiral galaxy of approximate Hubble type Sb at right ascension = 202.91800$^\circ$ and a declination = 36.46999$^\circ$ (epoch J2000). It has bluish spiral arms and a large reddish bulge (see Figures \ref{fig:F450W} and \ref{fig:F814W}), which is superimposed by quadruplet of extended bluish images approximately at a distance of 1 arcsec from the galaxy center (see Figure \ref{fig:lens_just_imgpos}). The lensed object might be a star-forming blob of a background galaxy. J1331 stands out of the SWELLS sample because of its large counter-rotating core (see Figure \ref{fig:kinematics}), which might be an indication that J1331 underwent a minor merger in its past.\\

%Previous results
\citet{SWELLSI} confirmed that J1331 was a strong gravitational lens, measured its apparent brightness and estimated the stellar masses of disk and bulge. The lensing properties of J1331 were first analysed by \citet{SWELLSIII}. \citet{SWELLSV} measured the gas and stellar kinematics along the major axis and deduced J1331's mass profile from the gas rotation curve at large radii and total mass inside the Einstein radius from gravitational lensing, focusing mostly on the outer regions of J1331.

%Goal of this work
The goal of this work is to complement the previous work on J1331 by an in-depth analysis of the matter distribution in J1331's inner regions. We use stellar dynamical Jeans modelling in addition to lensing constraints, similar to a study of the Einstein Cross by \citet{GlennEC}. We attempt to disentangle the stellar and dark matter components and test if Jeans modelling works also in the presence of a counter-rotating core. Ideally this work on J1331 could also help understanding how minor mergers modify the mass distribution of a galaxy.\\

This paper is organized as follows: Section \ref{sec:Modelling} gives an overview of the modelling techniques used in this work, Section \ref{sec:data} summarizes the data and Section \ref{sec:Results} presents our results on the surface photometry of J1331 using Multi-Gaussian expansions (Section \ref{sec:MGE_results}), constraints from lensing (Section \ref{sec:results_lensing}) and Jeans modelling based on the surface brightness only (Section \ref{sec:results_JAM_SB}) and including a NFW dark matter halo (Section \ref{sec:results_JAM_NFW}). Finally Section \ref{sec:Discussion} uses the result to discuss J1331's stellar mass-to-light ratio and possible merger history and starting points for future work.

%\paragraph{Methods}
%\begin{itemize}
%\item lensing: fitting scale-free galaxy model to image positions \citep{EvansWitt}
%\item photometry: MGE expansion of surface brightness in the F814W filter (deconvolution with PSF), apparent magnitude, total luminosity, effective radius
%\item Jeans modelling: jeans axisymmetric modelling (JAM) by \citet{Cap08} to fit model predictions for the second velocity moments to the stellar kinematics data
%\end{itemize}

%============================================================================

\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/first_glimpse_450.ps}
  \caption{J1331 in F450W ("blue")}
  \label{fig:F450W}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/first_glimpse_814.ps}
  \caption{J1331 in F814W ("red")}
  \label{fig:F814W}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_imgpos.ps}
  \caption{The lensing images}
  \label{fig:lens_just_imgpos}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/stellar_kinematics_data.ps}
  \caption{Stellar Kinematics by \citet{SWELLSV}}
  \label{fig:kinematics}
\end{subfigure}
\caption{Hubble Space telescope (HST) images and stellar kinematics of the galaxy SDSS J1331+3638 (J1331), which has a large counter-rotating core and whose bulge acts as a strong lens for a bluish background source. \emph{Panel (a) and (b):} HST/WFPC2/WFC3 images of J1331 by \citet{SWELLSI} in two filters, F450W in panel (a) and F814W in panel (b). The galaxy's coordinates on the sky are right ascension $\alpha$ = 202.91800$^\circ$ and declination $\delta$ = 36.46999$^\circ$ (epoch J2000). Image orientation and scaling are indicated in panel (a); the scaling transformation from arcseconds to the physical size of the galaxy in kpc uses the galaxy's redshift $z_d = 0.113$ \citep{SWELLSIII} (i.e. assumes an angular diameter distance of 414 Mpc). The color scaling of these two images is the same. The black solid line in panel (b) shows the orientation of the major-axis. The line has a length of 10 arcsec and indicates the region within which we carry out the Jeans modelling. [TO DO: NOT ALL THE TIME.???????] \emph{Panel (c):} The central region of J1331 in F450W, surface brightness subtracted. An IRAF ellipse ???? fit to the F450W surface brightness in panel (a) was subtracted from the image. The (smoothed) residuals within the white square in panel (a) are shown in panel (c). Four bright blobs (A,B,C and D) become visible, which are arranged in a typical strong lensing configuration around the center of the galaxy (G). \emph{Panel (d):} Stellar Kinematics along the galaxy's major axis as measured by \citet{SWELLSV}, line-of-sight rotation velocity $v_\text{rot}$, line-of-sight velocity dispersion $\sigma$ and the rms-velocity $v_\text{rms} = \sqrt{v_\text{rot}^2 + \sigma^2}$. The dotted line in panel (b) indicates the galaxy's effective half-light radius (in the F814W filter), $R_\text{eff} = 2.6" = 5.2$ kpc. The $v_\text{rot}$ curve reveals that J1331 is counter-rotating within $R_\text{eff}$. [TO DO: Add (x,y) axis in figure b).???????]}
\label{fig:specialJ1331}
\end{figure*}

### 2015-09-11 archive/abstract_v1.01.tex
Added archive folder.

--- 2015-08-11 docs/abstract_v1.01.tex
@@
 By fitting a gravitational potential model to the image positions, we constrain the mass inside the Einstein radius ($R_\text{ein}=0.91\pm0.02$ arcsec) to within 4\% ($M_\text{ein} = (7.8\pm0.3) \cdot 10^{10} M_\odot$).
-From Multi-Gaussian Expansions (MGE) of J1331's surface brightness distribution we find that J1331 has an apparent I-band magnitude of $m_I \simeq 15.8$ mag, a total luminosity of $L_{I,tot} \simeq 5.6 \cdot 10^{10}L_{I,\odot}$ and an effective radius of $R_\text{eff} \simeq 2.6$ arcsec = 5.6 kpc.
+From Multi-Gaussian Expansions (MGE) of J1331's surface brightness distribution we find that J1331 has a total luminosity of $L_{I,tot} \simeq 5.6 \cdot 10^{10}L_{I,\odot}$ and an effective radius of $R_\text{eff} \simeq 2.6$ arcsec = 5.6 kpc.
+[TO DO: apparent brightness is boring, right?]
 

### 2015-09-11 docs/data_v1.01.tex
Removed some TO DOs.

@@
 \paragraph{Redshift.} [TO DO: WHO???] found from SDSS spectra that J1331 has two redshifts inside 1 arcsec: The smaller one, $z_d = 0.113$, is the redshift of J1331 itself, the larger one, $z_s = 0.254$, is the redshift of the lensed background source \citep{SWELLSIII}.
-According to its redshift and the WMAP5 [TO DO: CHECK] cosmology \citep{WMAP5cosm}, J1331 has an angular diameter distance of 414 Mpc, which translates into a transverse scaling of 1 arcsec $\hat{=}$ 2.01 kpc.
+According to its redshift and the WMAP5 [TO DO: Explain?] cosmology \citep{WMAP5cosm}, J1331 has an angular diameter distance of 414 Mpc, which translates into a transverse scaling of 1 arcsec $\hat{=}$ 2.01 kpc.
 
@@
 The rotation curve reveals a counter-rotating core within 2 arcsec $\simeq$ 4 kpc.
-Outside of $\sim 3.5 arcsec$ there is a steep drop in the dispersion, which is exptected at the boundary between the pressure supported bulge and the rotationally supported disk, which appears around this radius in the F450W filter in Figure \ref{fig:F450W}.
+Outside of $\sim 3.5$ arcsec there is a steep drop in the dispersion, which is exptected at the boundary between the pressure supported bulge and the rotationally supported disk, which appears around this radius in the F450W filter in Figure \ref{fig:F450W}.
 However, in the brighter F814W filter in Figure \ref{fig:F814W}  the large reddish bulge extends out to $\sim$5 arcsec.
 \\Inside of $\sim 4$ arcsec, the data appears to be symmetric, outside of this the assumption of axisymmetry seems not to be valid anymore, considering the data.
-We add -2.3 km/s to the $v_\text{rot}$ to ensure $v_\text{rot}(R=0) \sim 0$ as a possible correction term for a systematic misjudgement of the systemic velocity.
+We add -2.3 km/s to the $v_\text{rot}$ to ensure $v_\text{rot}(R'=0) \sim 0$ as a possible correction term for a systematic misjudgement of the systemic velocity.
 We also symmetrize the data within 4 arcsec and asign a minimum error of $\delta v_\text{rms} > 5$ km/s to the $v_\text{rms}$ data.

### 2015-09-11 docs/discussion_ML_v1.02.tex
Finished introduction (references still missing).
Removed some TO DOs.

@@
 An alternative JAM model was introduced in Section \ref{sec:results_JAM_SB}, where we used the surface brightness distribution without a halo component but together with an increasing mass-to-light ratio.
-We found that such a model would be perfectly consistent with the lensing results and predict a total mass-to-light ratio in the center of J1331 of  $\Upsilon_\text{I,tot}(R\sim0) = 2.53$.
+We found that such a model would be perfectly consistent with the lensing results and predict a total mass-to-light ratio in the center of J1331 of  $\Upsilon_\text{I,tot}(R'\sim0) = 2.53$.
 This is very close to the stellar mass-to-light ratio we got from \citet{SWELLSI} estimates of the bulge's stellar mass using the Chabrier IMF $\Upsilon_\text{I,*}^\text{Chabrier} = 2.5 \pm 0.6$, i.e.
@@
 
-[TO DO: Einheitlich: $Upsilon_{I,*}^{comment}$, $\Upsilon_\text{I,tot}^\text{ein}$]
+[TO DO: Einheitlich: $\Upsilon_{I,*}^{comment}$, $\Upsilon_\text{I,tot}^\text{ein}$]
+
+[TO DO: Why are disk and bulge mass in SWELLS I different to the one in SWELLS IV??]
 

### 2015-09-11 docs/introduction_v1.02.tex
Removed some TO DOs.

@@
 the stellar movements in the solar neighbourhood \citep{1932BAN.....6..249O} and $H\alpha$ rotation curves in external galaxies \citep{1978ApJ...225L.107R}) were the first indication that galaxies might reside in massive, almost spherical halos made of invisible ``dark'' matter.
-The standard model of cosmology, based on results by the Planck Mission [TO DO: REF], predicts that $\sim 85\%$ of the universe's total matter content is in the form of non-baryonic cold dark matter.
+The standard model of cosmology, based on results by the Planck Mission \citep{WMAP5cosm}, predicts that $\sim 85\%$ of the universe's total matter content is in the form of non-baryonic cold dark matter.
 Simulations suggest that this kind of dark matter forms cuspy halos following a Navarro-Frenck-White (NFW) profile \citep{NFW96}.
@@
 The line has a length of 10 arcsec and indicates the region within which we carry out the Jeans modelling.
-[TO DO: NOT ALL THE TIME.???????] \emph{Panel (c):} The central region of J1331 in F450W, surface brightness subtracted.
-An IRAF ellipse ????
-fit to the F450W surface brightness in panel (a) was subtracted from the image.
+\emph{Panel (c):} The central region of J1331 in F450W, surface brightness subtracted.
+An IRAF ellipse [TO DO: How to write and reference????] fit to the F450W surface brightness in panel (a) was subtracted from the image.
 The (smoothed) residuals within the white square in panel (a) are shown in panel (c).
@@
 The $v_\text{rot}$ curve reveals that J1331 is counter-rotating within $R_\text{eff}$.
-[TO DO: Add (x,y) axis in figure b).???????]}
+[TO DO: Projected radius $R'$ on x-axis in panel d).] [TO DO: Add (x,y) axis in figure b).???????]}
 \label{fig:specialJ1331}

### 2015-09-11 docs/model_JAM_v1.01.tex
Removed some TO DOs.

@@
 The density of stellar tracers is assumed to be proportional to the observed and deprojected brightness distribution $\nu(R,z)$ in Equation \ref{eq:deprojMGE}.
-The mass density $\rho(R,z)$ consists of several sets of MGEs: One MGE, that is usually taken to be $\nu(R,z)$ multiplied by a constant stellar mass-to-light ratio $\Upsilon_*$, describes the distribution of stellar mass in the galaxy.
-(To mimick gradients of mass-to-light ratio, each Gaussian could be assigned its own $\Upsilon_{*,i}$.) To add a Navarro-Frenck-White (NFW) \citep{Navarro+1995c,NFW96} dark matter halo component, a MGE generated from a fit to a NFW profile can be added to the stellar component.
-[TO DO: Maybe remove detailed description of the mass MGE here, if it is described in detail somewhere else.] The gravitational potential is generated from the mass MGE by integrating the Poisson equation \citep{1994A&A...285..723E}.
+The mass density $\rho(R,z)$ can consist of several sets of MGEs, describing stellar and dark matter components.
+The gravitational potential is generated from the mass MGE by integrating the Poisson equation \citep{1994A&A...285..723E}.
 Equations \ref{eq:Jeans1} and \ref{eq:Jeans2} together with \ref{eq:bz} provide the velocity dispersion tensor $\langle v_i v_j \rangle = \langle v_i^2 \rangle$ (with $i,j \in \{ R,\phi, z\}$).
@@
 
-[TO DO: make primed and unprimed coordinate systems clear.]
-
 \paragraph{Data comparison.} As data we use stellar line-of-sight rotation velocities $v_\text{rot} \equiv \langle v_\text{los} \rangle$ [TO DO: consistent, los or rot] and velocity dispersions $\sigma$ as described in Section \ref{sec:data}.
@@
 \begin{equation*}
-\text{AP}(x,y) = \left\{ \begin{array}{ll} 1 & \text{for } -\frac{L_x}{2} \leq x \leq + \frac{L_x}{2}\\
-& \text{and } - \frac{L_y}{2} \leq y \leq + \frac{L_y}{2}  \\ 0 & \text{otherwise.} \end{array} \right.
+\text{AP}(x',y') = \left\{ \begin{array}{ll} 1 & \text{for } -\frac{L_x}{2} \leq x' \leq + \frac{L_x}{2}\\
+& \text{and } - \frac{L_y}{2} \leq y' \leq + \frac{L_y}{2}  \\ 0 & \text{otherwise.} \end{array} \right.
 \end{equation*}
-The light arriving at the spectrograph itself was subject to seeing, i.e. a Gaussian with Full Width Half Maximum (FWHM) of1.1 arcsec \citep{SWELLSV}
+The light arriving at the spectrograph itself was subject to seeing, i.e. a Gaussian with Full Width Half Maximum (FWHM) of 1.1 arcsec \citep{SWELLSV}
 \begin{equation*}
-\text{PSF}(x,y)=\mathscr{N}(0,\text{FWHM}/2\sqrt{2\ln2}).
+\text{PSF}(x',y')=\mathscr{N}(0,\text{FWHM}/2\sqrt{2\ln2}).
 \end{equation*}
@@
 \begin{eqnarray*}
-K(x,y) &=& (\text{PSF} \ast \text{AP})(x,y) \\
-&=& \frac{1}{4} \prod_{u \in \{x,y\}} \left[ \text{erf}\left( \frac{L_u/2 - u}{\sqrt{2}\sigma_\text{seeing}}\right) + \text{erf} \left( \frac{L_u/2 + u}{\sqrt{2} \sigma_\text{seeing}} \right) \right]
+K(x',y') &=& (\text{PSF} \ast \text{AP})(x',y') \\
+&=& \frac{1}{4} \prod_{u \in \{x',y'\}} \left[ \text{erf}\left( \frac{L_u/2 - u}{\sqrt{2}\sigma_\text{seeing}}\right) + \text{erf} \left( \frac{L_u/2 + u}{\sqrt{2} \sigma_\text{seeing}} \right) \right]
 \end{eqnarray*}
-and weighted by the surface brightness $I(x,y)$ [TO DO: primed x and y or not????]
+and weighted by the surface brightness $I(x',y')$
 \begin{eqnarray*}
@@
 is then the light-weighted circular velocity curve, given the second velocity moments found from the Jeans equations.
-\\To model the counter-rotating core of J1331 with one free parameter for, we employ the condition that the overall $\kappa(R)$ profile should smoothly and relatively steeply transition from $\kappa(R) = -\kappa' < 0$ at small $R$ [TO DO: Check, ich glaube das hier ist das intrinsische R in Zylinder-Coordinaten] trough $\kappa(R_0) \equiv 0$ and increase to $\kappa(R) = \kappa' > 0$ at large $R$.
+\\To model the counter-rotating core of J1331 with one free parameter for, we employ the condition that the overall $\kappa(R)$ profile should smoothly and relatively steeply transition from $\kappa(R) = -\kappa' < 0$ at small $R$ through $\kappa(R_0) \equiv 0$ and increase to $\kappa(R) = \kappa' > 0$ at large $R$.
 Our imposed profile is

### 2015-09-11 docs/model_MGE_v1.01.tex
Removed some TO DOs.

@@
 We assume all Gaussians to have the same center and position angle $\phi$, i.e.
-orientation of w.r.t.
-the $y'$-axis of the coordinate system with polar coordinates $(R',\theta')$ [TO DO: CHECK].
+orientation of the Gaussians' major axis measured counter-clockwise from the $y'$-axis of the coordinate system with polar coordinates $(R',\theta')$.
 Then the surface brightness can be written as
@@
 \begin{equation}
-\text{PSF}(x,y) = \sum_j \frac{G_j}{2 \pi \delta_j^2} \exp\left[- \frac{1}{2 \delta_j^2} \left(x^2 + y^2 \right)\right], \label{eq:PSFgeneral}
+\text{PSF}(x',y') = \sum_j \frac{G_j}{2 \pi \delta_j^2} \exp\left[- \frac{1}{2 \delta_j^2} \left({x'}^2 + {y'}^2 \right)\right], \label{eq:PSFgeneral}
 \end{equation}
 where $\sum_j G_j = 1$ and $\delta_j$ are in this case the dispersions of the circular PSF Gaussians.
-In this case the observed surface brightness distribution is a convolution of the intrinsic surface brightness in Eq.
-(\ref{eq:MGEgeneral}) with the PSF in Eq.
-(\ref{eq:PSFgeneral}): $(I \ast \text{PSF}) (x',y')$ is then again a sum of Gaussians and can be directly fitted to an image of the galaxy in question.
+In this case the observed surface brightness distribution is a convolution of the intrinsic surface brightness in Equation \ref{eq:MGEgeneral} with the PSF in Equation \ref{eq:PSFgeneral}: $(I \ast \text{PSF}) (x',y')$ is then again a sum of Gaussians and can be directly fitted to an image of the galaxy in question.
 

### 2015-09-11 docs/model_lensing_v1.02.tex
Removed some TO DOs.

--- 2015-08-04 docs/model_lensing_v1.01.tex
@@
 \begin{equation}
-\psi(\vec{\theta}) := \frac{D_{ds}}{D_d D_s} \frac{2}{c^2} \int \Phi(\vec{r}=D_d \vec{\theta},z) {\ \mathrm d} z, \label{eq:psidef}
+\psi(\vect{\theta}) := \frac{D_{ds}}{D_d D_s} \frac{2}{c^2} \int \Phi(\vect{r}=D_d \vect{\theta},z) {\ \mathrm d} z, \label{eq:psidef}
 \end{equation}
-where $\vec{\theta}$ is a 2-dimensional vector on the plane of the sky. The light from the source at $\vec{\beta} = (\xi,\eta)$ is deflected according to the lens equation
+where $\vect{\theta}$ is a 2-dimensional vector on the plane of the sky.
+The light from the source at $\vect{\beta} = (\xi,\eta)$\footnote{$\xi$ and $\eta$ are cartesian coordinates on the plane of the sky.} is deflected according to the lens equation
 \begin{equation}
-\vec{\beta} = \vec{\theta}_i - \left.\vec{\nabla}_\theta \psi(\vec{\theta})\right|_{\vec{\theta}_i} \label{eq:lenseqpot}
+\vect{\beta} = \vect{\theta}_i - \left.\vect{\nabla}_\theta \psi(\vect{\theta})\right|_{\vect{\theta}_i} \label{eq:lenseqpot}
 \end{equation}
-into an image $\vec{\theta}_i = (x_i,y_i)$.
-The gradient of the deflection potential $\vec{\nabla}_\theta \psi(\vec{\theta})$ is equal to the angle by which the light is deflected multiplied by $D_{ds}/D_{s}$.
-\\The total time delay of an deflected light path through $\vec{\theta}$ with respect to the unperturbed light path is given by 
+into an image $\vect{\theta}_i = (x_i,y_i)$.
+The gradient of the deflection potential $\vect{\nabla}_\theta \psi(\vect{\theta})$ is equal to the angle by which the light is deflected multiplied by $D_{ds}/D_{s}$.
+\\The total time delay of an deflected light path through $\vect{\theta}$ with respect to the unperturbed light path is given by 
 \begin{equation}
-\Delta t(\vec{\theta}) = \frac{(1+z_d)}{c} \frac{D_d D_s}{D_{ds}} \left[ \frac 12 (\vec{\theta} - \vec{\beta})^2 - \psi(\vec{\theta})\right], \label{eq:timedelay}
+\Delta t(\vect{\theta}) = \frac{(1+z_d)}{c} \frac{D_d D_s}{D_{ds}} \left[ \frac 12 (\vect{\theta} - \vect{\beta})^2 - \psi(\vect{\theta})\right], \label{eq:timedelay}
 \end{equation}
-\citep{BartGravLens}. According to Fermat's principle the image positions will be observed at the extrema of $\Delta t(\vec{\theta})$.
+\citep{BartGravLens}. According to Fermat's principle the image positions will be observed at the extrema of $\Delta t(\vect{\theta})$.
 \\The inverse magnification tensor
 \begin{equation}
-\mathscr{M}^{-1} \equiv \frac{\partial \vec{\beta}}{\partial \vec{\theta}} \overset{(\ref{eq:lenseqpot})}{=} \left(\delta_{ij} - \frac{\partial^2 \psi}{\partial \theta_i \partial \theta_j} \right)\label{eq:magnificationtensor}
+\mathscr{M}^{-1} \equiv \frac{\partial \vect{\beta}}{\partial \vect{\theta}} \overset{(\ref{eq:lenseqpot})}{=} \left(\delta_{ij} - \frac{\partial^2 \psi}{\partial \theta_i \partial \theta_j} \right)\label{eq:magnificationtensor}
 \end{equation}
@@
 \paragraph{Lens Model.} Following \citet{EvansWitt} we assume a scale-free model
-\begin{equation*}
-\psi(R',\theta) = R^{'\alpha} F(\theta) \label{eq:scalefreemodel}
-\end{equation*}
-for the lensing potential, consisting of an angular part $F(\theta)$ and a power-law radial part, with $(R',\theta)$ being polar coordinates on the plane of the sky.
+\begin{equation}
+\psi(R',\theta') = R^{'\alpha} F(\theta') \label{eq:scalefreemodel}
+\end{equation}
+for the lensing potential, consisting of an angular part $F(\theta')$ and a power-law radial part, with $(R',\theta')$ being polar coordinates on the plane of the sky.
 The case $\alpha = 1$ corresponds to a flat rotation curve.
-We expand $F(\theta)$ into a Fourier series,
+We expand $F(\theta')$ into a Fourier series,
 \begin{equation}
-F(\theta) = \frac{a_0}{2} + \sum_{k=1}^{\infty} \left(a_k \cos(k\theta) + b_k \sin (k\theta) \right). \label{eq:Fourieransatz}
+F(\theta') = \frac{a_0}{2} + \sum_{k=1}^{\infty} \left(a_k \cos(k\theta') + b_k \sin (k\theta') \right). \label{eq:Fourieransatz}
 \end{equation}
@@
 \begin{equation}
-\begin{pmatrix} \xi \\ \eta \end{pmatrix} = \begin{pmatrix} R'_i \cos \theta_i - R_i^{'\alpha-1} \left(\alpha \cos \theta_i F(\theta_i) - \sin \theta_i F'(\theta_i) \right) \\ R'_i \sin \theta_i - R_i^{'\alpha-1} \left(\alpha \sin \theta_i F(\theta_i + \cos \theta_i F'(\theta_i) \right)\end{pmatrix}\label{eq:Fourierlenseq}
+\begin{pmatrix} \xi \\ \eta \end{pmatrix} = \begin{pmatrix} R'_i \cos \theta'_i - R_i^{'\alpha-1} \left(\alpha \cos \theta'_i F(\theta'_i) - \sin \theta'_i F'(\theta'_i) \right) \\ R'_i \sin \theta'_i - R_i^{'\alpha-1} \left(\alpha \sin \theta'_i F(\theta'_i + \cos \theta'_i F'(\theta'_i) \right)\end{pmatrix}\label{eq:Fourierlenseq}
 \end{equation}
-\citep{EvansWitt}, where $F'(\theta) = \partial F(\theta) / \partial \theta$.
-When we fix the slope $\alpha$, then the lens equation is a purely linear problem and can be solved numerically for the source position $(\xi,\eta)$ and the Fourier parameters $(a_k,b_k)$ given one observed image at position $(x_i=R'_i \cos \theta_i,y_i=R'_i \sin \theta_i)$.
+\citep{EvansWitt}, where $F'(\theta') \equiv \partial F(\theta') / \partial \theta'$.
+When we fix the slope $\alpha$, then the lens equation is a purely linear problem and can be solved numerically for the source position $(\xi,\eta)$ and the Fourier parameters $(a_k,b_k)$ given one observed image at position $(x_i=R'_i \cos \theta'_i,y_i=R'_i \sin \theta'_i)$.
+
+\paragraph{Model fitting.} As described above our lensing model has the following free parameters: the source position $(\xi,\eta)$, and the radial slope $\alpha$ and Fourier parameters $(a_k,b_k)$ of the lens mass distribution in Equations \ref{eq:scalefreemodel} and \ref{eq:Fourieransatz}.
+We want to find the lensing model which minimizes for all four images the distance between the observed image positions $\vect{\theta}_{oi}$ and those predicted by the lensing model $\vect{\theta}_{pi}$.
+Because we want to avoid solving the lens equation (see Equations \ref{eq:lenseqpot} and \ref{eq:Fourierlenseq}) for $\vect{\theta}_{pi}$, we follow \citet{1991ApJ...373..354K} and cast the calculation back to the source plane using the magnification tensor in Equation \ref{eq:magnificationtensor} to approximate $\vect{\theta} \simeq (\partial \vect{\theta} / \partial \vect{\beta}) \vect{\beta} = \mathscr{M} \vect{\beta} $ and the $\chi^2_\text{lens}$ that the fit wants to minimize becomes
+\begin{eqnarray*}
+\chi^2_\text{lens} &=& \sum_{i=1}^{4} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right) \left( \vect{\theta}_{pi} - \vect{\theta}_{oi} \right)\right|^2\\
+&\simeq& \sum_{i=1}^{N} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right)  \left.\mathscr{M}\right|_{\vect{\theta}=\vect{\theta}_{oi}} \left( \begin{matrix} \xi - \tilde{\xi}_i \\ \eta - \tilde{\eta}_i \end{matrix} \right) \right|^2,
+\end{eqnarray*}
+where $(\Delta_x,\Delta_y)$ are the measurement errors of the image positions $\vect{\theta}_{oi}$.
+$\left.\mathscr{M}\right|_{\vect{\theta}=\vect{\theta}_{oi}}$ is the magnification tensor and $(\tilde{\xi}_i,\tilde{\eta}_i)$ the source position according to the lens equation, both evaluated at $\vect{\theta}_{oi}$.
+Following \citet{GlennEC} we add a term
+\begin{equation*}
+\chi^2_\text{shape} = \lambda \sum_{k \geq 3} \frac{\left(a_k^2 +b_k^2 \right)}{a_0^2} 
+\end{equation*}
+which forces the shape of the mass distribution to be close to an ellipse. The total $\chi^2$ to minimize is therefore
+\begin{equation*}
+\chi^2 = \chi^2_\text{lens} + \chi^2_\text{shape}
+\end{equation*}
+We set $a_1 = b_1 = 0$, which corresponds to the choice of origin; in this case the center of the galaxy.
+\\To be able to constrain the slope $\alpha$, we would have needed flux ratios for the images as in \citet{GlennEC}.
+But the extended quality of the images, possible dust obscuration and surface brightness fluctuations due to microlensing events, as well as the uncertainty in surface brightness subtraction make flux determination too unreliable and we do not include them in the fitting.

### 2015-09-11 docs/results_JAMwithNFW_v1.01.tex
Removed some TO DOs.

@@
 A dark matter halo in addition to the stellar component could explain these findings.
-We therefore proceed by modelling the mass distribution with a) a stellar component, which we get from the light MGE in Table \ref{tab:MGEF814W} times a constant stellar mass-to-light ratio $\Upsilon_*$), and b) a spherical NFW dark matter component \citep{Navarro+1995c,NFW96}.
+We therefore proceed by modelling the mass distribution with a) a stellar component, which we get from the light MGE in Table \ref{tab:MGEF814W} (deprojected to the intrinsic $\nu(R,z)$) times a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$), and b) a spherical NFW [TO DO: introduce abbreviation somewhere] dark matter component \citep{Navarro+1995c,NFW96}.
 In the JAM modelling we use a 10-Gaussian MGE fit to the classical NFW profile
@@
 \end{equation}
-(their equation 10), with a Gaussian scatter of $\sigma_{\log c_{200}} = 0.105$ (their table A2).
+(their equation 10), with a Gaussian scatter of $\sigma_{\log c_{200}} = 0.105$ (their Table A2).
 
-\paragraph{Modelling.} The full set of fit parameters is $(\Upsilon_{I,*},R_\text{S,NFW},v_{200},\beta)$ [TO DO: $\beta$ or $\beta_0$???] [TO DO: Einheitlich $\Upsilon_{I,*}$????], where $\beta$ is the constant velocity anisotropy parameter (see \S\ref{sec:model_JAM}).
+\paragraph{Modelling.} The full set of fit parameters is $(\Upsilon_{I,*},R_\text{S,NFW},v_{200},\beta)$ [TO DO: $\beta$ or $\beta_0$???] [TO DO: Einheitlich $\Upsilon_{I,*}$????], where $\beta$ is the constant velocity anisotropy parameter (see Section \ref{sec:model_JAM}).
 We will investigate this parameter space with a MCMC \citep{emcee} and use priors for the halo parameters to guide the fit to a realistic NFW halo shape.
@@
 \end{equation*}
-\\We also use the concentration vs. halo mass relation by \citet{Maccio08} in Eq. (\ref{eq:Maccio08}) as a prior on the concentration, i.e.
+\\We also use the concentration vs. halo mass relation by \citet{Maccio08} in Equation \ref{eq:Maccio08} as a prior on the concentration, i.e.
 \begin{equation*}
@@
 Shown are also the priors used for J1331's NFW halo, $\mathscr{N}(200 \text{km/s},40 \text{km/s})$ (green) and the concentration vs.
-halo mass relation by \citet{Maccio08} from Eq.
-(\ref{eq:Maccio08}) in terms of $v_{200}$ vs.
+halo mass relation by \citet{Maccio08} from Equation \ref{eq:Maccio08} in terms of $v_{200}$ vs.
 $R_\text{s,NFW}$ with $1\sigma$ scatter (blue).
@@
 The histograms of the marginalized 1D distributions are overplotted by the mean (black solid lines) and $1\sigma$ error (black dashed lines), whose values are also quoted in the figure and in Table \ref{tab:modelB4_bestfit}.
-The grey diamonds mark a random sub-selection of 12 samples; the corresponding models are shown in Figure \ref{fig:modelB4_models}.}
+The grey diamonds mark a random sub-selection of 12 samples; the corresponding models are shown in Figure \ref{fig:modelB4_models}.
+[TO DO: Rename $\beta_0$ to $\beta_z$, rename $R_\text{s,NFW}$ to $r_\text{s,NFW}$, rename $\Upsilon_*$ to $\Upsilon_{I,*}$]}
 \label{fig:modelB4_triangle}
@@
 \emph{Panel b)} shows the circular velocity curve of the total mass (green), and separately the contribution of the stellar mass (yellow, again generated from the MGE in Table \ref{tab:F814WMGE}) and dark matter (grey).
-\emph{Panel c)} shows the corresponding enclosed mass profile.
+[TO DO: Is this really the spherical $r$?
+I would think it is actually the cylindrical $R$.] \emph{Panel c)} shows the corresponding enclosed mass profile.
 Overplotted is also the Einstein mass at the Einstein radius with a 10\% error, which was used in the fit as an additional constraint.[TO DO: radius benennungen sind irgendwie verrutscht]}
@@
 
-\paragraph{Rotation curve.} Following the procedure in \S\ref{sec:model_JAM} we find the rotation curve from the best fit mean model in Table \ref{tab:modelB4_bestfit} by fitting the rotation parameter $\kappa'$ to the symmetrized $v_\text{rot}$ data within $R' = 3.5$ arcsec.
+\paragraph{Rotation curve.} Following the procedure in Section \ref{sec:model_JAM} we find the rotation curve from the best fit mean model in Table \ref{tab:modelB4_bestfit} by fitting the rotation parameter $\kappa'$ to the symmetrized $v_\text{rot}$ data within $R' = 3.5$ arcsec.
 The best fit with $\kappa' = 0.76$ is shown in the second panel of Figure \ref{fig:modelB4_vrot}.
@@
 \includegraphics[width=0.7\linewidth]{fig/B4_rms_rot_curves_best_model.ps}
-\caption{Generating the rotation curve from the JAM model with NFW halo and constant velocity anisotropy with the mean parameters in Table \ref{tab:modelB4_bestfit} and with the best fit rotation parameter $\kappa' = 0.76$ in Eq.
-(\ref{eq:kappa_profile}) (red solid lines).
+\caption{Generating the rotation curve from the JAM model with NFW halo and constant velocity anisotropy with the mean parameters in Table \ref{tab:modelB4_bestfit} and with the best fit rotation parameter $\kappa' = 0.76$ in Equation \ref{eq:kappa_profile} (red solid lines).
 The second velocity moment in the first panel and the first velocity moment in the second panel with the additional fit parameter $\kappa'$ were fitted to the symmetrized data (solid blue points).
@@
 \end{figure*}
+
+[TO DO: $R_\text{s,NFW}$ is a spherical radius. Should be a small $r_\text{s,NFW}$ everywhere.]

### 2015-09-11 docs/results_JAMwithSB_v1.01.tex
Finished discussion on stellar mass-to-light ratios.
Removed some TO DOs.

@@
-\subsection{JAM based on Surface Brightness}
+\subsection{JAM based on Surface Brightness} \label{sec:results_JAM_SB}
 
 \paragraph{...
-with the Lens Mass Model.} Our first JAM model uses the mass distribution which we found from lensing constraints in \S\ref{sec:results_lensing} to generate an independent prediction for the $v_\text{rms}$ curve following the procedure in \S\ref{sec:model_JAM}.
+with the Lens Mass Model.} Our first JAM model uses the mass distribution which we found from lensing constraints in Section \ref{sec:results_lensing} to generate an independent prediction for the $v_\text{rms}$ curve following the procedure in Section \ref{sec:model_JAM}.
 In addition to the flat rotation curve model with $\alpha = 1$ in Table \ref{tab:bestfitlensmodel}, we also investigate a lens model, which was found as a best fit to the lensing images when assuming a [TO DO: rising or droppint???] rotation curve slope of $\alpha=1.1$.
@@
 The $\alpha = 1$ model fits the wings nicely, while the $\alpha = 1.1$ model recreates almost exactly the observed central dip.
-The sharp drop in $v_\text{rms}$ around $R' \sim 3$ arcsec [TO DO: make sure all projected Rs are $R'$] cannot be reproduced, however.
+The sharp drop in $v_\text{rms}$ around $R' \sim 3$ arcsec cannot be reproduced, however.
 But outside of the Einstein radius our lensing models are only extrapolations and the true constraint is around the Einstein radius.
@@
   \includegraphics[height=6cm]{fig/lensing_JAM_comparision.ps}
-  \caption{Comparison (not a fit!) of the symmetrized stellar $v_\text{rms}$ data of J1331 (blue dots) with JAM models generated from mass distributions which were independently derived from lensing constraints in \S\ref{sec:results_lensing}.
+  \caption{Comparison (not a fit!) of the symmetrized stellar $v_\text{rms}$ data of J1331 (blue dots) with JAM models generated from mass distributions which were independently derived from lensing constraints in Section \ref{sec:results_lensing}.
 The red solid line corresponds to the lens model for a flat rotation curve ($\alpha = 1$) in Table \ref{tab:bestfitlensmodel}; the green line is a best fit lens model found analogously from the image positions, but for a fixed rotation curve slope of $\alpha = 1.1$.
@@
 with "Mass-follows-Light" and Velocity Anisotropy.} Our second JAM model is a mass-follows-light model, which are often used in dynamical JAM modelling (e.g.
-\citet{GlennEC,Cap06}), where the mass distribution ins generated by multiplying the light distribution in Table \ref{tab:MGEF814W} by a constant total mass-to-light ratio  $\Upsilon_{I,\text{tot}}^\text{dyn}$.
+\citet{GlennEC,Cap06}), where the mass distribution ins generated by multiplying the intrinsic light distribution $\nu(R,z)$ (the MGE given in Table \ref{tab:MGEF814W} deprojected according to the inclination) by a constant total mass-to-light ratio  $\Upsilon_{I,\text{tot}}^\text{dyn}$.
 This assumes that the dark matter is always a constant fraction of the total matter distribution everywhere.
@@
 \paragraph{...
-with Increasing Mass-to-Light Ratio.} In \S\ref{sec:results_lensing} we found from the lensing, that the light distribution might drop faster with radius than the mass distribution.
+with Increasing Mass-to-Light Ratio.} In Section \ref{sec:results_lensing} we found from the lensing, that the light distribution might drop faster with radius than the mass distribution.
 This would correspond to a radially increasing total mass-to-light ratio.
 As velocity anisotropy alone cannot explain the observed kinematics in a simple a mass-follows-light model, we now allow for an mass-to-light ratio gradient in the JAM modelling to generate a mass model from the light distribution in Table \ref{tab:MGEF814W}.
-We do this by assigning each of the five Gaussians in the MGE its own mass-to-light ratio and replace the total luminosity in Eq.
-(\ref{eq:centralItotalL}) $L_i$ with the Gaussians total Mass $M_i = \Upsilon_{i} L_i$.
-We treat the five $\Upsilon_i$ as free parameters and only require that $\Upsilon_{j} \geq \Upsilon_i$ when the corresponding $\sigma_j \geq \sigma_i$ to ensure an overall mass-to-light ratio that is increasing with radius.
+We do this by assigning each of the five Gaussians in the MGE its own total mass-to-light ratio $\Upsilon_{\text{I,tot},i}$ and replace the total luminosity in Equation \ref{eq:centralItotalL} $L_i$ with the Gaussians total Mass $M_i = \Upsilon_{\text{I,tot},i} L_i$.
+We treat the five $\Upsilon_{\text{I,tot},i}$ as free parameters and only require that $\Upsilon_{\text{I,tot},j} \geq \Upsilon_{\text{I,tot},i}$ when the corresponding $\sigma_j \geq \sigma_i$ to ensure an overall mass-to-light ratio that is increasing with radius.
 \\Figure \ref{fig:enclMass_modelG} shows the (local projected) mass-to-light ratio gradient generated by the best fit to the dynamics data, which rises from $\Upsilon_\text{tot} = 2.53$ in the center and approaches a value of $\Upsilon_\text{tot}$ outside of the fitted region at $R'\gtrsim 3$ arcsec of $\Upsilon_\text{tot} = 7.60)$.
 The central mass-to-light ratio corresponds to the Chabrier IMF stellar mass-to-light ratio found by [TO DO: REF: TREU ET AL 2011] $\Upsilon_{i,*}^\text{Chab} = 2.5 \pm 0.6$ [TO DO: introduce and explain????].
-The strong rise  of$\Upsilon_\text{tot}(R')$ cannot be explained by an increase in the stellar $\Upsilon_*$ alone [TO DO: Really???
+The strong rise of $\Upsilon_\text{tot}(R')$ cannot be explained by an increase in the stellar $\Upsilon_*$ alone [TO DO: Really???
 Maybe it would have dropped again in the blue disk, if I had allowed for it????], so we deduce that we might need  contribution of dark matter halo in J1331.
-\\Fig.
-\ref{fig:JAM_modelG} shows that the best fit model greatly reproduces the central dip in the $v_\text{rms}$ curve, even though it has slight problems fitting the drop around $R' \sim 4$ arcsec.
+\\Figure \ref{fig:JAM_modelG} shows that the best fit model greatly reproduces the central dip in the $v_\text{rms}$ curve, even though it has slight problems fitting the drop around $R' \sim 4$ arcsec.
 The latter might be because we only allowed the $\Upsilon_\text{tot}(R')$ to rise.
 A slight drop could be expected when the reddish bulge turns into the bluish disk and the contribution of the stellar component becomes less due to a lower $\Upsilon_{*}$ for younger and bluer populations.
-\\In Fig.
-\ref{fig:enclMass_modelG} we overplot the enclosed mass profile with the Einstein mass $M_\text{ein} = (7.77 \pm 0.33) \cdot 10^{10} M_\odot$ at the Einstein radius found from lensing in Table [TO DO: REF].
+\\In Figure \ref{fig:enclMass_modelG} we overplot the enclosed mass profile with the Einstein mass $M_\text{ein} = (7.77 \pm 0.33) \cdot 10^{10} M_\odot$ at the Einstein radius found from lensing in Table [TO DO: REF].
 The agreement between the Einstein mass and the independently found $M(<R_\text{ein}) = 7.49 \cdot 10^{10} M_\odot$ from dynamical modelling is striking.
@@
 Include legend.???] [TO DO: weird  ticks on right axis???] [TO DO: Why does this plot look different than the others???] [TO DO: Switch the two y-axes.
-It's better to have ML on the left side, to read up the central ML.]}
+It's better to have ML on the left side, to read up the central ML.] [TO DO: local mass to light ratio $\Upsilon_\text{I,tot}(R')$]}
   \label{fig:enclMass_modelG}

### 2015-09-11 docs/results_photometry_v1.01.tex
Revistied most of the lensing section.
Removed some TO DOs.

@@
-\subsection{Surface Photometry for J1331 with MGEs}
+\subsection{Surface Photometry for J1331 with MGEs} \label{sec:MGE_results}
 
@@
 \includegraphics[width=0.8\columnwidth]{fig/1331F814Wsci_MGE_M.ps}
-\caption{MGE for J1331's inner regions: Comparison of contours with constant F814W surface brightness of J1331's central region (orange lines) with the corresponding iso-brightness contours of the best fit MGE in table \ref{tab:MGEF814W}, convolved with the PSF in table \ref{tab:MGEF814W}, (gray lines).
+\caption{MGE for J1331's inner regions: Comparison of contours with constant F814W surface brightness of J1331's central region (orange lines) with the corresponding iso-brightness contours of the best fit MGE in Table \ref{tab:MGEF814W}, convolved with the PSF in Table \ref{tab:MGEF814W}, (gray lines).
 The MGE model is a good representation of the galaxy's light distribution within $\sim 5$ arcsec.
 Image scaling and orientation are indicated in the figure.
-The black line has a length of 10 arcsec and it's orientation corresponds to the galaxy's position angle as found in table \ref{tab:galaxyparameters}.
-For comparison the Einstein radius as found in table ???
-is indicated as red dashed line.
-This MGE is used in the dynamical Jeans modelling in \S ???.
+The black line has a length of 10 arcsec and it's orientation corresponds to the galaxy's position angle as found in Table \ref{tab:galaxyparameters}.
+For comparison the Einstein radius as found in Table \ref{tab:bestfitlensmodel}  is indicated as red dashed line.
+This MGE is used in the dynamical Jeans modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}.
 [TO DO: explain how this MGE is used in dynamical modelling]}
@@
 \caption{MGE for J1331's outer regions: Comparison of contours with constant surface brightness of the smooth IRAF ELLIPSE model for J1331 in the F814W filter (yellow) with a corresponding best fit MGE (gray lines).
-The green box corresponds to the image section shown in Fig.
-\ref{fig:MGEinnerRegions}, with the Einstein radius as dashed red line.
+The green box corresponds to the image section shown in Figure \ref{fig:MGEinnerRegions}, with the Einstein radius as dashed red line.
 [TO DO: caption]}
@@
 \centering
-\caption{F814W PSF MGE: Parameters of the circular four-Gaussian MGE in Eq. (\ref{eq:PSFgeneral} fitted to the radial profile of the synthetic HST/F814W PSF image by [TO DO].}
+\caption{F814W PSF MGE: Parameters of the circular four-Gaussian MGE in Equation \ref{eq:PSFgeneral} fitted to the radial profile of the synthetic HST/F814W PSF image by [TO DO].}
 \begin{tabular}{ccc}
@@
 \centering
-\caption{J1331's F814W MGE: Parameters of the best fit MGE to the F814W surface brightness of J1331 in Fig.
-\ref{fig:F814W}.
+\caption{J1331's F814W MGE: Parameters of the best fit MGE to the F814W surface brightness of J1331 in Figure \ref{fig:F814W}.
 The fit is best inside an radius of 5 arcsec.
-The galaxy center and position angle, which gives the orientation of the MGE with respect to the original image, are given in table \ref{tab:galaxyparameters}.
-This MGE is used in the dynamical modelling in \S ???.
-The first column gives the total F814W luminosity of the Gaussian in Eq.
-(\ref{eq:centralItotalL}) in units of counts.
-The second column is the corresponding I-band peak surface brightness in Eq.
-(\ref{eq:MGEgeneral}) in units of a luminosity surface density, calculated from the first column following the procedure described in \S ???.
-The third and fourth column give the dispersion and the last column the axis ratio of the Gaussian in Eq.
-(\ref{eq:MGEgeneral}).}
+The galaxy center and position angle, which gives the orientation of the MGE with respect to the original image, are given in Table \ref{tab:galaxyparameters}.
+This MGE is used in the dynamical modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}.
+The first column gives the total F814W luminosity of the Gaussian in Equation \ref{eq:centralItotalL} in units of counts.
+The second column is the corresponding I-band peak surface brightness in Equation \ref{eq:MGEgeneral} in units of a luminosity surface density, calculated from the first column following the procedure described in Section \ref{sec:MGE_results}.
+The third and fourth column give the dispersion and the last column the axis ratio of the Gaussian in Equation \ref{eq:MGEgeneral}.}
 \begin{tabular}{cccccc}
@@
 
-In \S ???
-we derived a mass model for J1331 from Lensing.
-In this section set up a model for the galaxy's intrinsic light distribution in terms of an MGE, which we will then compare to the mass distribution.
-The light model will also be the basis of the dynamical Jeans modelling in \S ???.
-\\To derive J1331's surface brightness distribution, we use the HST image in the infrared F814W filter, shown in Fig.
-\ref{fig:F814W}.
-In infrared J1331's central old and smooth stellar component is more extended than in the F450W filter in Fig.
-\ref{fig:F450W}, which is more sensitive to young clumpy star-forming regions.
+In Section \ref{sec:results_lensing} we will derive a mass model for J1331 from Lensing.
+In this section set up a model for the galaxy's intrinsic light distribution in terms of an MGE, which we will then compare in Section \ref{sec:results_lensing} to the mass distribution.
+The light model will also be the basis of the dynamical Jeans modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}.
+\\To derive J1331's surface brightness distribution, we use the HST image in the infrared F814W filter, shown in Figure \ref{fig:F814W}.
+In infrared J1331's central old and smooth stellar component is more extended than in the F450W filter in Figure \ref{fig:F450W}, which is more sensitive to young clumpy star-forming regions.
 In infrared the bulge is also much brighter than the bluish lens images and the imaging is less prone to extinction.
@@
 \paragraph{PSF for the HST/F814W filter.} We find a radial profile for the HST/F814W filter PSF from circular annuli within a synthetic PSF image from [TO DO: Where did we get this image from???], ignoring diffraction spikes.
-The one-dimensional MGE fit of Eq.
-(\ref{eq:PSFgeneral}) to this radial profile is performed using the code by [TO DO: REF and footnote to code].
-The MGE parameters of the normalized PSF model are given in Tab.
-\ref{tab:PSFMGEF814W}.
+The one-dimensional MGE fit of Equation \ref{eq:PSFgeneral} to this radial profile is performed using the code by [TO DO: REF and footnote to code].
+The MGE parameters of the normalized PSF model are given in Table \ref{tab:PSFMGEF814W}.
 
-\paragraph{MGE for the inner regions.} We fit a MGE to the smooth central region within radius $\sim 5$ arcsec of the HST/WFPC2/WF3/F814W image of J1331 in Fig.
-\ref{fig:F814W}.
+\paragraph{MGE for the inner regions.} We fit a MGE to the smooth central region within radius $\sim 5$ arcsec of the HST/WFPC2/WF3/F814W image of J1331 in Figure \ref{fig:F814W}.
 Bright objects  close to the galaxy, blobs possibly belonging to the background galaxy and parts of the foreground spiral arm were masked during the fit.
-J1331's galaxy center, position angle and average apparent ellipticity (see table \ref{tab:galaxyparameters}) are found from the images weighted first and second moment.
-The MGE fit, as performed by the code \cite{Cap02}, splits the image in annuli with the given ellipticity and position angle and sectors of $5^\circ$ width and fits an 5-Gaussian MGE of the form in Eq.
-(\ref{eq:MGEgeneral}) convolved with the PSF MGE in table \ref{tab:PSFMGEF814W} to it.
-The best fit MGE (PSF convolved) is compared to the data in Fig.
-\ref{fig:MGEinnerRegions} and the corresponding parameters of the intrinsic surface brightness distribution are given in table \ref{tab:MGEF814W}.
+J1331's galaxy center, position angle and average apparent ellipticity (see Table \ref{tab:galaxyparameters}) are found from the images weighted first and second moment.
+The MGE fit, as performed by the code \cite{Cap02}, splits the image in annuli with the given ellipticity and position angle and sectors of $5^\circ$ width and fits an 5-Gaussian MGE of the form in Equation \ref{eq:MGEgeneral} convolved with the PSF MGE in Table \ref{tab:PSFMGEF814W} to it.
+The best fit MGE (PSF convolved) is compared to the data in Figure \ref{fig:MGEinnerRegions} and the corresponding parameters of the intrinsic surface brightness distribution are given in Table \ref{tab:MGEF814W}.
 The fit is a very good representation of the light distribution in the inner 5 arcsec, but underestimates the light distribution outside of this.
@@
 
-\paragraph{Total luminosity and effective radius.} J1331's total I-band luminosity is easily determined by summing up the luminosity contributions of all the Gaussians of the MGE for the outer regions (shown as gray lines in Fig.
-\ref{fig:MGEouterRegions}).
+\paragraph{Total luminosity and effective radius.} J1331's total I-band luminosity is easily determined by summing up the luminosity contributions of all the Gaussians of the MGE for the outer regions (shown as gray lines in Figure \ref{fig:MGEouterRegions}).
 We find $L_\text{tot,I} \simeq 5.6 \cdot 10^{10} L_\odot$.
 This corresponds to an apparent magnitude of $m_I = 15.77$ mag.
-We determine the circularized effective radius $R_\text{eff}$ of J1331 from the definition $L(<R_\text{eff}) \equiv \frac 12 L_\text{tot}$ and the growth curve $L(<R)$ from the MGE model of the outer regions [TO DO: Maybe I need a table anyway???], where $R$ is the projected radius on the sky [TO DO: Or is it $R'$???].
-We find the effective radius to be $R_\text{eff} \simeq 2.6 \text{arcsec} \hat{=} 5.2 \text{kpc}$.
+We determine the circularized effective radius $R_\text{eff}$ of J1331 from the definition $L(<R_\text{eff}) \equiv \frac 12 L_\text{tot}$ and the growth curve $L(<R')$ from the MGE model of the outer regions [TO DO: Maybe I need a table anyway???], where $R'$ is the projected radius on the sky.
+We find the effective radius to be $R_\text{eff} \simeq 2.6 \text{ arcsec } \hat{=} 5.2 \text{ kpc}$.
 All values are summarized in Table \ref{tab:galaxyparameters}.

### 2015-09-14 docs/discussion_ML_v1.02.tex
Wrote section on future work and removed some TO DOs.

@@
 \citet{SWELLSI} estimated J1331's stellar bulge mass given a Salpeter IMF and measured the I-band AB magnitude of the bulge.
-Transformed to a stellar I-band mass-to-light ratio (see Table \ref{tab:previousresults}) this would correspond to $\Upsilon_\text{I,*}^\text{Salpeter} = 4.7 \pm 1.2$.\\
+Transformed to a stellar I-band mass-to-light ratio (see Table \ref{tab:previousresults}) this would correspond to $\Upsilon_\text{I,*}^\text{sal} = 4.7 \pm 1.2$.\\
 
 We compare our findings of the stellar mass-to-light ratios with the study by \cite{SWELLSV}: \cite{SWELLSV} found that the bulge of J1331 has an IMF more bottom-heavy than the Salpeter IMF from fitting a NFW halo to (1) the Einstein mass and (2) gas kinematics at larger radii $\gtrsim 8$ arcsec.
-In Section \ref{sec:results_JAM_NFW} we fitted the stellar kinematics within $\sim 3.5$ arcsec and the Einstein mass with a NFW halo and the best fit $\Upsilon_\text{I,*}^\text{dyn} = 4.2 \pm 0.2$ (see Table \ref{tab:modelB4_bestfit}) indicates a less bottom-heavy IMF than the Salpeter IMF.
+In Section \ref{sec:results_JAM_NFW} we fitted the stellar kinematics within $\sim 3.5$ arcsec and the Einstein mass with a NFW halo and the best fit $\Upsilon_\text{I,*} = 4.2 \pm 0.2$ (see Table \ref{tab:modelB4_bestfit}) indicates a less bottom-heavy IMF than the Salpeter IMF.
 \cite{SWELLSV}  found systematically lower NFW halos ($v_\text{circ}(5\text{arcsec}) \sim 120 \text{km s}^{-1}$ according to their Figure 2) than we did ($v_\text{circ}(5\text{arcsec}) \sim 200 \text{km s}^{-1}$, see Figure \ref{fig:kinematics}).
@@
 We get a very similar circular velocity curve (at least at small radii) for a mass-follows-light model with constant $\Upsilon_\text{I,tot}^\text{ein} = 5.6$, which peaks at $v_\text{circ}(R\sim0.9 \text{arcsec}) \sim 360 \text{km s}^{-1}$.
-From this comparison follows, that the model by \citet{SWELLS} corresponds approximately to a mass-follows-light model in the inner regions of J1331.
+From this comparison follows, that the model by \citet{SWELLSV} corresponds approximately to a mass-follows-light model in the inner regions of J1331.
 In Section \ref{sec:results_JAM_SB} however we showed, that this is \emph{not} a good model for J1331 and won't be able to reproduce the central stellar $v_\text{rms}$ dip.
@@
 
-Another feature in the stellar kinematics, that none of our JAM models was able to reproduce in the slightest and which we therefore excluded in the modelling, was the dip in $v_\text{rms}$ around $\sim 6$ arcsec, which occurs around the transition from bulge to disk (see Figure [TO DO: 1b]).\\
+Another feature in the stellar kinematics, that none of our JAM models was able to reproduce in the slightest and which we therefore excluded in the modelling, was the dip in $v_\text{rms}$ around $\sim 6$ arcsec, which occurs around the transition from bulge to disk (see Figures \ref{fig:F814W} and \ref{fig:kinematics}).\\
 
@@
 Such a drop in $\Upsilon_\text{I,*}$ at the transition region from bulge to disk around $\sim 5$ arcsec could lead to the observed drop in $v_\text{rms}$, while an increasing contribution of a lower mass dark matter halo at larger radii as found by \citet{SWELLSV}, would recover the kinematics in the out regions of J1331's disk.\\
-
-[TO DO: Rewrite the paper such, that it's main message is, that there is a strong indication of increasing stellar mass-to-light ratio in the center of the galaxy, i.e.
-a bluish core, because neither velocity anisotropy, neither a strong dark matter contribution alone can explain all dynamical signatures.
-"Evidence from Lensing and Dynamics for a bluish core in the center of J1331" as a possible alternative title???
-Eher nicht...]
-
-[TO DO: Einheitlich: $\Upsilon_{I,*}^{comment}$, $\Upsilon_\text{I,tot}^\text{ein}$]
 
@@
 & & \multicolumn{2}{c}{Chabrier IMF} & \multicolumn{2}{c}{Salpeter IMF}\\
-      &  $L$ [$10^{10}L_{\odot}$]                & $M_*$ [$10^{10}M_\odot$]               & $\Upsilon_\text{I,*}^\text{chab}$ & $M_*$ [$10^{10}M_\odot$] & $\Upsilon_\text{I,*}^\text{Salpeter}$ \\\hline
+      &  $L$ [$10^{10}L_{\odot}$]                & $M_*$ [$10^{10}M_\odot$]               & $\Upsilon_\text{I,*}^\text{chab}$ & $M_*$ [$10^{10}M_\odot$] & $\Upsilon_\text{I,*}^\text{sal}$ \\\hline
 bulge &   $3.10 \pm 0.15 $  & $7.8 \pm 1.8$ & $2.5 \pm 0.6$ & $14.5 \pm 3.7 $ & $4.7 \pm 1.2$ \\
@@
 \end{tabular}
-\caption{Total I-band luminosity, stellar mass and mass-to-light ratio, calculated from the I-band AB magnitudes and stellar masses found for J133's bulge and disk by \citet{SWELLS} (their table 2) for comparison with this work.
+\caption{Total I-band luminosity, stellar mass and mass-to-light ratio, calculated from the I-band AB magnitudes and stellar masses found for J133's bulge and disk by \citet{SWELLSI} (their table 2) for comparison with this work.
 The transformation from AB magnitudes to the Johnson-Cousins I-Band used the relation $I[\text{mag}] = I[\text{ABmag}] - 0.309$ from \citet{FG1994} (their table 2).
-For the conversion from apparent magnitude to total luminosity the redshift $z=0.113$ \citet{SWELLSIII} was turned into a luminosity distance using the cosmology by \ref{WMAP5cosm}.
+For the conversion from apparent magnitude to total luminosity the redshift $z=0.113$ \citet{SWELLSIII} was turned into a luminosity distance using the cosmology by \citet{WMAP5cosm}.
 }

### 2015-09-14 docs/discussion_merger_v1.01.tex
Wrote section on future work and removed some TO DOs.

@@
-\subsection{Does J1331 have a Merger History?}
+\subsection{On J1331's possible merger history and potential model failures}
+
+[TO DO: Einheitliche Gross / Klein schreibung in allen Ueberschriften]
 
@@
 \item Normally this gradient is only weak, but there are exceptions [TO DO: CAROLLO 1997].
-\item A second effect of the minor merger could be a misalignement of the photometric and kinematic major axis
+\item A second effect of the minor merger could be a misalignement of the photometric and kinematic major axis (warp)
+\item Assumption of axisymmetry is not true anymore
+\item Merger could have changed 3D shape of dark matter halo, or NFW halo was not a good model in the first place (core-cusp problem).
+However, due to degeneracies in the modelling, we were not able to constrain the profile for a cored logarithmic halo, or to rule it out.
 \end{itemize}
@@
 Because of degeneracies between stellar and dark mass, and matter distribution and anisotropy profile, such a dynamical model would not lead to very tight constraints on the model parameters.
-Further priors are needed.
-Detailed stellar population analyses of the spectra taken along J1331's major axis could possibly support or contradict the suspicion of the existence of stellar mass-to-light ratio gradients in J1331.
-
-\paragraph{Model Failures}
-\begin{itemize}
-\item Assumption of axisymmetry is not true anymore
-\item [TO DO: more]
-\end{itemize}
+A search for color gradients in J1331 and/or investigation of absorption line indices could support or contradict the suspicion of the existence of stellar mass-to-light ratio gradients in J133.
+Subsequently detailed stellar population analyses of the spectra taken along J1331's major axis should be conducted to constrain the mass-to-light ratio reliably.
+In addition, the dynamical modelling should use more of the available information on J1331 and fit dynamics (stellar and gas kinematics from \citet{SWELLSV}) simultaneously with the gravitational lensing (image positions, shape and even flux ratios) in a similar fashion to \citet{SWELLSIV}.
+To also model the extent, shape and flux of the lensing images, the method by \citet{2004ApJ...611..739T,2003ApJ...590..673W} could be employed, which models the surface brightness distribution of the images and source on a pixelated grid.
+However, for this to work a good model for the galactic extinction would be needed.
+High-resolution integral-field spectroscopy could help with this, allow for spatially resolved stellar population analysis and dynamical modelling in two dimensions.
+This would lead to much better understanding of J1331's structure and mass distribution and therefore answer questions on how minor mergers might modify spiral galaxies.

### 2015-09-14 docs/model_JAM_v1.01.tex
Wrote section on future work and removed some TO DOs.

@@
 
-\paragraph{Data comparison.} As data we use stellar line-of-sight rotation velocities $v_\text{rot} \equiv \langle v_\text{los} \rangle$ [TO DO: consistent, los or rot] and velocity dispersions $\sigma$ as described in Section \ref{sec:data}.
+\paragraph{Data comparison.} As data we use stellar line-of-sight rotation velocities $v_\text{rot} \equiv \langle v_\text{los} \rangle$ and velocity dispersions $\sigma$ as described in Section \ref{sec:data}.
 The JAM models give us a prediction for the second line-of-sight velocity moment $\langle v_\text{los}^2 \rangle$.
@@
 \end{eqnarray*}
-If provided with the convolution kernel, the JAM code by \citet{Cap08} [TO DO: reference code] performs the convolution numerically.
+If provided with the convolution kernel, the JAM code\footnote{The IDL code package for Jeans Axisymmetric Modelling (JAM) by \citet{Cap08} is available online at \url{http://www-astro.physics.ox.ac.uk/~mxc/software}.
+The version from June 2012 was used in this work.} by \citet{Cap08} performs the convolution numerically.
 We set $L_x = 0.21$ arcsec as the width of the model pixel, and get a prediction for the actual measurements in bins of width 0.63, 1.26 and 1.89 arcsec \citep{SWELLSV} as light-weighted mean from each 3, 6 and 9 model pixels.

### 2015-09-14 docs/model_MGE_v1.01.tex
Wrote section on future work and removed some TO DOs.

@@
 Multi-Gaussian Expansions (MGE) are used to parametrize the observed surface brightness or projected total mass of a galaxy as a sum of $N$ two-dimensional, elliptical Gaussians \citep{1991ApJ...366..599B,1992A&A...253..366M,1994A&A...285..723E,1999MNRAS.303..495E}.
-This work makes use of the algorithm and code\footnote{Michele Cappellari's IDL code package for fitting MGEs to images is available online at \url{http://www-astro.physics.ox.ac.uk/~mxc/software}.
+This work makes use of the algorithm and code\footnote{The IDL code package for fitting MGEs to images by \citet{Cap02} is available online at \url{http://www-astro.physics.ox.ac.uk/~mxc/software}.
 The version from June 2012 was used in this work.} by \citet{Cap02}.

### 2015-09-14 docs/results_JAMwithNFW_v1.01.tex
Wrote section on future work and removed some TO DOs.

@@
 
-\paragraph{Modelling.} The full set of fit parameters is $(\Upsilon_{I,*},R_\text{S,NFW},v_{200},\beta)$ [TO DO: $\beta$ or $\beta_0$???] [TO DO: Einheitlich $\Upsilon_{I,*}$????], where $\beta$ is the constant velocity anisotropy parameter (see Section \ref{sec:model_JAM}).
-We will investigate this parameter space with a MCMC \citep{emcee} and use priors for the halo parameters to guide the fit to a realistic NFW halo shape.
+\paragraph{Modelling.} The full set of fit parameters is $(\Upsilon_\text{I,*},R_\text{S,NFW},v_{200},\beta_z)$ [TO DO: $\beta$ or $\beta_0$???], where $\beta_z$ is the constant velocity anisotropy parameter (see Section \ref{sec:model_JAM}).
+We will investigate this parameter space with a MCMC\footnote{The Python code package for \emph{emcee}, a Monte Carlo Markov Chain implementation by \citet{emcee} is available online at \url{http://dan.iel.fm/emcee/current/}.
+The version from October 2013 was used in this work.} \citep{emcee} and use priors for the halo parameters to guide the fit to a realistic NFW halo shape.
 \\\citet{Dutton10} give a relation for halo vs. stellar mass for late-type galaxies. For an Chabrier IMF stellar population they found
@@
 \begin{eqnarray*}
-&&p(\Upsilon_{I,*},R_\text{S,NFW},v_{200},\beta) \\
+&&p(\Upsilon_\text{I,*},R_\text{S,NFW},v_{200},\beta) \\
 &&= \frac{1}{\ln\left( 10 R_{s,NFW}\right)} p(\log c_{200} \mid v_{200}) \cdot p(v_{200}) \cdot p(\beta), 
@@
 Both, the concentrated halo and the low anisotropy are needed to reproduce the central dip of the $v_\text{rms}$ curve.
-There are slight covariances between $\Upsilon_{I,*}$,  $R_\text{s,NFW}$ and $\beta_z$: The smaller the dark matter contribution in the center (i.e.
-the larger $\Upsilon_{I,*}$ [TO DO: make sure, mass-to-light ratio is everywhere named properly]), the less concentrated is the halo (i.e.
+There are slight covariances between $\Upsilon_\text{I,*}$,  $R_\text{s,NFW}$ and $\beta_z$: The smaller the dark matter contribution in the center (i.e.
+the larger $\Upsilon_\text{I,*}$), the less concentrated is the halo (i.e.
 the larger $R_\text{s,NFW}$), the more velocity anisotropy is needed to reproduce the central dip.
@@
 \includegraphics[width=0.9\linewidth]{fig/B4_contour_plot_short.ps}
-\caption{Posterior probability distribution sampled with MCMC (red dots and histograms) for a JAM model with NFW halo, parametrized by $R_\text{s,NFW}$ and $v_\text{200}$, a stellar mass distribution generated from the I-band MGE in Table \ref{tab:MGEF814W} and a constant stellar mass-to-light ratio $\Upsilon_{I,*}$, and constant velocity anisotropy $\beta_z$.
+\caption{Posterior probability distribution sampled with MCMC (red dots and histograms) for a JAM model with NFW halo, parametrized by $R_\text{s,NFW}$ and $v_\text{200}$, a stellar mass distribution generated from the I-band MGE in Table \ref{tab:MGEF814W} and a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and constant velocity anisotropy $\beta_z$.
 Shown are also the priors used for J1331's NFW halo, $\mathscr{N}(200 \text{km/s},40 \text{km/s})$ (green) and the concentration vs.
@@
 The grey diamonds mark a random sub-selection of 12 samples; the corresponding models are shown in Figure \ref{fig:modelB4_models}.
-[TO DO: Rename $\beta_0$ to $\beta_z$, rename $R_\text{s,NFW}$ to $r_\text{s,NFW}$, rename $\Upsilon_*$ to $\Upsilon_{I,*}$]}
+[TO DO: Rename $\beta_0$ to $\beta_z$, rename $R_\text{s,NFW}$ to $r_\text{s,NFW}$, rename $\Upsilon_*$ to $\Upsilon_\text{I,*}$]}
 \label{fig:modelB4_triangle}
@@
 \hline
-stellar I-band mass-to-light ratio & $\Upsilon_{I,*}$ & 4.2 & $\pm$ & 0.2\\
+stellar I-band mass-to-light ratio & $\Upsilon_\text{I,*}$ & 4.2 & $\pm$ & 0.2\\
 velocity anisotropy & $\beta_z$ & -0.4 & $\pm$ & 0.1 \\
@@
 Also shown is the non-symmetrized data at larger radii (open blue dots) and an extrapolation of the best fit models, using the same model parameters but the I-band surface brightness MGE for the outer regions of J1331 derived from the Ellipse model (red dashed lines).
-\emph{Panel b)} shows the circular velocity curve of the total mass (green), and separately the contribution of the stellar mass (yellow, again generated from the MGE in Table \ref{tab:F814WMGE}) and dark matter (grey).
+\emph{Panel b)} shows the circular velocity curve of the total mass (green), and separately the contribution of the stellar mass (yellow, again generated from the MGE in Table \ref{tab:MGEF814W}) and dark matter (grey).
 [TO DO: Is this really the spherical $r$?

### 2015-09-14 docs/results_JAMwithSB_v1.01.tex
Wrote section on future work and removed some TO DOs.

@@
 with "Mass-follows-Light" and Velocity Anisotropy.} Our second JAM model is a mass-follows-light model, which are often used in dynamical JAM modelling (e.g.
-\citet{GlennEC,Cap06}), where the mass distribution ins generated by multiplying the intrinsic light distribution $\nu(R,z)$ (the MGE given in Table \ref{tab:MGEF814W} deprojected according to the inclination) by a constant total mass-to-light ratio  $\Upsilon_{I,\text{tot}}^\text{dyn}$.
+\citet{GlennEC,Cap06}), where the mass distribution ins generated by multiplying the intrinsic light distribution $\nu(R,z)$ (the MGE given in Table \ref{tab:MGEF814W} deprojected according to the inclination) by a constant total mass-to-light ratio  $\Upsilon_\text{I,tot}^\text{dyn}$.
 This assumes that the dark matter is always a constant fraction of the total matter distribution everywhere.
@@
 Testing this model for J1331 is also motivated by our findings from lensing in Section \ref{sec:results_lensing}, where around the Einstein radius total and luminous mass seem to have a similar distribution.
-\\In addition to the free fit parameter  $\Upsilon_{I,\text{tot}}^\text{dyn}$, we also allow for a overall constant but non-zero velocity anisotropy $\beta_z$.
+\\In addition to the free fit parameter  $\Upsilon_\text{I,tot}^\text{dyn}$, we also allow for a overall constant but non-zero velocity anisotropy $\beta_z$.
 The best fit is found by minimizing $\chi^2$ between the $v_\text{rms}$ data and model prediction and is demonstrated in Figure \ref{fig:JAM_modelA2}.
@@
   \includegraphics[height=6cm]{fig/jam_A2_vrms.ps}
-  \caption{Comparison of the symmetrized $v_\text{rms}$ data of J1331 (blue dots) with a best fit dynamical JAM model (solid red line) assuming mass-follows-light and with two free parameters: $\Upsilon_{I,\text{tot}}^\text{dyn}$, the total I-band mass-to-light ratio found from dynamics, which converts the observed surface brightness in Table \ref{tab:MGEF814W} into a mass distribution, and the velocity anisotropy parameter $\beta_z$.
-The "best" fit is $\Upsilon_{I,*}^\text{dyn} = 4.8 \pm 0.1$ and $\beta_z = -0.5$, where the latter is however pegged at the lower limit of the allowed value range.
+  \caption{Comparison of the symmetrized $v_\text{rms}$ data of J1331 (blue dots) with a best fit dynamical JAM model (solid red line) assuming mass-follows-light and with two free parameters: $\Upsilon_\text{I,tot}^\text{dyn}$, the total I-band mass-to-light ratio found from dynamics, which converts the observed surface brightness in Table \ref{tab:MGEF814W} into a mass distribution, and the velocity anisotropy parameter $\beta_z$.
+The ``best'' fit is $\Upsilon_\text{I,tot}^\text{dyn} = 4.8 \pm 0.1$ and $\beta_z = -0.5$, where the latter is however pegged at the lower limit of the allowed value range.
 This is obviously not a good model.}
@@
 As velocity anisotropy alone cannot explain the observed kinematics in a simple a mass-follows-light model, we now allow for an mass-to-light ratio gradient in the JAM modelling to generate a mass model from the light distribution in Table \ref{tab:MGEF814W}.
-We do this by assigning each of the five Gaussians in the MGE its own total mass-to-light ratio $\Upsilon_{\text{I,tot},i}$ and replace the total luminosity in Equation \ref{eq:centralItotalL} $L_i$ with the Gaussians total Mass $M_i = \Upsilon_{\text{I,tot},i} L_i$.
-We treat the five $\Upsilon_{\text{I,tot},i}$ as free parameters and only require that $\Upsilon_{\text{I,tot},j} \geq \Upsilon_{\text{I,tot},i}$ when the corresponding $\sigma_j \geq \sigma_i$ to ensure an overall mass-to-light ratio that is increasing with radius.
-\\Figure \ref{fig:enclMass_modelG} shows the (local projected) mass-to-light ratio gradient generated by the best fit to the dynamics data, which rises from $\Upsilon_\text{tot} = 2.53$ in the center and approaches a value of $\Upsilon_\text{tot}$ outside of the fitted region at $R'\gtrsim 3$ arcsec of $\Upsilon_\text{tot} = 7.60)$.
-The central mass-to-light ratio corresponds to the Chabrier IMF stellar mass-to-light ratio found by [TO DO: REF: TREU ET AL 2011] $\Upsilon_{i,*}^\text{Chab} = 2.5 \pm 0.6$ [TO DO: introduce and explain????].
-The strong rise of $\Upsilon_\text{tot}(R')$ cannot be explained by an increase in the stellar $\Upsilon_*$ alone [TO DO: Really???
+We do this by assigning each of the five Gaussians in the MGE its own total mass-to-light ratio $\Upsilon_{\text{I,tot,}i}$ and replace the total luminosity in Equation \ref{eq:centralItotalL} $L_i$ with the Gaussians total Mass $M_i = \Upsilon_{\text{I,tot,}i} L_i$.
+We treat the five $\Upsilon_{\text{I,tot,}i}$ as free parameters and only require that $\Upsilon_{\text{I,tot,}j} \geq \Upsilon_{\text{I,tot,}i}$ when the corresponding $\sigma_j \geq \sigma_i$ to ensure an overall mass-to-light ratio that is increasing with radius.
+\\Figure \ref{fig:enclMass_modelG} shows the (local projected) mass-to-light ratio gradient generated by the best fit to the dynamics data, which rises from $\Upsilon_\text{I,tot} = 2.53$ in the center and approaches a value of $\Upsilon_\text{I,tot}$ outside of the fitted region at $R'\gtrsim 3$ arcsec of $\Upsilon_\text{tot} = 7.60)$.
+The central mass-to-light ratio corresponds to the Chabrier IMF stellar mass-to-light ratio found by [TO DO: REF: TREU ET AL 2011] $\Upsilon_\text{I,*}^\text{chab} = 2.5 \pm 0.6$ [TO DO: introduce and explain????].
+The strong rise of $\Upsilon_\text{I,tot}(R')$ cannot be explained by an increase in the stellar $\Upsilon_\text{i,*}$ alone [TO DO: Really???
 Maybe it would have dropped again in the blue disk, if I had allowed for it????], so we deduce that we might need  contribution of dark matter halo in J1331.
 \\Figure \ref{fig:JAM_modelG} shows that the best fit model greatly reproduces the central dip in the $v_\text{rms}$ curve, even though it has slight problems fitting the drop around $R' \sim 4$ arcsec.
-The latter might be because we only allowed the $\Upsilon_\text{tot}(R')$ to rise.
-A slight drop could be expected when the reddish bulge turns into the bluish disk and the contribution of the stellar component becomes less due to a lower $\Upsilon_{*}$ for younger and bluer populations.
+The latter might be because we only allowed the $\Upsilon_\text{I,tot}(R')$ to rise.
+A slight drop could be expected when the reddish bulge turns into the bluish disk and the contribution of the stellar component becomes less due to a lower $\Upsilon_\text{I,*}$ for younger and bluer populations.
 \\In Figure \ref{fig:enclMass_modelG} we overplot the enclosed mass profile with the Einstein mass $M_\text{ein} = (7.77 \pm 0.33) \cdot 10^{10} M_\odot$ at the Einstein radius found from lensing in Table [TO DO: REF].
@@
 \end{subfigure}
-\caption{JAM model found by fitting an increasing total mass-to-light ratio $\Upsilon_\text{tot}$ profile used to generate a mass model from the light distribution.
+\caption{JAM model found by fitting an increasing total mass-to-light ratio $\Upsilon_\text{I,tot}(R')$ profile used to generate a mass model from the light distribution.
 This is done by assigning a different mass-to-light ratio to each Gaussian in the MGE in Table \ref{tab:MGEF814W}.
 \emph{Panel (a):} Comparison between the stellar $v_\text{rms}$ data (blue points) and the best fit model (green line).
-\emph{Panel (b):} Enclosed mass inside the projected radius $R'$ on the sky (green line, left axis) and mass-to-light profile $\Upsilon(R')$ along the major axis [TO DO: CHECK???] (blue line, right axis) of the best fit model.
+\emph{Panel (b):} Enclosed mass inside the projected radius $R'$ on the sky (green line, left axis) and projected mass-to-light profile $\Upsilon_\text{I,tot}(R')$ along the major axis [TO DO: CHECK???] (blue line, right axis) of the best fit model.
 The enclosed mass curve is overplotted with the independent finding for the Einstein mass $\pm 4 \%$ in Table [TO DO: TABLE REFERENCE???] (red dot) at the Einstein radius (red dotted line).

### 2015-09-14 docs/results_lensing_v1.02.tex
Finished discussion on stellar mass-to-light ratios.
Wrote section on future work and removed some TO DOs.

@@
 The image positions were determined from the lens subtracted image for J1331 in Figure 4 of \citet{SWELLSIII}, rotated to the $(x,y)$ coordinate system in Figure \ref{fig:lens_just_imgpos}.
-The pixel scale is 1 pixel = 0.05 arcsec and the error of each image position is $\pm$ 1 pixel.
-\textit{SMALL PROBLEM: Somehow I used $\sqrt(2)$ pixel as the error on the galaxy center in the Monte Carlo sampling code instead of the 0.5 pixel I claim here.
-Should I change this table and the error bars in the figures to match this bug????}}
+The pixel scale is 1 pixel = 0.05 arcsec and the error of each image position is $\pm$ 1 pixel.}
 \label{tab:lenspos}
@@
 \centering
-\caption{[TO DO: Caption] ??? in Table \ref{tab:lenspos}, for $\alpha = 1$}
+\caption{Best fit lens model found from the peak image positions in Table \ref{tab:lenspos} (first column) following the procedure described in Section \ref{sec:lensing_theo} and assuming a flat rotation curve ($\alpha = 1$).
+The second column gives the corresponding best fit mean and standard deviation derived from Monte Carlo sampling of the Gaussian uncertainties around the image positions (column 2).}
 \begin{tabular}{llrrclr}
@@
 $L_\text{I,ein}$ and $\Upsilon_\text{I,tot}^\text{ein}$ are given in Table \ref{tab:einsteinML}.
-$\Upsilon_\text{I,tot}^\text{ein} \sim 5.6$ is consistent or slightly larger than the stellar mass-to-light ratio assuming a Salpeter Initial Mass Function $\Upsilon_\text{I,*}^\text{Salpeter} = 4.7 \pm 1.2$ according to \citet{SWELLSI} and Table \ref{tab:previousresults} (see also discussion in Section \ref{sec:MLdiscussion}).
+$\Upsilon_\text{I,tot}^\text{ein} \sim 5.6$ is consistent or slightly larger than the stellar mass-to-light ratio assuming a Salpeter Initial Mass Function $\Upsilon_\text{I,*}^\text{sal} = 4.7 \pm 1.2$ according to \citet{SWELLSI} and Table \ref{tab:previousresults} (see also discussion in Section \ref{sec:MLdiscussion}).
 We use $\Upsilon_\text{I,tot}^\text{ein}$ to transform the observed surface brightness in the F814W filter into a surface mass density to compare it to the lensing mass distribution (Figure \ref{fig:lenscomparelight}).
@@
 Astrophysical reasons for the differences in observed light and measured mass distribution could be, e.g.
-an apparent change of shape due to dust extinction, a strongly changing $\Upsilon_{I,*}$, or the stellar component of the galaxy could be superimposed by a more roundish dark matter component.
+an apparent change of shape due to dust extinction, a strongly changing $\Upsilon_\text{I,*}$, or the stellar component of the galaxy could be superimposed by a more roundish dark matter component.
 We have to note however that the mass distribution is only constraint around the Einstein radius and otherwise an extrapolation.
@@
 \label{tab:einsteinML} 
-\end{table}
+\end{table*}
 
@@
   \includegraphics[width=.9\linewidth]{fig/lens_surface_brightness.ps}
-  \caption{Observed light distribution. [TO DO: use $\Upsilon_\text{I,tot}^\text{ein}$ on colorbar]}
+  \caption{Observed light distribution.}
   \label{fig:lenscomparelight}
@@
 The smooth black contours correspond to the best fit model in the first column of Table \ref{tab:bestfitlensmodel}.
-The background in Panel (c) shows again the surface brightness subtracted center of the galaxy to make the lensing images visible.}
+The background in Panel (c) shows again the surface brightness subtracted center of the galaxy to make the lensing images visible.
+[TO DO: use $\Upsilon_\text{I,tot}^\text{ein}$ on colorbar]}
 \label{fig:lenslightcompareALL}

### 2015-09-14 docs/results_photometry_v1.01.tex
Wrote section on future work and removed some TO DOs.

@@
 \caption{MGE for J1331's inner regions: Comparison of contours with constant F814W surface brightness of J1331's central region (orange lines) with the corresponding iso-brightness contours of the best fit MGE in Table \ref{tab:MGEF814W}, convolved with the PSF in Table \ref{tab:MGEF814W}, (gray lines).
-The MGE model is a good representation of the galaxy's light distribution within $\sim 5$ arcsec.
+The MGE model is a good representation of the galaxy's light distribution along the major axis within $\sim 5$ arcsec.
 Image scaling and orientation are indicated in the figure.
@@
 For comparison the Einstein radius as found in Table \ref{tab:bestfitlensmodel}  is indicated as red dashed line.
-This MGE is used in the dynamical Jeans modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}.
-[TO DO: explain how this MGE is used in dynamical modelling]}
+This MGE is used as model for the stellar tracer distribution in the dynamical Jeans modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}.}
 \label{fig:MGEinnerRegions}
@@
 \includegraphics[width=0.8\columnwidth]{fig/1331F814W_MGE_disk_L.ps}
-\caption{MGE for J1331's outer regions: Comparison of contours with constant surface brightness of the smooth IRAF ELLIPSE model for J1331 in the F814W filter (yellow) with a corresponding best fit MGE (gray lines).
-The green box corresponds to the image section shown in Figure \ref{fig:MGEinnerRegions}, with the Einstein radius as dashed red line.
-[TO DO: caption]}
+\caption{MGE for J1331's outer regions: Comparison of contours with constant surface brightness of the smooth IRAF ELLIPSE [TO DO: How to write Iraf Ellipse???] model for J1331 in the F814W filter (yellow) with a corresponding best fit MGE (gray lines).
+The green box corresponds to the image section shown in Figure \ref{fig:MGEinnerRegions}, with the Einstein radius as dashed red line and the black 10 arcsec orientation line along the major axis (see Figure \ref{fig:MGEinnerRegions}).
+This MGE found from the smooth, symmetric Iraf Ellipse [TO DO] model is not used to find a dynamical model for J1331, because the dynamics in the outer regions are strongly affected by non-axisymmetries (e.g.
+spiral arms).
+We use it, however, to estimate the galaxy's total luminosity and effective radius, and to get a prediction for the dynamics of the outer regions by extrapolation the best fit model of the inner regions.}
 \label{fig:MGEouterRegions}
@@
 \centering
-\caption{F814W PSF MGE: Parameters of the circular four-Gaussian MGE in Equation \ref{eq:PSFgeneral} fitted to the radial profile of the synthetic HST/F814W PSF image by [TO DO].}
+\caption{F814W PSF MGE: Parameters of the circular four-Gaussian MGE in Equation \ref{eq:PSFgeneral} fitted to the radial profile of the synthetic HST/F814W PSF image by [TO DO: WHO???].}
 \begin{tabular}{ccc}
@@
 scaling                   & 1 kpc / 1 arcsec & 2.006 & \\
-position angle            & $\phi$ [degrees] & wrt what???\\
+position angle            & $\phi$ [degrees] & [TO DO: wrt what???]\\
 average axis ratio & $q'$ & 0.598\\
@@
 \paragraph{PSF for the HST/F814W filter.} We find a radial profile for the HST/F814W filter PSF from circular annuli within a synthetic PSF image from [TO DO: Where did we get this image from???], ignoring diffraction spikes.
-The one-dimensional MGE fit of Equation \ref{eq:PSFgeneral} to this radial profile is performed using the code by [TO DO: REF and footnote to code].
+The one-dimensional MGE fit of Equation \ref{eq:PSFgeneral} to this radial profile is performed using the code by \citet{Cap02}.
 The MGE parameters of the normalized PSF model are given in Table \ref{tab:PSFMGEF814W}.
@@
 
-\paragraph{Transformation into physical units.} To transform the MGE in units of counts into physical units, we apply a simplified version of the procedure described in \citet{Holtzman}, analogous to [TO DO: Cappellari Read me file???]
+\paragraph{Transformation into physical units.} To transform the MGE in units of counts into physical units, we apply a simplified version of the procedure described in \citet{Holtzman}, analogous to [TO DO: Cappellari Read me file???
+How to reference this???]
 \\The scaling of the drizzled HST/WFC3 images is  $S = 0.05$ arcsec/pixel and the total exposure time $T = 1600$ sec.
@@
 $C= 0.1$ corrects for the finite aperture of the WFPC2.
-And $A_I =0.015$ mag  is the extinction in the I-band tpwards J1331, according to the NASA/IPAC Extragalactic Database [TO DO: proper reference].
+And $A_I =0.015$ mag  is the extinction in the (Landolt) I-band towards J1331, according to the NASA/IPAC Extragalactic Database (NED)\footnote{The NASA/IPAC Extragalactic Database (NED, \url{https://ned.ipac.caltech.edu/}) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.
+The data for J1331 (SDSS J133140.33+362811.9) was retrieved in October 2013.}.
 The color-dependent correction between the F814W filter and the I-band of the UBVRI photometric system is  small \citep{Holtzman} and we neglect it therefore.
@@
 Check, that everything is correct and the naming of quantities, e.g.
-with or without subscripts of 0, is fine???] [TO DO: Maybe shift to appendix???]
+with or without subscripts of 0, is fine???] [TO DO: Maybe shift to appendix or theory part???]
 
 \paragraph{Inclination.} To estimate the inclination of J1331 with respect to the observer, we use the observed axis ratio of the flattest ellipse in the Iraf Ellipse [TO DO] model for J1331, which is $q'=0.42$.
-This is similar to the disk axis ratio of $q' = 0.40$ found by \citet{SWELLSI} [TO DO: CHECK].
-If a typical thickness of an oblate disk was around $q_0 \sim 0.2$ [TO DO: REF: Holmberg 1985], the inclination would follow from $\cos^2 i = \frac{q'^2 - q_0^2}{1 - q_0^2}$ and a correction of $+3^\circ$ [TO DO: REF: Tully 1988].
+This is similar to the disk axis ratio of $q' = 0.40$ found by \citet{SWELLSI}.
+If a typical thickness of an oblate disk was around $q_0 \sim 0.2$ \citep{1958MeLu2.136....1H}, the inclination would follow from $\cos^2 i = \frac{q'^2 - q_0^2}{1 - q_0^2}$ and a correction of $+3^\circ$ \citep{1988ngc..book.....T}.
 Our estimate for the inclination is therefore $i \approx 70^\circ$.
+Given this inclination, the 2D MGE models can be deprojected into three dimensions (see Section \ref{sec:MGE_theo}).
 

### 2015-09-14 docs/results_JAMwithNFW_v1.01.tex
Corrected some plots.

@@
 \begin{equation*}
-\rho_\text{NFW}(r) \propto 1 / \frac{r}{R_\text{s,NFW}} \left( 1 + \frac{r}{R_\text{s,NFW}} \right)^2.
+\rho_\text{NFW}(r) \propto 1 / \frac{r}{r_s} \left( 1 + \frac{r}{r_s} \right)^2.
 \end{equation*}
-The NFW halo has two free parameters, the scale length $R_\text{s,NFW}$ and a parameter describing the total mass of the halo.
+The NFW halo has two free parameters, the scale length $r_s$ and a parameter describing the total mass of the halo.
 We use $v_\text{200}$, which is the circular velocity at the radius $r_\text{200}$ within which the mean density of the halo is 200 times the cosmological [TO DO: how to express this] critical density, i.e.
@@
 with $\rho_\text{crit}(z=0)=1.43 \cdot 10^{-7} M_\odot / \text{pc}^3$ in the WMAP5 cosmology by \citet{WMAP5cosm}.
-How much the mass is concentrated in the center of the NFW halo is given by the concentration of the NFW halo defined by $c_{200}\equiv r_{200} / R_{s,NFW}$.
+How much the mass is concentrated in the center of the NFW halo is given by the concentration of the NFW halo defined by $c_{200}\equiv r_{200} / r_s$.
 [TO DO: so toll ist das mit der Radiusbenennung noch nicht.????].
@@
 
-\paragraph{Modelling.} The full set of fit parameters is $(\Upsilon_\text{I,*},R_\text{S,NFW},v_{200},\beta_z)$ [TO DO: $\beta$ or $\beta_0$???], where $\beta_z$ is the constant velocity anisotropy parameter (see Section \ref{sec:model_JAM}).
+\paragraph{Modelling.} The full set of fit parameters is $(\Upsilon_\text{I,*},r_s,v_{200},\beta_z)$, where $\beta_z$ is the constant velocity anisotropy parameter (see Section \ref{sec:model_JAM}).
 We will investigate this parameter space with a MCMC\footnote{The Python code package for \emph{emcee}, a Monte Carlo Markov Chain implementation by \citet{emcee} is available online at \url{http://dan.iel.fm/emcee/current/}.
@@
 \begin{eqnarray*}
-&&p(\Upsilon_\text{I,*},R_\text{S,NFW},v_{200},\beta) \\
-&&= \frac{1}{\ln\left( 10 R_{s,NFW}\right)} p(\log c_{200} \mid v_{200}) \cdot p(v_{200}) \cdot p(\beta), 
+&&p(\Upsilon_\text{I,*},r_s,v_{200},\beta) \\
+&&= \frac{1}{\ln\left( 10 r_s\right)} p(\log c_{200} \mid v_{200}) \cdot p(v_{200}) \cdot p(\beta), 
 \end{eqnarray*}
-where the factor $1/\ln\left( 10 R_{s,NFW}\right)$ is the Jacobian of the transformation from the halo parameters $(v_{200},\log c_{200})$ [TO DO: introduce concentration] to $(v_{200},R_{s,NFW})$.
-\\We restrict the $v_\text{rms}$ fit to a region $R' \lesssim 3.5$ arcsec, approximately within the effective half-light radius $R_\text{eff} = 2.6$ arcsec  [TO DO: make sure R' everywhere ???].
+where the factor $1/\ln\left( 10 r_s\right)$ is the Jacobian of the transformation from the halo parameters $(v_{200},\log c_{200})$ [TO DO: introduce concentration] to $(v_{200},r_s)$.
+\\We restrict the $v_\text{rms}$ fit to a region $R' \lesssim 3.5$ arcsec, approximately within the effective half-light radius $R_\text{eff} = 2.6$ arcsec.
 We also include the Einstein mass $M(<R_\text{ein}$ with a 10\% error as an additional constraint in the fit.
@@
 The mean parameters are summarized in Table \ref{tab:modelB4_bestfit}.
-We find that the best fit NFW halo strives to be more massive and with a higher concentration (due to a smaller $R_\text{s,NFW}$) than  proposed by the prior.
+We find that the best fit NFW halo strives to be more massive and with a higher concentration (due to a smaller $r_s$) than  proposed by the prior.
 At the same time the model prefers again very negative velocity anisotropies: The sample with the highest probability is pegged at the lower limit of the unifrom prior.
 Both, the concentrated halo and the low anisotropy are needed to reproduce the central dip of the $v_\text{rms}$ curve.
-There are slight covariances between $\Upsilon_\text{I,*}$,  $R_\text{s,NFW}$ and $\beta_z$: The smaller the dark matter contribution in the center (i.e.
+There are slight covariances between $\Upsilon_\text{I,*}$,  $r_s$ and $\beta_z$: The smaller the dark matter contribution in the center (i.e.
 the larger $\Upsilon_\text{I,*}$), the less concentrated is the halo (i.e.
-the larger $R_\text{s,NFW}$), the more velocity anisotropy is needed to reproduce the central dip.
+the larger $r_s$), the more velocity anisotropy is needed to reproduce the central dip.
 As the effect of $v_{200}$ is mostly at larger radii, this parameter doesn't show any covariances - but is also mostly constrained by the prior.
@@
 \includegraphics[width=0.9\linewidth]{fig/B4_contour_plot_short.ps}
-\caption{Posterior probability distribution sampled with MCMC (red dots and histograms) for a JAM model with NFW halo, parametrized by $R_\text{s,NFW}$ and $v_\text{200}$, a stellar mass distribution generated from the I-band MGE in Table \ref{tab:MGEF814W} and a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and constant velocity anisotropy $\beta_z$.
+\caption{Posterior probability distribution sampled with MCMC (red dots and histograms) for a JAM model with NFW halo, parametrized by $r_s$ and $v_\text{200}$, a stellar mass distribution generated from the I-band MGE in Table \ref{tab:MGEF814W} and a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and constant velocity anisotropy $\beta_z$.
 Shown are also the priors used for J1331's NFW halo, $\mathscr{N}(200 \text{km/s},40 \text{km/s})$ (green) and the concentration vs.
 halo mass relation by \citet{Maccio08} from Equation \ref{eq:Maccio08} in terms of $v_{200}$ vs.
-$R_\text{s,NFW}$ with $1\sigma$ scatter (blue).
+$r_s$ with $1\sigma$ scatter (blue).
 The MCMC samples are color coded according to their probability (darker red for higher probability); the sample point with the highest probability is marked by a black diamond.
@@
 The histograms of the marginalized 1D distributions are overplotted by the mean (black solid lines) and $1\sigma$ error (black dashed lines), whose values are also quoted in the figure and in Table \ref{tab:modelB4_bestfit}.
-The grey diamonds mark a random sub-selection of 12 samples; the corresponding models are shown in Figure \ref{fig:modelB4_models}.
-[TO DO: Rename $\beta_0$ to $\beta_z$, rename $R_\text{s,NFW}$ to $r_\text{s,NFW}$, rename $\Upsilon_*$ to $\Upsilon_\text{I,*}$]}
+The grey diamonds mark a random sub-selection of 12 samples; the corresponding models are shown in Figure \ref{fig:modelB4_models}.}
 \label{fig:modelB4_triangle}
@@
 velocity anisotropy & $\beta_z$ & -0.4 & $\pm$ & 0.1 \\
-NFW halo scale length & $R_\text{s,NFW}$ [kpc] & 40 & $\pm$ & 20\\
+NFW halo scale length & $r_s$ [kpc] & 40 & $\pm$ & 20\\
 NFW halo virial velocity & $v_{200}$ [km/s] & 240 & $\pm$ & 40\\
@@
 \caption{Summary of the best fit parameters of the JAM model with NFW halo from the MCMC exploration in Figure \ref{fig:modelB4_triangle}.
-The halo mass and concentration are calculated from the the best fit $R_\text{s,NFW}$ and $v_{200}$.}
+The halo mass and concentration are calculated from the the best fit $r_s$ and $v_{200}$.}
 \label{tab:modelB4_bestfit}
@@
 I would think it is actually the cylindrical $R$.] \emph{Panel c)} shows the corresponding enclosed mass profile.
-Overplotted is also the Einstein mass at the Einstein radius with a 10\% error, which was used in the fit as an additional constraint.[TO DO: radius benennungen sind irgendwie verrutscht]}
+Overplotted is also the Einstein mass at the Einstein radius with a 10\% error, which was used in the fit as an additional constraint.}
 \label{fig:modelB4_models}
@@
 \end{figure*}
-
-[TO DO: $R_\text{s,NFW}$ is a spherical radius. Should be a small $r_\text{s,NFW}$ everywhere.]

### 2015-09-14 docs/results_JAMwithSB_v1.01.tex
Corrected some plots.

@@
   \includegraphics[height=6cm]{fig/jam_G_enclMass.ps}
-  \caption{Enclosed mass and mass-to-light ratio profile.
-[TO DO: Make figure wider.
-Include legend.???] [TO DO: weird  ticks on right axis???] [TO DO: Why does this plot look different than the others???] [TO DO: Switch the two y-axes.
-It's better to have ML on the left side, to read up the central ML.] [TO DO: local mass to light ratio $\Upsilon_\text{I,tot}(R')$]}
+  \caption{Projected local mass-to-light ratio profile and enclosed mass.}
   \label{fig:enclMass_modelG}
@@
 \emph{Panel (a):} Comparison between the stellar $v_\text{rms}$ data (blue points) and the best fit model (green line).
-\emph{Panel (b):} Enclosed mass inside the projected radius $R'$ on the sky (green line, left axis) and projected mass-to-light profile $\Upsilon_\text{I,tot}(R')$ along the major axis [TO DO: CHECK???] (blue line, right axis) of the best fit model.
-The enclosed mass curve is overplotted with the independent finding for the Einstein mass $\pm 4 \%$ in Table [TO DO: TABLE REFERENCE???] (red dot) at the Einstein radius (red dotted line).
+\emph{Panel (b):} Enclosed mass inside the projected radius $R'$ on the sky (green line, right axis) and projected mass-to-light profile $\Upsilon_\text{I,tot}(R')$ along the major axis (blue line, left axis) of the best fit model.
+The enclosed mass curve is overplotted with the independent finding for the Einstein mass $\pm 4 \%$ in Table \ref{tab:bestfitlensmodel} (red dot) at the Einstein radius (red dotted line).
 The best fit mass-to-light ratios of the first four Gaussians are plotted against each Gaussians $\sigma$ (yellow stars).
 The two Gaussians with the largest $\sigma$ (the fifth is not shown) have the same best fit mass-to-light ratio.
-Overplotted is also the effective half-light ratio $R_\text{eff}$ (black dotted line).}
+Overplotted is also the effective half-light ratio $R_\text{eff}$ (black dotted line).
+[TO DO: These plots look slightly different, because they were created directly as ps files.
+The others have to be re plotted to look the same.] }
 \label{fig:modelG}

### 2015-09-15 docs/results_JAMwithSB_v1.01.tex
Finished the first draft version (only summary and a few references are still missing).

@@
-\subsection{JAM based on Surface Brightness} \label{sec:results_JAM_SB}
+\subsection{JAM based on surface brightness} \label{sec:results_JAM_SB}
 
-\paragraph{...
-with the Lens Mass Model.} Our first JAM model uses the mass distribution which we found from lensing constraints in Section \ref{sec:results_lensing} to generate an independent prediction for the $v_\text{rms}$ curve following the procedure in Section \ref{sec:model_JAM}.
-In addition to the flat rotation curve model with $\alpha = 1$ in Table \ref{tab:bestfitlensmodel}, we also investigate a lens model, which was found as a best fit to the lensing images when assuming a [TO DO: rising or droppint???] rotation curve slope of $\alpha=1.1$.
+\paragraph{JAM with lens mass model.} Our first JAM model uses the mass distribution which we found from lensing constraints in Section \ref{sec:results_lensing} to generate an independent prediction for the $v_\text{rms}$ curve following the procedure in Section \ref{sec:model_JAM}.
+In addition to the flat rotation curve model with $\alpha = 1$ in Table \ref{tab:bestfitlensmodel}, we also investigate a lens model, which was found as a best fit to the lensing images when assuming a slightly rising rotation curve slope of $\alpha=1.1$.
 The predictions are compared with the data in Figure \ref{fig:JAM_modelL}.
@@
 
-\paragraph{...
-with "Mass-follows-Light" and Velocity Anisotropy.} Our second JAM model is a mass-follows-light model, which are often used in dynamical JAM modelling (e.g.
+\paragraph{JAM with "mass-follows-light" and velocity anisotropy.} Our second JAM model is a mass-follows-light model, which are often used in dynamical JAM modelling (e.g.
 \citet{GlennEC,Cap06}), where the mass distribution ins generated by multiplying the intrinsic light distribution $\nu(R,z)$ (the MGE given in Table \ref{tab:MGEF814W} deprojected according to the inclination) by a constant total mass-to-light ratio  $\Upsilon_\text{I,tot}^\text{dyn}$.
@@
 
-\paragraph{...
-with Increasing Mass-to-Light Ratio.} In Section \ref{sec:results_lensing} we found from the lensing, that the light distribution might drop faster with radius than the mass distribution.
+\paragraph{JAM with increasing mass-to-light ratio.} In Section \ref{sec:results_lensing} we found from the lensing, that the light distribution might drop faster with radius than the mass distribution.
 This would correspond to a radially increasing total mass-to-light ratio.
@@
 \\Figure \ref{fig:enclMass_modelG} shows the (local projected) mass-to-light ratio gradient generated by the best fit to the dynamics data, which rises from $\Upsilon_\text{I,tot} = 2.53$ in the center and approaches a value of $\Upsilon_\text{I,tot}$ outside of the fitted region at $R'\gtrsim 3$ arcsec of $\Upsilon_\text{tot} = 7.60)$.
-The central mass-to-light ratio corresponds to the Chabrier IMF stellar mass-to-light ratio found by [TO DO: REF: TREU ET AL 2011] $\Upsilon_\text{I,*}^\text{chab} = 2.5 \pm 0.6$ [TO DO: introduce and explain????].
-The strong rise of $\Upsilon_\text{I,tot}(R')$ cannot be explained by an increase in the stellar $\Upsilon_\text{i,*}$ alone [TO DO: Really???
-Maybe it would have dropped again in the blue disk, if I had allowed for it????], so we deduce that we might need  contribution of dark matter halo in J1331.
+The central mass-to-light ratio corresponds to the mass-to-light ratio found in Table \ref{tab:previousresults} based on the results of \citet{SWELLSI} assuming a stellar population with an \citet{Chabrier2003} initial mass-function (IMF, see also Section \ref{sec:MLdiscussion}), $\Upsilon_\text{I,*}^\text{chab} = 2.5 \pm 0.6$.
+When assuming that galaxy bulges are generally older and redder in the center [TO DO: REF], i.e.
+$\Upsilon_\text{I,*}$ is rather dropping with increasing radius than increasing, the strong rise of $\Upsilon_\text{I,tot}(R')$ might be due to a strong contribution of dark matter in J1331.
 \\Figure \ref{fig:JAM_modelG} shows that the best fit model greatly reproduces the central dip in the $v_\text{rms}$ curve, even though it has slight problems fitting the drop around $R' \sim 4$ arcsec.
@@
 A slight drop could be expected when the reddish bulge turns into the bluish disk and the contribution of the stellar component becomes less due to a lower $\Upsilon_\text{I,*}$ for younger and bluer populations.
-\\In Figure \ref{fig:enclMass_modelG} we overplot the enclosed mass profile with the Einstein mass $M_\text{ein} = (7.77 \pm 0.33) \cdot 10^{10} M_\odot$ at the Einstein radius found from lensing in Table [TO DO: REF].
+\\In Figure \ref{fig:enclMass_modelG} we overplot the enclosed mass profile with the Einstein mass $M_\text{ein} = (7.77 \pm 0.33) \cdot 10^{10} M_\odot$ at the Einstein radius found from lensing in Table \ref{tab:bestfitlensmodel}.
 The agreement between the Einstein mass and the independently found $M(<R_\text{ein}) = 7.49 \cdot 10^{10} M_\odot$ from dynamical modelling is striking.
@@
 The two Gaussians with the largest $\sigma$ (the fifth is not shown) have the same best fit mass-to-light ratio.
-Overplotted is also the effective half-light ratio $R_\text{eff}$ (black dotted line).
-[TO DO: These plots look slightly different, because they were created directly as ps files.
-The others have to be re plotted to look the same.] }
+Overplotted is also the effective half-light ratio $R_\text{eff}$ (black dotted line).}
 \label{fig:modelG}

### 2015-09-15 docs/results_photometry_v1.01.tex
Finished the first draft version (only summary and a few references are still missing).

@@
-\subsection{Surface Photometry for J1331 with MGEs} \label{sec:MGE_results}
+\subsection{Surface photometry for J1331 with MGEs} \label{sec:MGE_results}
 
@@
 Check, that everything is correct and the naming of quantities, e.g.
-with or without subscripts of 0, is fine???] [TO DO: Maybe shift to appendix or theory part???]
+with or without subscripts of 0, is fine???]
 
@@
 
-\paragraph{[TO DO: Stuff to mention]}
-\begin{itemize}
-\item the deporjecten if the galaxy under the assumption of oblate axisymmetry and an estimated inclination of $\sim70^\circ$ can be performed analytically.
-\end{itemize}
+[TO DO: Reff and Rein are also projected radii. Maybe prime them as well?]

### 2015-09-15 archive/docs/model_lensing_v1.02.tex
Started second draft version (waiting for comments by Glenn and Aaron).

--- 2015-09-11 docs/model_lensing_v1.02.tex
@@
-\subsection{Strong Gravitational Lensing Formalism and Lens Model} \label{sec:lensing_theo}
+\subsection{Strong gravitational lensing formalism and lens model} \label{sec:lensing_theo}
 
-\paragraph{Lensing Formalism.} A gravitational lens is a mass distribution, whose gravitational potential $\Phi$ acts as a lens for light coming from a source positioned somewhere on a plane behind the lens.
+\paragraph{Lensing formalism.} A gravitational lens is a mass distribution, whose gravitational potential $\Phi$ acts as a lens for light coming from a source positioned somewhere on a plane behind the lens.
 The angular diameter distance from the observer to the lens is $D_d$, to the source plane it is $D_s$ and the distance between the lens and source plane is $D_{ds}$.
@@
 
-\paragraph{Lens Model.} Following \citet{EvansWitt} we assume a scale-free model
+\paragraph{Lens model.} Following \citet{EvansWitt} we assume a scale-free model
 \begin{equation}

### 2015-09-15 docs/discussion_merger_v2.01.tex
Started second draft version (waiting for comments by Glenn and Aaron).

--- 2015-08-04 docs/discussion_merger_v1.01.tex
@@
-\subsection{Does J1331 have a Merger History?}
+\subsection{On J1331's possible merger history}
 
-[TO DO]
+\paragraph{Counter-rotating core and minor merger.} J1331 has a large counter-rotating stellar core within $\sim 2$ arcsec.
+This suggests a process in J1331's past in which two components with angular momenta oriented in opposite directions were involved.
+Accretion of gas on retrograde orbits and subsequent star formation could lead to a younger and counter-rotating stellar population [TO DO: REF].
+However, the to form enough stars such that the net rotation of the large and massive core is retrograde, a very large amount of gas would have had to be accreted by J1331- which is not very likely [TO DO: REF].
+Another scenario are galaxy mergers.
+The products of major mergers of similarly massive disk galaxies are often quiescent, elliptical galaxies \citep{1972ApJ...178..623T} [TO DO: correct reference???].
+Therefore a minor merger is more likely to have occured in J1331.
+The dense nucleus of a satellite galaxy on a retrograde orbit could survive the dissipationless accretion and could spiral to core due to tidal friction \citep{1984ApJ...287..577K}.
+Usually large bulges of spirals or ellipticals are reddest in the center and become bluer further out.
+Because star formation in low-mass satellite galaxies occurred later than in massive galaxies [TO DO: REF], the merger remnant would now host a younger and bluer population with lower velocity dispersion within the older and redder bulge of the massive progenitor.
+Such a reverse color gradient could correspond to an increasing stellar mass-to-light ratio.
+\\The minor merger theory could explain and support our findings from dynamical modelling and the previous sections, that J1331 might have an increasing stellar mass-to-light ratio within its core.
+
+\paragraph{Possible modelling failures for merger remnants.} Another effect that minor mergers can have on galaxies are a misalignement (warp) of the photometric and kinematic major axis [TO DO: REF].
+Would this be the case for J1331 the assumption of axisymmetry is not true anymore and our dynamical modelling would fail.
+\\Mergers also could have changed the 3D shape of the dark matter halo and the NFW halo was therefore not a good model for J1331's dark matter halo.
+We also tried to model J1331 with a cored logarithmic halo.
+However, due to degeneracies in the modelling, we were not able to either constrain the profile for a cored logarithmic halo, or to rule it out.
+
+\subsection{Future work}
+
+Standard JAM modelling approaches seem not to work for J1331.
+A JAM model for J1331 would need to allow for stellar mass-to-light ratio gradients within the galaxy, velocity anisotropy and a dark matter halo.
+Because of degeneracies between stellar and dark mass, and matter distribution and anisotropy profile, such a dynamical model would not lead to very tight constraints on the model parameters.
+A search for color gradients in J1331 and/or investigation of absorption line indices could support or contradict the suspicion of the existence of stellar mass-to-light ratio gradients in J133.
+Subsequently detailed stellar population analyses of the spectra taken along J1331's major axis should be conducted to constrain the mass-to-light ratio reliably.
+In addition, the dynamical modelling should use more of the available information on J1331 and fit dynamics (stellar and gas kinematics from \citet{SWELLSV}) simultaneously with the gravitational lensing (image positions, shape and even flux ratios) in a similar fashion to \citet{SWELLSIV}.
+To also model the extent, shape and flux of the lensing images, the method by \citet{2004ApJ...611..739T,2003ApJ...590..673W} could be employed, which models the surface brightness distribution of the images and source on a pixelated grid.
+However, for this to work a good model for the galactic extinction would be needed.
+High-resolution integral-field spectroscopy could help with this, allow for spatially resolved stellar population analysis and dynamical modelling in two dimensions.
+This would lead to much better understanding of J1331's structure and mass distribution and therefore answer questions on how minor mergers might modify spiral galaxies.

### 2015-09-15 docs/introduction_v2.01.tex
Started second draft version (waiting for comments by Glenn and Aaron).

--- 2015-09-11 docs/introduction_v1.02.tex
@@
 Overall, observations suggest cored dark matter halos.
-This discrepancy, known as the core-cusp problem, might be due to a yet unknown interaction between dark matter and baryons [TO DO: REF].\\
+This discrepancy, known as the core-cusp problem, might be due to a yet unknown interaction between dark matter and baryons (e.g.
+\citealt{2001ApJ...560..636E} [TO DO: more REF]).\\
 
@@
   \includegraphics[width=.9\linewidth]{fig/first_glimpse_450.ps}
-  \caption{J1331 in F450W ("blue")}
+  \caption{J1331 in F450W}
   \label{fig:F450W}
@@
   \includegraphics[width=.9\linewidth]{fig/first_glimpse_814.ps}
-  \caption{J1331 in F814W ("red")}
+  \caption{J1331 in F814W}
   \label{fig:F814W}
@@
 The $v_\text{rot}$ curve reveals that J1331 is counter-rotating within $R_\text{eff}$.
-[TO DO: Projected radius $R'$ on x-axis in panel d).] [TO DO: Add (x,y) axis in figure b).???????]}
+[TO DO: Add (x,y) axis in figure b).???????]}
 \label{fig:specialJ1331}

### 2015-11-12 archive/v1/docs/data_v1.01.tex
Started corrections.

--- 2015-09-11 docs/data_v1.01.tex
@@
 \paragraph{Redshift.} [TO DO: WHO???] found from SDSS spectra that J1331 has two redshifts inside 1 arcsec: The smaller one, $z_d = 0.113$, is the redshift of J1331 itself, the larger one, $z_s = 0.254$, is the redshift of the lensed background source \citep{SWELLSIII}.
-According to its redshift and the WMAP5 [TO DO: Explain?] cosmology \citep{WMAP5cosm}, J1331 has an angular diameter distance of 414 Mpc, which translates into a transverse scaling of 1 arcsec $\hat{=}$ 2.01 kpc.
+According to its redshift and the WMAP5 [TO DO: Do I have to explain the Acronym???] cosmology \citep{WMAP5cosm}, J1331 has an angular diameter distance of 414 Mpc, which translates into a transverse scaling of 1 arcsec $\hat{=}$ 2.01 kpc.
 
-\paragraph{HST imaging.} We use the follow-up HST imaging, with which \citet{SWELLSI} confirmed that J1331 is indeed a strong gravitational lens [TO DO: REALLY???].
+\paragraph{HST imaging.} We use the follow-up HST imaging, with which \citet{SWELLSI} confirmed that J1331 is indeed a strong gravitational lens [TO DO: Was it actually SWELLS I that confirmed that???].
 They performed high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) and its WF3 CCD chip.
@@
 
-[TO DO: How to deal with the typo in J1331s name????]
+[TO DO: How to deal with the typo in J1331s name???? SWELLS call it J1331+3638, but its actual coordinates are 1331+3628.]

### 2015-11-12 archive/v1/docs/model_JAM_v1.01.tex
Started corrections.

--- 2015-09-14 docs/model_JAM_v1.01.tex
@@
 
-Jeans axisymmetric models (JAM) assume galaxies (a) to be collisionless, i.e.
+\paragraph{JAM modelling.} Jeans axisymmetric models (JAM) assume galaxies (a) to be collisionless, i.e.
 the collisionless Boltzmann equation for the distribution function $f(\vect{x},\vect{v},t)$ has to be satisfied ($\frac{\diff f(\vect{x},\vect{v},t}{\diff t} = 0$), (b) in a steady state ($\frac{\partial}{\partial t} = 0$), (c) axisymmetric (best described in cylindrical coordinates $(R,z,\phi)$ and $\frac{\partial}{\partial \phi} = 0$).
@@
 In the deprojected galactic plane the radius of zero rotation would be at a $R_0 \gtrsim 2$ arcsec, and we choose it to be at 2.2 arcsec.
+
+\paragraph{Including a NFW halo.} As mentioned above, JAM modelling allows to incorporate an invisible matter component in addition to the luminous matter in the form of an MGE.
+In Section \ref{sec:results_JAM_NFW} we will include a spherical Navarro-Frenck-White (NFW) dark matter halo \citep{Navarro+1995c,NFW96} in the dynamical model.
+The classical NFW profile has the form
+\begin{equation}
+\rho_\text{NFW}(r) \propto \frac{1}{\frac{r}{r_s} \left( 1 + \frac{r}{r_s} \right)^2} \label{eq:NFWprofile}
+\end{equation}
+and two free parameters, the scale length $r_s$ and a parameter describing the total mass of the halo.
+We will use $v_\text{200}$, which is the circular velocity at the radius $r_\text{200}$ within which the mean density of the halo is 200 times the cosmological critical density $\rho_\text{crit} \equiv (2H^2)/(8\pi G)$, i.e.
+\begin{eqnarray*}
+M_\text{200} &=& M(<r_{200})\\
+\frac{M_{200}}{ \frac 43 \pi r_{200}^3} &=& 200 \rho_\text{crit}(z=0) \\
+v_\text{200} &=& \sqrt{\frac{GM_{200}}{r_\text{200}}}
+\end{eqnarray*}
+with $\rho_\text{crit}(z=0)=1.43 \cdot 10^{-7} M_\odot / \text{pc}^3$ in the WMAP5 cosmology by \citet{WMAP5cosm}.
+How much the mass is concentrated in the center of the NFW halo is given by the concentration of the NFW halo defined by
+\begin{equation}
+c_{200}\equiv r_{200} / r_s. \label{eq:NFW_c}
+\end{equation} 
+There is a close relation between the concentration and halo mass in simulations \citep{NFW96}. \citet{Maccio08} found this relation for the WMAP5 cosmology \citep{WMAP5cosm} to be
+\begin{equation}
+\langle \log c_{200} \rangle (M_{200}) = 0.830 - 0.098 \log \left(h \frac{M_{200}}{10^{12} M_\odot} \right) \label{eq:Maccio08}
+\end{equation}
+(their equation 10), with a Gaussian scatter of $\sigma_{\log c_{200}} = 0.105$ (their Table A2).

### 2015-11-12 archive/v1/docs/results_JAMwithNFW_v1.01.tex
Started corrections.

--- 2015-09-14 docs/results_JAMwithNFW_v1.01.tex
@@
-\subsection{JAM with a NFW Dark Matter Halo} \label{sec:results_JAM_NFW}
+\subsection{JAM with a NFW dark matter halo} \label{sec:results_JAM_NFW}
 
-\paragraph{Including a NFW halo.} The dynamical modelling attempts in the previous sections suggest that J1331's inner regions have a slightly more roundish and at large radii more massive mass distribution than expected from the distribution of stars alone.
+\paragraph{Including a dark matter halo.} The dynamical modelling attempts in the previous sections suggest that J1331's inner regions have a slightly more roundish and at large radii more massive mass distribution than expected from the distribution of stars alone.
 A dark matter halo in addition to the stellar component could explain these findings.
-We therefore proceed by modelling the mass distribution with a) a stellar component, which we get from the light MGE in Table \ref{tab:MGEF814W} (deprojected to the intrinsic $\nu(R,z)$) times a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$), and b) a spherical NFW [TO DO: introduce abbreviation somewhere] dark matter component \citep{Navarro+1995c,NFW96}.
-In the JAM modelling we use a 10-Gaussian MGE fit to the classical NFW profile
-\begin{equation*}
-\rho_\text{NFW}(r) \propto 1 / \frac{r}{r_s} \left( 1 + \frac{r}{r_s} \right)^2.
-\end{equation*}
-The NFW halo has two free parameters, the scale length $r_s$ and a parameter describing the total mass of the halo.
-We use $v_\text{200}$, which is the circular velocity at the radius $r_\text{200}$ within which the mean density of the halo is 200 times the cosmological [TO DO: how to express this] critical density, i.e.
-\begin{eqnarray*}
-M_\text{200} &=& M(<r_{200})\\
-\frac{M_{200}}{ \frac 43 \pi r_{200}^3} &=& 200 \rho_\text{crit}(z=0) \\
-v_\text{200} &=& \sqrt{\frac{GM_{200}}{r_\text{200}}}
-\end{eqnarray*}
-with $\rho_\text{crit}(z=0)=1.43 \cdot 10^{-7} M_\odot / \text{pc}^3$ in the WMAP5 cosmology by \citet{WMAP5cosm}.
-How much the mass is concentrated in the center of the NFW halo is given by the concentration of the NFW halo defined by $c_{200}\equiv r_{200} / r_s$.
-[TO DO: so toll ist das mit der Radiusbenennung noch nicht.????].
-There is a close relation between the concentration and halo mass in simulations \citep{NFW96}.
-\citet{Maccio08} found this relation for the WMAP5 cosmology \citep{WMAP5cosm} to be
-\begin{equation}
-\langle \log c_{200} \rangle (M_{200}) = 0.830 - 0.098 \log \left(h \frac{M_{200}}{10^{12} M_\odot} \right) \label{eq:Maccio08}
-\end{equation}
-(their equation 10), with a Gaussian scatter of $\sigma_{\log c_{200}} = 0.105$ (their Table A2).
+We therefore proceed by modelling the mass distribution with a) a stellar component, which we get from the light MGE in Table \ref{tab:MGEF814W} (deprojected to the intrinsic $\nu(R,z)$) times a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$), and b) a spherical NFW dark matter component (see Section \ref{sec:model_JAM}) with free parameters halo scale length $r_s$ and circular velocity at the virial radius $v_{200}$.
+In the JAM modelling we use a 10-Gaussian MGE fit to the classical NFW profile in Equation \ref{eq:NFWprofile}.
 
-\paragraph{Modelling.} The full set of fit parameters is $(\Upsilon_\text{I,*},r_s,v_{200},\beta_z)$, where $\beta_z$ is the constant velocity anisotropy parameter (see Section \ref{sec:model_JAM}).
+\paragraph{Modelling and priors.} The full set of fit parameters is $(\Upsilon_\text{I,*},r_s,v_{200},\beta_z)$, where $\beta_z$ is the constant velocity anisotropy parameter (see Section \ref{sec:model_JAM}).
 We will investigate this parameter space with a MCMC\footnote{The Python code package for \emph{emcee}, a Monte Carlo Markov Chain implementation by \citet{emcee} is available online at \url{http://dan.iel.fm/emcee/current/}.
 The version from October 2013 was used in this work.} \citep{emcee} and use priors for the halo parameters to guide the fit to a realistic NFW halo shape.
-\\\citet{Dutton10} give a relation for halo vs. stellar mass for late-type galaxies. For an Chabrier IMF stellar population they found
+\\\citet{Dutton10} give a relation for halo vs. stellar mass for late-type galaxies. For a stellar population with a Chabrier IMF they found
 \begin{equation*}
@@
 The parameters for the mean and $2\sigma$ error curves for this relation are$\alpha = -0.5\pm0.15$, $\beta = 0$, $\gamma = 1.0$, $\log_{10} x_0 = 10.4$, $\log_{10} {y_0}_{-0.24}^{+0.28}$ \citet{Dutton10}.
-Using the stellar mass estimate for J1331 from \citet{SWELLSI} $m_* = (1.06 \pm 0.25) \cdot 10^{11} M_\odot$ for the Chabrier IMF estimate [TO DO: introduce somewhere], we find ${v_{200}} = (202_{-33}^{+44})_{-13}^{+12}$.
+Using the stellar mass estimate for J1331 from \citet{SWELLSI} $m_* = (1.06 \pm 0.25) \cdot 10^{11} M_\odot$ for the Chabrier IMF estimate, we find ${v_{200}} = (202_{-33}^{+44})_{-13}^{+12}$.
 The first of the two quoted errors is due to the $2\sigma$ scatter in the relation by \citet{Dutton10}.
@@
 \end{eqnarray*}
-where the factor $1/\ln\left( 10 r_s\right)$ is the Jacobian of the transformation from the halo parameters $(v_{200},\log c_{200})$ [TO DO: introduce concentration] to $(v_{200},r_s)$.
+where the factor $1/\ln\left( 10 r_s\right)$ is the Jacobian of the transformation from the halo parameters $(v_{200},\log c_{200})$ to $(v_{200},r_s)$.
 \\We restrict the $v_\text{rms}$ fit to a region $R' \lesssim 3.5$ arcsec, approximately within the effective half-light radius $R_\text{eff} = 2.6$ arcsec.
@@
 \emph{Panel b)} shows the circular velocity curve of the total mass (green), and separately the contribution of the stellar mass (yellow, again generated from the MGE in Table \ref{tab:MGEF814W}) and dark matter (grey).
-[TO DO: Is this really the spherical $r$?
-I would think it is actually the cylindrical $R$.] \emph{Panel c)} shows the corresponding enclosed mass profile.
+[TO DO: maybe make one separate circular velocity plot, that also contains the mass-follows-light with Einstein M/L vcirc and compares it with Aaron's vcirc curve.] \emph{Panel c)} shows the corresponding enclosed mass profile.
 Overplotted is also the Einstein mass at the Einstein radius with a 10\% error, which was used in the fit as an additional constraint.}
@@
 The velocity dispersion is simply $\sigma = \sqrt{v_\text{rms}^2 - v_\text{rot}^2}$.
-At larger radii we compare the unsymmetrized data (open blue dots), the gas kinematics from \citet{SWELLSV} (green diamonds) and a JAM model using the same model parameters but the light distribution MGE generated from the Ellipse model in Figure [TO DO: REF FIGURE] as a prediction for the outer regions of J1331 (red dashed lines).
+At larger radii we compare the unsymmetrized data (open blue dots), the gas kinematics from \citet{SWELLSV} (green diamonds) and a JAM model using the same model parameters but the light distribution MGE generated from the Ellipse model in Figure \ref{fig:MGEouterRegions} as a prediction for the outer regions of J1331 (red dashed lines).
 The central regions are very well reproduced and we can also greatly predict the rotation curve at larger radii.

### 2015-11-12 archive/v1/docs/results_lensing_v1.02.tex
Started corrections.

--- 2015-09-14 docs/results_lensing_v1.02.tex
@@
-\subsection{Mass distribution from Lensing} \label{sec:results_lensing}
+\subsection{Mass distribution from lensing} \label{sec:results_lensing}
 
-\paragraph{Image Positions.} We determine the positions of the lensing images by first subtracting a smooth model for the galaxy's surface brightness from the original image.
+\paragraph{Image positions.} We determine the positions of the lensing images by first subtracting a smooth model for the galaxy's surface brightness from the original image.
 As models we use MGE fits and IRAF ellipse fits  (see Sections \ref{sec:MGE_theo} and \ref{sec:MGE_results})  to the galaxy in each the F450W and F814W filter.
@@
 
-\paragraph{Comparison with Light Distribution.} The surface mass distribution as predicted by the best fit model in Table \ref{tab:bestfitlensmodel} is shown in Figure \ref{fig:lenscomparemass}.
+\paragraph{Comparison with light distribution.} The surface mass distribution as predicted by the best fit model in Table \ref{tab:bestfitlensmodel} is shown in Figure \ref{fig:lenscomparemass}.
 We introduced random noise according to the uncertainties in the Fourier shape parameters to create a mock observation that visualizes the effect of the measurement errors.

### 2015-11-12 archive/v2/docs/discussion_ML_v2.01.tex
Started corrections.

--- 2015-09-14 docs/discussion_ML_v1.02.tex
@@
 
-\subsection{On J1331's Stellar Mass-to-Light Ratio} \label{sec:MLdiscussion}
+\subsection{On J1331's stellar mass-to-light ratio} \label{sec:MLdiscussion}
 
@@
 The circular velocity curve $v_\text{circ}(R) = \left.
-sqrt{R \frac{\partial \Phi}{\partial R}} \right|_{z=0}$ \citet{SWELLSV} find for J1331 peaks at $v_\text{circ}(R\sim0.9 \text{arcsec}) \sim 350 \text{km s}^{-1}$ (from lensing constraints only) and at $v_\text{circ}(R\sim0.9 \text{arcsec}) \sim 370 \text{km s}^{-1}$ (when including a dark matter halo and gas kinematics in the fit).
+\sqrt{R \frac{\partial \Phi}{\partial R}} \right|_{z=0}$ \citet{SWELLSV} find for J1331 peaks at $v_\text{circ}(R\sim0.9 \text{arcsec}) \sim 350 \text{km s}^{-1}$ (from lensing constraints only) and at $v_\text{circ}(R\sim0.9 \text{arcsec}) \sim 370 \text{km s}^{-1}$ (when including a dark matter halo and gas kinematics in the fit).
 We get a very similar circular velocity curve (at least at small radii) for a mass-follows-light model with constant $\Upsilon_\text{I,tot}^\text{ein} = 5.6$, which peaks at $v_\text{circ}(R\sim0.9 \text{arcsec}) \sim 360 \text{km s}^{-1}$.

### 2015-11-13 docs/abstract_v3.01.tex
Included corrections in abstract and introduction.

We analyse the stellar and dark matter distribution in the spiral galaxy SDSS J1331+3638 (J1331) by means of two independent methods: gravitational lensing and dynamical modelling. Hubble Space Telescope (HST) imaging by the SWELLS survey shows, that J1331's bulge is superimposed by a quadruplet of extended lensing images. By fitting a gravitational potential model to the image positions, we tightly constrain the mass inside the Einstein radius $R_\text{ein}=(0.91\pm0.02)''(\simeq1.83\pm0.04~\text{kpc})$ to within 4\%: $M_\text{ein} = (7.8\pm0.3) \cdot 10^{10} M_\odot$. According to long-slit major axis stellar kinematics, J1331 has a counter-rotating stellar core inside $\sim 2''(\simeq4.02~\text{kpc})$. We model the observed stellar kinematics in J1331's central regions by finding Multi-Gaussian Expansion (MGE) models for the stellar and dark matter distribution that solve the axisymmetric Jeans equations. We find that J1331 requires a steep total mass-to-light ratio gradient in the center to reproduce the observed stellar kinematics. The best fit dynamical model predicts a total mass inside the Einstein radius consistent with the lens model, and vice versa the lens model gives an successful prediction for the observed kinematics in the galaxy center. For a dynamical model including a NFW dark matter halo,  we constrain the halo to have virial velocity $v_{200} \simeq 240 \pm 40$ km/s and a concentration of $c_{200} \simeq 8 \pm 2$ in case of a moderate tangential velocity anisotropy of $\beta_z \simeq -0.4 \pm 0.1$. The NFW halo models can successfully reproduce the signatures of J1331's counter-rotating stellar core and predict J1331's stellar and gas rotation curve at larger radii. However, all these models are more massive than expected from the stellar velocity dispersion at larger radii alone. We speculate that this could indicate a non-trivial re-distribution of matter due to a possible merger event in J1331's past. This could have resulted in a stellar core in J1331's very center with a Milky-Way-like Kroupa/Chabrier initial mass function (IMF), surrounded by a extended stellar bulge population with an IMF even more bottom-heavy than a Salpeter IMF \Wilma{[TO DO: Word limit is 250.]}.

### 2015-11-13 docs/data_v3.01.tex
Included corrections in abstract and introduction.

--- 2015-09-11 docs/data_v1.01.tex
@@
 
-\paragraph{Redshift.} [TO DO: WHO???] found from SDSS spectra that J1331 has two redshifts inside 1 arcsec: The smaller one, $z_d = 0.113$, is the redshift of J1331 itself, the larger one, $z_s = 0.254$, is the redshift of the lensed background source \citep{SWELLSIII}.
-According to its redshift and the WMAP5 [TO DO: Explain?] cosmology \citep{WMAP5cosm}, J1331 has an angular diameter distance of 414 Mpc, which translates into a transverse scaling of 1 arcsec $\hat{=}$ 2.01 kpc.
+\paragraph{Redshift.} \Wilma{[TO DO: WHO???]} found from SDSS spectra that J1331 has two redshifts inside $1''$: The smaller one, $z_d = 0.113$, is the redshift of J1331 itself, the larger one, $z_s = 0.254$, is the redshift of the lensed background source \citep{SWELLSIII}.
+According to its redshift and the WMAP5 \Wilma{[TO DO: Do I have to explain the Acronym???]} cosmology \citep{WMAP5cosm}, J1331 has an angular diameter distance of 414 Mpc, which translates into a transverse scaling of $1'' \hat{=} 2.01~\text{kpc}$.
 
-\paragraph{HST imaging.} We use the follow-up HST imaging, with which \citet{SWELLSI} confirmed that J1331 is indeed a strong gravitational lens [TO DO: REALLY???].
+\paragraph{HST imaging.} We use the follow-up HST imaging, with which \citet{SWELLSI} confirmed that J1331 is indeed a strong gravitational lens \Wilma{[TO DO: Was it actually SWELLS I that confirmed that???]}.
 They performed high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) and its WF3 CCD chip.
-The images we are using are a combination of four exposures with each an exposure of 400s and were drizzled to a pixel scale of 1 pixel = 0.05 arcsec.
+The images we are using are a combination of four exposures with each an exposure of 400s and were drizzled to a pixel scale of 1 pixel = $0.05''$.
 In particular we use the images in the filters F450W, to identify the positions of the bluish lensing images, and F814W to create a surface brightness MGE model of the reddish bulge (I-band), used in the JAM dynamical modelling.
@@
 They obtained long-slit spectra along J1331's major-axis with the Low Resolution Imaging Spectrograph (LRIS) on the Keck I 10m telescope.
-The width of the slot was 1 arcsec and the seeing Conditions had a FWHM of $\sim 1.1$ arcsec.
+The width of the slot was $1''$ and the seeing conditions had a FWHM of $\sim 1.1''$.
 Spectra for spatial bins of different widths along the major axis were extracted.
@@
 \\The stellar kinematics, $v_\text{rot}$, $\sigma$ and $v_\text{rms}^2=v_\text{rot}^2 + \sigma^2$ are shown in Figure \ref{fig:kinematics}.
-The rotation curve reveals a counter-rotating core within 2 arcsec $\simeq$ 4 kpc.
-Outside of $\sim 3.5$ arcsec there is a steep drop in the dispersion, which is exptected at the boundary between the pressure supported bulge and the rotationally supported disk, which appears around this radius in the F450W filter in Figure \ref{fig:F450W}.
-However, in the brighter F814W filter in Figure \ref{fig:F814W}  the large reddish bulge extends out to $\sim$5 arcsec.
-\\Inside of $\sim 4$ arcsec, the data appears to be symmetric, outside of this the assumption of axisymmetry seems not to be valid anymore, considering the data.
+The rotation curve reveals a counter-rotating core within $2''\simeq$ 4 kpc.
+Outside of $\sim 3.5''$ there is a steep drop in the dispersion, which is exptected at the boundary between the pressure supported bulge and the rotationally supported disk, which appears around this radius in the F450W filter in Figure \ref{fig:F450W}.
+However, in the brighter F814W filter in Figure \ref{fig:F814W}  the large reddish bulge extends out to $\sim5''$.
+\\Inside of $\sim 4''$, the data appears to be symmetric, outside of this the assumption of axisymmetry seems not to be valid anymore, considering the data.
 We add -2.3 km/s to the $v_\text{rot}$ to ensure $v_\text{rot}(R'=0) \sim 0$ as a possible correction term for a systematic misjudgement of the systemic velocity.
-We also symmetrize the data within 4 arcsec and asign a minimum error of $\delta v_\text{rms} > 5$ km/s to the $v_\text{rms}$ data.
-In the JAM modelling, which is based on the assumption of axisymmetry, only kinematics within $\sim 2.5$ and 4 arcsec are used.
-Another reason to restrict to modelling on the bulge region is that our MGE in Table \ref{tab:MGEF814W} is only a good representation of J1331's F814W light distribution inside $\sim 5$ arcsec.\\
+We also symmetrize the data within $4''$ and asign a minimum error of $\delta v_\text{rms} > 5$ km/s to the $v_\text{rms}$ data.
+In the JAM modelling, which is based on the assumption of axisymmetry, only kinematics within $\sim 2.5$ and $4''$ are used.
+Another reason to restrict to modelling on the bulge region is that our MGE in Table \ref{tab:MGEF814W} is only a good representation of J1331's F814W light distribution inside $\sim 5''$.\\
 
-[TO DO: How to deal with the typo in J1331s name????]
+\Wilma{[TO DO: How to deal with the typo in J1331s name???? SWELLS call it J1331+3638, but its actual coordinates are 1331+3628.]}

### 2015-11-13 docs/discussion_ML_v3.01.tex
Included corrections in abstract and introduction.

--- 2015-11-12 archive/v2/docs/discussion_ML_v2.01.tex
@@
 
-We compare our findings of the stellar mass-to-light ratios with the study by \cite{SWELLSV}: \cite{SWELLSV} found that the bulge of J1331 has an IMF more bottom-heavy than the Salpeter IMF from fitting a NFW halo to (1) the Einstein mass and (2) gas kinematics at larger radii $\gtrsim 8$ arcsec.
-In Section \ref{sec:results_JAM_NFW} we fitted the stellar kinematics within $\sim 3.5$ arcsec and the Einstein mass with a NFW halo and the best fit $\Upsilon_\text{I,*} = 4.2 \pm 0.2$ (see Table \ref{tab:modelB4_bestfit}) indicates a less bottom-heavy IMF than the Salpeter IMF.
-\cite{SWELLSV}  found systematically lower NFW halos ($v_\text{circ}(5\text{arcsec}) \sim 120 \text{km s}^{-1}$ according to their Figure 2) than we did ($v_\text{circ}(5\text{arcsec}) \sim 200 \text{km s}^{-1}$, see Figure \ref{fig:kinematics}).
+We compare our findings of the stellar mass-to-light ratios with the study by \cite{SWELLSV}: \cite{SWELLSV} found that the bulge of J1331 has an IMF more bottom-heavy than the Salpeter IMF from fitting a NFW halo to (1) the Einstein mass and (2) gas kinematics at larger radii $\gtrsim 8''$.
+In Section \ref{sec:results_JAM_NFW} we fitted the stellar kinematics within $\sim 3.5''$ and the Einstein mass with a NFW halo and the best fit $\Upsilon_\text{I,*} = 4.2 \pm 0.2$ (see Table \ref{tab:modelB4_bestfit}) indicates a less bottom-heavy IMF than the Salpeter IMF.
+\cite{SWELLSV}  found systematically lower NFW halos ($v_\text{circ}(5'') \sim 120 \text{km s}^{-1}$ according to their Figure 2) than we did ($v_\text{circ}(5'') \sim 200 \text{km s}^{-1}$, see Figure \ref{fig:kinematics}).
 We note however, that our results would be much closer to those by \citet{SWELLSV}, if we only used the lensing results at small radii as they did: The total mass-to-light ratio of $\Upsilon_\text{I,tot}^\text{ein} = 5.6$ inside the Einstein radius (see Table \ref{tab:einsteinML}).
@@
 The circular velocity curve $v_\text{circ}(R) = \left.
-\sqrt{R \frac{\partial \Phi}{\partial R}} \right|_{z=0}$ \citet{SWELLSV} find for J1331 peaks at $v_\text{circ}(R\sim0.9 \text{arcsec}) \sim 350 \text{km s}^{-1}$ (from lensing constraints only) and at $v_\text{circ}(R\sim0.9 \text{arcsec}) \sim 370 \text{km s}^{-1}$ (when including a dark matter halo and gas kinematics in the fit).
-We get a very similar circular velocity curve (at least at small radii) for a mass-follows-light model with constant $\Upsilon_\text{I,tot}^\text{ein} = 5.6$, which peaks at $v_\text{circ}(R\sim0.9 \text{arcsec}) \sim 360 \text{km s}^{-1}$.
+\sqrt{R \frac{\partial \Phi}{\partial R}} \right|_{z=0}$ \citet{SWELLSV} find for J1331 peaks at $v_\text{circ}(R\sim0.9'') \sim 350 \text{km s}^{-1}$ (from lensing constraints only) and at $v_\text{circ}(R\sim0.9'') \sim 370 \text{km s}^{-1}$ (when including a dark matter halo and gas kinematics in the fit).
+We get a very similar circular velocity curve (at least at small radii) for a mass-follows-light model with constant $\Upsilon_\text{I,tot}^\text{ein} = 5.6$, which peaks at $v_\text{circ}(R\sim0.9'') \sim 360 \text{km s}^{-1}$.
 From this comparison follows, that the model by \citet{SWELLSV} corresponds approximately to a mass-follows-light model in the inner regions of J1331.
@@
 
-Another feature in the stellar kinematics, that none of our JAM models was able to reproduce in the slightest and which we therefore excluded in the modelling, was the dip in $v_\text{rms}$ around $\sim 6$ arcsec, which occurs around the transition from bulge to disk (see Figures \ref{fig:F814W} and \ref{fig:kinematics}).\\
+Another feature in the stellar kinematics, that none of our JAM models was able to reproduce in the slightest and which we therefore excluded in the modelling, was the dip in $v_\text{rms}$ around $\sim 6''$, which occurs around the transition from bulge to disk (see Figures \ref{fig:F814W} and \ref{fig:kinematics}).\\
 
@@
 (According to Figure \ref{fig:lenscompareboth} the lensing result might not predict a mass to light ratio gradient inside $R_\text{ein}$, but then again the mass slope $alpha=1$ was only weakly constrained.) The disk of J1331 has a lower $\Upsilon_\text{I,*}$ than the bulge (see Table \ref{tab:previousresults} according to \citet{SWELLSI}).
-Such a drop in $\Upsilon_\text{I,*}$ at the transition region from bulge to disk around $\sim 5$ arcsec could lead to the observed drop in $v_\text{rms}$, while an increasing contribution of a lower mass dark matter halo at larger radii as found by \citet{SWELLSV}, would recover the kinematics in the out regions of J1331's disk.\\
+Such a drop in $\Upsilon_\text{I,*}$ at the transition region from bulge to disk around $\sim 5''$ could lead to the observed drop in $v_\text{rms}$, while an increasing contribution of a lower mass dark matter halo at larger radii as found by \citet{SWELLSV}, would recover the kinematics in the out regions of J1331's disk.\\
 
-[TO DO: Why are disk and bulge mass in SWELLS I different to the one in SWELLS IV??]
+\Wilma{[TO DO: Why are disk and bulge mass in SWELLS I different to the one in SWELLS IV??]}
 

### 2015-11-13 docs/discussion_merger_v3.01.tex
Included corrections in abstract and introduction.

--- 2015-09-15 docs/discussion_merger_v2.01.tex
@@
 
-\paragraph{Counter-rotating core and minor merger.} J1331 has a large counter-rotating stellar core within $\sim 2$ arcsec.
+\paragraph{Counter-rotating core and minor merger.} J1331 has a large counter-rotating stellar core within $\sim 2''$.
 This suggests a process in J1331's past in which two components with angular momenta oriented in opposite directions were involved.
-Accretion of gas on retrograde orbits and subsequent star formation could lead to a younger and counter-rotating stellar population [TO DO: REF].
+Accretion of gas on retrograde orbits and subsequent star formation could lead to a younger and counter-rotating stellar population \Wilma{[TO DO: REF]}.
 However, the to form enough stars such that the net rotation of the large and massive core is retrograde, a very large amount of gas would have had to be accreted by J1331- which is not very likely [TO DO: REF].
@@
 Usually large bulges of spirals or ellipticals are reddest in the center and become bluer further out.
-Because star formation in low-mass satellite galaxies occurred later than in massive galaxies [TO DO: REF], the merger remnant would now host a younger and bluer population with lower velocity dispersion within the older and redder bulge of the massive progenitor.
+Because star formation in low-mass satellite galaxies occurred later than in massive galaxies \Wilma{[TO DO: REF]}, the merger remnant would now host a younger and bluer population with lower velocity dispersion within the older and redder bulge of the massive progenitor.
 Such a reverse color gradient could correspond to an increasing stellar mass-to-light ratio.
@@
 
-\paragraph{Possible modelling failures for merger remnants.} Another effect that minor mergers can have on galaxies are a misalignement (warp) of the photometric and kinematic major axis [TO DO: REF].
+\paragraph{Possible modelling failures for merger remnants.} Another effect that minor mergers can have on galaxies are a misalignement (warp) of the photometric and kinematic major axis \Wilma{[TO DO: REF]}.
 Would this be the case for J1331 the assumption of axisymmetry is not true anymore and our dynamical modelling would fail.

### 2015-11-13 docs/introduction_v3.01.tex
Included corrections in abstract and introduction.

--- 2015-09-15 docs/introduction_v2.01.tex
@@
 Combining them allows for valuable cross-checking opportunities to resolve degeneracies inherent in both methods.
-It can also help to disentangle the stellar and dark matter content of galaxies, of which the latter is still shrouded by many open questions.\\
+It can also help to disentangle the stellar and dark matter content of galaxies.
 
 %Dark Matter
-The flat rotation curves of galaxies (deduced from e.g.
-the stellar movements in the solar neighbourhood \citep{1932BAN.....6..249O} and $H\alpha$ rotation curves in external galaxies \citep{1978ApJ...225L.107R}) were the first indication that galaxies might reside in massive, almost spherical halos made of invisible ``dark'' matter.
-The standard model of cosmology, based on results by the Planck Mission \citep{WMAP5cosm}, predicts that $\sim 85\%$ of the universe's total matter content is in the form of non-baryonic cold dark matter.
+The flat rotation curves of galaxies \citep{1978ApJ...225L.107R} were the first indication that galaxies might reside in massive, almost spherical halos made of invisible ``dark'' matter.
+The standard model of cosmology, based on results by the Planck Mission \citep{WMAP5cosm} \Wilma{[TO DO: Aaron thinks Dunkley is a WMAP paper....
+Check difference WMAP/Planck...]}, infers that $\sim 85\%$ of the universe's total matter content is in the form of non-baryonic cold dark matter.
 Simulations suggest that this kind of dark matter forms cuspy halos following a Navarro-Frenck-White (NFW) profile \citep{NFW96}.
-However, central dark matter density cusps are not observed in dark matter dominated dwarf galaxies [TO DO: REF].
-If they exist in more massive galaxies depends strongly on stellar mass-to-light ratio [TO DO: REF].
+However, central dark matter density cusps are not observed in dark matter dominated dwarf galaxies \Wilma{[TO DO: REF: Aaron suggests Moore 1994, de Blok et al.
+2001]}.
+Their existence in more massive galaxies depends strongly on stellar mass-to-light ratio \Wilma{[TO DO: REF: Aaron suggests Dutton et al.
+2011 "dark halo response and the IMF"]}.
 Overall, observations suggest cored dark matter halos.
-This discrepancy, known as the core-cusp problem, might be due to a yet unknown interaction between dark matter and baryons (e.g.
-\citealt{2001ApJ...560..636E} [TO DO: more REF]).\\
+This discrepancy, known as the core-cusp problem, might be resolved by galaxy formation processes such as mergers and outflows (e.g., \citealt{2001ApJ...560..636E} \Wilma{[TO DO: more REF: Aaron suggests Pontzen \& Governato 2012]}).
 
-Determining the overall mass distribution in massive galaxies and separating the dark from the stellar mass components is therefore a crucial step in better understanding the structure of galaxies and nature or dark matter.\\
+Determining the overall mass distribution in massive galaxies and separating the dark from the stellar mass components is therefore a crucial step in better understanding the structure of galaxies and nature or dark matter.
 
 %Lensing
-Strong gravitational lensing is an independent method to tightly constrain the projected total mass of galaxies inside $\sim 1$ arcsec [TO DO: REF].
-Massive galaxies can act as gravitational lenses and deflect the light of background sources, giving rise to multiple distorted images of the source [TO DO: REF].
-By 2010 over 200 strong gravitational galaxy lenses had been discovered \citep{2010ARA&A..48...87T} and the number is still rising.\\
+Strong gravitational lensing is an independent method to tightly constrain the projected total mass of galaxies inside $\sim 1''$ \Wilma{[TO DO: REF: Aaron suggests Treu 2010]}.
+Massive galaxies can act as gravitational lenses and deflect the light of background sources, giving rise to multiple distorted images of the source \Wilma{[TO DO: REF]}.
+By 2010 over 200 strong gravitational galaxy lenses had been discovered \citep{2010ARA&A..48...87T} and the number is still rising.
 
 %Dynamical modelling
-The mass profile at larger galactocentric radii can be probed by gas rotation curves that directly measure the galaxy's circlar velocity profile [TO DO: REF].
+The mass profile at larger galactocentric radii can be probed by gas rotation curves that directly measure the galaxy's circlar velocity profile \Wilma{[TO DO: REF]}.
 However, due to its dissipative nature, gas motions are very sensitive to disturbances by e.g.
-spiral arms and bars [TO DO: REF].\\
-Very good and dissipationless dynamical tracers for the underlying gravitational potential are the stars.
-Their motions are complex, a bulk rotation around one principal axis combined with random motions in all coordinate directions, full dynamical modelling of rotation, dispersion and velocity anisotropies is needed to deduce the matter distribution.
-An example is axisymmetric Jeans modelling, which solves the Jeans equations for an assumed mass distribution and velocity anisotropy under the assumption of axisymmetry (e.g.
-\citealt{Cap08}).
-Degeneracies between stellar and dark matter and velocity anisotropy have to be resolved using additional assumptions.\\
-Another dynamical modelling method often applied to external galaxies is e.g. Schwarzschild's orbital superposition approach \citep{schwarzschild}.\\
-Because stars are present almost everywhere in the galaxy, stellar dynamical modelling can complement mass constraints from lensing at small and gas motions at large radii.\\
+spiral arms and bars \Wilma{[TO DO: REF]}.
+
+Because stars are dissipationless dynamical tracers and present almost everywhere in the galaxy, stellar dynamical modelling can complement mass constraints from lensing at small and gas motions at large radii.
+But stellar motions are complex: a bulk rotation around one principal axis combined with random motions in all coordinate direction.
+Full dynamical modelling of rotation, dispersion and velocity anisotropies is needed to deduce the matter distribution.
 
@@
 By combining lensing and dynamical modelling degeneracies inherent in both methods can be broken.
-SWELLS picked galaxies in SDSS whose spectra had two different redshifts within 3 arcsec, which makes it likely to capture strong lenses with typical Einstein radii of 1 arcsec.
+SWELLS picked galaxies in SDSS whose spectra had two different redshifts within $3''$, which makes it likely to capture strong lenses with typical Einstein radii of $1''$.
 Sufficiently inclined galaxies were picked by eye.
-Follow up high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) was performed to confirm their lensing status \citep{SWELLSI}.\\
+Follow up high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) was performed to confirm their lensing status \citep{SWELLSI}.
 
@@
 It is a spiral galaxy of approximate Hubble type Sb at right ascension = 202.91800$^\circ$ and a declination = 36.46999$^\circ$ (epoch J2000).
-It has bluish spiral arms and a large reddish bulge (see Figures \ref{fig:F450W} and \ref{fig:F814W}), which is superimposed by quadruplet of extended bluish images approximately at a distance of 1 arcsec from the galaxy center (see Figure \ref{fig:lens_just_imgpos}).
+It has bluish spiral arms and a large reddish bulge (see Figures \ref{fig:F450W} and \ref{fig:F814W}), which is superimposed by quadruplet of extended bluish images approximately at a distance of $1''$ from the galaxy center (see Figure \ref{fig:lens_just_imgpos}).
 The lensed object might be a star-forming blob of a background galaxy.
-J1331 stands out of the SWELLS sample because of its large counter-rotating core (see Figure \ref{fig:kinematics}), which might be an indication that J1331 underwent a minor merger in its past.\\
+J1331 stands out of the SWELLS sample because of its large counter-rotating core (see Figure \ref{fig:kinematics}), which might be an indication that J1331 underwent a minor merger in its recent past.
 
@@
 The goal of this work is to complement the previous work on J1331 by an in-depth analysis of the matter distribution in J1331's inner regions.
-We use stellar dynamical Jeans modelling in addition to lensing constraints, similar to a study of the Einstein Cross by \citet{GlennEC}.
-We attempt to disentangle the stellar and dark matter components and test if Jeans modelling works also in the presence of a counter-rotating core.
-Ideally this work on J1331 could also help understanding how minor mergers modify the mass distribution of a galaxy.\\
+We use stellar dynamical modelling in addition to lensing constraints, similar to a study of the Einstein Cross by \citet{GlennEC}.
+We attempt to disentangle the stellar and dark matter components and test if employed axisymmetric Jeans models work also in the presence of a counter-rotating core.
+Ideally this work on J1331 could also help understanding how minor mergers modify the mass distribution of a galaxy.
 
@@
 The black solid line in panel (b) shows the orientation of the major-axis.
-The line has a length of 10 arcsec and indicates the region within which we carry out the Jeans modelling.
+The line has a length of $10''$ and indicates the region within which we carry out the Jeans modelling.
 \emph{Panel (c):} The central region of J1331 in F450W, surface brightness subtracted.
-An IRAF ellipse [TO DO: How to write and reference????] fit to the F450W surface brightness in panel (a) was subtracted from the image.
+An IRAF ellipse \Wilma{[TO DO: How to write and reference????]} fit to the F450W surface brightness in panel (a) was subtracted from the image.
 The (smoothed) residuals within the white square in panel (a) are shown in panel (c).
@@
 The $v_\text{rot}$ curve reveals that J1331 is counter-rotating within $R_\text{eff}$.
-[TO DO: Add (x,y) axis in figure b).???????]}
+\Wilma{[TO DO: Replace arcsec with '' in panel d)]} \Wilma{[TO DO: Mention, that the configuration of the additional two bright blobs do not suggest that they form a lensing doublet.
+They are probably background star formation regions as well.
+The blob above A could be stretched due to lensing and have a faint counter image between B and G.
+Maybe indicate in plot?]}}
 \label{fig:specialJ1331}

### 2015-11-13 docs/model_JAM_v3.01.tex
Included corrections in abstract and introduction.

--- 2015-11-12 archive/v1/docs/model_JAM_v1.01.tex
@@
 The model in Equation \ref{eq:explicitLOSvelCap} predicts the intrinsic $\langle v_\text{los}^2 \rangle$ at a given position on the sky, which have then to be modified according to the mode of observation, to be comparable to the measurements.
-The measured $v_\text{rms}$ is a light-weighted mean for a pixel along the long-slit of the spectrograph, with height $L_y = 1$ arcsec \citep{SWELLSV} and a certain given extent in along the galaxy's major axis, $L_x$, i.e.
+The measured $v_\text{rms}$ is a light-weighted mean for a pixel along the long-slit of the spectrograph, with height $L_y = 1''$ \citep{SWELLSV} and a certain given extent in along the galaxy's major axis, $L_x$, i.e.
 for a rectangular aperture
@@
 \end{equation*}
-The light arriving at the spectrograph itself was subject to seeing, i.e. a Gaussian with Full Width Half Maximum (FWHM) of 1.1 arcsec \citep{SWELLSV}
+The light arriving at the spectrograph itself was subject to seeing, i.e. a Gaussian with Full Width Half Maximum (FWHM) of $1.1''$ \citep{SWELLSV}
 \begin{equation*}
@@
 The version from June 2012 was used in this work.} by \citet{Cap08} performs the convolution numerically.
-We set $L_x = 0.21$ arcsec as the width of the model pixel, and get a prediction for the actual measurements in bins of width 0.63, 1.26 and 1.89 arcsec \citep{SWELLSV} as light-weighted mean from each 3, 6 and 9 model pixels.
+We set $L_x = 0.21''$ as the width of the model pixel, and get a prediction for the actual measurements in bins of width $0.63''$, $1.26''$ and $1.89''$ \citep{SWELLSV} as light-weighted mean from each 3, 6 and 9 model pixels.
 
@@
 We find $\kappa'$ by matching the model $\langle v_\text{los} \rangle$ with the symmetrized $v_\text{rot}$ data, where for a given $\kappa'$ the $\kappa_k$ are found from fitting the MGE generated profile $\kappa(R) = \sum_k \kappa_k \nu_k(r)/\sum_k \nu_k(r)$ to Equation \ref{eq:kappa_profile}.
-The observed zero point is at $R'_0\approx 2$ arcsec.
-In the deprojected galactic plane the radius of zero rotation would be at a $R_0 \gtrsim 2$ arcsec, and we choose it to be at 2.2 arcsec.
+The observed zero point is at $R'_0\approx 2''$.
+In the deprojected galactic plane the radius of zero rotation would be at a $R_0 \gtrsim 2''$, and we choose it to be at $2.2''$.
 

### 2015-11-13 docs/model_MGE_v3.01.tex
Included corrections in abstract and introduction.

--- 2015-09-14 docs/model_MGE_v1.01.tex
@@
-\subsection{Multi-Gaussian Expansion Formalism} \label{sec:MGE_theo}
+\subsection{Surface brightness model} \label{sec:MGE_theo}
 
-Multi-Gaussian Expansions (MGE) are used to parametrize the observed surface brightness or projected total mass of a galaxy as a sum of $N$ two-dimensional, elliptical Gaussians \citep{1991ApJ...366..599B,1992A&A...253..366M,1994A&A...285..723E,1999MNRAS.303..495E}.
+\paragraph{Multi-Gaussian Expansion (MGE).} MGEs are used to parametrize the observed surface brightness or projected total mass of a galaxy as a sum of $N$ two-dimensional, elliptical Gaussians \citep{1991ApJ...366..599B,1992A&A...253..366M,1994A&A...285..723E,1999MNRAS.303..495E}.
 This work makes use of the algorithm and code\footnote{The IDL code package for fitting MGEs to images by \citet{Cap02} is available online at \url{http://www-astro.physics.ox.ac.uk/~mxc/software}.

### 2015-11-13 docs/results_JAMwithNFW_v3.01.tex
Included corrections in abstract and introduction.

--- 2015-11-12 archive/v1/docs/results_JAMwithNFW_v1.01.tex
@@
 where the factor $1/\ln\left( 10 r_s\right)$ is the Jacobian of the transformation from the halo parameters $(v_{200},\log c_{200})$ to $(v_{200},r_s)$.
-\\We restrict the $v_\text{rms}$ fit to a region $R' \lesssim 3.5$ arcsec, approximately within the effective half-light radius $R_\text{eff} = 2.6$ arcsec.
+\\We restrict the $v_\text{rms}$ fit to a region $R' \lesssim 3.5''$, approximately within the effective half-light radius $R_\text{eff} = 2.6''$.
 We also include the Einstein mass $M(<R_\text{ein}$ with a 10\% error as an additional constraint in the fit.
-[TO DO: Didn't include the results from the Moster 2010 relation, because they where quite close to the Dutton 2010 relation anyway.
-Or should I?]
+\Wilma{[TO DO: Didn't include the results from the Moster 2010 relation, because they where quite close to the Dutton 2010 relation anyway.
+Or should I?]}
 
@@
 The model fits the $v_\text{rms}$ data in the inner regions quite well (Figure \ref{fig:modelB4_vrms}) and is also consistent with the Einstein mass (see Figure \ref{fig:modelB4_enclMass}).
-The extrapolation of the model to larger radii however overestimates the data, does not exhibit a drop around $\sim 6$ arcsec at all and seems to be therefore overall too massive.\\
+The extrapolation of the model to larger radii however overestimates the data, does not exhibit a drop around $\sim 6''$ at all and seems to be therefore overall too massive.\\
 
@@
 \emph{Panel b)} shows the circular velocity curve of the total mass (green), and separately the contribution of the stellar mass (yellow, again generated from the MGE in Table \ref{tab:MGEF814W}) and dark matter (grey).
-[TO DO: maybe make one separate circular velocity plot, that also contains the mass-follows-light with Einstein M/L vcirc and compares it with Aaron's vcirc curve.] \emph{Panel c)} shows the corresponding enclosed mass profile.
-Overplotted is also the Einstein mass at the Einstein radius with a 10\% error, which was used in the fit as an additional constraint.}
+\Wilma{[TO DO: maybe make one separate circular velocity plot, that also contains the mass-follows-light with Einstein M/L vcirc and compares it with Aaron's vcirc curve.]} \emph{Panel c)} shows the corresponding enclosed mass profile.
+Overplotted is also the Einstein mass at the Einstein radius with a 10\% error, which was used in the fit as an additional constraint.
+\Wilma{[TO DO: Replace arcsec with '']}}
 \label{fig:modelB4_models}
@@
 
-\paragraph{Rotation curve.} Following the procedure in Section \ref{sec:model_JAM} we find the rotation curve from the best fit mean model in Table \ref{tab:modelB4_bestfit} by fitting the rotation parameter $\kappa'$ to the symmetrized $v_\text{rot}$ data within $R' = 3.5$ arcsec.
+\paragraph{Rotation curve.} Following the procedure in Section \ref{sec:model_JAM} we find the rotation curve from the best fit mean model in Table \ref{tab:modelB4_bestfit} by fitting the rotation parameter $\kappa'$ to the symmetrized $v_\text{rot}$ data within $R' = 3.5''$.
 The best fit with $\kappa' = 0.76$ is shown in the second panel of Figure \ref{fig:modelB4_vrot}.
@@
 The predicted dispersion is much larger than the data; we would expect the disk rotationally supported and therefore have a low velocity dispersion; especially dispersions as high as $\sim 200 km/s$ are more likely to be observed in the pressure supported bulges of galaxies.
-There \emph{might} be something unexpeted with the $\sigma$ measurements around $\sim 5$ arcsec, but at large radii the the best fit model NFW halo is simply too massive.
+There \emph{might} be something unexpeted with the $\sigma$ measurements around $\sim 5''$, but at large radii the the best fit model NFW halo is simply too massive.
 
@@
 The central regions are very well reproduced and we can also greatly predict the rotation curve at larger radii.
-Only at larger radii the $v_\text{rms}$ and $v_\text{rot}$ overestimate the measurements, probably due to a too massive NFW halo.}
+Only at larger radii the $v_\text{rms}$ and $v_\text{rot}$ overestimate the measurements, probably due to a too massive NFW halo.
+\Wilma{[TO DO: Replace arcsec with '']}}
 \label{fig:modelB4_vrot}

### 2015-11-13 docs/results_JAMwithSB_v3.01.tex
Included corrections in abstract and introduction.

--- 2015-09-15 docs/results_JAMwithSB_v1.01.tex
@@
 The predictions are compared with the data in Figure \ref{fig:JAM_modelL}.
-The agreement between the lensing prediction and the observed kinematics within $R' \sim 3$ arcsec is striking, especially around the Einstein radius.
+The agreement between the lensing prediction and the observed kinematics within $R' \sim 3''$ is striking, especially around the Einstein radius.
 The $\alpha = 1$ model fits the wings nicely, while the $\alpha = 1.1$ model recreates almost exactly the observed central dip.
-The sharp drop in $v_\text{rms}$ around $R' \sim 3$ arcsec cannot be reproduced, however.
+The sharp drop in $v_\text{rms}$ around $R' \sim 3''$ cannot be reproduced, however.
 But outside of the Einstein radius our lensing models are only extrapolations and the true constraint is around the Einstein radius.
@@
 The red solid line corresponds to the lens model for a flat rotation curve ($\alpha = 1$) in Table \ref{tab:bestfitlensmodel}; the green line is a best fit lens model found analogously from the image positions, but for a fixed rotation curve slope of $\alpha = 1.1$.
-For the JAM modelling a best fit MGE to the lens mass models were used, as well as the observed surface brightness MGE in Table \ref{tab:MGEF814W}, assuming velocity isotropy $\beta_z = 0$ and an inclination of $i = 70^\circ$.The red and black dotted lines are the Einstein radius and the effective half-light radius, respectively.}
+For the JAM modelling a best fit MGE to the lens mass models were used, as well as the observed surface brightness MGE in Table \ref{tab:MGEF814W}, assuming velocity isotropy $\beta_z = 0$ and an inclination of $i = 70^\circ$.The red and black dotted lines are the Einstein radius and the effective half-light radius, respectively.
+\Wilma{[TO DO: Replace arcsec with '' in panel d)]}}
   \label{fig:JAM_modelL}
@@
 We also tested radial profiles for $\beta_z(R)$ of the form proposed by \citet{BaesVanHese}, which was however equally unable to reproduce the data.
-We conclude, that this is due to the well-known degeneracy between anisotropy and mass profile [TO DO: REF] and the mass-follows-light model is \emph{not} a good representation of the mass distribution in J1331's inner regions.
+We conclude, that this is due to the well-known degeneracy between anisotropy and mass profile \Wilma{[TO DO: REF]} and the mass-follows-light model is \emph{not} a good representation of the mass distribution in J1331's inner regions.
 
@@
 The ``best'' fit is $\Upsilon_\text{I,tot}^\text{dyn} = 4.8 \pm 0.1$ and $\beta_z = -0.5$, where the latter is however pegged at the lower limit of the allowed value range.
-This is obviously not a good model.}
+This is obviously not a good model.
+\Wilma{[TO DO: Replace arcsec with '' in panel d)]}}
   \label{fig:JAM_modelA2}
@@
 We treat the five $\Upsilon_{\text{I,tot,}i}$ as free parameters and only require that $\Upsilon_{\text{I,tot,}j} \geq \Upsilon_{\text{I,tot,}i}$ when the corresponding $\sigma_j \geq \sigma_i$ to ensure an overall mass-to-light ratio that is increasing with radius.
-\\Figure \ref{fig:enclMass_modelG} shows the (local projected) mass-to-light ratio gradient generated by the best fit to the dynamics data, which rises from $\Upsilon_\text{I,tot} = 2.53$ in the center and approaches a value of $\Upsilon_\text{I,tot}$ outside of the fitted region at $R'\gtrsim 3$ arcsec of $\Upsilon_\text{tot} = 7.60)$.
+\\Figure \ref{fig:enclMass_modelG} shows the (local projected) mass-to-light ratio gradient generated by the best fit to the dynamics data, which rises from $\Upsilon_\text{I,tot} = 2.53$ in the center and approaches a value of $\Upsilon_\text{I,tot}$ outside of the fitted region at $R'\gtrsim 3''$ of $\Upsilon_\text{tot} = 7.60)$.
 The central mass-to-light ratio corresponds to the mass-to-light ratio found in Table \ref{tab:previousresults} based on the results of \citet{SWELLSI} assuming a stellar population with an \citet{Chabrier2003} initial mass-function (IMF, see also Section \ref{sec:MLdiscussion}), $\Upsilon_\text{I,*}^\text{chab} = 2.5 \pm 0.6$.
-When assuming that galaxy bulges are generally older and redder in the center [TO DO: REF], i.e.
+When assuming that galaxy bulges are generally older and redder in the center \Wilma{[TO DO: REF]}, i.e.
 $\Upsilon_\text{I,*}$ is rather dropping with increasing radius than increasing, the strong rise of $\Upsilon_\text{I,tot}(R')$ might be due to a strong contribution of dark matter in J1331.
-\\Figure \ref{fig:JAM_modelG} shows that the best fit model greatly reproduces the central dip in the $v_\text{rms}$ curve, even though it has slight problems fitting the drop around $R' \sim 4$ arcsec.
+\\Figure \ref{fig:JAM_modelG} shows that the best fit model greatly reproduces the central dip in the $v_\text{rms}$ curve, even though it has slight problems fitting the drop around $R' \sim 4''$.
 The latter might be because we only allowed the $\Upsilon_\text{I,tot}(R')$ to rise.
@@
 The two Gaussians with the largest $\sigma$ (the fifth is not shown) have the same best fit mass-to-light ratio.
-Overplotted is also the effective half-light ratio $R_\text{eff}$ (black dotted line).}
+Overplotted is also the effective half-light ratio $R_\text{eff}$ (black dotted line).
+\Wilma{[TO DO: Replace arcsec with '' in panel d)]}}
 \label{fig:modelG}

### 2015-11-13 docs/results_lensing_v3.01.tex
Included corrections in abstract and introduction.

--- 2015-11-12 archive/v1/docs/results_lensing_v1.02.tex
@@
 The image positions were determined from the lens subtracted image for J1331 in Figure 4 of \citet{SWELLSIII}, rotated to the $(x,y)$ coordinate system in Figure \ref{fig:lens_just_imgpos}.
-The pixel scale is 1 pixel = 0.05 arcsec and the error of each image position is $\pm$ 1 pixel.}
+The pixel scale is 1 pixel = $0.05''$ and the error of each image position is $\pm$ 1 pixel.}
 \label{tab:lenspos}
@@
 A Gaussian fit to the resulting distributions of best fit values leads to the constraints on the shape parameters and Einstein quantities in the second column in Table \ref{tab:bestfitlensmodel}.
-We therefore constrain the Einstein radius to within 2\%, $R_\text{ein} = (0.91 \pm 0.02)$ arcsec and the projected mass within the critical curve with a relative error of 4\%, $M_\text{crit} =(7.9\pm0.3)\cdot 10^{10} M_\odot$.
-Our measurement of $R_\text{ein}$ is consistent with that from \citet{SWELLSIII}, $R_\text{ein,SWELLS} = (0.96 \pm 0.04)$ arcsec (which used a singular isothermal ellipsoid as lens mass model and the intermediate-axis convention of the critical curve as the Einstein radius).
+We therefore constrain the Einstein radius to within 2\%, $R_\text{ein} = (0.91 \pm 0.02)''$ and the projected mass within the critical curve with a relative error of 4\%, $M_\text{crit} =(7.9\pm0.3)\cdot 10^{10} M_\odot$.
+Our measurement of $R_\text{ein}$ is consistent with that from \citet{SWELLSIII}, $R_\text{ein,SWELLS} = (0.96 \pm 0.04)''$ (which used a singular isothermal ellipsoid as lens mass model and the intermediate-axis convention of the critical curve as the Einstein radius).
 The relative difference between our critical mass and that of \citet{SWELLSIII}, $M_\text{crit,SWELLS} =(8.86\pm0.61)\cdot 10^{10} M_\odot$, is 13\%.
@@
  &  & \multicolumn{1}{c}{peak image positions}  & \multicolumn{4}{c}{of image positions }  \\ \hline
-Einstein radius      & $R_\text{ein}$ [arcsec]             & $0.907$ & $0.91$  & $\pm$ & $     0.02$ & ($2\%$)\\
+Einstein radius      & $R_\text{ein}$ [$''$]             & $0.907$ & $0.91$  & $\pm$ & $     0.02$ & ($2\%$)\\
 Einstein mass        & $M_\text{ein}$ [$10^{10} M_\odot$]  & $7.72$  & $7.8 $  & $\pm$ & $      0.3$ & ($4\%$) \\
 Critical mass        & $M_\text{crit}$ [$10^{10} M_\odot$] & $7.87$  & $7.9$   & $\pm$ & $      0.3$ & ($4\%$)\\
-Source position      & $\xi$ [arcsec]                      & $0.095$ & $0.09 $ & $\pm$ & $     0.03$ & ($28\%$)\\
-                     & $\eta$ [arcsec]                     & $0.107$ & $0.10 $ & $\pm$ & $     0.03$ & ($27\%$)\\
+Source position      & $\xi$ [$''$]                      & $0.095$ & $0.09 $ & $\pm$ & $     0.03$ & ($28\%$)\\
+                     & $\eta$ [$''$]                     & $0.107$ & $0.10 $ & $\pm$ & $     0.03$ & ($27\%$)\\
 Fourier coefficients & $a_0$                               & $1.814$ & $1.82 $ & $\pm$ & $   0.04$ & (2\%)\\
@@
 The other two right blobs (north east of A, south east of B) might be star forming regions of the background galaxy as well.
-[TO DO: Add A, B, C, D in the figure to make clear which image is which.]}
+\Wilma{[TO DO: Add A, B, C, D in the figure to make clear which image is which.]}}
 \label{fig:???}
@@
 The background in Panel (c) shows again the surface brightness subtracted center of the galaxy to make the lensing images visible.
-[TO DO: use $\Upsilon_\text{I,tot}^\text{ein}$ on colorbar]}
+\Wilma{[TO DO: use $\Upsilon_\text{I,tot}^\text{ein}$ on colorbar]}}
 \label{fig:lenslightcompareALL}

### 2015-11-13 docs/results_photometry_v3.01.tex
Included corrections in abstract and introduction.

--- 2015-09-15 docs/results_photometry_v1.01.tex
@@
 \caption{MGE for J1331's inner regions: Comparison of contours with constant F814W surface brightness of J1331's central region (orange lines) with the corresponding iso-brightness contours of the best fit MGE in Table \ref{tab:MGEF814W}, convolved with the PSF in Table \ref{tab:MGEF814W}, (gray lines).
-The MGE model is a good representation of the galaxy's light distribution along the major axis within $\sim 5$ arcsec.
+The MGE model is a good representation of the galaxy's light distribution along the major axis within $\sim 5''$.
 Image scaling and orientation are indicated in the figure.
-The black line has a length of 10 arcsec and it's orientation corresponds to the galaxy's position angle as found in Table \ref{tab:galaxyparameters}.
+The black line has a length of $10''$ and it's orientation corresponds to the galaxy's position angle as found in Table \ref{tab:galaxyparameters}.
 For comparison the Einstein radius as found in Table \ref{tab:bestfitlensmodel}  is indicated as red dashed line.
@@
 \includegraphics[width=0.8\columnwidth]{fig/1331F814W_MGE_disk_L.ps}
-\caption{MGE for J1331's outer regions: Comparison of contours with constant surface brightness of the smooth IRAF ELLIPSE [TO DO: How to write Iraf Ellipse???] model for J1331 in the F814W filter (yellow) with a corresponding best fit MGE (gray lines).
-The green box corresponds to the image section shown in Figure \ref{fig:MGEinnerRegions}, with the Einstein radius as dashed red line and the black 10 arcsec orientation line along the major axis (see Figure \ref{fig:MGEinnerRegions}).
-This MGE found from the smooth, symmetric Iraf Ellipse [TO DO] model is not used to find a dynamical model for J1331, because the dynamics in the outer regions are strongly affected by non-axisymmetries (e.g.
+\caption{MGE for J1331's outer regions: Comparison of contours with constant surface brightness of the smooth IRAF ELLIPSE \Wilma{[TO DO: How to write Iraf Ellipse???]} model for J1331 in the F814W filter (yellow) with a corresponding best fit MGE (gray lines).
+The green box corresponds to the image section shown in Figure \ref{fig:MGEinnerRegions}, with the Einstein radius as dashed red line and the black $10''$ orientation line along the major axis (see Figure \ref{fig:MGEinnerRegions}).
+This MGE found from the smooth, symmetric Iraf Ellipse \Wilma{[TO DO]} model is not used to find a dynamical model for J1331, because the dynamics in the outer regions are strongly affected by non-axisymmetries (e.g.
 spiral arms).
@@
 \centering
-\caption{F814W PSF MGE: Parameters of the circular four-Gaussian MGE in Equation \ref{eq:PSFgeneral} fitted to the radial profile of the synthetic HST/F814W PSF image by [TO DO: WHO???].}
+\caption{F814W PSF MGE: Parameters of the circular four-Gaussian MGE in Equation \ref{eq:PSFgeneral} fitted to the radial profile of the synthetic HST/F814W PSF image by \Wilma{[TO DO: WHO???]}.}
 \begin{tabular}{ccc}
 \hline
-$k$ & $G_k$ & $\delta_k$ [arcsec] \\\hline
+$k$ & $G_k$ & $\delta_k$ [$''$] \\\hline
 1 & 0.184 & 0.038\\
@@
 \caption{J1331's F814W MGE: Parameters of the best fit MGE to the F814W surface brightness of J1331 in Figure \ref{fig:F814W}.
-The fit is best inside an radius of 5 arcsec.
+The fit is best inside an radius of $5''$.
 The galaxy center and position angle, which gives the orientation of the MGE with respect to the original image, are given in Table \ref{tab:galaxyparameters}.
@@
  & total luminosity  & surface density & \multicolumn{2}{c}{Gaussian dispersion} & axis ratio\\
-$k$  & $L_k$ [counts] & $I_{0,k}$ [$L_\odot$/pc$^2$] & $\sigma_k$ [arcsec] & $\sigma_k$ [kpc] & $q'_k$\\\hline
+$k$  & $L_k$ [counts] & $I_{0,k}$ [$L_\odot$/pc$^2$] & $\sigma_k$ [$''$] & $\sigma_k$ [kpc] & $q'_k$\\\hline
 1  &     9425.96 &      20768.  &  0.051   & 0.103  & 1.00\\
@@
 angular diameter distance & $D_d$ [Mpc] & 414 & \\
-scaling                   & 1 kpc / 1 arcsec & 2.006 & \\
-position angle            & $\phi$ [degrees] & [TO DO: wrt what???]\\
+scaling                   & 1 kpc / 1 $''$ & 2.006 & \\
+position angle            & $\phi$ [degrees] & \Wilma{[TO DO: wrt what???]}\\
 average axis ratio & $q'$ & 0.598\\
@@
 total I-band luminosity & $L_\text{tot,I}$ [$10^{10} L_\odot$] & 5.6 & \\
-effective half-light radius & $R_\text{eff}$ [arcsec] & 2.6 & \\
+effective half-light radius & $R_\text{eff}$ [$''$] & 2.6 & \\
 & $R_\text{eff}$ [pc]& 5.2 & \\
@@
 
-\paragraph{PSF for the HST/F814W filter.} We find a radial profile for the HST/F814W filter PSF from circular annuli within a synthetic PSF image from [TO DO: Where did we get this image from???], ignoring diffraction spikes.
+\paragraph{PSF for the HST/F814W filter.} We find a radial profile for the HST/F814W filter PSF from circular annuli within a synthetic PSF image from \Wilma{[TO DO: Where did we get this image from???]}, ignoring diffraction spikes.
 The one-dimensional MGE fit of Equation \ref{eq:PSFgeneral} to this radial profile is performed using the code by \citet{Cap02}.
@@
 
-\paragraph{MGE for the inner regions.} We fit a MGE to the smooth central region within radius $\sim 5$ arcsec of the HST/WFPC2/WF3/F814W image of J1331 in Figure \ref{fig:F814W}.
+\paragraph{MGE for the inner regions.} We fit a MGE to the smooth central region within radius $\sim 5''$ of the HST/WFPC2/WF3/F814W image of J1331 in Figure \ref{fig:F814W}.
 Bright objects  close to the galaxy, blobs possibly belonging to the background galaxy and parts of the foreground spiral arm were masked during the fit.
@@
 The best fit MGE (PSF convolved) is compared to the data in Figure \ref{fig:MGEinnerRegions} and the corresponding parameters of the intrinsic surface brightness distribution are given in Table \ref{tab:MGEF814W}.
-The fit is a very good representation of the light distribution in the inner 5 arcsec, but underestimates the light distribution outside of this.
+The fit is a very good representation of the light distribution in the inner $5''$, but underestimates the light distribution outside of this.
 
-\paragraph{MGE for the outer regions.} To get an handle on the light distribution also in the outer parts of J1331, where spiral arms dominate, we first fit a IRAF ELLIPSE [TO DO: How to reference???] model to the F814W image (masking the brightest blobs in the spiral arms and outer regions).
+\paragraph{MGE for the outer regions.} To get an handle on the light distribution also in the outer parts of J1331, where spiral arms dominate, we first fit a IRAF ELLIPSE \Wilma{[TO DO: How to reference???]} model to the F814W image (masking the brightest blobs in the spiral arms and outer regions).
 Only then we fit a 7-Gaussian MGE to the smooth ellipse model.
@@
 
-\paragraph{Transformation into physical units.} To transform the MGE in units of counts into physical units, we apply a simplified version of the procedure described in \citet{Holtzman}, analogous to [TO DO: Cappellari Read me file???
-How to reference this???]
-\\The scaling of the drizzled HST/WFC3 images is  $S = 0.05$ arcsec/pixel and the total exposure time $T = 1600$ sec.
+\paragraph{Transformation into physical units.} To transform the MGE in units of counts into physical units, we apply a simplified version of the procedure described in \citet{Holtzman}, analogous to \Wilma{[TO DO: Cappellari Read me file???
+How to reference this???]}
+\\The scaling of the drizzled HST/WFC3 images is  $S = 0.05''/$pixel and the total exposure time $T = 1600$ sec.
 The total F814W luminosity in counts of each Gaussian of the MGE has a central surface brightness in counts per pixel of
@@
 \begin{equation}
-\mu_I \simeq -2.5 \log_{10}\left( \frac{C_0\text{[counts/pixel]}}{T[\text{sec}] \cdot S[\text{arcsec/pixel}]^2}\right) + Z + C + A_I, \label{eq:muI_}
+\mu_I \simeq -2.5 \log_{10}\left( \frac{C_0\text{[counts/pixel]}}{T[\text{sec}] \cdot S[''/\text{pixel}]^2}\right) + Z + C + A_I, \label{eq:muI_}
 \end{equation}
@@
 The luminosity $L_k$[counts] and the corresponding surface brightness density $I \equiv I_{0,k}[L_\odot \text{pc}^{-2}]$ of each Gaussian are given in Table \ref{fig:MGEinnerRegions}.
-[TO DO: I'm really confused about this.
+\Wilma{[TO DO: I'm really confused about this.
 Check, that everything is correct and the naming of quantities, e.g.
-with or without subscripts of 0, is fine???]
+with or without subscripts of 0, is fine???]}
 
-\paragraph{Inclination.} To estimate the inclination of J1331 with respect to the observer, we use the observed axis ratio of the flattest ellipse in the Iraf Ellipse [TO DO] model for J1331, which is $q'=0.42$.
+\paragraph{Inclination.} To estimate the inclination of J1331 with respect to the observer, we use the observed axis ratio of the flattest ellipse in the Iraf Ellipse \Wilma{[TO DO]} model for J1331, which is $q'=0.42$.
 This is similar to the disk axis ratio of $q' = 0.40$ found by \citet{SWELLSI}.
@@
 This corresponds to an apparent magnitude of $m_I = 15.77$ mag.
-We determine the circularized effective radius $R_\text{eff}$ of J1331 from the definition $L(<R_\text{eff}) \equiv \frac 12 L_\text{tot}$ and the growth curve $L(<R')$ from the MGE model of the outer regions [TO DO: Maybe I need a table anyway???], where $R'$ is the projected radius on the sky.
-We find the effective radius to be $R_\text{eff} \simeq 2.6 \text{ arcsec } \hat{=} 5.2 \text{ kpc}$.
+We determine the circularized effective radius $R_\text{eff}$ of J1331 from the definition $L(<R_\text{eff}) \equiv \frac 12 L_\text{tot}$ and the growth curve $L(<R')$ from the MGE model of the outer regions \Wilma{[TO DO: Maybe I need a table anyway???]}, where $R'$ is the projected radius on the sky.
+We find the effective radius to be $R_\text{eff} \simeq 2.6'' \hat{=} 5.2 \text{ kpc}$.
 All values are summarized in Table \ref{tab:galaxyparameters}.
 
-[TO DO: Reff and Rein are also projected radii. Maybe prime them as well?]
+\Wilma{[TO DO: Reff and Rein are also projected radii. Maybe prime them as well?]}

### 2015-11-13 docs/summary_v3.01.tex
Included corrections in abstract and introduction.

\subsection{Summary}

\Wilma{[TO DO: Ask Glenn and Aaron how much of the above should find its way into the summary.]}

### 2015-11-13 docs/abstract_v3.01.tex
Corrections in Section 2 and 3

@@
-We analyse the stellar and dark matter distribution in the spiral galaxy SDSS J1331+3638 (J1331) by means of two independent methods: gravitational lensing and dynamical modelling.
+We analyse the stellar and dark matter distribution in the spiral galaxy SDSS J1331+3628 (J1331) by means of two independent methods: gravitational lensing and dynamical modelling.
 Hubble Space Telescope (HST) imaging by the SWELLS survey shows, that J1331's bulge is superimposed by a quadruplet of extended lensing images.

### 2015-11-13 docs/data_v3.01.tex
Corrections in Section 2 and 3

@@
 
-For our lensing and dynamics analysis of J1331 we use on the one hand Hubble Space Telescope (HST) imaging by \cite{SWELLSI} in two filters (F450W and F814W), and on the other hand line-of-sight stellar kinematics along J1331's major axis by \citet{SWELLSV}.
+For our lensing and dynamics analysis of J1331 we use both Hubble Space Telescope (HST) imaging by \cite{SWELLSI} in two filters (F450W and F814W), as well as line-of-sight stellar kinematics along J1331's major axis by \citet{SWELLSV}.
 
-\paragraph{Redshift.} \Wilma{[TO DO: WHO???]} found from SDSS spectra that J1331 has two redshifts inside $1''$: The smaller one, $z_d = 0.113$, is the redshift of J1331 itself, the larger one, $z_s = 0.254$, is the redshift of the lensed background source \citep{SWELLSIII}.
-According to its redshift and the WMAP5 \Wilma{[TO DO: Do I have to explain the Acronym???]} cosmology \citep{WMAP5cosm}, J1331 has an angular diameter distance of 414 Mpc, which translates into a transverse scaling of $1'' \hat{=} 2.01~\text{kpc}$.
+\paragraph{Redshift.} \citet{SWELLSI} found from SDSS spectra that J1331 has two redshifts inside $1''$: The smaller one, $z_d = 0.113$, is the redshift of J1331 itself, the larger one, $z_s = 0.254$, is the redshift of the lensed background source \citep{SWELLSIII}.
+According to its redshift and the WMAP5 cosmology \citep{WMAP5cosm}, J1331 has an angular diameter distance of 414 Mpc, which translates into a transverse scaling of $1'' \hat{=} 2.01~\text{kpc}$.
 
-\paragraph{HST imaging.} We use the follow-up HST imaging, with which \citet{SWELLSI} confirmed that J1331 is indeed a strong gravitational lens \Wilma{[TO DO: Was it actually SWELLS I that confirmed that???]}.
+\paragraph{HST imaging.} We use the follow-up HST imaging, with which \citet{SWELLSI} confirmed that J1331 is indeed a strong gravitational lens.
 They performed high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) and its WF3 CCD chip.
@@
 Spectra for spatial bins of different widths along the major axis were extracted.
-Analogously to \citet{SWELLSII} they measured line-of-sight rotation velocities ($v_\text{rot}$) and stellar velocity dispersion ($\sigma$) by fitting Gaussian line profiles to emission lines in these spectra.
-Gas kinematics were extracted from fits to H$\alpha$ and NII lines, as tracers for inonized gas.
+They measured line-of-sight stellar rotation velocities ($v_\text{rot}$) and stellar velocity dispersion ($\sigma$) by fitting Gaussian line profiles to emission \Wilma{[TO DO: Check if really emission lines or, more likely, absorption lines]} lines in these spectra \Wilma{[TO DO: Find out which lines]}.
+Gas kinematics were extracted from fits to H$\alpha$ and NII lines, as tracers for ionized gas.
 \\The stellar kinematics, $v_\text{rot}$, $\sigma$ and $v_\text{rms}^2=v_\text{rot}^2 + \sigma^2$ are shown in Figure \ref{fig:kinematics}.
 The rotation curve reveals a counter-rotating core within $2''\simeq$ 4 kpc.
-Outside of $\sim 3.5''$ there is a steep drop in the dispersion, which is exptected at the boundary between the pressure supported bulge and the rotationally supported disk, which appears around this radius in the F450W filter in Figure \ref{fig:F450W}.
+Outside of $\sim 3.5''$ there is a steep drop in the dispersion, which is expected at the boundary between the pressure supported bulge and the rotationally supported disk, which appears around this radius in the F450W filter in Figure \ref{fig:F450W}.
 However, in the brighter F814W filter in Figure \ref{fig:F814W}  the large reddish bulge extends out to $\sim5''$.
 \\Inside of $\sim 4''$, the data appears to be symmetric, outside of this the assumption of axisymmetry seems not to be valid anymore, considering the data.
-We add -2.3 km/s to the $v_\text{rot}$ to ensure $v_\text{rot}(R'=0) \sim 0$ as a possible correction term for a systematic misjudgement of the systemic velocity.
+We add -2.3 km/s to the $v_\text{rot}$ to ensure $v_\text{rot}(R'=0) \sim 0$ as a possible correction term for a misjudgement of the systemic velocity.
 We also symmetrize the data within $4''$ and asign a minimum error of $\delta v_\text{rms} > 5$ km/s to the $v_\text{rms}$ data.
-In the JAM modelling, which is based on the assumption of axisymmetry, only kinematics within $\sim 2.5$ and $4''$ are used.
+In the JAM modelling, which is based on the assumption of axisymmetry, only stellar kinematics with $R'  \lesssim 2.5''$ or $R' \lesssim 4''$ are used.
 Another reason to restrict to modelling on the bulge region is that our MGE in Table \ref{tab:MGEF814W} is only a good representation of J1331's F814W light distribution inside $\sim 5''$.\\
-
-\Wilma{[TO DO: How to deal with the typo in J1331s name???? SWELLS call it J1331+3638, but its actual coordinates are 1331+3628.]}

### 2015-11-13 docs/introduction_v3.01.tex
Corrections in Section 2 and 3

@@
 Check difference WMAP/Planck...]}, infers that $\sim 85\%$ of the universe's total matter content is in the form of non-baryonic cold dark matter.
-Simulations suggest that this kind of dark matter forms cuspy halos following a Navarro-Frenck-White (NFW) profile \citep{NFW96}.
-However, central dark matter density cusps are not observed in dark matter dominated dwarf galaxies \Wilma{[TO DO: REF: Aaron suggests Moore 1994, de Blok et al.
-2001]}.
-Their existence in more massive galaxies depends strongly on stellar mass-to-light ratio \Wilma{[TO DO: REF: Aaron suggests Dutton et al.
-2011 "dark halo response and the IMF"]}.
+Simulations suggest that this kind of dark matter forms cuspy halos following a Navarro-Frenk-White (NFW) profile \citep{NFW96}.
+However, central dark matter density cusps are not observed in dark matter dominated dwarf galaxies (e.g., \citealt{1994Natur.370..629M,2001ApJ...552L..23D}).
+Their existence in more massive galaxies depends strongly on stellar mass-to-light ratio (e.g., \citealt{2011MNRAS.416..322D}).
 Overall, observations suggest cored dark matter halos.
-This discrepancy, known as the core-cusp problem, might be resolved by galaxy formation processes such as mergers and outflows (e.g., \citealt{2001ApJ...560..636E} \Wilma{[TO DO: more REF: Aaron suggests Pontzen \& Governato 2012]}).
+This discrepancy, known as the core-cusp problem, might be resolved by galaxy formation processes such as mergers and outflows (e.g., \citealt{2001ApJ...560..636E,2012MNRAS.421.3464P}).
 
@@
 %Lensing
-Strong gravitational lensing is an independent method to tightly constrain the projected total mass of galaxies inside $\sim 1''$ \Wilma{[TO DO: REF: Aaron suggests Treu 2010]}.
-Massive galaxies can act as gravitational lenses and deflect the light of background sources, giving rise to multiple distorted images of the source \Wilma{[TO DO: REF]}.
-By 2010 over 200 strong gravitational galaxy lenses had been discovered \citep{2010ARA&A..48...87T} and the number is still rising.
+Strong gravitational lensing is an independent method to tightly constrain the projected total mass of galaxies inside $\sim 1''$.
+Massive galaxies can act as gravitational lenses and deflect the light of background sources, giving rise to multiple distorted images of the source.
+By 2010 over 200 strong gravitational galaxy lenses had been discovered and the number is still rising (e.g., \citealt{2010ARA&A..48...87T}).
 
@@
 %Characteristics of J1331
-One of the SWELLS galaxies is SDSS J1331+3638, to which we refer as J1331 in the remainder of this work.
+One of the SWELLS galaxies is SDSS J1331+3628, to which we refer as J1331 in the remainder of this work.
 It is a spiral galaxy of approximate Hubble type Sb at right ascension = 202.91800$^\circ$ and a declination = 36.46999$^\circ$ (epoch J2000).
@@
 \end{subfigure}
-\caption{Hubble Space telescope (HST) images and stellar kinematics of the galaxy SDSS J1331+3638 (J1331), which has a large counter-rotating core and whose bulge acts as a strong lens for a bluish background source.
+\caption{Hubble Space telescope (HST) images and stellar kinematics of the galaxy SDSS J1331+3628 (J1331), which has a large counter-rotating core and whose bulge acts as a strong lens for a bluish background source.
 \emph{Panel (a) and (b):} HST/WFPC2/WFC3 images of J1331 by \citet{SWELLSI} in two filters, F450W in panel (a) and F814W in panel (b).
@@
 \emph{Panel (c):} The central region of J1331 in F450W, surface brightness subtracted.
-An IRAF ellipse \Wilma{[TO DO: How to write and reference????]} fit to the F450W surface brightness in panel (a) was subtracted from the image.
+An IRAF \emph{ellipse} fit to the F450W surface brightness in panel (a) was subtracted from the image.
 The (smoothed) residuals within the white square in panel (a) are shown in panel (c).

### 2015-11-13 docs/model_JAM_v3.01.tex
Corrections in Section 2 and 3

@@
-\subsection{Jeans Axisymmetric Modelling (JAM)} \label{sec:model_JAM}
+\subsection{Axisymmetric dynamical model} \label{sec:model_JAM}
 
-\paragraph{JAM modelling.} Jeans axisymmetric models (JAM) assume galaxies (a) to be collisionless, i.e.
+\paragraph{Jeans Anisotropic Models (JAM).} JAM modelling assumes galaxies (a) to be collisionless, i.e.
 the collisionless Boltzmann equation for the distribution function $f(\vect{x},\vect{v},t)$ has to be satisfied ($\frac{\diff f(\vect{x},\vect{v},t}{\diff t} = 0$), (b) in a steady state ($\frac{\partial}{\partial t} = 0$), (c) axisymmetric (best described in cylindrical coordinates $(R,z,\phi)$ and $\frac{\partial}{\partial \phi} = 0$).
@@
 To be able to solve the Jeans equations, additional assumptions about the velocity ellipsoid tensor $\langle v_i v_j\rangle$ have to be made.
-We follow \citet{Cap08} and assume firstly, that the galaxy's velocity ellipsoid is aligned with the cylindrical coordinate system, i.e.
-$\langle v_i v_j\rangle = 0$ for $i\neq j$.
+We follow \citet{Cap08} and assume firstly, that the galaxy's velocity ellipsoid is aligned with the cylindrical coordinate system, i.e., $\langle v_R v_z\rangle = \langle v_z v_\phi \rangle = \langle v_\phi v_R \rangle = 0$.
 Secondly, we assume a constant ratio between the radial and vertical 2nd velocity moments,
@@
 Taking a light-weighted projection along the line-of-sight gives a model prediction for the line-of-sight velocity second moment, which is comparable to actual spectroscopic measurements of the second velocity moment.
-Details of the derivation using the MGE formalism are given in \citet{Cap08} and repeated in \citet{GlennEC}, we therefore just quote the result by \citet{Cap08} (their Equation 28) for the line-of-sight second velocity moment prediction from the Jeans equations,
+Details of the derivation using the MGE formalism are given in \citet{Cap08} and in the appendix of \citet{GlennEC}.
+We therefore just give the result for the line-of-sight second velocity moment prediction from the Jeans equations,
 \begin{eqnarray}
@@
 The model in Equation \ref{eq:explicitLOSvelCap} predicts the intrinsic $\langle v_\text{los}^2 \rangle$ at a given position on the sky, which have then to be modified according to the mode of observation, to be comparable to the measurements.
-The measured $v_\text{rms}$ is a light-weighted mean for a pixel along the long-slit of the spectrograph, with height $L_y = 1''$ \citep{SWELLSV} and a certain given extent in along the galaxy's major axis, $L_x$, i.e.
+The measured $v_\text{rms}$ is a light-weighted mean for a pixel along the long-slit of the spectrograph, with width $L_y = 1''$ \citep{SWELLSV} and a certain given extent along the galaxy's major axis, $L_x$, i.e.
 for a rectangular aperture
@@
 \end{eqnarray*}
-If provided with the convolution kernel, the JAM code\footnote{The IDL code package for Jeans Axisymmetric Modelling (JAM) by \citet{Cap08} is available online at \url{http://www-astro.physics.ox.ac.uk/~mxc/software}.
+If provided with the convolution kernel, the JAM code\footnote{The IDL code package for Jeans Anisotropic Models (JAM) by \citet{Cap08} is available online at \url{http://www-astro.physics.ox.ac.uk/~mxc/software}.
 The version from June 2012 was used in this work.} by \citet{Cap08} performs the convolution numerically.
@@
 is then the light-weighted circular velocity curve, given the second velocity moments found from the Jeans equations.
-\\To model the counter-rotating core of J1331 with one free parameter for, we employ the condition that the overall $\kappa(R)$ profile should smoothly and relatively steeply transition from $\kappa(R) = -\kappa' < 0$ at small $R$ through $\kappa(R_0) \equiv 0$ and increase to $\kappa(R) = \kappa' > 0$ at large $R$.
+\\To model the counter-rotating core of J1331 with one free parameter, we employ the condition that the overall $\kappa(R)$ profile should smoothly and relatively steeply transition from $\kappa(R) = -\kappa' < 0$ at small $R$ through $\kappa(R_0) \equiv 0$ and increase to $\kappa(R) = \kappa' > 0$ at large $R$.
 Our imposed profile is
@@
 
+%============================================================================
+\begin{table*}
+\centering
+\caption{Galaxy Parameters of J1331}
+\begin{tabular}{lllrl}
+\hline
+redshift                  & $z_d$ & 0.113 & \citep{SWELLSIII}\\
+angular diameter distance & $D_d$ [Mpc] & 414 & \\
+scaling                   & 1 kpc / 1 $''$ & 2.006 & \\
+position angle            & $\phi$ [degrees] & \Wilma{[TO DO: wrt N through E]}\\
+average axis ratio & $q'$ & 0.598\\
+average ellipticity & $\epsilon = 1 - q'$ & 0.402 & \\
+apparent I-band magnitude & $m_\text{I}$ [mag] & 15.77 & \\
+total I-band luminosity & $L_\text{tot,I}$ [$10^{10} L_\odot$] & 5.6 & \\
+effective half-light radius & $R_\text{eff}$ [$''$] & 2.6 & \\
+& $R_\text{eff}$ [pc]& 5.2 & \\
+\hline
+\end{tabular}
+\label{tab:galaxyparameters}
+\end{table*}
+%============================================================================
+
 \paragraph{Including a NFW halo.} As mentioned above, JAM modelling allows to incorporate an invisible matter component in addition to the luminous matter in the form of an MGE.
-In Section \ref{sec:results_JAM_NFW} we will include a spherical Navarro-Frenck-White (NFW) dark matter halo \citep{Navarro+1995c,NFW96} in the dynamical model.
+In Section \ref{sec:results_JAM_NFW} we will include a spherical Navarro-Frenk-White (NFW) dark matter halo \citep{NFW96} in the dynamical model.
 The classical NFW profile has the form
 \begin{equation}
-\rho_\text{NFW}(r) \propto \frac{1}{\frac{r}{r_s} \left( 1 + \frac{r}{r_s} \right)^2} \label{eq:NFWprofile}
+\rho_\text{NFW}(r) \propto r^{-1} \left( r+r_s \right)^{-2} \label{eq:NFWprofile}
 \end{equation}
@@
 \end{equation} 
-There is a close relation between the concentration and halo mass in simulations \citep{NFW96}. \citet{Maccio08} found this relation for the WMAP5 cosmology \citep{WMAP5cosm} to be
+There is a close relation between the concentration and halo mass in simulations \citep{NFW96}. \citet{Maccio08} found this relation for the WMAP5 cosmology to be
 \begin{equation}

### 2015-11-13 docs/results_lensing_v3.01.tex
Corrections in Section 2 and 3

@@
 \paragraph{Image positions.} We determine the positions of the lensing images by first subtracting a smooth model for the galaxy's surface brightness from the original image.
-As models we use MGE fits and IRAF ellipse fits  (see Sections \ref{sec:MGE_theo} and \ref{sec:MGE_results})  to the galaxy in each the F450W and F814W filter.
+As models we use MGE fits and IRAF \emph{ellipse} fits  (see Sections \ref{sec:MGE_theo} and \ref{sec:MGE_results})  to the galaxy in each the F450W and F814W filter.
 (For example the MGE we use for F814W is the MGE given in Table \ref{tab:MGEF814W} convolved with the PSF in Table \ref{tab:PSFMGEF814W}.) The lensing images become then visible in the residuals (see Figure \ref{fig:lens_just_imgpos}), in which we smooth out noise smaller than the PSF.
@@
 This is a good indication that indeed all four images are indeed lensing images of the same object.
-Figure \ref{fig:lensbestfittimedelay} overplots the smoothed residuals from the F450W image subtracted by the IRAF ellipse fit to the surface brightness with the contours of the best fit model's time delay surface.
+Figure \ref{fig:lensbestfittimedelay} overplots the smoothed residuals from the F450W image subtracted by the IRAF \emph{ellipse} fit to the surface brightness with the contours of the best fit model's time delay surface.
 This demonstrates that, although we did not include any information about the shape of the lensing images in the fit, it is consistent with the predicted distortion for an extended source by the best fit lens model.
@@
 \caption{Best fit lens model in Table \ref{tab:bestfitlensmodel} found from the image positions.
-In the background we show the central region of J1331 in the F450W filter, subtracted by an Iraf Ellipse model of the F450W surface brightness and smoothed by boxcar smoothing of the order of the PSF size.
+In the background we show the central region of J1331 in the F450W filter, subtracted by an IRAF \emph{ellipse} model of the F450W surface brightness and smoothed by boxcar smoothing of the order of the PSF size.
 The four bluish lensing images are clearly visible and we mark the brightness peaks in Table \ref{tab:lenspos} as well as the galaxy center (G) as red dots.

### 2015-11-13 docs/results_photometry_v3.01.tex
Corrections in Section 2 and 3

@@
 
+In this section we construct a model for the galaxy's intrinsic light distribution in terms of an MGE, which we will then compare in Section \ref{sec:results_lensing} to the mass distribution.
+The light model will also be the basis of the dynamical Jeans modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}.
+\\To derive J1331's surface brightness distribution, we use the HST image in the F814W (I-band) filter, shown in Figure \ref{fig:F814W}.
+At longer wavelengths J1331's central old and smooth stellar component is more extended than in the F450W filter in Figure \ref{fig:F450W}, which is more sensitive to young clumpy star-forming regions.
+In the I-band the bulge is also much brighter than the bluish lens images and the imaging is less prone to extinction.
+The F814W image is therefore best suited for fitting a MGE.
+
+\paragraph{PSF for the HST/F814W filter.} We find a radial profile for the HST/F814W filter PSF from circular annuli within a synthetic PSF image, ignoring diffraction spikes.
+The one-dimensional MGE fit of Equation \ref{eq:PSFgeneral} to this radial profile is performed using the code by \citet{Cap02}.
+The MGE parameters of the normalized PSF model are given in Table \ref{tab:PSFMGEF814W}.
+
 %============================================================================
-
 \begin{figure}
@@
 \end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=0.8\columnwidth]{fig/1331F814W_MGE_disk_L.ps}
-\caption{MGE for J1331's outer regions: Comparison of contours with constant surface brightness of the smooth IRAF ELLIPSE \Wilma{[TO DO: How to write Iraf Ellipse???]} model for J1331 in the F814W filter (yellow) with a corresponding best fit MGE (gray lines).
-The green box corresponds to the image section shown in Figure \ref{fig:MGEinnerRegions}, with the Einstein radius as dashed red line and the black $10''$ orientation line along the major axis (see Figure \ref{fig:MGEinnerRegions}).
-This MGE found from the smooth, symmetric Iraf Ellipse \Wilma{[TO DO]} model is not used to find a dynamical model for J1331, because the dynamics in the outer regions are strongly affected by non-axisymmetries (e.g.
-spiral arms).
-We use it, however, to estimate the galaxy's total luminosity and effective radius, and to get a prediction for the dynamics of the outer regions by extrapolation the best fit model of the inner regions.}
-\label{fig:MGEouterRegions}
-\end{figure}
+%============================================================================
 
 %============================================================================
-
 \begin{table}
@@
 \end{table}
+%============================================================================
 
+\paragraph{MGE for the inner regions.} We fit a MGE to the smooth central region within radius $\sim 5''$ of the HST/WFPC2/WF3/F814W image of J1331 in Figure \ref{fig:F814W}.
+Bright objects  close to the galaxy, blobs possibly belonging to the background galaxy and parts of the foreground spiral arm were masked during the fit.
+J1331's galaxy center, position angle and average apparent ellipticity (see Table \ref{tab:galaxyparameters}) are found from the images weighted first and second moment.
+The MGE fit splits the image in annuli with the given ellipticity and position angle and sectors of $5^\circ$ width and fits an 5-Gaussian MGE of the form in Equation \ref{eq:MGEgeneral} convolved with the PSF MGE in Table \ref{tab:PSFMGEF814W} to it.
+The best fit MGE (PSF convolved) is compared to the data in Figure \ref{fig:MGEinnerRegions} and the corresponding parameters of the intrinsic surface brightness distribution are given in Table \ref{tab:MGEF814W}.
+The fit is a very good representation of the light distribution in the inner $5''$, but underestimates the light distribution outward.
+
+%============================================================================
+\begin{figure}
+\centering
+\includegraphics[width=0.8\columnwidth]{fig/1331F814W_MGE_disk_L.ps}
+\caption{MGE for J1331's outer regions: Comparison of contours with constant surface brightness of the smooth IRAF \emph{ellipse} model for J1331 in the F814W filter (yellow) with a corresponding best fit MGE (gray lines).
+The green box corresponds to the image section shown in Figure \ref{fig:MGEinnerRegions}, with the Einstein radius as dashed red line and the black $10''$ orientation line along the major axis (see Figure \ref{fig:MGEinnerRegions}).
+This MGE found from the smooth, symmetric IRAF \emph{ellipse} model is not used to find a dynamical model for J1331, because the dynamics in the outer regions are strongly affected by non-axisymmetries (e.g.
+spiral arms).
+We use it, however, to estimate the galaxy's total luminosity and effective radius, and to get a prediction for the dynamics of the outer regions by extrapolation the best fit model of the inner regions.
+\Wilma{[TO DO: Maybe merge Figures 2 + 3, panels next to each other?]}}
+\label{fig:MGEouterRegions}
+\end{figure}
+%============================================================================
+
+\paragraph{MGE for the outer regions.} To get an handle on the light distribution also in the outer parts of J1331, where spiral arms dominate, we first fit a IRAF \citep{1993ASPC...52..173T} \emph{ellipse} model to the F814W image (masking the brightest blobs in the spiral arms and outer regions).
+Only then we fit a 7-Gaussian MGE to the smooth ellipse model.
+The MGE does not perfectly reproduce the flattness of the ellipse model at every radius (see Figure \ref{fig:MGEouterRegions}), but considering the spiral arm dominated outer regions of J1331, it is good enough for an approximate handling of the overall light distribution.
+
+%============================================================================
 \begin{table*}
@@
 \end{table*}
-
 %============================================================================
 
-\begin{table*}
-\centering
-\caption{Galaxy Parameters of J1331}
-\begin{tabular}{lllrl}
-\hline
-redshift                  & $z_d$ & 0.113 & \citep{SWELLSIII}\\
-angular diameter distance & $D_d$ [Mpc] & 414 & \\
-scaling                   & 1 kpc / 1 $''$ & 2.006 & \\
-position angle            & $\phi$ [degrees] & \Wilma{[TO DO: wrt what???]}\\
-average axis ratio & $q'$ & 0.598\\
-average ellipticity & $\epsilon = 1 - q'$ & 0.402 & \\
-apparent I-band magnitude & $m_\text{I}$ [mag] & 15.77 & \\
-total I-band luminosity & $L_\text{tot,I}$ [$10^{10} L_\odot$] & 5.6 & \\
-effective half-light radius & $R_\text{eff}$ [$''$] & 2.6 & \\
-& $R_\text{eff}$ [pc]& 5.2 & \\
-\hline
-\end{tabular}
-\label{tab:galaxyparameters}
-\end{table*}
-
-%============================================================================
-
-In Section \ref{sec:results_lensing} we will derive a mass model for J1331 from Lensing.
-In this section set up a model for the galaxy's intrinsic light distribution in terms of an MGE, which we will then compare in Section \ref{sec:results_lensing} to the mass distribution.
-The light model will also be the basis of the dynamical Jeans modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}.
-\\To derive J1331's surface brightness distribution, we use the HST image in the infrared F814W filter, shown in Figure \ref{fig:F814W}.
-In infrared J1331's central old and smooth stellar component is more extended than in the F450W filter in Figure \ref{fig:F450W}, which is more sensitive to young clumpy star-forming regions.
-In infrared the bulge is also much brighter than the bluish lens images and the imaging is less prone to extinction.
-The F814W image is therefore best suited for fitting a MGE.
-
-\paragraph{PSF for the HST/F814W filter.} We find a radial profile for the HST/F814W filter PSF from circular annuli within a synthetic PSF image from \Wilma{[TO DO: Where did we get this image from???]}, ignoring diffraction spikes.
-The one-dimensional MGE fit of Equation \ref{eq:PSFgeneral} to this radial profile is performed using the code by \citet{Cap02}.
-The MGE parameters of the normalized PSF model are given in Table \ref{tab:PSFMGEF814W}.
-
-\paragraph{MGE for the inner regions.} We fit a MGE to the smooth central region within radius $\sim 5''$ of the HST/WFPC2/WF3/F814W image of J1331 in Figure \ref{fig:F814W}.
-Bright objects  close to the galaxy, blobs possibly belonging to the background galaxy and parts of the foreground spiral arm were masked during the fit.
-J1331's galaxy center, position angle and average apparent ellipticity (see Table \ref{tab:galaxyparameters}) are found from the images weighted first and second moment.
-The MGE fit, as performed by the code \cite{Cap02}, splits the image in annuli with the given ellipticity and position angle and sectors of $5^\circ$ width and fits an 5-Gaussian MGE of the form in Equation \ref{eq:MGEgeneral} convolved with the PSF MGE in Table \ref{tab:PSFMGEF814W} to it.
-The best fit MGE (PSF convolved) is compared to the data in Figure \ref{fig:MGEinnerRegions} and the corresponding parameters of the intrinsic surface brightness distribution are given in Table \ref{tab:MGEF814W}.
-The fit is a very good representation of the light distribution in the inner $5''$, but underestimates the light distribution outside of this.
-
-\paragraph{MGE for the outer regions.} To get an handle on the light distribution also in the outer parts of J1331, where spiral arms dominate, we first fit a IRAF ELLIPSE \Wilma{[TO DO: How to reference???]} model to the F814W image (masking the brightest blobs in the spiral arms and outer regions).
-Only then we fit a 7-Gaussian MGE to the smooth ellipse model.
-The MGE does not perfectly reproduce the flattness of the ellipse model at every radius, but considering the spiral arm dominated outer regions of J1331, it is good enough for an approximate handling of the overall light distribution.
-
-\paragraph{Transformation into physical units.} To transform the MGE in units of counts into physical units, we apply a simplified version of the procedure described in \citet{Holtzman}, analogous to \Wilma{[TO DO: Cappellari Read me file???
-How to reference this???]}
+\paragraph{Transformation into physical units.} To transform the MGE in units of counts into physical units, we apply a simplified version of the procedure described in \citet{Holtzman}.
 \\The scaling of the drizzled HST/WFC3 images is  $S = 0.05''/$pixel and the total exposure time $T = 1600$ sec.
@@
 \begin{equation}
-\mu_I \simeq -2.5 \log_{10}\left( \frac{C_0\text{[counts/pixel]}}{T[\text{sec}] \cdot S[''/\text{pixel}]^2}\right) + Z + C + A_I, \label{eq:muI_}
+\mu_{I,0} \simeq -2.5 \log_{10}\left( \frac{C_0\text{[counts/pixel]}}{T[\text{sec}] \cdot S[''/\text{pixel}]^2}\right) + Z + C + A_I, \label{eq:muI_}
 \end{equation}
-where $Z\simeq21.62$ is a the zero-point from \citet{Holtzman}  (updated according to \citet{Dolphin,DolphinNew}) for the photometric system of the HST/WFPC2 camera and the F814W filter plus a correction for the difference in gain between calibration and observation.
+\Wilma{[TO DO: Make sure to use $\mu_{I,0}$ where applicable.]} where $Z\simeq21.62$ is a the zero-point from \citet{Holtzman}  (updated according to \citet{Dolphin,DolphinNew}) for the photometric system of the HST/WFPC2 camera and the F814W filter plus a correction for the difference in gain between calibration and observation.
 $C= 0.1$ corrects for the finite aperture of the WFPC2.
@@
 \begin{eqnarray*}
-I_0[L_\odot \text{pc}^{-2}] = \left( 64800/\pi\right)^2 \left(1+z \right)^4 10^{0.4\left(M_{\odot,I}-\mu_I \right)},
+I_0[L_\odot \text{pc}^{-2}] = \left( 64800/\pi\right)^2 \left(1+z \right)^4 10^{0.4\left(M_{\odot,I}-\mu_{I,0} \right)},
 \end{eqnarray*}
@@
 
-\paragraph{Inclination.} To estimate the inclination of J1331 with respect to the observer, we use the observed axis ratio of the flattest ellipse in the Iraf Ellipse \Wilma{[TO DO]} model for J1331, which is $q'=0.42$.
+\paragraph{Inclination.} To estimate the inclination of J1331 with respect to the observer, we use the observed axis ratio of the flattest ellipse in the IRAF \emph{ellipse} model for J1331, which is $q'=0.42$.
 This is similar to the disk axis ratio of $q' = 0.40$ found by \citet{SWELLSI}.
-If a typical thickness of an oblate disk was around $q_0 \sim 0.2$ \citep{1958MeLu2.136....1H}, the inclination would follow from $\cos^2 i = \frac{q'^2 - q_0^2}{1 - q_0^2}$ and a correction of $+3^\circ$ \citep{1988ngc..book.....T}.
+If a typical thickness of an oblate disk was around $q_0 \sim 0.2$ \citep{1958MeLu2.136....1H}, the inclination would follow from
+\begin{equation*}
+\cos^2 i = \frac{q'^2 - q_0^2}{1 - q_0^2}
+\end{equation*}
+and a correction of $+3^\circ$ \citep{1988ngc..book.....T}.
 Our estimate for the inclination is therefore $i \approx 70^\circ$.
@@
 This corresponds to an apparent magnitude of $m_I = 15.77$ mag.
-We determine the circularized effective radius $R_\text{eff}$ of J1331 from the definition $L(<R_\text{eff}) \equiv \frac 12 L_\text{tot}$ and the growth curve $L(<R')$ from the MGE model of the outer regions \Wilma{[TO DO: Maybe I need a table anyway???]}, where $R'$ is the projected radius on the sky.
+We determine the circularized effective radius $R_\text{eff}$ of J1331 from the definition $L(<R_\text{eff}) \equiv \frac 12 L_\text{tot}$ and the growth curve $L(<R')$ from the MGE model of the outer regions, where $R'$ is the projected radius on the sky.
 We find the effective radius to be $R_\text{eff} \simeq 2.6'' \hat{=} 5.2 \text{ kpc}$.
 All values are summarized in Table \ref{tab:galaxyparameters}.
-
-\Wilma{[TO DO: Reff and Rein are also projected radii. Maybe prime them as well?]}

### 2015-11-16 LensingPaper_draft_v3.01.tex
Included corrections in abstract and introduction.
More corrections; abstract is now 250 words long; edited introduction.

--- 2015-08-04 LensingPaper_draft_v1.01.tex
@@
-\documentclass[useAMS,usenatbib]{mn2e}
+\documentclass[useAMS,usenatbib]{mnras}
 
@@
 \setcounter{secnumdepth}{2}	%depth of section numbering
+\usepackage{hyperref} %ready-to-lick referencing
+
+%_____MACROS______
+\newcommand*\diff{\mathop{}\!\mathrm{d}}
+\newcommand*\Diff[1]{\mathop{}\!\mathrm{d^#1}}
+%\newcommand{\vect}[1]{\boldsymbol{#1}} % Uncomment for BOLD vectors.
+\newcommand{\vect}[1]{\vec{#1}} % Uncomment for ARROW vectors.
+\usepackage[usenames,dvipsnames]{xcolor}
+\newcommand{\Wilma}[1]{\textcolor{Magenta}{#1}}
 
@@
 \title[A spiral galaxy's mass distribution uncovered]{A spiral galaxy's mass distribution uncovered through lensing and dynamics}
-\author[W. Trick, G. van de Ven and A. Dutton]{W. Trick$^{1}$\thanks{E-mail:
-trick@mpia.de}, G. van de Ven$^{1}$ and A. Dutton$^{1}$\\
+\author[W. H. Trick, G. van de Ven and A. A. Dutton]{Wilma H. Trick$^{1}$\thanks{E-mail:
+trick@mpia.de}, Glenn van de Ven$^{1}$ and Aaron A. Dutton$^{1}$\\
 $^{1}$Max-Planck-Institute for Astronomy, K\"{o}nigstuhl 17, 69117 Heidelberg, Germany}
@@
 
-\date{Accepted ????. Received ????; in original form ????}
+\date{Accepted ???. Received ???; in original form ???}
 
-\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2014}
+\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2015}
 
@@
 \begin{abstract}
-\include{docs/abstract_v1.01}
+\input{docs/abstract_v3.02} %[Fertig.]
 \end{abstract}
@@
 \begin{keywords}
-blabla -- blabla: bla.
+gravitational lensing: strong -- stars: kinematics and dynamics -- galaxies: kinematics and dynamics -- galaxies: photometry -- galaxies: structure
 \end{keywords}
@@
 %Introduction
-\include{docs/introduction_v1.01}
+\input{docs/introduction_v3.02} %[Fast fertig ueberarbeitet - fehlen noch 2 referenzen.]
 %--------------------------------------------
@@
 %------------------------
-\include{docs/data_v1.01}
+\section{Modelling} \label{sec:Modelling}
+\input{docs/model_MGE_v3.01}
+\input{docs/model_lensing_v3.01}
+\input{docs/model_JAM_v3.01}
 %------------------------
@@
 %------------------------
-\section{Modelling}
-\include{docs/model_MGE_v1.01}
-\include{docs/model_lensing_v1.01}
-\include{docs/model_fitting_v1.01}
-\include{docs/model_JAM_v1.01}
+\input{docs/data_v3.02}
 %------------------------
@@
 %------------------------
-\section{Results}
-\include{docs/results_photometry_v1.01}
-\include{docs/results_lensing_v1.01}
-\include{docs/results_JAMwithSB_v1.01}
-\include{docs/results_JAMwithNFW_v1.01}
+\section{Results} \label{sec:Results}
+\input{docs/results_photometry_v3.01}
+\input{docs/results_lensing_v3.01}
+\input{docs/results_JAMwithSB_v3.01}
+\input{docs/results_JAMwithNFW_v3.01}
 %------------------------
@@
 %------------------------
-\section{Discussion and Conclusion}
-\include{docs/discussion_merger_v1.01}
-\include{docs/summary_v1.01}
+\section{Discussion and Conclusion} \label{sec:Discussion}
+\input{docs/discussion_ML_v3.01}
+\input{docs/discussion_merger_v3.01}
+\input{docs/summary_v3.01}
 %------------------------
@@
 %---------------------------------------------------------------------------
-\bibliographystyle{mn2e}
+\bibliographystyle{mnras}
 \bibliography{literaturelist}

### 2015-11-16 archive/v3/docs/abstract_v3.01.tex
More corrections; abstract is now 250 words long; edited introduction.

--- 2015-11-13 docs/abstract_v3.01.tex
@@
 The best fit dynamical model predicts a total mass inside the Einstein radius consistent with the lens model, and vice versa the lens model gives an successful prediction for the observed kinematics in the galaxy center.
-For a dynamical model including a NFW dark matter halo,  we constrain the halo to have virial velocity $v_{200} \simeq 240 \pm 40$ km/s and a concentration of $c_{200} \simeq 8 \pm 2$ in case of a moderate tangential velocity anisotropy of $\beta_z \simeq -0.4 \pm 0.1$.
+For a dynamical model including a NFW dark matter halo,  we constrain the halo to have virial velocity $v_{200} \simeq 240 \pm 40~\text{km s}^{-1}$ and a concentration of $c_{200} \simeq 8 \pm 2$ in case of a moderate tangential velocity anisotropy of $\beta_z \simeq -0.4 \pm 0.1$.
 The NFW halo models can successfully reproduce the signatures of J1331's counter-rotating stellar core and predict J1331's stellar and gas rotation curve at larger radii.

### 2015-11-16 docs/abstract_v3.02.tex
More corrections; abstract is now 250 words long; edited introduction.

We investigate the matter distribution of a spiral galaxy with counter-rotating stellar core, SDSS J1331+3628 (J1331), independently with gravitational lensing and dynamical modelling. By fitting a gravitational potential model to a quadruplet of lensing images around J1331's bulge, we tightly constrain the mass inside the Einstein radius $R_\text{ein}=(0.91\pm0.02)''(\simeq1.83\pm0.04~\text{kpc})$ to within 4\%: $M_\text{ein} = (7.8\pm0.3) \cdot 10^{10} M_\odot$. We model observed long-slit major axis stellar kinematics in J1331's central regions by finding Multi-Gaussian Expansion (MGE) models for the stellar and dark matter distribution that solve the axisymmetric Jeans equations. The lens and dynamical model are independently derived, but in very good agreement with each other around $\sim R_\text{ein}$. We find that J1331's center requires a steep total mass-to-light ratio gradient. A dynamical model including a NFW halo (with virial velocity $v_{200} \simeq 240 \pm 40~\text{km s}^{-1}$ and concentration of $c_{200} \simeq 8 \pm 2$) and moderate tangential velocity anisotropy ($\beta_z \simeq -0.4 \pm 0.1$) can reproduce the signatures of J1331's counter-rotating core and predict the stellar and gas rotation curve at larger radii. However, our models do not agree with the observed velocity dispersion at large radii. We speculate that the reason could be a non-trivial re-distribution of matter due to a possible merger event in J1331's recent past.

### 2015-11-16 docs/data_v3.02.tex
More corrections; abstract is now 250 words long; edited introduction.

--- 2015-11-13 docs/data_v3.01.tex
@@
 \\Inside of $\sim 4''$, the data appears to be symmetric, outside of this the assumption of axisymmetry seems not to be valid anymore, considering the data.
-We add -2.3 km/s to the $v_\text{rot}$ to ensure $v_\text{rot}(R'=0) \sim 0$ as a possible correction term for a misjudgement of the systemic velocity.
-We also symmetrize the data within $4''$ and asign a minimum error of $\delta v_\text{rms} > 5$ km/s to the $v_\text{rms}$ data.
+We add $-2.3~\text{km s}^{-1}$ to the $v_\text{rot}$ to ensure $v_\text{rot}(R'=0) \sim 0$ as a possible correction term for a misjudgement of the systemic velocity.
+We also symmetrize the data within $4''$ and asign a minimum error of $\delta v_\text{rms} > 5~\text{km s}^{-1}$ to the $v_\text{rms}$ data.
 In the JAM modelling, which is based on the assumption of axisymmetry, only stellar kinematics with $R'  \lesssim 2.5''$ or $R' \lesssim 4''$ are used.
-Another reason to restrict to modelling on the bulge region is that our MGE in Table \ref{tab:MGEF814W} is only a good representation of J1331's F814W light distribution inside $\sim 5''$.\\
+Another reason to restrict to modelling on the bulge region is that our MGE in Table \ref{tab:MGEF814W} is only a good representation of J1331's F814W light distribution inside $\sim 5''$.
+
+ \Wilma{[TO DO: Maybe mention the following details better in the data section....
+"SWELLS picked galaxies in SDSS whose spectra had two different redshifts within $3''$, which makes it likely to capture strong lenses with typical Einstein radii of $1''$.
+Sufficiently inclined galaxies were picked by eye.
+Follow-up high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) was performed to confirm their lensing status \citep{SWELLSI}."]}
+
+ \Wilma{[TO DO: Include better in data section. "of approximate Hubble type Sb at right ascension = 202.91800$^\circ$ and a declination = 36.46999$^\circ$ (epoch J2000)"]}

### 2015-11-16 docs/discussion_ML_v3.01.tex
More corrections; abstract is now 250 words long; edited introduction.

@@
 We've presented different dynamical models of the central region of J1331, some of them capturing the observed kinematics well, but none of them work both at small and large radii.
-In the following we will discuss possible reasons for these deviations by also comparing our results to previous work.
+In the following we will discuss possible reasons for these deviations, also by comparing our results to previous work.
 
@@
 Further knowledge of the stellar populations within J1331 and their initial mass functions (IMF) would be useful.
-In particular a sophisticated guess for the \emph{stellar} mass-to-light ratio in J1331's bulge could be compared to our very reliable measurement of the \emph{total} mass-to-light ratio inside the Einstein radius (see Table \ref{tab:einsteinML} ) to support or contradict the presence of a lot of dark matter in the bulge.
-\\
+In particular a sophisticated guess for the \emph{stellar} mass-to-light ratio in J1331's bulge could be compared to our very reliable measurement of the \emph{total} mass-to-light ratio inside the Einstein radius (see Table \ref{tab:einsteinML} ) to support or contradict the presence of a significant amount of dark matter in the bulge.
 
@@
 $$\xi(m) \propto m^{-x}, x=2.35,$$
-(where $\xi(m) \diff m$ is the number of stars with mass $m$ in $[m,m+\diff m]$) and the IMFs by \citet{2002Sci...295...82K} and \citet{Chabrier2003}, which are in agreement with each other and predict less low-mass stars.
-\\
+where $\xi(m) \diff m$ is the number of stars with mass $m$ in $[m,m+\diff m]$, and the IMFs by \citet{2002Sci...295...82K} and \citet{Chabrier2003}, which are in agreement with each other and predict less low-mass stars.
 
@@
 A higher $\sigma_0$ suggests a more bottom-heavy IMF.
-For an unimodal (Salpeter-like) IMF and a $\sigma_0 \propto 200 $ km/s for J1331 (see Figure \ref{fig:kinematics}) they predict $x \approx 2.33$ (see Figure 4 in \citet{Ferreras}), which is close to the standard Salpeter slope.
-These findings are supported by \citet{2014MNRAS.438.1483S}, who found for SDSS galaxies also a relation between unimodal (single power-law) IMF slope and stellar velocity dispersion.
-Their Table 2 lists $x(\sigma_*=190 \pm 20 \text{ km s}^{-1}) = 2.08 \pm 2.08$ and $x(\sigma_*= 230 \pm 20 \text{ km s}^{-1}) = 2.33 \pm 0.4$.
-When assuming a bi-modal (Kroupa-equivalent-like) IMF, \citet{Ferreras} predict $x \approx 2.85$ (see Figure 4 in \citet{Ferreras}) for J1331's central velocity dispersion.
+For an unimodal (Salpeter-like) IMF and a $\sigma_0 \simeq 200~\text{km s}^{-1}$ for J1331 (see Figure \ref{fig:kinematics}) they predict $x \approx 2.33$, which is close to the standard Salpeter slope, also supported by \citet{2014MNRAS.438.1483S}.
+When assuming a bi-modal (Kroupa-equivalent-like) IMF, \citet{Ferreras} predict $x \approx 2.85$ for J1331's central velocity dispersion.
 This is more bottom-heavy than the standard \citet{2002Sci...295...82K} IMF.
-Overall the central velocity dispersion suggests a rather bottom-heavy IMF J1331's bulge and therefore large stellar mass-to-light ratio.\\
+Overall the central velocity dispersion suggests a rather bottom-heavy IMF J1331's bulge and therefore large stellar mass-to-light ratio.
+\citet{SWELLSI} estimated J1331's stellar bulge mass given a Salpeter IMF and measured the I-band AB magnitude of the bulge.
+Transformed to a stellar I-band mass-to-light ratio (see Table \ref{tab:previousresults}) this would correspond to $\Upsilon_\text{I,*}^\text{sal} = 4.7 \pm 1.2$.
 
-\citet{SWELLSI} estimated J1331's stellar bulge mass given a Salpeter IMF and measured the I-band AB magnitude of the bulge.
-Transformed to a stellar I-band mass-to-light ratio (see Table \ref{tab:previousresults}) this would correspond to $\Upsilon_\text{I,*}^\text{sal} = 4.7 \pm 1.2$.\\
+We compare our findings of the stellar mass-to-light ratios with the study by \cite{SWELLSV}: They found that the bulge of J1331 has an IMF more bottom-heavy than the Salpeter IMF from fitting a NFW halo to (1) the Einstein mass and (2) gas kinematics at larger radii $\gtrsim 8''$.
+In Section \ref{sec:results_JAM_NFW} we fitted the stellar kinematics within $\sim 3.5''$ and the Einstein mass with a NFW halo and the best fit $\Upsilon_\text{I,*} = 4.2 \pm 0.2$ (see Table \ref{tab:modelB4_bestfit}) indicates a less bottom-heavy IMF than the Salpeter IMF.
+\cite{SWELLSV}  found systematically lower NFW halos ($v_\text{circ}(5'') \sim 120~\text{km s}^{-1}$ according to their Figure 2) than we did ($v_\text{circ}(5'') \sim 200~\text{km s}^{-1}$, see Figure \ref{fig:kinematics}).
 
-We compare our findings of the stellar mass-to-light ratios with the study by \cite{SWELLSV}: \cite{SWELLSV} found that the bulge of J1331 has an IMF more bottom-heavy than the Salpeter IMF from fitting a NFW halo to (1) the Einstein mass and (2) gas kinematics at larger radii $\gtrsim 8''$.
-In Section \ref{sec:results_JAM_NFW} we fitted the stellar kinematics within $\sim 3.5''$ and the Einstein mass with a NFW halo and the best fit $\Upsilon_\text{I,*} = 4.2 \pm 0.2$ (see Table \ref{tab:modelB4_bestfit}) indicates a less bottom-heavy IMF than the Salpeter IMF.
-\cite{SWELLSV}  found systematically lower NFW halos ($v_\text{circ}(5'') \sim 120 \text{km s}^{-1}$ according to their Figure 2) than we did ($v_\text{circ}(5'') \sim 200 \text{km s}^{-1}$, see Figure \ref{fig:kinematics}).
 We note however, that our results would be much closer to those by \citet{SWELLSV}, if we only used the lensing results at small radii as they did: The total mass-to-light ratio of $\Upsilon_\text{I,tot}^\text{ein} = 5.6$ inside the Einstein radius (see Table \ref{tab:einsteinML}).
-In case of a lower mass dark matter halo, the largest contribution to this mass-to-light ratio would then be stellar mass.
-And the corresponding IMF would be more bottom-heavy than Salpeter,  like what \citet{SWELLSV} found.
-The circular velocity curve $v_\text{circ}(R) = \left.
-\sqrt{R \frac{\partial \Phi}{\partial R}} \right|_{z=0}$ \citet{SWELLSV} find for J1331 peaks at $v_\text{circ}(R\sim0.9'') \sim 350 \text{km s}^{-1}$ (from lensing constraints only) and at $v_\text{circ}(R\sim0.9'') \sim 370 \text{km s}^{-1}$ (when including a dark matter halo and gas kinematics in the fit).
-We get a very similar circular velocity curve (at least at small radii) for a mass-follows-light model with constant $\Upsilon_\text{I,tot}^\text{ein} = 5.6$, which peaks at $v_\text{circ}(R\sim0.9'') \sim 360 \text{km s}^{-1}$.
+In case of a lower mass dark matter halo, the largest contribution to this mass-to-light ratio would then be stellar mass, so that the corresponding IMF would be more bottom-heavy than Salpeter.
+The circular velocity curve that \citet{SWELLSV} find for J1331 peaks at $v_\text{circ}(R\sim0.9'') \sim 350~\text{km s}^{-1}$ (from lensing constraints only) and at $v_\text{circ}(R\sim0.9'') \sim 370~\text{km s}^{-1}$ (when including a dark matter halo and gas kinematics in the fit).
+We get a very similar circular velocity curve (at least at small radii) for a mass-follows-light model with constant $\Upsilon_\text{I,tot}^\text{ein} = 5.6$, which peaks at $v_\text{circ}(R\sim0.9'') \sim 360~\text{km s}^{-1}$.
 From this comparison follows, that the model by \citet{SWELLSV} corresponds approximately to a mass-follows-light model in the inner regions of J1331.
 In Section \ref{sec:results_JAM_SB} however we showed, that this is \emph{not} a good model for J1331 and won't be able to reproduce the central stellar $v_\text{rms}$ dip.
-On the other hand, because our NFW JAM models fail to predict the stellar kinematics at large radii, the true halo parameters are more likely closer to the findings by \citet{SWELLSV}.\\
 
+On the other hand, because our NFW JAM models fail to predict the stellar kinematics at large radii, the true halo parameters are more likely closer to the findings by \citet{SWELLSV}.
 All of this leaves the central dip unexplained: It cannot be due to tangential velocity anisotropy in the center alone (see Section \ref{sec:results_JAM_SB}, Figure \ref{fig:JAM_modelA2}).
-It also cannot be explained by a strong contribution of dark matter inside the bulge together with a moderate tagential velocity anisotropy, because the corresponding dark matter halos would still be too massive to fit the data in the outer regions (see Section \ref{sec:results_JAM_NFW}, Figure \ref{fig:modelB4_vrms}]).\\
+It also cannot be explained by a strong contribution of dark matter inside the bulge together with a moderate tagential velocity anisotropy, because the corresponding dark matter halos would still be too massive to fit the data in the outer regions (see Section \ref{sec:results_JAM_NFW}, Figure \ref{fig:modelB4_vrms}]).
 
@@
 This is very close to the stellar mass-to-light ratio we got from \citet{SWELLSI} estimates of the bulge's stellar mass using the Chabrier IMF $\Upsilon_\text{I,*}^\text{Chabrier} = 2.5 \pm 0.6$, i.e.
-less bottom-heavy (more bluish) population.\\
+less bottom-heavy (more bluish) population.
 
-Another feature in the stellar kinematics, that none of our JAM models was able to reproduce in the slightest and which we therefore excluded in the modelling, was the dip in $v_\text{rms}$ around $\sim 6''$, which occurs around the transition from bulge to disk (see Figures \ref{fig:F814W} and \ref{fig:kinematics}).\\
+Another feature in the stellar kinematics, that none of our JAM models was able to reproduce in the slightest and which we therefore excluded in the modelling, was the dip in $v_\text{rms}$ around $\sim 6''$, which occurs around the transition from bulge to disk (see Figures \ref{fig:F814W} and \ref{fig:kinematics}).
 
@@
 (According to Figure \ref{fig:lenscompareboth} the lensing result might not predict a mass to light ratio gradient inside $R_\text{ein}$, but then again the mass slope $alpha=1$ was only weakly constrained.) The disk of J1331 has a lower $\Upsilon_\text{I,*}$ than the bulge (see Table \ref{tab:previousresults} according to \citet{SWELLSI}).
-Such a drop in $\Upsilon_\text{I,*}$ at the transition region from bulge to disk around $\sim 5''$ could lead to the observed drop in $v_\text{rms}$, while an increasing contribution of a lower mass dark matter halo at larger radii as found by \citet{SWELLSV}, would recover the kinematics in the out regions of J1331's disk.\\
+Such a drop in $\Upsilon_\text{I,*}$ at the transition region from bulge to disk around $\sim 5''$ could lead to the observed drop in $v_\text{rms}$, while an increasing contribution of a lower mass dark matter halo at larger radii as found by \citet{SWELLSV}, would recover the kinematics in the out regions of J1331's disk.
 

### 2015-11-16 docs/discussion_merger_v3.01.tex
More corrections; abstract is now 250 words long; edited introduction.

@@
 \subsection{On J1331's possible merger history}
+
+\Wilma{[TO DO: Remove minor in merger.]}
 
@@
 Accretion of gas on retrograde orbits and subsequent star formation could lead to a younger and counter-rotating stellar population \Wilma{[TO DO: REF]}.
-However, the to form enough stars such that the net rotation of the large and massive core is retrograde, a very large amount of gas would have had to be accreted by J1331- which is not very likely [TO DO: REF].
+However, to form enough stars such that the net rotation of the large and massive core is retrograde, a very large amount of gas would have had to be accreted by J1331---which is not very likely [TO DO: REF].
+
 Another scenario are galaxy mergers.
-The products of major mergers of similarly massive disk galaxies are often quiescent, elliptical galaxies \citep{1972ApJ...178..623T} [TO DO: correct reference???].
-Therefore a minor merger is more likely to have occured in J1331.
-The dense nucleus of a satellite galaxy on a retrograde orbit could survive the dissipationless accretion and could spiral to core due to tidal friction \citep{1984ApJ...287..577K}.
+Major mergers including large amounts of gas can form kinematically decoupled cores (KDCs), see e.g., \Wilma{[TO DO: REF: Lauren Hofman et al 2010 - read paper how this fits with the reverse color gradient]}.
+During a minor merger, the dense nucleus of a satellite galaxy on a retrograde orbit could survive the dissipationless accretion and could spiral to the core due to tidal friction \citep{1984ApJ...287..577K}.
 Usually large bulges of spirals or ellipticals are reddest in the center and become bluer further out.
@@
 Such a reverse color gradient could correspond to an increasing stellar mass-to-light ratio.
-\\The minor merger theory could explain and support our findings from dynamical modelling and the previous sections, that J1331 might have an increasing stellar mass-to-light ratio within its core.
+
+The merger theory could explain and support our findings from dynamical modelling and the previous sections, that J1331 might have an increasing stellar mass-to-light ratio within its core.
+
+\Wilma{[TO DO: Include in discussion: Kinematic twist due to merger.
+Bulge and disk have different kinematic major axis, and the measured velocities in the disk, which are off from the major axis, are much lower than the actual maximum vcirc.
+Could explain the dips in the outer regions.]}
 
@@
 Would this be the case for J1331 the assumption of axisymmetry is not true anymore and our dynamical modelling would fail.
-\\Mergers also could have changed the 3D shape of the dark matter halo and the NFW halo was therefore not a good model for J1331's dark matter halo.
+
+Mergers also could have changed the 3D shape of the dark matter halo and the NFW halo was therefore not a good model for J1331's dark matter halo.
 We also tried to model J1331 with a cored logarithmic halo.
 However, due to degeneracies in the modelling, we were not able to either constrain the profile for a cored logarithmic halo, or to rule it out.
+
+\Wilma{[TO DO: Include in this discussion the findings from the color profile.]}
 
@@
 Subsequently detailed stellar population analyses of the spectra taken along J1331's major axis should be conducted to constrain the mass-to-light ratio reliably.
+\Wilma{[TO DO: Include in this discussion the findings from the color profile.]}
+
 In addition, the dynamical modelling should use more of the available information on J1331 and fit dynamics (stellar and gas kinematics from \citet{SWELLSV}) simultaneously with the gravitational lensing (image positions, shape and even flux ratios) in a similar fashion to \citet{SWELLSIV}.
@@
 However, for this to work a good model for the galactic extinction would be needed.
+
 High-resolution integral-field spectroscopy could help with this, allow for spatially resolved stellar population analysis and dynamical modelling in two dimensions.
-This would lead to much better understanding of J1331's structure and mass distribution and therefore answer questions on how minor mergers might modify spiral galaxies.
+\Wilma{[TO DO: Include in this discussion that this could also help test, if the vrms dip is maybe because of twist, i.e.
+the measurements where not done along the major axis in the disk]} This would lead to much better understanding of J1331's structure and mass distribution and therefore answer questions on how minor mergers might modify spiral galaxies.
+
+\Wilma{[TO DO: Include in discussion: High resolution IFU: high spatial resolution --> to resolve small features.
+High spectral resolution --> because the velocity dispersion in the outer regions of the galaxy are very low and to measure them accurately, need high spectral resolution.]}

### 2015-11-16 docs/introduction_v3.02.tex
More corrections; abstract is now 250 words long; edited introduction.

--- 2015-11-13 docs/introduction_v3.01.tex
@@
 
-%Intro
 Gravitational lensing and dynamical modelling provide independent constraints on the mass distribution of galaxies.
-Combining them allows for valuable cross-checking opportunities to resolve degeneracies inherent in both methods.
-It can also help to disentangle the stellar and dark matter content of galaxies.
+Combining them allows for valuable cross-checking opportunities to disentangle the stellar and dark matter (DM) content of galaxies.
 
-%Dark Matter
-The flat rotation curves of galaxies \citep{1978ApJ...225L.107R} were the first indication that galaxies might reside in massive, almost spherical halos made of invisible ``dark'' matter.
-The standard model of cosmology, based on results by the Planck Mission \citep{WMAP5cosm} \Wilma{[TO DO: Aaron thinks Dunkley is a WMAP paper....
-Check difference WMAP/Planck...]}, infers that $\sim 85\%$ of the universe's total matter content is in the form of non-baryonic cold dark matter.
-Simulations suggest that this kind of dark matter forms cuspy halos following a Navarro-Frenk-White (NFW) profile \citep{NFW96}.
-However, central dark matter density cusps are not observed in dark matter dominated dwarf galaxies (e.g., \citealt{1994Natur.370..629M,2001ApJ...552L..23D}).
-Their existence in more massive galaxies depends strongly on stellar mass-to-light ratio (e.g., \citealt{2011MNRAS.416..322D}).
-Overall, observations suggest cored dark matter halos.
+Cosmological simulations suggest that cold DM forms cuspy halos following a Navarro-Frenk-White (NFW) profile \citep{NFW96}.
+However, the existence of central DM density cusps in more massive galaxies depends strongly on the stellar mass-to-light ratio (e.g., \citealt{2011MNRAS.416..322D}), while DM dominated dwarf galaxies strongly favour cored DM halos (e.g., \citealt{1994Natur.370..629M,2001ApJ...552L..23D}).
 This discrepancy, known as the core-cusp problem, might be resolved by galaxy formation processes such as mergers and outflows (e.g., \citealt{2001ApJ...560..636E,2012MNRAS.421.3464P}).
 
-Determining the overall mass distribution in massive galaxies and separating the dark from the stellar mass components is therefore a crucial step in better understanding the structure of galaxies and nature or dark matter.
+Determining the overall mass distribution in massive galaxies and separating the DM from the stellar mass components is therefore a crucial step in better understanding the structure and formation of galaxies and nature of DM.
 
-%Lensing
-Strong gravitational lensing is an independent method to tightly constrain the projected total mass of galaxies inside $\sim 1''$.
-Massive galaxies can act as gravitational lenses and deflect the light of background sources, giving rise to multiple distorted images of the source.
-By 2010 over 200 strong gravitational galaxy lenses had been discovered and the number is still rising (e.g., \citealt{2010ARA&A..48...87T}).
+Massive galaxies can act as gravitational lenses, deflect the light of background sources and give rise to multiple images.
+This strong gravitational lensing tightly constrains the projected total mass of the lens galaxy inside $\sim 1''$ (e.g., \citealt{2010ARA&A..48...87T}).
 
-%Dynamical modelling
-The mass profile at larger galactocentric radii can be probed by gas rotation curves that directly measure the galaxy's circlar velocity profile \Wilma{[TO DO: REF]}.
+The mass profile at larger galactocentric radii can be probed by gas rotation curves that directly measure the galaxy's circular velocity profile \Wilma{[TO DO: REF]}.
 However, due to its dissipative nature, gas motions are very sensitive to disturbances by e.g.
@@
 Because stars are dissipationless dynamical tracers and present almost everywhere in the galaxy, stellar dynamical modelling can complement mass constraints from lensing at small and gas motions at large radii.
-But stellar motions are complex: a bulk rotation around one principal axis combined with random motions in all coordinate direction.
-Full dynamical modelling of rotation, dispersion and velocity anisotropies is needed to deduce the matter distribution.
+As stellar motions are complex---a bulk rotation around one principal axis combined with random motions in all coordinate directions---, full dynamical modelling of rotation, dispersion and velocity anisotropies is needed to deduce the matter distribution.
 
-The Sloan WFC Edge-on Late-type Lens Survey (SWELLS, WFC = Wide field camera) \citep{SWELLSI,SWELLSII,SWELLSIII,SWELLSIV,SWELLSV,SWELLSVI} is dedicated to find and investigate spiral galaxies, seen almost edge-on so rotation curves can be easily measured, that are also strong gravitational lenses.
+The Sloan WFC Edge-on Late-type Lens Survey (SWELLS, WFC = Wide field camera) \citep{SWELLSI,SWELLSII,SWELLSIII,SWELLSIV,SWELLSV,SWELLSVI} is dedicated to find and investigate spiral galaxies, which are (a) strong gravitational lenses and (b) seen almost edge-on, such that rotation curves can be easily measured.
 By combining lensing and dynamical modelling degeneracies inherent in both methods can be broken.
-SWELLS picked galaxies in SDSS whose spectra had two different redshifts within $3''$, which makes it likely to capture strong lenses with typical Einstein radii of $1''$.
-Sufficiently inclined galaxies were picked by eye.
-Follow up high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) was performed to confirm their lensing status \citep{SWELLSI}.
 
-%Characteristics of J1331
-One of the SWELLS galaxies is SDSS J1331+3628, to which we refer as J1331 in the remainder of this work.
-It is a spiral galaxy of approximate Hubble type Sb at right ascension = 202.91800$^\circ$ and a declination = 36.46999$^\circ$ (epoch J2000).
+One of the SWELLS galaxies is the massive spiral SDSS J1331+3628, to which we refer as J1331 in the remainder of this work.
 It has bluish spiral arms and a large reddish bulge (see Figures \ref{fig:F450W} and \ref{fig:F814W}), which is superimposed by quadruplet of extended bluish images approximately at a distance of $1''$ from the galaxy center (see Figure \ref{fig:lens_just_imgpos}).
 The lensed object might be a star-forming blob of a background galaxy.
-J1331 stands out of the SWELLS sample because of its large counter-rotating core (see Figure \ref{fig:kinematics}), which might be an indication that J1331 underwent a minor merger in its recent past.
+J1331 stands out of the SWELLS sample because of its large counter-rotating core (see Figure \ref{fig:kinematics}), which might be an indication that J1331 underwent a merger in its recent past.
 
-%Previous results
 \citet{SWELLSI} confirmed that J1331 was a strong gravitational lens, measured its apparent brightness and estimated the stellar masses of disk and bulge.
@@
 
-%Goal of this work
 The goal of this work is to complement the previous work on J1331 by an in-depth analysis of the matter distribution in J1331's inner regions.
 We use stellar dynamical modelling in addition to lensing constraints, similar to a study of the Einstein Cross by \citet{GlennEC}.
-We attempt to disentangle the stellar and dark matter components and test if employed axisymmetric Jeans models work also in the presence of a counter-rotating core.
-Ideally this work on J1331 could also help understanding how minor mergers modify the mass distribution of a galaxy.
+We attempt to disentangle the stellar and DM components and test if employed axisymmetric Jeans models work also in the presence of a counter-rotating core.
+Ideally this work on J1331 could also help understanding how mergers modify the mass distribution of a galaxy.
 
-This paper is organized as follows: Section \ref{sec:Modelling} gives an overview of the modelling techniques used in this work, Section \ref{sec:data} summarizes the data and Section \ref{sec:Results} presents our results on the surface photometry of J1331 using Multi-Gaussian expansions (Section \ref{sec:MGE_results}), constraints from lensing (Section \ref{sec:results_lensing}) and Jeans modelling based on the surface brightness only (Section \ref{sec:results_JAM_SB}) and including a NFW dark matter halo (Section \ref{sec:results_JAM_NFW}).
+This paper is organized as follows: Section \ref{sec:Modelling} gives an overview of the modelling techniques used in this work, Section \ref{sec:data} summarizes the data and Section \ref{sec:Results} presents our results on the surface photometry of J1331 using Multi-Gaussian expansions (Section \ref{sec:MGE_results}), constraints from lensing (Section \ref{sec:results_lensing}) and Jeans modelling based on the surface brightness only (Section \ref{sec:results_JAM_SB}) and including a NFW DM halo (Section \ref{sec:results_JAM_NFW}).
 Finally Section \ref{sec:Discussion} uses the result to discuss J1331's stellar mass-to-light ratio and possible merger history and starting points for future work.
-
-%\paragraph{Methods}
-%\begin{itemize}
-%\item lensing: fitting scale-free galaxy model to image positions \citep{EvansWitt}
-%\item photometry: MGE expansion of surface brightness in the F814W filter (deconvolution with PSF), apparent magnitude, total luminosity, effective radius
-%\item Jeans modelling: jeans axisymmetric modelling (JAM) by \citet{Cap08} to fit model predictions for the second velocity moments to the stellar kinematics data
-%\end{itemize}
 
@@
 The blob above A could be stretched due to lensing and have a faint counter image between B and G.
-Maybe indicate in plot?]}}
+Maybe indicate in plot?]} \Wilma{[TO DO: Use $\text{km s}^{-1}$ instead of km/s]}}
 \label{fig:specialJ1331}

### 2015-11-16 docs/model_JAM_v3.01.tex
More corrections; abstract is now 250 words long; edited introduction.

@@
 where $n(\vect{x}) = \int f(\vect{x},\vect{v}) \Diff3 v$ is the number density of tracers and $\Phi(\vect{x})$ the galaxy's gravitational potential, generated by the mass density $\rho(\vect{x})$ via Poisson's equation.
-\\The JAM modelling approach by \citet{Cap08} makes use of expressing the tracer density and the mass density as MGEs (see also \citet{1994A&A...285..723E}).
+
+The JAM modelling approach by \citet{Cap08} makes use of expressing the tracer density and the mass density as MGEs (see also \citet{1994A&A...285..723E}).
 The density of stellar tracers is assumed to be proportional to the observed and deprojected brightness distribution $\nu(R,z)$ in Equation \ref{eq:deprojMGE}.
@@
 is then the light-weighted circular velocity curve, given the second velocity moments found from the Jeans equations.
-\\To model the counter-rotating core of J1331 with one free parameter, we employ the condition that the overall $\kappa(R)$ profile should smoothly and relatively steeply transition from $\kappa(R) = -\kappa' < 0$ at small $R$ through $\kappa(R_0) \equiv 0$ and increase to $\kappa(R) = \kappa' > 0$ at large $R$.
+
+To model the counter-rotating core of J1331 with one free parameter, we employ the condition that the overall $\kappa(R)$ profile should smoothly and relatively steeply transition from $\kappa(R) = -\kappa' < 0$ at small $R$ through $\kappa(R_0) \equiv 0$ and increase to $\kappa(R) = \kappa' > 0$ at large $R$.
 Our imposed profile is

### 2015-11-16 docs/model_lensing_v3.01.tex
Included corrections in abstract and introduction.
More corrections; abstract is now 250 words long; edited introduction.

--- 2015-09-15 archive/docs/model_lensing_v1.02.tex
@@
-\subsection{Strong gravitational lensing formalism and lens model} \label{sec:lensing_theo}
+\subsection{Strong gravitational lens model} \label{sec:lensing_theo}
 
@@
 The gradient of the deflection potential $\vect{\nabla}_\theta \psi(\vect{\theta})$ is equal to the angle by which the light is deflected multiplied by $D_{ds}/D_{s}$.
-\\The total time delay of an deflected light path through $\vect{\theta}$ with respect to the unperturbed light path is given by 
+
+The total time delay of an deflected light path through $\vect{\theta}$ with respect to the unperturbed light path is given by 
 \begin{equation}
@@
 \citep{BartGravLens}. According to Fermat's principle the image positions will be observed at the extrema of $\Delta t(\vect{\theta})$.
-\\The inverse magnification tensor
+
+The inverse magnification tensor
 \begin{equation}
@@
 The position of the source with respect to the caustic detemines the number of images and their configuration and shape with respect to each other.
-\\The \emph{Einstein mass} $M_\text{ein}$ and \emph{Einstein radius} $R_\text{ein}$ are defined via the relation
+
+The \emph{Einstein mass} $M_\text{ein}$ and \emph{Einstein radius} $R_\text{ein}$ are defined via the relation
 \begin{equation*}
@@
 We set $a_1 = b_1 = 0$, which corresponds to the choice of origin; in this case the center of the galaxy.
-\\To be able to constrain the slope $\alpha$, we would have needed flux ratios for the images as in \citet{GlennEC}.
+
+To be able to constrain the slope $\alpha$, we would have needed flux ratios for the images as in \citet{GlennEC}.
 But the extended quality of the images, possible dust obscuration and surface brightness fluctuations due to microlensing events, as well as the uncertainty in surface brightness subtraction make flux determination too unreliable and we do not include them in the fitting.

### 2015-11-16 docs/results_JAMwithNFW_v3.01.tex
More corrections; abstract is now 250 words long; edited introduction.

@@
 The version from October 2013 was used in this work.} \citep{emcee} and use priors for the halo parameters to guide the fit to a realistic NFW halo shape.
-\\\citet{Dutton10} give a relation for halo vs. stellar mass for late-type galaxies. For a stellar population with a Chabrier IMF they found
-\begin{equation*}
-y = y_0 \left( \frac{x}{x_0} \right)^\alpha \left[ \frac 12 + \frac 12 \left(\frac{x}{x_0} \right)^\gamma \right]^{(\beta - \alpha)/\gamma},
-\end{equation*}
-where $x= m_*$ [$M_\odot h^{-2}$] is the stellar mass, $y = \frac{\langle M_{200}\rangle}{m_*}$ and $\langle M_{200}\rangle$ [$M_\odot h^{-2}$] is the mean halo mass.
-The parameters for the mean and $2\sigma$ error curves for this relation are$\alpha = -0.5\pm0.15$, $\beta = 0$, $\gamma = 1.0$, $\log_{10} x_0 = 10.4$, $\log_{10} {y_0}_{-0.24}^{+0.28}$ \citet{Dutton10}.
+
+\citet{Dutton10} give a relation for halo vs.
+stellar mass for late-type galaxies.
 Using the stellar mass estimate for J1331 from \citet{SWELLSI} $m_* = (1.06 \pm 0.25) \cdot 10^{11} M_\odot$ for the Chabrier IMF estimate, we find ${v_{200}} = (202_{-33}^{+44})_{-13}^{+12}$.
@@
 \begin{equation*}
-p(v_{200}) = \mathscr{N}(200 \text{km/s} ,40 \text{km/s}).
+p(v_{200}) = \mathscr{N}(200~\text{km s}^{-1},40~\text{km s}^{-1}).
 \end{equation*}
@@
 \\We restrict the $v_\text{rms}$ fit to a region $R' \lesssim 3.5''$, approximately within the effective half-light radius $R_\text{eff} = 2.6''$.
-We also include the Einstein mass $M(<R_\text{ein}$ with a 10\% error as an additional constraint in the fit.
-\Wilma{[TO DO: Didn't include the results from the Moster 2010 relation, because they where quite close to the Dutton 2010 relation anyway.
-Or should I?]}
+We also include the Einstein mass $M(<R_\text{ein})$ with a 10\% error as an additional constraint in the fit.
 
@@
 As the effect of $v_{200}$ is mostly at larger radii, this parameter doesn't show any covariances - but is also mostly constrained by the prior.
-The $v_\text{rms}$ curve corresponding to the mean best fit values from Table \ref{tab:modelB4_bestfit} is shown in the first panel of Figure \ref{fig:modelB4_vrot}.
-Figure \ref{fig:modelB4_models} illustrates the range of parameters fitting the data according to the full posterior probability function.
+\Wilma{[TO DO: Mention the following later in the text: "The $v_\text{rms}$ curve corresponding to the mean best fit values from Table \ref{tab:modelB4_bestfit} is shown in the first panel of Figure \ref{fig:modelB4_vrot}."]} Figure \ref{fig:modelB4_models} illustrates the range of parameters fitting the data according to the full posterior probability function.
 The model fits the $v_\text{rms}$ data in the inner regions quite well (Figure \ref{fig:modelB4_vrms}) and is also consistent with the Einstein mass (see Figure \ref{fig:modelB4_enclMass}).
@@
 However, the density profile of the cored halo as well as the I-band light distribution within the plane drop as $\rho(r) \propto r^{-2}$, there is a strong degeneracy between the stellar mass and the dark matter.
-Overall we were not able to give tight constraints on the cored logarithmic halo.
+Overall, we were not able to obtain tight constraints on the cored logarithmic halo.
 
@@
 \caption{Posterior probability distribution sampled with MCMC (red dots and histograms) for a JAM model with NFW halo, parametrized by $r_s$ and $v_\text{200}$, a stellar mass distribution generated from the I-band MGE in Table \ref{tab:MGEF814W} and a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and constant velocity anisotropy $\beta_z$.
-Shown are also the priors used for J1331's NFW halo, $\mathscr{N}(200 \text{km/s},40 \text{km/s})$ (green) and the concentration vs.
+Shown are also the priors used for J1331's NFW halo, $\mathscr{N}(200~\text{km s}^{-1},40~\text{km s}^{-1})$ (green) and the concentration vs.
 halo mass relation by \citet{Maccio08} from Equation \ref{eq:Maccio08} in terms of $v_{200}$ vs.
@@
 The histograms of the marginalized 1D distributions are overplotted by the mean (black solid lines) and $1\sigma$ error (black dashed lines), whose values are also quoted in the figure and in Table \ref{tab:modelB4_bestfit}.
-The grey diamonds mark a random sub-selection of 12 samples; the corresponding models are shown in Figure \ref{fig:modelB4_models}.}
+The grey diamonds mark a random sub-selection of 12 samples; the corresponding models are shown in Figure \ref{fig:modelB4_models}.
+\Wilma{[TO DO: Use $\text{km s}^{-1}$ instead of km/s]} \Wilma{[TO DO: More space between titles and upper axes tick labels.]}}
 \label{fig:modelB4_triangle}
@@
 NFW halo scale length & $r_s$ [kpc] & 40 & $\pm$ & 20\\
-NFW halo virial velocity & $v_{200}$ [km/s] & 240 & $\pm$ & 40\\
+NFW halo virial velocity & $v_{200}$ [$\text{km s}^{-1}$] & 240 & $\pm$ & 40\\
 NFW halo concentration & $c_{200}$ & 8 & $\pm$ & 2 \\
@@
 \emph{Panel b)} shows the circular velocity curve of the total mass (green), and separately the contribution of the stellar mass (yellow, again generated from the MGE in Table \ref{tab:MGEF814W}) and dark matter (grey).
-\Wilma{[TO DO: maybe make one separate circular velocity plot, that also contains the mass-follows-light with Einstein M/L vcirc and compares it with Aaron's vcirc curve.]} \emph{Panel c)} shows the corresponding enclosed mass profile.
+\Wilma{[TO DO: make one separate circular velocity plot, that also contains the mass-follows-light with Einstein M/L vcirc and compares it with Aaron's vcirc curve.
+Ask Aaron for data.]} \emph{Panel c)} shows the corresponding enclosed mass profile.
 Overplotted is also the Einstein mass at the Einstein radius with a 10\% error, which was used in the fit as an additional constraint.
-\Wilma{[TO DO: Replace arcsec with '']}}
+\Wilma{[TO DO: Replace arcsec with '']} \Wilma{[TO DO: Use $\text{km s}^{-1}$ instead of km/s]} \Wilma{[TO DO: Make two figures from this: vrms (shrinked horizontally) and encl Mass should be first and second panel of one figure, and circular velocity curve should be separate figure.
+]}}
 \label{fig:modelB4_models}
@@
 The best fit with $\kappa' = 0.76$ is shown in the second panel of Figure \ref{fig:modelB4_vrot}.
-The third panel gives the dispersion that was calculated simply by $\sigma = \sqrt{v_\text{rms}^2 - v_\text{rot}^2}$.
+Given in the first panel the best fit to $v_\text{rms}$, the third panel shows the dispersion that follows from $\sigma = \sqrt{v_\text{rms}^2 - v_\text{rot}^2}$.
 Our assumptions for $\kappa(R)$ nicely reproduce a $v_\text{rot}$ model with counter-rotating core.
@@
 While the dispersion $\sigma$ in the center fits by construction quite good, there is a huge discrepancy at large radii.
-The predicted dispersion is much larger than the data; we would expect the disk rotationally supported and therefore have a low velocity dispersion; especially dispersions as high as $\sim 200 km/s$ are more likely to be observed in the pressure supported bulges of galaxies.
+The predicted dispersion is much larger than the data; we would expect the disk rotationally supported and therefore have a low velocity dispersion; especially dispersions as high as $\sim 200~\text{km s}^{-1}$ are more likely to be observed in the pressure supported bulges of galaxies.
 There \emph{might} be something unexpeted with the $\sigma$ measurements around $\sim 5''$, but at large radii the the best fit model NFW halo is simply too massive.
@@
 At larger radii we compare the unsymmetrized data (open blue dots), the gas kinematics from \citet{SWELLSV} (green diamonds) and a JAM model using the same model parameters but the light distribution MGE generated from the Ellipse model in Figure \ref{fig:MGEouterRegions} as a prediction for the outer regions of J1331 (red dashed lines).
-The central regions are very well reproduced and we can also greatly predict the rotation curve at larger radii.
+The central regions are very well reproduced and we can also nicely predict the rotation curve at larger radii.
 Only at larger radii the $v_\text{rms}$ and $v_\text{rot}$ overestimate the measurements, probably due to a too massive NFW halo.
-\Wilma{[TO DO: Replace arcsec with '']}}
+\Wilma{[TO DO: Replace arcsec with '']} \Wilma{[TO DO: Use $\text{km s}^{-1}$ instead of km/s]}}
 \label{fig:modelB4_vrot}

### 2015-11-16 docs/results_JAMwithSB_v3.01.tex
More corrections; abstract is now 250 words long; edited introduction.

@@
   \caption{Comparison (not a fit!) of the symmetrized stellar $v_\text{rms}$ data of J1331 (blue dots) with JAM models generated from mass distributions which were independently derived from lensing constraints in Section \ref{sec:results_lensing}.
-The red solid line corresponds to the lens model for a flat rotation curve ($\alpha = 1$) in Table \ref{tab:bestfitlensmodel}; the green line is a best fit lens model found analogously from the image positions, but for a fixed rotation curve slope of $\alpha = 1.1$.
+\Wilma{[TO DO: Add Note that outside Rein extrapolation.]} The red solid line corresponds to the lens model for a flat rotation curve ($\alpha = 1$) in Table \ref{tab:bestfitlensmodel}; the green line is a best fit lens model found analogously from the image positions, but for a fixed rotation curve slope of $\alpha = 1.1$.
 For the JAM modelling a best fit MGE to the lens mass models were used, as well as the observed surface brightness MGE in Table \ref{tab:MGEF814W}, assuming velocity isotropy $\beta_z = 0$ and an inclination of $i = 70^\circ$.The red and black dotted lines are the Einstein radius and the effective half-light radius, respectively.
-\Wilma{[TO DO: Replace arcsec with '' in panel d)]}}
+\Wilma{[TO DO: Replace arcsec with '' in panel d)]} \Wilma{[TO DO: Use $\text{km s}^{-1}$ instead of km/s]}}
   \label{fig:JAM_modelL}
@@
 \paragraph{JAM with "mass-follows-light" and velocity anisotropy.} Our second JAM model is a mass-follows-light model, which are often used in dynamical JAM modelling (e.g.
-\citet{GlennEC,Cap06}), where the mass distribution ins generated by multiplying the intrinsic light distribution $\nu(R,z)$ (the MGE given in Table \ref{tab:MGEF814W} deprojected according to the inclination) by a constant total mass-to-light ratio  $\Upsilon_\text{I,tot}^\text{dyn}$.
-This assumes that the dark matter is always a constant fraction of the total matter distribution everywhere.
+\citet{GlennEC,Cap06}), where the mass distribution is generated by multiplying the intrinsic light distribution $\nu(R,z)$ (the MGE given in Table \ref{tab:MGEF814W} deprojected according to the inclination) by a constant total mass-to-light ratio  $\Upsilon_\text{I,tot}^\text{dyn}$.
+This assumes that the dark matter is always a constant fraction of the total matter distribution within the region covered by the kinematics.
 This simplified model sometimes gives good representations of the inner parts of galaxies, where the stellar component dominates.
@@
 around in-spiralling supermassive black holes \citep{1997NewA....2..533Q}) velocity anisotropies as low as $\sim -1$ have been found.
-A lower limit of $\beta_z \geq -0.5$ is a realistic assumption for J1331, for which we do not expect extreme dynamical conditions.
 The best fit in Figure \ref{fig:JAM_modelA2} however strives to very negative velocity anisotropies to be able to get the deep central dip in the  $v_\text{rms}$ curve.
@@
 This is obviously not a good model.
-\Wilma{[TO DO: Replace arcsec with '' in panel d)]}}
+\Wilma{[TO DO: Replace arcsec with '' in panel d)]} \Wilma{[TO DO: Use $\text{km s}^{-1}$ instead of km/s]}}
   \label{fig:JAM_modelA2}
@@
 We treat the five $\Upsilon_{\text{I,tot,}i}$ as free parameters and only require that $\Upsilon_{\text{I,tot,}j} \geq \Upsilon_{\text{I,tot,}i}$ when the corresponding $\sigma_j \geq \sigma_i$ to ensure an overall mass-to-light ratio that is increasing with radius.
-\\Figure \ref{fig:enclMass_modelG} shows the (local projected) mass-to-light ratio gradient generated by the best fit to the dynamics data, which rises from $\Upsilon_\text{I,tot} = 2.53$ in the center and approaches a value of $\Upsilon_\text{I,tot}$ outside of the fitted region at $R'\gtrsim 3''$ of $\Upsilon_\text{tot} = 7.60)$.
-The central mass-to-light ratio corresponds to the mass-to-light ratio found in Table \ref{tab:previousresults} based on the results of \citet{SWELLSI} assuming a stellar population with an \citet{Chabrier2003} initial mass-function (IMF, see also Section \ref{sec:MLdiscussion}), $\Upsilon_\text{I,*}^\text{chab} = 2.5 \pm 0.6$.
+
+Figure \ref{fig:enclMass_modelG} shows the (local projected) mass-to-light ratio gradient generated by the best fit to the dynamics data, which rises from $\Upsilon_\text{I,tot} = 2.53$ in the center and approaches a value of $\Upsilon_\text{I,tot}$ outside of the fitted region at $R'\gtrsim 3''$ of $\Upsilon_\text{tot} = 7.60$.
+The central mass-to-light ratio is in agreement with to the mass-to-light ratio $\Upsilon_\text{I,*}^\text{chab} = 2.5 \pm 0.6$, given in Table \ref{tab:previousresults} based on the results of \citet{SWELLSI} assuming a stellar population with an \citet{Chabrier2003} initial mass-function (IMF, see also Section \ref{sec:MLdiscussion}).
 When assuming that galaxy bulges are generally older and redder in the center \Wilma{[TO DO: REF]}, i.e.
 $\Upsilon_\text{I,*}$ is rather dropping with increasing radius than increasing, the strong rise of $\Upsilon_\text{I,tot}(R')$ might be due to a strong contribution of dark matter in J1331.
-\\Figure \ref{fig:JAM_modelG} shows that the best fit model greatly reproduces the central dip in the $v_\text{rms}$ curve, even though it has slight problems fitting the drop around $R' \sim 4''$.
+
+Figure \ref{fig:JAM_modelG} shows that the best fit model nicely reproduces the central dip in the $v_\text{rms}$ curve, even though it has slight problems fitting the drop around $R' \sim 4''$.
 The latter might be because we only allowed the $\Upsilon_\text{I,tot}(R')$ to rise.
 A slight drop could be expected when the reddish bulge turns into the bluish disk and the contribution of the stellar component becomes less due to a lower $\Upsilon_\text{I,*}$ for younger and bluer populations.
-\\In Figure \ref{fig:enclMass_modelG} we overplot the enclosed mass profile with the Einstein mass $M_\text{ein} = (7.77 \pm 0.33) \cdot 10^{10} M_\odot$ at the Einstein radius found from lensing in Table \ref{tab:bestfitlensmodel}.
+
+In Figure \ref{fig:enclMass_modelG} we overplot the enclosed mass profile with the Einstein mass $M_\text{ein} = (7.77 \pm 0.33) \cdot 10^{10} M_\odot$ at the Einstein radius found from lensing in Table \ref{tab:bestfitlensmodel}.
 The agreement between the Einstein mass and the independently found $M(<R_\text{ein}) = 7.49 \cdot 10^{10} M_\odot$ from dynamical modelling is striking.
@@
 \emph{Panel (a):} Comparison between the stellar $v_\text{rms}$ data (blue points) and the best fit model (green line).
-\emph{Panel (b):} Enclosed mass inside the projected radius $R'$ on the sky (green line, right axis) and projected mass-to-light profile $\Upsilon_\text{I,tot}(R')$ along the major axis (blue line, left axis) of the best fit model.
-The enclosed mass curve is overplotted with the independent finding for the Einstein mass $\pm 4 \%$ in Table \ref{tab:bestfitlensmodel} (red dot) at the Einstein radius (red dotted line).
+\emph{Panel (b):} Projected mass-to-light profile $\Upsilon_\text{I,tot}(R')$ along the major axis (blue line, left axis) of the best fit model.
 The best fit mass-to-light ratios of the first four Gaussians are plotted against each Gaussians $\sigma$ (yellow stars).
 The two Gaussians with the largest $\sigma$ (the fifth is not shown) have the same best fit mass-to-light ratio.
-Overplotted is also the effective half-light ratio $R_\text{eff}$ (black dotted line).
-\Wilma{[TO DO: Replace arcsec with '' in panel d)]}}
+Shown is also the enclosed mass inside the projected radius $R'$ on the sky (green line, right axis).
+The enclosed mass curve is overplotted with the independent finding for the Einstein mass $\pm 4 \%$ in Table \ref{tab:bestfitlensmodel} (red dot) at the Einstein radius (red dotted line).
+Shown is also the effective half-light ratio $R_\text{eff}$ (black dotted line).
+\Wilma{[TO DO: Replace arcsec with '' in panel d)]} \Wilma{[TO DO: Mention second axis only after 1st axis is explained.]} \Wilma{[TO DO: Use $\text{km s}^{-1}$ instead of km/s]}}
 \label{fig:modelG}

### 2015-11-16 docs/results_lensing_v3.01.tex
More corrections; abstract is now 250 words long; edited introduction.

@@
 We find slightly different positions for the peak of the surface brightness in the different filters and apply correspondingly an error of one diagonal pixel to the brightness peak in the F450W image which we use as center of the galaxy.
-\\Eight image position coordinates allow us to fit a lens mass model with only $<8$ free parameters. We therefore do not fit Fourier components $(a_k,b_k)$ with $k > 3$.
-\\Even though the constraints from the image positions on $\alpha$ is very weak, we were however able to show that the image positions in Table \ref{tab:lenspos} are consistent with a model with flat rotation curve.
+
+Eight image position coordinates allow us to fit a lens mass model with only $<8$ free parameters. We therefore do not fit Fourier components $(a_k,b_k)$ with $k > 3$.
+
+Even though the constraints from the image positions on $\alpha$ is very weak, we were however able to show that the image positions in Table \ref{tab:lenspos} are consistent with a model with flat rotation curve.
 In the following we therefore set $\alpha=1$.
@@
 This demonstrates that, although we did not include any information about the shape of the lensing images in the fit, it is consistent with the predicted distortion for an extended source by the best fit lens model.
-\\To estimate how the uncertainties in the determination of the image positions and galaxy center affect the results, we Monte Carlo sample random positions from a two-dimensional Normal distribution centered at the positions in Table \ref{tab:lenspos} and a standard deviation corresponding to the measurement error.
+
+To estimate how the uncertainties in the determination of the image positions and galaxy center affect the results, we Monte Carlo sample random positions from a two-dimensional Normal distribution centered at the positions in Table \ref{tab:lenspos} and a standard deviation corresponding to the measurement error.
 A Gaussian fit to the resulting distributions of best fit values leads to the constraints on the shape parameters and Einstein quantities in the second column in Table \ref{tab:bestfitlensmodel}.
@@
 The other two right blobs (north east of A, south east of B) might be star forming regions of the background galaxy as well.
-\Wilma{[TO DO: Add A, B, C, D in the figure to make clear which image is which.]}}
+\Wilma{[TO DO: Add A, B, C, D in the figure to make clear which image is which.]} \Wilma{[TO DO: Combine in one figure.
+Make all lines except time delay surface very thick.]}}
 \label{fig:???}
@@
 
-\paragraph{Comparison with light distribution.} The surface mass distribution as predicted by the best fit model in Table \ref{tab:bestfitlensmodel} is shown in Figure \ref{fig:lenscomparemass}.
+\paragraph{Comparison with light distribution.} The surface mass distribution as predicted by the best fit lens model in Table \ref{tab:bestfitlensmodel} is shown in Figure \ref{fig:lenscomparemass}.
 We introduced random noise according to the uncertainties in the Fourier shape parameters to create a mock observation that visualizes the effect of the measurement errors.
 From the mock image's second moment we find an average axis ratio for the lens mass model of $q_\text{lens} \simeq 0.695$, which is consistent with the one found by \citet{SWELLSIII}, $q_\text{lens,SWELLSIII} = 0.67 \pm 0.09$, while the light's average axis ratio in Table \ref{tab:galaxyparameters} is $q' = 0.598$.
-\\To estimate the total mass-to-light ratio within the Einstein radius $\Upsilon_\text{I,tot}^\text{ein} = M_\text{ein} / L_\text{I,ein}$, we first integrate the MGE in Table \ref{tab:MGEF814W} to get the total luminosity within the Einstein radius $L_\text{I,ein}$.
-$L_\text{I,ein}$ and $\Upsilon_\text{I,tot}^\text{ein}$ are given in Table \ref{tab:einsteinML}.
+
+To estimate the total mass-to-light ratio within the Einstein radius $\Upsilon_\text{I,tot}^\text{ein} = M_\text{ein} / L_\text{I,ein}$, we first integrate the MGE in Table \ref{tab:MGEF814W} to get the total luminosity within the Einstein radius $L_\text{I,ein}$.
+$L_\text{I,ein}$ and $\Upsilon_\text{I,tot}^\text{ein}$ are given in Table \ref{tab:einsteinML} \Wilma{[TO DO: Put in text, no separate table.]}.
 $\Upsilon_\text{I,tot}^\text{ein} \sim 5.6$ is consistent or slightly larger than the stellar mass-to-light ratio assuming a Salpeter Initial Mass Function $\Upsilon_\text{I,*}^\text{sal} = 4.7 \pm 1.2$ according to \citet{SWELLSI} and Table \ref{tab:previousresults} (see also discussion in Section \ref{sec:MLdiscussion}).
@@
 Figure \ref{fig:lenscompareboth} then compares equidensity contours at the same values of both the predicted lens mass distribution and the observed surface brightness times $\Upsilon_\text{I,tot}^\text{ein}$.
-\\Figure \ref{fig:lenslightcompareALL} leads to the following three findings: (1)The mass predicted from lensing and the observed light distribution are oriented in the same direction (i.e.
+
+Figure \ref{fig:lenslightcompareALL} leads to the following three findings: (1)The mass predicted from lensing and the observed light distribution are oriented in the same direction (i.e.
 have the same position angle).
 (2) Within and around the Einstein radius, mass and light distribution have a similar elliptical shape, while further out the mass distribution is slightly rounder.
-(3) The light distribution drops faster than the mass with increasing radius.
-Astrophysical reasons for the differences in observed light and measured mass distribution could be, e.g.
-an apparent change of shape due to dust extinction, a strongly changing $\Upsilon_\text{I,*}$, or the stellar component of the galaxy could be superimposed by a more roundish dark matter component.
-We have to note however that the mass distribution is only constraint around the Einstein radius and otherwise an extrapolation.
+(3) The light distribution drops faster than the mass with increasing radius (at least partly because of the assumption of a flat rotation curve).
+However, the mass distribution is only constraint around the Einstein radius and otherwise an extrapolation.
 
@@
 \caption{Total I-band (F814W) luminosity inside the Einstein radius $R_\text{ein}$, found from integrating the MGE in Table \ref{tab:MGEF814W} and corresponding total mass-to-light ratio $\Upsilon_\text{I,tot}^\text{ein}$ using the Einstein mass $M_\text{ein}$.
-$R_\text{ein}$ and $M_\text{ein}$ are given in Table \ref{tab:bestfitlensmodel}.}
+$R_\text{ein}$ and $M_\text{ein}$ are given in Table \ref{tab:bestfitlensmodel}.
+\Wilma{[TO DO: No separate table, put instead in text]}}
 \begin{tabular}{cc}

### 2015-11-16 docs/results_photometry_v3.01.tex
More corrections; abstract is now 250 words long; edited introduction.

@@
 The light model will also be the basis of the dynamical Jeans modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}.
-\\To derive J1331's surface brightness distribution, we use the HST image in the F814W (I-band) filter, shown in Figure \ref{fig:F814W}.
+
+To derive J1331's surface brightness distribution, we use the HST image in the F814W (I-band) filter, shown in Figure \ref{fig:F814W}.
 At longer wavelengths J1331's central old and smooth stellar component is more extended than in the F450W filter in Figure \ref{fig:F450W}, which is more sensitive to young clumpy star-forming regions.
@@
 \paragraph{Transformation into physical units.} To transform the MGE in units of counts into physical units, we apply a simplified version of the procedure described in \citet{Holtzman}.
-\\The scaling of the drizzled HST/WFC3 images is  $S = 0.05''/$pixel and the total exposure time $T = 1600$ sec.
+
+The scaling of the drizzled HST/WFC3 images is  $S = 0.05''/$pixel and the total exposure time $T = 1600$ sec.
 The total F814W luminosity in counts of each Gaussian of the MGE has a central surface brightness in counts per pixel of

### 2015-11-18 archive/v3/docs/data_v3.01.tex
Edited modelling section. Some figure corrections.

--- 2015-11-16 docs/data_v3.02.tex
@@
 Another reason to restrict to modelling on the bulge region is that our MGE in Table \ref{tab:MGEF814W} is only a good representation of J1331's F814W light distribution inside $\sim 5''$.
-
- \Wilma{[TO DO: Maybe mention the following details better in the data section....
-"SWELLS picked galaxies in SDSS whose spectra had two different redshifts within $3''$, which makes it likely to capture strong lenses with typical Einstein radii of $1''$.
-Sufficiently inclined galaxies were picked by eye.
-Follow-up high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) was performed to confirm their lensing status \citep{SWELLSI}."]}
-
- \Wilma{[TO DO: Include better in data section. "of approximate Hubble type Sb at right ascension = 202.91800$^\circ$ and a declination = 36.46999$^\circ$ (epoch J2000)"]}

### 2015-11-18 archive/v3/docs/introduction_v3.01.tex
Edited modelling section. Some figure corrections.

--- 2015-11-13 docs/introduction_v3.01.tex
@@
 The mass profile at larger galactocentric radii can be probed by gas rotation curves that directly measure the galaxy's circlar velocity profile \Wilma{[TO DO: REF]}.
-However, due to its dissipative nature, gas motions are very sensitive to disturbances by e.g.
-spiral arms and bars \Wilma{[TO DO: REF]}.
+However, due to its dissipative nature, gas motions are very sensitive to disturbances by, e.g., spiral arms and bars \Wilma{[TO DO: REF]}.
 
@@
 The galaxy's coordinates on the sky are right ascension $\alpha$ = 202.91800$^\circ$ and declination $\delta$ = 36.46999$^\circ$ (epoch J2000).
-Image orientation and scaling are indicated in panel (a); the scaling transformation from arcseconds to the physical size of the galaxy in kpc uses the galaxy's redshift $z_d = 0.113$ \citep{SWELLSIII} (i.e.
-assumes an angular diameter distance of 414 Mpc).
+Image orientation and scaling are indicated in panel (a); the scaling transformation from arcseconds to the physical size of the galaxy in kpc uses the galaxy's redshift $z_d = 0.113$ \citep{SWELLSIII} (i.e., assumes an angular diameter distance of 414 Mpc).
 The color scaling of these two images is the same.

### 2015-11-18 archive/v3/docs/model_MGE_v3.01.tex
Edited modelling section. Some figure corrections.

--- 2015-11-13 docs/model_MGE_v3.01.tex
@@
 
-\paragraph{Multi-Gaussian Expansion (MGE).} MGEs are used to parametrize the observed surface brightness or projected total mass of a galaxy as a sum of $N$ two-dimensional, elliptical Gaussians \citep{1991ApJ...366..599B,1992A&A...253..366M,1994A&A...285..723E,1999MNRAS.303..495E}.
+\paragraph{Multi-Gaussian Expansion (MGE).} MGEs are used to parametrize the observed surface brightness (or projected total mass) of a galaxy as a sum of $N$ two-dimensional, elliptical Gaussians \citep{1991ApJ...366..599B,1992A&A...253..366M,1994A&A...285..723E,1999MNRAS.303..495E}.
 This work makes use of the algorithm and code\footnote{The IDL code package for fitting MGEs to images by \citet{Cap02} is available online at \url{http://www-astro.physics.ox.ac.uk/~mxc/software}.
 The version from June 2012 was used in this work.} by \citet{Cap02}.
-We assume all Gaussians to have the same center and position angle $\phi$, i.e.
-orientation of the Gaussians' major axis measured counter-clockwise from the $y'$-axis of the coordinate system with polar coordinates $(R',\theta')$.
+We assume all Gaussians to have the same center and position angle $\phi$, i.e., the orientation of the Gaussians' major axis measured counter-clockwise from the $y'$-axis of the coordinate system with polar coordinates $(R',\theta')$.
 Then the surface brightness can be written as
@@
 where $I_{0,i}$ is the central surface brightness of each Gaussian, $L_i$ its total luminosity, $\sigma_i$ its dispersion along the major axis and $q'_i$ the axis ratio between the elliptical Gaussians major and minor axis.
-\\We can also expand the telescopes point-spread function (PSF) as a sum of circular Gaussians,
+
+We can also expand the telescopes point-spread function (PSF) as a sum of circular Gaussians,
 \begin{equation}

### 2015-11-18 docs/discussion_ML_v3.01.tex
Edited modelling section. Some figure corrections.

@@
 We found that such a model would be perfectly consistent with the lensing results and predict a total mass-to-light ratio in the center of J1331 of  $\Upsilon_\text{I,tot}(R'\sim0) = 2.53$.
-This is very close to the stellar mass-to-light ratio we got from \citet{SWELLSI} estimates of the bulge's stellar mass using the Chabrier IMF $\Upsilon_\text{I,*}^\text{Chabrier} = 2.5 \pm 0.6$, i.e.
-less bottom-heavy (more bluish) population.
+This is very close to the stellar mass-to-light ratio we got from \citet{SWELLSI} estimates of the bulge's stellar mass using the Chabrier IMF $\Upsilon_\text{I,*}^\text{Chabrier} = 2.5 \pm 0.6$, i.e., less bottom-heavy (more bluish) population.
 

### 2015-11-18 docs/discussion_merger_v3.01.tex
Edited modelling section. Some figure corrections.

@@
 Because of degeneracies between stellar and dark mass, and matter distribution and anisotropy profile, such a dynamical model would not lead to very tight constraints on the model parameters.
-A search for color gradients in J1331 and/or investigation of absorption line indices could support or contradict the suspicion of the existence of stellar mass-to-light ratio gradients in J133.
+A search for colour gradients in J1331 and/or investigation of absorption line indices could support or contradict the suspicion of the existence of stellar mass-to-light ratio gradients in J1331.
 Subsequently detailed stellar population analyses of the spectra taken along J1331's major axis should be conducted to constrain the mass-to-light ratio reliably.
@@
 High-resolution integral-field spectroscopy could help with this, allow for spatially resolved stellar population analysis and dynamical modelling in two dimensions.
-\Wilma{[TO DO: Include in this discussion that this could also help test, if the vrms dip is maybe because of twist, i.e.
-the measurements where not done along the major axis in the disk]} This would lead to much better understanding of J1331's structure and mass distribution and therefore answer questions on how minor mergers might modify spiral galaxies.
+\Wilma{[TO DO: Include in this discussion that this could also help test, if the vrms dip is maybe because of twist, i.e., the measurements where not done along the major axis in the disk]} This would lead to much better understanding of J1331's structure and mass distribution and therefore answer questions on how minor mergers might modify spiral galaxies.
 

### 2015-11-18 docs/introduction_v3.02.tex
Edited modelling section. Some figure corrections.

@@
 Cosmological simulations suggest that cold DM forms cuspy halos following a Navarro-Frenk-White (NFW) profile \citep{NFW96}.
-However, the existence of central DM density cusps in more massive galaxies depends strongly on the stellar mass-to-light ratio (e.g., \citealt{2011MNRAS.416..322D}), while DM dominated dwarf galaxies strongly favour cored DM halos (e.g., \citealt{1994Natur.370..629M,2001ApJ...552L..23D}).
+However, the existence of central DM density cusps in massive galaxies depends strongly on the stellar mass-to-light ratio (e.g., \citealt{2011MNRAS.416..322D}) and DM dominated dwarf galaxies even favour DM halos with cores (e.g., \citealt{1994Natur.370..629M,2001ApJ...552L..23D}).
 This discrepancy, known as the core-cusp problem, might be resolved by galaxy formation processes such as mergers and outflows (e.g., \citealt{2001ApJ...560..636E,2012MNRAS.421.3464P}).
@@
 The mass profile at larger galactocentric radii can be probed by gas rotation curves that directly measure the galaxy's circular velocity profile \Wilma{[TO DO: REF]}.
-However, due to its dissipative nature, gas motions are very sensitive to disturbances by e.g.
-spiral arms and bars \Wilma{[TO DO: REF]}.
+However, due to its dissipative nature, gas motions are very sensitive to disturbances by e.g., spiral arms and bars \Wilma{[TO DO: REF]}.
 
@@
 One of the SWELLS galaxies is the massive spiral SDSS J1331+3628, to which we refer as J1331 in the remainder of this work.
-It has bluish spiral arms and a large reddish bulge (see Figures \ref{fig:F450W} and \ref{fig:F814W}), which is superimposed by quadruplet of extended bluish images approximately at a distance of $1''$ from the galaxy center (see Figure \ref{fig:lens_just_imgpos}).
+It has bluish spiral arms and a large reddish bulge (see Figures \ref{fig:F450W} and \ref{fig:F814W}), which is superimposed by a quadruplet of extended bluish images approximately at a distance of $1''$ from the galaxy center (see Figure \ref{fig:lens_just_imgpos}).
 The lensed object might be a star-forming blob of a background galaxy.
@@
 We attempt to disentangle the stellar and DM components and test if employed axisymmetric Jeans models work also in the presence of a counter-rotating core.
-Ideally this work on J1331 could also help understanding how mergers modify the mass distribution of a galaxy.
+Ideally, this work on J1331 could also help understanding how mergers modify the mass distribution of a galaxy.
 
-This paper is organized as follows: Section \ref{sec:Modelling} gives an overview of the modelling techniques used in this work, Section \ref{sec:data} summarizes the data and Section \ref{sec:Results} presents our results on the surface photometry of J1331 using Multi-Gaussian expansions (Section \ref{sec:MGE_results}), constraints from lensing (Section \ref{sec:results_lensing}) and Jeans modelling based on the surface brightness only (Section \ref{sec:results_JAM_SB}) and including a NFW DM halo (Section \ref{sec:results_JAM_NFW}).
-Finally Section \ref{sec:Discussion} uses the result to discuss J1331's stellar mass-to-light ratio and possible merger history and starting points for future work.
+This paper is organized as follows: Section \ref{sec:data} summarizes the data, Section \ref{sec:Modelling} gives an overview of the modelling techniques used in this work, and Section \ref{sec:Results} presents our results on the surface photometry of J1331 using Multi-Gaussian expansions (Section \ref{sec:MGE_results}), constraints from lensing (Section \ref{sec:results_lensing}) and Jeans modelling based on the surface brightness only (Section \ref{sec:results_JAM_SB}) and including a NFW DM halo (Section \ref{sec:results_JAM_NFW}).
+Finally Section \ref{sec:Discussion} uses the result to discuss J1331's stellar mass-to-light ratio, possible merger history and starting points for future work.
 

### 2015-11-18 docs/model_JAM_v3.02.tex
Edited modelling section. Some figure corrections.

--- 2015-11-16 docs/model_JAM_v3.01.tex
@@
 
-\paragraph{Jeans Anisotropic Models (JAM).} JAM modelling assumes galaxies (a) to be collisionless, i.e.
-the collisionless Boltzmann equation for the distribution function $f(\vect{x},\vect{v},t)$ has to be satisfied ($\frac{\diff f(\vect{x},\vect{v},t}{\diff t} = 0$), (b) in a steady state ($\frac{\partial}{\partial t} = 0$), (c) axisymmetric (best described in cylindrical coordinates $(R,z,\phi)$ and $\frac{\partial}{\partial \phi} = 0$).
-From this follow the axisymmetric Jeans equations as the vector-valued first moment of the Boltzmann equation, i.e.
+\paragraph{Jeans Anisotropic Models (JAM).} JAM modelling assumes galaxies to be (a) collisionless (i.e., the collisionless Boltzmann equation for the distribution function $f(\vect{x},\vect{v},t)$ has to be satisfied, $\frac{\diff f(\vect{x},\vect{v},t)}{\diff t} = 0$), (b) in a steady state ($\frac{\partial}{\partial t} = 0$), (c) axisymmetric (best described in cylindrical coordinates $(R,z,\phi)$ and $\frac{\partial}{\partial \phi} = 0$).
+From this follow the axisymmetric Jeans equations as the vector-valued first moment of the Boltzmann equation, i.e.,
 \begin{equation*}
-\int \frac{\diff f}{\diff t} \Diff3 v = 0.
+\int \vect{v} \frac{\diff f}{\diff t} \Diff3 v = 0.
 \end{equation*}
@@
 We follow \citet{Cap08} and assume firstly, that the galaxy's velocity ellipsoid is aligned with the cylindrical coordinate system, i.e., $\langle v_R v_z\rangle = \langle v_z v_\phi \rangle = \langle v_\phi v_R \rangle = 0$.
-Secondly, we assume a constant ratio between the radial and vertical 2nd velocity moments,
+Secondly, we assume a constant ratio between the radial and vertical second velocity moments,
 \begin{equation}
@@
 \end{eqnarray}
-where $n(\vect{x}) = \int f(\vect{x},\vect{v}) \Diff3 v$ is the number density of tracers and $\Phi(\vect{x})$ the galaxy's gravitational potential, generated by the mass density $\rho(\vect{x})$ via Poisson's equation.
+where $n(\vect{x}) \equiv \int f(\vect{x},\vect{v}) \Diff3 v$ is the number density of (stellar) tracers and $\Phi(\vect{x})$ the galaxy's gravitational potential, generated by the mass density $\rho(\vect{x})$.
 
-The JAM modelling approach by \citet{Cap08} makes use of expressing the tracer density and the mass density as MGEs (see also \citet{1994A&A...285..723E}).
-The density of stellar tracers is assumed to be proportional to the observed and deprojected brightness distribution $\nu(R,z)$ in Equation \ref{eq:deprojMGE}.
-The mass density $\rho(R,z)$ can consist of several sets of MGEs, describing stellar and dark matter components.
-The gravitational potential is generated from the mass MGE by integrating the Poisson equation \citep{1994A&A...285..723E}.
-Equations \ref{eq:Jeans1} and \ref{eq:Jeans2} together with \ref{eq:bz} provide the velocity dispersion tensor $\langle v_i v_j \rangle = \langle v_i^2 \rangle$ (with $i,j \in \{ R,\phi, z\}$).
-It is then rotated by the inclination angle $i$ to the coordinate system of the observer ($(x',y')$ being the plane of the sky and $z'$ the line-of-sight, where $x'$ is alinged with the galaxy's major axis).
+The JAM modelling approach by \citet{Cap08} expresses the tracer and mass density in terms of MGEs (see also \citealt{1994A&A...285..723E}).
+The tracer density $n(\vect{x})$ is assumed to be proportional to the observed and deprojected brightness distribution $\nu(R,z)$ in Equation \eqref{eq:deprojMGE}.
+The mass density $\rho(R,z)$ can consist of several sets of MGEs, describing stellar and DM components.
+$\Phi(R,z)$ is generated from the mass density MGE by integrating the Poisson equation \citep{1994A&A...285..723E}.
+Equations \eqref{eq:Jeans1} and \eqref{eq:Jeans2} together with \eqref{eq:bz} provide the velocity dispersion tensor $\langle v_i v_j \rangle = \langle v_i^2 \rangle$ (with $i,j \in \{ R,\phi, z\}$).
+$\langle v_i^2 \rangle$ is then rotated by the inclination angle $i$ to the coordinate system of the observer; $(x',y')$ is the plane of the sky and $z'$ the line-of-sight, where $x'$ is alinged with the galaxy's major axis.
 Taking a light-weighted projection along the line-of-sight gives a model prediction for the line-of-sight velocity second moment, which is comparable to actual spectroscopic measurements of the second velocity moment.
@@
 \end{eqnarray*}
-The JAM modelling code by \citet{Cap08} evaluates numerically Equation \ref{eq:explicitLOSvelCap} for a given luminous tracer and mass distribution MGE and a given inclination.
+The JAM modelling code by \citet{Cap08} evaluates Equation \eqref{eq:explicitLOSvelCap} numerically for a given luminous tracer and mass distribution MGE and a given inclination.
 
@@
 \end{equation*}
-The model in Equation \ref{eq:explicitLOSvelCap} predicts the intrinsic $\langle v_\text{los}^2 \rangle$ at a given position on the sky, which have then to be modified according to the mode of observation, to be comparable to the measurements.
-The measured $v_\text{rms}$ is a light-weighted mean for a pixel along the long-slit of the spectrograph, with width $L_y = 1''$ \citep{SWELLSV} and a certain given extent along the galaxy's major axis, $L_x$, i.e.
-for a rectangular aperture
+The model in Equation \eqref{eq:explicitLOSvelCap} predicts the intrinsic $\langle v_\text{los}^2 \rangle$ at a given position on the sky, which needs then to be modified according to the mode of observation, to be comparable to the measurements.
+The measured $v_\text{rms}$ is a light-weighted mean for a pixel along the long-slit of the spectrograph, with width $L_y = 1''$ \citep{SWELLSV} and a certain given extent along the galaxy's major axis, $L_x$, i.e., for a rectangular aperture
 \begin{equation*}
-\text{AP}(x',y') = \left\{ \begin{array}{ll} 1 & \text{for } -\frac{L_x}{2} \leq x' \leq + \frac{L_x}{2}\\
+\text{AP}(x',y') \equiv \left\{ \begin{array}{ll} 1 & \text{for } -\frac{L_x}{2} \leq x' < + \frac{L_x}{2}\\
 & \text{and } - \frac{L_y}{2} \leq y' \leq + \frac{L_y}{2}  \\ 0 & \text{otherwise.} \end{array} \right.
 \end{equation*}
-The light arriving at the spectrograph itself was subject to seeing, i.e. a Gaussian with Full Width Half Maximum (FWHM) of $1.1''$ \citep{SWELLSV}
+The light arriving at the spectrograph itself was subject to seeing, i.e., a Gaussian with Full Width Half Maximum (FWHM) of $1.1''$ \citep{SWELLSV},
 \begin{equation*}
-\text{PSF}(x',y')=\mathscr{N}(0,\text{FWHM}/2\sqrt{2\ln2}).
+\text{PSF}(x',y')\equiv\mathscr{N}(0,\text{FWHM}/2\sqrt{2\ln2}).
 \end{equation*}
-The model predictions have therefore to be convolved with the convolution kernel
+The model predictions for $\langle v_\text{los}^2 \rangle$ have therefore to be convolved with the convolution kernel
 \begin{eqnarray*}
-K(x',y') &=& (\text{PSF} \ast \text{AP})(x',y') \\
-&=& \frac{1}{4} \prod_{u \in \{x',y'\}} \left[ \text{erf}\left( \frac{L_u/2 - u}{\sqrt{2}\sigma_\text{seeing}}\right) + \text{erf} \left( \frac{L_u/2 + u}{\sqrt{2} \sigma_\text{seeing}} \right) \right]
+K(x',y') &\equiv& (\text{PSF} \ast \text{AP})(x',y') \\
+&=& \frac{1}{4} \prod_{u \in \{x',y'\}} \left[ \text{erf}\left( \frac{L_u/2 - u}{\sqrt{2}\sigma_\text{seeing}}\right) + \text{erf} \left( \frac{L_u/2 + u}{\sqrt{2} \sigma_\text{seeing}} \right) \right],
 \end{eqnarray*}
-and weighted by the surface brightness $I(x',y')$
+and weighted by the surface brightness $I(x',y')$, i.e.,
 \begin{eqnarray*}
@@
 \paragraph{Rotation curve.} The intrinsic rotation curve is the first velocity moment $\langle v_\phi\rangle = \sqrt{\langle v_\phi^2 \rangle - \sigma_\phi^2}$.
-The observed rotation curve is the projection of the light-weighted contributions to $\langle v_\phi\rangle$ along the line-of-sight(\cite{Cap08}),
+The observed rotation curve is the projection of the light-weighted contributions to $\langle v_\phi\rangle$ along the line-of-sight \citep{Cap08},
 \begin{equation*}
@@
 Further assumptions are needed to separate the second velocity moments into ordered and random motion.
-\citet{Cap08} assumes that in a steady state there is no streaming velocity in $R$ direction, i.e.
-$\langle v_R \rangle = 0$ and therefore $\sigma_R^2 = \langle v_R^2 \rangle$.
+\citet{Cap08} assumes that in a steady state there is no streaming velocity in $R$ direction, i.e., $\langle v_R \rangle = 0$ and therefore $\sigma_R^2 = \langle v_R^2 \rangle$.
 Then \citet{Cap08} relates the dispersions in $R$ and $\phi$ direction such that
@@
 
-To model the counter-rotating core of J1331 with one free parameter, we employ the condition that the overall $\kappa(R)$ profile should smoothly and relatively steeply transition from $\kappa(R) = -\kappa' < 0$ at small $R$ through $\kappa(R_0) \equiv 0$ and increase to $\kappa(R) = \kappa' > 0$ at large $R$.
+To model the counter-rotating core of J1331 with one free parameter, we employ the condition that the overall $\kappa(R)$ profile should smoothly and relatively steeply transit from $\kappa(R) = -\kappa' < 0$ at small $R$ through $\kappa(R_0) = 0$ and increase to $\kappa(R) = \kappa' > 0$ at large $R$.
 Our imposed profile is
@@
 \end{equation}
-We find $\kappa'$ by matching the model $\langle v_\text{los} \rangle$ with the symmetrized $v_\text{rot}$ data, where for a given $\kappa'$ the $\kappa_k$ are found from fitting the MGE generated profile $\kappa(R) = \sum_k \kappa_k \nu_k(r)/\sum_k \nu_k(r)$ to Equation \ref{eq:kappa_profile}.
+We find $\kappa'$ by matching the model $\langle v_\text{los} \rangle$ with the symmetrized $v_\text{rot}$ data, where for a given $\kappa'$ the $\kappa_k$ are found from fitting the MGE generated profile $\kappa(R) = \sum_k \kappa_k \nu_k(r)/\sum_k \nu_k(r)$ to Equation \eqref{eq:kappa_profile}.
 The observed zero point is at $R'_0\approx 2''$.
@@
 \paragraph{Including a NFW halo.} As mentioned above, JAM modelling allows to incorporate an invisible matter component in addition to the luminous matter in the form of an MGE.
-In Section \ref{sec:results_JAM_NFW} we will include a spherical Navarro-Frenk-White (NFW) dark matter halo \citep{NFW96} in the dynamical model.
+In Section \ref{sec:results_JAM_NFW} we will include a spherical Navarro-Frenk-White (NFW) DM halo \citep{NFW96} in the dynamical model.
 The classical NFW profile has the form

### 2015-11-18 docs/model_lensing_v3.01.tex
Edited modelling section. Some figure corrections.

@@
 \paragraph{Lensing formalism.} A gravitational lens is a mass distribution, whose gravitational potential $\Phi$ acts as a lens for light coming from a source positioned somewhere on a plane behind the lens.
-The angular diameter distance from the observer to the lens is $D_d$, to the source plane it is $D_s$ and the distance between the lens and source plane is $D_{ds}$.
+The angular diameter distance from the observer to the lens is $D_d$, to the source plane $D_s$, and the distance between the lens and source plane is $D_{ds}$.
 The deflection potential of the lens is its potential, projected along the line of sight $z$ and rescaled to
@@
 \begin{equation}
-\Delta t(\vect{\theta}) = \frac{(1+z_d)}{c} \frac{D_d D_s}{D_{ds}} \left[ \frac 12 (\vect{\theta} - \vect{\beta})^2 - \psi(\vect{\theta})\right], \label{eq:timedelay}
+\Delta t(\vect{\theta}) = \frac{(1+z_d)}{c} \frac{D_d D_s}{D_{ds}} \left[ \frac 12 (\vect{\theta} - \vect{\beta})^2 - \psi(\vect{\theta})\right] \label{eq:timedelay}
 \end{equation}
@@
 $$\mu \equiv \frac{\text{image area}}{\text{source area}} = \det \mathscr{M}.$$
-Lines in the image plane for which the magnification becomes infinite, i.e.
-$\det \mathscr{M}^{-1} = 0$, are called \emph{critical curves}.
-The corresponding lines in the source plane are called \emph{caustics}.
+Lines in the image plane for which the magnification becomes infinite, i.e., $\det \mathscr{M}^{-1} = 0$, are called critical curves.
+The corresponding lines in the source plane are called caustics.
 The position of the source with respect to the caustic detemines the number of images and their configuration and shape with respect to each other.
 
-The \emph{Einstein mass} $M_\text{ein}$ and \emph{Einstein radius} $R_\text{ein}$ are defined via the relation
+The Einstein mass $M_\text{ein}$ and Einstein radius $R_\text{ein}$ are defined via the relation
 \begin{equation*}
@@
 \end{equation}
-For this scale-free lens model the lens equation (\ref{eq:lenseqpot}) becomes
+For this scale-free lens model the lens equation \eqref{eq:lenseqpot} becomes
 \begin{equation}
@@
 
-\paragraph{Model fitting.} As described above our lensing model has the following free parameters: the source position $(\xi,\eta)$, and the radial slope $\alpha$ and Fourier parameters $(a_k,b_k)$ of the lens mass distribution in Equations \ref{eq:scalefreemodel} and \ref{eq:Fourieransatz}.
-We want to find the lensing model which minimizes for all four images the distance between the observed image positions $\vect{\theta}_{oi}$ and those predicted by the lensing model $\vect{\theta}_{pi}$.
-Because we want to avoid solving the lens equation (see Equations \ref{eq:lenseqpot} and \ref{eq:Fourierlenseq}) for $\vect{\theta}_{pi}$, we follow \citet{1991ApJ...373..354K} and cast the calculation back to the source plane using the magnification tensor in Equation \ref{eq:magnificationtensor} to approximate $\vect{\theta} \simeq (\partial \vect{\theta} / \partial \vect{\beta}) \vect{\beta} = \mathscr{M} \vect{\beta} $ and the $\chi^2_\text{lens}$ that the fit wants to minimize becomes
+\paragraph{Model fitting.} The free parameters of the lens model are: the source position $(\xi,\eta)$, the radial slope $\alpha$ and Fourier parameters $(a_k,b_k)$ of the lens mass distribution in Equations \eqref{eq:scalefreemodel} and \eqref{eq:Fourieransatz}.
+We want to minimize the distance between the observed image positions, $\vect{\theta}_{oi}$, and those predicted by the lensing model, $\vect{\theta}_{pi}$.
+To avoid having to solve the lens equation \eqref{eq:Fourierlenseq} for $\vect{\theta}_{pi}$, we follow \citet{1991ApJ...373..354K} and cast the calculation back to the source plane using the magnification tensor in Equation \eqref{eq:magnificationtensor} to approximate $\vect{\theta} \simeq (\partial \vect{\theta} / \partial \vect{\beta}) \vect{\beta} = \mathscr{M} \vect{\beta} $.
+The best fit lens model is then the one that minimizes
 \begin{eqnarray*}
-\chi^2_\text{lens} &=& \sum_{i=1}^{4} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right) \left( \vect{\theta}_{pi} - \vect{\theta}_{oi} \right)\right|^2\\
-&\simeq& \sum_{i=1}^{N} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right)  \left.\mathscr{M}\right|_{\vect{\theta}=\vect{\theta}_{oi}} \left( \begin{matrix} \xi - \tilde{\xi}_i \\ \eta - \tilde{\eta}_i \end{matrix} \right) \right|^2,
+\chi^2_\text{lens} &=& \sum_{i} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right) \left( \vect{\theta}_{pi} - \vect{\theta}_{oi} \right)\right|^2\\
+&\simeq& \sum_{i} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right)  \left.\mathscr{M}\right|_{\vect{\theta}=\vect{\theta}_{oi}} \left( \begin{matrix} \xi - \tilde{\xi}_i \\ \eta - \tilde{\eta}_i \end{matrix} \right) \right|^2,
 \end{eqnarray*}
 where $(\Delta_x,\Delta_y)$ are the measurement errors of the image positions $\vect{\theta}_{oi}$.
-$\left.\mathscr{M}\right|_{\vect{\theta}=\vect{\theta}_{oi}}$ is the magnification tensor and $(\tilde{\xi}_i,\tilde{\eta}_i)$ the source position according to the lens equation, both evaluated at $\vect{\theta}_{oi}$.
+$\left.\mathscr{M}\right|_{\vect{\theta}=\vect{\theta}_{oi}}$ is the magnification tensor and $(\tilde{\xi}_i,\tilde{\eta}_i)$ the source position according to the lens equation, both evaluated at the position of the $i$-th lensing image, $\vect{\theta}_{oi}$.
 Following \citet{GlennEC} we add a term
@@
 
-To be able to constrain the slope $\alpha$, we would have needed flux ratios for the images as in \citet{GlennEC}.
-But the extended quality of the images, possible dust obscuration and surface brightness fluctuations due to microlensing events, as well as the uncertainty in surface brightness subtraction make flux determination too unreliable and we do not include them in the fitting.
+To be able to constrain the slope $\alpha$, we would need flux ratios for the images as in \citet{GlennEC}.
+But the extended quality of the images, possible dust obscuration and surface brightness fluctuations due to microlensing events, as well as the uncertainty in surface brightness subtraction, make flux determination too unreliable and we do not include them in the fitting.

### 2015-11-18 docs/results_JAMwithNFW_v3.01.tex
Edited modelling section. Some figure corrections.

@@
 We therefore proceed by modelling the mass distribution with a) a stellar component, which we get from the light MGE in Table \ref{tab:MGEF814W} (deprojected to the intrinsic $\nu(R,z)$) times a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$), and b) a spherical NFW dark matter component (see Section \ref{sec:model_JAM}) with free parameters halo scale length $r_s$ and circular velocity at the virial radius $v_{200}$.
-In the JAM modelling we use a 10-Gaussian MGE fit to the classical NFW profile in Equation \ref{eq:NFWprofile}.
+In the JAM modelling we use a 10-Gaussian MGE fit to the classical NFW profile in Equation \eqref{eq:NFWprofile}.
 
-\paragraph{Modelling and priors.} The full set of fit parameters is $(\Upsilon_\text{I,*},r_s,v_{200},\beta_z)$, where $\beta_z$ is the constant velocity anisotropy parameter (see Section \ref{sec:model_JAM}).
-We will investigate this parameter space with a MCMC\footnote{The Python code package for \emph{emcee}, a Monte Carlo Markov Chain implementation by \citet{emcee} is available online at \url{http://dan.iel.fm/emcee/current/}.
-The version from October 2013 was used in this work.} \citep{emcee} and use priors for the halo parameters to guide the fit to a realistic NFW halo shape.
-
-\citet{Dutton10} give a relation for halo vs.
-stellar mass for late-type galaxies.
-Using the stellar mass estimate for J1331 from \citet{SWELLSI} $m_* = (1.06 \pm 0.25) \cdot 10^{11} M_\odot$ for the Chabrier IMF estimate, we find ${v_{200}} = (202_{-33}^{+44})_{-13}^{+12}$.
-The first of the two quoted errors is due to the $2\sigma$ scatter in the relation by \citet{Dutton10}.
-The second error is the propagated error due to the uncertainty in the stellar mass.
-We use this as a rough estimate for the halo of J1331 and as Gaussian prior on $v_{200}$,
-\begin{equation*}
-p(v_{200}) = \mathscr{N}(200~\text{km s}^{-1},40~\text{km s}^{-1}).
-\end{equation*}
-\\We also use the concentration vs. halo mass relation by \citet{Maccio08} in Equation \ref{eq:Maccio08} as a prior on the concentration, i.e.
-\begin{equation*}
-p(\log c_{200} \mid v_{200}) = \mathscr{N}\left(\langle \log c_{200} \rangle (M_{200}) \mid 0.105 \right).
-\end{equation*}
-\\For the velocity anisotropy parameter $\beta$ we will again employ a uniform prior 
-\begin{equation*}
-p(\beta) = \mathscr{U}(-0.5,+0.5)
-\end{equation*}
-to exclude very unrealistic anisotropies. The full prior used is then
-\begin{eqnarray*}
-&&p(\Upsilon_\text{I,*},r_s,v_{200},\beta) \\
-&&= \frac{1}{\ln\left( 10 r_s\right)} p(\log c_{200} \mid v_{200}) \cdot p(v_{200}) \cdot p(\beta), 
-\end{eqnarray*}
-where the factor $1/\ln\left( 10 r_s\right)$ is the Jacobian of the transformation from the halo parameters $(v_{200},\log c_{200})$ to $(v_{200},r_s)$.
-\\We restrict the $v_\text{rms}$ fit to a region $R' \lesssim 3.5''$, approximately within the effective half-light radius $R_\text{eff} = 2.6''$.
-We also include the Einstein mass $M(<R_\text{ein})$ with a 10\% error as an additional constraint in the fit.
-
-\paragraph{Result.} Figure \ref{fig:modelB4_triangle} shows the posterior probability distribution of the fit sampled with an MCMC.
-Overplotted are also the priors used to constrain the NFW halo.
-The mean parameters are summarized in Table \ref{tab:modelB4_bestfit}.
-We find that the best fit NFW halo strives to be more massive and with a higher concentration (due to a smaller $r_s$) than  proposed by the prior.
-At the same time the model prefers again very negative velocity anisotropies: The sample with the highest probability is pegged at the lower limit of the unifrom prior.
-Both, the concentrated halo and the low anisotropy are needed to reproduce the central dip of the $v_\text{rms}$ curve.
-There are slight covariances between $\Upsilon_\text{I,*}$,  $r_s$ and $\beta_z$: The smaller the dark matter contribution in the center (i.e.
-the larger $\Upsilon_\text{I,*}$), the less concentrated is the halo (i.e.
-the larger $r_s$), the more velocity anisotropy is needed to reproduce the central dip.
-As the effect of $v_{200}$ is mostly at larger radii, this parameter doesn't show any covariances - but is also mostly constrained by the prior.
-\Wilma{[TO DO: Mention the following later in the text: "The $v_\text{rms}$ curve corresponding to the mean best fit values from Table \ref{tab:modelB4_bestfit} is shown in the first panel of Figure \ref{fig:modelB4_vrot}."]} Figure \ref{fig:modelB4_models} illustrates the range of parameters fitting the data according to the full posterior probability function.
-The model fits the $v_\text{rms}$ data in the inner regions quite well (Figure \ref{fig:modelB4_vrms}) and is also consistent with the Einstein mass (see Figure \ref{fig:modelB4_enclMass}).
-The extrapolation of the model to larger radii however overestimates the data, does not exhibit a drop around $\sim 6''$ at all and seems to be therefore overall too massive.\\
-
-We also fitted a model with a cored logarithmic dark matter halo.
-The cored halo models are in general slightly less massive than the NFW halo and therefore fit the outer regions of J1331 better.
-However, the density profile of the cored halo as well as the I-band light distribution within the plane drop as $\rho(r) \propto r^{-2}$, there is a strong degeneracy between the stellar mass and the dark matter.
-Overall, we were not able to obtain tight constraints on the cored logarithmic halo.
-
+%=======================
 \begin{figure*}
@@
 Shown are also the priors used for J1331's NFW halo, $\mathscr{N}(200~\text{km s}^{-1},40~\text{km s}^{-1})$ (green) and the concentration vs.
-halo mass relation by \citet{Maccio08} from Equation \ref{eq:Maccio08} in terms of $v_{200}$ vs.
+halo mass relation by \citet{Maccio08} from Equation \eqref{eq:Maccio08} in terms of $v_{200}$ vs.
 $r_s$ with $1\sigma$ scatter (blue).
@@
 \end{figure*}
+%=======================
 
+%==============
 \begin{table*}
@@
 \end{table*}
+%==============
 
+\paragraph{Modelling and priors.} The full set of fit parameters is $(\Upsilon_\text{I,*},r_s,v_{200},\beta_z)$, where $\beta_z$ is the constant velocity anisotropy parameter (see Section \ref{sec:model_JAM}).
+We will investigate this parameter space with a MCMC\footnote{The Python code package for \emph{emcee}, a Monte Carlo Markov Chain implementation by \citet{emcee} is available online at \url{http://dan.iel.fm/emcee/current/}.
+The version from October 2013 was used in this work.} \citep{emcee} and use priors for the halo parameters to guide the fit to a realistic NFW halo shape.
+
+\citet{Dutton10} give a relation for halo vs.
+stellar mass for late-type galaxies.
+Using the stellar mass estimate for J1331 from \citet{SWELLSI} $m_* = (1.06 \pm 0.25) \cdot 10^{11} M_\odot$ for the Chabrier IMF estimate, we find ${v_{200}} = (202_{-33}^{+44})_{-13}^{+12}$.
+The first of the two quoted errors is due to the $2\sigma$ scatter in the relation by \citet{Dutton10}.
+The second error is the propagated error due to the uncertainty in the stellar mass.
+We use this as a rough estimate for the halo of J1331 and as Gaussian prior on $v_{200}$,
+\begin{equation*}
+p(v_{200}) = \mathscr{N}(200~\text{km s}^{-1},40~\text{km s}^{-1}).
+\end{equation*}
+
+We also use the concentration vs. halo mass relation by \citet{Maccio08} in Equation \eqref{eq:Maccio08} as a prior on the concentration, i.e.
+\begin{equation*}
+p(\log c_{200} \mid v_{200}) = \mathscr{N}\left(\langle \log c_{200} \rangle (M_{200}) \mid 0.105 \right).
+\end{equation*}
+
+For the velocity anisotropy parameter $\beta$ we will again employ a uniform prior 
+\begin{equation*}
+p(\beta) = \mathscr{U}(-0.5,+0.5)
+\end{equation*}
+to exclude very unrealistic anisotropies. The full prior used is then
+\begin{eqnarray*}
+&&p(\Upsilon_\text{I,*},r_s,v_{200},\beta) \\
+&&= \frac{1}{\ln\left( 10 r_s\right)} p(\log c_{200} \mid v_{200}) \cdot p(v_{200}) \cdot p(\beta), 
+\end{eqnarray*}
+where the factor $1/\ln\left( 10 r_s\right)$ is the Jacobian of the transformation from the halo parameters $(v_{200},\log c_{200})$ to $(v_{200},r_s)$.
+
+%==============
 \begin{figure*}
 \centering
-\begin{subfigure}{\textwidth}
+\begin{subfigure}{.48\textwidth}
   \centering
-  \includegraphics[width=0.8\linewidth]{fig/B4_rms_error_curves.ps}
+  \includegraphics[width=0.9\linewidth]{fig/B4_rms_error_curves.ps}
   \caption{Comparison of the $v_\text{rms}$ data with the best fit JAM models.}
   \label{fig:modelB4_vrms}
-\end{subfigure}
-\begin{subfigure}{.48\textwidth}
-  \centering
-  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_vcirc.ps}
-  \caption{Circular velocity curve.}
-  \label{fig:modelB4_vcirc}
 \end{subfigure}%
@@
   \label{fig:modelB4_enclMass}
+\end{subfigure}
+\hspace{\textwidth}
+\begin{subfigure}{.48\textwidth}
+  \centering
+  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_vcirc.ps}
+  \caption{Circular velocity curve.}
+  \label{fig:modelB4_vcirc}
 \end{subfigure}
@@
 \end{figure*}
+%==============
+
+%==============
+\begin{figure*}
+\centering
+\includegraphics[width=0.7\linewidth]{fig/B4_rms_rot_curves_best_model.ps}
+\caption{Generating the rotation curve from the JAM model with NFW halo and constant velocity anisotropy with the mean parameters in Table \ref{tab:modelB4_bestfit} and with the best fit rotation parameter $\kappa' = 0.76$ in Equation \eqref{eq:kappa_profile} (red solid lines).
+The second velocity moment in the first panel and the first velocity moment in the second panel with the additional fit parameter $\kappa'$ were fitted to the symmetrized data (solid blue points).
+The velocity dispersion is simply $\sigma = \sqrt{v_\text{rms}^2 - v_\text{rot}^2}$.
+At larger radii we compare the unsymmetrized data (open blue dots), the gas kinematics from \citet{SWELLSV} (green diamonds) and a JAM model using the same model parameters but the light distribution MGE generated from the Ellipse model in Figure \ref{fig:MGEouterRegions} as a prediction for the outer regions of J1331 (red dashed lines).
+The central regions are very well reproduced and we can also nicely predict the rotation curve at larger radii.
+Only at larger radii the $v_\text{rms}$ and $v_\text{rot}$ overestimate the measurements, probably due to a too massive NFW halo.
+\Wilma{[TO DO: Replace arcsec with '']} \Wilma{[TO DO: Use $\text{km s}^{-1}$ instead of km/s]}}
+\label{fig:modelB4_vrot}
+\end{figure*}
+%==============
+
+We restrict the $v_\text{rms}$ fit to a region $R' \lesssim 3.5''$, approximately within the effective half-light radius $R_\text{eff} = 2.6''$.
+We also include the Einstein mass $M(<R_\text{ein})$ with a 10\% error as an additional constraint in the fit.
+
+\paragraph{Result.} Figure \ref{fig:modelB4_triangle} shows the posterior probability distribution of the fit sampled with an MCMC.
+Overplotted are also the priors used to constrain the NFW halo.
+The mean parameters are summarized in Table \ref{tab:modelB4_bestfit}.
+We find that the best fit NFW halo strives to be more massive and with a higher concentration (due to a smaller $r_s$) than  proposed by the prior.
+At the same time the model prefers again very negative velocity anisotropies: The sample with the highest probability is pegged at the lower limit of the unifrom prior.
+Both, the concentrated halo and the low anisotropy are needed to reproduce the central dip of the $v_\text{rms}$ curve.
+There are slight covariances between $\Upsilon_\text{I,*}$,  $r_s$ and $\beta_z$: The smaller the dark matter contribution in the center (i.e., the larger $\Upsilon_\text{I,*}$), the less concentrated is the halo (i.e., the larger $r_s$), the more velocity anisotropy is needed to reproduce the central dip.
+As the effect of $v_{200}$ is mostly at larger radii, this parameter doesn't show any covariances - but is also mostly constrained by the prior.
+\Wilma{[TO DO: Mention the following later in the text: "The $v_\text{rms}$ curve corresponding to the mean best fit values from Table \ref{tab:modelB4_bestfit} is shown in the first panel of Figure \ref{fig:modelB4_vrot}."]} Figure \ref{fig:modelB4_models} illustrates the range of parameters fitting the data according to the full posterior probability function.
+The model fits the $v_\text{rms}$ data in the inner regions quite well (Figure \ref{fig:modelB4_vrms}) and is also consistent with the Einstein mass (see Figure \ref{fig:modelB4_enclMass}).
+The extrapolation of the model to larger radii however overestimates the data, does not exhibit a drop around $\sim 6''$ at all and seems to be therefore overall too massive.\\
+
+We also fitted a model with a cored logarithmic dark matter halo.
+The cored halo models are in general slightly less massive than the NFW halo and therefore fit the outer regions of J1331 better.
+However, the density profile of the cored halo as well as the I-band light distribution within the plane drop as $\rho(r) \propto r^{-2}$, there is a strong degeneracy between the stellar mass and the dark matter.
+Overall, we were not able to obtain tight constraints on the cored logarithmic halo.
 
@@
 There \emph{might} be something unexpeted with the $\sigma$ measurements around $\sim 5''$, but at large radii the the best fit model NFW halo is simply too massive.
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.7\linewidth]{fig/B4_rms_rot_curves_best_model.ps}
-\caption{Generating the rotation curve from the JAM model with NFW halo and constant velocity anisotropy with the mean parameters in Table \ref{tab:modelB4_bestfit} and with the best fit rotation parameter $\kappa' = 0.76$ in Equation \ref{eq:kappa_profile} (red solid lines).
-The second velocity moment in the first panel and the first velocity moment in the second panel with the additional fit parameter $\kappa'$ were fitted to the symmetrized data (solid blue points).
-The velocity dispersion is simply $\sigma = \sqrt{v_\text{rms}^2 - v_\text{rot}^2}$.
-At larger radii we compare the unsymmetrized data (open blue dots), the gas kinematics from \citet{SWELLSV} (green diamonds) and a JAM model using the same model parameters but the light distribution MGE generated from the Ellipse model in Figure \ref{fig:MGEouterRegions} as a prediction for the outer regions of J1331 (red dashed lines).
-The central regions are very well reproduced and we can also nicely predict the rotation curve at larger radii.
-Only at larger radii the $v_\text{rms}$ and $v_\text{rot}$ overestimate the measurements, probably due to a too massive NFW halo.
-\Wilma{[TO DO: Replace arcsec with '']} \Wilma{[TO DO: Use $\text{km s}^{-1}$ instead of km/s]}}
-\label{fig:modelB4_vrot}
-\end{figure*}

### 2015-11-18 docs/results_JAMwithSB_v3.01.tex
Edited modelling section. Some figure corrections.

@@
 The predictions are compared with the data in Figure \ref{fig:JAM_modelL}.
-The agreement between the lensing prediction and the observed kinematics within $R' \sim 3''$ is striking, especially around the Einstein radius.
-The $\alpha = 1$ model fits the wings nicely, while the $\alpha = 1.1$ model recreates almost exactly the observed central dip.
-The sharp drop in $v_\text{rms}$ around $R' \sim 3''$ cannot be reproduced, however.
-But outside of the Einstein radius our lensing models are only extrapolations and the true constraint is around the Einstein radius.
+The agreement between the lensing prediction and the observed kinematics within $R' \sim 3''$ is striking.
+The $\alpha = 1$ model fits the wings around $R_\text{eff}$, while the $\alpha > 1$ model recreates the observed central dip.
+This is in concordance with observations in other galaxies, where also $\alpha<1$ at large radii.
+Our lensing model assumes $\alpha(R')=\text{const}$, although these results suggest, that a model with variable $\alpha(R')$ might fit even better, and maybe also reproduce the sharp drop in $v_\text{rms}$ around $R' \sim 3''$.
+We note however, that the most reliable constraint is around $R_\text{ein}$.
+Outside of $R_\text{ein}$ lensing models are only extrapolations.
 
@@
 
-\paragraph{JAM with "mass-follows-light" and velocity anisotropy.} Our second JAM model is a mass-follows-light model, which are often used in dynamical JAM modelling (e.g.
-\citet{GlennEC,Cap06}), where the mass distribution is generated by multiplying the intrinsic light distribution $\nu(R,z)$ (the MGE given in Table \ref{tab:MGEF814W} deprojected according to the inclination) by a constant total mass-to-light ratio  $\Upsilon_\text{I,tot}^\text{dyn}$.
-This assumes that the dark matter is always a constant fraction of the total matter distribution within the region covered by the kinematics.
-This simplified model sometimes gives good representations of the inner parts of galaxies, where the stellar component dominates.
-Testing this model for J1331 is also motivated by our findings from lensing in Section \ref{sec:results_lensing}, where around the Einstein radius total and luminous mass seem to have a similar distribution.
-\\In addition to the free fit parameter  $\Upsilon_\text{I,tot}^\text{dyn}$, we also allow for a overall constant but non-zero velocity anisotropy $\beta_z$.
-The best fit is found by minimizing $\chi^2$ between the $v_\text{rms}$ data and model prediction and is demonstrated in Figure \ref{fig:JAM_modelA2}.
-For $\beta_z$ we impose the fitting limits $\beta_z \in [-0.5,+0.5]$.
-While the outer parts of galaxies often show radially biased velocity anisotropy up to $\sim 0.5$ (from dynamical modelling of observed elliptical galaxies (e.g.
-\citet{Kronawitter2000}) and cosmological simulations (e.g.
-\citet{2004MNRAS.352..535D,2001ApJ...557..533F}), the centers of galaxies are near-isotropic or have  negative velocity anisotropy \citep{2003ApJ...583...92G}.
-Only in extreme models (e.g.
-around in-spiralling supermassive black holes \citep{1997NewA....2..533Q}) velocity anisotropies as low as $\sim -1$ have been found.
-The best fit in Figure \ref{fig:JAM_modelA2} however strives to very negative velocity anisotropies to be able to get the deep central dip in the  $v_\text{rms}$ curve.
-But $\beta_z = -0.5$ is not even a remotely agreeable fit and lower anisotropies are not to be expected and realistic.
-We also tested radial profiles for $\beta_z(R)$ of the form proposed by \citet{BaesVanHese}, which was however equally unable to reproduce the data.
-We conclude, that this is due to the well-known degeneracy between anisotropy and mass profile \Wilma{[TO DO: REF]} and the mass-follows-light model is \emph{not} a good representation of the mass distribution in J1331's inner regions.
-
 %==================================================================
@@
 
+\paragraph{JAM with "mass-follows-light" and velocity anisotropy.} Our second JAM model is a mass-follows-light model, which are often used in dynamical JAM modelling (e.g., \citet{GlennEC,Cap06}), where the mass distribution is generated by multiplying the intrinsic light distribution $\nu(R,z)$ (the MGE given in Table \ref{tab:MGEF814W} deprojected according to the inclination) by a constant total mass-to-light ratio  $\Upsilon_\text{I,tot}^\text{dyn}$.
+This assumes that the dark matter is always a constant fraction of the total matter distribution within the region covered by the kinematics.
+This simplified model sometimes gives good representations of the inner parts of galaxies, where the stellar component dominates.
+Testing this model for J1331 is also motivated by our findings from lensing in Section \ref{sec:results_lensing}, where around the Einstein radius total and luminous mass seem to have a similar distribution.
+\\In addition to the free fit parameter  $\Upsilon_\text{I,tot}^\text{dyn}$, we also allow for a overall constant but non-zero velocity anisotropy $\beta_z$.
+The best fit is found by minimizing $\chi^2$ between the $v_\text{rms}$ data and model prediction and is demonstrated in Figure \ref{fig:JAM_modelA2}.
+For $\beta_z$ we impose the fitting limits $\beta_z \in [-0.5,+0.5]$.
+While the outer parts of galaxies often show radially biased velocity anisotropy up to $\sim 0.5$ (from dynamical modelling of observed elliptical galaxies (e.g., \citet{Kronawitter2000}) and cosmological simulations (e.g., \citet{2004MNRAS.352..535D,2001ApJ...557..533F}), the centers of galaxies are near-isotropic or have  negative velocity anisotropy \citep{2003ApJ...583...92G}.
+Only in extreme models (e.g., around in-spiralling supermassive black holes \citep{1997NewA....2..533Q}) velocity anisotropies as low as $\sim -1$ have been found.
+The best fit in Figure \ref{fig:JAM_modelA2} however strives to very negative velocity anisotropies to be able to get the deep central dip in the  $v_\text{rms}$ curve.
+But $\beta_z = -0.5$ is not even a remotely agreeable fit and lower anisotropies are not to be expected and realistic.
+We also tested radial profiles for $\beta_z(R)$ of the form proposed by \citet{BaesVanHese}, which was however equally unable to reproduce the data.
+We conclude, that this is due to the well-known degeneracy between anisotropy and mass profile \Wilma{[TO DO: REF]} and the mass-follows-light model is \emph{not} a good representation of the mass distribution in J1331's inner regions.
+
 \paragraph{JAM with increasing mass-to-light ratio.} In Section \ref{sec:results_lensing} we found from the lensing, that the light distribution might drop faster with radius than the mass distribution.
@@
 As velocity anisotropy alone cannot explain the observed kinematics in a simple a mass-follows-light model, we now allow for an mass-to-light ratio gradient in the JAM modelling to generate a mass model from the light distribution in Table \ref{tab:MGEF814W}.
-We do this by assigning each of the five Gaussians in the MGE its own total mass-to-light ratio $\Upsilon_{\text{I,tot,}i}$ and replace the total luminosity in Equation \ref{eq:centralItotalL} $L_i$ with the Gaussians total Mass $M_i = \Upsilon_{\text{I,tot,}i} L_i$.
+We do this by assigning each of the five Gaussians in the MGE its own total mass-to-light ratio $\Upsilon_{\text{I,tot,}i}$ and replace the total luminosity in Equation \eqref{eq:centralItotalL} $L_i$ with the Gaussians total Mass $M_i = \Upsilon_{\text{I,tot,}i} L_i$.
 We treat the five $\Upsilon_{\text{I,tot,}i}$ as free parameters and only require that $\Upsilon_{\text{I,tot,}j} \geq \Upsilon_{\text{I,tot,}i}$ when the corresponding $\sigma_j \geq \sigma_i$ to ensure an overall mass-to-light ratio that is increasing with radius.
-
-Figure \ref{fig:enclMass_modelG} shows the (local projected) mass-to-light ratio gradient generated by the best fit to the dynamics data, which rises from $\Upsilon_\text{I,tot} = 2.53$ in the center and approaches a value of $\Upsilon_\text{I,tot}$ outside of the fitted region at $R'\gtrsim 3''$ of $\Upsilon_\text{tot} = 7.60$.
-The central mass-to-light ratio is in agreement with to the mass-to-light ratio $\Upsilon_\text{I,*}^\text{chab} = 2.5 \pm 0.6$, given in Table \ref{tab:previousresults} based on the results of \citet{SWELLSI} assuming a stellar population with an \citet{Chabrier2003} initial mass-function (IMF, see also Section \ref{sec:MLdiscussion}).
-When assuming that galaxy bulges are generally older and redder in the center \Wilma{[TO DO: REF]}, i.e.
-$\Upsilon_\text{I,*}$ is rather dropping with increasing radius than increasing, the strong rise of $\Upsilon_\text{I,tot}(R')$ might be due to a strong contribution of dark matter in J1331.
-
-Figure \ref{fig:JAM_modelG} shows that the best fit model nicely reproduces the central dip in the $v_\text{rms}$ curve, even though it has slight problems fitting the drop around $R' \sim 4''$.
-The latter might be because we only allowed the $\Upsilon_\text{I,tot}(R')$ to rise.
-A slight drop could be expected when the reddish bulge turns into the bluish disk and the contribution of the stellar component becomes less due to a lower $\Upsilon_\text{I,*}$ for younger and bluer populations.
-
-In Figure \ref{fig:enclMass_modelG} we overplot the enclosed mass profile with the Einstein mass $M_\text{ein} = (7.77 \pm 0.33) \cdot 10^{10} M_\odot$ at the Einstein radius found from lensing in Table \ref{tab:bestfitlensmodel}.
-The agreement between the Einstein mass and the independently found $M(<R_\text{ein}) = 7.49 \cdot 10^{10} M_\odot$ from dynamical modelling is striking.
 
@@
 %==================================================================
+
+Figure \ref{fig:enclMass_modelG} shows the (local projected) mass-to-light ratio gradient generated by the best fit to the dynamics data, which rises from $\Upsilon_\text{I,tot} = 2.53$ in the center and approaches a value of $\Upsilon_\text{I,tot}$ outside of the fitted region at $R'\gtrsim 3''$ of $\Upsilon_\text{tot} = 7.60$.
+The central mass-to-light ratio is in agreement with to the mass-to-light ratio $\Upsilon_\text{I,*}^\text{chab} = 2.5 \pm 0.6$, given in Table \ref{tab:previousresults} based on the results of \citet{SWELLSI} assuming a stellar population with an \citet{Chabrier2003} initial mass-function (IMF, see also Section \ref{sec:MLdiscussion}).
+When assuming that galaxy bulges are generally older and redder in the center \Wilma{[TO DO: REF]}, i.e., $\Upsilon_\text{I,*}$ is rather dropping with increasing radius than increasing, the strong rise of $\Upsilon_\text{I,tot}(R')$ might be due to a strong contribution of dark matter in J1331.
+
+Figure \ref{fig:JAM_modelG} shows that the best fit model nicely reproduces the central dip in the $v_\text{rms}$ curve, even though it has slight problems fitting the drop around $R' \sim 4''$.
+The latter might be because we only allowed the $\Upsilon_\text{I,tot}(R')$ to rise.
+A slight drop could be expected when the reddish bulge turns into the bluish disk and the contribution of the stellar component becomes less due to a lower $\Upsilon_\text{I,*}$ for younger and bluer populations.
+
+In Figure \ref{fig:enclMass_modelG} we overplot the enclosed mass profile with the Einstein mass $M_\text{ein} = (7.77 \pm 0.33) \cdot 10^{10} M_\odot$ at the Einstein radius found from lensing in Table \ref{tab:bestfitlensmodel}.
+The agreement between the Einstein mass and the independently found $M(<R_\text{ein}) = 7.49 \cdot 10^{10} M_\odot$ from dynamical modelling is striking.

### 2015-11-18 docs/results_lensing_v3.01.tex
Edited modelling section. Some figure corrections.

@@
 This demonstrates that, although we did not include any information about the shape of the lensing images in the fit, it is consistent with the predicted distortion for an extended source by the best fit lens model.
-
-To estimate how the uncertainties in the determination of the image positions and galaxy center affect the results, we Monte Carlo sample random positions from a two-dimensional Normal distribution centered at the positions in Table \ref{tab:lenspos} and a standard deviation corresponding to the measurement error.
-A Gaussian fit to the resulting distributions of best fit values leads to the constraints on the shape parameters and Einstein quantities in the second column in Table \ref{tab:bestfitlensmodel}.
-We therefore constrain the Einstein radius to within 2\%, $R_\text{ein} = (0.91 \pm 0.02)''$ and the projected mass within the critical curve with a relative error of 4\%, $M_\text{crit} =(7.9\pm0.3)\cdot 10^{10} M_\odot$.
-Our measurement of $R_\text{ein}$ is consistent with that from \citet{SWELLSIII}, $R_\text{ein,SWELLS} = (0.96 \pm 0.04)''$ (which used a singular isothermal ellipsoid as lens mass model and the intermediate-axis convention of the critical curve as the Einstein radius).
-The relative difference between our critical mass and that of \citet{SWELLSIII}, $M_\text{crit,SWELLS} =(8.86\pm0.61)\cdot 10^{10} M_\odot$, is 13\%.
 
@@
 For $\alpha=1$ (which we assumed for our lens model) the critical curve is a contour of constant surface density of the mass model.
-\emph{Panel (b)} The yellow lines show (arbitrary) contours of the time delay surface given by Equation \ref{eq:timedelay} of the best fit lens model.
+\emph{Panel (b)} The yellow lines show (arbitrary) contours of the time delay surface given by Equation \eqref{eq:timedelay} of the best fit lens model.
 Not only the position of the extrema, but also their shape is consistent with the observed, extended images, even though we did not use information about the image shape in the analysis.
@@
 
-\paragraph{Comparison with light distribution.} The surface mass distribution as predicted by the best fit lens model in Table \ref{tab:bestfitlensmodel} is shown in Figure \ref{fig:lenscomparemass}.
-We introduced random noise according to the uncertainties in the Fourier shape parameters to create a mock observation that visualizes the effect of the measurement errors.
-From the mock image's second moment we find an average axis ratio for the lens mass model of $q_\text{lens} \simeq 0.695$, which is consistent with the one found by \citet{SWELLSIII}, $q_\text{lens,SWELLSIII} = 0.67 \pm 0.09$, while the light's average axis ratio in Table \ref{tab:galaxyparameters} is $q' = 0.598$.
-
-To estimate the total mass-to-light ratio within the Einstein radius $\Upsilon_\text{I,tot}^\text{ein} = M_\text{ein} / L_\text{I,ein}$, we first integrate the MGE in Table \ref{tab:MGEF814W} to get the total luminosity within the Einstein radius $L_\text{I,ein}$.
-$L_\text{I,ein}$ and $\Upsilon_\text{I,tot}^\text{ein}$ are given in Table \ref{tab:einsteinML} \Wilma{[TO DO: Put in text, no separate table.]}.
-$\Upsilon_\text{I,tot}^\text{ein} \sim 5.6$ is consistent or slightly larger than the stellar mass-to-light ratio assuming a Salpeter Initial Mass Function $\Upsilon_\text{I,*}^\text{sal} = 4.7 \pm 1.2$ according to \citet{SWELLSI} and Table \ref{tab:previousresults} (see also discussion in Section \ref{sec:MLdiscussion}).
-We use $\Upsilon_\text{I,tot}^\text{ein}$ to transform the observed surface brightness in the F814W filter into a surface mass density to compare it to the lensing mass distribution (Figure \ref{fig:lenscomparelight}).
-Figure \ref{fig:lenscompareboth} then compares equidensity contours at the same values of both the predicted lens mass distribution and the observed surface brightness times $\Upsilon_\text{I,tot}^\text{ein}$.
-
-Figure \ref{fig:lenslightcompareALL} leads to the following three findings: (1)The mass predicted from lensing and the observed light distribution are oriented in the same direction (i.e.
-have the same position angle).
-(2) Within and around the Einstein radius, mass and light distribution have a similar elliptical shape, while further out the mass distribution is slightly rounder.
-(3) The light distribution drops faster than the mass with increasing radius (at least partly because of the assumption of a flat rotation curve).
-However, the mass distribution is only constraint around the Einstein radius and otherwise an extrapolation.
+To estimate how the uncertainties in the determination of the image positions and galaxy center affect the results, we Monte Carlo sample random positions from a two-dimensional Normal distribution centered at the positions in Table \ref{tab:lenspos} and a standard deviation corresponding to the measurement error.
+A Gaussian fit to the resulting distributions of best fit values leads to the constraints on the shape parameters and Einstein quantities in the second column in Table \ref{tab:bestfitlensmodel}.
+We therefore constrain the Einstein radius to within 2\%, $R_\text{ein} = (0.91 \pm 0.02)''$ and the projected mass within the critical curve with a relative error of 4\%, $M_\text{crit} =(7.9\pm0.3)\cdot 10^{10} M_\odot$.
+Our measurement of $R_\text{ein}$ is consistent with that from \citet{SWELLSIII}, $R_\text{ein,SWELLS} = (0.96 \pm 0.04)''$ (which used a singular isothermal ellipsoid as lens mass model and the intermediate-axis convention of the critical curve as the Einstein radius).
+The relative difference between our critical mass and that of \citet{SWELLSIII}, $M_\text{crit,SWELLS} =(8.86\pm0.61)\cdot 10^{10} M_\odot$, is 13\%.
 
@@
 \end{figure*}
+
+%========================================================================================
+
+\paragraph{Comparison with light distribution.} The surface mass distribution as predicted by the best fit lens model in Table \ref{tab:bestfitlensmodel} is shown in Figure \ref{fig:lenscomparemass}.
+We introduced random noise according to the uncertainties in the Fourier shape parameters to create a mock observation that visualizes the effect of the measurement errors.
+From the mock image's second moment we find an average axis ratio for the lens mass model of $q_\text{lens} \simeq 0.695$, which is consistent with the one found by \citet{SWELLSIII}, $q_\text{lens,SWELLSIII} = 0.67 \pm 0.09$, while the light's average axis ratio in Table \ref{tab:galaxyparameters} is $q' = 0.598$.
+
+To estimate the total mass-to-light ratio within the Einstein radius $\Upsilon_\text{I,tot}^\text{ein} = M_\text{ein} / L_\text{I,ein}$, we first integrate the MGE in Table \ref{tab:MGEF814W} to get the total luminosity within the Einstein radius $L_\text{I,ein}$.
+$L_\text{I,ein}$ and $\Upsilon_\text{I,tot}^\text{ein}$ are given in Table \ref{tab:einsteinML} \Wilma{[TO DO: Put in text, no separate table.]}.
+$\Upsilon_\text{I,tot}^\text{ein} \sim 5.6$ is consistent or slightly larger than the stellar mass-to-light ratio assuming a Salpeter Initial Mass Function $\Upsilon_\text{I,*}^\text{sal} = 4.7 \pm 1.2$ according to \citet{SWELLSI} and Table \ref{tab:previousresults} (see also discussion in Section \ref{sec:MLdiscussion}).
+We use $\Upsilon_\text{I,tot}^\text{ein}$ to transform the observed surface brightness in the F814W filter into a surface mass density to compare it to the lensing mass distribution (Figure \ref{fig:lenscomparelight}).
+Figure \ref{fig:lenscompareboth} then compares equidensity contours at the same values of both the predicted lens mass distribution and the observed surface brightness times $\Upsilon_\text{I,tot}^\text{ein}$.
+
+Figure \ref{fig:lenslightcompareALL} leads to the following three findings: (1)The mass predicted from lensing and the observed light distribution are oriented in the same direction (i.e., have the same position angle).
+(2) Within and around the Einstein radius, mass and light distribution have a similar elliptical shape, while further out the mass distribution is slightly rounder.
+(3) The light distribution drops faster than the mass with increasing radius (at least partly because of the assumption of a flat rotation curve).
+However, the mass distribution is only constraint around the Einstein radius and otherwise an extrapolation.

### 2015-11-20 LensingPaper_draft_v3.01.tex
Edited modelling section. Some figure corrections.
Started editing the results section.

@@
 %Introduction
-\input{docs/introduction_v3.02} %[Fast fertig ueberarbeitet - fehlen noch 2 referenzen.]
+\input{docs/introduction_v3.02} %[Fertig gekuerzt. Es fehlen noch 2 Referenzen.]
 %--------------------------------------------
@@
 %------------------------
-\section{Modelling} \label{sec:Modelling}
-\input{docs/model_MGE_v3.01}
-\input{docs/model_lensing_v3.01}
-\input{docs/model_JAM_v3.01}
+\input{docs/data_v3.02} %[Not done yet]
 %------------------------
@@
 %------------------------
-\input{docs/data_v3.02}
+\section{Modelling} \label{sec:Modelling}
+\input{docs/model_MGE_v3.02} %[Fertig]
+\input{docs/model_lensing_v3.01} %[Fertig]
+\input{docs/model_JAM_v3.02} %[Fertig - wenn auch nicht so toll.]
 %------------------------
@@
 \section{Results} \label{sec:Results}
-\input{docs/results_photometry_v3.01}
-\input{docs/results_lensing_v3.01}
+\input{docs/results_photometry_v3.02} %[Text bin ich durchgegangen. Allerdings muessen Captions noch ueberarbeitet werden.]
+\input{docs/results_lensing_v3.01} %[Text bin ich durchgegangen. Allerdings muessen Captions noch ueberarbeitet werden.]
 \input{docs/results_JAMwithSB_v3.01}

### 2015-11-20 archive/v3/docs/results_photometry_v3.01.tex
Started editing the results section.

--- 2015-11-16 docs/results_photometry_v3.01.tex
@@
 
+%============================================================================
+\begin{table}
+\centering
+\caption{F814W PSF MGE: Parameters of the circular four-Gaussian MGE in Equation \eqref{eq:PSFgeneral} fitted to the radial profile of the synthetic HST/F814W PSF image by \Wilma{[TO DO: WHO???]}.}
+\begin{tabular}{ccc}
+\hline
+$k$ & $G_k$ & $\delta_k$ [$''$] \\\hline
+1 & 0.184 & 0.038\\
+2 & 0.485 & 0.085\\
+3 & 0.222 & 0.169\\
+4 & 0.109 & 0.487\\\hline
+\end{tabular}
+\label{tab:PSFMGEF814W}
+\end{table}
+%============================================================================
+
 \paragraph{PSF for the HST/F814W filter.} We find a radial profile for the HST/F814W filter PSF from circular annuli within a synthetic PSF image, ignoring diffraction spikes.
-The one-dimensional MGE fit of Equation \ref{eq:PSFgeneral} to this radial profile is performed using the code by \citet{Cap02}.
+The one-dimensional MGE fit of Equation \eqref{eq:PSFgeneral} to this radial profile is performed using the code by \citet{Cap02}.
 The MGE parameters of the normalized PSF model are given in Table \ref{tab:PSFMGEF814W}.
+
+\paragraph{MGE for the inner regions.} We fit a MGE to the smooth central region within radius $\sim 5''$ of the HST/WFPC2/WF3/F814W image of J1331 in Figure \ref{fig:F814W}.
+Bright objects  close to the galaxy, blobs possibly belonging to the background galaxy and parts of the foreground spiral arm were masked during the fit.
+J1331's galaxy center, position angle and average apparent ellipticity (see Table \ref{tab:galaxyparameters}) are found from the images weighted first and second moment.
+The MGE fit splits the image in annuli with the given ellipticity and position angle and sectors of $5^\circ$ width and fits an 5-Gaussian MGE of the form in Equation \eqref{eq:MGEgeneral} convolved with the PSF MGE in Table \ref{tab:PSFMGEF814W} to it.
+The best fit MGE (PSF convolved) is compared to the data in Figure \ref{fig:MGEinnerRegions} and the corresponding parameters of the intrinsic surface brightness distribution are given in Table \ref{tab:MGEF814W}.
+The fit is a very good representation of the light distribution in the inner $5''$, but underestimates the light distribution outward.
+
+\paragraph{MGE for the outer regions.} To get an handle on the light distribution also in the outer parts of J1331, where spiral arms dominate, we first fit a IRAF \citep{1993ASPC...52..173T} \emph{ellipse} model to the F814W image (masking the brightest blobs in the spiral arms and outer regions).
+Only then we fit a 7-Gaussian MGE to the smooth ellipse model.
+The MGE does not perfectly reproduce the flattness of the ellipse model at every radius (see Figure \ref{fig:MGEouterRegions}), but considering the spiral arm dominated outer regions of J1331, it is good enough for an approximate handling of the overall light distribution.
+
+\paragraph{Transformation into physical units.} To transform the MGE in units of counts into physical units, we apply a simplified version of the procedure described in \citet{Holtzman}.
 
@@
 %============================================================================
-
-%============================================================================
-\begin{table}
-\centering
-\caption{F814W PSF MGE: Parameters of the circular four-Gaussian MGE in Equation \ref{eq:PSFgeneral} fitted to the radial profile of the synthetic HST/F814W PSF image by \Wilma{[TO DO: WHO???]}.}
-\begin{tabular}{ccc}
-\hline
-$k$ & $G_k$ & $\delta_k$ [$''$] \\\hline
-1 & 0.184 & 0.038\\
-2 & 0.485 & 0.085\\
-3 & 0.222 & 0.169\\
-4 & 0.109 & 0.487\\\hline
-\end{tabular}
-\label{tab:PSFMGEF814W}
-\end{table}
-%============================================================================
-
-\paragraph{MGE for the inner regions.} We fit a MGE to the smooth central region within radius $\sim 5''$ of the HST/WFPC2/WF3/F814W image of J1331 in Figure \ref{fig:F814W}.
-Bright objects  close to the galaxy, blobs possibly belonging to the background galaxy and parts of the foreground spiral arm were masked during the fit.
-J1331's galaxy center, position angle and average apparent ellipticity (see Table \ref{tab:galaxyparameters}) are found from the images weighted first and second moment.
-The MGE fit splits the image in annuli with the given ellipticity and position angle and sectors of $5^\circ$ width and fits an 5-Gaussian MGE of the form in Equation \ref{eq:MGEgeneral} convolved with the PSF MGE in Table \ref{tab:PSFMGEF814W} to it.
-The best fit MGE (PSF convolved) is compared to the data in Figure \ref{fig:MGEinnerRegions} and the corresponding parameters of the intrinsic surface brightness distribution are given in Table \ref{tab:MGEF814W}.
-The fit is a very good representation of the light distribution in the inner $5''$, but underestimates the light distribution outward.
-
-%============================================================================
-\begin{figure}
-\centering
-\includegraphics[width=0.8\columnwidth]{fig/1331F814W_MGE_disk_L.ps}
-\caption{MGE for J1331's outer regions: Comparison of contours with constant surface brightness of the smooth IRAF \emph{ellipse} model for J1331 in the F814W filter (yellow) with a corresponding best fit MGE (gray lines).
-The green box corresponds to the image section shown in Figure \ref{fig:MGEinnerRegions}, with the Einstein radius as dashed red line and the black $10''$ orientation line along the major axis (see Figure \ref{fig:MGEinnerRegions}).
-This MGE found from the smooth, symmetric IRAF \emph{ellipse} model is not used to find a dynamical model for J1331, because the dynamics in the outer regions are strongly affected by non-axisymmetries (e.g.
-spiral arms).
-We use it, however, to estimate the galaxy's total luminosity and effective radius, and to get a prediction for the dynamics of the outer regions by extrapolation the best fit model of the inner regions.
-\Wilma{[TO DO: Maybe merge Figures 2 + 3, panels next to each other?]}}
-\label{fig:MGEouterRegions}
-\end{figure}
-%============================================================================
-
-\paragraph{MGE for the outer regions.} To get an handle on the light distribution also in the outer parts of J1331, where spiral arms dominate, we first fit a IRAF \citep{1993ASPC...52..173T} \emph{ellipse} model to the F814W image (masking the brightest blobs in the spiral arms and outer regions).
-Only then we fit a 7-Gaussian MGE to the smooth ellipse model.
-The MGE does not perfectly reproduce the flattness of the ellipse model at every radius (see Figure \ref{fig:MGEouterRegions}), but considering the spiral arm dominated outer regions of J1331, it is good enough for an approximate handling of the overall light distribution.
-
-%============================================================================
-\begin{table*}
-\centering
-\caption{J1331's F814W MGE: Parameters of the best fit MGE to the F814W surface brightness of J1331 in Figure \ref{fig:F814W}.
-The fit is best inside an radius of $5''$.
-The galaxy center and position angle, which gives the orientation of the MGE with respect to the original image, are given in Table \ref{tab:galaxyparameters}.
-This MGE is used in the dynamical modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}.
-The first column gives the total F814W luminosity of the Gaussian in Equation \ref{eq:centralItotalL} in units of counts.
-The second column is the corresponding I-band peak surface brightness in Equation \ref{eq:MGEgeneral} in units of a luminosity surface density, calculated from the first column following the procedure described in Section \ref{sec:MGE_results}.
-The third and fourth column give the dispersion and the last column the axis ratio of the Gaussian in Equation \ref{eq:MGEgeneral}.}
-\begin{tabular}{cccccc}
-\hline
- & total luminosity  & surface density & \multicolumn{2}{c}{Gaussian dispersion} & axis ratio\\
-$k$  & $L_k$ [counts] & $I_{0,k}$ [$L_\odot$/pc$^2$] & $\sigma_k$ [$''$] & $\sigma_k$ [kpc] & $q'_k$\\\hline
-1  &     9425.96 &      20768.  &  0.051   & 0.103  & 1.00\\
-2  &    13173.0 &        3161.2 &  0.178   & 0.358  & 0.76\\
-3  &    40235.0 &        1588.2 &  0.503   & 1.008  & 0.58\\
-4  &    67755.2 &         502.25&  1.180   & 2.368  & 0.56\\
-5  &    203677. &         136.51&  3.891   & 7.805  & 0.57\\\hline
-\end{tabular}
-\label{tab:MGEF814W}
-\end{table*}
-%============================================================================
-
-\paragraph{Transformation into physical units.} To transform the MGE in units of counts into physical units, we apply a simplified version of the procedure described in \citet{Holtzman}.
 
@@
 \Wilma{[TO DO: I'm really confused about this.
-Check, that everything is correct and the naming of quantities, e.g.
-with or without subscripts of 0, is fine???]}
+Check, that everything is correct and the naming of quantities, e.g., with or without subscripts of 0, is fine???]}
+
+%============================================================================
+\begin{figure}
+\centering
+\includegraphics[width=0.8\columnwidth]{fig/1331F814W_MGE_disk_L.ps}
+\caption{MGE for J1331's outer regions: Comparison of contours with constant surface brightness of the smooth IRAF \emph{ellipse} model for J1331 in the F814W filter (yellow) with a corresponding best fit MGE (gray lines).
+The green box corresponds to the image section shown in Figure \ref{fig:MGEinnerRegions}, with the Einstein radius as dashed red line and the black $10''$ orientation line along the major axis (see Figure \ref{fig:MGEinnerRegions}).
+This MGE found from the smooth, symmetric IRAF \emph{ellipse} model is not used to find a dynamical model for J1331, because the dynamics in the outer regions are strongly affected by non-axisymmetries (e.g., spiral arms).
+We use it, however, to estimate the galaxy's total luminosity and effective radius, and to get a prediction for the dynamics of the outer regions by extrapolation the best fit model of the inner regions.
+\Wilma{[TO DO: Maybe merge Figures 2 + 3, panels next to each other?]}}
+\label{fig:MGEouterRegions}
+\end{figure}
+%============================================================================
+
+%============================================================================
+\begin{table*}
+\centering
+\caption{J1331's F814W MGE: Parameters of the best fit MGE to the F814W surface brightness of J1331 in Figure \ref{fig:F814W}.
+The fit is best inside an radius of $5''$.
+The galaxy center and position angle, which gives the orientation of the MGE with respect to the original image, are given in Table \ref{tab:galaxyparameters}.
+This MGE is used in the dynamical modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}.
+The first column gives the total F814W luminosity of the Gaussian in Equation \eqref{eq:centralItotalL} in units of counts.
+The second column is the corresponding I-band peak surface brightness in Equation \eqref{eq:MGEgeneral} in units of a luminosity surface density, calculated from the first column following the procedure described in Section \ref{sec:MGE_results}.
+The third and fourth column give the dispersion and the last column the axis ratio of the Gaussian in Equation \eqref{eq:MGEgeneral}.}
+\begin{tabular}{cccccc}
+\hline
+ & total luminosity  & surface density & \multicolumn{2}{c}{Gaussian dispersion} & axis ratio\\
+$k$  & $L_k$ [counts] & $I_{0,k}$ [$L_\odot$/pc$^2$] & $\sigma_k$ [$''$] & $\sigma_k$ [kpc] & $q'_k$\\\hline
+1  &     9425.96 &      20768.  &  0.051   & 0.103  & 1.00\\
+2  &    13173.0 &        3161.2 &  0.178   & 0.358  & 0.76\\
+3  &    40235.0 &        1588.2 &  0.503   & 1.008  & 0.58\\
+4  &    67755.2 &         502.25&  1.180   & 2.368  & 0.56\\
+5  &    203677. &         136.51&  3.891   & 7.805  & 0.57\\\hline
+\end{tabular}
+\label{tab:MGEF814W}
+\end{table*}
+%============================================================================
 

### 2015-11-20 docs/data_v3.02.tex
Started editing the results section.

@@
 
-For our lensing and dynamics analysis of J1331 we use both Hubble Space Telescope (HST) imaging by \cite{SWELLSI} in two filters (F450W and F814W), as well as line-of-sight stellar kinematics along J1331's major axis by \citet{SWELLSV}.
+\paragraph{Redshift and position.} J1331 is located at right ascension = 202.91800$^\circ$ and a declination = 36.46999$^\circ$ (epoch J2000).
+\citet{SWELLSI} found from SDSS spectra that J1331 has two redshifts inside $1''$: J1331 itself has $z_d = 0.113$ and $z_s = 0.254$ is the redshift of the lensed background source \citep{SWELLSIII}.
+According to the WMAP5 cosmology \citep{WMAP5cosm}, J1331 has an angular diameter distance of 414 Mpc, which translates into a transverse scaling of $1'' \hat{=} 2.01~\text{kpc}$.
 
-\paragraph{Redshift.} \citet{SWELLSI} found from SDSS spectra that J1331 has two redshifts inside $1''$: The smaller one, $z_d = 0.113$, is the redshift of J1331 itself, the larger one, $z_s = 0.254$, is the redshift of the lensed background source \citep{SWELLSIII}.
-According to its redshift and the WMAP5 cosmology \citep{WMAP5cosm}, J1331 has an angular diameter distance of 414 Mpc, which translates into a transverse scaling of $1'' \hat{=} 2.01~\text{kpc}$.
+\paragraph{HST imaging.} We use HST imaging of J1331 by \citet{SWELLSI}.
+They performed high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) and its WF3 CCD chip.
+The images are a combination of four exposures with each an exposure time of $400~\text{sec}$ and were drizzled to a pixel scale of 1 pixel = $0.05''$.
+In particular, we use the images in the filters F450W, to identify the positions of the bluish lensing images, and F814W (I-band) to create a surface brightness MGE model of the reddish bulge.
 
-\paragraph{HST imaging.} We use the follow-up HST imaging, with which \citet{SWELLSI} confirmed that J1331 is indeed a strong gravitational lens.
-They performed high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) and its WF3 CCD chip.
-The images we are using are a combination of four exposures with each an exposure of 400s and were drizzled to a pixel scale of 1 pixel = $0.05''$.
-In particular we use the images in the filters F450W, to identify the positions of the bluish lensing images, and F814W to create a surface brightness MGE model of the reddish bulge (I-band), used in the JAM dynamical modelling.
-
-\paragraph{Stellar kinematics.} For the dynamical modelling we also use the stellar kinematics for J1331 measured by \citet{SWELLSV}.
+\paragraph{Stellar kinematics.} For the dynamical modelling we use the stellar kinematics for J1331 measured by \citet{SWELLSV}.
 They obtained long-slit spectra along J1331's major-axis with the Low Resolution Imaging Spectrograph (LRIS) on the Keck I 10m telescope.
@@
  \Wilma{[TO DO: Maybe mention the following details better in the data section....
-"SWELLS picked galaxies in SDSS whose spectra had two different redshifts within $3''$, which makes it likely to capture strong lenses with typical Einstein radii of $1''$.
-Sufficiently inclined galaxies were picked by eye.
+"Sufficiently inclined galaxies were picked by eye.
 Follow-up high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) was performed to confirm their lensing status \citep{SWELLSI}."]}
-
- \Wilma{[TO DO: Include better in data section. "of approximate Hubble type Sb at right ascension = 202.91800$^\circ$ and a declination = 36.46999$^\circ$ (epoch J2000)"]}

### 2015-11-20 docs/introduction_v3.02.tex
Started editing the results section.

@@
 \emph{Panel (a) and (b):} HST/WFPC2/WFC3 images of J1331 by \citet{SWELLSI} in two filters, F450W in panel (a) and F814W in panel (b).
-The galaxy's coordinates on the sky are right ascension $\alpha$ = 202.91800$^\circ$ and declination $\delta$ = 36.46999$^\circ$ (epoch J2000).
-Image orientation and scaling are indicated in panel (a); the scaling transformation from arcseconds to the physical size of the galaxy in kpc uses the galaxy's redshift $z_d = 0.113$ \citep{SWELLSIII} (i.e., assumes an angular diameter distance of 414 Mpc).
-The color scaling of these two images is the same.
 The black solid line in panel (b) shows the orientation of the major-axis.
-The line has a length of $10''$ and indicates the region within which we carry out the Jeans modelling.
-\emph{Panel (c):} The central region of J1331 in F450W, surface brightness subtracted.
+Its length is $10''$ and it indicates approximately where we carry out the dynamical modelling.
+\emph{Panel (c):} Lensing images in the central region of J1331.
 An IRAF \emph{ellipse} fit to the F450W surface brightness in panel (a) was subtracted from the image.
 The (smoothed) residuals within the white square in panel (a) are shown in panel (c).
-Four bright blobs (A,B,C and D) become visible, which are arranged in a typical strong lensing configuration around the center of the galaxy (G).
-\emph{Panel (d):} Stellar Kinematics along the galaxy's major axis as measured by \citet{SWELLSV}, line-of-sight rotation velocity $v_\text{rot}$, line-of-sight velocity dispersion $\sigma$ and the rms-velocity $v_\text{rms} = \sqrt{v_\text{rot}^2 + \sigma^2}$.
-The dotted line in panel (b) indicates the galaxy's effective half-light radius (in the F814W filter), $R_\text{eff} = 2.6" = 5.2$ kpc.
-The $v_\text{rot}$ curve reveals that J1331 is counter-rotating within $R_\text{eff}$.
-\Wilma{[TO DO: Replace arcsec with '' in panel d)]} \Wilma{[TO DO: Mention, that the configuration of the additional two bright blobs do not suggest that they form a lensing doublet.
-They are probably background star formation regions as well.
-The blob above A could be stretched due to lensing and have a faint counter image between B and G.
-Maybe indicate in plot?]} \Wilma{[TO DO: Use $\text{km s}^{-1}$ instead of km/s]}}
+(The four bright blobs (A,B,C and D), that become visible, are arranged in a typical strong lensing configuration around the center of the galaxy (G).
+The configuration of the two additional blobs, that lie approximately on a line with A, B and G, does not suggest that they form a lensing doublet.
+They might be star forming regions of a background galaxy.) \emph{Panel (d):} Stellar Kinematics along the galaxy's major axis as measured by \citet{SWELLSV}, line-of-sight rotation velocity $v_\text{rot}$, line-of-sight velocity dispersion $\sigma$ and the rms-velocity $v_\text{rms} = \sqrt{v_\text{rot}^2 + \sigma^2}$.
+The dotted line in panel (b) indicates the galaxy's effective half-light radius (in the F814W filter), $R_\text{eff} = 2.6" = 5.2~\text{kpc}$.
+The $v_\text{rot}$ curve reveals that J1331 has a counter-rotating core within $R_\text{eff}$.}
 \label{fig:specialJ1331}

### 2015-11-20 docs/results_lensing_v3.01.tex
Started editing the results section.

@@
 \paragraph{Image positions.} We determine the positions of the lensing images by first subtracting a smooth model for the galaxy's surface brightness from the original image.
-As models we use MGE fits and IRAF \emph{ellipse} fits  (see Sections \ref{sec:MGE_theo} and \ref{sec:MGE_results})  to the galaxy in each the F450W and F814W filter.
-(For example the MGE we use for F814W is the MGE given in Table \ref{tab:MGEF814W} convolved with the PSF in Table \ref{tab:PSFMGEF814W}.) The lensing images become then visible in the residuals (see Figure \ref{fig:lens_just_imgpos}), in which we smooth out noise smaller than the PSF.
-Because the lensing images are extended, we use the position of the brightest pixel in each of the images.
-We also use the F450W-MGE subtracted residuals from \citet{SWELLSIII}.
-The lensing positions as determined from the latter are given in Table \ref{tab:lenspos}.
-The scatter of lensing positions as determined from subtracting different surface brightness models from the galaxy in different filters gives an error of $\pm 1$ pixel on the image positions.
-We find slightly different positions for the peak of the surface brightness in the different filters and apply correspondingly an error of one diagonal pixel to the brightness peak in the F450W image which we use as center of the galaxy.
+As models we use MGE fits and IRAF \emph{ellipse} fits to J1331 in each the F450W and F814W filter.
+The lensing images become visible in the residuals (see Figure \ref{fig:lens_just_imgpos}).
+Because the images are extended, we use the position of the brightest pixel in each of the images.
+In addition, we consider the F450W-MGE subtracted residuals from \citet{SWELLSIII}.
+The lensing positions, as determined from the latter, are given in Table \ref{tab:lenspos}.
+The scatter of lensing positions, as determined from subtracting different brightness models from the galaxy in different filters, gives an error of $\pm 1$ pixel on the image positions.
+To the galaxy center, which we assume to be the surface brightness peak in the F450W image, we apply an error of $\pm \sqrt{2}$ pixel.
 
-Eight image position coordinates allow us to fit a lens mass model with only $<8$ free parameters. We therefore do not fit Fourier components $(a_k,b_k)$ with $k > 3$.
+Eight image position coordinates allow us to fit a lens mass model with only $<8$ free parameters.
+We therefore do not fit Fourier components $(a_k,b_k)$ with $k > 3$ in the lens mass model in Equations \eqref{eq:scalefreemodel}-\eqref{eq:Fourieransatz}.
 
-Even though the constraints from the image positions on $\alpha$ is very weak, we were however able to show that the image positions in Table \ref{tab:lenspos} are consistent with a model with flat rotation curve.
+Even though the constraint from the image positions on $\alpha$ is very weak, we were however able to show that the image positions in Table \ref{tab:lenspos} are consistent with a model with flat rotation curve.
 In the following we therefore set $\alpha=1$.
@@
 
-\paragraph{Best fit lens model.} The best fit lens model for the image positions in Table \ref{tab:lenspos} is given in the first column of Table \ref{tab:bestfitlensmodel}.
+\paragraph{Best fit lens model.} We fit the lens mass model to the image positions in Table \ref{tab:lenspos} by minimizing $\chi^2 = \chi_\text{lens}^2 + \chi_\text{shape}^2$ (see Equations \eqref{eq:chi2lens}-\eqref{eq:chi2total}).
+The best fit parameters are given in the first column of Table \ref{tab:bestfitlensmodel}.
 Figure \ref{fig:lensbestfiteinsteincurves} shows the corresponding critical curve, caustic and Einstein radius, and the best fit source position.
-In this case, where $\alpha=1$, the critical curve is also an equidensity contour of the galaxy model \citep{EvansWitt}, which appears to have an elliptical mass distribution.
-This cricital curve is called \emph{tangential}, because of the tangential orientation of the images close to it.
+In this case, where $\alpha=1$, the (tangential) critical curve is also an equidensity contour of the galaxy model \citep{EvansWitt}, which appears to have an elliptical mass distribution.
 The source is located close to a cusp of the diamond-shaped caustic: a lensing configuration for which we indeed expect four images.
-This is a good indication that indeed all four images are indeed lensing images of the same object.
-Figure \ref{fig:lensbestfittimedelay} overplots the smoothed residuals from the F450W image subtracted by the IRAF \emph{ellipse} fit to the surface brightness with the contours of the best fit model's time delay surface.
-This demonstrates that, although we did not include any information about the shape of the lensing images in the fit, it is consistent with the predicted distortion for an extended source by the best fit lens model.
+Figure \ref{fig:lensbestfittimedelay} overplots the (smoothed) residuals from the F450W image subtracted by an IRAF \emph{ellipse} brightness model with the contours of the best fit model's time delay surface.
+This demonstrates that, although we did not include any information about the shape of the lensing images in the fit, it is consistent with the predicted distortion for an extended source.
 
@@
 \Wilma{[TO DO: Add A, B, C, D in the figure to make clear which image is which.]} \Wilma{[TO DO: Combine in one figure.
-Make all lines except time delay surface very thick.]}}
+Make all lines except time delay surface very thick.]} \Wilma{[TO CO: Mention: in which we smooth out noise smaller than the PSF]}}
 \label{fig:???}
@@
 
-To estimate how the uncertainties in the determination of the image positions and galaxy center affect the results, we Monte Carlo sample random positions from a two-dimensional Normal distribution centered at the positions in Table \ref{tab:lenspos} and a standard deviation corresponding to the measurement error.
-A Gaussian fit to the resulting distributions of best fit values leads to the constraints on the shape parameters and Einstein quantities in the second column in Table \ref{tab:bestfitlensmodel}.
-We therefore constrain the Einstein radius to within 2\%, $R_\text{ein} = (0.91 \pm 0.02)''$ and the projected mass within the critical curve with a relative error of 4\%, $M_\text{crit} =(7.9\pm0.3)\cdot 10^{10} M_\odot$.
+To estimate how the uncertainties in the determination of image positions and galaxy center affect the results, we sample random positions from two-dimensional Normal distributions with peaks and standard deviations according to Table \ref{tab:lenspos}.
+Model fits to many sampled image positions lead to probability distributions for the best fit shape parameters and Einstein quantities; peak and standard deviations are given in the second column of Table \ref{tab:bestfitlensmodel}.
+We constrain the Einstein radius to within 2\%, $R_\text{ein} = (0.91 \pm 0.02)''$ and the projected mass within the critical curve with a relative error of 4\%, $M_\text{crit} =(7.9\pm0.3)\cdot 10^{10} M_\odot$.
 Our measurement of $R_\text{ein}$ is consistent with that from \citet{SWELLSIII}, $R_\text{ein,SWELLS} = (0.96 \pm 0.04)''$ (which used a singular isothermal ellipsoid as lens mass model and the intermediate-axis convention of the critical curve as the Einstein radius).
 The relative difference between our critical mass and that of \citet{SWELLSIII}, $M_\text{crit,SWELLS} =(8.86\pm0.61)\cdot 10^{10} M_\odot$, is 13\%.
-
-%========================================================================================
-
-\begin{table*}
-\centering
-\caption{Total I-band (F814W) luminosity inside the Einstein radius $R_\text{ein}$, found from integrating the MGE in Table \ref{tab:MGEF814W} and corresponding total mass-to-light ratio $\Upsilon_\text{I,tot}^\text{ein}$ using the Einstein mass $M_\text{ein}$.
-$R_\text{ein}$ and $M_\text{ein}$ are given in Table \ref{tab:bestfitlensmodel}.
-\Wilma{[TO DO: No separate table, put instead in text]}}
-\begin{tabular}{cc}
-\hline
-Total I-band luminosity within $R_\text{ein}$ & Mass-to-light ratio within $R_\text{ein}$\\
- $L_\text{I,ein}$ [$10^{10} L_\odot$] & $\Upsilon_\text{I,tot}^\text{ein} = M_\text{ein} / L_\text{I,ein}$ [$\Upsilon_{\text{I},\odot}$]\\\hline
-1.40 & 5.56\\\hline
-\end{tabular}  
-\label{tab:einsteinML} 
-\end{table*}
 
@@
 
-\paragraph{Comparison with light distribution.} The surface mass distribution as predicted by the best fit lens model in Table \ref{tab:bestfitlensmodel} is shown in Figure \ref{fig:lenscomparemass}.
-We introduced random noise according to the uncertainties in the Fourier shape parameters to create a mock observation that visualizes the effect of the measurement errors.
-From the mock image's second moment we find an average axis ratio for the lens mass model of $q_\text{lens} \simeq 0.695$, which is consistent with the one found by \citet{SWELLSIII}, $q_\text{lens,SWELLSIII} = 0.67 \pm 0.09$, while the light's average axis ratio in Table \ref{tab:galaxyparameters} is $q' = 0.598$.
+\paragraph{Comparison with light distribution.} The surface mass distribution as predicted by the best fit lens model (Table \ref{tab:bestfitlensmodel}) is shown in Figure \ref{fig:lenscomparemass}.
+We visualize the effect of the Fourier shape parameter uncertainties by introducing random noise to create a mock observation.
+From the mock image's second moment we find an average axis ratio for the lens mass model of $q_\text{lens} \simeq 0.695$, which is consistent with the one found by \citet{SWELLSIII}, $q_\text{lens,SWELLSIII} = 0.67 \pm 0.09$, while the light's average axis ratio is $q' = 0.598$ (see Table \ref{tab:galaxyparameters}).
 
-To estimate the total mass-to-light ratio within the Einstein radius $\Upsilon_\text{I,tot}^\text{ein} = M_\text{ein} / L_\text{I,ein}$, we first integrate the MGE in Table \ref{tab:MGEF814W} to get the total luminosity within the Einstein radius $L_\text{I,ein}$.
-$L_\text{I,ein}$ and $\Upsilon_\text{I,tot}^\text{ein}$ are given in Table \ref{tab:einsteinML} \Wilma{[TO DO: Put in text, no separate table.]}.
-$\Upsilon_\text{I,tot}^\text{ein} \sim 5.6$ is consistent or slightly larger than the stellar mass-to-light ratio assuming a Salpeter Initial Mass Function $\Upsilon_\text{I,*}^\text{sal} = 4.7 \pm 1.2$ according to \citet{SWELLSI} and Table \ref{tab:previousresults} (see also discussion in Section \ref{sec:MLdiscussion}).
-We use $\Upsilon_\text{I,tot}^\text{ein}$ to transform the observed surface brightness in the F814W filter into a surface mass density to compare it to the lensing mass distribution (Figure \ref{fig:lenscomparelight}).
-Figure \ref{fig:lenscompareboth} then compares equidensity contours at the same values of both the predicted lens mass distribution and the observed surface brightness times $\Upsilon_\text{I,tot}^\text{ein}$.
+We estimate the total mass-to-light ratio within the Einstein radius $\Upsilon_\text{I,tot}^\text{ein} \equiv M_\text{ein} / L_\text{I,ein}$.
+For this, we integrate the MGE in Table \ref{tab:MGEF814W} to get the total I-band luminosity within the Einstein radius $L_\text{I,ein} = 1.40\cdot 10^{10} L_\odot$.
+The corresponding Einstein mass-to-light ratio is therefore $\Upsilon_\text{I,tot}^\text{ein} = 5.56 \Upsilon_{I,\odot}$.
+This is consistent with or slightly larger than the stellar mass-to-light ratio assuming a Salpeter IMF $\Upsilon_\text{I,*}^\text{sal} = 4.7 \pm 1.2$ according to \citet{SWELLSI} and Table \ref{tab:previousresults} (see also discussion in Section \ref{sec:MLdiscussion}).
+
+We use $\Upsilon_\text{I,tot}^\text{ein}$ to transform the observed surface brightness in the F814W filter into a surface mass density (Figure \ref{fig:lenscomparelight}).
+Figure \ref{fig:lenscompareboth} then compares equidensity contours of both the predicted lens mass distribution and the observed surface brightness times $\Upsilon_\text{I,tot}^\text{ein}$.
 
@@
 (2) Within and around the Einstein radius, mass and light distribution have a similar elliptical shape, while further out the mass distribution is slightly rounder.
-(3) The light distribution drops faster than the mass with increasing radius (at least partly because of the assumption of a flat rotation curve).
+(3) The light distribution drops faster than the mass with increasing radius (which is---at least partly---because of the assumption of a flat rotation curve).
 However, the mass distribution is only constraint around the Einstein radius and otherwise an extrapolation.
+
+\Wilma{[TO DO: Make sure IMF is introduced somewhere.]}

### 2015-11-20 docs/results_photometry_v3.02.tex
Started editing the results section.

--- 2015-11-20 archive/v3/docs/results_photometry_v3.01.tex
@@
 
-In this section we construct a model for the galaxy's intrinsic light distribution in terms of an MGE, which we will then compare in Section \ref{sec:results_lensing} to the mass distribution.
-The light model will also be the basis of the dynamical Jeans modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}.
-
-To derive J1331's surface brightness distribution, we use the HST image in the F814W (I-band) filter, shown in Figure \ref{fig:F814W}.
-At longer wavelengths J1331's central old and smooth stellar component is more extended than in the F450W filter in Figure \ref{fig:F450W}, which is more sensitive to young clumpy star-forming regions.
-In the I-band the bulge is also much brighter than the bluish lens images and the imaging is less prone to extinction.
-The F814W image is therefore best suited for fitting a MGE.
+In this section we construct a model for the J1331's intrinsic light distribution in terms of MGEs (see Section \ref{sec:MGE_theo}).
+We use the HST image in the F814W (I-band) filter (Figure \ref{fig:F814W}) because J1331's central stellar component appears at longer wavelengths (a) smoother and more extended than in the F450W filter (Figure \ref{fig:F450W}), as it is less sensitive to young clumpy star-forming regions, (b) much brighter than the bluish lensing images, and (c) the imaging is less prone to extinction.
 
@@
 \centering
-\caption{F814W PSF MGE: Parameters of the circular four-Gaussian MGE in Equation \eqref{eq:PSFgeneral} fitted to the radial profile of the synthetic HST/F814W PSF image by \Wilma{[TO DO: WHO???]}.}
+\caption{F814W PSF MGE: Parameters of the circular four-Gaussian MGE in Equation \eqref{eq:PSFgeneral} fitted to the radial profile of the synthetic HST/F814W PSF image.}
 \begin{tabular}{ccc}
 \hline
-$k$ & $G_k$ & $\delta_k$ [$''$] \\\hline
+$j$ & $G_j$ & $\delta_j$ [$''$] \\\hline
 1 & 0.184 & 0.038\\
@@
 
-\paragraph{PSF for the HST/F814W filter.} We find a radial profile for the HST/F814W filter PSF from circular annuli within a synthetic PSF image, ignoring diffraction spikes.
-The one-dimensional MGE fit of Equation \eqref{eq:PSFgeneral} to this radial profile is performed using the code by \citet{Cap02}.
+\paragraph{PSF for the HST/F814W filter.} The one-dimensional MGE in Equation \eqref{eq:PSFgeneral} is fitted to the radial profile of a synthetic image of the HST/F814W filter PSF, ignoring diffraction spikes and using the code by \citet{Cap02}.
 The MGE parameters of the normalized PSF model are given in Table \ref{tab:PSFMGEF814W}.
 
-\paragraph{MGE for the inner regions.} We fit a MGE to the smooth central region within radius $\sim 5''$ of the HST/WFPC2/WF3/F814W image of J1331 in Figure \ref{fig:F814W}.
-Bright objects  close to the galaxy, blobs possibly belonging to the background galaxy and parts of the foreground spiral arm were masked during the fit.
+\paragraph{MGE for the inner regions.} We fit a MGE to J1331's smooth central region within $\sim 5''$ from the HST/WFPC2/WF3/F814W image (Figure \ref{fig:F814W}).
+Bright objects close to the bulge (blobs possibly belonging to the background galaxy and parts of the foreground spiral arm) were masked during the fit.
 J1331's galaxy center, position angle and average apparent ellipticity (see Table \ref{tab:galaxyparameters}) are found from the images weighted first and second moment.
@@
 
-\paragraph{MGE for the outer regions.} To get an handle on the light distribution also in the outer parts of J1331, where spiral arms dominate, we first fit a IRAF \citep{1993ASPC...52..173T} \emph{ellipse} model to the F814W image (masking the brightest blobs in the spiral arms and outer regions).
+\paragraph{MGE for the outer regions.} To get a handle on the light distribution also in the outer parts of J1331, where spiral arms dominate, we first fit a IRAF \citep{1993ASPC...52..173T} \emph{ellipse} model to the F814W image (masking the brightest blobs in the spiral arms and outer regions).
 Only then we fit a 7-Gaussian MGE to the smooth ellipse model.
-The MGE does not perfectly reproduce the flattness of the ellipse model at every radius (see Figure \ref{fig:MGEouterRegions}), but considering the spiral arm dominated outer regions of J1331, it is good enough for an approximate handling of the overall light distribution.
+The MGE does not perfectly reproduce the flatness of the ellipse model at every radius (see Figure \ref{fig:MGEouterRegions}), but considering the spiral arm dominated outer regions of J1331, it is good enough for an approximate handling of the overall light distribution.
 
@@
 %============================================================================
-\begin{figure}
+\begin{figure*}
 \centering
-\includegraphics[width=0.8\columnwidth]{fig/1331F814Wsci_MGE_M.ps}
-\caption{MGE for J1331's inner regions: Comparison of contours with constant F814W surface brightness of J1331's central region (orange lines) with the corresponding iso-brightness contours of the best fit MGE in Table \ref{tab:MGEF814W}, convolved with the PSF in Table \ref{tab:MGEF814W}, (gray lines).
-The MGE model is a good representation of the galaxy's light distribution along the major axis within $\sim 5''$.
-Image scaling and orientation are indicated in the figure.
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=.8\columnwidth]{fig/1331F814Wsci_MGE_M.ps}
+  \caption{MGE for J1331's inner regions.}
+ \label{fig:MGEinnerRegions}
+\end{subfigure}%
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=.8\columnwidth]{fig/1331F814W_MGE_disk_L.ps}
+  \caption{MGE for J1331's outer regions.}
+ \label{fig:MGEouterRegions}
+\end{subfigure}%
+\caption{MGEs for J1331's surface brightness distribution.
+Comparison of contours with constant F814W surface brightness (orange lines) with the corresponding iso-brightness contours of the best fit MGE, convolved with the PSF in Table \ref{tab:MGEF814W}, (gray lines).
 The black line has a length of $10''$ and it's orientation corresponds to the galaxy's position angle as found in Table \ref{tab:galaxyparameters}.
 For comparison the Einstein radius as found in Table \ref{tab:bestfitlensmodel}  is indicated as red dashed line.
-This MGE is used as model for the stellar tracer distribution in the dynamical Jeans modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}.}
-\label{fig:MGEinnerRegions}
-\end{figure}
+\emph{Panel (a)} Central regions of J1331.
+The MGE model is a good representation of the galaxy's light distribution along the major axis within $\sim 5''$.
+Its parameters are given in Table \ref{tab:MGEF814W}.
+This MGE is used as model for the stellar tracer distribution in the dynamical Jeans modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}.
+\emph{Panel (b)} Outer regions of J1331.
+The orange lines indicate here contours of a smooth IRAF \emph{ellipse} fit to J1331 in the F814W filter; the gray lines are the corresponding best fit MGE.
+The green box corresponds to the image section shown in Panel (a).
+This MGE is not used for dynamical modelling, because the dynamics in the outer regions are strongly affected by non-axisymmetries (e.g., spiral arms).
+We use it, however, to estimate the galaxy's total luminosity and effective radius, and to get a prediction for the dynamics of the outer regions.}
+\end{figure*}
 %============================================================================
 
-The scaling of the drizzled HST/WFC3 images is  $S = 0.05''/$pixel and the total exposure time $T = 1600$ sec.
-The total F814W luminosity in counts of each Gaussian of the MGE has a central surface brightness in counts per pixel of
+The scaling of the drizzled HST/WFC3 images is  $S \equiv 0.05''/\text{pixel width}$ and the total exposure time $T = 1600$ sec.
+Each Gaussian in the MGE has a total F814W luminosity $L_i$ (in counts) and a central surface brightness (in counts per pixel) of
 \begin{equation*}
-C_0\text{[counts/pixel]} = \frac{L[\text{counts}]}{2\pi \sigma[\text{pixel}]^2 q}.
+C_{0,i}\text{[counts/pixel]} = \frac{L_i[\text{counts}]}{2\pi \sigma[\text{pixel}]^2 q}.
 \end{equation*}
-This is then transformed into an I-band surface brightness via
+This is then transformed into an I-band surface brightness (in $\text{mag}\times(1'')^{-2}$) via
 \begin{equation}
-\mu_{I,0} \simeq -2.5 \log_{10}\left( \frac{C_0\text{[counts/pixel]}}{T[\text{sec}] \cdot S[''/\text{pixel}]^2}\right) + Z + C + A_I, \label{eq:muI_}
+\mu_{I,0,i} \simeq -2.5 \log_{10}\left( \frac{C_{0,i}\text{[counts/pixel]}}{T[\text{sec}] \cdot S[''/\text{pixel width}]^2}\right) + Z + C + A_I, \label{eq:muI_}
 \end{equation}
-\Wilma{[TO DO: Make sure to use $\mu_{I,0}$ where applicable.]} where $Z\simeq21.62$ is a the zero-point from \citet{Holtzman}  (updated according to \citet{Dolphin,DolphinNew}) for the photometric system of the HST/WFPC2 camera and the F814W filter plus a correction for the difference in gain between calibration and observation.
-$C= 0.1$ corrects for the finite aperture of the WFPC2.
-And $A_I =0.015$ mag  is the extinction in the (Landolt) I-band towards J1331, according to the NASA/IPAC Extragalactic Database (NED)\footnote{The NASA/IPAC Extragalactic Database (NED, \url{https://ned.ipac.caltech.edu/}) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.
+where $Z\simeq21.62~\text{mag}$ is a the zero-point from \citet{Holtzman}, updated according to \citet{Dolphin,DolphinNew}, for the photometric system of the HST/WFPC2 camera and the F814W filter, plus a correction for the difference in gain between calibration and observation.
+$C= 0.1~\text{mag}$ corrects for the finite aperture of the WFPC2; and $A_I =0.015~\text{mag}$ is the extinction in the (Landolt) I-band towards J1331, according to the NASA/IPAC Extragalactic Database (NED)\footnote{The NASA/IPAC Extragalactic Database (NED, \url{https://ned.ipac.caltech.edu/}) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.
 The data for J1331 (SDSS J133140.33+362811.9) was retrieved in October 2013.}.
 The color-dependent correction between the F814W filter and the I-band of the UBVRI photometric system is  small \citep{Holtzman} and we neglect it therefore.
-The last step is to transform the surface brightness $\mu_i$ in mag to the I-band surface density of the Gaussian in $L_\odot$/pc$^2$ as
+The last step is to transform the surface brightness $\mu_{I,0,i}$ (in mag) to the I-band surface density $I_{0,i}$ (in $L_\odot$/pc$^2$) of the Gaussian, i.e.,
 \begin{eqnarray*}
-I_0[L_\odot \text{pc}^{-2}] = \left( 64800/\pi\right)^2 \left(1+z \right)^4 10^{0.4\left(M_{\odot,I}-\mu_{I,0} \right)},
+I_{0,i}[L_\odot \text{pc}^{-2}] = \left( 64800/\pi\right)^2 \left(1+z_d \right)^4 10^{0.4\left(M_{\odot,I}-\mu_{I,0,i} \right)},
 \end{eqnarray*}
-where the term with $z$ accounts for redshift dimming and $M_{\odot,I}=4.08$ mag is the sun's absolute I-band magnitude \citep{1998gaas.book.....B}.
-The luminosity $L_k$[counts] and the corresponding surface brightness density $I \equiv I_{0,k}[L_\odot \text{pc}^{-2}]$ of each Gaussian are given in Table \ref{fig:MGEinnerRegions}.
-\Wilma{[TO DO: I'm really confused about this.
-Check, that everything is correct and the naming of quantities, e.g., with or without subscripts of 0, is fine???]}
-
-%============================================================================
-\begin{figure}
-\centering
-\includegraphics[width=0.8\columnwidth]{fig/1331F814W_MGE_disk_L.ps}
-\caption{MGE for J1331's outer regions: Comparison of contours with constant surface brightness of the smooth IRAF \emph{ellipse} model for J1331 in the F814W filter (yellow) with a corresponding best fit MGE (gray lines).
-The green box corresponds to the image section shown in Figure \ref{fig:MGEinnerRegions}, with the Einstein radius as dashed red line and the black $10''$ orientation line along the major axis (see Figure \ref{fig:MGEinnerRegions}).
-This MGE found from the smooth, symmetric IRAF \emph{ellipse} model is not used to find a dynamical model for J1331, because the dynamics in the outer regions are strongly affected by non-axisymmetries (e.g., spiral arms).
-We use it, however, to estimate the galaxy's total luminosity and effective radius, and to get a prediction for the dynamics of the outer regions by extrapolation the best fit model of the inner regions.
-\Wilma{[TO DO: Maybe merge Figures 2 + 3, panels next to each other?]}}
-\label{fig:MGEouterRegions}
-\end{figure}
-%============================================================================
+where the term with $z_d$ accounts for redshift dimming and $M_{\odot,I}=4.08~\text{mag}$ is the Sun's absolute I-band magnitude \citep{1998gaas.book.....B}.
+The luminosity $L_i$[counts] and the corresponding surface brightness density $I_{0,i} [L_\odot \text{pc}^{-2}]$ of each Gaussian are given in Table \ref{fig:MGEinnerRegions}.
 
@@
  & total luminosity  & surface density & \multicolumn{2}{c}{Gaussian dispersion} & axis ratio\\
-$k$  & $L_k$ [counts] & $I_{0,k}$ [$L_\odot$/pc$^2$] & $\sigma_k$ [$''$] & $\sigma_k$ [kpc] & $q'_k$\\\hline
+$i$  & $L_i$ [counts] & $I_{0,i}$ [$L_\odot$/pc$^2$] & $\sigma_i$ [$''$] & $\sigma_i$ [kpc] & $q'_i$\\\hline
 1  &     9425.96 &      20768.  &  0.051   & 0.103  & 1.00\\
@@
 This is similar to the disk axis ratio of $q' = 0.40$ found by \citet{SWELLSI}.
-If a typical thickness of an oblate disk was around $q_0 \sim 0.2$ \citep{1958MeLu2.136....1H}, the inclination would follow from
+If a typical thickness of an oblate disk is around $q_0 \sim 0.2$ \citep{1958MeLu2.136....1H}, the inclination follows from
 \begin{equation*}
@@
 
-\paragraph{Total luminosity and effective radius.} J1331's total I-band luminosity is easily determined by summing up the luminosity contributions of all the Gaussians of the MGE for the outer regions (shown as gray lines in Figure \ref{fig:MGEouterRegions}).
-We find $L_\text{tot,I} \simeq 5.6 \cdot 10^{10} L_\odot$.
-This corresponds to an apparent magnitude of $m_I = 15.77$ mag.
+\paragraph{Total luminosity and effective radius.} J1331's total I-band luminosity is determined by summing up the luminosity contributions of all the MGE Gaussians for the outer regions (shown as gray lines in Figure \ref{fig:MGEouterRegions}).
+We find $L_\text{tot,I} \simeq 5.6 \cdot 10^{10} ~L_\odot$.
+This corresponds to an apparent magnitude of $m_I = 15.77~\text{mag}$.
 We determine the circularized effective radius $R_\text{eff}$ of J1331 from the definition $L(<R_\text{eff}) \equiv \frac 12 L_\text{tot}$ and the growth curve $L(<R')$ from the MGE model of the outer regions, where $R'$ is the projected radius on the sky.

### 2015-11-23 archive/v3/docs/model_JAM_v3.01.tex
Edited dynamical modelling results sections.

--- 2015-11-16 docs/model_JAM_v3.01.tex
@@
 
-\paragraph{Jeans Anisotropic Models (JAM).} JAM modelling assumes galaxies (a) to be collisionless, i.e.
-the collisionless Boltzmann equation for the distribution function $f(\vect{x},\vect{v},t)$ has to be satisfied ($\frac{\diff f(\vect{x},\vect{v},t}{\diff t} = 0$), (b) in a steady state ($\frac{\partial}{\partial t} = 0$), (c) axisymmetric (best described in cylindrical coordinates $(R,z,\phi)$ and $\frac{\partial}{\partial \phi} = 0$).
+\paragraph{Jeans Anisotropic Models (JAM).} JAM modelling assumes galaxies (a) to be collisionless, i.e., the collisionless Boltzmann equation for the distribution function $f(\vect{x},\vect{v},t)$ has to be satisfied ($\frac{\diff f(\vect{x},\vect{v},t}{\diff t} = 0$), (b) in a steady state ($\frac{\partial}{\partial t} = 0$), (c) axisymmetric (best described in cylindrical coordinates $(R,z,\phi)$ and $\frac{\partial}{\partial \phi} = 0$).
 From this follow the axisymmetric Jeans equations as the vector-valued first moment of the Boltzmann equation, i.e.
@@
 The JAM modelling approach by \citet{Cap08} makes use of expressing the tracer density and the mass density as MGEs (see also \citet{1994A&A...285..723E}).
-The density of stellar tracers is assumed to be proportional to the observed and deprojected brightness distribution $\nu(R,z)$ in Equation \ref{eq:deprojMGE}.
+The density of stellar tracers is assumed to be proportional to the observed and deprojected brightness distribution $\nu(R,z)$ in Equation \eqref{eq:deprojMGE}.
 The mass density $\rho(R,z)$ can consist of several sets of MGEs, describing stellar and dark matter components.
 The gravitational potential is generated from the mass MGE by integrating the Poisson equation \citep{1994A&A...285..723E}.
-Equations \ref{eq:Jeans1} and \ref{eq:Jeans2} together with \ref{eq:bz} provide the velocity dispersion tensor $\langle v_i v_j \rangle = \langle v_i^2 \rangle$ (with $i,j \in \{ R,\phi, z\}$).
+Equations \eqref{eq:Jeans1} and \eqref{eq:Jeans2} together with \ref{eq:bz} provide the velocity dispersion tensor $\langle v_i v_j \rangle = \langle v_i^2 \rangle$ (with $i,j \in \{ R,\phi, z\}$).
 It is then rotated by the inclination angle $i$ to the coordinate system of the observer ($(x',y')$ being the plane of the sky and $z'$ the line-of-sight, where $x'$ is alinged with the galaxy's major axis).
@@
 \end{eqnarray*}
-The JAM modelling code by \citet{Cap08} evaluates numerically Equation \ref{eq:explicitLOSvelCap} for a given luminous tracer and mass distribution MGE and a given inclination.
+The JAM modelling code by \citet{Cap08} evaluates numerically Equation \eqref{eq:explicitLOSvelCap} for a given luminous tracer and mass distribution MGE and a given inclination.
 
@@
 \end{equation*}
-The model in Equation \ref{eq:explicitLOSvelCap} predicts the intrinsic $\langle v_\text{los}^2 \rangle$ at a given position on the sky, which have then to be modified according to the mode of observation, to be comparable to the measurements.
-The measured $v_\text{rms}$ is a light-weighted mean for a pixel along the long-slit of the spectrograph, with width $L_y = 1''$ \citep{SWELLSV} and a certain given extent along the galaxy's major axis, $L_x$, i.e.
-for a rectangular aperture
+The model in Equation \eqref{eq:explicitLOSvelCap} predicts the intrinsic $\langle v_\text{los}^2 \rangle$ at a given position on the sky, which have then to be modified according to the mode of observation, to be comparable to the measurements.
+The measured $v_\text{rms}$ is a light-weighted mean for a pixel along the long-slit of the spectrograph, with width $L_y = 1''$ \citep{SWELLSV} and a certain given extent along the galaxy's major axis, $L_x$, i.e., for a rectangular aperture
 \begin{equation*}
@@
 \end{equation*}
-The light arriving at the spectrograph itself was subject to seeing, i.e. a Gaussian with Full Width Half Maximum (FWHM) of $1.1''$ \citep{SWELLSV}
+The light arriving at the spectrograph itself was subject to seeing, i.e., a Gaussian with Full Width Half Maximum (FWHM) of $1.1''$ \citep{SWELLSV}
 \begin{equation*}

### 2015-11-23 archive/v3/docs/results_JAMwithNFW_v3.01.tex
Edited dynamical modelling results sections.

--- 2015-11-18 docs/results_JAMwithNFW_v3.01.tex
@@
 
-\paragraph{Including a dark matter halo.} The dynamical modelling attempts in the previous sections suggest that J1331's inner regions have a slightly more roundish and at large radii more massive mass distribution than expected from the distribution of stars alone.
-A dark matter halo in addition to the stellar component could explain these findings.
-We therefore proceed by modelling the mass distribution with a) a stellar component, which we get from the light MGE in Table \ref{tab:MGEF814W} (deprojected to the intrinsic $\nu(R,z)$) times a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$), and b) a spherical NFW dark matter component (see Section \ref{sec:model_JAM}) with free parameters halo scale length $r_s$ and circular velocity at the virial radius $v_{200}$.
-In the JAM modelling we use a 10-Gaussian MGE fit to the classical NFW profile in Equation \eqref{eq:NFWprofile}.
+The modelling attempts in the previous sections suggest that J1331's mass distribution could be more roundish in the inner regions and more massive at larger radii than expected from the distribution of stars alone.
+A DM halo in addition to the stellar component could explain these findings.
 
@@
 %=======================
+
+\paragraph{Including a DM halo.} We therefore proceed by modelling the mass distribution with (a) a stellar component, which we get from the light MGE in Table \ref{tab:MGEF814W} (deprojected to the intrinsic $\nu(R,z)$) times a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and (b) a spherical NFW DM component (see Section \ref{sec:model_JAM}) with halo scale length $r_s$ and circular velocity at the virial radius $v_{200}$ as free parameters.
+In the JAM modelling we use a 10-Gaussian MGE fit to the classical NFW profile in Equation \eqref{eq:NFWprofile}.
 
@@
 
-\paragraph{Modelling and priors.} The full set of fit parameters is $(\Upsilon_\text{I,*},r_s,v_{200},\beta_z)$, where $\beta_z$ is the constant velocity anisotropy parameter (see Section \ref{sec:model_JAM}).
-We will investigate this parameter space with a MCMC\footnote{The Python code package for \emph{emcee}, a Monte Carlo Markov Chain implementation by \citet{emcee} is available online at \url{http://dan.iel.fm/emcee/current/}.
-The version from October 2013 was used in this work.} \citep{emcee} and use priors for the halo parameters to guide the fit to a realistic NFW halo shape.
-
-\citet{Dutton10} give a relation for halo vs.
-stellar mass for late-type galaxies.
-Using the stellar mass estimate for J1331 from \citet{SWELLSI} $m_* = (1.06 \pm 0.25) \cdot 10^{11} M_\odot$ for the Chabrier IMF estimate, we find ${v_{200}} = (202_{-33}^{+44})_{-13}^{+12}$.
-The first of the two quoted errors is due to the $2\sigma$ scatter in the relation by \citet{Dutton10}.
-The second error is the propagated error due to the uncertainty in the stellar mass.
-We use this as a rough estimate for the halo of J1331 and as Gaussian prior on $v_{200}$,
-\begin{equation*}
-p(v_{200}) = \mathscr{N}(200~\text{km s}^{-1},40~\text{km s}^{-1}).
-\end{equation*}
-
-We also use the concentration vs. halo mass relation by \citet{Maccio08} in Equation \eqref{eq:Maccio08} as a prior on the concentration, i.e.
-\begin{equation*}
-p(\log c_{200} \mid v_{200}) = \mathscr{N}\left(\langle \log c_{200} \rangle (M_{200}) \mid 0.105 \right).
-\end{equation*}
-
-For the velocity anisotropy parameter $\beta$ we will again employ a uniform prior 
-\begin{equation*}
-p(\beta) = \mathscr{U}(-0.5,+0.5)
-\end{equation*}
-to exclude very unrealistic anisotropies. The full prior used is then
-\begin{eqnarray*}
-&&p(\Upsilon_\text{I,*},r_s,v_{200},\beta) \\
-&&= \frac{1}{\ln\left( 10 r_s\right)} p(\log c_{200} \mid v_{200}) \cdot p(v_{200}) \cdot p(\beta), 
-\end{eqnarray*}
-where the factor $1/\ln\left( 10 r_s\right)$ is the Jacobian of the transformation from the halo parameters $(v_{200},\log c_{200})$ to $(v_{200},r_s)$.
-
 %==============
@@
 \end{subfigure}
-\hspace{\textwidth}
-\begin{subfigure}{.48\textwidth}
-  \centering
-  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_vcirc.ps}
-  \caption{Circular velocity curve.}
-  \label{fig:modelB4_vcirc}
-\end{subfigure}
-\caption{Best fit JAM model including a NFW halo and velocity anisotropy with parameters given in Table \ref{tab:modelB4_bestfit}.
+\caption{\Wilma{[TO DO: Rewrite caption]} Best fit JAM model including a NFW halo and velocity anisotropy with parameters given in Table \ref{tab:modelB4_bestfit}.
 The 12 lines shown correspond to the 12 models randomly drawn from the posterior probability distribution and marked as grey diamonds in Figure \ref{fig:modelB4_triangle}.
@@
 Also shown is the non-symmetrized data at larger radii (open blue dots) and an extrapolation of the best fit models, using the same model parameters but the I-band surface brightness MGE for the outer regions of J1331 derived from the Ellipse model (red dashed lines).
-\emph{Panel b)} shows the circular velocity curve of the total mass (green), and separately the contribution of the stellar mass (yellow, again generated from the MGE in Table \ref{tab:MGEF814W}) and dark matter (grey).
+\emph{Panel b)} shows the circular velocity curve of the total mass (green), and separately the contribution of the stellar mass (yellow, again generated from the MGE in Table \ref{tab:MGEF814W}) and DM (grey).
 \Wilma{[TO DO: make one separate circular velocity plot, that also contains the mass-follows-light with Einstein M/L vcirc and compares it with Aaron's vcirc curve.
@@
 \Wilma{[TO DO: Replace arcsec with '']} \Wilma{[TO DO: Use $\text{km s}^{-1}$ instead of km/s]} \Wilma{[TO DO: Make two figures from this: vrms (shrinked horizontally) and encl Mass should be first and second panel of one figure, and circular velocity curve should be separate figure.
-]}}
+] \Wilma{[TO DO: Use MGE for the inenr regions in circular velocity plot.]}}}
 \label{fig:modelB4_models}
@@
 
+\paragraph{Modelling and priors.} The full set of fit parameters is $(\Upsilon_\text{I,*},r_s,v_{200},\beta_z)$, where $\beta_z$ is again the constant velocity anisotropy parameter.
+We will investigate this parameter space with a MCMC\footnote{The Python code package for \emph{emcee}, a Monte Carlo Markov Chain implementation by \citet{emcee} is available online at \url{http://dan.iel.fm/emcee/current/}.
+The version from October 2013 was used in this work.} \citep{emcee} and use priors for the halo parameters to guide the fit to a realistic NFW halo shape.
+
+\citet{Dutton10} give a relation for halo vs.
+stellar mass for late-type galaxies.
+Using the stellar mass estimate for J1331 from \citet{SWELLSI}, $m_* = (1.06 \pm 0.25) \cdot 10^{11} M_\odot$ for the Chabrier IMF estimate, we find ${v_{200}} = (202_{-33}^{+44})_{-13}^{+12}$.
+The first error is due to the $2\sigma$ scatter in the relation by \citet{Dutton10}.
+The second error is the propagated error due to the uncertainty in the stellar mass.
+We use this as a rough estimate for the halo of J1331 and as Gaussian prior on $v_{200}$,
+\begin{equation*}
+p(v_{200}) = \mathscr{N}(200~\text{km s}^{-1},40~\text{km s}^{-1}).
+\end{equation*}
+
+We also use the concentration vs. halo mass relation by \citet{Maccio08} in Equation \eqref{eq:Maccio08} as a prior on the concentration, i.e.
+\begin{equation*}
+p(\log c_{200} \mid v_{200}) = \mathscr{N}\left(\langle \log c_{200} \rangle (M_{200}) \mid 0.105 \right).
+\end{equation*}
+
+For the velocity anisotropy parameter $\beta_z$ we will again employ a uniform prior 
+\begin{equation*}
+p(\beta) = \mathscr{U}(-0.5,+0.5)
+\end{equation*}
+to exclude very unrealistic anisotropies. The full prior used is then
+\begin{eqnarray*}
+&&p(\Upsilon_\text{I,*},r_s,v_{200},\beta) \\
+&&= \frac{1}{\ln\left( 10 r_s\right)} p(\log c_{200} \mid v_{200}) \cdot p(v_{200}) \cdot p(\beta), 
+\end{eqnarray*}
+where the factor $1/\ln\left( 10 r_s\right)$ is the Jacobian of the transformation from the halo parameters $(v_{200},\log c_{200})$ to $(v_{200},r_s)$.
+
 %==============
-\begin{figure*}
+\begin{figure}
 \centering
-\includegraphics[width=0.7\linewidth]{fig/B4_rms_rot_curves_best_model.ps}
+  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_vcirc.ps}
+  \caption{Circular velocity curve. \Wilma{[TO DO: Write caption]}}
+  \label{fig:modelB4_vcirc}
+\end{figure}
+
+%==============
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{fig/B4_rms_rot_curves_best_model.ps}
 \caption{Generating the rotation curve from the JAM model with NFW halo and constant velocity anisotropy with the mean parameters in Table \ref{tab:modelB4_bestfit} and with the best fit rotation parameter $\kappa' = 0.76$ in Equation \eqref{eq:kappa_profile} (red solid lines).
@@
 \label{fig:modelB4_vrot}
-\end{figure*}
+\end{figure}
 %==============
@@
 The mean parameters are summarized in Table \ref{tab:modelB4_bestfit}.
-We find that the best fit NFW halo strives to be more massive and with a higher concentration (due to a smaller $r_s$) than  proposed by the prior.
-At the same time the model prefers again very negative velocity anisotropies: The sample with the highest probability is pegged at the lower limit of the unifrom prior.
-Both, the concentrated halo and the low anisotropy are needed to reproduce the central dip of the $v_\text{rms}$ curve.
-There are slight covariances between $\Upsilon_\text{I,*}$,  $r_s$ and $\beta_z$: The smaller the dark matter contribution in the center (i.e., the larger $\Upsilon_\text{I,*}$), the less concentrated is the halo (i.e., the larger $r_s$), the more velocity anisotropy is needed to reproduce the central dip.
-As the effect of $v_{200}$ is mostly at larger radii, this parameter doesn't show any covariances - but is also mostly constrained by the prior.
-\Wilma{[TO DO: Mention the following later in the text: "The $v_\text{rms}$ curve corresponding to the mean best fit values from Table \ref{tab:modelB4_bestfit} is shown in the first panel of Figure \ref{fig:modelB4_vrot}."]} Figure \ref{fig:modelB4_models} illustrates the range of parameters fitting the data according to the full posterior probability function.
+We find that the best fit NFW halo strives to be more massive and with a higher concentration (due to a smaller $r_s$) than  proposed by the priors.
+The model also prefers  very negative velocity anisotropies.
+Both, the high halo concentration and low $\beta_z$, are needed to reproduce the central dip of the $v_\text{rms}$ curve.
+There are slight covariances between $\Upsilon_\text{I,*}$,  $r_s$ and $\beta_z$: The smaller the DM contribution in the center (i.e., the larger $\Upsilon_\text{I,*}$), the less concentrated is the halo (i.e., the larger $r_s$), the more velocity anisotropy is needed to reproduce the central dip.
+As the effect of $v_{200}$ is mostly at larger radii, this parameter doesn't show any covariances, but is also mostly constrained by the prior.
+Figure \ref{fig:modelB4_models} illustrates the range of models fitting the data according to the full posterior probability distribution.
 The model fits the $v_\text{rms}$ data in the inner regions quite well (Figure \ref{fig:modelB4_vrms}) and is also consistent with the Einstein mass (see Figure \ref{fig:modelB4_enclMass}).
-The extrapolation of the model to larger radii however overestimates the data, does not exhibit a drop around $\sim 6''$ at all and seems to be therefore overall too massive.\\
+The extrapolation of the model to larger radii however overestimates the data, does not exhibit a drop around $\sim 6''$ at all and seems to be therefore overall too massive.
 
-We also fitted a model with a cored logarithmic dark matter halo.
+We also fitted a model with a cored logarithmic DM halo.
 The cored halo models are in general slightly less massive than the NFW halo and therefore fit the outer regions of J1331 better.
-However, the density profile of the cored halo as well as the I-band light distribution within the plane drop as $\rho(r) \propto r^{-2}$, there is a strong degeneracy between the stellar mass and the dark matter.
+However, the density profile of the cored halo as well as the I-band light distribution within the plane drop as $\rho(r) \propto r^{-2}$, there is a strong degeneracy between the stellar mass and the DM.
 Overall, we were not able to obtain tight constraints on the cored logarithmic halo.
+
+\Wilma{[TO DO: Mention the following later in the text: "The $v_\text{rms}$ curve corresponding to the mean best fit values from Table \ref{tab:modelB4_bestfit} is shown in the first panel of Figure \ref{fig:modelB4_vrot}."]}
 

### 2015-11-23 docs/results_JAMwithNFW_v3.02.tex
Edited dynamical modelling results sections.

--- 2015-11-23 archive/v3/docs/results_JAMwithNFW_v3.01.tex
@@
 The grey diamonds mark a random sub-selection of 12 samples; the corresponding models are shown in Figure \ref{fig:modelB4_models}.
-\Wilma{[TO DO: Use $\text{km s}^{-1}$ instead of km/s]} \Wilma{[TO DO: More space between titles and upper axes tick labels.]}}
+\Wilma{[TO DO: Use $\text{km s}^{-1}$ instead of km/s]} \Wilma{[TO DO: More space between titles and upper axes tick labels.]} \Wilma{[TO DO: Maybe mention also: There are slight covariances between $\Upsilon_\text{I,*}$,  $r_s$ and $\beta_z$: The smaller the DM contribution in the center (i.e., the larger $\Upsilon_\text{I,*}$), the less concentrated is the halo (i.e., the larger $r_s$), the more velocity anisotropy is needed to reproduce the central dip.
+As the effect of $v_{200}$ is mostly at larger radii, this parameter doesn't show any covariances, but is also mostly constrained by the prior.
+]}}
 \label{fig:modelB4_triangle}
@@
 \centering
-  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_vcirc.ps}
-  \caption{Circular velocity curve. \Wilma{[TO DO: Write caption]}}
-  \label{fig:modelB4_vcirc}
-\end{figure}
-
-%==============
-\begin{figure}
-\centering
 \includegraphics[width=\linewidth]{fig/B4_rms_rot_curves_best_model.ps}
@@
 
-\paragraph{Result.} Figure \ref{fig:modelB4_triangle} shows the posterior probability distribution of the fit sampled with an MCMC.
+\paragraph{Result.} Figure \ref{fig:modelB4_triangle} shows the posterior probability distribution (pdf) of the fit sampled with an MCMC.
 Overplotted are also the priors used to constrain the NFW halo.
@@
 Both, the high halo concentration and low $\beta_z$, are needed to reproduce the central dip of the $v_\text{rms}$ curve.
-There are slight covariances between $\Upsilon_\text{I,*}$,  $r_s$ and $\beta_z$: The smaller the DM contribution in the center (i.e., the larger $\Upsilon_\text{I,*}$), the less concentrated is the halo (i.e., the larger $r_s$), the more velocity anisotropy is needed to reproduce the central dip.
-As the effect of $v_{200}$ is mostly at larger radii, this parameter doesn't show any covariances, but is also mostly constrained by the prior.
-Figure \ref{fig:modelB4_models} illustrates the range of models fitting the data according to the full posterior probability distribution.
-The model fits the $v_\text{rms}$ data in the inner regions quite well (Figure \ref{fig:modelB4_vrms}) and is also consistent with the Einstein mass (see Figure \ref{fig:modelB4_enclMass}).
+Figure \ref{fig:modelB4_models} illustrates the range of best fit models according to the extent of the pdf.
+The models fit the $v_\text{rms}$ data in the inner regions quite well (Figure \ref{fig:modelB4_vrms}) and are also consistent with the Einstein mass (see Figure \ref{fig:modelB4_enclMass}).
 The extrapolation of the model to larger radii however overestimates the data, does not exhibit a drop around $\sim 6''$ at all and seems to be therefore overall too massive.
@@
 The cored halo models are in general slightly less massive than the NFW halo and therefore fit the outer regions of J1331 better.
-However, the density profile of the cored halo as well as the I-band light distribution within the plane drop as $\rho(r) \propto r^{-2}$, there is a strong degeneracy between the stellar mass and the DM.
+However, the density profile of the cored halo as well as the I-band light distribution within the plane drop as $\rho(r) \propto r^{-2}$.
+There is therefore a strong degeneracy between the stellar mass and the DM.
 Overall, we were not able to obtain tight constraints on the cored logarithmic halo.
 
-\Wilma{[TO DO: Mention the following later in the text: "The $v_\text{rms}$ curve corresponding to the mean best fit values from Table \ref{tab:modelB4_bestfit} is shown in the first panel of Figure \ref{fig:modelB4_vrot}."]}
-
-\paragraph{Rotation curve.} Following the procedure in Section \ref{sec:model_JAM} we find the rotation curve from the best fit mean model in Table \ref{tab:modelB4_bestfit} by fitting the rotation parameter $\kappa'$ to the symmetrized $v_\text{rot}$ data within $R' = 3.5''$.
-The best fit with $\kappa' = 0.76$ is shown in the second panel of Figure \ref{fig:modelB4_vrot}.
-Given in the first panel the best fit to $v_\text{rms}$, the third panel shows the dispersion that follows from $\sigma = \sqrt{v_\text{rms}^2 - v_\text{rot}^2}$.
+\paragraph{Rotation curve.} We generate a rotation curve from the best fit mean model in Table \ref{tab:modelB4_bestfit}, whose $v_\text{rms}$ curve is shown in the first panel of Figure \ref{fig:modelB4_vrot}.
+Following the procedure in Section \ref{sec:model_JAM}, we find the rotation curve by fitting the rotation parameter $\kappa'$ to the symmetrized $v_\text{rot}$ data within $R' = 3.5''$.
+The best fit with $\kappa' = 0.76$ is given in the second panel of Figure \ref{fig:modelB4_vrot}.
+The third panel shows the dispersion that follows from $\sigma = \sqrt{v_\text{rms}^2 - v_\text{rot}^2}$.
 Our assumptions for $\kappa(R)$ nicely reproduce a $v_\text{rot}$ model with counter-rotating core.
 Although we fitted $v_\text{rot}$ only to the inner regions, the extrapolation to large radii fits the data also very well.
-While the dispersion $\sigma$ in the center fits by construction quite good, there is a huge discrepancy at large radii.
-The predicted dispersion is much larger than the data; we would expect the disk rotationally supported and therefore have a low velocity dispersion; especially dispersions as high as $\sim 200~\text{km s}^{-1}$ are more likely to be observed in the pressure supported bulges of galaxies.
-There \emph{might} be something unexpeted with the $\sigma$ measurements around $\sim 5''$, but at large radii the the best fit model NFW halo is simply too massive.
+
+While the dispersion $\sigma$ in the center fits by construction quite good, the predicted dispersion is much larger than the data.
+We would expect the disk rotationally supported and therefore have a low velocity dispersion; especially dispersions as high as $\sim 200~\text{km s}^{-1}$ are more likely to be observed in the pressure supported bulges of galaxies.
+There might be something unexpected with the $\sigma$ measurements around $\sim 5''$, but at large radii the the best fit model NFW halo is simply too massive.

### 2015-11-23 docs/results_JAMwithSB_v3.01.tex
Edited dynamical modelling results sections.

@@
 
-\paragraph{JAM with lens mass model.} Our first JAM model uses the mass distribution which we found from lensing constraints in Section \ref{sec:results_lensing} to generate an independent prediction for the $v_\text{rms}$ curve following the procedure in Section \ref{sec:model_JAM}.
-In addition to the flat rotation curve model with $\alpha = 1$ in Table \ref{tab:bestfitlensmodel}, we also investigate a lens model, which was found as a best fit to the lensing images when assuming a slightly rising rotation curve slope of $\alpha=1.1$.
+In this section we create dynamical models for J1331 following the procedure in Section \ref{sec:model_JAM}.
+We use the deprojected surface brightness MGE from Table \ref{tab:MGEF814W} for the tracer distribution $\nu(R,z)$ and to generate mass models $\rho(R,z)$.
+The only exception is the first test, where the mass model comes from lensing constraints.
+
+\paragraph{JAM with lens mass model.} We make an independent prediction for the $v_\text{rms}$ curve by evaluating Equation \Wilma{[TO DO]} (with $\beta_z = 0$) for the lens mass model in Table \ref{tab:bestfitlensmodel} ($\alpha = 1$, flat rotation curve).
+In addition, we also calculate a  $v_\text{rms}$ curve for a lens model which was found analogously, but assumed a slightly rising rotation curve slope of $\alpha=1.1$.
 The predictions are compared with the data in Figure \ref{fig:JAM_modelL}.
-The agreement between the lensing prediction and the observed kinematics within $R' \sim 3''$ is striking.
-The $\alpha = 1$ model fits the wings around $R_\text{eff}$, while the $\alpha > 1$ model recreates the observed central dip.
-This is in concordance with observations in other galaxies, where also $\alpha<1$ at large radii.
-Our lensing model assumes $\alpha(R')=\text{const}$, although these results suggest, that a model with variable $\alpha(R')$ might fit even better, and maybe also reproduce the sharp drop in $v_\text{rms}$ around $R' \sim 3''$.
+The agreement within $R' \sim 3''$ is striking: The $\alpha > 1$ model recreates the observed central dip, while the $\alpha = 1$ model fits the wings around $R_\text{eff}$.
+This is in concordance with observations in other galaxies.
+For $R'> R_\text{eff}$ we would expect $\alpha<1$.
+Our lensing model assumes $\alpha(R')=\text{const}$, although Figure \ref{fig:JAM_modelL} suggests, that a model with variable $\alpha(R')$ might fit even better, and maybe also reproduce the sharp drop in $v_\text{rms}$ around $R' \sim 3''$.
 We note however, that the most reliable constraint is around $R_\text{ein}$.
@@
 \Wilma{[TO DO: Add Note that outside Rein extrapolation.]} The red solid line corresponds to the lens model for a flat rotation curve ($\alpha = 1$) in Table \ref{tab:bestfitlensmodel}; the green line is a best fit lens model found analogously from the image positions, but for a fixed rotation curve slope of $\alpha = 1.1$.
-For the JAM modelling a best fit MGE to the lens mass models were used, as well as the observed surface brightness MGE in Table \ref{tab:MGEF814W}, assuming velocity isotropy $\beta_z = 0$ and an inclination of $i = 70^\circ$.The red and black dotted lines are the Einstein radius and the effective half-light radius, respectively.
-\Wilma{[TO DO: Replace arcsec with '' in panel d)]} \Wilma{[TO DO: Use $\text{km s}^{-1}$ instead of km/s]}}
+For the JAM modelling a best fit MGE to the lens mass models were used, as well as the observed surface brightness MGE in Table \ref{tab:MGEF814W}, assuming velocity isotropy $\beta_z = 0$ and an inclination of $i = 70^\circ$.The red and black dotted lines are the Einstein radius and the effective half-light radius, respectively.}
   \label{fig:JAM_modelL}
@@
 The ``best'' fit is $\Upsilon_\text{I,tot}^\text{dyn} = 4.8 \pm 0.1$ and $\beta_z = -0.5$, where the latter is however pegged at the lower limit of the allowed value range.
-This is obviously not a good model.
-\Wilma{[TO DO: Replace arcsec with '' in panel d)]} \Wilma{[TO DO: Use $\text{km s}^{-1}$ instead of km/s]}}
+This is obviously not a good model.}
   \label{fig:JAM_modelA2}
@@
 
-\paragraph{JAM with "mass-follows-light" and velocity anisotropy.} Our second JAM model is a mass-follows-light model, which are often used in dynamical JAM modelling (e.g., \citet{GlennEC,Cap06}), where the mass distribution is generated by multiplying the intrinsic light distribution $\nu(R,z)$ (the MGE given in Table \ref{tab:MGEF814W} deprojected according to the inclination) by a constant total mass-to-light ratio  $\Upsilon_\text{I,tot}^\text{dyn}$.
-This assumes that the dark matter is always a constant fraction of the total matter distribution within the region covered by the kinematics.
-This simplified model sometimes gives good representations of the inner parts of galaxies, where the stellar component dominates.
-Testing this model for J1331 is also motivated by our findings from lensing in Section \ref{sec:results_lensing}, where around the Einstein radius total and luminous mass seem to have a similar distribution.
-\\In addition to the free fit parameter  $\Upsilon_\text{I,tot}^\text{dyn}$, we also allow for a overall constant but non-zero velocity anisotropy $\beta_z$.
-The best fit is found by minimizing $\chi^2$ between the $v_\text{rms}$ data and model prediction and is demonstrated in Figure \ref{fig:JAM_modelA2}.
-For $\beta_z$ we impose the fitting limits $\beta_z \in [-0.5,+0.5]$.
-While the outer parts of galaxies often show radially biased velocity anisotropy up to $\sim 0.5$ (from dynamical modelling of observed elliptical galaxies (e.g., \citet{Kronawitter2000}) and cosmological simulations (e.g., \citet{2004MNRAS.352..535D,2001ApJ...557..533F}), the centers of galaxies are near-isotropic or have  negative velocity anisotropy \citep{2003ApJ...583...92G}.
-Only in extreme models (e.g., around in-spiralling supermassive black holes \citep{1997NewA....2..533Q}) velocity anisotropies as low as $\sim -1$ have been found.
-The best fit in Figure \ref{fig:JAM_modelA2} however strives to very negative velocity anisotropies to be able to get the deep central dip in the  $v_\text{rms}$ curve.
-But $\beta_z = -0.5$ is not even a remotely agreeable fit and lower anisotropies are not to be expected and realistic.
-We also tested radial profiles for $\beta_z(R)$ of the form proposed by \citet{BaesVanHese}, which was however equally unable to reproduce the data.
-We conclude, that this is due to the well-known degeneracy between anisotropy and mass profile \Wilma{[TO DO: REF]} and the mass-follows-light model is \emph{not} a good representation of the mass distribution in J1331's inner regions.
+\paragraph{JAM with "mass-follows-light" and velocity anisotropy.} The first JAM model that we fit to the observed $v_\text{rms}$ within $R'<5''$ is a mass-follows-light model.
+Mass-follows-light models are often used in dynamical JAM modelling (e.g., \citealt{GlennEC,Cap06}) and generate a mass distribution by multiplying the intrinsic light distribution $\nu(R,z)$ by a constant total mass-to-light ratio  $\Upsilon_\text{I,tot}^\text{dyn}$.
+This assumes that the DM is always a constant fraction of the total matter distribution within the region covered by the kinematics.
+This simplified mass model sometimes gives good representations of the inner parts of galaxies, where the stellar component dominates.
 
-\paragraph{JAM with increasing mass-to-light ratio.} In Section \ref{sec:results_lensing} we found from the lensing, that the light distribution might drop faster with radius than the mass distribution.
-This would correspond to a radially increasing total mass-to-light ratio.
-As velocity anisotropy alone cannot explain the observed kinematics in a simple a mass-follows-light model, we now allow for an mass-to-light ratio gradient in the JAM modelling to generate a mass model from the light distribution in Table \ref{tab:MGEF814W}.
-We do this by assigning each of the five Gaussians in the MGE its own total mass-to-light ratio $\Upsilon_{\text{I,tot,}i}$ and replace the total luminosity in Equation \eqref{eq:centralItotalL} $L_i$ with the Gaussians total Mass $M_i = \Upsilon_{\text{I,tot,}i} L_i$.
-We treat the five $\Upsilon_{\text{I,tot,}i}$ as free parameters and only require that $\Upsilon_{\text{I,tot,}j} \geq \Upsilon_{\text{I,tot,}i}$ when the corresponding $\sigma_j \geq \sigma_i$ to ensure an overall mass-to-light ratio that is increasing with radius.
+We also allow for a overall constant but non-zero velocity anisotropy $\beta_z$ in the model.
+The model parameters ($\Upsilon_\text{I,tot}^\text{dyn},\beta_z$) that fit the $v_\text{rms}$ data best are found using a $\chi^2$-fit and are demonstrated in Figure \ref{fig:JAM_modelA2}.
+
+For $\beta_z$ we imposed the fitting limits $\beta_z \in [-0.5,+0.5]$.
+While the outer parts of galaxies often show radially biased velocity anisotropy up to $\sim 0.5$ (from dynamical modelling of observed elliptical galaxies, e.g., \citet{Kronawitter2000}) and cosmological simulations (e.g., \citealt{2004MNRAS.352..535D,2001ApJ...557..533F}), the centers of galaxies are near-isotropic or have negative velocity anisotropy \citep{2003ApJ...583...92G}.
+Only in extreme models (e.g., around in-spiralling supermassive black holes, e.g., \citealt{1997NewA....2..533Q}) velocity anisotropies as low as $\sim -1$ have been found.
 
@@
 Shown is also the effective half-light ratio $R_\text{eff}$ (black dotted line).
-\Wilma{[TO DO: Replace arcsec with '' in panel d)]} \Wilma{[TO DO: Mention second axis only after 1st axis is explained.]} \Wilma{[TO DO: Use $\text{km s}^{-1}$ instead of km/s]}}
+\Wilma{[TO DO: Mention second axis only after 1st axis is explained.]}}
 \label{fig:modelG}
@@
 
-Figure \ref{fig:enclMass_modelG} shows the (local projected) mass-to-light ratio gradient generated by the best fit to the dynamics data, which rises from $\Upsilon_\text{I,tot} = 2.53$ in the center and approaches a value of $\Upsilon_\text{I,tot}$ outside of the fitted region at $R'\gtrsim 3''$ of $\Upsilon_\text{tot} = 7.60$.
-The central mass-to-light ratio is in agreement with to the mass-to-light ratio $\Upsilon_\text{I,*}^\text{chab} = 2.5 \pm 0.6$, given in Table \ref{tab:previousresults} based on the results of \citet{SWELLSI} assuming a stellar population with an \citet{Chabrier2003} initial mass-function (IMF, see also Section \ref{sec:MLdiscussion}).
-When assuming that galaxy bulges are generally older and redder in the center \Wilma{[TO DO: REF]}, i.e., $\Upsilon_\text{I,*}$ is rather dropping with increasing radius than increasing, the strong rise of $\Upsilon_\text{I,tot}(R')$ might be due to a strong contribution of dark matter in J1331.
+The best fit in Figure \ref{fig:JAM_modelA2} however strives to very negative $\beta_z$ to be able to reproduce the deep central dip in the  $v_\text{rms}$ curve.\footnote{Without limiting the fitting range, the best fit would be a unrealistically low $\beta_z \sim -2$.} But $\beta_z = -0.5$ is not even a remotely agreeable fit and lower anisotropies are not to be expected or realistic.
+We also tested radial profiles for $\beta_z(R)$ of the form proposed by \citet{BaesVanHese}, which was however equally unable to reproduce the data.
+We conclude, that this is due to the well-known degeneracy between anisotropy and mass profile \Wilma{[TO DO: REF]} and the mass-follows-light model is \emph{not} a good representation of the mass distribution in J1331's inner regions.
 
-Figure \ref{fig:JAM_modelG} shows that the best fit model nicely reproduces the central dip in the $v_\text{rms}$ curve, even though it has slight problems fitting the drop around $R' \sim 4''$.
+\Wilma{[TO DO: Make sure that we explain somewhere, why we model only in the inner regions]}
+
+\paragraph{JAM with increasing mass-to-light ratio.} In Section \ref{sec:results_lensing} we found from lensing constraints, that the light distribution might drop faster with radius than the mass distribution.
+This could correspond to a radially increasing total mass-to-light ratio.
+As velocity anisotropy alone cannot explain the observed kinematics in a simple a mass-follows-light model, we now allow for a mass-to-light ratio gradient in the JAM modelling.
+We therefore generate a mass model from the light distribution in Table \ref{tab:MGEF814W} by assigning each of the five Gaussians in the MGE its own total mass-to-light ratio $\Upsilon_{\text{I,tot,}i}$ and replace the total luminosity in Equation \eqref{eq:centralItotalL} $L_i$ with the Gaussians total Mass $M_i = \Upsilon_{\text{I,tot,}i} L_i$.
+We treat the five $\Upsilon_{\text{I,tot,}i}$ as free fit parameters and only require that $\Upsilon_{\text{I,tot,}j} \geq \Upsilon_{\text{I,tot,}i}$ when the corresponding $\sigma_j \geq \sigma_i$ to ensure that the overall mass-to-light ratio is increasing with radius.
+
+Figure \ref{fig:enclMass_modelG} shows the best fit (projected local) mass-to-light ratio profile, which rises from $\Upsilon_\text{I,tot} = 2.53$ in the center and approaches a value of $\Upsilon_\text{I,tot} = 7.60$ outside of the fitted region at $R'\gtrsim 3''$.
+The central mass-to-light ratio is in agreement with the mass-to-light ratio $\Upsilon_\text{I,*}^\text{chab} = 2.5 \pm 0.6$, given in Table \ref{tab:previousresults} based on the results of \citet{SWELLSI} assuming a stellar population with a \citet{Chabrier2003} IMF (see also Section \ref{sec:MLdiscussion}).
+When assuming that galaxy bulges are in general older and redder in the center \Wilma{[TO DO: REF]}, i.e., $\Upsilon_\text{I,*}$ is more likely to drop with radius than to rise, the strong increase of $\Upsilon_\text{I,tot}(R')$ might be due to a strong contribution of dark matter in J1331.
+
+Figure \ref{fig:JAM_modelG} shows that the best fit model nicely reproduces the central dip in the $v_\text{rms}$ curve, even though it has difficulties fitting the drop around $R' \sim 4''$.
 The latter might be because we only allowed the $\Upsilon_\text{I,tot}(R')$ to rise.

### 2015-11-23 docs/results_lensing_v3.01.tex
Edited dynamical modelling results sections.

@@
+%========================================================================================
+\begin{table}
+\centering
+\begin{minipage}{70mm}
+\begin{tabular}{r|rrrr|c}
+\hline
+  & A & B & C & D & G\\\hline
+$x_i$ [pixel] & 12.1 & -8.5 & 21.7 & -3.3 & 0.5 $\pm \sqrt{2}$ \\
+$y_i$ [pixel] & 16.6 & -10.4 & -0.5 & 19.2 & 0.5 $\pm \sqrt{2}$ \\
+\hline
+\end{tabular}
+\caption{Positions of the lensing images (A-D) and the galaxy center (G) in Figure \ref{fig:lens_just_imgpos}.
+The image positions were determined from the lens subtracted image for J1331 in Figure 4 of \citet{SWELLSIII}, rotated to the $(x,y)$ coordinate system in Figure \ref{fig:lens_just_imgpos}.
+The pixel scale is 1 pixel = $0.05''$ and the error of each image position is $\pm$ 1 pixel.}
+\label{tab:lenspos}
+\end{minipage}
+\end{table}
+%========================================================================================
+
 \subsection{Mass distribution from lensing} \label{sec:results_lensing}
+
+\Wilma{[TO DO: Intro Sentence]}
 
@@
 
-\begin{table}
+%========================================================================================
+
+\begin{figure}
 \centering
-\begin{minipage}{70mm}
-\begin{tabular}{r|rrrr|c}
-\hline
-  & A & B & C & D & G\\\hline
-$x_i$ [pixel] & 12.1 & -8.5 & 21.7 & -3.3 & 0.5 $\pm \sqrt{2}$ \\
-$y_i$ [pixel] & 16.6 & -10.4 & -0.5 & 19.2 & 0.5 $\pm \sqrt{2}$ \\
-\hline
-\end{tabular}
-\caption{Positions of the lensing images (A-D) and the galaxy center (G) in Figure \ref{fig:lens_just_imgpos}.
-The image positions were determined from the lens subtracted image for J1331 in Figure 4 of \citet{SWELLSIII}, rotated to the $(x,y)$ coordinate system in Figure \ref{fig:lens_just_imgpos}.
-The pixel scale is 1 pixel = $0.05''$ and the error of each image position is $\pm$ 1 pixel.}
-\label{tab:lenspos}
-\end{minipage}
-\end{table}
+  \includegraphics[width=\linewidth]{fig/lens_all_in_one.ps}
+\caption{Lensing model (Table \ref{tab:bestfitlensmodel}) found as best fit to the image positions.
+In the background we show the central region of J1331 in the F450W filter, subtracted by an IRAF \emph{ellipse} model of the F450W surface brightness and smoothed to remove noise smaller than the PSF.
+The brightness peaks of the four lensing images and the galaxy center (Table \ref{tab:lenspos}) are marked as red dots.
+For the best fit lens model we show the Einstein radius (red dotted circle) and the critical curve (red solid line), which are located in the lens plane.
+We also show the caustic (green solid line) corresponding to the critical curve and best fit source position (green dot), which are located in the source plane.
+For $\alpha=1$ the critical curve is a contour of constant surface density of the mass model.
+The grey  lines show contours of the time delay surface given by Equation \eqref{eq:timedelay}.
+Not only the position of the extrema, but also their shape is consistent with the observed, extended images, even though we did not use information about the image shape in the analysis.}
+\label{fig:???}
+\end{figure}
+
+%========================================================================================
 
@@
 %========================================================================================
-
 \begin{table*}
@@
 \end{table*}
-
 %========================================================================================
-
-\begin{figure*}
-\centering
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[width=.9\linewidth]{fig/lens_einstein.ps}
-  \caption{Best fit critical curve, Einstein radius, caustic, source position.}
-  \label{fig:lensbestfiteinsteincurves}
-\end{subfigure}%
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[width=.9\linewidth]{fig/lens_timedelay.ps}
-  \caption{Time delay surface.}
-  \label{fig:lensbestfittimedelay}
-\end{subfigure}
-\caption{Best fit lens model in Table \ref{tab:bestfitlensmodel} found from the image positions.
-In the background we show the central region of J1331 in the F450W filter, subtracted by an IRAF \emph{ellipse} model of the F450W surface brightness and smoothed by boxcar smoothing of the order of the PSF size.
-The four bluish lensing images are clearly visible and we mark the brightness peaks in Table \ref{tab:lenspos} as well as the galaxy center (G) as red dots.
-The Einstein radius of the best fit lens model is shown as a red dotted circle.
-\emph{Panel (a)} Besides the image positions and Einstein radius, the critical curve (red solid line) is shown in the lens plane.
-The caustic (green solid line) corresponding to the critical curve and best fit source position (green dot), which are both located in the source plane, are shown as well.
-For $\alpha=1$ (which we assumed for our lens model) the critical curve is a contour of constant surface density of the mass model.
-\emph{Panel (b)} The yellow lines show (arbitrary) contours of the time delay surface given by Equation \eqref{eq:timedelay} of the best fit lens model.
-Not only the position of the extrema, but also their shape is consistent with the observed, extended images, even though we did not use information about the image shape in the analysis.
-The other two right blobs (north east of A, south east of B) might be star forming regions of the background galaxy as well.
-\Wilma{[TO DO: Add A, B, C, D in the figure to make clear which image is which.]} \Wilma{[TO DO: Combine in one figure.
-Make all lines except time delay surface very thick.]} \Wilma{[TO CO: Mention: in which we smooth out noise smaller than the PSF]}}
-\label{fig:???}
-\end{figure*}
-
-%========================================================================================
-
-To estimate how the uncertainties in the determination of image positions and galaxy center affect the results, we sample random positions from two-dimensional Normal distributions with peaks and standard deviations according to Table \ref{tab:lenspos}.
-Model fits to many sampled image positions lead to probability distributions for the best fit shape parameters and Einstein quantities; peak and standard deviations are given in the second column of Table \ref{tab:bestfitlensmodel}.
-We constrain the Einstein radius to within 2\%, $R_\text{ein} = (0.91 \pm 0.02)''$ and the projected mass within the critical curve with a relative error of 4\%, $M_\text{crit} =(7.9\pm0.3)\cdot 10^{10} M_\odot$.
-Our measurement of $R_\text{ein}$ is consistent with that from \citet{SWELLSIII}, $R_\text{ein,SWELLS} = (0.96 \pm 0.04)''$ (which used a singular isothermal ellipsoid as lens mass model and the intermediate-axis convention of the critical curve as the Einstein radius).
-The relative difference between our critical mass and that of \citet{SWELLSIII}, $M_\text{crit,SWELLS} =(8.86\pm0.61)\cdot 10^{10} M_\odot$, is 13\%.
 
@@
 
+To estimate how the uncertainties in the determination of image positions and galaxy center affect the results, we sample random positions from two-dimensional Normal distributions with peaks and standard deviations according to Table \ref{tab:lenspos}.
+Model fits to many sampled image positions lead to probability distributions for the best fit shape parameters and Einstein quantities; peak and standard deviations are given in the second column of Table \ref{tab:bestfitlensmodel}.
+We constrain the Einstein radius to within 2\%, $R_\text{ein} = (0.91 \pm 0.02)''$ and the projected mass within the critical curve with a relative error of 4\%, $M_\text{crit} =(7.9\pm0.3)\cdot 10^{10} M_\odot$.
+Our measurement of $R_\text{ein}$ is consistent with that from \citet{SWELLSIII}, $R_\text{ein,SWELLS} = (0.96 \pm 0.04)''$ (which used a singular isothermal ellipsoid as lens mass model and the intermediate-axis convention of the critical curve as the Einstein radius).
+The relative difference between our critical mass and that of \citet{SWELLSIII}, $M_\text{crit,SWELLS} =(8.86\pm0.61)\cdot 10^{10} M_\odot$, is 13\%.
+
 \paragraph{Comparison with light distribution.} The surface mass distribution as predicted by the best fit lens model (Table \ref{tab:bestfitlensmodel}) is shown in Figure \ref{fig:lenscomparemass}.

### 2015-11-23 docs/results_photometry_v3.02.tex
Edited dynamical modelling results sections.

@@
+%============================================================================
+\begin{table}
+\centering
+\caption{Galaxy Parameters of J1331.}
+\begin{tabular}{lllr}
+\hline
+redshift \citep{SWELLSIII}                 & $z_d$ & 0.113 \\
+angular diameter distance & $D_d$ [Mpc] & 414 \\
+scaling                   & 1 kpc / 1 $''$ & 2.006 \\
+position angle from North          & $\phi$ [degrees] & $42.90^\circ$\\
+average axis ratio & $q'$ & 0.598\\
+average ellipticity & $\epsilon = 1 - q'$ & 0.402 \\
+apparent I-band magnitude & $m_\text{I}$ [mag] & 15.77 \\
+total I-band luminosity & $L_\text{tot,I}$ [$10^{10} L_\odot$] & 5.6 \\
+effective half-light radius & $R_\text{eff}$ [$''$] & 2.6 \\
+& $R_\text{eff}$ [pc]& 5.2 & \\
+\hline
+\end{tabular}
+\label{tab:galaxyparameters}
+\end{table}
+%============================================================================
+
 \subsection{Surface photometry for J1331 with MGEs} \label{sec:MGE_results}
@@
 We use the HST image in the F814W (I-band) filter (Figure \ref{fig:F814W}) because J1331's central stellar component appears at longer wavelengths (a) smoother and more extended than in the F450W filter (Figure \ref{fig:F450W}), as it is less sensitive to young clumpy star-forming regions, (b) much brighter than the bluish lensing images, and (c) the imaging is less prone to extinction.
+
+\paragraph{PSF for the HST/F814W filter.} The one-dimensional MGE in Equation \eqref{eq:PSFgeneral} is fitted to the radial profile of a synthetic image of the HST/F814W filter PSF, ignoring diffraction spikes and using the code by \citet{Cap02}.
+The MGE parameters of the normalized PSF model are given in Table \ref{tab:PSFMGEF814W}.
 
@@
 
-\paragraph{PSF for the HST/F814W filter.} The one-dimensional MGE in Equation \eqref{eq:PSFgeneral} is fitted to the radial profile of a synthetic image of the HST/F814W filter PSF, ignoring diffraction spikes and using the code by \citet{Cap02}.
-The MGE parameters of the normalized PSF model are given in Table \ref{tab:PSFMGEF814W}.
-
 \paragraph{MGE for the inner regions.} We fit a MGE to J1331's smooth central region within $\sim 5''$ from the HST/WFPC2/WF3/F814W image (Figure \ref{fig:F814W}).
 Bright objects close to the bulge (blobs possibly belonging to the background galaxy and parts of the foreground spiral arm) were masked during the fit.
-J1331's galaxy center, position angle and average apparent ellipticity (see Table \ref{tab:galaxyparameters}) are found from the images weighted first and second moment.
+J1331's galaxy center, position angle (with respect to North through East) and average apparent ellipticity (see Table \ref{tab:galaxyparameters}) are found from the images weighted first and second moment.
 The MGE fit splits the image in annuli with the given ellipticity and position angle and sectors of $5^\circ$ width and fits an 5-Gaussian MGE of the form in Equation \eqref{eq:MGEgeneral} convolved with the PSF MGE in Table \ref{tab:PSFMGEF814W} to it.
@@
 This MGE is not used for dynamical modelling, because the dynamics in the outer regions are strongly affected by non-axisymmetries (e.g., spiral arms).
-We use it, however, to estimate the galaxy's total luminosity and effective radius, and to get a prediction for the dynamics of the outer regions.}
+We use it, however, to estimate the galaxy's total luminosity and effective radius, and to get a prediction for the dynamics of the outer regions.
+\Wilma{[TO DO: No dotted line]}}
 \end{figure*}
+%============================================================================
+
+%============================================================================
+\begin{table*}
+\centering
+\caption{Parameters of the best fit MGE to the F814W surface brightness of J1331 in Figure \ref{fig:MGEinnerRegions}.
+The fit is best inside an radius of $5''$.
+The position angle is given in Table \ref{tab:galaxyparameters}.
+This MGE is used in the dynamical modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}.
+The first column gives for each Gaussian the total F814W luminosity in Equation \eqref{eq:centralItotalL} in units of counts.
+The second column is the corresponding I-band peak surface brightness in Equation \eqref{eq:MGEgeneral} in units of a luminosity surface density.
+The third and fourth column give the dispersion and the last column the axis ratio of the Gaussian in Equation \eqref{eq:MGEgeneral}.}
+\begin{tabular}{cccccc}
+\hline
+ & total luminosity  & surface density & \multicolumn{2}{c}{Gaussian dispersion} & axis ratio\\
+$i$  & $L_i$ [counts] & $I_{0,i}$ [$L_\odot$/pc$^2$] & $\sigma_i$ [$''$] & $\sigma_i$ [kpc] & $q'_i$\\\hline
+1  &     9425.96 &      20768.  &  0.051   & 0.103  & 1.00\\
+2  &    13173.0 &        3161.2 &  0.178   & 0.358  & 0.76\\
+3  &    40235.0 &        1588.2 &  0.503   & 1.008  & 0.58\\
+4  &    67755.2 &         502.25&  1.180   & 2.368  & 0.56\\
+5  &    203677. &         136.51&  3.891   & 7.805  & 0.57\\\hline
+\end{tabular}
+\label{tab:MGEF814W}
+\end{table*}
 %============================================================================
@@
 
-%============================================================================
-\begin{table*}
-\centering
-\caption{J1331's F814W MGE: Parameters of the best fit MGE to the F814W surface brightness of J1331 in Figure \ref{fig:F814W}.
-The fit is best inside an radius of $5''$.
-The galaxy center and position angle, which gives the orientation of the MGE with respect to the original image, are given in Table \ref{tab:galaxyparameters}.
-This MGE is used in the dynamical modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}.
-The first column gives the total F814W luminosity of the Gaussian in Equation \eqref{eq:centralItotalL} in units of counts.
-The second column is the corresponding I-band peak surface brightness in Equation \eqref{eq:MGEgeneral} in units of a luminosity surface density, calculated from the first column following the procedure described in Section \ref{sec:MGE_results}.
-The third and fourth column give the dispersion and the last column the axis ratio of the Gaussian in Equation \eqref{eq:MGEgeneral}.}
-\begin{tabular}{cccccc}
-\hline
- & total luminosity  & surface density & \multicolumn{2}{c}{Gaussian dispersion} & axis ratio\\
-$i$  & $L_i$ [counts] & $I_{0,i}$ [$L_\odot$/pc$^2$] & $\sigma_i$ [$''$] & $\sigma_i$ [kpc] & $q'_i$\\\hline
-1  &     9425.96 &      20768.  &  0.051   & 0.103  & 1.00\\
-2  &    13173.0 &        3161.2 &  0.178   & 0.358  & 0.76\\
-3  &    40235.0 &        1588.2 &  0.503   & 1.008  & 0.58\\
-4  &    67755.2 &         502.25&  1.180   & 2.368  & 0.56\\
-5  &    203677. &         136.51&  3.891   & 7.805  & 0.57\\\hline
-\end{tabular}
-\label{tab:MGEF814W}
-\end{table*}
-%============================================================================
-
 \paragraph{Inclination.} To estimate the inclination of J1331 with respect to the observer, we use the observed axis ratio of the flattest ellipse in the IRAF \emph{ellipse} model for J1331, which is $q'=0.42$.

### 2015-11-24 docs/results_JAMwithNFW_v3.02.tex
Legends in three figures; added lensing models in two of them.

@@
 The central regions are very well reproduced and we can also nicely predict the rotation curve at larger radii.
-Only at larger radii the $v_\text{rms}$ and $v_\text{rot}$ overestimate the measurements, probably due to a too massive NFW halo.
-\Wilma{[TO DO: Replace arcsec with '']} \Wilma{[TO DO: Use $\text{km s}^{-1}$ instead of km/s]}}
+Only at larger radii the $v_\text{rms}$ and $v_\text{rot}$ overestimate the measurements, probably due to a too massive NFW halo.}
 \label{fig:modelB4_vrot}

### 2015-11-24 docs/results_JAMwithSB_v3.01.tex
Legends in three figures; added lensing models in two of them.

@@
 \Wilma{[TO DO: Add Note that outside Rein extrapolation.]} The red solid line corresponds to the lens model for a flat rotation curve ($\alpha = 1$) in Table \ref{tab:bestfitlensmodel}; the green line is a best fit lens model found analogously from the image positions, but for a fixed rotation curve slope of $\alpha = 1.1$.
-For the JAM modelling a best fit MGE to the lens mass models were used, as well as the observed surface brightness MGE in Table \ref{tab:MGEF814W}, assuming velocity isotropy $\beta_z = 0$ and an inclination of $i = 70^\circ$.The red and black dotted lines are the Einstein radius and the effective half-light radius, respectively.}
+For the JAM modelling a best fit MGE to the lens mass models were used, as well as the observed surface brightness MGE in Table \ref{tab:MGEF814W}, assuming velocity isotropy $\beta_z = 0$ and an inclination of $i = 70^\circ$.The red and black dotted lines are the Einstein radius and the effective half-light radius, respectively.
+\Wilma{[TO DO: rewrite Caption.
+Maybe also rewrite text to acknowledge alpha=0.9]}}
   \label{fig:JAM_modelL}
@@
 The ``best'' fit is $\Upsilon_\text{I,tot}^\text{dyn} = 4.8 \pm 0.1$ and $\beta_z = -0.5$, where the latter is however pegged at the lower limit of the allowed value range.
-This is obviously not a good model.}
+This is obviously not a good model.
+\Wilma{[TO DO: Make Line purpel or yellow.]}}
   \label{fig:JAM_modelA2}

### 2015-11-24 docs/discussion_ML_v3.02.tex
Started rewriting the discussion.

We've presented different dynamical models for the central region of J1331. Some of them capture the observed kinematics, but none of them work at both small and large radii. In the following we discuss possible reasons, also by comparing our results to previous work.

\subsection{On J1331's central stellar mass-to-light ratio} \label{sec:MLdiscussion}

Some of the ambiguities in recovering J1331's matter distribution could be resolved by learning more about stellar populations with different IMFs in J1331. In particular, a sophisticated guess for the stellar mass-to-light ratio in the bulge could be compared to our very reliable measurement of the total mass-to-light ratio inside the Einstein radius (see Table \ref{tab:einsteinML}). This would then either support or contradict the presence of a significant amount of DM in the bulge.

Traditional choices for the IMF are the bottom-heavy IMF by \citet{Salpeter1955},
$$\xi(m) \propto m^{-x}, x=2.35,$$
where $\xi(m) \diff m$ is the number of stars with mass $m$ in $[m,m+\diff m]$, and the IMFs by \citet{2002Sci...295...82K} and \citet{Chabrier2003}, which are in agreement with each other and predict less low-mass stars.

\citet{Ferreras} found a relation between the central stellar velocity dispersion $\sigma_0$ in early-type galaxies and the IMF slope $x$; a higher $\sigma_0$ suggests a more bottom-heavy IMF. For a unimodal (Salpeter-like) IMF and $\sigma_0 \simeq 200~\text{km s}^{-1}$ in J1331 (see Figure \ref{fig:kinematics}) they predict $x \approx 2.33$, which is close to the standard Salpeter slope, also supported by \citet{2014MNRAS.438.1483S}. When assuming a bi-modal (Kroupa-equivalent-like) IMF, \citet{Ferreras} predict $x \approx 2.85$ for J1331's central velocity dispersion. This is more bottom-heavy than the standard \citet{2002Sci...295...82K} IMF. Overall, the central velocity dispersion suggests a rather bottom-heavy IMF in J1331's bulge and therefore large stellar mass-to-light ratio. \citet{SWELLSI} estimated J1331's stellar bulge mass given a Salpeter IMF and measured the I-band AB magnitude of the bulge. Transformed to a stellar I-band mass-to-light ratio their results would correspond to $\Upsilon_\text{I,*}^\text{sal} = 4.7 \pm 1.2$ (see Table \ref{tab:previousresults}).

We compare our findings of the stellar mass-to-light ratios with the study by \cite{SWELLSV}: They found that the bulge of J1331 has an IMF \emph{more} bottom-heavy than the Salpeter IMF from fitting a NFW halo to (1) the Einstein mass and (2) gas kinematics at larger radii $\gtrsim 8''$. In Section \ref{sec:results_JAM_NFW} we fitted a mass model with NFW halo to (1) the Einstein mass and (2) stellar kinematics within $\sim 3.5''$. Our best fit $\Upsilon_\text{I,*} = 4.2 \pm 0.2$ (see Table \ref{tab:modelB4_bestfit}) indicates a \emph{less} bottom-heavy IMF than the Salpeter IMF. \cite{SWELLSV} found systematically lower NFW halo masses ($v_\text{circ,halo}(5'') \sim 120~\text{km s}^{-1}$ according to their Figure 2) than we did ($v_\text{circ,halo}(5'') \sim 200~\text{km s}^{-1}$).

%==============
\begin{table*}
\centering
\begin{tabular}{cccccc}
\hline\hline
& & \multicolumn{2}{c}{Chabrier IMF} & \multicolumn{2}{c}{Salpeter IMF}\\
      &  $L$ [$10^{10}L_{\odot}$]                & $M_*$ [$10^{10}M_\odot$]               & $\Upsilon_\text{I,*}^\text{chab}$ & $M_*$ [$10^{10}M_\odot$] & $\Upsilon_\text{I,*}^\text{sal}$ \\\hline
bulge &   $3.10 \pm 0.15 $  & $7.8 \pm 1.8$ & $2.5 \pm 0.6$ & $14.5 \pm 3.7 $ & $4.7 \pm 1.2$ \\
disk  &   $2.35 \pm 0.11 $  & $2.9 \pm 0.7$ & $1.2 \pm 0.3$ & $5.2 \pm 1.1$ & $2.2 \pm 0.5$ \\
total &   $5.45 \pm 0.19$ & $10.6 \pm 1.9$& & $19.7 \pm 3.9$&\\\hline
\end{tabular}
\caption{Total I-band luminosity, stellar mass and mass-to-light ratio, calculated from the I-band AB magnitudes and stellar masses found for J133's bulge and disk by \citet{SWELLSI} (their table 2) for comparison with this work. The transformation from AB magnitudes to the Johnson-Cousins I-Band used the relation $I[\text{mag}] = I[\text{ABmag}] - 0.309$ from \citet{FG1994} (their table 2). For the conversion from apparent magnitude to total luminosity the redshift $z=0.113$ \citet{SWELLSIII} was turned into a luminosity distance using the cosmology by \citet{WMAP5cosm}. }
\label{tab:previousresults}
\end{table*}
%==============

\subsection{On J1331's central kinematics}

%==============
\begin{figure}
\centering
  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_vcirc.ps}
  \caption{Circular velocity curve. \Wilma{[TO DO: Write caption]}}
  \label{fig:vcirc_comparison}
\end{figure}
%==============

In Figure \ref{fig:vcirc_comparison} we compare the circular velocity curve found by \citet{SWELLSV} with a mass-follows-light model scaled to fit our Einstein mass (by multiplying the light distribution in Table \Wilma{[TO DO]} with $\Upsilon_\text{I,tot}^\text{ein} = 5.6$). Within $R < 5''$ they agree with each other.

The models in this work used more than just the Einstein mass to constrain the matter distribution at small radii: The lens mass model constrained also the shape of the mass distribution within the lensing image configuration at $R_\text{ein} \sim 1''$. The dynamical models used stellar kinematics inside $R' \simeq 3.5''$ \Wilma{[TO DO: Check]}. We compare the lens mass model's $v_\text{circ}$ (for $\alpha=1.0\pm 0.1$) with the NFW JAM model (Table \Wilma{[TO DO]}) in Figure \ref{fig:vcirc_comparison} as well. Within and around $R_\text{ein}$ they are consistent with each other, even though they where independently derived. They do not agree with the result by \citet{SWELLSV} and in Section \ref{sec:results_JAM_SB} we showed, that ``mass-follows-light'' is not a good model for J1331.

Overall, we were not able to find a consistent explanation for J1331's central $v_\text{rms}$ dip. It cannot be due to tangential velocity anisotropy in the center alone (see Section \ref{sec:results_JAM_SB}, Figure \ref{fig:JAM_modelA2}). It also cannot be explained by a strong contribution of DM inside the bulge together with a moderate tagential velocity anisotropy, because the corresponding DM halos would still be too massive to fit the data in the outer regions (see Section \ref{sec:results_JAM_NFW}, Figure \ref{fig:modelB4_vrms}]).

In Section \ref{sec:results_JAM_SB} we created a dynamical model from only the surface brightness distribution and an increasing mass-to-light ratio profile without additional DM halo. We found that such a model would be perfectly consistent with the lensing results and predict a total $\Upsilon_\text{I,tot}(R'\sim0) = 2.53$ in the center of J1331. This is very close to the stellar $\Upsilon_\text{I,*}^\text{Chabrier} = 2.5 \pm 0.6$ based on the estimates by \citet{SWELLSI} for the bulge stellar mass using the Chabrier IMF , i.e., less bottom-heavy (more bluish) population.

Another feature in the stellar kinematics, that none of our JAM models was able to reproduce in the slightest and which we therefore excluded in the modelling, was the dip in $v_\text{rms}$ around $\sim 6''$, which occurs around the transition from bulge to disk (see Figures \ref{fig:F814W} and \ref{fig:kinematics}).

The above discussion motivates the following speculation: In the absence of a strong DM contribution in the center, the overall stellar-mass-to-light ratio within the Einstein radius indicates a bottom-heavy IMF close to the Salpeter IMF, consistent with estimates from the velocity dispersion. At the same time the central dip can then be only explained, if there was an increase in stellar mass-to-light ratio with radius \textit{within} the bulge. \emph{If} there was a central stellar population with an IMF close to the \citet{Chabrier2003} IMF, surrounded by a more bottom-heavy population, the central stellar kinematics would be well explained and be fully consistent with the lensing results. (According to Figure \ref{fig:lenscompareboth} the lensing result might not predict a mass to light ratio gradient inside $R_\text{ein}$, but then again the mass slope $alpha=1$ was only weakly constrained.) The disk of J1331 has a lower $\Upsilon_\text{I,*}$ than the bulge (see Table \ref{tab:previousresults} according to \citet{SWELLSI}). Such a drop in $\Upsilon_\text{I,*}$ at the transition region from bulge to disk around $\sim 5''$ could lead to the observed drop in $v_\text{rms}$, while an increasing contribution of a lower mass DM halo at larger radii as found by \citet{SWELLSV}, would recover the kinematics in the out regions of J1331's disk.

\Wilma{[TO DO: Why are disk and bulge mass in SWELLS I different to the one in SWELLS IV??]}

### 2015-11-24 docs/discussion_v3.02.tex
Started rewriting the discussion.

--- 2015-11-24 docs/discussion_ML_v3.02.tex
@@
 
-We compare our findings of the stellar mass-to-light ratios with the study by \cite{SWELLSV}: They found that the bulge of J1331 has an IMF \emph{more} bottom-heavy than the Salpeter IMF from fitting a NFW halo to (1) the Einstein mass and (2) gas kinematics at larger radii $\gtrsim 8''$.
-In Section \ref{sec:results_JAM_NFW} we fitted a mass model with NFW halo to (1) the Einstein mass and (2) stellar kinematics within $\sim 3.5''$.
+We compare our results from Section \ref{sec:results_JAM_NFW} with the study by \citet{SWELLSV}: They found that the bulge of J1331 has an IMF \emph{more} bottom-heavy than the Salpeter IMF from fitting a NFW halo to (1) the Einstein mass and (2) gas kinematics at larger radii $\gtrsim 8''$.
+In Section we fitted a mass model with NFW halo to (1) the Einstein mass and (2) stellar kinematics within $\sim 3.5''$.
 Our best fit $\Upsilon_\text{I,*} = 4.2 \pm 0.2$ (see Table \ref{tab:modelB4_bestfit}) indicates a \emph{less} bottom-heavy IMF than the Salpeter IMF.
 \cite{SWELLSV} found systematically lower NFW halo masses ($v_\text{circ,halo}(5'') \sim 120~\text{km s}^{-1}$ according to their Figure 2) than we did ($v_\text{circ,halo}(5'') \sim 200~\text{km s}^{-1}$).
+
+We compare our result from Section \ref{sec:results_JAM_SB} with the findings from \citet{SWELLSI}: We created a dynamical model from only the surface brightness distribution and an increasing mass-to-light ratio profile without additional DM halo.
+We found that such a model would be perfectly consistent with the Einstein mass and predict a total $\Upsilon_\text{I,tot}(R'\sim0) = 2.53$ in the very center of J1331.
+This is close to the stellar $\Upsilon_\text{I,*}^\text{Chabrier} = 2.5 \pm 0.6$ based on the estimates by \citet{SWELLSI} for the bulge stellar mass using the Chabrier IMF , i.e., less bottom-heavy (more bluish) population.
 
@@
 
-In Section \ref{sec:results_JAM_SB} we created a dynamical model from only the surface brightness distribution and an increasing mass-to-light ratio profile without additional DM halo.
-We found that such a model would be perfectly consistent with the lensing results and predict a total $\Upsilon_\text{I,tot}(R'\sim0) = 2.53$ in the center of J1331.
-This is very close to the stellar $\Upsilon_\text{I,*}^\text{Chabrier} = 2.5 \pm 0.6$ based on the estimates by \citet{SWELLSI} for the bulge stellar mass using the Chabrier IMF , i.e., less bottom-heavy (more bluish) population.
-
 Another feature in the stellar kinematics, that none of our JAM models was able to reproduce in the slightest and which we therefore excluded in the modelling, was the dip in $v_\text{rms}$ around $\sim 6''$, which occurs around the transition from bulge to disk (see Figures \ref{fig:F814W} and \ref{fig:kinematics}).
 
-The above discussion motivates the following speculation: In the absence of a strong DM contribution in the center, the overall stellar-mass-to-light ratio within the Einstein radius indicates a bottom-heavy IMF close to the Salpeter IMF, consistent with estimates from the velocity dispersion.
+\subsection{On J1331's possible merger history}
+
+\Wilma{[TO DO: Remove minor in merger.]}
+
+J1331 has a large counter-rotating stellar core within $\sim 2''$.
+This suggests a process in J1331's past in which two components with angular momenta oriented in opposite directions were involved.
+Accretion of gas on retrograde orbits and subsequent star formation could lead to a younger and counter-rotating stellar population \Wilma{[TO DO: REF]}.
+However, to form enough stars such that the net rotation of the large and massive core is retrograde, a very large amount of gas would have had to be accreted by J1331---which is not very likely [TO DO: REF].
+
+Another scenario are galaxy mergers.
+Major mergers including large amounts of gas can form kinematically decoupled cores (KDCs), see e.g., \Wilma{[TO DO: REF: Lauren Hofman et al 2010 - read paper how this fits with the reverse color gradient]}.
+During a minor merger, the dense nucleus of a satellite galaxy on a retrograde orbit could survive the dissipationless accretion and could spiral to the core due to tidal friction \citep{1984ApJ...287..577K}.
+Usually large bulges of spirals or ellipticals are reddest in the center and become bluer further out.
+Because star formation in low-mass satellite galaxies occurred later than in massive galaxies \Wilma{[TO DO: REF]}, the merger remnant would now host a younger and bluer population with lower velocity dispersion within the older and redder bulge of the massive progenitor.
+Such a reverse color gradient could correspond to an increasing stellar mass-to-light ratio.
+
+The merger theory could explain and support our findings from dynamical modelling and the previous sections, that J1331 might have an increasing stellar mass-to-light ratio within its core.
+
+\subsection{On possible modelling failures and speculations how to resolve them}
+
+\Wilma{[TO DO: Include in discussion: Kinematic twist due to merger.
+Bulge and disk have different kinematic major axis, and the measured velocities in the disk, which are off from the major axis, are much lower than the actual maximum vcirc.
+Could explain the dips in the outer regions.]}
+
+Another effect that minor mergers can have on galaxies are a misalignement (warp) of the photometric and kinematic major axis \Wilma{[TO DO: REF]}.
+Would this be the case for J1331 the assumption of axisymmetry is not true anymore and our dynamical modelling would fail.
+
+Mergers also could have changed the 3D shape of the dark matter halo and the NFW halo was therefore not a good model for J1331's dark matter halo.
+We also tried to model J1331 with a cored logarithmic halo.
+However, due to degeneracies in the modelling, we were not able to either constrain the profile for a cored logarithmic halo, or to rule it out.
+
+\Wilma{[TO DO: Include in this discussion the findings from the color profile.]}
+
+\subsection{Future work}
+
+Standard JAM modelling approaches seem not to work for J1331.
+A JAM model for J1331 would need to allow for stellar mass-to-light ratio gradients within the galaxy, velocity anisotropy and a dark matter halo.
+Because of degeneracies between stellar and dark mass, and matter distribution and anisotropy profile, such a dynamical model would not lead to very tight constraints on the model parameters.
+A search for colour gradients in J1331 and/or investigation of absorption line indices could support or contradict the suspicion of the existence of stellar mass-to-light ratio gradients in J1331.
+Subsequently detailed stellar population analyses of the spectra taken along J1331's major axis should be conducted to constrain the mass-to-light ratio reliably.
+\Wilma{[TO DO: Include in this discussion the findings from the color profile.]}
+
+In addition, the dynamical modelling should use more of the available information on J1331 and fit dynamics (stellar and gas kinematics from \citet{SWELLSV}) simultaneously with the gravitational lensing (image positions, shape and even flux ratios) in a similar fashion to \citet{SWELLSIV}.
+To also model the extent, shape and flux of the lensing images, the method by \citet{2004ApJ...611..739T,2003ApJ...590..673W} could be employed, which models the surface brightness distribution of the images and source on a pixelated grid.
+However, for this to work a good model for the galactic extinction would be needed.
+
+High-resolution integral-field spectroscopy could help with this, allow for spatially resolved stellar population analysis and dynamical modelling in two dimensions.
+\Wilma{[TO DO: Include in this discussion that this could also help test, if the vrms dip is maybe because of twist, i.e., the measurements where not done along the major axis in the disk]} This would lead to much better understanding of J1331's structure and mass distribution and therefore answer questions on how minor mergers might modify spiral galaxies.
+
+\Wilma{[TO DO: Include in discussion: High resolution IFU: high spatial resolution --> to resolve small features.
+High spectral resolution --> because the velocity dispersion in the outer regions of the galaxy are very low and to measure them accurately, need high spectral resolution.]}
+
+\Wilma{[TO DO: Include the following discssion somwhere: The above discussion motivates the following speculation: In the absence of a strong DM contribution in the center, the overall stellar-mass-to-light ratio within the Einstein radius indicates a bottom-heavy IMF close to the Salpeter IMF, consistent with estimates from the velocity dispersion.
 At the same time the central dip can then be only explained, if there was an increase in stellar mass-to-light ratio with radius \textit{within} the bulge.
@@
 (According to Figure \ref{fig:lenscompareboth} the lensing result might not predict a mass to light ratio gradient inside $R_\text{ein}$, but then again the mass slope $alpha=1$ was only weakly constrained.) The disk of J1331 has a lower $\Upsilon_\text{I,*}$ than the bulge (see Table \ref{tab:previousresults} according to \citet{SWELLSI}).
-Such a drop in $\Upsilon_\text{I,*}$ at the transition region from bulge to disk around $\sim 5''$ could lead to the observed drop in $v_\text{rms}$, while an increasing contribution of a lower mass DM halo at larger radii as found by \citet{SWELLSV}, would recover the kinematics in the out regions of J1331's disk.
+Such a drop in $\Upsilon_\text{I,*}$ at the transition region from bulge to disk around $\sim 5''$ could lead to the observed drop in $v_\text{rms}$, while an increasing contribution of a lower mass DM halo at larger radii as found by \citet{SWELLSV}, would recover the kinematics in the out regions of J1331's disk.]}
 

### 2015-11-25 docs/discussion_v3.02.tex
Small changes in Discussion.

@@
 Overall, the central velocity dispersion suggests a rather bottom-heavy IMF in J1331's bulge and therefore large stellar mass-to-light ratio.
+
 \citet{SWELLSI} estimated J1331's stellar bulge mass given a Salpeter IMF and measured the I-band AB magnitude of the bulge.
-Transformed to a stellar I-band mass-to-light ratio their results would correspond to $\Upsilon_\text{I,*}^\text{sal} = 4.7 \pm 1.2$ (see Table \ref{tab:previousresults}).
+Transformed to a stellar I-band mass-to-light ratio, their results would correspond to $\Upsilon_\text{I,*}^\text{sal} = 4.7 \pm 1.2$ (see Table \ref{tab:previousresults}).
+This is not too far from $\Upsilon_\text{I,*} = 4.2 \pm 0.2$ (see Table \Wilma{[TO DO]}), which we found when including a NFW halo in the JAM modelling.
 
-We compare our results from Section \ref{sec:results_JAM_NFW} with the study by \citet{SWELLSV}: They found that the bulge of J1331 has an IMF \emph{more} bottom-heavy than the Salpeter IMF from fitting a NFW halo to (1) the Einstein mass and (2) gas kinematics at larger radii $\gtrsim 8''$.
+When \citet{SWELLSI} assumed a Chabrier IMF, their result translates to $\Upsilon_\text{I,*}^\text{chab} = 2.5 \pm 0.6$ (see Table \ref{tab:previousresults}).
+In Section \ref{sec:results_JAM_SB} we created a dynamical model from only the surface brightness distribution and an increasing mass-to-light ratio profile without additional DM halo.
+We found that such a model would be perfectly consistent with the Einstein mass, predict a total $\Upsilon_\text{I,tot}(R'\sim0) = 2.53$---being consistent with the Chabrier IMF estimate by \citet{SWELLSI}---and rise quickly to $\Upsilon_\text{I,tot}(R'\gtrsim R_\text{ein}) \gtrsim 6$.
+
+We also compare our results from Section \ref{sec:results_JAM_NFW} with the study by \citet{SWELLSV}.
+They found that the bulge of J1331 has an IMF \emph{more} bottom-heavy than the Salpeter IMF from fitting a NFW halo to (1) the Einstein mass and (2) gas kinematics at larger radii $\gtrsim 8''$.
 In Section we fitted a mass model with NFW halo to (1) the Einstein mass and (2) stellar kinematics within $\sim 3.5''$.
@@
 \cite{SWELLSV} found systematically lower NFW halo masses ($v_\text{circ,halo}(5'') \sim 120~\text{km s}^{-1}$ according to their Figure 2) than we did ($v_\text{circ,halo}(5'') \sim 200~\text{km s}^{-1}$).
-
-We compare our result from Section \ref{sec:results_JAM_SB} with the findings from \citet{SWELLSI}: We created a dynamical model from only the surface brightness distribution and an increasing mass-to-light ratio profile without additional DM halo.
-We found that such a model would be perfectly consistent with the Einstein mass and predict a total $\Upsilon_\text{I,tot}(R'\sim0) = 2.53$ in the very center of J1331.
-This is close to the stellar $\Upsilon_\text{I,*}^\text{Chabrier} = 2.5 \pm 0.6$ based on the estimates by \citet{SWELLSI} for the bulge stellar mass using the Chabrier IMF , i.e., less bottom-heavy (more bluish) population.
 
@@
 
+This could indicate that there might be a less bottom-heavy, more bluish population, with an IMF close to the Chabrier IMF, in the very center of J1331.
+
 \subsection{Future work}

### 2015-12-10 archive/v3/docs/discussion_v3.02.tex
Continued rewriting discussion (merger).

--- 2015-11-25 docs/discussion_v3.02.tex
@@
   \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_vcirc.ps}
-  \caption{Circular velocity curve. \Wilma{[TO DO: Write caption]}}
+  \caption{Comparison of the circular velocity curve of J1331's inner regions for different models: (a) JAM model with NFW DM halo from Section \ref{sec:results_JAM_NFW} and Figure \ref{fig:modelB4_models} (green).
+(b) Lens model from Section \ref{sec:results_lensing} and Figure \ref{fig:JAM_modelL} with $\alpha = 1.1$ (red dashed line), $\alpha = 1$ (red solid line) and $\alpha=0.9$ (red dash-dotted line).
+(c) Mass-follows-light model, which uses the F814W surface brightness in Table \ref{tab:MGEF814W} and the mass-to-light ratio in the Einstein radius, $\Upsilon^\text{ein}_\text{I,tot} = 5.56$, to generate a mass distribution, as in Figure \ref{fig:lenscomparelight} (orange line).
+(d) Model from gas kinematics and Einstein mass found by \citet{SWELLSV} (their Figure 2, best model with 68\% confidence region) (blue lines).
+\Wilma{[TO DO: In Plot, change symbol for M/L einstein and use full number.
+Mass follows light curve orange.
+Dutton blue.]}}
   \label{fig:vcirc_comparison}
@@
 It cannot be due to tangential velocity anisotropy in the center alone (see Section \ref{sec:results_JAM_SB}, Figure \ref{fig:JAM_modelA2}).
-It also cannot be explained by a strong contribution of DM inside the bulge together with a moderate tagential velocity anisotropy, because the corresponding DM halos would still be too massive to fit the data in the outer regions (see Section \ref{sec:results_JAM_NFW}, Figure \ref{fig:modelB4_vrms}]).
+It also cannot be explained by a strong contribution of DM inside the bulge together with a moderate tagential velocity anisotropy, because the corresponding DM halos would still be too massive to fit the data in the outer regions (see Section \ref{sec:results_JAM_NFW}, Figure \ref{fig:modelB4_vrms}]).e
 

### 2015-12-10 docs/discussion_ML_v3.03.tex
Continued rewriting discussion (merger).

--- 2015-11-25 docs/discussion_v3.02.tex
@@
 %==============
-
-\subsection{On J1331's central kinematics}
-
-%==============
-\begin{figure}
-\centering
-  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_vcirc.ps}
-  \caption{Circular velocity curve. \Wilma{[TO DO: Write caption]}}
-  \label{fig:vcirc_comparison}
-\end{figure}
-%==============
-
-In Figure \ref{fig:vcirc_comparison} we compare the circular velocity curve found by \citet{SWELLSV} with a mass-follows-light model scaled to fit our Einstein mass (by multiplying the light distribution in Table \Wilma{[TO DO]} with $\Upsilon_\text{I,tot}^\text{ein} = 5.6$).
-Within $R < 5''$ they agree with each other.
-
-The models in this work used more than just the Einstein mass to constrain the matter distribution at small radii: The lens mass model constrained also the shape of the mass distribution within the lensing image configuration at $R_\text{ein} \sim 1''$.
-The dynamical models used stellar kinematics inside $R' \simeq 3.5''$ \Wilma{[TO DO: Check]}.
-We compare the lens mass model's $v_\text{circ}$ (for $\alpha=1.0\pm 0.1$) with the NFW JAM model (Table \Wilma{[TO DO]}) in Figure \ref{fig:vcirc_comparison} as well.
-Within and around $R_\text{ein}$ they are consistent with each other, even though they where independently derived.
-They do not agree with the result by \citet{SWELLSV} and in Section \ref{sec:results_JAM_SB} we showed, that ``mass-follows-light'' is not a good model for J1331.
-
-Overall, we were not able to find a consistent explanation for J1331's central $v_\text{rms}$ dip.
-It cannot be due to tangential velocity anisotropy in the center alone (see Section \ref{sec:results_JAM_SB}, Figure \ref{fig:JAM_modelA2}).
-It also cannot be explained by a strong contribution of DM inside the bulge together with a moderate tagential velocity anisotropy, because the corresponding DM halos would still be too massive to fit the data in the outer regions (see Section \ref{sec:results_JAM_NFW}, Figure \ref{fig:modelB4_vrms}]).
-
-Another feature in the stellar kinematics, that none of our JAM models was able to reproduce in the slightest and which we therefore excluded in the modelling, was the dip in $v_\text{rms}$ around $\sim 6''$, which occurs around the transition from bulge to disk (see Figures \ref{fig:F814W} and \ref{fig:kinematics}).
-
-\subsection{On J1331's possible merger history}
-
-\Wilma{[TO DO: Remove minor in merger.]}
-
-J1331 has a large counter-rotating stellar core within $\sim 2''$.
-This suggests a process in J1331's past in which two components with angular momenta oriented in opposite directions were involved.
-Accretion of gas on retrograde orbits and subsequent star formation could lead to a younger and counter-rotating stellar population \Wilma{[TO DO: REF]}.
-However, to form enough stars such that the net rotation of the large and massive core is retrograde, a very large amount of gas would have had to be accreted by J1331---which is not very likely [TO DO: REF].
-
-Another scenario are galaxy mergers.
-Major mergers including large amounts of gas can form kinematically decoupled cores (KDCs), see e.g., \Wilma{[TO DO: REF: Lauren Hofman et al 2010 - read paper how this fits with the reverse color gradient]}.
-During a minor merger, the dense nucleus of a satellite galaxy on a retrograde orbit could survive the dissipationless accretion and could spiral to the core due to tidal friction \citep{1984ApJ...287..577K}.
-Usually large bulges of spirals or ellipticals are reddest in the center and become bluer further out.
-Because star formation in low-mass satellite galaxies occurred later than in massive galaxies \Wilma{[TO DO: REF]}, the merger remnant would now host a younger and bluer population with lower velocity dispersion within the older and redder bulge of the massive progenitor.
-Such a reverse color gradient could correspond to an increasing stellar mass-to-light ratio.
-
-The merger theory could explain and support our findings from dynamical modelling and the previous sections, that J1331 might have an increasing stellar mass-to-light ratio within its core.
-
-\subsection{On possible modelling failures and speculations how to resolve them}
-
-\Wilma{[TO DO: Include in discussion: Kinematic twist due to merger.
-Bulge and disk have different kinematic major axis, and the measured velocities in the disk, which are off from the major axis, are much lower than the actual maximum vcirc.
-Could explain the dips in the outer regions.]}
-
-Another effect that minor mergers can have on galaxies are a misalignement (warp) of the photometric and kinematic major axis \Wilma{[TO DO: REF]}.
-Would this be the case for J1331 the assumption of axisymmetry is not true anymore and our dynamical modelling would fail.
-
-Mergers also could have changed the 3D shape of the dark matter halo and the NFW halo was therefore not a good model for J1331's dark matter halo.
-We also tried to model J1331 with a cored logarithmic halo.
-However, due to degeneracies in the modelling, we were not able to either constrain the profile for a cored logarithmic halo, or to rule it out.
-
-\Wilma{[TO DO: Include in this discussion the findings from the color profile.]}
-
-This could indicate that there might be a less bottom-heavy, more bluish population, with an IMF close to the Chabrier IMF, in the very center of J1331.
-
-\subsection{Future work}
-
-Standard JAM modelling approaches seem not to work for J1331.
-A JAM model for J1331 would need to allow for stellar mass-to-light ratio gradients within the galaxy, velocity anisotropy and a dark matter halo.
-Because of degeneracies between stellar and dark mass, and matter distribution and anisotropy profile, such a dynamical model would not lead to very tight constraints on the model parameters.
-A search for colour gradients in J1331 and/or investigation of absorption line indices could support or contradict the suspicion of the existence of stellar mass-to-light ratio gradients in J1331.
-Subsequently detailed stellar population analyses of the spectra taken along J1331's major axis should be conducted to constrain the mass-to-light ratio reliably.
-\Wilma{[TO DO: Include in this discussion the findings from the color profile.]}
-
-In addition, the dynamical modelling should use more of the available information on J1331 and fit dynamics (stellar and gas kinematics from \citet{SWELLSV}) simultaneously with the gravitational lensing (image positions, shape and even flux ratios) in a similar fashion to \citet{SWELLSIV}.
-To also model the extent, shape and flux of the lensing images, the method by \citet{2004ApJ...611..739T,2003ApJ...590..673W} could be employed, which models the surface brightness distribution of the images and source on a pixelated grid.
-However, for this to work a good model for the galactic extinction would be needed.
-
-High-resolution integral-field spectroscopy could help with this, allow for spatially resolved stellar population analysis and dynamical modelling in two dimensions.
-\Wilma{[TO DO: Include in this discussion that this could also help test, if the vrms dip is maybe because of twist, i.e., the measurements where not done along the major axis in the disk]} This would lead to much better understanding of J1331's structure and mass distribution and therefore answer questions on how minor mergers might modify spiral galaxies.
-
-\Wilma{[TO DO: Include in discussion: High resolution IFU: high spatial resolution --> to resolve small features.
-High spectral resolution --> because the velocity dispersion in the outer regions of the galaxy are very low and to measure them accurately, need high spectral resolution.]}
-
-\Wilma{[TO DO: Include the following discssion somwhere: The above discussion motivates the following speculation: In the absence of a strong DM contribution in the center, the overall stellar-mass-to-light ratio within the Einstein radius indicates a bottom-heavy IMF close to the Salpeter IMF, consistent with estimates from the velocity dispersion.
-At the same time the central dip can then be only explained, if there was an increase in stellar mass-to-light ratio with radius \textit{within} the bulge.
-\emph{If} there was a central stellar population with an IMF close to the \citet{Chabrier2003} IMF, surrounded by a more bottom-heavy population, the central stellar kinematics would be well explained and be fully consistent with the lensing results.
-(According to Figure \ref{fig:lenscompareboth} the lensing result might not predict a mass to light ratio gradient inside $R_\text{ein}$, but then again the mass slope $alpha=1$ was only weakly constrained.) The disk of J1331 has a lower $\Upsilon_\text{I,*}$ than the bulge (see Table \ref{tab:previousresults} according to \citet{SWELLSI}).
-Such a drop in $\Upsilon_\text{I,*}$ at the transition region from bulge to disk around $\sim 5''$ could lead to the observed drop in $v_\text{rms}$, while an increasing contribution of a lower mass DM halo at larger radii as found by \citet{SWELLSV}, would recover the kinematics in the out regions of J1331's disk.]}
-
-\Wilma{[TO DO: Why are disk and bulge mass in SWELLS I different to the one in SWELLS IV??]}

### 2015-12-10 docs/discussion_kinematics_v3.03.tex
Continued rewriting discussion (merger).

--- 2015-12-10 archive/v3/docs/discussion_v3.02.tex
@@
-We've presented different dynamical models for the central region of J1331.
-Some of them capture the observed kinematics, but none of them work at both small and large radii.
-In the following we discuss possible reasons, also by comparing our results to previous work.
-
-\subsection{On J1331's central stellar mass-to-light ratio} \label{sec:MLdiscussion}
-
-Some of the ambiguities in recovering J1331's matter distribution could be resolved by learning more about stellar populations with different IMFs in J1331.
-In particular, a sophisticated guess for the stellar mass-to-light ratio in the bulge could be compared to our very reliable measurement of the total mass-to-light ratio inside the Einstein radius (see Table \ref{tab:einsteinML}).
-This would then either support or contradict the presence of a significant amount of DM in the bulge.
-
-Traditional choices for the IMF are the bottom-heavy IMF by \citet{Salpeter1955},
-$$\xi(m) \propto m^{-x}, x=2.35,$$
-where $\xi(m) \diff m$ is the number of stars with mass $m$ in $[m,m+\diff m]$, and the IMFs by \citet{2002Sci...295...82K} and \citet{Chabrier2003}, which are in agreement with each other and predict less low-mass stars.
-
-\citet{Ferreras} found a relation between the central stellar velocity dispersion $\sigma_0$ in early-type galaxies and the IMF slope $x$; a higher $\sigma_0$ suggests a more bottom-heavy IMF.
-For a unimodal (Salpeter-like) IMF and $\sigma_0 \simeq 200~\text{km s}^{-1}$ in J1331 (see Figure \ref{fig:kinematics}) they predict $x \approx 2.33$, which is close to the standard Salpeter slope, also supported by \citet{2014MNRAS.438.1483S}.
-When assuming a bi-modal (Kroupa-equivalent-like) IMF, \citet{Ferreras} predict $x \approx 2.85$ for J1331's central velocity dispersion.
-This is more bottom-heavy than the standard \citet{2002Sci...295...82K} IMF.
-Overall, the central velocity dispersion suggests a rather bottom-heavy IMF in J1331's bulge and therefore large stellar mass-to-light ratio.
-
-\citet{SWELLSI} estimated J1331's stellar bulge mass given a Salpeter IMF and measured the I-band AB magnitude of the bulge.
-Transformed to a stellar I-band mass-to-light ratio, their results would correspond to $\Upsilon_\text{I,*}^\text{sal} = 4.7 \pm 1.2$ (see Table \ref{tab:previousresults}).
-This is not too far from $\Upsilon_\text{I,*} = 4.2 \pm 0.2$ (see Table \Wilma{[TO DO]}), which we found when including a NFW halo in the JAM modelling.
-
-When \citet{SWELLSI} assumed a Chabrier IMF, their result translates to $\Upsilon_\text{I,*}^\text{chab} = 2.5 \pm 0.6$ (see Table \ref{tab:previousresults}).
-In Section \ref{sec:results_JAM_SB} we created a dynamical model from only the surface brightness distribution and an increasing mass-to-light ratio profile without additional DM halo.
-We found that such a model would be perfectly consistent with the Einstein mass, predict a total $\Upsilon_\text{I,tot}(R'\sim0) = 2.53$---being consistent with the Chabrier IMF estimate by \citet{SWELLSI}---and rise quickly to $\Upsilon_\text{I,tot}(R'\gtrsim R_\text{ein}) \gtrsim 6$.
-
-We also compare our results from Section \ref{sec:results_JAM_NFW} with the study by \citet{SWELLSV}.
-They found that the bulge of J1331 has an IMF \emph{more} bottom-heavy than the Salpeter IMF from fitting a NFW halo to (1) the Einstein mass and (2) gas kinematics at larger radii $\gtrsim 8''$.
-In Section we fitted a mass model with NFW halo to (1) the Einstein mass and (2) stellar kinematics within $\sim 3.5''$.
-Our best fit $\Upsilon_\text{I,*} = 4.2 \pm 0.2$ (see Table \ref{tab:modelB4_bestfit}) indicates a \emph{less} bottom-heavy IMF than the Salpeter IMF.
-\cite{SWELLSV} found systematically lower NFW halo masses ($v_\text{circ,halo}(5'') \sim 120~\text{km s}^{-1}$ according to their Figure 2) than we did ($v_\text{circ,halo}(5'') \sim 200~\text{km s}^{-1}$).
-
-%==============
-\begin{table*}
-\centering
-\begin{tabular}{cccccc}
-\hline\hline
-& & \multicolumn{2}{c}{Chabrier IMF} & \multicolumn{2}{c}{Salpeter IMF}\\
-      &  $L$ [$10^{10}L_{\odot}$]                & $M_*$ [$10^{10}M_\odot$]               & $\Upsilon_\text{I,*}^\text{chab}$ & $M_*$ [$10^{10}M_\odot$] & $\Upsilon_\text{I,*}^\text{sal}$ \\\hline
-bulge &   $3.10 \pm 0.15 $  & $7.8 \pm 1.8$ & $2.5 \pm 0.6$ & $14.5 \pm 3.7 $ & $4.7 \pm 1.2$ \\
-disk  &   $2.35 \pm 0.11 $  & $2.9 \pm 0.7$ & $1.2 \pm 0.3$ & $5.2 \pm 1.1$ & $2.2 \pm 0.5$ \\
-total &   $5.45 \pm 0.19$ & $10.6 \pm 1.9$& & $19.7 \pm 3.9$&\\\hline
-\end{tabular}
-\caption{Total I-band luminosity, stellar mass and mass-to-light ratio, calculated from the I-band AB magnitudes and stellar masses found for J133's bulge and disk by \citet{SWELLSI} (their table 2) for comparison with this work.
-The transformation from AB magnitudes to the Johnson-Cousins I-Band used the relation $I[\text{mag}] = I[\text{ABmag}] - 0.309$ from \citet{FG1994} (their table 2).
-For the conversion from apparent magnitude to total luminosity the redshift $z=0.113$ \citet{SWELLSIII} was turned into a luminosity distance using the cosmology by \citet{WMAP5cosm}.
-}
-\label{tab:previousresults}
-\end{table*}
-%==============
-
 \subsection{On J1331's central kinematics}
@@
 Another feature in the stellar kinematics, that none of our JAM models was able to reproduce in the slightest and which we therefore excluded in the modelling, was the dip in $v_\text{rms}$ around $\sim 6''$, which occurs around the transition from bulge to disk (see Figures \ref{fig:F814W} and \ref{fig:kinematics}).
-
-\subsection{On J1331's possible merger history}
-
-\Wilma{[TO DO: Remove minor in merger.]}
-
-J1331 has a large counter-rotating stellar core within $\sim 2''$.
-This suggests a process in J1331's past in which two components with angular momenta oriented in opposite directions were involved.
-Accretion of gas on retrograde orbits and subsequent star formation could lead to a younger and counter-rotating stellar population \Wilma{[TO DO: REF]}.
-However, to form enough stars such that the net rotation of the large and massive core is retrograde, a very large amount of gas would have had to be accreted by J1331---which is not very likely [TO DO: REF].
-
-Another scenario are galaxy mergers.
-Major mergers including large amounts of gas can form kinematically decoupled cores (KDCs), see e.g., \Wilma{[TO DO: REF: Lauren Hofman et al 2010 - read paper how this fits with the reverse color gradient]}.
-During a minor merger, the dense nucleus of a satellite galaxy on a retrograde orbit could survive the dissipationless accretion and could spiral to the core due to tidal friction \citep{1984ApJ...287..577K}.
-Usually large bulges of spirals or ellipticals are reddest in the center and become bluer further out.
-Because star formation in low-mass satellite galaxies occurred later than in massive galaxies \Wilma{[TO DO: REF]}, the merger remnant would now host a younger and bluer population with lower velocity dispersion within the older and redder bulge of the massive progenitor.
-Such a reverse color gradient could correspond to an increasing stellar mass-to-light ratio.
-
-The merger theory could explain and support our findings from dynamical modelling and the previous sections, that J1331 might have an increasing stellar mass-to-light ratio within its core.
-
-\subsection{On possible modelling failures and speculations how to resolve them}
-
-\Wilma{[TO DO: Include in discussion: Kinematic twist due to merger.
-Bulge and disk have different kinematic major axis, and the measured velocities in the disk, which are off from the major axis, are much lower than the actual maximum vcirc.
-Could explain the dips in the outer regions.]}
-
-Another effect that minor mergers can have on galaxies are a misalignement (warp) of the photometric and kinematic major axis \Wilma{[TO DO: REF]}.
-Would this be the case for J1331 the assumption of axisymmetry is not true anymore and our dynamical modelling would fail.
-
-Mergers also could have changed the 3D shape of the dark matter halo and the NFW halo was therefore not a good model for J1331's dark matter halo.
-We also tried to model J1331 with a cored logarithmic halo.
-However, due to degeneracies in the modelling, we were not able to either constrain the profile for a cored logarithmic halo, or to rule it out.
-
-\Wilma{[TO DO: Include in this discussion the findings from the color profile.]}
-
-This could indicate that there might be a less bottom-heavy, more bluish population, with an IMF close to the Chabrier IMF, in the very center of J1331.
-
-\subsection{Future work}
-
-Standard JAM modelling approaches seem not to work for J1331.
-A JAM model for J1331 would need to allow for stellar mass-to-light ratio gradients within the galaxy, velocity anisotropy and a dark matter halo.
-Because of degeneracies between stellar and dark mass, and matter distribution and anisotropy profile, such a dynamical model would not lead to very tight constraints on the model parameters.
-A search for colour gradients in J1331 and/or investigation of absorption line indices could support or contradict the suspicion of the existence of stellar mass-to-light ratio gradients in J1331.
-Subsequently detailed stellar population analyses of the spectra taken along J1331's major axis should be conducted to constrain the mass-to-light ratio reliably.
-\Wilma{[TO DO: Include in this discussion the findings from the color profile.]}
-
-In addition, the dynamical modelling should use more of the available information on J1331 and fit dynamics (stellar and gas kinematics from \citet{SWELLSV}) simultaneously with the gravitational lensing (image positions, shape and even flux ratios) in a similar fashion to \citet{SWELLSIV}.
-To also model the extent, shape and flux of the lensing images, the method by \citet{2004ApJ...611..739T,2003ApJ...590..673W} could be employed, which models the surface brightness distribution of the images and source on a pixelated grid.
-However, for this to work a good model for the galactic extinction would be needed.
-
-High-resolution integral-field spectroscopy could help with this, allow for spatially resolved stellar population analysis and dynamical modelling in two dimensions.
-\Wilma{[TO DO: Include in this discussion that this could also help test, if the vrms dip is maybe because of twist, i.e., the measurements where not done along the major axis in the disk]} This would lead to much better understanding of J1331's structure and mass distribution and therefore answer questions on how minor mergers might modify spiral galaxies.
-
-\Wilma{[TO DO: Include in discussion: High resolution IFU: high spatial resolution --> to resolve small features.
-High spectral resolution --> because the velocity dispersion in the outer regions of the galaxy are very low and to measure them accurately, need high spectral resolution.]}
-
-\Wilma{[TO DO: Include the following discssion somwhere: The above discussion motivates the following speculation: In the absence of a strong DM contribution in the center, the overall stellar-mass-to-light ratio within the Einstein radius indicates a bottom-heavy IMF close to the Salpeter IMF, consistent with estimates from the velocity dispersion.
-At the same time the central dip can then be only explained, if there was an increase in stellar mass-to-light ratio with radius \textit{within} the bulge.
-\emph{If} there was a central stellar population with an IMF close to the \citet{Chabrier2003} IMF, surrounded by a more bottom-heavy population, the central stellar kinematics would be well explained and be fully consistent with the lensing results.
-(According to Figure \ref{fig:lenscompareboth} the lensing result might not predict a mass to light ratio gradient inside $R_\text{ein}$, but then again the mass slope $alpha=1$ was only weakly constrained.) The disk of J1331 has a lower $\Upsilon_\text{I,*}$ than the bulge (see Table \ref{tab:previousresults} according to \citet{SWELLSI}).
-Such a drop in $\Upsilon_\text{I,*}$ at the transition region from bulge to disk around $\sim 5''$ could lead to the observed drop in $v_\text{rms}$, while an increasing contribution of a lower mass DM halo at larger radii as found by \citet{SWELLSV}, would recover the kinematics in the out regions of J1331's disk.]}
-
-\Wilma{[TO DO: Why are disk and bulge mass in SWELLS I different to the one in SWELLS IV??]}

### 2015-12-10 docs/discussion_merger_v3.03.tex
Continued rewriting discussion (merger).

\subsection{On J1331's possible merger history and resolution of modelling failures}

J1331 has a large counter-rotating stellar core within $\sim 2''$. This suggests a process in J1331's past in which two components with angular momenta oriented in opposite directions were involved. Accretion of gas on retrograde orbits and subsequent star formation could lead to a younger and counter-rotating stellar population \Wilma{[TO DO: REF]}. However, to form enough stars such that the net rotation of the large and massive core is retrograde, a very large amount of gas would have had to be accreted by J1331---which is not very likely [TO DO: REF].

Another scenario are galaxy mergers. Major mergers including large amounts of gas can form kinematically decoupled cores (KDCs), see e.g., \Wilma{[TO DO: REF: Lauren Hofman et al 2010 - read paper how this fits with the reverse color gradient]}. During a minor merger, the dense nucleus of a satellite galaxy on a retrograde orbit could survive the dissipationless accretion and spiral to the core due to tidal friction \citep{1984ApJ...287..577K}.

Usually ellipticals and the bulges of massive spirals appear reddest in their center and getting increasingly bluer with larger radii. Mergers can reverse this behaviour in the remnant's core. A star formation burst triggered by the major merger could lead to a new young stellar population in the galaxy's bulge \Wilma{[TO DO: Check, if I can claim that]}. In case of a minor merger the satellite nucleus now residing in the merger remnant's very center is also much younger than the bulge stars of the massive progenitor, because star formation in low-mass satellite galaxies occurs over a longer period and later than in massive galaxies \Wilma{[TO DO: REF]}. The different stellar populations in a merger remnant can be associated with different $\Upsilon_*$ and sometimes even show up as a reverse colour gradient within the bulge in photometry \Wilma{[TO DO: REF]}.

Even though investigation of the photometry of J1331 did not reveal a clear and distinct blue core in J1331, we cannot fully exclude the possibility that J1331 has $\Upsilon_*$ gradient. And as discussed \Wilma{[TO DO: Where???]} an increasing $\Upsilon_*$ could explain the observed central $v_\text{rms}$ dip.

Another way how major mergers can modify the structure of galaxies is a kinematic twist \Wilma{[TO DO: REF]} or misalignment (warp) of kinematic and photometric major axis \Wilma{[TO DO: REF]}. In projection a kinematic twist shows up as a misalignment of the kinematic major axis of bulge and disk \Wilma{[TO DO: No idea if it works like this.]}. In both cases---kinematic twist and warp---th \Wilma{[TO DO: Continue]}

%---------------

If one or both of the merger effects mentioned above---$\Upsilon_*$ gradient in the bulge and misalignment of the kinematic major axes---were also the case for J1331, this would introduce complexities in our dynamical modelling that we cannot account for based alone on stellar kinematics along the photometric major axis.

We speculate that the modelling approaches in this work could indeed point towards such merger modifications in J1331. Investigation, but...

%---------------

%satellite core has lower velocity dispersion.
% Kinematic twist due to merger. Bulge and disk have different kinematic major axis, and the measured velocities in the disk, which are off from the major axis, are much lower than the actual maximum vcirc. Could explain the dips in the outer regions.
%Another effect that minor mergers can have on galaxies are a misalignement (warp) of the photometric and kinematic major axis \Wilma{[TO DO: REF]}. Would this be the case for J1331 the assumption of axisymmetry is not true anymore and our dynamical modelling would fail.

Mergers also could have changed the 3D shape of the dark matter halo and the NFW halo was therefore not a good model for J1331's dark matter halo. We also tried to model J1331 with a cored logarithmic halo. However, due to degeneracies in the modelling, we were not able to either constrain the profile for a cored logarithmic halo, or to rule it out.

\Wilma{[TO DO: Include in this discussion the findings from the color profile.]}

This could indicate that there might be a less bottom-heavy, more bluish population, with an IMF close to the Chabrier IMF, in the very center of J1331.

\Wilma{[TO DO: Remove minor in merger.]}

### 2015-12-14 docs/discussion_merger_v3.03.tex
Almost finished merger part of discussion.

@@
-\subsection{On J1331's possible merger history and resolution of modelling failures}
+\subsection{On J1331's possible merger history and modelling failures}
 
-J1331 has a large counter-rotating stellar core within $\sim 2''$.
-This suggests a process in J1331's past in which two components with angular momenta oriented in opposite directions were involved.
+%Why we think that J1331 had a merger
+J1331 has a large counter-rotating stellar core within $\sim 2''$. This suggests a process in J1331's past in which two components with angular momenta oriented in opposite directions were involved.
+
+%Gas accretion - no!
 Accretion of gas on retrograde orbits and subsequent star formation could lead to a younger and counter-rotating stellar population \Wilma{[TO DO: REF]}.
@@
 
+%Mergers - yes!
 Another scenario are galaxy mergers.
@@
 
+%Merger + color gradient
 Usually ellipticals and the bulges of massive spirals appear reddest in their center and getting increasingly bluer with larger radii.
@@
 
-Even though investigation of the photometry of J1331 did not reveal a clear and distinct blue core in J1331, we cannot fully exclude the possibility that J1331 has $\Upsilon_*$ gradient.
+%Color gradient in J1331
+Even though investigation of the photometry of J1331 did not reveal a distinct blue core in J1331, we cannot fully exclude the possibility that J1331 has $\Upsilon_*$ gradient.
 And as discussed \Wilma{[TO DO: Where???]} an increasing $\Upsilon_*$ could explain the observed central $v_\text{rms}$ dip.
+While $\Upsilon_*$ gradients could be easily included in JAM modelling, it would add much more complexity and degeneracies.
+We would need either more kinematic data and/or a sophisticated guess for the $\Upsilon_*$ gradient to constrain the model parameters reliably.
 
+%Merger and kinematic twist
 Another way how major mergers can modify the structure of galaxies is a kinematic twist \Wilma{[TO DO: REF]} or misalignment (warp) of kinematic and photometric major axis \Wilma{[TO DO: REF]}.
-In projection a kinematic twist shows up as a misalignment of the kinematic major axis of bulge and disk \Wilma{[TO DO: No idea if it works like this.]}.
-In both cases---kinematic twist and warp---th \Wilma{[TO DO: Continue]}
+A kinematic twist shows up as a misalignment of the kinematic major axis of bulge and disk in projection \Wilma{[TO DO: No idea if it works like this.]}.
+
+%Kinematic twist in J1331
+In both cases---kinematic twist and warp in J1331---the assumption of axisymmetry in our dynamical modelling would not be satisfied anymore.
+If such a kinematic twist is present in J1331 cannot be identified from kinematics along the photometric major axis alone, but should be immediately obvious in 2D kinematic maps.
+We note that if the kinematic major axis was off from the photometric major axis in the outer regions of J1331, the measured $v_\text{rot}$ in the disk \Wilma{[TO DO: some sinus i]} would be much lower than the actual maximum $v_\text{circ}$.
+This could maybe also explain the so far inexplicable dips in $v_\text{rms}$ at the transition from bulge to disk.
+It is therefore not completely ruled out, that J1331 might have a more massive DM halo than \citet{SWELLSV} found.
+
+%Merger and halo in J1331
+Mergers also could have changed the 3D shape of the DM halo and the NFW halo would be therefore not a good model for J1331's DM halo.
+We also tried to model J1331 with a cored logarithmic halo.
+However, due to degeneracies in the modelling, we were not able to either constrain the profile for a cored logarithmic halo, or to rule it out.
 
@@
 
-If one or both of the merger effects mentioned above---$\Upsilon_*$ gradient in the bulge and misalignment of the kinematic major axes---were also the case for J1331, this would introduce complexities in our dynamical modelling that we cannot account for based alone on stellar kinematics along the photometric major axis.
-
-We speculate that the modelling approaches in this work could indeed point towards such merger modifications in J1331. Investigation, but...
-
-%---------------
-
-%satellite core has lower velocity dispersion.
-% Kinematic twist due to merger.
-Bulge and disk have different kinematic major axis, and the measured velocities in the disk, which are off from the major axis, are much lower than the actual maximum vcirc.
-Could explain the dips in the outer regions.
-%Another effect that minor mergers can have on galaxies are a misalignement (warp) of the photometric and kinematic major axis \Wilma{[TO DO: REF]}.
-Would this be the case for J1331 the assumption of axisymmetry is not true anymore and our dynamical modelling would fail.
-
-Mergers also could have changed the 3D shape of the dark matter halo and the NFW halo was therefore not a good model for J1331's dark matter halo.
-We also tried to model J1331 with a cored logarithmic halo.
-However, due to degeneracies in the modelling, we were not able to either constrain the profile for a cored logarithmic halo, or to rule it out.
-
-\Wilma{[TO DO: Include in this discussion the findings from the color profile.]}
-
-This could indicate that there might be a less bottom-heavy, more bluish population, with an IMF close to the Chabrier IMF, in the very center of J1331.
-
-\Wilma{[TO DO: Remove minor in merger.]}
+\Wilma{[TO DO: include somewhere "satellite core has lower velocity dispersion."]}

### 2016-01-05 docs/discussion_merger_v3.03.tex
Small corrections in text and changes in plot legends.

@@
 Accretion of gas on retrograde orbits and subsequent star formation could lead to a younger and counter-rotating stellar population \Wilma{[TO DO: REF]}.
-However, to form enough stars such that the net rotation of the large and massive core is retrograde, a very large amount of gas would have had to be accreted by J1331---which is not very likely [TO DO: REF].
+However, to form enough stars such that the net rotation of the large and massive core is retrograde, a very large amount of gas would have had to be accreted by J1331---which is not very likely \Wilma{[TO DO: REF]}.
 

### 2016-01-05 docs/introduction_v3.02.tex
Edited dynamical modelling results sections.
Small corrections in text and changes in plot legends.

@@
 
-The mass profile at larger galactocentric radii can be probed by gas rotation curves that directly measure the galaxy's circular velocity profile \Wilma{[TO DO: REF]}.
-However, due to its dissipative nature, gas motions are very sensitive to disturbances by e.g., spiral arms and bars \Wilma{[TO DO: REF]}.
+The mass profile at larger galactocentric radii can be probed by gas rotation curves that directly measure the galaxy's circular velocity profile (e.g., \citealt{1980ApJ...238..471R})\Wilma{[TO DO: Can I use this here?]}.
+However, due to its dissipative nature, gas motions are very sensitive to disturbances by e.g., spiral arms and bars (e.g., \citealt{2004dad..book.....S}).
 

### 2016-01-05 docs/results_JAMwithNFW_v3.02.tex
Started rewriting the discussion.
Small corrections in text and changes in plot legends.

@@
 The grey diamonds mark a random sub-selection of 12 samples; the corresponding models are shown in Figure \ref{fig:modelB4_models}.
-\Wilma{[TO DO: Use $\text{km s}^{-1}$ instead of km/s]} \Wilma{[TO DO: More space between titles and upper axes tick labels.]} \Wilma{[TO DO: Maybe mention also: There are slight covariances between $\Upsilon_\text{I,*}$,  $r_s$ and $\beta_z$: The smaller the DM contribution in the center (i.e., the larger $\Upsilon_\text{I,*}$), the less concentrated is the halo (i.e., the larger $r_s$), the more velocity anisotropy is needed to reproduce the central dip.
+\Wilma{[TO DO: Maybe mention also: There are slight covariances between $\Upsilon_\text{I,*}$,  $r_s$ and $\beta_z$: The smaller the DM contribution in the center (i.e., the larger $\Upsilon_\text{I,*}$), the less concentrated is the halo (i.e., the larger $r_s$), the more velocity anisotropy is needed to reproduce the central dip.
 As the effect of $v_{200}$ is mostly at larger radii, this parameter doesn't show any covariances, but is also mostly constrained by the prior.
@@
 \emph{Panel b)} shows the circular velocity curve of the total mass (green), and separately the contribution of the stellar mass (yellow, again generated from the MGE in Table \ref{tab:MGEF814W}) and DM (grey).
-\Wilma{[TO DO: make one separate circular velocity plot, that also contains the mass-follows-light with Einstein M/L vcirc and compares it with Aaron's vcirc curve.
-Ask Aaron for data.]} \emph{Panel c)} shows the corresponding enclosed mass profile.
-Overplotted is also the Einstein mass at the Einstein radius with a 10\% error, which was used in the fit as an additional constraint.
-\Wilma{[TO DO: Replace arcsec with '']} \Wilma{[TO DO: Use $\text{km s}^{-1}$ instead of km/s]} \Wilma{[TO DO: Make two figures from this: vrms (shrinked horizontally) and encl Mass should be first and second panel of one figure, and circular velocity curve should be separate figure.
-] \Wilma{[TO DO: Use MGE for the inenr regions in circular velocity plot.]}}}
+\emph{Panel c)} shows the corresponding enclosed mass profile.
+Overplotted is also the Einstein mass at the Einstein radius with a 10\% error, which was used in the fit as an additional constraint.}
 \label{fig:modelB4_models}

### 2016-01-05 docs/results_JAMwithSB_v3.01.tex
Small corrections in text and changes in plot legends.

--- 2015-11-23 docs/results_JAMwithSB_v3.01.tex
@@
 
-\paragraph{JAM with lens mass model.} We make an independent prediction for the $v_\text{rms}$ curve by evaluating Equation \Wilma{[TO DO]} (with $\beta_z = 0$) for the lens mass model in Table \ref{tab:bestfitlensmodel} ($\alpha = 1$, flat rotation curve).
-In addition, we also calculate a  $v_\text{rms}$ curve for a lens model which was found analogously, but assumed a slightly rising rotation curve slope of $\alpha=1.1$.
+\paragraph{JAM with lens mass model.} We make an independent prediction for the $v_\text{rms}$ curve by evaluating Equation \ref{eq:explicitLOSvelCap} (with $\beta_z = 0$) for the lens mass model in Table \ref{tab:bestfitlensmodel} ($\alpha = 1$, flat rotation curve).
+In addition, we also calculate a  $v_\text{rms}$ curve for two lens models which were found analogously, but assumed a slightly rising (falling) rotation curve slope of $\alpha=1.1$ ($\alpha=0.9$).
 The predictions are compared with the data in Figure \ref{fig:JAM_modelL}.
-The agreement within $R' \sim 3''$ is striking: The $\alpha > 1$ model recreates the observed central dip, while the $\alpha = 1$ model fits the wings around $R_\text{eff}$.
+While the most reliable constraint is around $R_\text{ein}$, the agreement within $R' \sim 3''$ is still striking: The $\alpha > 1$ model recreates the observed central dip, while the $\alpha = 1$ model fits the wings around $R_\text{eff}$.
 This is in concordance with observations in other galaxies.
-For $R'> R_\text{eff}$ we would expect $\alpha<1$.
-Our lensing model assumes $\alpha(R')=\text{const}$, although Figure \ref{fig:JAM_modelL} suggests, that a model with variable $\alpha(R')$ might fit even better, and maybe also reproduce the sharp drop in $v_\text{rms}$ around $R' \sim 3''$.
-We note however, that the most reliable constraint is around $R_\text{ein}$.
-Outside of $R_\text{ein}$ lensing models are only extrapolations.
+For $R'> R_\text{eff}$ we would expect $\alpha<1$---and the lensing model for $\alpha=0.9$ has indeed a slightly dropping $v_\text{rms}$ around $R_\text{eff}$, like the data.
+A definite comparison in this regime is however difficult as the lens models are just extrapolations outside of $R_\text{ein}$.
+While our lensing model assumes $\alpha(R')=\text{const}$, Figure \ref{fig:JAM_modelL} suggests, that a model with variable $\alpha(R')$ could fit even better.
+Overall the lensing model is in very good agreement with the $v_\text{rms}$ data within $R' \sim 3''$---even though it was derived completely independently.
 
@@
   \includegraphics[height=6cm]{fig/lensing_JAM_comparision.ps}
-  \caption{Comparison (not a fit!) of the symmetrized stellar $v_\text{rms}$ data of J1331 (blue dots) with JAM models generated from mass distributions which were independently derived from lensing constraints in Section \ref{sec:results_lensing}.
-\Wilma{[TO DO: Add Note that outside Rein extrapolation.]} The red solid line corresponds to the lens model for a flat rotation curve ($\alpha = 1$) in Table \ref{tab:bestfitlensmodel}; the green line is a best fit lens model found analogously from the image positions, but for a fixed rotation curve slope of $\alpha = 1.1$.
-For the JAM modelling a best fit MGE to the lens mass models were used, as well as the observed surface brightness MGE in Table \ref{tab:MGEF814W}, assuming velocity isotropy $\beta_z = 0$ and an inclination of $i = 70^\circ$.The red and black dotted lines are the Einstein radius and the effective half-light radius, respectively.}
+  \caption{Comparison (not a fit!) of the symmetrized stellar $v_\text{rms}$ data of J1331 (blue dots) with JAM models generated from mass distributions which were independently derived from lensing constraints in Section \ref{sec:results_lensing} (red lines).
+The red solid line corresponds to the lens model for a flat rotation curve ($\alpha = 1$) in Table \ref{tab:bestfitlensmodel}; the red dashed and dash-dotted lines are best fit lens models found analogously from the image positions, but for a fixed rotation curve slope of $\alpha = 1.1$ and $0.9$, respectively.
+For the JAM modelling a best fit MGE to the lens mass models were used, as well as the observed surface brightness MGE in Table \ref{tab:MGEF814W}, assuming velocity isotropy $\beta_z = 0$ and an inclination of $i = 70^\circ$.
+The most reliable constraints are around the Einstein radius (vertical red dotted line); outside of it the JAM model is just an extrapolation.}
   \label{fig:JAM_modelL}
@@
   \includegraphics[height=6cm]{fig/jam_A2_vrms.ps}
-  \caption{Comparison of the symmetrized $v_\text{rms}$ data of J1331 (blue dots) with a best fit dynamical JAM model (solid red line) assuming mass-follows-light and with two free parameters: $\Upsilon_\text{I,tot}^\text{dyn}$, the total I-band mass-to-light ratio found from dynamics, which converts the observed surface brightness in Table \ref{tab:MGEF814W} into a mass distribution, and the velocity anisotropy parameter $\beta_z$.
+  \caption{Comparison of the symmetrized $v_\text{rms}$ data of J1331 (blue dots) with a best fit dynamical JAM model (orange line) assuming mass-follows-light and with two free parameters: $\Upsilon_\text{I,tot}^\text{dyn}$, the total I-band mass-to-light ratio found from dynamics, which converts the observed surface brightness in Table \ref{tab:MGEF814W} into a mass distribution, and the velocity anisotropy parameter $\beta_z$.
 The ``best'' fit is $\Upsilon_\text{I,tot}^\text{dyn} = 4.8 \pm 0.1$ and $\beta_z = -0.5$, where the latter is however pegged at the lower limit of the allowed value range.

### 2016-01-05 docs/results_lensing_v3.01.tex
Small corrections in text and changes in plot legends.

@@
 
-\Wilma{[TO DO: Intro Sentence]}
+In this section we use the gravitational lensing formalism summarized in Section \ref{sec:lensing_theo} to fit a scale-free galaxy mass model to the positions of the lensing images observed in J1331's central region.
 
@@
 Not only the position of the extrema, but also their shape is consistent with the observed, extended images, even though we did not use information about the image shape in the analysis.}
-\label{fig:???}
+\label{fig:bestfitlensmodel}
 \end{figure}
@@
 The best fit parameters are given in the first column of Table \ref{tab:bestfitlensmodel}.
-Figure \ref{fig:lensbestfiteinsteincurves} shows the corresponding critical curve, caustic and Einstein radius, and the best fit source position.
+Figure \ref{fig:bestfitlensmodel} shows the corresponding critical curve, caustic and Einstein radius, and the best fit source position.
 In this case, where $\alpha=1$, the (tangential) critical curve is also an equidensity contour of the galaxy model \citep{EvansWitt}, which appears to have an elliptical mass distribution.
 The source is located close to a cusp of the diamond-shaped caustic: a lensing configuration for which we indeed expect four images.
-Figure \ref{fig:lensbestfittimedelay} overplots the (smoothed) residuals from the F450W image subtracted by an IRAF \emph{ellipse} brightness model with the contours of the best fit model's time delay surface.
+Figure \ref{fig:bestfitlensmodel} also shows the (smoothed) residuals from the F450W image subtracted by an IRAF \emph{ellipse} brightness model and the contours of the best fit model's time delay surface.
 This demonstrates that, although we did not include any information about the shape of the lensing images in the fit, it is consistent with the predicted distortion for an extended source.
@@
 \caption{Comparison of the observed F814W/I-band surface brightness distribution (Panel (a) and orange contours) and predicted mass distribution from lensing constraints (Panel (b) and pink contours).
-To allow for a qualitative comparison of the contours in Panel (c), the light distribution was turned into a mass distribution by multiplication with the total mass-to-light ratio inside the Einstein radius $\Upsilon_\text{I,tot}^\text{ein}$ in Table \ref{tab:einsteinML}.
+To allow for a qualitative comparison of the contours in Panel (c), the light distribution was turned into a mass distribution by multiplication with the total mass-to-light ratio inside the Einstein radius $\Upsilon_\text{I,tot}^\text{ein} = 5.56 \Upsilon_{I,\odot}$.
 The Einstein radius is overplotted as red dotted circle.
@@
 The smooth black contours correspond to the best fit model in the first column of Table \ref{tab:bestfitlensmodel}.
-The background in Panel (c) shows again the surface brightness subtracted center of the galaxy to make the lensing images visible.
-\Wilma{[TO DO: use $\Upsilon_\text{I,tot}^\text{ein}$ on colorbar]}}
+The background in Panel (c) shows again the surface brightness subtracted center of the galaxy to make the lensing images visible.}
 \label{fig:lenslightcompareALL}
@@
 The corresponding Einstein mass-to-light ratio is therefore $\Upsilon_\text{I,tot}^\text{ein} = 5.56 \Upsilon_{I,\odot}$.
-This is consistent with or slightly larger than the stellar mass-to-light ratio assuming a Salpeter IMF $\Upsilon_\text{I,*}^\text{sal} = 4.7 \pm 1.2$ according to \citet{SWELLSI} and Table \ref{tab:previousresults} (see also discussion in Section \ref{sec:MLdiscussion}).
+This is consistent with or slightly larger than the stellar mass-to-light ratio assuming a Salpeter initial mass function (IMF) $\Upsilon_\text{I,*}^\text{sal} = 4.7 \pm 1.2$ according to \citet{SWELLSI} and Table \ref{tab:previousresults} (see also discussion in Section \ref{sec:MLdiscussion}).
 
@@
 However, the mass distribution is only constraint around the Einstein radius and otherwise an extrapolation.
-
-\Wilma{[TO DO: Make sure IMF is introduced somewhere.]}

### 2016-01-05 docs/results_photometry_v3.02.tex
Small corrections in text and changes in plot legends.

@@
 In this section we construct a model for the J1331's intrinsic light distribution in terms of MGEs (see Section \ref{sec:MGE_theo}).
-We use the HST image in the F814W (I-band) filter (Figure \ref{fig:F814W}) because J1331's central stellar component appears at longer wavelengths (a) smoother and more extended than in the F450W filter (Figure \ref{fig:F450W}), as it is less sensitive to young clumpy star-forming regions, (b) much brighter than the bluish lensing images, and (c) the imaging is less prone to extinction.
+We use the HST image in the F814W (I-band) filter (Figure \ref{fig:F814W}) because J1331's central stellar component appears at longer wavelengths (i) smoother and more extended than in the F450W filter (Figure \ref{fig:F450W}), as it is less sensitive to young clumpy star-forming regions, (ii) much brighter than the bluish lensing images, and (iii) the imaging is less prone to extinction.
 
@@
 This MGE is not used for dynamical modelling, because the dynamics in the outer regions are strongly affected by non-axisymmetries (e.g., spiral arms).
-We use it, however, to estimate the galaxy's total luminosity and effective radius, and to get a prediction for the dynamics of the outer regions.
-\Wilma{[TO DO: No dotted line]}}
+We use it, however, to estimate the galaxy's total luminosity and effective radius, and to get a prediction for the dynamics of the outer regions.}
 \end{figure*}

### 2016-01-06 docs/results_photometry_v3.02.tex
Wrote summary.

@@
 apparent I-band magnitude & $m_\text{I}$ [mag] & 15.77 \\
-total I-band luminosity & $L_\text{tot,I}$ [$10^{10} L_\odot$] & 5.6 \\
+total I-band luminosity & $L_\text{I,tot}$ [$10^{10} L_\odot$] & 5.6 \\
 effective half-light radius & $R_\text{eff}$ [$''$] & 2.6 \\
@@
 \paragraph{Total luminosity and effective radius.} J1331's total I-band luminosity is determined by summing up the luminosity contributions of all the MGE Gaussians for the outer regions (shown as gray lines in Figure \ref{fig:MGEouterRegions}).
-We find $L_\text{tot,I} \simeq 5.6 \cdot 10^{10} ~L_\odot$.
+We find $L_\text{I,tot} \simeq 5.6 \cdot 10^{10} ~L_\odot$.
 This corresponds to an apparent magnitude of $m_I = 15.77~\text{mag}$.

### 2016-01-06 docs/summary_v3.01.tex
Wrote summary.

@@
 
-\Wilma{[TO DO: Ask Glenn and Aaron how much of the above should find its way into the summary.]}
+%Intro:
+J1331 is a massive spiral galaxy which acts as strong gravitational lens for a background source.
+J1331 appears also to be a merger remnant due to it's large counter-rotating core.
+The goal of this work was to recover J1331's matter distribution by means of two methods, gravitational lensing and dynamical modelling.
+We focus on the bulge region of J1331, to complement previous studies of J1331 by \citet{SWELLSIII,SWELLSV}.
+The independent mass constraint which we derive from lensing and dynamics agree very well with each other within $R_\text{eff}$.
+
+In our lensing approach we fitted a scale-free galaxy model to the lensing image position.
+This constrained the Einstein radius to within 2\% ($R_\text{ein}=(0.91\pm0.02)''\simeq(1.83\pm0.04)~\text{kpc}$), and the Einstein mass to within 4\% ($M_\text{ein} = (7.8\pm0.3) \cdot 10^{10} M_\odot$), consistent with results by \citet{SWELLSIII}.
+The recovered mass distribution agrees also very well with the shape of the observed lensing images.
+
+To get a handle of J1331's light distribution we used a MGE fit to J1331's surface brightness in the F814W filter in HST imaging by \citet{SWELLSI}.
+Based on this we found J1331's effective radius to be $R_\text{eff} \simeq 2.6'' \hat{=} 5.2~\text{kpc}$ and its total I-band luminosity to be $L_\text{I,tot} \simeq 5.6 \cdot 10^{10} L_\odot$.
+
+We used axisymmetric JAM modelling to calculate the second velocity moment of a tracer and mass distribution given in terms of MGEs.
+The JAM model of the lens mass model gave a independent prediction which was consistent with observed stellar kinematics from major axis long slit spectrography by \citet{SWELLSV} within $R_\text{eff}$.
+We also fitted mass models with and without NFW halo to the stellar kinematics within $R'=3.5~\text{kpc}$.
+From this we deduced that a mass-follows-light model with constant total mass-to-light ratio is not a good model for J1331---not even in the inner regions.
+To describe the observed stellar kinematics we either require a strong contribution of a dark matter halo already in the bulge, or a strongly varying stellar mass-to-light ratio.
+We also showed that it is possible to construct a model which includes the counter-rotating core and is consistent with the rotation curve at large radii.
+
+While both our independent mass models are consistent with each other within $\sim R_\text{eff}$, they do not agree with previous findings by \citet{SWELLSV}, nor the data at large radii.
+We attribute this to the fact \citet{SWELLSV} derived mass constraints from kinematics in the outer regions only, while we focussed on the inner regions in detail.
+We speculate that a merger might have modified the kinematic structure and/or mass distribution of J1331 such that crucial model assumptions are not valid anymore.
+To resolve the ambiguities in J1331's mass distribution two-dimensional kinematic maps of J1331 from integral-fiel units spectroscopy would be needed.

### 2016-01-07 docs/discussion_futureWork_v3.04.tex
Rewrote section on Future Work.

\subsection{Future work}

Standard JAM modelling approaches seem not to work for J1331. The existing data---photometry and major axis kinematics---is however not sufficient to decide which of our model assumptions lead to the failure to find an overall consistent mass model.

Two-dimensional stellar kinematics would greatly help to resolve this problem. The main future work would be therefore getting high-resolution integral-field spectroscopy for J1331. High spatial resolution would be required to clearly identify J1331's presumably complex kinematic structure. High spectral resolution would be important to be able to reliably measure the low velocity dispersion in the outer regions of J1331.

Specifically 2D kinematics should help to answer the following questions: Is the drop in $v_\text{rms}$ around $R' \sim 3-6~\text{kpc}$ real? Did the long slit spectrograph maybe miss the major axis of the disk? And most importantly: Are the kinematics asymmetric? Is it possible that there even exists a kinematic twist due to the merger in J1331's past?

Furthermore, learning more about different stellar populations in J1331 would lead to valuable constraints for the modelling. While a quick investigation of the photometric colour profile did not reveal obvious colour gradients in J1331's bulge, there could be still stellar $\Upsilon_{I,*}$ variations due to age of metallicity differences. Existing major axis spectroscopy and/or future IFU data could be employed (i) to investigate absorption line indices to confirm (or contradict) the existence of $\Upsilon_{I,*}$ gradients and (ii) to perform stellar population analyses to constrain $\Upsilon_{I,*}$ reliably and independently of kinematics.

Future modelling approaches should fit dynamics (stellar and gas kinematics from) simultaneously with the gravitational lensing (image positions, shape and even flux ratios) in a similar fashion to \citet{SWELLSIV}. To also model the extent, shape and flux of the lensing images, the method by \citet{2004ApJ...611..739T,2003ApJ...590..673W} could be employed, which models the surface brightness distribution of the images and source on a pixelated grid. For this to work a good model for the galactic extinction would be needed---but 2D spectroscopy could also help with this.

All of the would lead to a much better understanding of J1331's structure and mass distribution and therefore answer questions on how mergers might modify spiral galaxies.

### 2016-01-07 docs/results_JAMwithNFW_v3.02.tex
Rewrote section on Future Work.

@@
 The central regions are very well reproduced and we can also nicely predict the rotation curve at larger radii.
-Only at larger radii the $v_\text{rms}$ and $v_\text{rot}$ overestimate the measurements, probably due to a too massive NFW halo.}
+Only at larger radii the $v_\text{rms}$ and $v_\text{rot}$ overestimate the measurements, probably due to a too massive NFW halo.
+\Wilma{[TO DO: There seem to be no minor ticks on x-axis.]}}
 \label{fig:modelB4_vrot}

### 2016-01-13 archive/v3/docs/discussion_futureWork_v3.03.tex
Slightly wrote discussion section on merger.

--- 2015-11-24 docs/discussion_v3.02.tex
@@
-We've presented different dynamical models for the central region of J1331.
-Some of them capture the observed kinematics, but none of them work at both small and large radii.
-In the following we discuss possible reasons, also by comparing our results to previous work.
-
-\subsection{On J1331's central stellar mass-to-light ratio} \label{sec:MLdiscussion}
-
-Some of the ambiguities in recovering J1331's matter distribution could be resolved by learning more about stellar populations with different IMFs in J1331.
-In particular, a sophisticated guess for the stellar mass-to-light ratio in the bulge could be compared to our very reliable measurement of the total mass-to-light ratio inside the Einstein radius (see Table \ref{tab:einsteinML}).
-This would then either support or contradict the presence of a significant amount of DM in the bulge.
-
-Traditional choices for the IMF are the bottom-heavy IMF by \citet{Salpeter1955},
-$$\xi(m) \propto m^{-x}, x=2.35,$$
-where $\xi(m) \diff m$ is the number of stars with mass $m$ in $[m,m+\diff m]$, and the IMFs by \citet{2002Sci...295...82K} and \citet{Chabrier2003}, which are in agreement with each other and predict less low-mass stars.
-
-\citet{Ferreras} found a relation between the central stellar velocity dispersion $\sigma_0$ in early-type galaxies and the IMF slope $x$; a higher $\sigma_0$ suggests a more bottom-heavy IMF.
-For a unimodal (Salpeter-like) IMF and $\sigma_0 \simeq 200~\text{km s}^{-1}$ in J1331 (see Figure \ref{fig:kinematics}) they predict $x \approx 2.33$, which is close to the standard Salpeter slope, also supported by \citet{2014MNRAS.438.1483S}.
-When assuming a bi-modal (Kroupa-equivalent-like) IMF, \citet{Ferreras} predict $x \approx 2.85$ for J1331's central velocity dispersion.
-This is more bottom-heavy than the standard \citet{2002Sci...295...82K} IMF.
-Overall, the central velocity dispersion suggests a rather bottom-heavy IMF in J1331's bulge and therefore large stellar mass-to-light ratio.
-\citet{SWELLSI} estimated J1331's stellar bulge mass given a Salpeter IMF and measured the I-band AB magnitude of the bulge.
-Transformed to a stellar I-band mass-to-light ratio their results would correspond to $\Upsilon_\text{I,*}^\text{sal} = 4.7 \pm 1.2$ (see Table \ref{tab:previousresults}).
-
-We compare our results from Section \ref{sec:results_JAM_NFW} with the study by \citet{SWELLSV}: They found that the bulge of J1331 has an IMF \emph{more} bottom-heavy than the Salpeter IMF from fitting a NFW halo to (1) the Einstein mass and (2) gas kinematics at larger radii $\gtrsim 8''$.
-In Section we fitted a mass model with NFW halo to (1) the Einstein mass and (2) stellar kinematics within $\sim 3.5''$.
-Our best fit $\Upsilon_\text{I,*} = 4.2 \pm 0.2$ (see Table \ref{tab:modelB4_bestfit}) indicates a \emph{less} bottom-heavy IMF than the Salpeter IMF.
-\cite{SWELLSV} found systematically lower NFW halo masses ($v_\text{circ,halo}(5'') \sim 120~\text{km s}^{-1}$ according to their Figure 2) than we did ($v_\text{circ,halo}(5'') \sim 200~\text{km s}^{-1}$).
-
-We compare our result from Section \ref{sec:results_JAM_SB} with the findings from \citet{SWELLSI}: We created a dynamical model from only the surface brightness distribution and an increasing mass-to-light ratio profile without additional DM halo.
-We found that such a model would be perfectly consistent with the Einstein mass and predict a total $\Upsilon_\text{I,tot}(R'\sim0) = 2.53$ in the very center of J1331.
-This is close to the stellar $\Upsilon_\text{I,*}^\text{Chabrier} = 2.5 \pm 0.6$ based on the estimates by \citet{SWELLSI} for the bulge stellar mass using the Chabrier IMF , i.e., less bottom-heavy (more bluish) population.
-
-%==============
-\begin{table*}
-\centering
-\begin{tabular}{cccccc}
-\hline\hline
-& & \multicolumn{2}{c}{Chabrier IMF} & \multicolumn{2}{c}{Salpeter IMF}\\
-      &  $L$ [$10^{10}L_{\odot}$]                & $M_*$ [$10^{10}M_\odot$]               & $\Upsilon_\text{I,*}^\text{chab}$ & $M_*$ [$10^{10}M_\odot$] & $\Upsilon_\text{I,*}^\text{sal}$ \\\hline
-bulge &   $3.10 \pm 0.15 $  & $7.8 \pm 1.8$ & $2.5 \pm 0.6$ & $14.5 \pm 3.7 $ & $4.7 \pm 1.2$ \\
-disk  &   $2.35 \pm 0.11 $  & $2.9 \pm 0.7$ & $1.2 \pm 0.3$ & $5.2 \pm 1.1$ & $2.2 \pm 0.5$ \\
-total &   $5.45 \pm 0.19$ & $10.6 \pm 1.9$& & $19.7 \pm 3.9$&\\\hline
-\end{tabular}
-\caption{Total I-band luminosity, stellar mass and mass-to-light ratio, calculated from the I-band AB magnitudes and stellar masses found for J133's bulge and disk by \citet{SWELLSI} (their table 2) for comparison with this work.
-The transformation from AB magnitudes to the Johnson-Cousins I-Band used the relation $I[\text{mag}] = I[\text{ABmag}] - 0.309$ from \citet{FG1994} (their table 2).
-For the conversion from apparent magnitude to total luminosity the redshift $z=0.113$ \citet{SWELLSIII} was turned into a luminosity distance using the cosmology by \citet{WMAP5cosm}.
-}
-\label{tab:previousresults}
-\end{table*}
-%==============
-
-\subsection{On J1331's central kinematics}
-
-%==============
-\begin{figure}
-\centering
-  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_vcirc.ps}
-  \caption{Circular velocity curve. \Wilma{[TO DO: Write caption]}}
-  \label{fig:vcirc_comparison}
-\end{figure}
-%==============
-
-In Figure \ref{fig:vcirc_comparison} we compare the circular velocity curve found by \citet{SWELLSV} with a mass-follows-light model scaled to fit our Einstein mass (by multiplying the light distribution in Table \Wilma{[TO DO]} with $\Upsilon_\text{I,tot}^\text{ein} = 5.6$).
-Within $R < 5''$ they agree with each other.
-
-The models in this work used more than just the Einstein mass to constrain the matter distribution at small radii: The lens mass model constrained also the shape of the mass distribution within the lensing image configuration at $R_\text{ein} \sim 1''$.
-The dynamical models used stellar kinematics inside $R' \simeq 3.5''$ \Wilma{[TO DO: Check]}.
-We compare the lens mass model's $v_\text{circ}$ (for $\alpha=1.0\pm 0.1$) with the NFW JAM model (Table \Wilma{[TO DO]}) in Figure \ref{fig:vcirc_comparison} as well.
-Within and around $R_\text{ein}$ they are consistent with each other, even though they where independently derived.
-They do not agree with the result by \citet{SWELLSV} and in Section \ref{sec:results_JAM_SB} we showed, that ``mass-follows-light'' is not a good model for J1331.
-
-Overall, we were not able to find a consistent explanation for J1331's central $v_\text{rms}$ dip.
-It cannot be due to tangential velocity anisotropy in the center alone (see Section \ref{sec:results_JAM_SB}, Figure \ref{fig:JAM_modelA2}).
-It also cannot be explained by a strong contribution of DM inside the bulge together with a moderate tagential velocity anisotropy, because the corresponding DM halos would still be too massive to fit the data in the outer regions (see Section \ref{sec:results_JAM_NFW}, Figure \ref{fig:modelB4_vrms}]).
-
-Another feature in the stellar kinematics, that none of our JAM models was able to reproduce in the slightest and which we therefore excluded in the modelling, was the dip in $v_\text{rms}$ around $\sim 6''$, which occurs around the transition from bulge to disk (see Figures \ref{fig:F814W} and \ref{fig:kinematics}).
-
-\subsection{On J1331's possible merger history}
-
-\Wilma{[TO DO: Remove minor in merger.]}
-
-J1331 has a large counter-rotating stellar core within $\sim 2''$.
-This suggests a process in J1331's past in which two components with angular momenta oriented in opposite directions were involved.
-Accretion of gas on retrograde orbits and subsequent star formation could lead to a younger and counter-rotating stellar population \Wilma{[TO DO: REF]}.
-However, to form enough stars such that the net rotation of the large and massive core is retrograde, a very large amount of gas would have had to be accreted by J1331---which is not very likely [TO DO: REF].
-
-Another scenario are galaxy mergers.
-Major mergers including large amounts of gas can form kinematically decoupled cores (KDCs), see e.g., \Wilma{[TO DO: REF: Lauren Hofman et al 2010 - read paper how this fits with the reverse color gradient]}.
-During a minor merger, the dense nucleus of a satellite galaxy on a retrograde orbit could survive the dissipationless accretion and could spiral to the core due to tidal friction \citep{1984ApJ...287..577K}.
-Usually large bulges of spirals or ellipticals are reddest in the center and become bluer further out.
-Because star formation in low-mass satellite galaxies occurred later than in massive galaxies \Wilma{[TO DO: REF]}, the merger remnant would now host a younger and bluer population with lower velocity dispersion within the older and redder bulge of the massive progenitor.
-Such a reverse color gradient could correspond to an increasing stellar mass-to-light ratio.
-
-The merger theory could explain and support our findings from dynamical modelling and the previous sections, that J1331 might have an increasing stellar mass-to-light ratio within its core.
-
-\subsection{On possible modelling failures and speculations how to resolve them}
-
-\Wilma{[TO DO: Include in discussion: Kinematic twist due to merger.
-Bulge and disk have different kinematic major axis, and the measured velocities in the disk, which are off from the major axis, are much lower than the actual maximum vcirc.
-Could explain the dips in the outer regions.]}
-
-Another effect that minor mergers can have on galaxies are a misalignement (warp) of the photometric and kinematic major axis \Wilma{[TO DO: REF]}.
-Would this be the case for J1331 the assumption of axisymmetry is not true anymore and our dynamical modelling would fail.
-
-Mergers also could have changed the 3D shape of the dark matter halo and the NFW halo was therefore not a good model for J1331's dark matter halo.
-We also tried to model J1331 with a cored logarithmic halo.
-However, due to degeneracies in the modelling, we were not able to either constrain the profile for a cored logarithmic halo, or to rule it out.
-
-\Wilma{[TO DO: Include in this discussion the findings from the color profile.]}
-
 \subsection{Future work}

### 2016-01-25 docs/results_JAMwithSB_v3.01.tex
Edited captions.

@@
   \includegraphics[height=6cm]{fig/jam_A2_vrms.ps}
-  \caption{Comparison of the symmetrized $v_\text{rms}$ data of J1331 (blue dots) with a best fit dynamical JAM model (orange line) assuming mass-follows-light and with two free parameters: $\Upsilon_\text{I,tot}^\text{dyn}$, the total I-band mass-to-light ratio found from dynamics, which converts the observed surface brightness in Table \ref{tab:MGEF814W} into a mass distribution, and the velocity anisotropy parameter $\beta_z$.
+  \caption{Comparison of the symmetrized $v_\text{rms}$ data of J1331 (blue dots) with a best fit dynamical JAM model (orange line) assuming mass-follows-light and with two free parameters: $\Upsilon_\text{I,tot}^\text{dyn}$, the total constant I-band mass-to-light ratio which converts the observed surface brightness in Table \ref{tab:MGEF814W} into a mass distribution, and the velocity anisotropy parameter $\beta_z$.
 The ``best'' fit is $\Upsilon_\text{I,tot}^\text{dyn} = 4.8 \pm 0.1$ and $\beta_z = -0.5$, where the latter is however pegged at the lower limit of the allowed value range.
@@
 \end{subfigure}
-\caption{JAM model found by fitting an increasing total mass-to-light ratio $\Upsilon_\text{I,tot}(R')$ profile used to generate a mass model from the light distribution.
-This is done by assigning a different mass-to-light ratio to each Gaussian in the MGE in Table \ref{tab:MGEF814W}.
-\emph{Panel (a):} Comparison between the stellar $v_\text{rms}$ data (blue points) and the best fit model (green line).
-\emph{Panel (b):} Projected mass-to-light profile $\Upsilon_\text{I,tot}(R')$ along the major axis (blue line, left axis) of the best fit model.
-The best fit mass-to-light ratios of the first four Gaussians are plotted against each Gaussians $\sigma$ (yellow stars).
-The two Gaussians with the largest $\sigma$ (the fifth is not shown) have the same best fit mass-to-light ratio.
-Shown is also the enclosed mass inside the projected radius $R'$ on the sky (green line, right axis).
-The enclosed mass curve is overplotted with the independent finding for the Einstein mass $\pm 4 \%$ in Table \ref{tab:bestfitlensmodel} (red dot) at the Einstein radius (red dotted line).
-Shown is also the effective half-light ratio $R_\text{eff}$ (black dotted line).
-\Wilma{[TO DO: Mention second axis only after 1st axis is explained.]}}
+\caption{JAM model found by fitting a galaxy model with increasing total mass-to-light ratio profile $\Upsilon_\text{I,tot}(R')$ to the symmetrized $v_\text{rms}$ data (blue dots).
+The mass distribution is generated by assigning a different mass-to-light ratio $\Upsilon_{\text{I,tot,}i}$ to each Gaussian $i$ in the light distribution MGE in Table \ref{tab:MGEF814W}.
+The $\Upsilon_{\text{I,tot,}i}$ were treated as free fit parameters.
+\emph{Panel (a):} Comparison between the stellar $v_\text{rms}$ data (blue dots) and the best fit model (green line).
+\emph{Panel (b):} Projected total mass-to-light profile $\Upsilon_\text{I,tot}(R')$ along the major axis (blue line, left axis) of the best fit model.
+The best fit mass-to-light ratios $\Upsilon_{\text{I,tot,}i}$ are plotted against $\sigma_i$ for each MGE Gaussian ($i<5$, yellow stars).
+(The Gaussians $i=4$ and $i=5$ have the same $\Upsilon_{\text{I,tot,}i}$.) Shown is also the enclosed mass inside the projected radius $R'$ on the sky, $M(<R')$ (green line, right axis).
+The enclosed mass curve is overplotted with the independent finding for the Einstein mass $\pm 4 \%$ in Table \ref{tab:bestfitlensmodel} (red dot) at the Einstein radius (red dotted line); the agreement is very good.}
 \label{fig:modelG}

### 2016-01-25 docs/results_lensing_v3.01.tex
Edited captions.

@@
 \centering
-\begin{minipage}{70mm}
+\caption{Positions of the lensing images (A-D) and the galaxy center (G) in Figure \ref{fig:lens_just_imgpos}.
+The image positions were determined from the lens \Wilma{[TO DO: lens subtracted???
+Check.]} subtracted image for J1331 in Figure 4 of \citet{SWELLSIII}, rotated to the $(x,y)$ coordinate system in Figure \ref{fig:lens_just_imgpos}.
+The pixel scale is 1 pixel = $0.05''$ and the error of each image position is $\pm$ 1 pixel.}
 \begin{tabular}{r|rrrr|c}
@@
 \end{tabular}
-\caption{Positions of the lensing images (A-D) and the galaxy center (G) in Figure \ref{fig:lens_just_imgpos}.
-The image positions were determined from the lens subtracted image for J1331 in Figure 4 of \citet{SWELLSIII}, rotated to the $(x,y)$ coordinate system in Figure \ref{fig:lens_just_imgpos}.
-The pixel scale is 1 pixel = $0.05''$ and the error of each image position is $\pm$ 1 pixel.}
 \label{tab:lenspos}
-\end{minipage}
 \end{table}
@@
 For the best fit lens model we show the Einstein radius (red dotted circle) and the critical curve (red solid line), which are located in the lens plane.
-We also show the caustic (green solid line) corresponding to the critical curve and best fit source position (green dot), which are located in the source plane.
+We also show the caustic (green solid line) corresponding to the critical curve and the best fit source position (green dot), which are located in the source plane.
 For $\alpha=1$ the critical curve is a contour of constant surface density of the mass model.
@@
 \centering
-\caption{Best fit lens model found from the peak image positions in Table \ref{tab:lenspos} (first column) following the procedure described in Section \ref{sec:lensing_theo} and assuming a flat rotation curve ($\alpha = 1$).
-The second column gives the corresponding best fit mean and standard deviation derived from Monte Carlo sampling of the Gaussian uncertainties around the image positions (column 2).}
+\caption{Best fit lens model (first column) found from the peak image positions in Table \ref{tab:lenspos} following the procedure described in Section \ref{sec:lensing_theo} and assuming a flat rotation curve ($\alpha = 1$).
+The second column gives the corresponding best fit mean and standard deviation derived from Monte Carlo sampling of the Gaussian uncertainties around the image positions, with the relative error given in parentheses.}
 \begin{tabular}{llrrclr}
@@
  &  & \multicolumn{1}{c}{lens model for} &\multicolumn{4}{c}{lens model from Monte Carlo sampling  } \\
- &  & \multicolumn{1}{c}{peak image positions}  & \multicolumn{4}{c}{of image positions }  \\ \hline
+ &  & \multicolumn{1}{c}{peak image positions}  & \multicolumn{4}{c}{of image position uncertainties}  \\ \hline
 Einstein radius      & $R_\text{ein}$ [$''$]             & $0.907$ & $0.91$  & $\pm$ & $     0.02$ & ($2\%$)\\
@@
   \includegraphics[width=.9\linewidth]{fig/lens_surface_density.ps}
-  \caption{Predicted mass distribution.}
+  \caption{Lens model mass distribution.}
   \label{fig:lenscomparemass}
@@
 \end{subfigure}
-\caption{Comparison of the observed F814W/I-band surface brightness distribution (Panel (a) and orange contours) and predicted mass distribution from lensing constraints (Panel (b) and pink contours).
-To allow for a qualitative comparison of the contours in Panel (c), the light distribution was turned into a mass distribution by multiplication with the total mass-to-light ratio inside the Einstein radius $\Upsilon_\text{I,tot}^\text{ein} = 5.56 \Upsilon_{I,\odot}$.
+\caption{Comparison of the observed F814W/I-band surface brightness distribution (panel (a) and orange contours) and derived mass distribution from lensing constraints (panel (b) and pink contours).
+To allow for a qualitative comparison of the contours in panel (c), the light distribution was turned into a mass distribution by multiplication with the total mass-to-light ratio inside the Einstein radius, $\Upsilon_\text{I,tot}^\text{ein} = 5.56 \Upsilon_{I,\odot}$.
 The Einstein radius is overplotted as red dotted circle.
@@
 The smooth black contours correspond to the best fit model in the first column of Table \ref{tab:bestfitlensmodel}.
+We find, that the lens mass model is more roundish than the light distribution.
 The background in Panel (c) shows again the surface brightness subtracted center of the galaxy to make the lensing images visible.}

### 2016-01-25 docs/results_photometry_v3.02.tex
Edited captions.

@@
 \centering
-\caption{Galaxy Parameters of J1331.}
+\caption{Galaxy parameters of J1331.}
 \begin{tabular}{lllr}
 \hline
-redshift \citep{SWELLSIII}                 & $z_d$ & 0.113 \\
-angular diameter distance & $D_d$ [Mpc] & 414 \\
-scaling                   & 1 kpc / 1 $''$ & 2.006 \\
+redshift \citep{SWELLSIII}                 & $z_d$ & $0.113$ \\
+angular diameter distance & $D_d$ [Mpc] & $414$ \\
+scaling                   & 1 kpc / 1$''$ & $2.006$ \\
 position angle from North          & $\phi$ [degrees] & $42.90^\circ$\\
-average axis ratio & $q'$ & 0.598\\
-average ellipticity & $\epsilon = 1 - q'$ & 0.402 \\
-apparent I-band magnitude & $m_\text{I}$ [mag] & 15.77 \\
-total I-band luminosity & $L_\text{I,tot}$ [$10^{10} L_\odot$] & 5.6 \\
-effective half-light radius & $R_\text{eff}$ [$''$] & 2.6 \\
+average axis ratio & $q'$ & $0.598$\\
+average ellipticity & $\epsilon = 1 - q'$ & $0.402$ \\
+estimated inclination & $i$ [degrees] & $70^\circ$\\
+apparent I-band magnitude & $m_\text{I}$ [mag] & $15.77$ \\
+total I-band luminosity & $L_\text{I,tot}$ [$10^{10} L_\odot$] & $5.6$ \\
+effective half-light radius & $R_\text{eff}$ [$''$] & $2.6$ \\
 & $R_\text{eff}$ [pc]& 5.2 & \\
@@
   \includegraphics[width=.8\columnwidth]{fig/1331F814W_MGE_disk_L.ps}
-  \caption{MGE for J1331's outer regions.}
+  \caption{MGE and IRAF \emph{ellipse} model for J1331's outer regions.}
  \label{fig:MGEouterRegions}
@@
 \caption{MGEs for J1331's surface brightness distribution.
-Comparison of contours with constant F814W surface brightness (orange lines) with the corresponding iso-brightness contours of the best fit MGE, convolved with the PSF in Table \ref{tab:MGEF814W}, (gray lines).
-The black line has a length of $10''$ and it's orientation corresponds to the galaxy's position angle as found in Table \ref{tab:galaxyparameters}.
-For comparison the Einstein radius as found in Table \ref{tab:bestfitlensmodel}  is indicated as red dashed line.
-\emph{Panel (a)} Central regions of J1331.
+Comparison of contours with constant F814W surface brightness (orange lines) with the corresponding iso-brightness contours of the best fit MGE, convolved with the PSF in Table \ref{tab:MGEF814W}, (grey lines).
+The black line has a length of $10''$ and its orientation corresponds to the galaxy's position angle as found in Table \ref{tab:galaxyparameters}.
+For comparison the Einstein radius as found in Table \ref{tab:bestfitlensmodel}  is indicated as red dashed circle.
+\emph{Panel (a):} Central regions of J1331.
 The MGE model is a good representation of the galaxy's light distribution along the major axis within $\sim 5''$.
@@
 This MGE is used as model for the stellar tracer distribution in the dynamical Jeans modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}.
-\emph{Panel (b)} Outer regions of J1331.
-The orange lines indicate here contours of a smooth IRAF \emph{ellipse} fit to J1331 in the F814W filter; the gray lines are the corresponding best fit MGE.
-The green box corresponds to the image section shown in Panel (a).
+\emph{Panel (b):} Outer regions of J1331.
+The orange lines indicate here contours of a smooth IRAF \emph{ellipse} fit to J1331 in the F814W filter; the grey lines are the corresponding best fit MGE.
 This MGE is not used for dynamical modelling, because the dynamics in the outer regions are strongly affected by non-axisymmetries (e.g., spiral arms).
@@
 
-\paragraph{Total luminosity and effective radius.} J1331's total I-band luminosity is determined by summing up the luminosity contributions of all the MGE Gaussians for the outer regions (shown as gray lines in Figure \ref{fig:MGEouterRegions}).
+\paragraph{Total luminosity and effective radius.} J1331's total I-band luminosity is determined by summing up the luminosity contributions of all the MGE Gaussians for the outer regions (shown as grey lines in Figure \ref{fig:MGEouterRegions}).
 We find $L_\text{I,tot} \simeq 5.6 \cdot 10^{10} ~L_\odot$.

### 2016-01-25 LensingPaper_draft_v3.05.tex
Started version v3.05 (one document only).

\documentclass[useAMS,usenatbib]{mnras}

%_____GENERAL PACKAGES_____
\usepackage{amsmath}	%for \text{} in math mode
\usepackage{amssymb}	%for symbols

%_____FIGURES_____
\usepackage{graphicx}	%for including images
\usepackage{float}	%for [Hhtb] etc of figures
\usepackage{grffile}    %for using underscores in figure filenames
\usepackage{subcaption} %for having sub-captions in figures with multiple panels
\usepackage{placeins} %for \FloatBarrier, which forces all figures to be printed before continuing

%_____SYMBOLS_____
\usepackage{ mathrsfs } %for slanted letters in math mode

%_____FORMAT_____
%\setcounter{secnumdepth}{3}	%depth of section numbering
\usepackage{hyperref} %ready-to-lick referencing

%_____MACROS______
\newcommand*\diff{\mathop{}\!\mathrm{d}}
\newcommand*\Diff[1]{\mathop{}\!\mathrm{d^#1}}
%\newcommand{\vect}[1]{\boldsymbol{#1}} % Uncomment for BOLD vectors.
\newcommand{\vect}[1]{\vec{#1}} % Uncomment for ARROW vectors.
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\Wilma}[1]{\textcolor{Magenta}{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title[A spiral galaxy's mass distribution uncovered]{A spiral galaxy's mass distribution uncovered through lensing and dynamics}
\author[W.H. Trick, G. van de Ven and A.A. Dutton]{Wilma H. Trick$^{1}$\thanks{E-mail:
trick@mpia.de}, Glenn van de Ven$^{1}$ and Aaron A. Dutton$^{1}$\\
$^{1}$Max-Planck-Institute for Astronomy, K\"{o}nigstuhl 17, 69117 Heidelberg, Germany}
\begin{document}

\date{Accepted ???. Received ???; in original form ???}

\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2015}

\maketitle

\label{firstpage}

%--------------------------------------------
\begin{abstract}
We investigate the matter distribution of a spiral galaxy with counter-rotating stellar core, SDSS J1331+3628 (J1331), independently with gravitational lensing and dynamical modelling. By fitting a gravitational potential model to a quadruplet of lensing images around J1331's bulge, we tightly constrain the mass inside the Einstein radius $R_\text{ein}=(0.91\pm0.02)''(\simeq1.83\pm0.04~\text{kpc})$ to within 4\%: $M_\text{ein} = (7.8\pm0.3) \cdot 10^{10} M_\odot$. We model observed long-slit major axis stellar kinematics in J1331's central regions by finding Multi-Gaussian Expansion (MGE) models for the stellar and dark matter distribution that solve the axisymmetric Jeans equations. The lens and dynamical model are independently derived, but in very good agreement with each other around $\sim R_\text{ein}$. We find that J1331's center requires a steep total mass-to-light ratio gradient. A dynamical model including a NFW halo (with virial velocity $v_{200} \simeq 240 \pm 40~\text{km s}^{-1}$ and concentration of $c_{200} \simeq 8 \pm 2$) and moderate tangential velocity anisotropy ($\beta_z \simeq -0.4 \pm 0.1$) can reproduce the signatures of J1331's counter-rotating core and predict the stellar and gas rotation curve at larger radii. However, our models do not agree with the observed velocity dispersion at large radii. We speculate that the reason could be a non-trivial re-distribution of matter due to a possible merger event in J1331's recent past.
\end{abstract}
%--------------------------------------------

\begin{keywords}
gravitational lensing: strong -- stars: kinematics and dynamics -- galaxies: kinematics and dynamics -- galaxies: photometry -- galaxies: structure
\end{keywords}

%--------------------------------------------
\section{Introduction}
%--------------------------------------------

%--------------------------------------------
Gravitational lensing and dynamical modelling provide independent constraints on the mass distribution of galaxies. Combining them allows for valuable cross-checking opportunities to disentangle the stellar and dark matter (DM) content of galaxies.

Cosmological simulations suggest that cold DM forms cuspy halos following a Navarro-Frenk-White (NFW) profile \citep{NFW96}. However, the existence of central DM density cusps in massive galaxies depends strongly on the stellar mass-to-light ratio (e.g., \citealt{2011MNRAS.416..322D}) and DM dominated dwarf galaxies even favour DM halos with cores (e.g., \citealt{1994Natur.370..629M,2001ApJ...552L..23D}). This discrepancy, known as the core-cusp problem, might be resolved by galaxy formation processes such as mergers and outflows (e.g., \citealt{2001ApJ...560..636E,2012MNRAS.421.3464P}).

Determining the overall mass distribution in massive galaxies and separating the DM from the stellar mass components is therefore a crucial step in better understanding the structure and formation of galaxies and nature of DM.

Massive galaxies can act as gravitational lenses, deflect the light of background sources and give rise to multiple images. This strong gravitational lensing tightly constrains the projected total mass of the lens galaxy inside $\sim 1''$ (e.g., \citealt{2010ARA&A..48...87T}).

The mass profile at larger galactocentric radii can be probed by gas rotation curves that directly measure the galaxy's circular velocity profile (e.g., \citealt{1980ApJ...238..471R})\Wilma{[TO DO: Can I use this here?]}. However, due to its dissipative nature, gas motions are very sensitive to disturbances by e.g., spiral arms and bars (e.g., \citealt{2004dad..book.....S}).

Because stars are dissipationless dynamical tracers and present almost everywhere in the galaxy, stellar dynamical modelling can complement mass constraints from lensing at small and gas motions at large radii. As stellar motions are complex---a bulk rotation around one principal axis combined with random motions in all coordinate directions---, full dynamical modelling of rotation, dispersion and velocity anisotropies is needed to deduce the matter distribution.

The Sloan WFC Edge-on Late-type Lens Survey (SWELLS, WFC = Wide field camera) \citep{SWELLSI,SWELLSII,SWELLSIII,SWELLSIV,SWELLSV,SWELLSVI} is dedicated to find and investigate spiral galaxies, which are (a) strong gravitational lenses and (b) seen almost edge-on, such that rotation curves can be easily measured. By combining lensing and dynamical modelling degeneracies inherent in both methods can be broken.

One of the SWELLS galaxies is the massive spiral SDSS J1331+3628, to which we refer as J1331 in the remainder of this work. It has bluish spiral arms and a large reddish bulge (see Figures \ref{fig:F450W} and \ref{fig:F814W}), which is superimposed by a quadruplet of extended bluish images approximately at a distance of $1''$ from the galaxy center (see Figure \ref{fig:lens_just_imgpos}). The lensed object might be a star-forming blob of a background galaxy. J1331 stands out of the SWELLS sample because of its large counter-rotating core (see Figure \ref{fig:kinematics}), which might be an indication that J1331 underwent a merger in its recent past.

\citet{SWELLSI} confirmed that J1331 was a strong gravitational lens, measured its apparent brightness and estimated the stellar masses of disk and bulge. The lensing properties of J1331 were first analysed by \citet{SWELLSIII}. \citet{SWELLSV} measured the gas and stellar kinematics along the major axis and deduced J1331's mass profile from the gas rotation curve at large radii and total mass inside the Einstein radius from gravitational lensing, focusing mostly on the outer regions of J1331.

The goal of this work is to complement the previous work on J1331 by an in-depth analysis of the matter distribution in J1331's inner regions. We use stellar dynamical modelling in addition to lensing constraints, similar to a study of the Einstein Cross by \citet{GlennEC}. We attempt to disentangle the stellar and DM components and test if employed axisymmetric Jeans models work also in the presence of a counter-rotating core. Ideally, this work on J1331 could also help understanding how mergers modify the mass distribution of a galaxy.

This paper is organized as follows: Section \ref{sec:data} summarizes the data, Section \ref{sec:Modelling} gives an overview of the modelling techniques used in this work, and Section \ref{sec:Results} presents our results on the surface photometry of J1331 using Multi-Gaussian expansions (Section \ref{sec:MGE_results}), constraints from lensing (Section \ref{sec:results_lensing}) and Jeans modelling based on the surface brightness only (Section \ref{sec:results_JAM_SB}) and including a NFW DM halo (Section \ref{sec:results_JAM_NFW}). Finally Section \ref{sec:Discussion} uses the result to discuss J1331's stellar mass-to-light ratio, possible merger history and starting points for future work.
%--------------------------------------------

%============================================
\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/first_glimpse_450.ps}
  \caption{J1331 in the F450W filter.}
  \label{fig:F450W}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/first_glimpse_814.ps}
  \caption{J1331 in the F814W filter.}
  \label{fig:F814W}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_imgpos.ps}
  \caption{Lensing images around the galaxy center.}
  \label{fig:lens_just_imgpos}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/stellar_kinematics_data.ps}
  \caption{Stellar kinematics by \citet{SWELLSV}.}
  \label{fig:kinematics}
\end{subfigure}
\caption{Hubble Space telescope (HST) images and stellar kinematics of the galaxy SDSS J1331+3628 (J1331), which has a large counter-rotating core and whose bulge acts as a strong lens for a bluish background source. \emph{Panel (a) and (b):} HST/WFPC2/WFC3 images of J1331 by \citet{SWELLSI} in two filters, F450W in panel (a) and F814W in panel (b). The black solid line in panel (b) shows the orientation of the major-axis. Its length is $10''$ and it marks approximately the region within which we carry out the dynamical modelling. \emph{Panel (c):} Lensing images in the central region of J1331.  An IRAF \emph{ellipse} model was fitted to and then subtracted from the galaxy's F450W surface brightness in panel (a). The (smoothed) residuals within the white square in panel (a) are shown in panel (c). The four bright blobs (A, B, C and D) which are visible in the residuals are arranged in a typical strong lensing configuration around the center of the galaxy (G). (The configuration of the two additional blobs which lie approximately on a line with A, B and G does not suggest that these blobs are a lensing doublet. They might rather be star forming regions of a background galaxy.) \emph{Panel (d):} Stellar Kinematics along the galaxy's major axis as measured by \citet{SWELLSV}. Shown are line-of-sight rotation velocity $v_\text{rot}$ (top), line-of-sight velocity dispersion $\sigma$ (middle) and the rms-velocity $v_\text{rms} = \sqrt{v_\text{rot}^2 + \sigma^2}$ (bottom). The dashed line indicates the galaxy's effective half-light radius (in the F814W filter), $R_\text{eff} = 2.6'' = 5.2~\text{kpc}$. The $v_\text{rot}$ curve reveals that J1331 has a counter-rotating core within $R_\text{eff}$.}
\label{fig:specialJ1331}
\end{figure*}
%============================================

%--------------------------------------------
\section{Data} \label{sec:data}
%--------------------------------------------

%--------------------------------------------
\subsection{Redshift and position}
%--------------------------------------------

%--------------------------------------------
J1331 is located at right ascension = 202.91800$^\circ$ and a declination = 36.46999$^\circ$ (epoch J2000). \citet{SWELLSI} found from SDSS spectra that J1331 has two redshifts inside $1''$: J1331 itself has $z_d = 0.113$ and $z_s = 0.254$ is the redshift of the lensed background source \citep{SWELLSIII}. According to the WMAP5 cosmology \citep{WMAP5cosm}, J1331 has an angular diameter distance of 414 Mpc, which translates into a transverse scaling of $1'' \hat{=} 2.01~\text{kpc}$.

%--------------------------------------------
\subsection{HST imaging}
%--------------------------------------------

%--------------------------------------------
We use HST imaging of J1331 by \citet{SWELLSI}. They performed high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) and its WF3 CCD chip. The images are a combination of four exposures with each an exposure time of $400~\text{sec}$ and were drizzled to a pixel scale of 1 pixel = $0.05''$. In particular, we use the images in the filters F450W, to identify the positions of the bluish lensing images, and F814W (I-band) to create a surface brightness MGE model of the reddish bulge.

%--------------------------------------------
\subsection{Stellar kinematics}
%--------------------------------------------

%--------------------------------------------
For the dynamical modelling we use the stellar kinematics for J1331 measured by \citet{SWELLSV}. They obtained long-slit spectra along J1331's major-axis with the Low Resolution Imaging Spectrograph (LRIS) on the Keck I 10m telescope. The width of the slit was $1''$ and the seeing conditions had a FWHM of $\sim 1.1''$. 1D Spectra for spatial bins of different widths along the major axis were extracted. They measured line-of-sight stellar rotation velocities ($v_\text{rot}$) and stellar velocity dispersion ($\sigma$) from the spectrum containing the absorption lines Mgb (5177 \AA) and FeII (5270, 5335 and 5406 \AA) (analogous to \citealt{SWELLSII}). Gas kinematics were extracted from Gaussian line profile fits to H$\alpha$ (6563 \AA) and [NII] (6583 and 6548 \AA) emission lines, as tracers for ionized gas.

The stellar kinematics, $v_\text{rot}$, $\sigma$ and $v_\text{rms}^2=v_\text{rot}^2 + \sigma^2$ are shown in Figure \ref{fig:kinematics}. The rotation curve reveals a counter-rotating core within $2''\simeq$ 4 kpc. Outside of $\sim 3.5''$ there is a steep drop in the dispersion. This could indicate the boundary between the pressure supported bulge and the rotationally supported disk, which appears around this radius in the F450W filter in Figure \ref{fig:F450W}. However, in the brighter F814W filter in Figure \ref{fig:F814W} the large reddish bulge extends out to $\sim5''$.

Inside of $\sim 4''$, the data appears to be symmetric, outside of this the assumption of axisymmetry seems not to be valid anymore, considering the data. We add $-2.3~\text{km s}^{-1}$ to the $v_\text{rot}$ to ensure $v_\text{rot}(R'=0) \sim 0$ as a possible correction term for a misjudgement of the systemic velocity. We also symmetrize the data within $4''$ and asign a minimum error of $\delta v_\text{rms} > 5~\text{km s}^{-1}$ to the $v_\text{rms}$ data. In the JAM modelling, which is based on the assumption of axisymmetry, only stellar kinematics with $R'  \lesssim 2.5''$ or $R' \lesssim 4''$ are used. Another reason to restrict to modelling on the bulge region is that our MGE in Table \ref{tab:MGEF814W} is only a good representation of J1331's F814W light distribution inside $\sim 5''$.
\Wilma{[TO DO: noch mal die data section editen]}
%--------------------------------------------

%--------------------------------------------
\section{Modelling} \label{sec:Modelling}
%--------------------------------------------

%--------------------------------------------
\subsection{Surface brightness model} \label{sec:MGE_theo}
%--------------------------------------------

%--------------------------------------------
\subsubsection{Multi-Gaussian Expansion (MGE)}
%--------------------------------------------

%--------------------------------------------
MGEs are used to parametrize the observed surface brightness (or projected total mass) of a galaxy as a sum of $N$ 2-dimensional, elliptical Gaussians \citep{1991ApJ...366..599B,1992A&A...253..366M,1994A&A...285..723E,1999MNRAS.303..495E}. This work makes use of the algorithm and code\footnote{The IDL code package for fitting MGEs to images by \citet{Cap02} is available online at \url{http://www-astro.physics.ox.ac.uk/~mxc/software}. The version from June 2012 was used in this work.} by \citet{Cap02}. We assume all Gaussians to have the same center and position angle $\phi$, i.e., the orientation of the Gaussians' major axis measured counter-clockwise from the $y'$-axis of the coordinate system with polar coordinates $(R',\theta')$. Then the surface brightness can be written as
\begin{eqnarray}
I(R',\theta') &=& \sum_{i=1}^{N} I_{0,i} \exp\left[ - \frac{1}{2\sigma_i^2} \left(x^{'2} + \frac{y^{'2}}{q_i^{'2}}\right)\right]\label{eq:MGEgeneral}\\
\text{with } I_{0,i} &=& \frac{L_i}{2\pi \sigma_i^2 q'_i}\label{eq:centralItotalL}\\
\text{and } x'_i &=& R' \cos(\theta' - \phi)\nonumber\\
y'_i &=& R' \sin(\theta' - \phi),\nonumber
\end{eqnarray}
where $I_{0,i}$ is the central surface brightness of each Gaussian, $L_i$ its total luminosity, $\sigma_i$ its dispersion along the major axis and $q'_i$ the axis ratio between the elliptical Gaussian's major and minor axis.

\subsubsection{Point spread function (PSF)}

We can also expand the telescope's PSF as a sum of circular Gaussians,
\begin{equation}
\text{PSF}(x',y') = \sum_j \frac{G_j}{2 \pi \delta_j^2} \exp\left[- \frac{1}{2 \delta_j^2} \left({x'}^2 + {y'}^2 \right)\right], \label{eq:PSFgeneral}
\end{equation}
where $\sum_j G_j = 1$ and $\delta_j$ are in this case the dispersions of the circular PSF Gaussians.

The observed surface brightness distribution is a convolution of the intrinsic surface brightness in Equation \eqref{eq:MGEgeneral} with the PSF in Equation \eqref{eq:PSFgeneral}: $(I \ast \text{PSF}) (x',y')$ is then again a sum of Gaussians and can be directly fitted to an image of the galaxy in question.

\subsubsection{Deprojection}

$I(R',\theta')$ describes the intrinsic, to 2D projected light distribution or surface density of the galaxy. Under the assumption that the galaxy is oblate and axisymmetric, and given the inclination angle $i$ of the galaxy with respect to the observer, MGEs allow an analytic deprojection of the 2D MGE to get a 3D light distribution or density $\nu(R,z)$ for the galaxy,
\begin{equation}
\nu(R,z) = \sum_i \nu_{0,i} \exp \left[-\frac{1}{2\sigma_i}\left(R^2 + \frac{z^2}{q_i^2} \right) \right]. \label{eq:deprojMGE}
\end{equation}
The flattening of each axisymmetric 3D Gaussian $q_i$ and its central density $\nu_{0,i}$ follow from the observed 2D axis ratio $q'_i$ and surface density $I_{0,i}$ as
\begin{eqnarray*}
q_i^2 &=& \frac{q_i'^2 - \cos^2 i}{\sin^2 i}\\
\nu_{0,i} &=& \frac{q_i' I_{0,i}}{q_i \sqrt{2 \pi \sigma_i^2}}.
\end{eqnarray*}
%--------------------------------------------

%--------------------------------------------
\subsection{Strong gravitational lens model} \label{sec:lensing_theo}
%--------------------------------------------

%--------------------------------------------
\subsubsection{Lensing formalism}
%--------------------------------------------

%--------------------------------------------
A gravitational lens is a mass distribution, whose gravitational potential $\Phi$ acts as a lens for light coming from a source positioned somewhere on a plane behind the lens. The angular diameter distance from the observer to the lens is $D_d$, to the source plane $D_s$, and the distance between the lens and source plane is $D_{ds}$. The deflection potential of the lens is its potential, projected along the line of sight $z$ and rescaled to
\begin{equation}
\psi(\vect{\theta}) := \frac{D_{ds}}{D_d D_s} \frac{2}{c^2} \int \Phi(\vect{r}=D_d \vect{\theta},z) {\ \mathrm d} z, \label{eq:psidef}
\end{equation}
where $\vect{\theta}$ is a 2-dimensional vector on the plane of the sky. The light from the source at $\vect{\beta} = (\xi,\eta)$\footnote{$\xi$ and $\eta$ are cartesian coordinates on the plane of the sky.} is deflected according to the lens equation
\begin{equation}
\vect{\beta} = \vect{\theta}_i - \left.\vect{\nabla}_\theta \psi(\vect{\theta})\right|_{\vect{\theta}_i} \label{eq:lenseqpot}
\end{equation}
into an image $\vect{\theta}_i = (x_i,y_i)$. The gradient of the deflection potential $\vect{\nabla}_\theta \psi(\vect{\theta})$ is equal to the angle by which the light is deflected multiplied by $D_{ds}/D_{s}$.

The total time delay of an deflected light path through $\vect{\theta}$ with respect to the unperturbed light path is given by 
\begin{equation}
\Delta t(\vect{\theta}) = \frac{(1+z_d)}{c} \frac{D_d D_s}{D_{ds}} \left[ \frac 12 (\vect{\theta} - \vect{\beta})^2 - \psi(\vect{\theta})\right] \label{eq:timedelay}
\end{equation}
\citep{BartGravLens}. According to Fermat's principle the image positions will be observed at the extrema of $\Delta t(\vect{\theta})$.

The inverse magnification tensor
\begin{equation}
\mathscr{M}^{-1} \equiv \frac{\partial \vect{\beta}}{\partial \vect{\theta}} \overset{(\ref{eq:lenseqpot})}{=} \left(\delta_{ij} - \frac{\partial^2 \psi}{\partial \theta_i \partial \theta_j} \right)\label{eq:magnificationtensor}
\end{equation}
describes how the source position changes with image position. It also describes the distortion of the image shape for an extended source and its magnification due to lensing according to
$$\mu \equiv \frac{\text{image area}}{\text{source area}} = \det \mathscr{M}.$$
Lines in the image plane for which the magnification becomes infinite, i.e., $\det \mathscr{M}^{-1} = 0$, are called critical curves. The corresponding lines in the source plane are called caustics. The position of the source with respect to the caustic detemines the number of images and their configuration and shape with respect to each other.

The Einstein mass $M_\text{ein}$ and Einstein radius $R_\text{ein}$ are defined via the relation
\begin{equation*}
M_\text{ein} \equiv M_\text{proj}(<R_\text{ein}) \overset{!}{=} \pi \Sigma_\text{crit} R_\text{ein}^2,
\end{equation*}
where $\Sigma_\text{crit} \equiv \frac{c^2}{4\pi G} \frac{D_s}{D_d D_{ds}}$ is the critical density and $M_\text{proj}(<R_\text{ein})$ is the mass projected along the line-of-sight within $R_\text{ein}$. $M_\text{ein}$ is similar to the projected mass within the critical curve $M_\text{crit}$.

%--------------------------------------------
\subsubsection{Lens model} 
%--------------------------------------------

%--------------------------------------------
Following \citet{EvansWitt} we assume a scale-free model
\begin{equation}
\psi(R',\theta') = R^{'\alpha} F(\theta') \label{eq:scalefreemodel}
\end{equation}
for the lensing potential, consisting of an angular part $F(\theta')$ and a power-law radial part, with $(R',\theta')$ being polar coordinates on the plane of the sky. The case $\alpha = 1$ corresponds to a flat rotation curve. We expand $F(\theta')$ into a Fourier series,
\begin{equation}
F(\theta') = \frac{a_0}{2} + \sum_{k=1}^{\infty} \left(a_k \cos(k\theta') + b_k \sin (k\theta') \right). \label{eq:Fourieransatz}
\end{equation}
For this scale-free lens model the lens equation \eqref{eq:lenseqpot} becomes
\begin{equation}
\begin{pmatrix} \xi \\ \eta \end{pmatrix} = \begin{pmatrix} R'_i \cos \theta'_i - R_i^{'\alpha-1} \left(\alpha \cos \theta'_i F(\theta'_i) - \sin \theta'_i F'(\theta'_i) \right) \\ R'_i \sin \theta'_i - R_i^{'\alpha-1} \left(\alpha \sin \theta'_i F(\theta'_i + \cos \theta'_i F'(\theta'_i) \right)\end{pmatrix}\label{eq:Fourierlenseq}
\end{equation}
\citep{EvansWitt}, where $F'(\theta') \equiv \partial F(\theta') / \partial \theta'$. When we fix the slope $\alpha$, then the lens equation is a purely linear problem and can be solved numerically for the source position $(\xi,\eta)$ and the Fourier parameters $(a_k,b_k)$ given one observed image at position $(x_i=R'_i \cos \theta'_i,y_i=R'_i \sin \theta'_i)$.

%--------------------------------------------
\subsubsection{Model fitting}
%--------------------------------------------

%--------------------------------------------
The free parameters of the lens model are: the source position $(\xi,\eta)$, the radial slope $\alpha$ and Fourier parameters $(a_k,b_k)$ of the lens mass distribution in Equations \eqref{eq:scalefreemodel} and \eqref{eq:Fourieransatz}. We want to minimize the distance between the observed image positions, $\vect{\theta}_{oi}$, and those predicted by the lensing model, $\vect{\theta}_{pi}$. To avoid having to solve the lens equation \eqref{eq:Fourierlenseq} for $\vect{\theta}_{pi}$, we follow \citet{1991ApJ...373..354K} and cast the calculation back to the source plane using the magnification tensor in Equation \eqref{eq:magnificationtensor} to approximate $\vect{\theta} \simeq (\partial \vect{\theta} / \partial \vect{\beta}) \vect{\beta} = \mathscr{M} \vect{\beta} $. The best fit lens model is then the one that minimizes
\begin{eqnarray}
\chi^2_\text{lens} &=& \sum_{i} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right) \left( \vect{\theta}_{pi} - \vect{\theta}_{oi} \right)\right|^2\nonumber\\
&\simeq& \sum_{i} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right)  \left.\mathscr{M}\right|_{\vect{\theta}=\vect{\theta}_{oi}} \left( \begin{matrix} \xi - \tilde{\xi}_i \\ \eta - \tilde{\eta}_i \end{matrix} \right) \right|^2,\label{eq:chi2lens}
\end{eqnarray}
where $(\Delta_x,\Delta_y)$ are the measurement errors of the image positions $\vect{\theta}_{oi}$. $\left.\mathscr{M}\right|_{\vect{\theta}=\vect{\theta}_{oi}}$ is the magnification tensor and $(\tilde{\xi}_i,\tilde{\eta}_i)$ the source position according to the lens equation, both evaluated at the position of the $i$-th lensing image, $\vect{\theta}_{oi}$. Following \citet{GlennEC} we add a term
\begin{equation}
\chi^2_\text{shape} = \lambda \sum_{k \geq 3} \frac{\left(a_k^2 +b_k^2 \right)}{a_0^2} \label{eq:chi2shape}
\end{equation}
which forces the shape of the mass distribution to be close to an ellipse. The total $\chi^2$ to minimize is therefore
\begin{equation}
\chi^2 = \chi^2_\text{lens} + \chi^2_\text{shape} \label{eq:chi2total}
\end{equation}
We set $a_1 = b_1 = 0$, which corresponds to the choice of origin; in this case the center of the galaxy.

To be able to constrain the slope $\alpha$, we would need flux ratios for the images as in \citet{GlennEC}. But the extended quality of the images, possible dust obscuration and surface brightness fluctuations due to microlensing events, as well as the uncertainty in surface brightness subtraction, make flux determination too unreliable and we do not include them in the fitting.
%--------------------------------------------

%--------------------------------------------
\subsection{Axisymmetric dynamical model} \label{sec:model_JAM}
%--------------------------------------------

%--------------------------------------------
\subsubsection{Jeans Anisotropic Models (JAM)} 
%--------------------------------------------

%--------------------------------------------
JAM modelling assumes galaxies to be (a) collisionless (i.e., the collisionless Boltzmann equation for the distribution function $f(\vect{x},\vect{v},t)$ has to be satisfied, $\frac{\diff f(\vect{x},\vect{v},t)}{\diff t} = 0$), (b) in a steady state ($\frac{\partial}{\partial t} = 0$), (c) axisymmetric (best described in cylindrical coordinates $(R,z,\phi)$ and $\frac{\partial}{\partial \phi} = 0$). From this follow the axisymmetric Jeans equations as the vector-valued first moment of the Boltzmann equation, i.e.,
\begin{equation*}
\int \vect{v} \frac{\diff f}{\diff t} \Diff3 v = 0.
\end{equation*}
To be able to solve the Jeans equations, additional assumptions about the velocity ellipsoid tensor $\langle v_i v_j\rangle$ have to be made. We follow \citet{Cap08} and assume firstly, that the galaxy's velocity ellipsoid is aligned with the cylindrical coordinate system, i.e., $\langle v_R v_z\rangle = \langle v_z v_\phi \rangle = \langle v_\phi v_R \rangle = 0$. Secondly, we assume a constant ratio between the radial and vertical second velocity moments, 
\begin{equation}
\beta_z \equiv 1 - \langle v_z^2 \rangle / \langle v_R^2\rangle. \label{eq:bz}
\end{equation}
This reduces the Jeans equations to two equations for $\langle v_z^2 \rangle$ and $\langle v_\phi^2 \rangle$, that can be solved by means of one integration,
\begin{eqnarray}
n \langle v_z^2 \rangle (R,z) &=& \int_0^\infty n \frac{\partial \Phi}{\partial z} \diff z \label{eq:Jeans1}\\
n \langle v_\phi^2 \rangle (R,z) &=& R \frac{\partial}{\partial R} \left( \frac{n \langle v_z^2 \rangle}{1-\beta_z} \right) + \frac{n \langle v_z^2 \rangle}{1 - \beta_z} + R n \frac{\partial \Phi}{\partial R},\label{eq:Jeans2}
\end{eqnarray}
where $n(\vect{x}) \equiv \int f(\vect{x},\vect{v}) \Diff3 v$ is the number density of (stellar) tracers and $\Phi(\vect{x})$ the galaxy's gravitational potential, generated by the mass density $\rho(\vect{x})$.

The JAM modelling approach by \citet{Cap08} expresses the tracer and mass density in terms of MGEs (see also \citealt{1994A&A...285..723E}). The tracer density $n(\vect{x})$ is assumed to be proportional to the observed and deprojected brightness distribution $\nu(R,z)$ in Equation \eqref{eq:deprojMGE}. The mass density $\rho(R,z)$ can consist of several sets of MGEs, describing stellar and DM components. $\Phi(R,z)$ is generated from the mass density MGE by integrating the Poisson equation \citep{1994A&A...285..723E}. Equations \eqref{eq:Jeans1} and \eqref{eq:Jeans2} together with \eqref{eq:bz} provide the velocity dispersion tensor $\langle v_i v_j \rangle = \langle v_i^2 \rangle$ (with $i,j \in \{ R,\phi, z\}$). $\langle v_i^2 \rangle$ is then rotated by the inclination angle $i$ to the coordinate system of the observer; $(x',y')$ is the plane of the sky and $z'$ the line-of-sight, where $x'$ is alinged with the galaxy's major axis. Taking a light-weighted projection along the line-of-sight gives a model prediction for the line-of-sight velocity second moment, which is comparable to actual spectroscopic measurements of the second velocity moment. Details of the derivation using the MGE formalism are given in \citet{Cap08} and in the appendix of \citet{GlennEC}. We therefore just give the result for the line-of-sight second velocity moment prediction from the Jeans equations,
\begin{eqnarray}
&&\left(I \langle v_\text{los}^2\rangle\right)(x',y')\nonumber\\
&&= 4 \pi^{3/2} G \int_0^1 \sum_{k=1}^N \sum_{j=1}^M \nu_{0,k} \ q_j \ \rho_{0,j} \ u^2\nonumber\\
&& \times \frac{\sigma_k^2 \ q^{2}_k \left( \cos^2 i + \frac{\sin^2 i}{1-\beta_{z,k}}\right) + \mathscr{D} \  {x'}^{2} \sin^2 i}{(1-\mathscr{C}u^2) \sqrt{(\mathscr{A} + \mathscr{B} \cos^2 i) \left[1-(1-q^{2}_j) u^2 \right]}}\nonumber\\
&& \times \exp\left\{- \mathscr{A} \left[{x'}^{2} + \frac{(\mathscr{A}+\mathscr{B}) \ {y'}^{2}}{\mathscr{A}+\mathscr{B}\cos^2 i}\right] \right\} \diff u, \label{eq:explicitLOSvelCap}
\end{eqnarray}
with $N$ Gaussians describing the tracer distribution and $M$ Gaussians describing the mass distribution, $\rho_{0,j}$ being the $j$-th mass density Gaussian evaluated at $(R=0,z=0)$ and
\begin{eqnarray*}
\mathscr{A} &=& \frac 12 \left(\frac{u^2}{\sigma_j^2} + \frac{1}{\sigma_k^2} \right)\nonumber\\
\mathscr{B} &=& \frac 12 \left\{\frac{1-q^{2}_k}{\sigma_k^2 q^{2}_k} + \frac{(1-q^{2}_j)u^4}{\sigma_j^2 \left[1-(1-{q}_j^{2})u^2 \right]} \right\}\nonumber\\
\mathscr{C} &=& 1- q^{2}_j - \frac{\sigma_k^2 q^{2}_k}{\sigma^2_j}\nonumber\\
\mathscr{D} &=& 1 - \frac{q^{2}_k}{1-\beta_{z,k}} - \left[ \left(1-\frac{1}{1-\beta_{k,z}}\right)\mathscr{C} + \frac{1-q^{2}_j}{1-\beta_{z,k}}\right] u^2.\nonumber
\end{eqnarray*}
The JAM modelling code by \citet{Cap08} evaluates Equation \eqref{eq:explicitLOSvelCap} numerically for a given luminous tracer and mass distribution MGE and a given inclination.

%--------------------------------------------
\subsubsection{Data comparison} 
%--------------------------------------------

%--------------------------------------------
As data we use stellar line-of-sight rotation velocities $v_\text{rot} \equiv \langle v_\text{los} \rangle$ and velocity dispersions $\sigma$ as described in Section \ref{sec:data}. The JAM models give us a prediction for the second line-of-sight velocity moment $\langle v_\text{los}^2 \rangle$. The root mean square (rms) line-of-sight velocity $v_\text{rms}$ allows a data-model comparison by relating theses velocities according to 
\begin{equation*}
v_\text{rms}^2 = \langle v_\text{los}^2 \rangle = v_\text{rot}^2 + \sigma^2.
\end{equation*}
The model in Equation \eqref{eq:explicitLOSvelCap} predicts the intrinsic $\langle v_\text{los}^2 \rangle$ at a given position on the sky, which needs then to be modified according to the mode of observation, to be comparable to the measurements. The measured $v_\text{rms}$ is a light-weighted mean for a pixel along the long-slit of the spectrograph, with width $L_y = 1''$ \citep{SWELLSV} and a certain given extent along the galaxy's major axis, $L_x$, i.e., for a rectangular aperture
\begin{equation*}
\text{AP}(x',y') \equiv \left\{ \begin{array}{ll} 1 & \text{for } -\frac{L_x}{2} \leq x' < + \frac{L_x}{2}\\
& \text{and } - \frac{L_y}{2} \leq y' \leq + \frac{L_y}{2}  \\ 0 & \text{otherwise.} \end{array} \right.
\end{equation*}
The light arriving at the spectrograph itself was subject to seeing, i.e., a Gaussian with Full Width Half Maximum (FWHM) of $1.1''$ \citep{SWELLSV},
\begin{equation*}
\text{PSF}(x',y')\equiv\mathscr{N}(0,\text{FWHM}/2\sqrt{2\ln2}).
\end{equation*}
The model predictions for $\langle v_\text{los}^2 \rangle$ have therefore to be convolved with the convolution kernel
\begin{eqnarray*}
K(x',y') &\equiv& (\text{PSF} \ast \text{AP})(x',y') \\
&=& \frac{1}{4} \prod_{u \in \{x',y'\}} \left[ \text{erf}\left( \frac{L_u/2 - u}{\sqrt{2}\sigma_\text{seeing}}\right) + \text{erf} \left( \frac{L_u/2 + u}{\sqrt{2} \sigma_\text{seeing}} \right) \right],
\end{eqnarray*}
and weighted by the surface brightness $I(x',y')$, i.e.,
\begin{eqnarray*}
I_\text{obs} &=& I \ast K\\
\langle v_\text{los}^2 \rangle |_\text{obs} &=& \frac{(I \langle v_\text{los}^2\rangle) \ast K}{I_\text{obs}}.
\end{eqnarray*}
If provided with the convolution kernel, the JAM code\footnote{The IDL code package for Jeans Anisotropic Models (JAM) by \citet{Cap08} is available online at \url{http://www-astro.physics.ox.ac.uk/~mxc/software}. The version from June 2012 was used in this work.} by \citet{Cap08} performs the convolution numerically. We set $L_x = 0.21''$ as the width of the model pixel, and get a prediction for the actual measurements in bins of width $0.63''$, $1.26''$ and $1.89''$ \citep{SWELLSV} as light-weighted mean from each 3, 6 and 9 model pixels.

%--------------------------------------------
\subsubsection{Rotation curve}
%--------------------------------------------

%--------------------------------------------
The intrinsic rotation curve is the first velocity moment $\langle v_\phi\rangle = \sqrt{\langle v_\phi^2 \rangle - \sigma_\phi^2}$. The observed rotation curve is the projection of the light-weighted contributions to $\langle v_\phi\rangle$ along the line-of-sight \citep{Cap08},
\begin{equation*}
I \langle v_\text{los}\rangle = \int_{-\infty}^{+\infty} \nu \langle v_\phi\rangle \cos \phi \sin i \diff z'.
\end{equation*}
The first velocity moments cannot be uniquely determined from the Jeans equations, which give only a prediction for the second velocity moments. Further assumptions are needed to separate the second velocity moments into ordered and random motion. \citet{Cap08} assumes that in a steady state there is no streaming velocity in $R$ direction, i.e., $\langle v_R \rangle = 0$ and therefore $\sigma_R^2 = \langle v_R^2 \rangle$. Then \citet{Cap08} relates the dispersions in $R$ and $\phi$ direction such that
$$\langle v_\phi\rangle = \sqrt{\langle v_\phi^2 \rangle - \sigma_\phi^2} \equiv \kappa \sqrt{\langle v_\phi^2 \rangle - \langle v_R^2 \rangle},$$
and the $\kappa$ parameter quantifies the rotation: $\kappa = 0$ means no rotation at all and $|\kappa| = 1$ describes a velocity dispersion ellipsoid that is a circle in the $R$-$\phi$ plane \citep{Cap08}. The sign of $\kappa$ determines the rotation direction. We can assign a constant $\kappa_k$ to every Gaussian in the MGE formalism and
\begin{equation*}
\nu \langle v_\phi\rangle = \left[\nu \sum_{k} \kappa_k^2 \left( [\nu\langle v_\phi^2 \rangle]_k - [\nu\langle v_R^2 \rangle]_k\right) \right]^{1/2}
\end{equation*} 
is then the light-weighted circular velocity curve, given the second velocity moments found from the Jeans equations.

To model the counter-rotating core of J1331 with one free parameter, we employ the condition that the overall $\kappa(R)$ profile should smoothly and relatively steeply transit from $\kappa(R) = -\kappa' < 0$ at small $R$ through $\kappa(R_0) = 0$ and increase to $\kappa(R) = \kappa' > 0$ at large $R$. Our imposed profile is
\begin{equation}
\kappa(R) = \kappa' \frac{R^2 - R_0^2}{R^2 + R_0^2}. \label{eq:kappa_profile}
\end{equation}
We find $\kappa'$ by matching the model $\langle v_\text{los} \rangle$ with the symmetrized $v_\text{rot}$ data, where for a given $\kappa'$ the $\kappa_k$ are found from fitting the MGE generated profile $\kappa(R) = \sum_k \kappa_k \nu_k(r)/\sum_k \nu_k(r)$ to Equation \eqref{eq:kappa_profile}. The observed zero point is at $R'_0\approx 2''$. In the deprojected galactic plane the radius of zero rotation would be at a $R_0 \gtrsim 2''$, and we choose it to be at $2.2''$.

%--------------------------------------------
\subsubsection{Including a NFW halo} 
%--------------------------------------------

%--------------------------------------------
As mentioned above, JAM modelling allows to incorporate an invisible matter component in addition to the luminous matter in the form of an MGE. In Section \ref{sec:results_JAM_NFW} we will include a spherical Navarro-Frenk-White (NFW) DM halo \citep{NFW96} in the dynamical model. The classical NFW profile has the form
\begin{equation}
\rho_\text{NFW}(r) \propto r^{-1} \left( r+r_s \right)^{-2} \label{eq:NFWprofile}
\end{equation}
and two free parameters, the scale length $r_s$ and a parameter describing the total mass of the halo. We will use $v_\text{200}$, which is the circular velocity at the radius $r_\text{200}$ within which the mean density of the halo is 200 times the cosmological critical density $\rho_\text{crit} \equiv (2H^2)/(8\pi G)$, i.e.
\begin{eqnarray*}
M_\text{200} &=& M(<r_{200})\\
\frac{M_{200}}{ \frac 43 \pi r_{200}^3} &=& 200 \rho_\text{crit}(z=0) \\
v_\text{200} &=& \sqrt{\frac{GM_{200}}{r_\text{200}}}
\end{eqnarray*}
with $\rho_\text{crit}(z=0)=1.43 \cdot 10^{-7} M_\odot / \text{pc}^3$ in the WMAP5 cosmology by \citet{WMAP5cosm}. How much the mass is concentrated in the center of the NFW halo is given by the concentration of the NFW halo defined by 
\begin{equation}
c_{200}\equiv r_{200} / r_s. \label{eq:NFW_c}
\end{equation} 
There is a close relation between the concentration and halo mass in simulations \citep{NFW96}. \citet{Maccio08} found this relation for the WMAP5 cosmology to be
\begin{equation}
\langle \log c_{200} \rangle (M_{200}) = 0.830 - 0.098 \log \left(h \frac{M_{200}}{10^{12} M_\odot} \right) \label{eq:Maccio08}
\end{equation}
(their equation 10), with a Gaussian scatter of $\sigma_{\log c_{200}} = 0.105$ (their Table A2). 
\Wilma{[TO DO: Section on JAM model noch mal durchgehen, ist noch nicht so toll.]}
%--------------------------------------------

%--------------------------------------------
\section{Results} \label{sec:Results}
%--------------------------------------------

%============================================
\begin{table}
\centering
\caption{General galaxy parameters of J1331.}
\begin{tabular}{lllr}
\hline
redshift \citep{SWELLSIII}                 & $z_d$ & $0.113$ \\
angular diameter distance & $D_d$ [Mpc] & $414$ \\
scaling                   & 1 kpc / 1$''$ & $2.006$ \\
position angle from North          & $\phi$ [degrees] & $42.90^\circ$\\
average axis ratio & $q'$ & $0.598$\\
average ellipticity & $\epsilon = 1 - q'$ & $0.402$ \\
estimated inclination & $i$ [degrees] & $70^\circ$\\
apparent I-band magnitude & $m_\text{I}$ [mag] & $15.77$ \\
total I-band luminosity & $L_\text{I,tot}$ [$10^{10} L_\odot$] & $5.6$ \\
effective half-light radius & $R_\text{eff}$ [$''$] & $2.6$ \\
& $R_\text{eff}$ [pc]& 5.2 & \\
\hline
\end{tabular}
\label{tab:galaxyparameters}
\end{table}
%============================================

%--------------------------------------------
\subsection{Surface photometry for J1331 with MGEs} \label{sec:MGE_results}
%--------------------------------------------

%--------------------------------------------
In this section we construct a model for the J1331's intrinsic light distribution in terms of MGEs (see Section \ref{sec:MGE_theo}). We use the HST image in the F814W (I-band) filter (Figure \ref{fig:F814W}) because J1331's central stellar component appears at longer wavelengths (i) smoother and more extended than in the F450W filter (Figure \ref{fig:F450W}), as it is less sensitive to young clumpy star-forming regions, (ii) much brighter than the bluish lensing images, and (iii) the imaging is less prone to extinction.

%--------------------------------------------
\subsubsection{PSF for the HST/F814W filter}
%--------------------------------------------

%--------------------------------------------
The one-dimensional MGE in Equation \eqref{eq:PSFgeneral} is fitted to the radial profile of a synthetic image of the HST/F814W filter PSF, ignoring diffraction spikes and using the code by \citet{Cap02}. The MGE parameters of the normalized PSF model are given in Table \ref{tab:PSFMGEF814W}.

%============================================
\begin{table}
\centering
\caption{F814W PSF MGE: Parameters of the circular four-Gaussian MGE in Equation \eqref{eq:PSFgeneral} fitted to the radial profile of the synthetic HST/F814W PSF image.}
\begin{tabular}{ccc}
\hline
$j$ & $G_j$ & $\delta_j$ [$''$] \\\hline
1 & 0.184 & 0.038\\
2 & 0.485 & 0.085\\
3 & 0.222 & 0.169\\
4 & 0.109 & 0.487\\\hline
\end{tabular}
\label{tab:PSFMGEF814W}
\end{table}
%============================================

%--------------------------------------------
\subsubsection{MGE for the inner regions.}
%--------------------------------------------

%--------------------------------------------
We fit a MGE to J1331's smooth central region within $\sim 5''$ from the HST/WFPC2/WF3/F814W image (Figure \ref{fig:F814W}). Bright objects close to the bulge (blobs possibly belonging to the background galaxy and parts of the foreground spiral arm) were masked during the fit. J1331's galaxy center, position angle (with respect to North through East) and average apparent ellipticity (see Table \ref{tab:galaxyparameters}) are found from the images weighted first and second moment. The MGE fit splits the image in annuli with the given ellipticity and position angle and sectors of $5^\circ$ width and fits an 5-Gaussian MGE of the form in Equation \eqref{eq:MGEgeneral} convolved with the PSF MGE in Table \ref{tab:PSFMGEF814W} to it. The best fit MGE (PSF convolved) is compared to the data in Figure \ref{fig:MGEinnerRegions} and the corresponding parameters of the intrinsic surface brightness distribution are given in Table \ref{tab:MGEF814W}. The fit is a very good representation of the light distribution in the inner $5''$, but underestimates the light distribution outward.

%--------------------------------------------
\subsubsection{MGE for the outer regions}
%--------------------------------------------

%--------------------------------------------
To get a handle on the light distribution also in the outer parts of J1331, where spiral arms dominate, we first fit a IRAF \citep{1993ASPC...52..173T} \emph{ellipse} model to the F814W image (masking the brightest blobs in the spiral arms and outer regions). Only then we fit a 7-Gaussian MGE to the smooth ellipse model. The MGE does not perfectly reproduce the flatness of the ellipse model at every radius (see Figure \ref{fig:MGEouterRegions}), but considering the spiral arm dominated outer regions of J1331, it is good enough for an approximate handling of the overall light distribution.

%============================================
\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\columnwidth]{fig/1331F814Wsci_MGE_M.ps}
  \caption{MGE for J1331's inner regions.}
 \label{fig:MGEinnerRegions}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\columnwidth]{fig/1331F814W_MGE_disk_L.ps}
  \caption{MGE and IRAF \emph{ellipse} model for J1331's outer regions.}
 \label{fig:MGEouterRegions}
\end{subfigure}%
\caption{MGEs for J1331's surface brightness distribution. Comparison of contours with constant F814W surface brightness (orange lines) with the corresponding iso-brightness contours of the best fit MGE, convolved with the PSF in Table \ref{tab:MGEF814W}, (grey lines). The black line has a length of $10''$ and its orientation corresponds to the galaxy's position angle as found in Table \ref{tab:galaxyparameters}. For comparison the Einstein radius as found in Table \ref{tab:bestfitlensmodel}  is indicated as red dashed circle. \emph{Panel (a):} Central regions of J1331. The MGE model is a good representation of the galaxy's light distribution along the major axis within $\sim 5''$. Its parameters are given in Table \ref{tab:MGEF814W}. This MGE is used as model for the stellar tracer distribution in the dynamical Jeans modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}. \emph{Panel (b):} Outer regions of J1331. The orange lines indicate here contours of a smooth IRAF \emph{ellipse} fit to J1331 in the F814W filter; the grey lines are the corresponding best fit MGE. This MGE is not used for dynamical modelling, because the dynamics in the outer regions are strongly affected by non-axisymmetries (e.g., spiral arms). We use it, however, to estimate the galaxy's total luminosity and effective radius, and to get a prediction for the dynamics of the outer regions.}
\end{figure*}
%============================================

%============================================
\begin{table*}
\centering
\caption{Parameters of the best fit MGE to the F814W surface brightness of J1331 in Figure \ref{fig:MGEinnerRegions}. The fit is best inside an radius of $5''$. The position angle is given in Table \ref{tab:galaxyparameters}. This MGE is used in the dynamical modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}. The first column gives for each Gaussian the total F814W luminosity in Equation \eqref{eq:centralItotalL} in units of counts. The second column is the corresponding I-band peak surface brightness in Equation \eqref{eq:MGEgeneral} in units of a luminosity surface density. The third and fourth column give the dispersion and the last column the axis ratio of the Gaussian in Equation \eqref{eq:MGEgeneral}.}
\begin{tabular}{cccccc}
\hline
 & total luminosity  & surface density & \multicolumn{2}{c}{Gaussian dispersion} & axis ratio\\
$i$  & $L_i$ [counts] & $I_{0,i}$ [$L_\odot$/pc$^2$] & $\sigma_i$ [$''$] & $\sigma_i$ [kpc] & $q'_i$\\\hline
1  &     9425.96 &      20768.  &  0.051   & 0.103  & 1.00\\
2  &    13173.0 &        3161.2 &  0.178   & 0.358  & 0.76\\
3  &    40235.0 &        1588.2 &  0.503   & 1.008  & 0.58\\
4  &    67755.2 &         502.25&  1.180   & 2.368  & 0.56\\
5  &    203677. &         136.51&  3.891   & 7.805  & 0.57\\\hline
\end{tabular}
\label{tab:MGEF814W}
\end{table*}
%============================================

%--------------------------------------------
\subsubsection{Transformation into physical units}
%--------------------------------------------

%--------------------------------------------
To transform the MGE in units of counts into physical units, we apply a simplified version of the procedure described in \citet{Holtzman}.

The scaling of the drizzled HST/WFC3 images is  $S \equiv 0.05''/\text{pixel width}$ and the total exposure time $T = 1600$ sec. Each Gaussian in the MGE has a total F814W luminosity $L_i$ (in counts) and a central surface brightness (in counts per pixel) of
\begin{equation*}
C_{0,i}\text{[counts/pixel]} = \frac{L_i[\text{counts}]}{2\pi \sigma[\text{pixel}]^2 q}.
\end{equation*}
This is then transformed into an I-band surface brightness (in $\text{mag}\times(1'')^{-2}$) via
\begin{equation}
\mu_{I,0,i} \simeq -2.5 \log_{10}\left( \frac{C_{0,i}\text{[counts/pixel]}}{T[\text{sec}] \cdot S[''/\text{pixel width}]^2}\right) + Z + C + A_I, \label{eq:muI_}
\end{equation}
where $Z\simeq21.62~\text{mag}$ is a the zero-point from \citet{Holtzman}, updated according to \citet{Dolphin,DolphinNew}, for the photometric system of the HST/WFPC2 camera and the F814W filter, plus a correction for the difference in gain between calibration and observation. $C= 0.1~\text{mag}$ corrects for the finite aperture of the WFPC2; and $A_I =0.015~\text{mag}$ is the extinction in the (Landolt) I-band towards J1331, according to the NASA/IPAC Extragalactic Database (NED)\footnote{The NASA/IPAC Extragalactic Database (NED, \url{https://ned.ipac.caltech.edu/}) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration. The data for J1331 (SDSS J133140.33+362811.9) was retrieved in October 2013.}. The color-dependent correction between the F814W filter and the I-band of the UBVRI photometric system is  small \citep{Holtzman} and we neglect it therefore. The last step is to transform the surface brightness $\mu_{I,0,i}$ (in mag) to the I-band surface density $I_{0,i}$ (in $L_\odot$/pc$^2$) of the Gaussian, i.e.,
\begin{eqnarray*}
I_{0,i}[L_\odot \text{pc}^{-2}] = \left( 64800/\pi\right)^2 \left(1+z_d \right)^4 10^{0.4\left(M_{\odot,I}-\mu_{I,0,i} \right)},
\end{eqnarray*}
where the term with $z_d$ accounts for redshift dimming and $M_{\odot,I}=4.08~\text{mag}$ is the Sun's absolute I-band magnitude \citep{1998gaas.book.....B}. The luminosity $L_i$[counts] and the corresponding surface brightness density $I_{0,i} [L_\odot \text{pc}^{-2}]$ of each Gaussian are given in Table \ref{fig:MGEinnerRegions}.

%--------------------------------------------
\subsubsection{Inclination}
%--------------------------------------------

%--------------------------------------------
To estimate the inclination of J1331 with respect to the observer, we use the observed axis ratio of the flattest ellipse in the IRAF \emph{ellipse} model for J1331, which is $q'=0.42$. This is similar to the disk axis ratio of $q' = 0.40$ found by \citet{SWELLSI}. If a typical thickness of an oblate disk is around $q_0 \sim 0.2$ \citep{1958MeLu2.136....1H}, the inclination follows from 
\begin{equation*}
\cos^2 i = \frac{q'^2 - q_0^2}{1 - q_0^2}
\end{equation*}
and a correction of $+3^\circ$ \citep{1988ngc..book.....T}. Our estimate for the inclination is therefore $i \approx 70^\circ$. Given this inclination, the 2D MGE models can be deprojected into three dimensions (see Section \ref{sec:MGE_theo}).

%--------------------------------------------
\subsubsection{Total luminosity and effective radius}
%--------------------------------------------

%--------------------------------------------
J1331's total I-band luminosity is determined by summing up the luminosity contributions of all the MGE Gaussians for the outer regions (shown as grey lines in Figure \ref{fig:MGEouterRegions}). We find $L_\text{I,tot} \simeq 5.6 \cdot 10^{10} ~L_\odot$. This corresponds to an apparent magnitude of $m_I = 15.77~\text{mag}$. We determine the circularized effective radius $R_\text{eff}$ of J1331 from the definition $L(<R_\text{eff}) \equiv \frac 12 L_\text{tot}$ and the growth curve $L(<R')$ from the MGE model of the outer regions, where $R'$ is the projected radius on the sky. We find the effective radius to be $R_\text{eff} \simeq 2.6'' \hat{=} 5.2 \text{ kpc}$.  All values are summarized in Table \ref{tab:galaxyparameters}.
%--------------------------------------------

%============================================
\begin{table}
\centering
\caption{Positions of the lensing images (A-D) and the galaxy center (G) in Figure \ref{fig:lens_just_imgpos}. The image positions were determined from the lens subtracted image for J1331 in Figure 4 of \citet{SWELLSIII}, rotated to the $(x,y)$ coordinate system in Figure \ref{fig:lens_just_imgpos}. The pixel scale is 1 pixel = $0.05''$ and the error of each image position is $\pm$ 1 pixel.}
\begin{tabular}{r|rrrr|c}
\hline
  & A & B & C & D & G\\\hline
$x_i$ [pixel] & 12.1 & -8.5 & 21.7 & -3.3 & 0.5 $\pm \sqrt{2}$ \\
$y_i$ [pixel] & 16.6 & -10.4 & -0.5 & 19.2 & 0.5 $\pm \sqrt{2}$ \\
\hline
\end{tabular}
\label{tab:lenspos}
\end{table}
%============================================

%============================================
\begin{figure}
\centering
  \includegraphics[width=\linewidth]{fig/lens_all_in_one.ps}
\caption{Lensing model (Table \ref{tab:bestfitlensmodel}) found as best fit to the image positions. In the background we show the central region of J1331 in the F450W filter, subtracted by an IRAF \emph{ellipse} model of the F450W surface brightness and smoothed to remove noise smaller than the PSF. The brightness peaks of the four lensing images and the galaxy center (Table \ref{tab:lenspos}) are marked as red dots. For the best fit lens model we show the Einstein radius (red dotted circle) and the critical curve (red solid line), which are located in the lens plane. We also show the caustic (green solid line) corresponding to the critical curve and the best fit source position (green dot), which are located in the source plane. For $\alpha=1$ the critical curve is a contour of constant surface density of the mass model. The grey  lines show contours of the time delay surface given by Equation \eqref{eq:timedelay}. Not only the position of the extrema, but also their shape is consistent with the observed, extended images, even though we did not use information about the image shape in the analysis.}
\label{fig:bestfitlensmodel}
\end{figure}
%============================================

%--------------------------------------------
\subsection{Mass distribution from lensing} \label{sec:results_lensing}
%--------------------------------------------

%--------------------------------------------
In this section we use the gravitational lensing formalism summarized in Section \ref{sec:lensing_theo} to fit a scale-free galaxy mass model to the positions of the lensing images observed in J1331's central region.

%============================================
\begin{table*}
\centering
\caption{Best fit lens model (first column) found from the peak image positions in Table \ref{tab:lenspos} following the procedure described in Section \ref{sec:lensing_theo} and assuming a flat rotation curve ($\alpha = 1$). The second column gives the corresponding best fit mean and standard deviation derived from Monte Carlo sampling of the Gaussian uncertainties around the image positions, with the relative error given in parentheses.}
\begin{tabular}{llrrclr}
\hline
 &  & \multicolumn{1}{c}{lens model for} &\multicolumn{4}{c}{lens model from Monte Carlo sampling  } \\
 &  & \multicolumn{1}{c}{peak image positions}  & \multicolumn{4}{c}{of image position uncertainties}  \\ \hline
Einstein radius      & $R_\text{ein}$ [$''$]             & $0.907$ & $0.91$  & $\pm$ & $     0.02$ & ($2\%$)\\
Einstein mass        & $M_\text{ein}$ [$10^{10} M_\odot$]  & $7.72$  & $7.8 $  & $\pm$ & $      0.3$ & ($4\%$) \\
Critical mass        & $M_\text{crit}$ [$10^{10} M_\odot$] & $7.87$  & $7.9$   & $\pm$ & $      0.3$ & ($4\%$)\\
Source position      & $\xi$ [$''$]                      & $0.095$ & $0.09 $ & $\pm$ & $     0.03$ & ($28\%$)\\
                     & $\eta$ [$''$]                     & $0.107$ & $0.10 $ & $\pm$ & $     0.03$ & ($27\%$)\\
Fourier coefficients & $a_0$                               & $1.814$ & $1.82 $ & $\pm$ & $   0.04$ & (2\%)\\
                     & $a_2$                               & $0.012$ & $ 0.011 $ & $\pm$ & $    0.004$ & (35\%)\\
                     & $b_2$                               & $-0.057$ & $-0.06 $  & $\pm$ & $  0.01$ & (25\%)\\
                     & $a_3$                               & $-0.0001$& $0.0000 $ & $\pm$ & $   0.0006$ & \\
                     & $b_3$                               & $-0.0002$&$0.000 $   & $\pm$ & $  0.001$ & \\\hline
\end{tabular}  
\label{tab:bestfitlensmodel} 
\end{table*}
%============================================

%============================================
\begin{figure*}
\centering
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_surface_brightness.ps}
  \caption{Observed light distribution.}
  \label{fig:lenscomparelight}
\end{subfigure}%
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_surface_density.ps}
  \caption{Lens model mass distribution.}
  \label{fig:lenscomparemass}
\end{subfigure}
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/paper_lensmass_brightness_compare.ps}
  \caption{Comparison of mass and light.}
  \label{fig:lenscompareboth}
\end{subfigure}
\caption{Comparison of the observed F814W/I-band surface brightness distribution (panel (a) and orange contours) and derived mass distribution from lensing constraints (panel (b) and pink contours). To allow for a qualitative comparison of the contours in panel (c), the light distribution was turned into a mass distribution by multiplication with the total mass-to-light ratio inside the Einstein radius, $\Upsilon_\text{I,tot}^\text{ein} = 5.56 \Upsilon_{I,\odot}$. The Einstein radius is overplotted as red dotted circle. The uncertainties in the mass model in the second column of Table \ref{tab:bestfitlensmodel} were translated into random Monte Carlo noise in the mass contours. The smooth black contours correspond to the best fit model in the first column of Table \ref{tab:bestfitlensmodel}. We find, that the lens mass model is more roundish than the light distribution. The background in Panel (c) shows again the surface brightness subtracted center of the galaxy to make the lensing images visible.}
\label{fig:lenslightcompareALL}
\end{figure*}
%============================================

%--------------------------------------------
\subsubsection{Image positions}
%--------------------------------------------

%--------------------------------------------
We determine the positions of the lensing images by first subtracting a smooth model for the galaxy's surface brightness from the original image. As models we use MGE fits and IRAF \emph{ellipse} fits to J1331 in each the F450W and F814W filter. The lensing images become visible in the residuals (see Figure \ref{fig:lens_just_imgpos}). Because the images are extended, we use the position of the brightest pixel in each of the images. In addition, we consider the F450W-MGE subtracted residuals from \citet{SWELLSIII}. The lensing positions, as determined from the latter, are given in Table \ref{tab:lenspos}. The scatter of lensing positions, as determined from subtracting different brightness models from the galaxy in different filters, gives an error of $\pm 1$ pixel on the image positions. To the galaxy center, which we assume to be the surface brightness peak in the F450W image, we apply an error of $\pm \sqrt{2}$ pixel.

Eight image position coordinates allow us to fit a lens mass model with only $<8$ free parameters. We therefore do not fit Fourier components $(a_k,b_k)$ with $k > 3$ in the lens mass model in Equations \eqref{eq:scalefreemodel}-\eqref{eq:Fourieransatz}.

Even though the constraint from the image positions on $\alpha$ is very weak, we were however able to show that the image positions in Table \ref{tab:lenspos} are consistent with a model with flat rotation curve. In the following we therefore set $\alpha=1$.

%--------------------------------------------
\subsubsection{Best fit lens model} 
%--------------------------------------------

%--------------------------------------------
We fit the lens mass model to the image positions in Table \ref{tab:lenspos} by minimizing $\chi^2 = \chi_\text{lens}^2 + \chi_\text{shape}^2$ (see Equations \eqref{eq:chi2lens}-\eqref{eq:chi2total}). The best fit parameters are given in the first column of Table \ref{tab:bestfitlensmodel}. Figure \ref{fig:bestfitlensmodel} shows the corresponding critical curve, caustic and Einstein radius, and the best fit source position. In this case, where $\alpha=1$, the (tangential) critical curve is also an equidensity contour of the galaxy model \citep{EvansWitt}, which appears to have an elliptical mass distribution. The source is located close to a cusp of the diamond-shaped caustic: a lensing configuration for which we indeed expect four images. Figure \ref{fig:bestfitlensmodel} also shows the (smoothed) residuals from the F450W image subtracted by an IRAF \emph{ellipse} brightness model and the contours of the best fit model's time delay surface. This demonstrates that, although we did not include any information about the shape of the lensing images in the fit, it is consistent with the predicted distortion for an extended source.

To estimate how the uncertainties in the determination of image positions and galaxy center affect the results, we sample random positions from two-dimensional Normal distributions with peaks and standard deviations according to Table \ref{tab:lenspos}. Model fits to many sampled image positions lead to probability distributions for the best fit shape parameters and Einstein quantities; peak and standard deviations are given in the second column of Table \ref{tab:bestfitlensmodel}. We constrain the Einstein radius to within 2\%, $R_\text{ein} = (0.91 \pm 0.02)''$ and the projected mass within the critical curve with a relative error of 4\%, $M_\text{crit} =(7.9\pm0.3)\cdot 10^{10} M_\odot$. Our measurement of $R_\text{ein}$ is consistent with that from \citet{SWELLSIII}, $R_\text{ein,SWELLS} = (0.96 \pm 0.04)''$ (which used a singular isothermal ellipsoid as lens mass model and the intermediate-axis convention of the critical curve as the Einstein radius). The relative difference between our critical mass and that of \citet{SWELLSIII}, $M_\text{crit,SWELLS} =(8.86\pm0.61)\cdot 10^{10} M_\odot$, is 13\%.
%--------------------------------------------

%============================================
\begin{figure}
  \centering
  \includegraphics[height=6cm]{fig/lensing_JAM_comparision.ps}
  \caption{Comparison (not a fit!) of the symmetrized stellar $v_\text{rms}$ data of J1331 (blue dots) with JAM models generated from mass distributions which were independently derived from lensing constraints in Section \ref{sec:results_lensing} (red lines). The red solid line corresponds to the lens model for a flat rotation curve ($\alpha = 1$) in Table \ref{tab:bestfitlensmodel}; the red dashed and dash-dotted lines are best fit lens models found analogously from the image positions, but for a fixed rotation curve slope of $\alpha = 1.1$ and $0.9$, respectively. For the JAM modelling a best fit MGE to the lens mass models were used, as well as the observed surface brightness MGE in Table \ref{tab:MGEF814W}, assuming velocity isotropy $\beta_z = 0$ and an inclination of $i = 70^\circ$. The most reliable constraints are around the Einstein radius (vertical red dotted line); outside of it the JAM model is just an extrapolation.}
  \label{fig:JAM_modelL}
\end{figure}
%============================================

%--------------------------------------------
\subsubsection{Comparison with light distribution}
%--------------------------------------------

%--------------------------------------------
The surface mass distribution as predicted by the best fit lens model (Table \ref{tab:bestfitlensmodel}) is shown in Figure \ref{fig:lenscomparemass}. We visualize the effect of the Fourier shape parameter uncertainties by introducing random noise to create a mock observation. From the mock image's second moment we find an average axis ratio for the lens mass model of $q_\text{lens} \simeq 0.695$, which is consistent with the one found by \citet{SWELLSIII}, $q_\text{lens,SWELLSIII} = 0.67 \pm 0.09$, while the light's average axis ratio is $q' = 0.598$ (see Table \ref{tab:galaxyparameters}).

We estimate the total mass-to-light ratio within the Einstein radius $\Upsilon_\text{I,tot}^\text{ein} \equiv M_\text{ein} / L_\text{I,ein}$. For this, we integrate the MGE in Table \ref{tab:MGEF814W} to get the total I-band luminosity within the Einstein radius $L_\text{I,ein} = 1.40\cdot 10^{10} L_\odot$. The corresponding Einstein mass-to-light ratio is therefore $\Upsilon_\text{I,tot}^\text{ein} = 5.56 \Upsilon_{I,\odot}$. This is consistent with or slightly larger than the stellar mass-to-light ratio assuming a Salpeter initial mass function (IMF) $\Upsilon_\text{I,*}^\text{sal} = 4.7 \pm 1.2$ according to \citet{SWELLSI} and Table \ref{tab:previousresults} (see also discussion in Section \ref{sec:MLdiscussion}).

We use $\Upsilon_\text{I,tot}^\text{ein}$ to transform the observed surface brightness in the F814W filter into a surface mass density (Figure \ref{fig:lenscomparelight}). Figure \ref{fig:lenscompareboth} then compares equidensity contours of both the predicted lens mass distribution and the observed surface brightness times $\Upsilon_\text{I,tot}^\text{ein}$.

Figure \ref{fig:lenslightcompareALL} leads to the following three findings: (1)The mass predicted from lensing and the observed light distribution are oriented in the same direction (i.e., have the same position angle). (2) Within and around the Einstein radius, mass and light distribution have a similar elliptical shape, while further out the mass distribution is slightly rounder. (3) The light distribution drops faster than the mass with increasing radius (which is---at least partly---because of the assumption of a flat rotation curve). However, the mass distribution is only constraint around the Einstein radius and otherwise an extrapolation. 
%--------------------------------------------

%============================================
\begin{figure}
  \centering
  \includegraphics[height=6cm]{fig/jam_A2_vrms.ps}
  \caption{Comparison of the symmetrized $v_\text{rms}$ data of J1331 (blue dots) with a best fit dynamical JAM model (orange line) assuming mass-follows-light and with two free parameters: $\Upsilon_\text{I,tot}^\text{dyn}$, the total constant I-band mass-to-light ratio which converts the observed surface brightness in Table \ref{tab:MGEF814W} into a mass distribution, and the velocity anisotropy parameter $\beta_z$. The ``best'' fit is $\Upsilon_\text{I,tot}^\text{dyn} = 4.8 \pm 0.1$ and $\beta_z = -0.5$, where the latter is however pegged at the lower limit of the allowed value range. This is obviously not a good model.}
  \label{fig:JAM_modelA2}
\end{figure}
%============================================

%--------------------------------------------
\subsection{JAM based on surface brightness} \label{sec:results_JAM_SB}
%--------------------------------------------

%--------------------------------------------
In this section we create dynamical models for J1331 following the procedure in Section \ref{sec:model_JAM}. We use the deprojected surface brightness MGE from Table \ref{tab:MGEF814W} for the tracer distribution $\nu(R,z)$ and to generate mass models $\rho(R,z)$. The only exception is the first test, where the mass model comes from lensing constraints.
%--------------------------------------------

%============================================
\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[height=6cm]{fig/jam_G_vrms.ps}
  \caption{Comparison of $v_\text{rms}$ data and best fit model.}
  \label{fig:JAM_modelG}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[height=6cm]{fig/jam_G_enclMass.ps}
  \caption{Projected local mass-to-light ratio profile and enclosed mass.}
  \label{fig:enclMass_modelG}
\end{subfigure}
\caption{JAM model found by fitting a galaxy model with increasing total mass-to-light ratio profile $\Upsilon_\text{I,tot}(R')$ to the symmetrized $v_\text{rms}$ data (blue dots). The mass distribution is generated by assigning a different mass-to-light ratio $\Upsilon_{\text{I,tot,}i}$ to each Gaussian $i$ in the light distribution MGE in Table \ref{tab:MGEF814W}. The $\Upsilon_{\text{I,tot,}i}$ were treated as free fit parameters. \emph{Panel (a):} Comparison between the stellar $v_\text{rms}$ data (blue dots) and the best fit model (green line). \emph{Panel (b):} Projected total mass-to-light profile $\Upsilon_\text{I,tot}(R')$ along the major axis (blue line, left axis) of the best fit model. The best fit mass-to-light ratios $\Upsilon_{\text{I,tot,}i}$ are plotted against $\sigma_i$ for each MGE Gaussian ($i<5$, yellow stars). (The Gaussians $i=4$ and $i=5$ have the same $\Upsilon_{\text{I,tot,}i}$.) Shown is also the enclosed mass inside the projected radius $R'$ on the sky, $M(<R')$ (green line, right axis). The enclosed mass curve is overplotted with the independent finding for the Einstein mass $\pm 4 \%$ in Table \ref{tab:bestfitlensmodel} (red dot) at the Einstein radius (red dotted line); the agreement is very good.}
\label{fig:modelG}
\end{figure*}
%============================================

%--------------------------------------------
\subsubsection{JAM with lens mass model}
%--------------------------------------------

%--------------------------------------------
We make an independent prediction for the $v_\text{rms}$ curve by evaluating Equation \ref{eq:explicitLOSvelCap} (with $\beta_z = 0$) for the lens mass model in Table \ref{tab:bestfitlensmodel} ($\alpha = 1$, flat rotation curve). In addition, we also calculate a  $v_\text{rms}$ curve for two lens models which were found analogously, but assumed a slightly rising (falling) rotation curve slope of $\alpha=1.1$ ($\alpha=0.9$). The predictions are compared with the data in Figure \ref{fig:JAM_modelL}. While the most reliable constraint is around $R_\text{ein}$, the agreement within $R' \sim 3''$ is still striking: The $\alpha > 1$ model recreates the observed central dip, while the $\alpha = 1$ model fits the wings around $R_\text{eff}$. This is in concordance with observations in other galaxies. For $R'> R_\text{eff}$ we would expect $\alpha<1$---and the lensing model for $\alpha=0.9$ has indeed a slightly dropping $v_\text{rms}$ around $R_\text{eff}$, like the data. A definite comparison in this regime is however difficult as the lens models are just extrapolations outside of $R_\text{ein}$. While our lensing model assumes $\alpha(R')=\text{const}$, Figure \ref{fig:JAM_modelL} suggests, that a model with variable $\alpha(R')$ could fit even better. Overall the lensing model is in very good agreement with the $v_\text{rms}$ data within $R' \sim 3''$---even though it was derived completely independently.
%--------------------------------------------

%--------------------------------------------
\subsubsection{JAM with "mass-follows-light" and velocity anisotropy}
%--------------------------------------------

%--------------------------------------------
The first JAM model that we fit to the observed $v_\text{rms}$ within $R'<5''$ is a mass-follows-light model. Mass-follows-light models are often used in dynamical JAM modelling (e.g., \citealt{GlennEC,Cap06}) and generate a mass distribution by multiplying the intrinsic light distribution $\nu(R,z)$ by a constant total mass-to-light ratio  $\Upsilon_\text{I,tot}^\text{dyn}$. This assumes that the DM is always a constant fraction of the total matter distribution within the region covered by the kinematics. This simplified mass model sometimes gives good representations of the inner parts of galaxies, where the stellar component dominates.

We also allow for a overall constant but non-zero velocity anisotropy $\beta_z$ in the model. The model parameters ($\Upsilon_\text{I,tot}^\text{dyn},\beta_z$) that fit the $v_\text{rms}$ data best are found using a $\chi^2$-fit and are demonstrated in Figure \ref{fig:JAM_modelA2}.

For $\beta_z$ we imposed the fitting limits $\beta_z \in [-0.5,+0.5]$. While the outer parts of galaxies often show radially biased velocity anisotropy up to $\sim 0.5$ (from dynamical modelling of observed elliptical galaxies, e.g., \citet{Kronawitter2000}) and cosmological simulations (e.g., \citealt{2004MNRAS.352..535D,2001ApJ...557..533F}), the centers of galaxies are near-isotropic or have negative velocity anisotropy \citep{2003ApJ...583...92G}. Only in extreme models (e.g., around in-spiralling supermassive black holes, e.g., \citealt{1997NewA....2..533Q}) velocity anisotropies as low as $\sim -1$ have been found.

The best fit in Figure \ref{fig:JAM_modelA2} however strives to very negative $\beta_z$ to be able to reproduce the deep central dip in the  $v_\text{rms}$ curve.\footnote{Without limiting the fitting range, the best fit would be a unrealistically low $\beta_z \sim -2$.} But $\beta_z = -0.5$ is not even a remotely agreeable fit and lower anisotropies are not to be expected or realistic. We also tested radial profiles for $\beta_z(R)$ of the form proposed by \citet{BaesVanHese}, which was however equally unable to reproduce the data. We conclude, that this is due to the well-known degeneracy between anisotropy and mass profile \Wilma{[TO DO: REF]} and the mass-follows-light model is \emph{not} a good representation of the mass distribution in J1331's inner regions.

\Wilma{[TO DO: Make sure that we explain somewhere, why we model only in the inner regions]}

%============================================
\begin{figure*}
\centering
\includegraphics[width=0.9\linewidth]{fig/B4_contour_plot_short.ps}
\caption{Posterior probability distribution sampled with an MCMC (red dots and histograms) for a JAM model fitted to the stellar $v_\text{rms}$ data, with NFW halo, parametrized by $r_s$ and $v_\text{200}$, a stellar mass distribution generated from the I-band MGE in Table \ref{tab:MGEF814W} and a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and constant velocity anisotropy $\beta_z$. Shown are also the priors used for J1331's NFW halo, $\mathscr{N}(200~\text{km s}^{-1},40~\text{km s}^{-1})$ (green, see Equation \eqref{eq:prior_v200}) and the concentration vs. halo mass relation by \citet{Maccio08} from Equation \eqref{eq:Maccio08} in terms of $v_{200}$ vs. $r_s$ with $1\sigma$ scatter (blue, see Equation \eqref{eq:prior_c200}). We find slight covariances between $\Upsilon_\text{I,*}$,  $r_s$ and $\beta_z$: The smaller the DM contribution in the center (i.e., the larger $\Upsilon_\text{I,*}$), the less concentrated is the halo (i.e., the larger $r_s$) and the more velocity anisotropy is needed to reproduce the central $v_\text{rms}$ dip. As the effect of $v_{200}$ is mostly at larger radii, this parameter doesn't show any covariances, but is also mostly constrained by the prior.\\The MCMC samples are colour coded according to their probability (darker red for higher probability); the sample point with the highest probability is marked by a black diamond. The black cross is the mean of the distribution and the ellipses are derived from the covariance matrix of the MCMC samples and correspond approximately to $1\sigma$ (black solid ellipse) and $2\sigma$ (black dotted ellipse) confidence. The histograms of the marginalized 1D distributions are overplotted by the mean (black solid lines) and $1\sigma$ error (black dashed lines), whose values are also quoted in the figure and in Table \ref{tab:modelB4_bestfit}. The grey diamonds mark a random sub-selection of 12 samples; the corresponding models are shown in Figure \ref{fig:modelB4_models}.}
\label{fig:modelB4_triangle}
\end{figure*}
%============================================

%============================================
\begin{figure*}
\centering
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/B4_rms_error_curves.ps}
  \caption{Comparison of the $v_\text{rms}$ data with the best fit JAM models.}
  \label{fig:modelB4_vrms}
\end{subfigure}%
\hspace{.02\textwidth}
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_projmass.ps}
  \caption{Enclosed mass profile.}
  \label{fig:modelB4_enclMass}
\end{subfigure}
\caption{JAM model including a NFW halo and velocity anisotropy fitted to the stellar $v_\text{rms}$ data (blue solid dots) within $\sim3.5''$ and the Einstein mass (red solid dot). The 12 lines shown correspond to 12 models randomly drawn from the pdf (marked as grey diamonds in Figure \ref{fig:modelB4_triangle}) and demonstrate how tight the modelling constraints are. The mean and standard deviation of the pdf, i.e., the "best fit" parameters, are given in Table \ref{tab:modelB4_bestfit}. \emph{Panel (a):} At $R'\lesssim 3.5''$ the symmetrized $v_\text{rms}$ data used in the fit (solid blue points) is shown together with the best fit $v_\text{rms}$ models (red solid lines). At larger radii the non-symmetrized data (open blue dots) is compared to an extrapolation of the best fit models using the surface brightness MGE for the outer regions from Figure \ref{fig:MGEouterRegions} (red dashed lines). \Wilma{[TO DO: Fehler in Legend.]} \emph{Panel (b):} Shown is the circular velocity curve of the total mass (green), and separately the contribution of the stellar mass (yellow, again generated from the MGE in Table \ref{tab:MGEF814W}) and DM (grey). At the Einstein radius $R_\text{ein}$ (red dotted line) the Einstein mass $M_\text{ein}$ is overplotted with a 10\% error, which was also included in the fit as additional constraint. Overplotted is also the effective half-light radius (black dotted line) and the blue dashed line marks the radius within which the data and model were fitted.}
\label{fig:modelB4_models}
\end{figure*}
%============================================

\Wilma{[TO DO: introduce pdf]}

%============================================
\begin{table*}
\centering
\begin{tabular}{llrcl}
\hline
stellar I-band mass-to-light ratio & $\Upsilon_\text{I,*}$ & 4.2 & $\pm$ & 0.2\\
velocity anisotropy & $\beta_z$ & -0.4 & $\pm$ & 0.1 \\
NFW halo scale length & $r_s$ [kpc] & 40 & $\pm$ & 20\\
NFW halo virial velocity & $v_{200}$ [$\text{km s}^{-1}$] & 240 & $\pm$ & 40\\
NFW halo concentration & $c_{200}$ & 8 & $\pm$ & 2 \\
NFW halo mass & $M_{200}$ [$10^{12} M_\odot$] & 5 & $\pm$ & 2\\
\hline
\end{tabular}
\caption{Summary of the best fit parameters of the JAM model with NFW halo and velocity anisotropy, fitted to the $v_\text{rms}$ data within $\sim 3.5''$ and the Einstein mass. These estimates correspond to the mean and standard deviation of the pdf in Figure \ref{fig:modelB4_triangle}. The halo mass and concentration are calculated from the the best fit $r_s$ and $v_{200}$.}
\label{tab:modelB4_bestfit}
\end{table*}
%============================================

%--------------------------------------------
\subsubsection{JAM with increasing mass-to-light ratio}
%--------------------------------------------

%--------------------------------------------
In Section \ref{sec:results_lensing} we found from lensing constraints, that the light distribution might drop faster with radius than the mass distribution. This could correspond to a radially increasing total mass-to-light ratio. As velocity anisotropy alone cannot explain the observed kinematics in a simple a mass-follows-light model, we now allow for a mass-to-light ratio gradient in the JAM modelling. We therefore generate a mass model from the light distribution in Table \ref{tab:MGEF814W} by assigning each of the five Gaussians in the MGE its own total mass-to-light ratio $\Upsilon_{\text{I,tot,}i}$ and replace the total luminosity in Equation \eqref{eq:centralItotalL} $L_i$ with the Gaussians total Mass $M_i = \Upsilon_{\text{I,tot,}i} L_i$. We treat the five $\Upsilon_{\text{I,tot,}i}$ as free fit parameters and only require that $\Upsilon_{\text{I,tot,}j} \geq \Upsilon_{\text{I,tot,}i}$ when the corresponding $\sigma_j \geq \sigma_i$ to ensure that the overall mass-to-light ratio is increasing with radius.

Figure \ref{fig:enclMass_modelG} shows the best fit (projected local) mass-to-light ratio profile, which rises from $\Upsilon_\text{I,tot} = 2.53$ in the center and approaches a value of $\Upsilon_\text{I,tot} = 7.60$ outside of the fitted region at $R'\gtrsim 3''$. The central mass-to-light ratio is in agreement with the mass-to-light ratio $\Upsilon_\text{I,*}^\text{chab} = 2.5 \pm 0.6$, given in Table \ref{tab:previousresults} based on the results of \citet{SWELLSI} assuming a stellar population with a \citet{Chabrier2003} IMF (see also Section \ref{sec:MLdiscussion}). When assuming that galaxy bulges are in general older and redder in the center \Wilma{[TO DO: REF]}, i.e., $\Upsilon_\text{I,*}$ is more likely to drop with radius than to rise, the strong increase of $\Upsilon_\text{I,tot}(R')$ might be due to a strong contribution of dark matter in J1331.

Figure \ref{fig:JAM_modelG} shows that the best fit model nicely reproduces the central dip in the $v_\text{rms}$ curve, even though it has difficulties fitting the drop around $R' \sim 4''$. The latter might be because we only allowed the $\Upsilon_\text{I,tot}(R')$ to rise. A slight drop could be expected when the reddish bulge turns into the bluish disk and the contribution of the stellar component becomes less due to a lower $\Upsilon_\text{I,*}$ for younger and bluer populations.

In Figure \ref{fig:enclMass_modelG} we overplot the enclosed mass profile with the Einstein mass $M_\text{ein} = (7.77 \pm 0.33) \cdot 10^{10} M_\odot$ at the Einstein radius found from lensing in Table \ref{tab:bestfitlensmodel}. The agreement between the Einstein mass and the independently found $M(<R_\text{ein}) = 7.49 \cdot 10^{10} M_\odot$ from dynamical modelling is striking.
%--------------------------------------------

%--------------------------------------------
\subsection{JAM with a NFW dark matter halo} \label{sec:results_JAM_NFW}
%--------------------------------------------

%--------------------------------------------
The modelling attempts in the previous sections suggest that J1331's mass distribution could be more roundish in the inner regions and more massive at larger radii than expected from the distribution of stars alone. A DM halo in addition to the stellar component could explain these findings. 
%--------------------------------------------

%--------------------------------------------
\subsubsection{Including a DM halo}
%--------------------------------------------

%--------------------------------------------
We therefore proceed by modelling the mass distribution with (a) a stellar component, which we get from the light MGE in Table \ref{tab:MGEF814W} (deprojected to the intrinsic $\nu(R,z)$) times a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and (b) a spherical NFW DM component (see Section \ref{sec:model_JAM}) with halo scale length $r_s$ and circular velocity at the virial radius $v_{200}$ as free parameters. In the JAM modelling we use a 10-Gaussian MGE fit to the classical NFW profile in Equation \eqref{eq:NFWprofile}.

%============================================
\begin{figure}
\centering
\includegraphics[width=\linewidth]{fig/B4_rms_rot_curves_best_model.ps}
\caption{Generating the rotation curve from the JAM model with NFW halo and constant velocity anisotropy with the mean parameters in Table \ref{tab:modelB4_bestfit} and with the best fit rotation parameter $\kappa' = 0.76$ in Equation \eqref{eq:kappa_profile} (red solid lines). The second velocity moment in the first panel and the first velocity moment in the second panel with the additional fit parameter $\kappa'$ were fitted to the symmetrized data (solid blue points). The velocity dispersion is simply $\sigma = \sqrt{v_\text{rms}^2 - v_\text{rot}^2}$. At larger radii we compare the unsymmetrized data (open blue dots), the gas kinematics from \citet{SWELLSV} (green diamonds) and a JAM model using the same model parameters but the light distribution MGE generated from the Ellipse model in Figure \ref{fig:MGEouterRegions} as a prediction for the outer regions of J1331 (red dashed lines). The central regions are very well reproduced and we can also nicely predict the rotation curve at larger radii. Only at larger radii the $v_\text{rms}$ and $v_\text{rot}$ overestimate the measurements, probably due to a too massive NFW halo. \Wilma{[TO DO: There seem to be no minor ticks on x-axis.]}}
\label{fig:modelB4_vrot}
\end{figure}
%============================================

%--------------------------------------------
\subsubsection{Modelling and priors}
%--------------------------------------------

%--------------------------------------------
The full set of fit parameters is $(\Upsilon_\text{I,*},r_s,v_{200},\beta_z)$, where $\beta_z$ is again the constant velocity anisotropy parameter. We will investigate this parameter space with a MCMC\footnote{The Python code package for \emph{emcee}, a Monte Carlo Markov Chain implementation by \citet{emcee} is available online at \url{http://dan.iel.fm/emcee/current/}. The version from October 2013 was used in this work.} \citep{emcee} and use priors for the halo parameters to guide the fit to a realistic NFW halo shape.

\citet{Dutton10} give a relation for halo vs. stellar mass for late-type galaxies. Using the stellar mass estimate for J1331 from \citet{SWELLSI}, $m_* = (1.06 \pm 0.25) \cdot 10^{11} M_\odot$ for the Chabrier IMF estimate, we find ${v_{200}} = (202_{-33}^{+44})_{-13}^{+12}$. The first error is due to the $2\sigma$ scatter in the relation by \citet{Dutton10}. The second error is the propagated error due to the uncertainty in the stellar mass. We use this as a rough estimate for the halo of J1331 and as Gaussian prior on $v_{200}$, 
\begin{equation}
p(v_{200}) = \mathscr{N}(200~\text{km s}^{-1},40~\text{km s}^{-1}). \label{eq:prior_v200}
\end{equation}

We also use the concentration vs. halo mass relation by \citet{Maccio08} in Equation \eqref{eq:Maccio08} as a prior on the concentration, i.e.
\begin{equation}
p(\log c_{200} \mid v_{200}) = \mathscr{N}\left(\langle \log c_{200} \rangle (M_{200}) \mid 0.105 \right). \label{eq:prior_c200}
\end{equation}

For the velocity anisotropy parameter $\beta_z$ we will again employ a uniform prior 
\begin{equation*}
p(\beta_z) = \mathscr{U}(-0.5,+0.5)
\end{equation*}
to exclude very unrealistic anisotropies. The full prior used is then
\begin{eqnarray*}
&&p(\Upsilon_\text{I,*},r_s,v_{200},\beta_z) \\
&&= \frac{1}{\ln\left( 10 r_s\right)} p(\log c_{200} \mid v_{200}) \cdot p(v_{200}) \cdot p(\beta_z), 
\end{eqnarray*}
where the factor $1/\ln\left( 10 r_s\right)$ is the Jacobian of the transformation from the halo parameters $(v_{200},\log c_{200})$ to $(v_{200},r_s)$.

We restrict the $v_\text{rms}$ fit to a region $R' \lesssim 3.5''$, approximately within the effective half-light radius $R_\text{eff} = 2.6''$. We also include the Einstein mass $M(<R_\text{ein})$ with a 10\% error as an additional constraint in the fit.

%--------------------------------------------
\subsubsection{Result}
%--------------------------------------------

%--------------------------------------------
Figure \ref{fig:modelB4_triangle} shows the posterior probability distribution (pdf) of the fit sampled with an MCMC. Overplotted are also the priors used to constrain the NFW halo. The mean parameters are summarized in Table \ref{tab:modelB4_bestfit}. We find that the best fit NFW halo strives to be more massive and with a higher concentration (due to a smaller $r_s$) than  proposed by the priors. The model also prefers  very negative velocity anisotropies. Both, the high halo concentration and low $\beta_z$, are needed to reproduce the central dip of the $v_\text{rms}$ curve. Figure \ref{fig:modelB4_models} illustrates the range of best fit models according to the extent of the pdf. The models fit the $v_\text{rms}$ data in the inner regions quite well (Figure \ref{fig:modelB4_vrms}) and are also consistent with the Einstein mass (see Figure \ref{fig:modelB4_enclMass}). The extrapolation of the model to larger radii however overestimates the data, does not exhibit a drop around $\sim 6''$ at all and seems to be therefore overall too massive.

We also fitted a model with a cored logarithmic DM halo. The cored halo models are in general slightly less massive than the NFW halo and therefore fit the outer regions of J1331 better. However, the density profile of the cored halo as well as the I-band light distribution within the plane drop as $\rho(r) \propto r^{-2}$. There is therefore a strong degeneracy between the stellar mass and the DM. Overall, we were not able to obtain tight constraints on the cored logarithmic halo.

%============================================
\begin{table*}
\centering
\begin{tabular}{cccccc}
\hline\hline
& & \multicolumn{2}{c}{Chabrier IMF} & \multicolumn{2}{c}{Salpeter IMF}\\
      &  $L$ [$10^{10}L_{\odot}$]                & $M_*$ [$10^{10}M_\odot$]               & $\Upsilon_\text{I,*}^\text{chab}$ & $M_*$ [$10^{10}M_\odot$] & $\Upsilon_\text{I,*}^\text{sal}$ \\\hline
bulge &   $3.10 \pm 0.15 $  & $7.8 \pm 1.8$ & $2.5 \pm 0.6$ & $14.5 \pm 3.7 $ & $4.7 \pm 1.2$ \\
disk  &   $2.35 \pm 0.11 $  & $2.9 \pm 0.7$ & $1.2 \pm 0.3$ & $5.2 \pm 1.1$ & $2.2 \pm 0.5$ \\
total &   $5.45 \pm 0.19$ & $10.6 \pm 1.9$& & $19.7 \pm 3.9$&\\\hline
\end{tabular}
\caption{Total I-band luminosity, stellar mass and mass-to-light ratio, calculated from the I-band AB magnitudes and stellar masses found for J133's bulge and disk by \citet{SWELLSI} (their table 2) for comparison with this work. The transformation from AB magnitudes to the Johnson-Cousins I-Band used the relation $I[\text{mag}] = I[\text{ABmag}] - 0.309$ from \citet{FG1994} (their table 2). For the conversion from apparent magnitude to total luminosity the redshift $z=0.113$ \citet{SWELLSIII} was turned into a luminosity distance using the cosmology by \citet{WMAP5cosm}. }
\label{tab:previousresults}
\end{table*}
%============================================

%--------------------------------------------
\subsubsection{Rotation curve}
%--------------------------------------------

%--------------------------------------------
We generate a rotation curve from the best fit mean model in Table \ref{tab:modelB4_bestfit}, whose $v_\text{rms}$ curve is shown in the first panel of Figure \ref{fig:modelB4_vrot}. Following the procedure in Section \ref{sec:model_JAM}, we find the rotation curve by fitting the rotation parameter $\kappa'$ to the symmetrized $v_\text{rot}$ data within $R' = 3.5''$. The best fit with $\kappa' = 0.76$ is given in the second panel of Figure \ref{fig:modelB4_vrot}. The third panel shows the dispersion that follows from $\sigma = \sqrt{v_\text{rms}^2 - v_\text{rot}^2}$. Our assumptions for $\kappa(R)$ nicely reproduce a $v_\text{rot}$ model with counter-rotating core. Although we fitted $v_\text{rot}$ only to the inner regions, the extrapolation to large radii fits the data also very well.

While the dispersion $\sigma$ in the center fits by construction quite good, the predicted dispersion is much larger than the data. We would expect the disk rotationally supported and therefore have a low velocity dispersion; especially dispersions as high as $\sim 200~\text{km s}^{-1}$ are more likely to be observed in the pressure supported bulges of galaxies. There might be something unexpected with the $\sigma$ measurements around $\sim 5''$, but at large radii the the best fit model NFW halo is simply too massive. 
\Wilma{[TO DO: Captions in Results JAMwithNFW muessen noch ueberarbeitet werden.]}
%--------------------------------------------

%--------------------------------------------
\section{Discussion and Conclusion} \label{sec:Discussion}
%--------------------------------------------

%--------------------------------------------
We've presented different dynamical models for the central region of J1331. Some of them capture the observed kinematics, but none of them work at both small and large radii. In the following we discuss possible reasons, also by comparing our results to previous work.
%--------------------------------------------

%--------------------------------------------
\subsection{On J1331's central stellar mass-to-light ratio} \label{sec:MLdiscussion}
%--------------------------------------------

%--------------------------------------------
Some of the ambiguities in recovering J1331's matter distribution could be resolved by learning more about stellar populations with different IMFs in J1331. In particular, a sophisticated guess for the stellar mass-to-light ratio in the bulge could be compared to our very reliable measurement of the total mass-to-light ratio inside the Einstein radius $\Upsilon_\text{I,tot}^\text{ein} = 5.56 \Upsilon_{I,\odot}$. This would then either support or contradict the presence of a significant amount of DM in the bulge.

Traditional choices for the IMF are the bottom-heavy IMF by \citet{Salpeter1955},
$$\xi(m) \propto m^{-x}, x=2.35,$$
where $\xi(m) \diff m$ is the number of stars with mass $m$ in $[m,m+\diff m]$, and the IMFs by \citet{2002Sci...295...82K} and \citet{Chabrier2003}, which are in agreement with each other and predict less low-mass stars.

\citet{Ferreras} found a relation between the central stellar velocity dispersion $\sigma_0$ in early-type galaxies and the IMF slope $x$; a higher $\sigma_0$ suggests a more bottom-heavy IMF. For a unimodal (Salpeter-like) IMF and $\sigma_0 \simeq 200~\text{km s}^{-1}$ in J1331 (see Figure \ref{fig:kinematics}) they predict $x \approx 2.33$, which is close to the standard Salpeter slope, also supported by \citet{2014MNRAS.438.1483S}. When assuming a bi-modal (Kroupa-equivalent-like) IMF, \citet{Ferreras} predict $x \approx 2.85$ for J1331's central velocity dispersion. This is more bottom-heavy than the standard \citet{2002Sci...295...82K} IMF. Overall, the central velocity dispersion suggests a rather bottom-heavy IMF in J1331's bulge and therefore large stellar mass-to-light ratio.

\citet{SWELLSI} estimated J1331's stellar bulge mass given a Salpeter IMF and measured the I-band AB magnitude of the bulge. Transformed to a stellar I-band mass-to-light ratio, their results would correspond to $\Upsilon_\text{I,*}^\text{sal} = 4.7 \pm 1.2$ (see Table \ref{tab:previousresults}). This is not too far from $\Upsilon_\text{I,*} = 4.2 \pm 0.2$ (see Table \ref{tab:modelB4_bestfit}), which we found when including a NFW halo in the JAM modelling.

When \citet{SWELLSI} assumed a Chabrier IMF, their result translates to $\Upsilon_\text{I,*}^\text{chab} = 2.5 \pm 0.6$ (see Table \ref{tab:previousresults}). In Section \ref{sec:results_JAM_SB} we created a dynamical model from only the surface brightness distribution and an increasing mass-to-light ratio profile without additional DM halo. We found that such a model would be perfectly consistent with the Einstein mass, predict a total $\Upsilon_\text{I,tot}(R'\sim0) = 2.53$---being consistent with the Chabrier IMF estimate by \citet{SWELLSI}---and rise quickly to $\Upsilon_\text{I,tot}(R'\gtrsim R_\text{ein}) \gtrsim 6$.

We also compare our results from Section \ref{sec:results_JAM_NFW} with the study by \citet{SWELLSV}. They found that the bulge of J1331 has an IMF \emph{more} bottom-heavy than the Salpeter IMF from fitting a NFW halo to (1) the Einstein mass and (2) gas kinematics at larger radii $\gtrsim 8''$. In Section we fitted a mass model with NFW halo to (1) the Einstein mass and (2) stellar kinematics within $\sim 3.5''$. Our best fit $\Upsilon_\text{I,*} = 4.2 \pm 0.2$ (see Table \ref{tab:modelB4_bestfit}) indicates a \emph{less} bottom-heavy IMF than the Salpeter IMF. \cite{SWELLSV} found systematically lower NFW halo masses ($v_\text{circ,halo}(5'') \sim 120~\text{km s}^{-1}$ according to their Figure 2) than we did ($v_\text{circ,halo}(5'') \sim 200~\text{km s}^{-1}$).
%--------------------------------------------

%============================================
\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_vcirc.ps}
\caption{Comparison of the circular velocity curve of J1331's inner regions for different models: (a) JAM model with NFW DM halo from Section \ref{sec:results_JAM_NFW} and Figure \ref{fig:modelB4_models} (green). (b) Lens model from Section \ref{sec:results_lensing} and Figure \ref{fig:JAM_modelL} with $\alpha = 1.1$ (red dashed line), $\alpha = 1$ (red solid line) and $\alpha=0.9$ (red dash-dotted line). (c) Mass-follows-light model, which uses the F814W surface brightness in Table \ref{tab:MGEF814W} and the mass-to-light ratio in the Einstein radius, $\Upsilon^\text{ein}_\text{I,tot} = 5.56$, to generate a mass distribution, as in Figure \ref{fig:lenscomparelight} (orange line).  (d) Model from gas kinematics and Einstein mass found by \citet{SWELLSV} (their Figure 2, best model with 68\% confidence region) (blue lines).}
\label{fig:vcirc_comparison}
\end{figure}
%============================================

%--------------------------------------------
\subsection{On J1331's central kinematics}
%--------------------------------------------

%--------------------------------------------
In Figure \ref{fig:vcirc_comparison} we compare the circular velocity curve found by \citet{SWELLSV} with a mass-follows-light model scaled to fit our Einstein mass (by multiplying the light distribution in Table \ref{tab:MGEF814W} with $\Upsilon_\text{I,tot}^\text{ein} = 5.56$). Within $R < 5''$ they agree with each other.

The models in this work used more than just the Einstein mass to constrain the matter distribution at small radii: The lens mass model constrained also the shape of the mass distribution within the lensing image configuration at $R_\text{ein} \sim 1''$. The dynamical models used stellar kinematics inside $R' \simeq 3.5''$ \Wilma{[TO DO: Check]}. We compare the lens mass model's $v_\text{circ}$ (for $\alpha=1.0\pm 0.1$) with the NFW JAM model (Table \ref{tab:modelB4_bestfit}) in Figure \ref{fig:vcirc_comparison} as well. Within and around $R_\text{ein}$ they are consistent with each other, even though they where independently derived. They do not agree with the result by \citet{SWELLSV} and in Section \ref{sec:results_JAM_SB} we showed, that ``mass-follows-light'' is not a good model for J1331.

Overall, we were not able to find a consistent explanation for J1331's central $v_\text{rms}$ dip. It cannot be due to tangential velocity anisotropy in the center alone (see Section \ref{sec:results_JAM_SB}, Figure \ref{fig:JAM_modelA2}). It also cannot be explained by a strong contribution of DM inside the bulge together with a moderate tagential velocity anisotropy, because the corresponding DM halos would still be too massive to fit the data in the outer regions (see Section \ref{sec:results_JAM_NFW}, Figure \ref{fig:modelB4_vrms}]).e

Another feature in the stellar kinematics, that none of our JAM models was able to reproduce in the slightest and which we therefore excluded in the modelling, was the dip in $v_\text{rms}$ around $\sim 6''$, which occurs around the transition from bulge to disk (see Figures \ref{fig:F814W} and \ref{fig:kinematics}).
%--------------------------------------------

%--------------------------------------------
\subsection{On J1331's possible merger history and modelling failures}
%--------------------------------------------

%--------------------------------------------
%Why we think that J1331 had a merger
J1331 has a large counter-rotating stellar core within $\sim 2''$. This suggests a process in J1331's past in which two components with angular momenta oriented in opposite directions were involved.

%Gas accretion - no!
Accretion of gas on retrograde orbits and subsequent star formation could lead to a younger and counter-rotating stellar population \Wilma{[TO DO: REF]}. However, to form enough stars such that the net rotation of the large and massive core is retrograde, a very large amount of gas would have had to be accreted by J1331---which is not very likely.

%Mergers - yes!
Another scenario are galaxy mergers. Major mergers can form kinematically decoupled cores (KDCs) (e.g., \citealt{2011MNRAS.414.2923K,2015ApJ...802L...3T}), if they include large amounts of gas \citep{2010ApJ...723..818H}. During a minor merger, the dense nucleus of a satellite galaxy on a retrograde orbit could survive the dissipationless accretion and spiral to the core due to tidal friction (e.g., \citealt{1984ApJ...287..577K}).

%Merger + color gradient
Usually ellipticals and the bulges of massive spirals appear reddest in their center and getting increasingly bluer with larger radii. Mergers can reverse this behaviour by inducing the creation of young stellar populations in the remnant's center. Major mergers can trigger star formation bursts (e.g., \Wilma{[TO DO: REF, maybe http://arxiv.org/pdf/1409.5126v2.pdf???]}). After a minor merger the satellite's stellar population now residing in the remnant's core is in general younger than the progenitor's bulge \Wilma{[TO DO: REF]} . The different stellar populations in a merger remnant can be associated with different $\Upsilon_*$ and sometimes even show up as a reverse colour gradient within the bulge in photometry \Wilma{[TO DO: REF]}.

%Color gradient in J1331
Even though investigation of the photometry of J1331 did not reveal a distinct blue core in J1331, we cannot fully exclude the possibility that J1331 has such a $\Upsilon_*$ gradient (see discussion in Section  \Wilma{[TO DO: Where???]}). In this case the restrictive assumption of a constant $\Upsilon_*$ in our JAM modelling could have lead to wrong conclusions about the DM distribution.

%Merger and kinematic twist
Other ways how mergers can can modify the structure of galaxies are warps in the outer parts or kinematic twists in the center of the remnant galaxy \citep{2013pss5.book..923S}, which show up as misalignments of kinematic and photometric major axis.

%Kinematic twist in J1331
From kinematics along the photometric major axis only it cannot be determined if such a misalignement is present in J1331. But if it were, our modelling assumption of axisymmetry would not be satisfied anymore.

We note that kinematics measured along an axis different from the kinematic major axis would result in $v_\text{rot}$ measurements being lower than the actual maximum $v_\text{circ}$. At large radii this could lead to an underestimation of the DM halo mass.
%--------------------------------------------

%--------------------------------------------
\subsection{Future work}
%--------------------------------------------

%--------------------------------------------
Standard JAM modelling approaches seem not to work for J1331. The existing data---photometry and major axis kinematics---is however not sufficient to decide which of our model assumptions lead to the failure to find an overall consistent mass model.

Two-dimensional stellar kinematics would greatly help to resolve this problem. The main future work would be therefore getting high-resolution integral-field spectroscopy for J1331. High spatial resolution would be required to clearly identify J1331's presumably complex kinematic structure. High spectral resolution would be important to be able to reliably measure the low velocity dispersion in the outer regions of J1331.

Specifically 2D kinematics should help to answer the following questions: Is the drop in $v_\text{rms}$ around $R' \sim 3-6~\text{kpc}$ real? Did the long slit spectrograph maybe miss the major axis of the disk? And most importantly: Are the kinematics asymmetric? Is it possible that there even exists a kinematic twist due to the merger in J1331's past?

Furthermore, learning more about different stellar populations in J1331 would lead to valuable constraints for the modelling. While a quick investigation of the photometric colour profile did not reveal obvious colour gradients in J1331's bulge, there could be still stellar $\Upsilon_{I,*}$ variations due to age of metallicity differences. Existing major axis spectroscopy and/or future IFU data could be employed (i) to investigate absorption line indices to confirm (or contradict) the existence of $\Upsilon_{I,*}$ gradients and (ii) to perform stellar population analyses to constrain $\Upsilon_{I,*}$ reliably and independently of kinematics.

Future modelling approaches should fit dynamics (stellar and gas kinematics from) simultaneously with the gravitational lensing (image positions, shape and even flux ratios) in a similar fashion to \citet{SWELLSIV}. To also model the extent, shape and flux of the lensing images, the method by \citet{2004ApJ...611..739T,2003ApJ...590..673W} could be employed, which models the surface brightness distribution of the images and source on a pixelated grid. For this to work a good model for the galactic extinction would be needed---but 2D spectroscopy could also help with this.

All of the would lead to a much better understanding of J1331's structure and mass distribution and therefore answer questions on how mergers might modify spiral galaxies.
%--------------------------------------------

%--------------------------------------------
\subsection{Summary}
%--------------------------------------------

%--------------------------------------------
%Intro:
J1331 is a massive spiral galaxy which acts as strong gravitational lens for a background source. J1331 appears also to be a merger remnant due to it's large counter-rotating core. The goal of this work was to recover J1331's matter distribution by means of two methods, gravitational lensing and dynamical modelling. We focus on the bulge region of J1331, to complement previous studies of J1331 by \citet{SWELLSIII,SWELLSV}. The independent mass constraint which we derive from lensing and dynamics agree very well with each other within $R_\text{eff}$.

In our lensing approach we fitted a scale-free galaxy model to the lensing image position. This constrained the Einstein radius to within 2\% ($R_\text{ein}=(0.91\pm0.02)''\simeq(1.83\pm0.04)~\text{kpc}$), and the Einstein mass to within 4\% ($M_\text{ein} = (7.8\pm0.3) \cdot 10^{10} M_\odot$), consistent with results by \citet{SWELLSIII}. The recovered mass distribution agrees also very well with the shape of the observed lensing images.

To get a handle of J1331's light distribution we used a MGE fit to J1331's surface brightness in the F814W filter in HST imaging by \citet{SWELLSI}. Based on this we found J1331's effective radius to be $R_\text{eff} \simeq 2.6'' \hat{=} 5.2~\text{kpc}$ and its total I-band luminosity to be $L_\text{I,tot} \simeq 5.6 \cdot 10^{10} L_\odot$.

We used axisymmetric JAM modelling to calculate the second velocity moment of a tracer and mass distribution given in terms of MGEs. The JAM model of the lens mass model gave a independent prediction which was consistent with observed stellar kinematics from major axis long slit spectrography by \citet{SWELLSV} within $R_\text{eff}$. We also fitted mass models with and without NFW halo to the stellar kinematics within $R'=3.5~\text{kpc}$. From this we deduced that a mass-follows-light model with constant total mass-to-light ratio is not a good model for J1331---not even in the inner regions. To describe the observed stellar kinematics we either require a strong contribution of a dark matter halo already in the bulge, or a strongly varying stellar mass-to-light ratio. We also showed that it is possible to construct a model which includes the counter-rotating core and is consistent with the rotation curve at large radii.

While both our independent mass models are consistent with each other within $\sim R_\text{eff}$, they do not agree with previous findings by \citet{SWELLSV}, nor the data at large radii. We attribute this to the fact \citet{SWELLSV} derived mass constraints from kinematics in the outer regions only, while we focussed on the inner regions in detail. We speculate that a merger might have modified the kinematic structure and/or mass distribution of J1331 such that crucial model assumptions are not valid anymore. To resolve the ambiguities in J1331's mass distribution two-dimensional kinematic maps of J1331 from integral-fiel units spectroscopy would be needed.
%--------------------------------------------

%--------------------------------------------
\bibliographystyle{mnras}
\bibliography{literaturelist}
%--------------------------------------------

\label{lastpage}

\end{document}

### 2016-01-25 LensingPaper_draft_v3.05.tex
Finished editing the captions.

@@
 %--------------------------------------------
-\subsubsection{Best fit lens model} 
+\subsubsection{Best fit lens model} \label{sec:results_lensing_bestfit}
 %--------------------------------------------
@@
   \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_projmass.ps}
-  \caption{Enclosed mass profile.}
+  \caption{Enclosed mass profiles for the best fit models.}
   \label{fig:modelB4_enclMass}
 \end{subfigure}
-\caption{JAM model including a NFW halo and velocity anisotropy fitted to the stellar $v_\text{rms}$ data (blue solid dots) within $\sim3.5''$ and the Einstein mass (red solid dot).
+\caption{JAM model including a NFW halo and constant velocity anisotropy fitted to the stellar $v_\text{rms}$ data (blue solid dots) within $\sim3.5''$ and the Einstein mass (red solid dot).
 The 12 lines shown correspond to 12 models randomly drawn from the pdf (marked as grey diamonds in Figure \ref{fig:modelB4_triangle}) and demonstrate how tight the modelling constraints are.
@@
 \end{tabular}
-\caption{Summary of the best fit parameters of the JAM model with NFW halo and velocity anisotropy, fitted to the $v_\text{rms}$ data within $\sim 3.5''$ and the Einstein mass.
+\caption{Summary of the best fit parameters of the JAM model with NFW halo and constant velocity anisotropy, fitted to the $v_\text{rms}$ data within $\sim 3.5''$ and the Einstein mass.
 These estimates correspond to the mean and standard deviation of the pdf in Figure \ref{fig:modelB4_triangle}.
@@
 \includegraphics[width=\linewidth]{fig/B4_rms_rot_curves_best_model.ps}
-\caption{Generating the rotation curve from the JAM model with NFW halo and constant velocity anisotropy with the mean parameters in Table \ref{tab:modelB4_bestfit} and with the best fit rotation parameter $\kappa' = 0.76$ in Equation \eqref{eq:kappa_profile} (red solid lines).
-The second velocity moment in the first panel and the first velocity moment in the second panel with the additional fit parameter $\kappa'$ were fitted to the symmetrized data (solid blue points).
-The velocity dispersion is simply $\sigma = \sqrt{v_\text{rms}^2 - v_\text{rot}^2}$.
-At larger radii we compare the unsymmetrized data (open blue dots), the gas kinematics from \citet{SWELLSV} (green diamonds) and a JAM model using the same model parameters but the light distribution MGE generated from the Ellipse model in Figure \ref{fig:MGEouterRegions} as a prediction for the outer regions of J1331 (red dashed lines).
+\caption{Generating the rotation curve $v_\text{rot}(R')$ (red solid line in middle panel) from the best fit JAM model with NFW halo by fitting the rotation parameter $\kappa'$ to the symmetrized $v_\text{rot}$ data within $R'\sim3.5''$ (solid blue dots in central panel).
+The first panel shows the $v_\text{rms}$ data and model analogous to Figure \ref{fig:modelB4_vrms} for the mean parameters in Table \ref{tab:modelB4_bestfit}.
+The second panel shows the corresponding $v_\text{rot}$ for the best fit rotation parameter $\kappa' = 0.76$ in Equation \eqref{eq:kappa_profile} (red solid lines).
+The third panel shows simply the velocity dispersion $\sigma = \sqrt{v_\text{rms}^2 - v_\text{rot}^2}$.
+At larger radii we compare the unsymmetrized data (open blue dots), the gas kinematics from \citet{SWELLSV} (green diamonds) and an extrapolation of the JAM model, using the light distribution MGE from Figure \ref{fig:MGEouterRegions} for the outer regions (red dashed lines).
 The central regions are very well reproduced and we can also nicely predict the rotation curve at larger radii.
@@
 %--------------------------------------------
-\subsubsection{Result}
+\subsubsection{Result} \label{sec:results_JAM_NFW_results}
 %--------------------------------------------
@@
 \centering
+\caption{Total I-band luminosity, stellar mass and mass-to-light ratio, calculated from the I-band AB magnitudes and stellar masses found for J133's bulge and disk by \citet{SWELLSI} (their table 2) for comparison with this work.
+The transformation from AB magnitudes to the Johnson-Cousins I-Band used the relation $I[\text{mag}] = I[\text{ABmag}] - 0.309$ from \citet{FG1994} (their table 2).
+For the conversion from apparent magnitude to total luminosity the redshift $z=0.113$ \citet{SWELLSIII} was turned into a luminosity distance using the cosmology by \citet{WMAP5cosm}.
+}
 \begin{tabular}{cccccc}
@@
 \end{tabular}
-\caption{Total I-band luminosity, stellar mass and mass-to-light ratio, calculated from the I-band AB magnitudes and stellar masses found for J133's bulge and disk by \citet{SWELLSI} (their table 2) for comparison with this work.
-The transformation from AB magnitudes to the Johnson-Cousins I-Band used the relation $I[\text{mag}] = I[\text{ABmag}] - 0.309$ from \citet{FG1994} (their table 2).
-For the conversion from apparent magnitude to total luminosity the redshift $z=0.113$ \citet{SWELLSIII} was turned into a luminosity distance using the cosmology by \citet{WMAP5cosm}.
-}
 \label{tab:previousresults}
@@
 \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_vcirc.ps}
-\caption{Comparison of the circular velocity curve of J1331's inner regions for different models: (a) JAM model with NFW DM halo from Section \ref{sec:results_JAM_NFW} and Figure \ref{fig:modelB4_models} (green).
-(b) Lens model from Section \ref{sec:results_lensing} and Figure \ref{fig:JAM_modelL} with $\alpha = 1.1$ (red dashed line), $\alpha = 1$ (red solid line) and $\alpha=0.9$ (red dash-dotted line).
+\caption{Comparison of the circular velocity curve of J1331's inner regions for different models: (a) JAM model with NFW DM halo from Section \ref{sec:results_JAM_NFW_results} and Figure \ref{fig:modelB4_models} (green).
+(b) Lens model from Section \ref{sec:results_lensing_bestfit} and Figure \ref{fig:JAM_modelL} with $\alpha = 1.1$ (red dashed line), $\alpha = 1$ (red solid line) and $\alpha=0.9$ (red dash-dotted line).
 (c) Mass-follows-light model, which uses the F814W surface brightness in Table \ref{tab:MGEF814W} and the mass-to-light ratio in the Einstein radius, $\Upsilon^\text{ein}_\text{I,tot} = 5.56$, to generate a mass distribution, as in Figure \ref{fig:lenscomparelight} (orange line).

### 2016-01-26 LensingPaper_draft_v3.05.tex
Last TO DO is done.

@@
 
-Cosmological simulations suggest that cold DM forms cuspy halos following a Navarro-Frenk-White (NFW) profile \citep{NFW96}.
+Cosmological simulations suggest that cold DM forms cuspy halos following a Navarro-Frenk-White (NFW) profile \citep{1996ApJ...462..563N}.
 However, the existence of central DM density cusps in massive galaxies depends strongly on the stellar mass-to-light ratio (e.g., \citealt{2011MNRAS.416..322D}) and DM dominated dwarf galaxies even favour DM halos with cores (e.g., \citealt{1994Natur.370..629M,2001ApJ...552L..23D}).
@@
 
-The mass profile at larger galactocentric radii can be probed by gas rotation curves that directly measure the galaxy's circular velocity profile (e.g., \citealt{1980ApJ...238..471R})\Wilma{[TO DO: Can I use this here?]}.
+The mass profile at larger galactocentric radii can be probed by gas rotation curves that directly measure the galaxy's circular velocity profile (e.g., \citealt{1980ApJ...238..471R}).
 However, due to its dissipative nature, gas motions are very sensitive to disturbances by e.g., spiral arms and bars (e.g., \citealt{2004dad..book.....S}).
@@
 
-The Sloan WFC Edge-on Late-type Lens Survey (SWELLS, WFC = Wide field camera) \citep{SWELLSI,SWELLSII,SWELLSIII,SWELLSIV,SWELLSV,SWELLSVI} is dedicated to find and investigate spiral galaxies, which are (a) strong gravitational lenses and (b) seen almost edge-on, such that rotation curves can be easily measured.
+The Sloan WFC Edge-on Late-type Lens Survey (SWELLS, WFC = Wide field camera) \citep{SWELLSI,SWELLSII,SWELLSIII,SWELLSIV,SWELLSV,SWELLSVI} is dedicated to find and investigate spiral galaxies, which are (i) strong gravitational lenses and (ii) seen almost edge-on, such that rotation curves can be easily measured.
 By combining lensing and dynamical modelling degeneracies inherent in both methods can be broken.
@@
 They might rather be star forming regions of a background galaxy.) \emph{Panel (d):} Stellar Kinematics along the galaxy's major axis as measured by \citet{SWELLSV}.
-Shown are line-of-sight rotation velocity $v_\text{rot}$ (top), line-of-sight velocity dispersion $\sigma$ (middle) and the rms-velocity $v_\text{rms} = \sqrt{v_\text{rot}^2 + \sigma^2}$ (bottom).
+Shown are line-of-sight rotation velocity $v_\text{rot}$ (top), line-of-sight velocity dispersion $\sigma$ (middle) and the root mean-square (rms) velocity $v_\text{rms} = \sqrt{v_\text{rot}^2 + \sigma^2}$ (bottom).
 The dashed line indicates the galaxy's effective half-light radius (in the F814W filter), $R_\text{eff} = 2.6'' = 5.2~\text{kpc}$.
@@
 %--------------------------------------------
-J1331 is located at right ascension = 202.91800$^\circ$ and a declination = 36.46999$^\circ$ (epoch J2000).
-\citet{SWELLSI} found from SDSS spectra that J1331 has two redshifts inside $1''$: J1331 itself has $z_d = 0.113$ and $z_s = 0.254$ is the redshift of the lensed background source \citep{SWELLSIII}.
+J1331 is located at right ascension = 202.91800$^\circ$ and declination = 36.46999$^\circ$ (epoch J2000).
+\citet{SWELLSI} found from SDSS spectra that J1331 has two redshifts inside $R'=1''$: J1331 itself has $z_d = 0.113$ and $z_s = 0.254$ is the redshift of the lensed background source \citep{SWELLSIII}.
 According to the WMAP5 cosmology \citep{WMAP5cosm}, J1331 has an angular diameter distance of 414 Mpc, which translates into a transverse scaling of $1'' \hat{=} 2.01~\text{kpc}$.
@@
 The images are a combination of four exposures with each an exposure time of $400~\text{sec}$ and were drizzled to a pixel scale of 1 pixel = $0.05''$.
-In particular, we use the images in the filters F450W, to identify the positions of the bluish lensing images, and F814W (I-band) to create a surface brightness MGE model of the reddish bulge.
+In particular, we use the images in the filters F450W, to identify the positions of the bluish lensing images, and F814W (I-band) to create a surface brightness model of the reddish bulge.
 
@@
 The width of the slit was $1''$ and the seeing conditions had a FWHM of $\sim 1.1''$.
-1D Spectra for spatial bins of different widths along the major axis were extracted.
-They measured line-of-sight stellar rotation velocities ($v_\text{rot}$) and stellar velocity dispersion ($\sigma$) from the spectrum containing the absorption lines Mgb (5177 \AA) and FeII (5270, 5335 and 5406 \AA) (analogous to \citealt{SWELLSII}).
-Gas kinematics were extracted from Gaussian line profile fits to H$\alpha$ (6563 \AA) and [NII] (6583 and 6548 \AA) emission lines, as tracers for ionized gas.
-
-The stellar kinematics, $v_\text{rot}$, $\sigma$ and $v_\text{rms}^2=v_\text{rot}^2 + \sigma^2$ are shown in Figure \ref{fig:kinematics}.
-The rotation curve reveals a counter-rotating core within $2''\simeq$ 4 kpc.
-Outside of $\sim 3.5''$ there is a steep drop in the dispersion.
+1D spectra for spatial bins of different widths along the major axis were extracted.
+They measured line-of-sight stellar rotation velocities ($v_\text{rot}$) and stellar velocity dispersions ($\sigma$) from the spectral region containing the absorption lines Mgb (5177 \AA) and FeII (5270, 5335 and 5406 \AA) (analogous to \citealt{SWELLSII}).
+Gas kinematics were extracted from Gaussian line profile fits to H$\alpha$ (6563 \AA) and [NII] (6583 and 6548 \AA) emission lines as tracers for ionized gas.
+
+The stellar kinematics, $v_\text{rot}$, $\sigma$ and the root-mean-square velocity $v_\text{rms}^2=v_\text{rot}^2 + \sigma^2$ are shown in Figure \ref{fig:kinematics}.
+The rotation curve reveals a counter-rotating core within $2''\hat{=}4~\text{kpc}$.
+Outside of $\sim 3.5''$ there is a drop in the dispersion.
 This could indicate the boundary between the pressure supported bulge and the rotationally supported disk, which appears around this radius in the F450W filter in Figure \ref{fig:F450W}.
@@
 
-Inside of $\sim 4''$, the data appears to be symmetric, outside of this the assumption of axisymmetry seems not to be valid anymore, considering the data.
+Inside of $\sim 4''$ the data appears to be symmetric; outside of it the data suggests that the assumption of axisymmetry seems not to be valid anymore.
 We add $-2.3~\text{km s}^{-1}$ to the $v_\text{rot}$ to ensure $v_\text{rot}(R'=0) \sim 0$ as a possible correction term for a misjudgement of the systemic velocity.
 We also symmetrize the data within $4''$ and asign a minimum error of $\delta v_\text{rms} > 5~\text{km s}^{-1}$ to the $v_\text{rms}$ data.
-In the JAM modelling, which is based on the assumption of axisymmetry, only stellar kinematics with $R'  \lesssim 2.5''$ or $R' \lesssim 4''$ are used.
-Another reason to restrict to modelling on the bulge region is that our MGE in Table \ref{tab:MGEF814W} is only a good representation of J1331's F814W light distribution inside $\sim 5''$.
-\Wilma{[TO DO: noch mal die data section editen]}
+In our dynamical Jeans modelling approach, which is based on the assumption of axisymmetry, only stellar kinematics with either $R'  \lesssim 2.5''$ or $R' \lesssim 4''$ are used.
+Another reason to restrict to modelling to the bulge region is that our surface brightness model (Table \ref{tab:MGEF814W} and Figure \ref{fig:MGEinnerRegions}) is only a good representation of J1331's F814W light distribution inside $\sim 5''$.
 %--------------------------------------------
@@
 %--------------------------------------------
-JAM modelling assumes galaxies to be (a) collisionless (i.e., the collisionless Boltzmann equation for the distribution function $f(\vect{x},\vect{v},t)$ has to be satisfied, $\frac{\diff f(\vect{x},\vect{v},t)}{\diff t} = 0$), (b) in a steady state ($\frac{\partial}{\partial t} = 0$), (c) axisymmetric (best described in cylindrical coordinates $(R,z,\phi)$ and $\frac{\partial}{\partial \phi} = 0$).
+JAM modelling assumes galaxies to be (i) collisionless (i.e., the collisionless Boltzmann equation for the distribution function $f(\vect{x},\vect{v},t)$ has to be satisfied, $\frac{\diff f(\vect{x},\vect{v},t)}{\diff t} = 0$), (ii) in a steady state ($\frac{\partial}{\partial t} = 0$), (iii) axisymmetric (best described in cylindrical coordinates $(R,z,\phi)$ and $\frac{\partial}{\partial \phi} = 0$).
 From this follow the axisymmetric Jeans equations as the vector-valued first moment of the Boltzmann equation, i.e.,
@@
 The JAM models give us a prediction for the second line-of-sight velocity moment $\langle v_\text{los}^2 \rangle$.
-The root mean square (rms) line-of-sight velocity $v_\text{rms}$ allows a data-model comparison by relating theses velocities according to
+The root-mean-square (rms) line-of-sight velocity $v_\text{rms}$ allows a data-model comparison by relating theses velocities according to
 \begin{equation*}
@@
 As mentioned above, JAM modelling allows to incorporate an invisible matter component in addition to the luminous matter in the form of an MGE.
-In Section \ref{sec:results_JAM_NFW} we will include a spherical Navarro-Frenk-White (NFW) DM halo \citep{NFW96} in the dynamical model.
+In Section \ref{sec:results_JAM_NFW} we will include a spherical Navarro-Frenk-White (NFW) DM halo \citep{1996ApJ...462..563N} in the dynamical model.
 The classical NFW profile has the form
@@
 \end{equation} 
-There is a close relation between the concentration and halo mass in simulations \citep{NFW96}. \citet{Maccio08} found this relation for the WMAP5 cosmology to be
+There is a close relation between the concentration and halo mass in simulations \citep{1996ApJ...462..563N}. \citet{Maccio08} found this relation for the WMAP5 cosmology to be
 \begin{equation}
@@
 (their equation 10), with a Gaussian scatter of $\sigma_{\log c_{200}} = 0.105$ (their Table A2). 
-\Wilma{[TO DO: Section on JAM model noch mal durchgehen, ist noch nicht so toll.]}
 %--------------------------------------------
@@
 angular diameter distance & $D_d$ [Mpc] & $414$ \\
-scaling                   & 1 kpc / 1$''$ & $2.006$ \\
+scaling                   & $1~\text{kpc} / 1''$ & $2.006$ \\
 position angle from North          & $\phi$ [degrees] & $42.90^\circ$\\
@@
 We determine the circularized effective radius $R_\text{eff}$ of J1331 from the definition $L(<R_\text{eff}) \equiv \frac 12 L_\text{tot}$ and the growth curve $L(<R')$ from the MGE model of the outer regions, where $R'$ is the projected radius on the sky.
-We find the effective radius to be $R_\text{eff} \simeq 2.6'' \hat{=} 5.2 \text{ kpc}$.
+We find the effective radius to be $R_\text{eff} \simeq 2.6'' \hat{=} 5.2~\text{kpc}$.
 All values are summarized in Table \ref{tab:galaxyparameters}.
@@
 %--------------------------------------------
-\subsubsection{JAM with "mass-follows-light" and velocity anisotropy}
+\subsubsection{JAM with "mass-follows-light" and velocity anisotropy} \label{sec:results_JAM_SB_MfL}
 %--------------------------------------------
@@
 We also tested radial profiles for $\beta_z(R)$ of the form proposed by \citet{BaesVanHese}, which was however equally unable to reproduce the data.
-We conclude, that this is due to the well-known degeneracy between anisotropy and mass profile \Wilma{[TO DO: REF]} and the mass-follows-light model is \emph{not} a good representation of the mass distribution in J1331's inner regions.
-
-\Wilma{[TO DO: Make sure that we explain somewhere, why we model only in the inner regions]}
+We conclude, that this is due to the well-known degeneracy between anisotropy and mass profile and the mass-follows-light model is \emph{not} a good representation of the mass distribution in J1331's inner regions.
 
@@
 \includegraphics[width=0.9\linewidth]{fig/B4_contour_plot_short.ps}
-\caption{Posterior probability distribution sampled with an MCMC (red dots and histograms) for a JAM model fitted to the stellar $v_\text{rms}$ data, with NFW halo, parametrized by $r_s$ and $v_\text{200}$, a stellar mass distribution generated from the I-band MGE in Table \ref{tab:MGEF814W} and a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and constant velocity anisotropy $\beta_z$.
+\caption{Posterior probability distribution (pdf) sampled with an MCMC (red dots and histograms) for a JAM model fitted to the stellar $v_\text{rms}$ data, with NFW halo, parametrized by $r_s$ and $v_\text{200}$, a stellar mass distribution generated from the I-band MGE in Table \ref{tab:MGEF814W} and a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and constant velocity anisotropy $\beta_z$.
 Shown are also the priors used for J1331's NFW halo, $\mathscr{N}(200~\text{km s}^{-1},40~\text{km s}^{-1})$ (green, see Equation \eqref{eq:prior_v200}) and the concentration vs.
@@
 At larger radii the non-symmetrized data (open blue dots) is compared to an extrapolation of the best fit models using the surface brightness MGE for the outer regions from Figure \ref{fig:MGEouterRegions} (red dashed lines).
-\Wilma{[TO DO: Fehler in Legend.]} \emph{Panel (b):} Shown is the circular velocity curve of the total mass (green), and separately the contribution of the stellar mass (yellow, again generated from the MGE in Table \ref{tab:MGEF814W}) and DM (grey).
+\emph{Panel (b):} Shown is the circular velocity curve of the total mass (green), and separately the contribution of the stellar mass (yellow, again generated from the MGE in Table \ref{tab:MGEF814W}) and DM (grey).
 At the Einstein radius $R_\text{ein}$ (red dotted line) the Einstein mass $M_\text{ein}$ is overplotted with a 10\% error, which was also included in the fit as additional constraint.
@@
 %============================================
-
-\Wilma{[TO DO: introduce pdf]}
 
@@
 %--------------------------------------------
-\subsubsection{JAM with increasing mass-to-light ratio}
+\subsubsection{JAM with increasing mass-to-light ratio} \label{sec:results_JAM_SB_gradient}
 %--------------------------------------------
@@
 The central mass-to-light ratio is in agreement with the mass-to-light ratio $\Upsilon_\text{I,*}^\text{chab} = 2.5 \pm 0.6$, given in Table \ref{tab:previousresults} based on the results of \citet{SWELLSI} assuming a stellar population with a \citet{Chabrier2003} IMF (see also Section \ref{sec:MLdiscussion}).
-When assuming that galaxy bulges are in general older and redder in the center \Wilma{[TO DO: REF]}, i.e., $\Upsilon_\text{I,*}$ is more likely to drop with radius than to rise, the strong increase of $\Upsilon_\text{I,tot}(R')$ might be due to a strong contribution of dark matter in J1331.
+When assuming that galaxy bulges are in general older and redder in the center, i.e., $\Upsilon_\text{I,*}$ is more likely to drop with radius than rise, the strong increase of $\Upsilon_\text{I,tot}(R')$ might be due to a strong contribution of DM in J1331.
 
@@
 %--------------------------------------------
-We therefore proceed by modelling the mass distribution with (a) a stellar component, which we get from the light MGE in Table \ref{tab:MGEF814W} (deprojected to the intrinsic $\nu(R,z)$) times a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and (b) a spherical NFW DM component (see Section \ref{sec:model_JAM}) with halo scale length $r_s$ and circular velocity at the virial radius $v_{200}$ as free parameters.
+We therefore proceed by modelling the mass distribution with (i) a stellar component, which we get from the light MGE in Table \ref{tab:MGEF814W} (deprojected to the intrinsic $\nu(R,z)$) times a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and (ii) a spherical NFW DM component (see Section \ref{sec:model_JAM}) with halo scale length $r_s$ and circular velocity at the virial radius $v_{200}$ as free parameters.
 In the JAM modelling we use a 10-Gaussian MGE fit to the classical NFW profile in Equation \eqref{eq:NFWprofile}.
@@
 The central regions are very well reproduced and we can also nicely predict the rotation curve at larger radii.
-Only at larger radii the $v_\text{rms}$ and $v_\text{rot}$ overestimate the measurements, probably due to a too massive NFW halo.
-\Wilma{[TO DO: There seem to be no minor ticks on x-axis.]}}
+Only at larger radii the $v_\text{rms}$ and $v_\text{rot}$ overestimate the measurements, probably due to a too massive NFW halo.}
 \label{fig:modelB4_vrot}
@@
 There might be something unexpected with the $\sigma$ measurements around $\sim 5''$, but at large radii the the best fit model NFW halo is simply too massive.
-\Wilma{[TO DO: Captions in Results JAMwithNFW muessen noch ueberarbeitet werden.]}
 %--------------------------------------------
@@
 \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_vcirc.ps}
-\caption{Comparison of the circular velocity curve of J1331's inner regions for different models: (a) JAM model with NFW DM halo from Section \ref{sec:results_JAM_NFW_results} and Figure \ref{fig:modelB4_models} (green).
-(b) Lens model from Section \ref{sec:results_lensing_bestfit} and Figure \ref{fig:JAM_modelL} with $\alpha = 1.1$ (red dashed line), $\alpha = 1$ (red solid line) and $\alpha=0.9$ (red dash-dotted line).
-(c) Mass-follows-light model, which uses the F814W surface brightness in Table \ref{tab:MGEF814W} and the mass-to-light ratio in the Einstein radius, $\Upsilon^\text{ein}_\text{I,tot} = 5.56$, to generate a mass distribution, as in Figure \ref{fig:lenscomparelight} (orange line).
-(d) Model from gas kinematics and Einstein mass found by \citet{SWELLSV} (their Figure 2, best model with 68\% confidence region) (blue lines).}
+\caption{Comparison of the circular velocity curve of J1331's inner regions for different models: (i) JAM model with NFW DM halo from Section \ref{sec:results_JAM_NFW_results} and Figure \ref{fig:modelB4_models} (green).
+(ii) Lens model from Section \ref{sec:results_lensing_bestfit} and Figure \ref{fig:JAM_modelL} with $\alpha = 1.1$ (red dashed line), $\alpha = 1$ (red solid line) and $\alpha=0.9$ (red dash-dotted line).
+(iii) Mass-follows-light model, which uses the F814W surface brightness in Table \ref{tab:MGEF814W} and the mass-to-light ratio in the Einstein radius, $\Upsilon^\text{ein}_\text{I,tot} = 5.56$, to generate a mass distribution, as in Figure \ref{fig:lenscomparelight} (orange line).
+(iv) Model from gas kinematics and Einstein mass found by \citet{SWELLSV} (their Figure 2, best model with 68\% confidence region) (blue lines).}
 \label{fig:vcirc_comparison}
@@
 The models in this work used more than just the Einstein mass to constrain the matter distribution at small radii: The lens mass model constrained also the shape of the mass distribution within the lensing image configuration at $R_\text{ein} \sim 1''$.
-The dynamical models used stellar kinematics inside $R' \simeq 3.5''$ \Wilma{[TO DO: Check]}.
+The dynamical models used stellar kinematics inside $R' \simeq 3.5''$.
 We compare the lens mass model's $v_\text{circ}$ (for $\alpha=1.0\pm 0.1$) with the NFW JAM model (Table \ref{tab:modelB4_bestfit}) in Figure \ref{fig:vcirc_comparison} as well.
@@
 %Gas accretion - no!
-Accretion of gas on retrograde orbits and subsequent star formation could lead to a younger and counter-rotating stellar population \Wilma{[TO DO: REF]}.
+Accretion of gas on retrograde orbits and subsequent star formation could lead to a younger and counter-rotating stellar population.
 However, to form enough stars such that the net rotation of the large and massive core is retrograde, a very large amount of gas would have had to be accreted by J1331---which is not very likely.
@@
 %Mergers - yes!
-Another scenario are galaxy mergers.
+Galaxy mergers are another possible scenario.
 Major mergers can form kinematically decoupled cores (KDCs) (e.g., \citealt{2011MNRAS.414.2923K,2015ApJ...802L...3T}), if they include large amounts of gas \citep{2010ApJ...723..818H}.
-During a minor merger, the dense nucleus of a satellite galaxy on a retrograde orbit could survive the dissipationless accretion and spiral to the core due to tidal friction (e.g., \citealt{1984ApJ...287..577K}).
+During a minor merger, the dense nucleus of a satellite galaxy on a retrograde orbit could survive the dissipationless accretion and spiral to the core due to tidal friction (e.g., \citealt{1984ApJ...287..577K,1988ApJ...327L..55F}).
 
@@
 Mergers can reverse this behaviour by inducing the creation of young stellar populations in the remnant's center.
-Major mergers can trigger star formation bursts (e.g., \Wilma{[TO DO: REF, maybe http://arxiv.org/pdf/1409.5126v2.pdf???]}).
-After a minor merger the satellite's stellar population now residing in the remnant's core is in general younger than the progenitor's bulge \Wilma{[TO DO: REF]} .
-The different stellar populations in a merger remnant can be associated with different $\Upsilon_*$ and sometimes even show up as a reverse colour gradient within the bulge in photometry \Wilma{[TO DO: REF]}.
+Major mergers can trigger star formation bursts (e.g., \citealt{2008gady.book.....B}, \S 8.5.5).
+After a minor merger the satellite's stellar population now residing in the remnant's core is in general younger than the progenitor's bulge \citep{1996AJ....112..839C,2010MNRAS.404.1775T} .
+The different stellar populations in a merger remnant can be associated with different $\Upsilon_*$ and in special cases they even show up as a reverse colour gradient within the bulge in photometry \citep{1990ApJ...361..381B, 1997ApJ...481..710C}.
 
 %Color gradient in J1331
-Even though investigation of the photometry of J1331 did not reveal a distinct blue core in J1331, we cannot fully exclude the possibility that J1331 has such a $\Upsilon_*$ gradient (see discussion in Section  \Wilma{[TO DO: Where???]}).
+Even though investigation of the photometry of J1331 did not reveal a distinct blue core in J1331, we cannot fully exclude the possibility that J1331 has such a $\Upsilon_*$ gradient (see discussion in Sections \ref{sec:results_JAM_SB_MfL} and \ref{sec:results_JAM_SB_gradient}).
 In this case the restrictive assumption of a constant $\Upsilon_*$ in our JAM modelling could have lead to wrong conclusions about the DM distribution.
 
-%Merger and kinematic twist
-Other ways how mergers can can modify the structure of galaxies are warps in the outer parts or kinematic twists in the center of the remnant galaxy \citep{2013pss5.book..923S}, which show up as misalignments of kinematic and photometric major axis.
-
-%Kinematic twist in J1331
-From kinematics along the photometric major axis only it cannot be determined if such a misalignement is present in J1331.
+Another way how galaxy encounters can can modify the structure of galaxies is the excitation of warps \citep{1991wdir.book.....C,2013pss5.book..923S}.
+Warps lead to a twist in the projected kinematic major axis with radius, which is then also misaligned with the photometric major axis (\citealt{1998gaas.book.....B}, \S 8.2.4).
+From kinematics along the photometric major axis only it cannot be determined if such a twist or misalignment is present in J1331.
 But if it were, our modelling assumption of axisymmetry would not be satisfied anymore.
@@
 %--------------------------------------------
-%Intro:
-J1331 is a massive spiral galaxy which acts as strong gravitational lens for a background source.
-J1331 appears also to be a merger remnant due to it's large counter-rotating core.
-The goal of this work was to recover J1331's matter distribution by means of two methods, gravitational lensing and dynamical modelling.
-We focus on the bulge region of J1331, to complement previous studies of J1331 by \citet{SWELLSIII,SWELLSV}.
-The independent mass constraint which we derive from lensing and dynamics agree very well with each other within $R_\text{eff}$.
+The goal of this work was to constrain the matter distribution of the massive spiral galaxy J1331.
+J1331 is of special interest because it firstly has a large counter-rotating core and might therefore be a merger remnant and it secondly acts as strong gravitational lens for a background source.
+The latter allowed us to constrain the galaxy's mass from gravitational lensing.
+As second independent approach we used dynamical Jeans modelling to recover and disentangle the stellar and DM distribution.
+We focussed on the bulge region of J1331 to complement previous studies of J1331 by \citet{SWELLSIII} and \citet{SWELLSV}.
+The independent mass constraints which we derived from lensing and dynamics agree very well with each other within $R_\text{eff}$.
 
@@
 
-To get a handle of J1331's light distribution we used a MGE fit to J1331's surface brightness in the F814W filter in HST imaging by \citet{SWELLSI}.
+To get a handle on J1331's light distribution we used a MGE fit to J1331's surface brightness in the F814W filter in HST imaging by \citet{SWELLSI}.
 Based on this we found J1331's effective radius to be $R_\text{eff} \simeq 2.6'' \hat{=} 5.2~\text{kpc}$ and its total I-band luminosity to be $L_\text{I,tot} \simeq 5.6 \cdot 10^{10} L_\odot$.
@@
 We used axisymmetric JAM modelling to calculate the second velocity moment of a tracer and mass distribution given in terms of MGEs.
-The JAM model of the lens mass model gave a independent prediction which was consistent with observed stellar kinematics from major axis long slit spectrography by \citet{SWELLSV} within $R_\text{eff}$.
+The JAM model of the lens mass model gave an independent prediction which was consistent with observed stellar kinematics from major axis long slit spectroscopy by \citet{SWELLSV} within $R_\text{eff}$.
 We also fitted mass models with and without NFW halo to the stellar kinematics within $R'=3.5~\text{kpc}$.
 From this we deduced that a mass-follows-light model with constant total mass-to-light ratio is not a good model for J1331---not even in the inner regions.
-To describe the observed stellar kinematics we either require a strong contribution of a dark matter halo already in the bulge, or a strongly varying stellar mass-to-light ratio.
-We also showed that it is possible to construct a model which includes the counter-rotating core and is consistent with the rotation curve at large radii.
+To describe the observed stellar kinematics we either require a strong contribution of a DM halo already in the bulge, or a strongly varying stellar mass-to-light ratio.
+We also showed that it is possible to construct a model which includes the counter-rotating core and fits the rotation curve at large radii.
 
@@
 \bibliography{literaturelist}
+%\begin{thebibliography}{}
+%\bibitem[Dutton et al.(2011)]{2011MNRAS.416..322D} Dutton, A.~A., Conroy, C., van den Bosch, F.~C., et al.\ 2011, \mnras, 416, 322 
+%\bibitem[Franx \& Illingworth(1988)]{1988ApJ...327L..55F} Franx, M., \& Illingworth, G.~D.\ 1988, \apjl, 327, L55 
+%\bibitem[Moore(1994)]{1994Natur.370..629M} Moore, B.\ 1994, \nat, 370, 629 
+%\bibitem[Navarro et al.(1996)]{1996ApJ...462..563N} Navarro, J.~F., Frenk, C.~S., \& White, S.~D.~M.\ 1996, \apj, 462, 563 
+%\bibitem[de Blok et al.(2001)]{2001ApJ...552L..23D} de Blok, W.~J.~G., McGaugh, S.~S., Bosma, A., \& Rubin, V.~C.\ 2001, \apjl, 552, L23
+
+%\end{thebibliography}
 %--------------------------------------------

### 2016-01-28 LensingPaper_draft_v3.05.tex
Included my typo corrections until 3.3.1.

@@
 \begin{abstract}
-We investigate the matter distribution of a spiral galaxy with counter-rotating stellar core, SDSS J1331+3628 (J1331), independently with gravitational lensing and dynamical modelling.
+We investigate the matter distribution of a spiral galaxy with counter-rotating stellar core, SDSS J1331+3628 (J1331), independently with gravitational lensing and stellar dynamical modelling.
 By fitting a gravitational potential model to a quadruplet of lensing images around J1331's bulge, we tightly constrain the mass inside the Einstein radius $R_\text{ein}=(0.91\pm0.02)''(\simeq1.83\pm0.04~\text{kpc})$ to within 4\%: $M_\text{ein} = (7.8\pm0.3) \cdot 10^{10} M_\odot$.
@@
 We find that J1331's center requires a steep total mass-to-light ratio gradient.
-A dynamical model including a NFW halo (with virial velocity $v_{200} \simeq 240 \pm 40~\text{km s}^{-1}$ and concentration of $c_{200} \simeq 8 \pm 2$) and moderate tangential velocity anisotropy ($\beta_z \simeq -0.4 \pm 0.1$) can reproduce the signatures of J1331's counter-rotating core and predict the stellar and gas rotation curve at larger radii.
+A dynamical model including a NFW halo (with virial velocity $v_{200} \simeq 240 \pm 40~\text{km s}^{-1}$ and concentration $c_{200} \simeq 8 \pm 2$) and moderate tangential velocity anisotropy ($\beta_z \simeq -0.4 \pm 0.1$) can reproduce the signatures of J1331's counter-rotating core and predict the stellar and gas rotation curve at larger radii.
 However, our models do not agree with the observed velocity dispersion at large radii.
-We speculate that the reason could be a non-trivial re-distribution of matter due to a possible merger event in J1331's recent past.
+We speculate that the reason could be a non-trivial change in structure and kinematics due to a possible merger event in J1331's recent past.
 \end{abstract}
@@
 Gravitational lensing and dynamical modelling provide independent constraints on the mass distribution of galaxies.
-Combining them allows for valuable cross-checking opportunities to disentangle the stellar and dark matter (DM) content of galaxies.
+Combining them allows for valuable cross-checking opportunities to disentangle the galactic stellar and dark matter (DM) content.
 
@@
 The mass profile at larger galactocentric radii can be probed by gas rotation curves that directly measure the galaxy's circular velocity profile (e.g., \citealt{1980ApJ...238..471R}).
-However, due to its dissipative nature, gas motions are very sensitive to disturbances by e.g., spiral arms and bars (e.g., \citealt{2004dad..book.....S}).
+However, due to its dissipative nature gas motions are very sensitive to disturbances by, e.g., spiral arms and bars (e.g., \citealt{2004dad..book.....S}).
 
 Because stars are dissipationless dynamical tracers and present almost everywhere in the galaxy, stellar dynamical modelling can complement mass constraints from lensing at small and gas motions at large radii.
-As stellar motions are complex---a bulk rotation around one principal axis combined with random motions in all coordinate directions---, full dynamical modelling of rotation, dispersion and velocity anisotropies is needed to deduce the matter distribution.
-
-The Sloan WFC Edge-on Late-type Lens Survey (SWELLS, WFC = Wide field camera) \citep{SWELLSI,SWELLSII,SWELLSIII,SWELLSIV,SWELLSV,SWELLSVI} is dedicated to find and investigate spiral galaxies, which are (i) strong gravitational lenses and (ii) seen almost edge-on, such that rotation curves can be easily measured.
-By combining lensing and dynamical modelling degeneracies inherent in both methods can be broken.
+As stellar motions are complex---a bulk rotation around one principal axis combined with random motions in all coordinate directions---\citep{2008gady.book.....B}, full dynamical modelling of rotation, dispersion and velocity anisotropies is needed to deduce the matter distribution.
+
+The Sloan WFC Edge-on Late-type Lens Survey (SWELLS, WFC = Wide field camera) \citep{SWELLSI,SWELLSII,SWELLSIII,SWELLSIV,SWELLSV,SWELLSVI} is dedicated to find and investigate spiral galaxies, which are (i) strong gravitational lenses and (ii) observed almost edge-on, such that rotation curves can be easily measured.
+By combining lensing and dynamical modelling, degeneracies inherent in both methods can be broken.
 
@@
 
-\citet{SWELLSI} confirmed that J1331 was a strong gravitational lens, measured its apparent brightness and estimated the stellar masses of disk and bulge.
+\citet{SWELLSI} confirmed that J1331 is a strong gravitational lens, measured its apparent brightness and estimated the stellar masses of disk and bulge.
 The lensing properties of J1331 were first analysed by \citet{SWELLSIII}.
@@
 
-The goal of this work is to complement the previous work on J1331 by an in-depth analysis of the matter distribution in J1331's inner regions.
+The goal of this work is to complement the previous studies of J1331 by an in-depth analysis of the matter distribution in J1331's inner regions.
 We use stellar dynamical modelling in addition to lensing constraints, similar to a study of the Einstein Cross by \citet{GlennEC}.
@@
 This paper is organized as follows: Section \ref{sec:data} summarizes the data, Section \ref{sec:Modelling} gives an overview of the modelling techniques used in this work, and Section \ref{sec:Results} presents our results on the surface photometry of J1331 using Multi-Gaussian expansions (Section \ref{sec:MGE_results}), constraints from lensing (Section \ref{sec:results_lensing}) and Jeans modelling based on the surface brightness only (Section \ref{sec:results_JAM_SB}) and including a NFW DM halo (Section \ref{sec:results_JAM_NFW}).
-Finally Section \ref{sec:Discussion} uses the result to discuss J1331's stellar mass-to-light ratio, possible merger history and starting points for future work.
+Finally, Section \ref{sec:Discussion} uses these results to discuss J1331's stellar mass-to-light ratio, central kinematics, possible merger history and starting points for future work.
 %--------------------------------------------
@@
 \end{subfigure}
-\caption{Hubble Space telescope (HST) images and stellar kinematics of the galaxy SDSS J1331+3628 (J1331), which has a large counter-rotating core and whose bulge acts as a strong lens for a bluish background source.
+\caption{Hubble Space Telescope (HST) images and stellar kinematics of the galaxy SDSS J1331+3628 (J1331), which has a large counter-rotating core and whose bulge acts as a strong lens for a bluish background source.
 \emph{Panel (a) and (b):} HST/WFPC2/WFC3 images of J1331 by \citet{SWELLSI} in two filters, F450W in panel (a) and F814W in panel (b).
-The black solid line in panel (b) shows the orientation of the major-axis.
+The black solid line in panel (b) shows the orientation of the major axis.
 Its length is $10''$ and it marks approximately the region within which we carry out the dynamical modelling.
@@
 The (smoothed) residuals within the white square in panel (a) are shown in panel (c).
-The four bright blobs (A, B, C and D) which are visible in the residuals are arranged in a typical strong lensing configuration around the center of the galaxy (G).
+The four bright blobs (A, B, C and D), which are visible in the residuals, are arranged in a typical strong lensing configuration around the center of the galaxy (G).
 (The configuration of the two additional blobs which lie approximately on a line with A, B and G does not suggest that these blobs are a lensing doublet.
-They might rather be star forming regions of a background galaxy.) \emph{Panel (d):} Stellar Kinematics along the galaxy's major axis as measured by \citet{SWELLSV}.
+They might rather be star-forming regions of a background galaxy.) \emph{Panel (d):} Stellar kinematics along the galaxy's major axis as measured by \citet{SWELLSV}.
 Shown are line-of-sight rotation velocity $v_\text{rot}$ (top), line-of-sight velocity dispersion $\sigma$ (middle) and the root mean-square (rms) velocity $v_\text{rms} = \sqrt{v_\text{rot}^2 + \sigma^2}$ (bottom).
-The dashed line indicates the galaxy's effective half-light radius (in the F814W filter), $R_\text{eff} = 2.6'' = 5.2~\text{kpc}$.
+The dashed line indicates the galaxy's effective half-light radius (in the F814W filter), $R_\text{eff} = 2.6'' \hat{=} 5.2~\text{kpc}$.
 The $v_\text{rot}$ curve reveals that J1331 has a counter-rotating core within $R_\text{eff}$.}
@@
 %--------------------------------------------
-\subsection{Stellar kinematics}
+\subsection{Stellar kinematics} \label{sec:data_kinematics}
 %--------------------------------------------
@@
 1D spectra for spatial bins of different widths along the major axis were extracted.
-They measured line-of-sight stellar rotation velocities ($v_\text{rot}$) and stellar velocity dispersions ($\sigma$) from the spectral region containing the absorption lines Mgb (5177 \AA) and FeII (5270, 5335 and 5406 \AA) (analogous to \citealt{SWELLSII}).
+Line-of-sight stellar rotation velocities ($v_\text{rot}$) and stellar velocity dispersions ($\sigma$) were determined from the spectral region containing the absorption lines Mgb (5177 \AA) and FeII (5270, 5335 and 5406 \AA) (analogous to \citealt{SWELLSII}).
 Gas kinematics were extracted from Gaussian line profile fits to H$\alpha$ (6563 \AA) and [NII] (6583 and 6548 \AA) emission lines as tracers for ionized gas.
@@
 This could indicate the boundary between the pressure supported bulge and the rotationally supported disk, which appears around this radius in the F450W filter in Figure \ref{fig:F450W}.
-However, in the brighter F814W filter in Figure \ref{fig:F814W} the large reddish bulge extends out to $\sim5''$.
+However, in the brighter F814W filter in Figure \ref{fig:F814W} the smooth reddish bulge extends out to $\sim5''$.
 
 Inside of $\sim 4''$ the data appears to be symmetric; outside of it the data suggests that the assumption of axisymmetry seems not to be valid anymore.
-We add $-2.3~\text{km s}^{-1}$ to the $v_\text{rot}$ to ensure $v_\text{rot}(R'=0) \sim 0$ as a possible correction term for a misjudgement of the systemic velocity.
-We also symmetrize the data within $4''$ and asign a minimum error of $\delta v_\text{rms} > 5~\text{km s}^{-1}$ to the $v_\text{rms}$ data.
-In our dynamical Jeans modelling approach, which is based on the assumption of axisymmetry, only stellar kinematics with either $R'  \lesssim 2.5''$ or $R' \lesssim 4''$ are used.
-Another reason to restrict to modelling to the bulge region is that our surface brightness model (Table \ref{tab:MGEF814W} and Figure \ref{fig:MGEinnerRegions}) is only a good representation of J1331's F814W light distribution inside $\sim 5''$.
+We subtract $2.3~\text{km s}^{-1}$ from $v_\text{rot}$ to ensure $v_\text{rot}(R'=0) \sim 0$ as a possible correction term for a misjudgement of the systemic velocity.
+We also symmetrize the data within $4''$ and asign a minimum error of $\delta v_\text{rms} \geq 5~\text{km s}^{-1}$ to the $v_\text{rms}$ data.
+In our dynamical Jeans modelling approach, which is based on the assumption of axisymmetry, only stellar kinematics with either $R'  \lesssim 3.5''$ or $R' \lesssim 4''$ are used.
+Another reason to restrict the modelling to the bulge region is that our surface brightness model (Table \ref{tab:MGEF814W} and Figure \ref{fig:MGEinnerRegions}) is only a good representation of J1331's F814W light distribution inside $\sim 5''$.
 %--------------------------------------------
@@
 The version from June 2012 was used in this work.} by \citet{Cap02}.
-We assume all Gaussians to have the same center and position angle $\phi$, i.e., the orientation of the Gaussians' major axis measured counter-clockwise from the $y'$-axis of the coordinate system with polar coordinates $(R',\theta')$.
-Then the surface brightness can be written as
+We assume all Gaussians to have the same center and position angle $\phi$, i.e., the orientation of the Gaussians' major axis measured from North through East in the polar coordinate system $(R',\theta')$ on the plane of the sky.
+Then a surface brightness model can be expressed as
 \begin{eqnarray}
@@
 
-\subsubsection{Point spread function (PSF)}
+\subsubsection{Convolution with the point spread function (PSF)}
 
@@
 \end{equation}
-where $\sum_j G_j = 1$ and $\delta_j$ are in this case the dispersions of the circular PSF Gaussians.
+where $\sum_j G_j = 1$ and $\delta_j$ are the dispersions of the circular PSF Gaussians.
 
@@
 $I(R',\theta')$ describes the intrinsic, to 2D projected light distribution or surface density of the galaxy.
-Under the assumption that the galaxy is oblate and axisymmetric, and given the inclination angle $i$ of the galaxy with respect to the observer, MGEs allow an analytic deprojection of the 2D MGE to get a 3D light distribution or density $\nu(R,z)$ for the galaxy,
-\begin{equation}
-\nu(R,z) = \sum_i \nu_{0,i} \exp \left[-\frac{1}{2\sigma_i}\left(R^2 + \frac{z^2}{q_i^2} \right) \right]. \label{eq:deprojMGE}
-\end{equation}
-The flattening of each axisymmetric 3D Gaussian $q_i$ and its central density $\nu_{0,i}$ follow from the observed 2D axis ratio $q'_i$ and surface density $I_{0,i}$ as
+Under the assumption that the galaxy is oblate and axisymmetric, and given the inclination angle $i$ of the galaxy with respect to the observer, MGEs allow an analytic deprojection of the 2-dimensional MGE to get a 3-dimensional axisymmetric light distribution or density $\nu(R,z)$ for the galaxy,
+\begin{equation}
+\nu(R,z) = \sum_i \nu_{0,i} \exp \left[-\frac{1}{2\sigma_i}\left(R^2 + \frac{z^2}{q_i^2} \right) \right], \label{eq:deprojMGE}
+\end{equation}
+where $R$ is the distance from the galaxy's short axis and $z$ the height above the galactic plane.
+The flattening $q_i$ of each axisymmetric 3D Gaussian and its central density $\nu_{0,i}$ follow from the observed 2D axis ratio $q'_i$ and surface density $I_{0,i}$ as
 \begin{eqnarray*}
@@
 %--------------------------------------------
-\subsubsection{Lensing formalism}
-%--------------------------------------------
-
-%--------------------------------------------
-A gravitational lens is a mass distribution, whose gravitational potential $\Phi$ acts as a lens for light coming from a source positioned somewhere on a plane behind the lens.
+\subsubsection{Strong lensing formalism}
+%--------------------------------------------
+
+%--------------------------------------------
+A gravitational lens is a mass distribution whose gravitational potential $\Phi$ acts as a lens for light coming from a source positioned somewhere on a plane behind the lens.
+We summarize the basic formalism (see also \citealt{1992grle.book.....S,1996astro.ph..6001N,2006glsw.conf....1S,2006glsw.conf...91K,2010ARA&A..48...87T}).
 The angular diameter distance from the observer to the lens is $D_d$, to the source plane $D_s$, and the distance between the lens and source plane is $D_{ds}$.
-The deflection potential of the lens is its potential, projected along the line of sight $z$ and rescaled to
-\begin{equation}
-\psi(\vect{\theta}) := \frac{D_{ds}}{D_d D_s} \frac{2}{c^2} \int \Phi(\vect{r}=D_d \vect{\theta},z) {\ \mathrm d} z, \label{eq:psidef}
-\end{equation}
-where $\vect{\theta}$ is a 2-dimensional vector on the plane of the sky.
-The light from the source at $\vect{\beta} = (\xi,\eta)$\footnote{$\xi$ and $\eta$ are cartesian coordinates on the plane of the sky.} is deflected according to the lens equation
+The deflection potential of the lens is its potential projected along the line of sight $z'$ and rescaled to
+\begin{equation}
+\psi(\vect{\theta}) := \frac{D_{ds}}{D_d D_s} \frac{2}{c^2} \int \Phi(\vect{r}=D_d \vect{\theta},z') {\ \mathrm d} z', \label{eq:psidef}
+\end{equation}
+where $\vect{\theta}\equiv(x',y')$ is a 2-dimensional vector on the plane of the sky. The light from the source at $\vect{\beta} \equiv (x_s',y_s')$ is deflected according to the lens equation
 \begin{equation}
@@
 \end{equation}
-into an image $\vect{\theta}_i = (x_i,y_i)$.
-The gradient of the deflection potential $\vect{\nabla}_\theta \psi(\vect{\theta})$ is equal to the angle by which the light is deflected multiplied by $D_{ds}/D_{s}$.
-
-The total time delay of an deflected light path through $\vect{\theta}$ with respect to the unperturbed light path is given by 
-\begin{equation}
-\Delta t(\vect{\theta}) = \frac{(1+z_d)}{c} \frac{D_d D_s}{D_{ds}} \left[ \frac 12 (\vect{\theta} - \vect{\beta})^2 - \psi(\vect{\theta})\right] \label{eq:timedelay}
-\end{equation}
-\citep{BartGravLens}. According to Fermat's principle the image positions will be observed at the extrema of $\Delta t(\vect{\theta})$.
+into an image $\vect{\theta}_i = (x_i',y_i')$.
+The gradient of the deflection potential, $\vect{\nabla}_\theta \psi(\vect{\theta})$, is equal to the angle by which the light is deflected multiplied by $D_{ds}/D_{s}$.
+
+The total time delay of a deflected light path through $\vect{\theta}$ with respect to the unperturbed light path is given by 
+\begin{equation}
+\Delta t(\vect{\theta}) = \frac{(1+z_d)}{c} \frac{D_d D_s}{D_{ds}} \left[ \frac 12 (\vect{\theta} - \vect{\beta})^2 - \psi(\vect{\theta})\right]. \label{eq:timedelay}
+\end{equation}
+ According to Fermat's principle the image positions will be observed at the extrema of $\Delta t(\vect{\theta})$.
 
@@
 \end{equation}
-describes how the source position changes with image position. It also describes the distortion of the image shape for an extended source and its magnification due to lensing according to
+describes how the source position changes with image position. It also describes the distortion of the image shape for an extended source and its magnification $\mu$ due to lensing according to
 $$\mu \equiv \frac{\text{image area}}{\text{source area}} = \det \mathscr{M}.$$
@@
 \begin{equation*}
-M_\text{ein} \equiv M_\text{proj}(<R_\text{ein}) \overset{!}{=} \pi \Sigma_\text{crit} R_\text{ein}^2,
+M_\text{ein} \equiv M(<R_\text{ein}) \overset{!}{=} \pi \Sigma_\text{crit} R_\text{ein}^2,
 \end{equation*}
-where $\Sigma_\text{crit} \equiv \frac{c^2}{4\pi G} \frac{D_s}{D_d D_{ds}}$ is the critical density and $M_\text{proj}(<R_\text{ein})$ is the mass projected along the line-of-sight within $R_\text{ein}$.
+where $\Sigma_\text{crit} \equiv \frac{c^2}{4\pi G} \frac{D_s}{D_d D_{ds}}$ is the critical density and $M(<R_\text{ein})$ is the mass projected along the line-of-sight within $R'=R_\text{ein}$.
 $M_\text{ein}$ is similar to the projected mass within the critical curve $M_\text{crit}$.
@@
 \end{equation}
-for the lensing potential, consisting of an angular part $F(\theta')$ and a power-law radial part, with $(R',\theta')$ being polar coordinates on the plane of the sky.
-The case $\alpha = 1$ corresponds to a flat rotation curve.
+for the lensing potential, consisting of an angular part $F(\theta')$ and a radial power-law part, with $(R',\theta')$ being again polar coordinates on the plane of the sky.
+$\alpha$ denotes the rotation curve slope of the lens and the case $\alpha = 1$ corresponds to a flat rotation curve.
+The surface density of this model is
+\begin{equation*}
+\Sigma(R',\theta')= \frac{ \Sigma_\text{crit}}{2} \left(\alpha^2 F(\theta') + \frac{\partial^2}{\partial \theta^{'2}}F(\theta')\right) R^{'\alpha-2}.
+\end{equation*}
 We expand $F(\theta')$ into a Fourier series,
@@
 \begin{equation}
-\begin{pmatrix} \xi \\ \eta \end{pmatrix} = \begin{pmatrix} R'_i \cos \theta'_i - R_i^{'\alpha-1} \left(\alpha \cos \theta'_i F(\theta'_i) - \sin \theta'_i F'(\theta'_i) \right) \\ R'_i \sin \theta'_i - R_i^{'\alpha-1} \left(\alpha \sin \theta'_i F(\theta'_i + \cos \theta'_i F'(\theta'_i) \right)\end{pmatrix}\label{eq:Fourierlenseq}
+\begin{pmatrix} x_s' \\ y_s' \end{pmatrix} = \begin{pmatrix} R'_i \cos \theta'_i - R_i^{'\alpha-1} \left(\alpha \cos \theta'_i F(\theta'_i) - \sin \theta'_i F'(\theta'_i) \right) \\ R'_i \sin \theta'_i - R_i^{'\alpha-1} \left(\alpha \sin \theta'_i F(\theta'_i + \cos \theta'_i F'(\theta'_i) \right)\end{pmatrix}\label{eq:Fourierlenseq}
 \end{equation}
 \citep{EvansWitt}, where $F'(\theta') \equiv \partial F(\theta') / \partial \theta'$.
-When we fix the slope $\alpha$, then the lens equation is a purely linear problem and can be solved numerically for the source position $(\xi,\eta)$ and the Fourier parameters $(a_k,b_k)$ given one observed image at position $(x_i=R'_i \cos \theta'_i,y_i=R'_i \sin \theta'_i)$.
+When we fix the slope $\alpha$, then the lens equation is a purely linear problem and can be solved numerically for the source position $(x_s',y_s')$ and the Fourier parameters $(a_k,b_k)$ given one observed image at position $(x'_i=R'_i \cos \theta'_i,y'_i=R'_i \sin \theta'_i)$.
 
@@
 %--------------------------------------------
-The free parameters of the lens model are: the source position $(\xi,\eta)$, the radial slope $\alpha$ and Fourier parameters $(a_k,b_k)$ of the lens mass distribution in Equations \eqref{eq:scalefreemodel} and \eqref{eq:Fourieransatz}.
+The free parameters of the lens model are: the source position $(x_s',y_s')$, the radial slope $\alpha$ and Fourier parameters $(a_k,b_k)$ of the lens mass distribution in Equations \eqref{eq:scalefreemodel}-\eqref{eq:Fourieransatz}.
 We want to minimize the distance between the observed image positions, $\vect{\theta}_{oi}$, and those predicted by the lensing model, $\vect{\theta}_{pi}$.
@@
 \chi^2_\text{lens} &=& \sum_{i} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right) \left( \vect{\theta}_{pi} - \vect{\theta}_{oi} \right)\right|^2\nonumber\\
-&\simeq& \sum_{i} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right)  \left.\mathscr{M}\right|_{\vect{\theta}=\vect{\theta}_{oi}} \left( \begin{matrix} \xi - \tilde{\xi}_i \\ \eta - \tilde{\eta}_i \end{matrix} \right) \right|^2,\label{eq:chi2lens}
+&\simeq& \sum_{i} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right)  \left.\mathscr{M}\right|_{\vect{\theta}=\vect{\theta}_{oi}} \left( \begin{matrix} x_s' - \tilde{x}'_{si} \\ y_s' - \tilde{y}'_{si} \end{matrix} \right) \right|^2,\label{eq:chi2lens}
 \end{eqnarray}
 where $(\Delta_x,\Delta_y)$ are the measurement errors of the image positions $\vect{\theta}_{oi}$.
-$\left.\mathscr{M}\right|_{\vect{\theta}=\vect{\theta}_{oi}}$ is the magnification tensor and $(\tilde{\xi}_i,\tilde{\eta}_i)$ the source position according to the lens equation, both evaluated at the position of the $i$-th lensing image, $\vect{\theta}_{oi}$.
+$\left.\mathscr{M}\right|_{\vect{\theta}=\vect{\theta}_{oi}}$ is the magnification tensor and $(\tilde{x}'_{si},\tilde{y}'_{si})$ the source position according to the lens equation, both evaluated at the position of the $i$-th lensing image, $\vect{\theta}_{oi}$.
 Following \citet{GlennEC} we add a term
@@
 \end{equation}
-which forces the shape of the mass distribution to be close to an ellipse. The total $\chi^2$ to minimize is therefore
+(with $\lambda$ being some weight factor) which forces the shape of the mass distribution to be close to an ellipse. The total $\chi^2$ to minimize is therefore
 \begin{equation}
@@
 
-To be able to constrain the slope $\alpha$, we would need flux ratios for the images as in \citet{GlennEC}.
-But the extended quality of the images, possible dust obscuration and surface brightness fluctuations due to microlensing events, as well as the uncertainty in surface brightness subtraction, make flux determination too unreliable and we do not include them in the fitting.
+To be able to constrain the slope $\alpha$ we would need flux ratios for the images as in \citet{GlennEC}.
+But the extent of the images, possible dust obscuration and surface brightness fluctuations due to microlensing events, as well as the uncertainty in surface brightness subtraction, make flux determination too unreliable and we do not include them in the fitting.
 %--------------------------------------------
@@
 To be able to solve the Jeans equations, additional assumptions about the velocity ellipsoid tensor $\langle v_i v_j\rangle$ have to be made.
-We follow \citet{Cap08} and assume firstly, that the galaxy's velocity ellipsoid is aligned with the cylindrical coordinate system, i.e., $\langle v_R v_z\rangle = \langle v_z v_\phi \rangle = \langle v_\phi v_R \rangle = 0$.
+We follow \citet{Cap08} and assume firstly that the galaxy's velocity ellipsoid is aligned with the cylindrical coordinate system, i.e., $\langle v_R v_z\rangle = \langle v_z v_\phi \rangle = \langle v_\phi v_R \rangle = 0$.
 Secondly, we assume a constant ratio between the radial and vertical second velocity moments,
 \begin{equation}
-\beta_z \equiv 1 - \langle v_z^2 \rangle / \langle v_R^2\rangle. \label{eq:bz}
-\end{equation}
-This reduces the Jeans equations to two equations for $\langle v_z^2 \rangle$ and $\langle v_\phi^2 \rangle$, that can be solved by means of one integration,
+\beta_z \equiv 1 - \langle v_z^2 \rangle / \langle v_R^2\rangle, \label{eq:bz}
+\end{equation}
+where $\beta_z$ is the velocity anisotropy parameter.
+This reduces the Jeans equations to two equations for $\langle v_z^2 \rangle$ and $\langle v_\phi^2 \rangle$ which can be solved by means of one integration,
 \begin{eqnarray}
@@
 \end{eqnarray}
-where $n(\vect{x}) \equiv \int f(\vect{x},\vect{v}) \Diff3 v$ is the number density of (stellar) tracers and $\Phi(\vect{x})$ the galaxy's gravitational potential, generated by the mass density $\rho(\vect{x})$.
+where $n(\vect{x}) \equiv \int f(\vect{x},\vect{v}) \Diff3 v$ is the number density of (stellar) tracers and $\Phi(\vect{x})$ the galaxy's gravitational potential generated by the mass density $\rho(\vect{x})$.
 
@@
 The mass density $\rho(R,z)$ can consist of several sets of MGEs, describing stellar and DM components.
-$\Phi(R,z)$ is generated from the mass density MGE by integrating the Poisson equation \citep{1994A&A...285..723E}.
-Equations \eqref{eq:Jeans1} and \eqref{eq:Jeans2} together with \eqref{eq:bz} provide the velocity dispersion tensor $\langle v_i v_j \rangle = \langle v_i^2 \rangle$ (with $i,j \in \{ R,\phi, z\}$).
+The MGE for $\Phi(R,z)$ is generated from the mass density MGE by integrating the Poisson equation \citep{1994A&A...285..723E}.
+Equations \eqref{eq:Jeans1} and \eqref{eq:Jeans2} together with \eqref{eq:bz} provide the velocity dispersion tensor $\langle v_i v_j \rangle(R,z) = \langle v_i^2 \rangle(R,z)$ (with $i,j \in \{ R,\phi, z\}$ and $\langle v_i v_j \rangle=0$ if $i\neq j$).
 $\langle v_i^2 \rangle$ is then rotated by the inclination angle $i$ to the coordinate system of the observer; $(x',y')$ is the plane of the sky and $z'$ the line-of-sight, where $x'$ is alinged with the galaxy's major axis.
@@
 &&\left(I \langle v_\text{los}^2\rangle\right)(x',y')\nonumber\\
-&&= 4 \pi^{3/2} G \int_0^1 \sum_{k=1}^N \sum_{j=1}^M \nu_{0,k} \ q_j \ \rho_{0,j} \ u^2\nonumber\\
-&& \times \frac{\sigma_k^2 \ q^{2}_k \left( \cos^2 i + \frac{\sin^2 i}{1-\beta_{z,k}}\right) + \mathscr{D} \  {x'}^{2} \sin^2 i}{(1-\mathscr{C}u^2) \sqrt{(\mathscr{A} + \mathscr{B} \cos^2 i) \left[1-(1-q^{2}_j) u^2 \right]}}\nonumber\\
+&&= 4 \pi^{3/2} G \int_0^1 \sum_{i=1}^N \sum_{k=1}^M \nu_{0,i} \ q_k \ \rho_{0,k} \ u^2\nonumber\\
+&& \times \frac{\sigma_i^2 \ q^{2}_i \left( \cos^2 i + \frac{\sin^2 i}{1-\beta_{z,i}}\right) + \mathscr{D} \  {x'}^{2} \sin^2 i}{(1-\mathscr{C}u^2) \sqrt{(\mathscr{A} + \mathscr{B} \cos^2 i) \left[1-(1-q^{2}_k) u^2 \right]}}\nonumber\\
 && \times \exp\left\{- \mathscr{A} \left[{x'}^{2} + \frac{(\mathscr{A}+\mathscr{B}) \ {y'}^{2}}{\mathscr{A}+\mathscr{B}\cos^2 i}\right] \right\} \diff u, \label{eq:explicitLOSvelCap}
 \end{eqnarray}
-with $N$ Gaussians describing the tracer distribution and $M$ Gaussians describing the mass distribution, $\rho_{0,j}$ being the $j$-th mass density Gaussian evaluated at $(R=0,z=0)$ and
+with $N$ Gaussians describing the tracer distribution $\nu(R,z)$ and $M$ Gaussians describing the mass distribution $\rho(R,z)$, $\rho_{0,k}$ being the $k$-th mass density Gaussian evaluated at $(R=0,z=0)$ and
 \begin{eqnarray*}
-\mathscr{A} &=& \frac 12 \left(\frac{u^2}{\sigma_j^2} + \frac{1}{\sigma_k^2} \right)\nonumber\\
-\mathscr{B} &=& \frac 12 \left\{\frac{1-q^{2}_k}{\sigma_k^2 q^{2}_k} + \frac{(1-q^{2}_j)u^4}{\sigma_j^2 \left[1-(1-{q}_j^{2})u^2 \right]} \right\}\nonumber\\
-\mathscr{C} &=& 1- q^{2}_j - \frac{\sigma_k^2 q^{2}_k}{\sigma^2_j}\nonumber\\
-\mathscr{D} &=& 1 - \frac{q^{2}_k}{1-\beta_{z,k}} - \left[ \left(1-\frac{1}{1-\beta_{k,z}}\right)\mathscr{C} + \frac{1-q^{2}_j}{1-\beta_{z,k}}\right] u^2.\nonumber
+\mathscr{A} &=& \frac 12 \left(\frac{u^2}{\sigma_k^2} + \frac{1}{\sigma_i^2} \right)\nonumber\\
+\mathscr{B} &=& \frac 12 \left\{\frac{1-q^{2}_i}{\sigma_i^2 q^{2}_i} + \frac{(1-q^{2}_k)u^4}{\sigma_k^2 \left[1-(1-{q}_k^{2})u^2 \right]} \right\}\nonumber\\
+\mathscr{C} &=& 1- q^{2}_k - \frac{\sigma_i^2 q^{2}_i}{\sigma^2_k}\nonumber\\
+\mathscr{D} &=& 1 - \frac{q^{2}_i}{1-\beta_{z,i}} - \left[ \left(1-\frac{1}{1-\beta_{i,z}}\right)\mathscr{C} + \frac{1-q^{2}_k}{1-\beta_{z,i}}\right] u^2.\nonumber
 \end{eqnarray*}
@@
 %--------------------------------------------
-As data we use stellar line-of-sight rotation velocities $v_\text{rot} \equiv \langle v_\text{los} \rangle$ and velocity dispersions $\sigma$ as described in Section \ref{sec:data}.
+As data we use stellar line-of-sight rotation velocities $v_\text{rot} \equiv \langle v_\text{los} \rangle$ and velocity dispersions $\sigma$ as described in Section \ref{sec:data_kinematics}.
 The JAM models give us a prediction for the second line-of-sight velocity moment $\langle v_\text{los}^2 \rangle$.
@@
 Critical mass        & $M_\text{crit}$ [$10^{10} M_\odot$] & $7.87$  & $7.9$   & $\pm$ & $      0.3$ & ($4\%$)\\
-Source position      & $\xi$ [$''$]                      & $0.095$ & $0.09 $ & $\pm$ & $     0.03$ & ($28\%$)\\
-                     & $\eta$ [$''$]                     & $0.107$ & $0.10 $ & $\pm$ & $     0.03$ & ($27\%$)\\
+Source position      & $x_s'$ [$''$]                      & $0.095$ & $0.09 $ & $\pm$ & $     0.03$ & ($28\%$)\\
+                     & $y_s'$ [$''$]                     & $0.107$ & $0.10 $ & $\pm$ & $     0.03$ & ($27\%$)\\
 Fourier coefficients & $a_0$                               & $1.814$ & $1.82 $ & $\pm$ & $   0.04$ & (2\%)\\
@@
 
-To estimate how the uncertainties in the determination of image positions and galaxy center affect the results, we sample random positions from two-dimensional Normal distributions with peaks and standard deviations according to Table \ref{tab:lenspos}.
+To estimate how the uncertainties in the determination of image positions and galaxy center affect the results, we sample random positions from 2-dimensional Normal distributions with peaks and standard deviations according to Table \ref{tab:lenspos}.
 Model fits to many sampled image positions lead to probability distributions for the best fit shape parameters and Einstein quantities; peak and standard deviations are given in the second column of Table \ref{tab:bestfitlensmodel}.
@@
 
-Two-dimensional stellar kinematics would greatly help to resolve this problem.
+2-dimensional stellar kinematics would greatly help to resolve this problem.
 The main future work would be therefore getting high-resolution integral-field spectroscopy for J1331.
@@
 We speculate that a merger might have modified the kinematic structure and/or mass distribution of J1331 such that crucial model assumptions are not valid anymore.
-To resolve the ambiguities in J1331's mass distribution two-dimensional kinematic maps of J1331 from integral-fiel units spectroscopy would be needed.
+To resolve the ambiguities in J1331's mass distribution 2-dimensional kinematic maps of J1331 from integral-field unit spectroscopy would be needed.
 %--------------------------------------------
@@
 \bibliography{literaturelist}
-%\begin{thebibliography}{}
-%\bibitem[Dutton et al.(2011)]{2011MNRAS.416..322D} Dutton, A.~A., Conroy, C., van den Bosch, F.~C., et al.\ 2011, \mnras, 416, 322 
-%\bibitem[Franx \& Illingworth(1988)]{1988ApJ...327L..55F} Franx, M., \& Illingworth, G.~D.\ 1988, \apjl, 327, L55 
-%\bibitem[Moore(1994)]{1994Natur.370..629M} Moore, B.\ 1994, \nat, 370, 629 
-%\bibitem[Navarro et al.(1996)]{1996ApJ...462..563N} Navarro, J.~F., Frenk, C.~S., \& White, S.~D.~M.\ 1996, \apj, 462, 563 
-%\bibitem[de Blok et al.(2001)]{2001ApJ...552L..23D} de Blok, W.~J.~G., McGaugh, S.~S., Bosma, A., \& Rubin, V.~C.\ 2001, \apjl, 552, L23
-
-%\end{thebibliography}
 %--------------------------------------------

### 2016-01-28 LensingPaper_draft_v3.05.tex
Corrected typos in 3.3.2 and 3.3.3

@@
 %--------------------------------------------
-As data we use stellar line-of-sight rotation velocities $v_\text{rot} \equiv \langle v_\text{los} \rangle$ and velocity dispersions $\sigma$ as described in Section \ref{sec:data_kinematics}.
-The JAM models give us a prediction for the second line-of-sight velocity moment $\langle v_\text{los}^2 \rangle$.
+As data we use stellar line-of-sight rotation velocities $v_\text{rot} = \langle v_\text{los} \rangle_\text{obs}$ and velocity dispersions $\sigma$ as described in Section \ref{sec:data_kinematics}.
+The JAM models give a prediction for the second line-of-sight velocity moment $\langle v_\text{los}^2 \rangle_\text{obs}$.
 The root-mean-square (rms) line-of-sight velocity $v_\text{rms}$ allows a data-model comparison by relating theses velocities according to
 \begin{equation*}
-v_\text{rms}^2 = \langle v_\text{los}^2 \rangle = v_\text{rot}^2 + \sigma^2.
+ v_\text{rms}^2 = v_\text{rot}^2 + \sigma^2  \stackrel{!}{=} \langle v_\text{los}^2 \rangle_\text{obs}.
 \end{equation*}
-The model in Equation \eqref{eq:explicitLOSvelCap} predicts the intrinsic $\langle v_\text{los}^2 \rangle$ at a given position on the sky, which needs then to be modified according to the mode of observation, to be comparable to the measurements.
+The model in Equation \eqref{eq:explicitLOSvelCap} predicts the intrinsic $\langle v_\text{los}^2 \rangle_\text{intr}\equiv\langle v_\text{los}^2\rangle$ at a given position on the sky, which needs then to be modified to $\langle v_\text{los}^2 \rangle_\text{obs}$ according to the mode of observation to be comparable to the measurements.
 The measured $v_\text{rms}$ is a light-weighted mean for a pixel along the long-slit of the spectrograph, with width $L_y = 1''$ \citep{SWELLSV} and a certain given extent along the galaxy's major axis, $L_x$, i.e., for a rectangular aperture
@@
 \begin{equation*}
-\text{PSF}(x',y')\equiv\mathscr{N}(0,\text{FWHM}/2\sqrt{2\ln2}).
+\text{PSF}(x',y')\equiv\mathscr{N}(0,\sigma_\text{seeing}=\text{FWHM}/2\sqrt{2\ln2}).
 \end{equation*}
-The model predictions for $\langle v_\text{los}^2 \rangle$ have therefore to be convolved with the convolution kernel
+The model predictions for $\langle v_\text{los}^2 \rangle_\text{intr}$ have therefore to be convolved with the convolution kernel
 \begin{eqnarray*}
@@
 I_\text{obs} &=& I \ast K\\
-\langle v_\text{los}^2 \rangle |_\text{obs} &=& \frac{(I \langle v_\text{los}^2\rangle) \ast K}{I_\text{obs}}.
+\langle v_\text{los}^2 \rangle_\text{obs} &=& \frac{(I \langle v_\text{los}^2\rangle_\text{intr}) \ast K}{I_\text{obs}}.
 \end{eqnarray*}
@@
 %--------------------------------------------
-The intrinsic rotation curve is the first velocity moment $\langle v_\phi\rangle = \sqrt{\langle v_\phi^2 \rangle - \sigma_\phi^2}$.
-The observed rotation curve is the projection of the light-weighted contributions to $\langle v_\phi\rangle$ along the line-of-sight \citep{Cap08},
+The intrinsic galaxy rotation curve is the first velocity moment $\langle v_\phi\rangle = \sqrt{\langle v_\phi^2 \rangle - \sigma_\phi^2}$.
+The observed rotation velocity is the projection of the light-weighted contributions to $\langle v_\phi\rangle$ along the line-of-sight \citep{Cap08},
 \begin{equation*}
@@
 The sign of $\kappa$ determines the rotation direction.
-We can assign a constant $\kappa_k$ to every Gaussian in the MGE formalism and
+We can assign a constant $\kappa_i$ to every Gaussian in the MGE formalism and
 \begin{equation*}
-\nu \langle v_\phi\rangle = \left[\nu \sum_{k} \kappa_k^2 \left( [\nu\langle v_\phi^2 \rangle]_k - [\nu\langle v_R^2 \rangle]_k\right) \right]^{1/2}
+\nu \langle v_\phi\rangle = \left[\nu \sum_{i=1}^N \kappa_i^2 \left( [\nu\langle v_\phi^2 \rangle]_i - [\nu\langle v_R^2 \rangle]_i\right) \right]^{1/2}
 \end{equation*} 
@@
 \end{equation}
-We find $\kappa'$ by matching the model $\langle v_\text{los} \rangle$ with the symmetrized $v_\text{rot}$ data, where for a given $\kappa'$ the $\kappa_k$ are found from fitting the MGE generated profile $\kappa(R) = \sum_k \kappa_k \nu_k(r)/\sum_k \nu_k(r)$ to Equation \eqref{eq:kappa_profile}.
+We find $\kappa'$ by matching the model $\langle v_\text{los} \rangle_\text{obs}$ with the symmetrized $v_\text{rot}$ data, where for a given $\kappa'$ the $\kappa_i$ are found from fitting the MGE generated profile $\kappa(R) = \sum_i \kappa_i \nu_i(r)/\sum_i \nu_i(r)$ to Equation \eqref{eq:kappa_profile}.
 The observed zero point is at $R'_0\approx 2''$.

### 2016-01-29 LensingPaper_draft_v3.05.tex
Finished last corrections.

@@
 %_____FORMAT_____
-%\setcounter{secnumdepth}{3}	%depth of section numbering
 \usepackage{hyperref} %ready-to-lick referencing
@@
 \newcommand*\Diff[1]{\mathop{}\!\mathrm{d^#1}}
-%\newcommand{\vect}[1]{\boldsymbol{#1}} % Uncomment for BOLD vectors.
-\newcommand{\vect}[1]{\vec{#1}} % Uncomment for ARROW vectors.
-\usepackage[usenames,dvipsnames]{xcolor}
-\newcommand{\Wilma}[1]{\textcolor{Magenta}{#1}}
+\newcommand{\vect}[1]{\vec{#1}} %  ARROW vectors.
 
@@
 
-\subsubsection{Deprojection}
+\subsubsection{Deprojection} \label{sec:MGE_theo_deprojection}
 
@@
 %--------------------------------------------
-\subsubsection{Jeans Anisotropic Models (JAM)} 
+\subsubsection{Jeans Anisotropic Models (JAM)} \label{sec:model_JAM_JAM}
 %--------------------------------------------
@@
 The JAM modelling code by \citet{Cap08} evaluates Equation \eqref{eq:explicitLOSvelCap} numerically for a given luminous tracer and mass distribution MGE and a given inclination.
-
-%--------------------------------------------
-\subsubsection{Data comparison} 
+%--------------------------------------------
+
+%--------------------------------------------
+\subsubsection{Data comparison} \label{sec:model_JAM_compare}
 %--------------------------------------------
@@
 We set $L_x = 0.21''$ as the width of the model pixel, and get a prediction for the actual measurements in bins of width $0.63''$, $1.26''$ and $1.89''$ \citep{SWELLSV} as light-weighted mean from each 3, 6 and 9 model pixels.
-
-%--------------------------------------------
-\subsubsection{Rotation curve}
+%--------------------------------------------
+
+%--------------------------------------------
+\subsubsection{Rotation curve} \label{sec:model_JAM_rotation}
 %--------------------------------------------
@@
 In the deprojected galactic plane the radius of zero rotation would be at a $R_0 \gtrsim 2''$, and we choose it to be at $2.2''$.
-
-%--------------------------------------------
-\subsubsection{Including a NFW halo} 
+%--------------------------------------------
+
+%--------------------------------------------
+\subsubsection{Including a NFW halo} \label{sec:model_JAM_NFW}
 %--------------------------------------------
@@
 and two free parameters, the scale length $r_s$ and a parameter describing the total mass of the halo.
-We will use $v_\text{200}$, which is the circular velocity at the radius $r_\text{200}$ within which the mean density of the halo is 200 times the cosmological critical density $\rho_\text{crit} \equiv (2H^2)/(8\pi G)$, i.e.
+We will use $v_\text{200}$, which is the circular velocity at the radius $r_\text{200}$ within which the mean density of the halo is 200 times the cosmological critical density $\rho_\text{crit} \equiv (2H^2)/(8\pi G)$, i.e.,
 \begin{eqnarray*}
@@
 with $\rho_\text{crit}(z=0)=1.43 \cdot 10^{-7} M_\odot / \text{pc}^3$ in the WMAP5 cosmology by \citet{WMAP5cosm}.
-How much the mass is concentrated in the center of the NFW halo is given by the concentration of the NFW halo defined by
+How much the mass is concentrated in the center of the NFW halo is given by the concentration parameter
 \begin{equation}
@@
 scaling                   & $1~\text{kpc} / 1''$ & $2.006$ \\
-position angle from North          & $\phi$ [degrees] & $42.90^\circ$\\
+position angle from North          & $\phi$ [$^\circ$] & $42.90$\\
 average axis ratio & $q'$ & $0.598$\\
 average ellipticity & $\epsilon = 1 - q'$ & $0.402$ \\
-estimated inclination & $i$ [degrees] & $70^\circ$\\
+estimated inclination & $i$ [$^\circ$] & $70$\\
 apparent I-band magnitude & $m_\text{I}$ [mag] & $15.77$ \\
@@
 %--------------------------------------------
-In this section we construct a model for the J1331's intrinsic light distribution in terms of MGEs (see Section \ref{sec:MGE_theo}).
+In this section we construct a model for J1331's intrinsic light distribution in terms of MGEs (see Section \ref{sec:MGE_theo}).
 We use the HST image in the F814W (I-band) filter (Figure \ref{fig:F814W}) because J1331's central stellar component appears at longer wavelengths (i) smoother and more extended than in the F450W filter (Figure \ref{fig:F450W}), as it is less sensitive to young clumpy star-forming regions, (ii) much brighter than the bluish lensing images, and (iii) the imaging is less prone to extinction.
@@
 \centering
-\caption{F814W PSF MGE: Parameters of the circular four-Gaussian MGE in Equation \eqref{eq:PSFgeneral} fitted to the radial profile of the synthetic HST/F814W PSF image.}
+\caption{F814W PSF MGE: Parameters of the circular 4-Gaussian MGE in Equation \eqref{eq:PSFgeneral} fitted to the radial profile of the synthetic HST/F814W PSF image.}
 \begin{tabular}{ccc}
@@
 %--------------------------------------------
-\subsubsection{MGE for the inner regions.}
-%--------------------------------------------
-
-%--------------------------------------------
-We fit a MGE to J1331's smooth central region within $\sim 5''$ from the HST/WFPC2/WF3/F814W image (Figure \ref{fig:F814W}).
+\subsubsection{MGE for the inner and outer regions}
+%--------------------------------------------
+
+%--------------------------------------------
+We fit a MGE to J1331's smooth central region within $\sim 5''$ of the HST/WFPC2/WF3/F814W image (Figure \ref{fig:F814W}).
 Bright objects close to the bulge (blobs possibly belonging to the background galaxy and parts of the foreground spiral arm) were masked during the fit.
@@
 The best fit MGE (PSF convolved) is compared to the data in Figure \ref{fig:MGEinnerRegions} and the corresponding parameters of the intrinsic surface brightness distribution are given in Table \ref{tab:MGEF814W}.
-The fit is a very good representation of the light distribution in the inner $5''$, but underestimates the light distribution outward.
-
-%--------------------------------------------
-\subsubsection{MGE for the outer regions}
-%--------------------------------------------
-
-%--------------------------------------------
-To get a handle on the light distribution also in the outer parts of J1331, where spiral arms dominate, we first fit a IRAF \citep{1993ASPC...52..173T} \emph{ellipse} model to the F814W image (masking the brightest blobs in the spiral arms and outer regions).
-Only then we fit a 7-Gaussian MGE to the smooth ellipse model.
-The MGE does not perfectly reproduce the flatness of the ellipse model at every radius (see Figure \ref{fig:MGEouterRegions}), but considering the spiral arm dominated outer regions of J1331, it is good enough for an approximate handling of the overall light distribution.
+The fit is a very good representation of the light distribution in the inner $5''$, but underestimates the light distribution further out.
+
+To get a handle on the light distribution also in the outer parts of J1331 where spiral arms dominate, we first fit a IRAF \citep{1993ASPC...52..173T} \emph{ellipse} model to the F814W image (masking the brightest blobs in the spiral arms and outer regions).
+Only then we fit a 7-Gaussian MGE to the smooth \emph{ellipse} model.
+The MGE does not perfectly reproduce the flatness of the \emph{ellipse} model at every radius (see Figure \ref{fig:MGEouterRegions}), but considering the spiral arm dominated outer regions of J1331 it is good enough for an approximate handling of the overall light distribution.
+%--------------------------------------------
 
@@
 The orange lines indicate here contours of a smooth IRAF \emph{ellipse} fit to J1331 in the F814W filter; the grey lines are the corresponding best fit MGE.
-This MGE is not used for dynamical modelling, because the dynamics in the outer regions are strongly affected by non-axisymmetries (e.g., spiral arms).
+This MGE is not used for dynamical modelling because the dynamics in the outer regions are strongly affected by non-axisymmetries (e.g., spiral arms).
 We use it, however, to estimate the galaxy's total luminosity and effective radius, and to get a prediction for the dynamics of the outer regions.}
@@
 \caption{Parameters of the best fit MGE to the F814W surface brightness of J1331 in Figure \ref{fig:MGEinnerRegions}.
-The fit is best inside an radius of $5''$.
+The fit is best inside a radius of $5''$.
 The position angle is given in Table \ref{tab:galaxyparameters}.
@@
 \begin{equation*}
-C_{0,i}\text{[counts/pixel]} = \frac{L_i[\text{counts}]}{2\pi \sigma[\text{pixel}]^2 q}.
+C_{0,i}\text{[counts/pixel]} = \frac{L_i[\text{counts}]}{2\pi \sigma_i[\text{pixel}]^2 q_i}.
 \end{equation*}
@@
 \end{equation}
-where $Z\simeq21.62~\text{mag}$ is a the zero-point from \citet{Holtzman}, updated according to \citet{Dolphin,DolphinNew}, for the photometric system of the HST/WFPC2 camera and the F814W filter, plus a correction for the difference in gain between calibration and observation.
+where $Z\simeq21.62~\text{mag}$ is the zero-point from \citet{Holtzman}, updated according to \citet{Dolphin,DolphinNew}, for the photometric system of the HST/WFPC2 camera and the F814W filter, plus a correction for the difference in gain between calibration and observation.
 $C= 0.1~\text{mag}$ corrects for the finite aperture of the WFPC2; and $A_I =0.015~\text{mag}$ is the extinction in the (Landolt) I-band towards J1331, according to the NASA/IPAC Extragalactic Database (NED)\footnote{The NASA/IPAC Extragalactic Database (NED, \url{https://ned.ipac.caltech.edu/}) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.
 The data for J1331 (SDSS J133140.33+362811.9) was retrieved in October 2013.}.
-The color-dependent correction between the F814W filter and the I-band of the UBVRI photometric system is  small \citep{Holtzman} and we neglect it therefore.
+The colour-dependent correction between the F814W filter and the I-band of the UBVRI photometric system is  small \citep{Holtzman} and we neglect it therefore.
 The last step is to transform the surface brightness $\mu_{I,0,i}$ (in mag) to the I-band surface density $I_{0,i}$ (in $L_\odot$/pc$^2$) of the Gaussian, i.e.,
@@
 The luminosity $L_i$[counts] and the corresponding surface brightness density $I_{0,i} [L_\odot \text{pc}^{-2}]$ of each Gaussian are given in Table \ref{fig:MGEinnerRegions}.
-
-%--------------------------------------------
-\subsubsection{Inclination}
+%--------------------------------------------
+
+%============================================
+\begin{table}
+\centering
+\caption{Positions of the lensing images (A-D) and the galaxy center (G) in Figure \ref{fig:lens_just_imgpos}.
+The image positions were determined from the lens-MGE subtracted F450W image for J1331by \citet{SWELLSIII} (their Figure 4), rotated to the $(x',y')$ coordinate system in Figure \ref{fig:lens_just_imgpos}.
+The pixel scale is 1 pixel = $0.05''$ and the error of the image positions A-D is $\pm$ 1 pixel.}
+\begin{tabular}{r|rrrr|c}
+\hline
+  & A & B & C & D & G\\\hline
+$x_i'$ [pixel] & 12.1 & -8.5 & 21.7 & -3.3 & 0.5 $\pm \sqrt{2}$ \\
+$y_i'$ [pixel] & 16.6 & -10.4 & -0.5 & 19.2 & 0.5 $\pm \sqrt{2}$ \\
+\hline
+\end{tabular}
+\label{tab:lenspos}
+\end{table}
+%============================================
+
+%--------------------------------------------
+\subsubsection{Inclination, total luminosity and effective radius}
 %--------------------------------------------
@@
 Our estimate for the inclination is therefore $i \approx 70^\circ$.
-Given this inclination, the 2D MGE models can be deprojected into three dimensions (see Section \ref{sec:MGE_theo}).
-
-%--------------------------------------------
-\subsubsection{Total luminosity and effective radius}
-%--------------------------------------------
-
-%--------------------------------------------
+Given this inclination, the 2-dimensional MGE models can be deprojected into three dimensions (see Section \ref{sec:MGE_theo_deprojection}).
+
 J1331's total I-band luminosity is determined by summing up the luminosity contributions of all the MGE Gaussians for the outer regions (shown as grey lines in Figure \ref{fig:MGEouterRegions}).
@@
 %============================================
-\begin{table}
-\centering
-\caption{Positions of the lensing images (A-D) and the galaxy center (G) in Figure \ref{fig:lens_just_imgpos}.
-The image positions were determined from the lens subtracted image for J1331 in Figure 4 of \citet{SWELLSIII}, rotated to the $(x,y)$ coordinate system in Figure \ref{fig:lens_just_imgpos}.
-The pixel scale is 1 pixel = $0.05''$ and the error of each image position is $\pm$ 1 pixel.}
-\begin{tabular}{r|rrrr|c}
-\hline
-  & A & B & C & D & G\\\hline
-$x_i$ [pixel] & 12.1 & -8.5 & 21.7 & -3.3 & 0.5 $\pm \sqrt{2}$ \\
-$y_i$ [pixel] & 16.6 & -10.4 & -0.5 & 19.2 & 0.5 $\pm \sqrt{2}$ \\
-\hline
-\end{tabular}
-\label{tab:lenspos}
-\end{table}
-%============================================
-
-%============================================
 \begin{figure}
@@
   \includegraphics[width=\linewidth]{fig/lens_all_in_one.ps}
-\caption{Lensing model (Table \ref{tab:bestfitlensmodel}) found as best fit to the image positions.
+\caption{Lensing model (Table \ref{tab:bestfitlensmodel}) found as best fit to the lensing image positions.
 In the background we show the central region of J1331 in the F450W filter, subtracted by an IRAF \emph{ellipse} model of the F450W surface brightness and smoothed to remove noise smaller than the PSF.
@@
 
-Even though the constraint from the image positions on $\alpha$ is very weak, we were however able to show that the image positions in Table \ref{tab:lenspos} are consistent with a model with flat rotation curve.
+Even though the constraint from the image positions on $\alpha$ is very weak, we were able to show that the image positions in Table \ref{tab:lenspos} are consistent with a model with flat rotation curve.
 In the following we therefore set $\alpha=1$.
@@
 Model fits to many sampled image positions lead to probability distributions for the best fit shape parameters and Einstein quantities; peak and standard deviations are given in the second column of Table \ref{tab:bestfitlensmodel}.
-We constrain the Einstein radius to within 2\%, $R_\text{ein} = (0.91 \pm 0.02)''$ and the projected mass within the critical curve with a relative error of 4\%, $M_\text{crit} =(7.9\pm0.3)\cdot 10^{10} M_\odot$.
+We constrain the Einstein radius to within 2\%, $R_\text{ein} = (0.91 \pm 0.02)'' \hat{=}(1.83\pm0.04)~\text{kpc}$, and the projected mass within the critical curve with a relative error of 4\%, $M_\text{crit} =(7.9\pm0.3)\cdot 10^{10} M_\odot$.
 Our measurement of $R_\text{ein}$ is consistent with that from \citet{SWELLSIII}, $R_\text{ein,SWELLS} = (0.96 \pm 0.04)''$ (which used a singular isothermal ellipsoid as lens mass model and the intermediate-axis convention of the critical curve as the Einstein radius).
@@
 The red solid line corresponds to the lens model for a flat rotation curve ($\alpha = 1$) in Table \ref{tab:bestfitlensmodel}; the red dashed and dash-dotted lines are best fit lens models found analogously from the image positions, but for a fixed rotation curve slope of $\alpha = 1.1$ and $0.9$, respectively.
-For the JAM modelling a best fit MGE to the lens mass models were used, as well as the observed surface brightness MGE in Table \ref{tab:MGEF814W}, assuming velocity isotropy $\beta_z = 0$ and an inclination of $i = 70^\circ$.
-The most reliable constraints are around the Einstein radius (vertical red dotted line); outside of it the JAM model is just an extrapolation.}
+For the JAM modelling best fit MGEs to the lens mass models were used, as well as the observed surface brightness MGE in Table \ref{tab:MGEF814W}, assuming velocity isotropy $\beta_z = 0$ and an inclination of $i = 70^\circ$.
+The most reliable constraints are around the Einstein radius (vertical red dotted line); outside of it the model is just an extrapolation.}
   \label{fig:JAM_modelL}
@@
 %--------------------------------------------
-\subsubsection{Comparison with light distribution}
+\subsubsection{Comparison with light distribution} \label{sec:results_lensing_compare}
 %--------------------------------------------
@@
 
-Figure \ref{fig:lenslightcompareALL} leads to the following three findings: (1)The mass predicted from lensing and the observed light distribution are oriented in the same direction (i.e., have the same position angle).
-(2) Within and around the Einstein radius, mass and light distribution have a similar elliptical shape, while further out the mass distribution is slightly rounder.
-(3) The light distribution drops faster than the mass with increasing radius (which is---at least partly---because of the assumption of a flat rotation curve).
-However, the mass distribution is only constraint around the Einstein radius and otherwise an extrapolation.
+Figure \ref{fig:lenslightcompareALL} leads to the following three findings: (i)The mass predicted from lensing and the observed light distribution are oriented in the same direction (i.e., have the same position angle).
+(ii) Within and around the Einstein radius, mass and light distribution have a similar elliptical shape, while further out the mass distribution is slightly rounder.
+(iii) The light distribution drops faster than the mass with increasing radius (which is---at least partly---because of the assumption of a flat rotation curve).
+However, the mass distribution is only constrained around the Einstein radius and otherwise an extrapolation.
 %--------------------------------------------
@@
   \includegraphics[height=6cm]{fig/jam_A2_vrms.ps}
-  \caption{Comparison of the symmetrized $v_\text{rms}$ data of J1331 (blue dots) with a best fit dynamical JAM model (orange line) assuming mass-follows-light and with two free parameters: $\Upsilon_\text{I,tot}^\text{dyn}$, the total constant I-band mass-to-light ratio which converts the observed surface brightness in Table \ref{tab:MGEF814W} into a mass distribution, and the velocity anisotropy parameter $\beta_z$.
+  \caption{Comparison of the symmetrized $v_\text{rms}$ data of J1331 (blue dots) with a best fit dynamical JAM model (orange line) assuming ``mass-follows-light'' and with two free parameters: $\Upsilon_\text{I,tot}^\text{dyn}$, the total constant I-band mass-to-light ratio which converts the observed surface brightness in Table \ref{tab:MGEF814W} into a mass distribution, and the velocity anisotropy parameter $\beta_z$.
 The ``best'' fit is $\Upsilon_\text{I,tot}^\text{dyn} = 4.8 \pm 0.1$ and $\beta_z = -0.5$, where the latter is however pegged at the lower limit of the allowed value range.
@@
 %--------------------------------------------
-In this section we create dynamical models for J1331 following the procedure in Section \ref{sec:model_JAM}.
+In this section we create dynamical models for J1331 following the procedure in Sections \ref{sec:model_JAM_JAM}-\ref{sec:model_JAM_compare}.
 We use the deprojected surface brightness MGE from Table \ref{tab:MGEF814W} for the tracer distribution $\nu(R,z)$ and to generate mass models $\rho(R,z)$.
@@
 %--------------------------------------------
-We make an independent prediction for the $v_\text{rms}$ curve by evaluating Equation \ref{eq:explicitLOSvelCap} (with $\beta_z = 0$) for the lens mass model in Table \ref{tab:bestfitlensmodel} ($\alpha = 1$, flat rotation curve).
+We make an independent prediction for the $v_\text{rms}$ curve by evaluating Equation \eqref{eq:explicitLOSvelCap} (with $\beta_z = 0$) for the lens mass model in Table \ref{tab:bestfitlensmodel} ($\alpha = 1$, flat rotation curve).
 In addition, we also calculate a  $v_\text{rms}$ curve for two lens models which were found analogously, but assumed a slightly rising (falling) rotation curve slope of $\alpha=1.1$ ($\alpha=0.9$).
@@
 This is in concordance with observations in other galaxies.
-For $R'> R_\text{eff}$ we would expect $\alpha<1$---and the lensing model for $\alpha=0.9$ has indeed a slightly dropping $v_\text{rms}$ around $R_\text{eff}$, like the data.
+For $R'> R_\text{eff}$ we would expect $\alpha<1$; and the lensing model for $\alpha=0.9$ has indeed a slightly dropping $v_\text{rms}$ around $R_\text{eff}$ like the data.
 A definite comparison in this regime is however difficult as the lens models are just extrapolations outside of $R_\text{ein}$.
-While our lensing model assumes $\alpha(R')=\text{const}$, Figure \ref{fig:JAM_modelL} suggests, that a model with variable $\alpha(R')$ could fit even better.
-Overall the lensing model is in very good agreement with the $v_\text{rms}$ data within $R' \sim 3''$---even though it was derived completely independently.
+While our lensing model assumes $\alpha(R')=\text{const}$, Figure \ref{fig:JAM_modelL} suggests that a model with variable $\alpha(R')$ could fit even better.
+Overall the lensing model is in very good agreement with the $v_\text{rms}$ data within $R' \sim 3''$, even though it was derived completely independently.
 %--------------------------------------------
@@
 This assumes that the DM is always a constant fraction of the total matter distribution within the region covered by the kinematics.
-This simplified mass model sometimes gives good representations of the inner parts of galaxies, where the stellar component dominates.
-
-We also allow for a overall constant but non-zero velocity anisotropy $\beta_z$ in the model.
+This simplified mass model sometimes gives good representations of the inner parts of galaxies where the stellar component dominates.
+
+We also allow for an overall constant but non-zero velocity anisotropy $\beta_z$ in the model.
 The model parameters ($\Upsilon_\text{I,tot}^\text{dyn},\beta_z$) that fit the $v_\text{rms}$ data best are found using a $\chi^2$-fit and are demonstrated in Figure \ref{fig:JAM_modelA2}.
@@
 We also tested radial profiles for $\beta_z(R)$ of the form proposed by \citet{BaesVanHese}, which was however equally unable to reproduce the data.
-We conclude, that this is due to the well-known degeneracy between anisotropy and mass profile and the mass-follows-light model is \emph{not} a good representation of the mass distribution in J1331's inner regions.
+We conclude that this is due to the well-known degeneracy between anisotropy and mass profile and the mass-follows-light model is \emph{not} a good representation of the mass distribution in J1331's inner regions.
 
@@
 \includegraphics[width=0.9\linewidth]{fig/B4_contour_plot_short.ps}
-\caption{Posterior probability distribution (pdf) sampled with an MCMC (red dots and histograms) for a JAM model fitted to the stellar $v_\text{rms}$ data, with NFW halo, parametrized by $r_s$ and $v_\text{200}$, a stellar mass distribution generated from the I-band MGE in Table \ref{tab:MGEF814W} and a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and constant velocity anisotropy $\beta_z$.
+\caption{Posterior probability distribution (pdf) sampled with a Monte Carlo Markov Chain (MCMC) (red dots and histograms) for a JAM model fitted to the stellar $v_\text{rms}$ data, with NFW halo, parametrized by $r_s$ and $v_\text{200}$, a stellar mass distribution generated from the I-band MGE in Table \ref{tab:MGEF814W} and a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and constant velocity anisotropy $\beta_z$.
 Shown are also the priors used for J1331's NFW halo, $\mathscr{N}(200~\text{km s}^{-1},40~\text{km s}^{-1})$ (green, see Equation \eqref{eq:prior_v200}) and the concentration vs.
@@
 \caption{JAM model including a NFW halo and constant velocity anisotropy fitted to the stellar $v_\text{rms}$ data (blue solid dots) within $\sim3.5''$ and the Einstein mass (red solid dot).
-The 12 lines shown correspond to 12 models randomly drawn from the pdf (marked as grey diamonds in Figure \ref{fig:modelB4_triangle}) and demonstrate how tight the modelling constraints are.
+The 12 lines shown correspond to 12 models randomly drawn from the pdf (marked as grey diamonds in Figure \ref{fig:modelB4_triangle}) and their range demonstrates how tight the modelling constraints are.
 The mean and standard deviation of the pdf, i.e., the "best fit" parameters, are given in Table \ref{tab:modelB4_bestfit}.
@@
 At larger radii the non-symmetrized data (open blue dots) is compared to an extrapolation of the best fit models using the surface brightness MGE for the outer regions from Figure \ref{fig:MGEouterRegions} (red dashed lines).
-\emph{Panel (b):} Shown is the circular velocity curve of the total mass (green), and separately the contribution of the stellar mass (yellow, again generated from the MGE in Table \ref{tab:MGEF814W}) and DM (grey).
+\emph{Panel (b):} Shown is the projected enclosed mass profile of the total mass (green), and separately the contribution of the stellar mass (yellow, again generated from the MGE in Table \ref{tab:MGEF814W}) and DM (grey).
 At the Einstein radius $R_\text{ein}$ (red dotted line) the Einstein mass $M_\text{ein}$ is overplotted with a 10\% error, which was also included in the fit as additional constraint.
@@
 \end{tabular}
-\caption{Summary of the best fit parameters of the JAM model with NFW halo and constant velocity anisotropy, fitted to the $v_\text{rms}$ data within $\sim 3.5''$ and the Einstein mass.
+\caption{Summary of the best fit parameters of the JAM model with NFW halo and constant velocity anisotropy, fitted to the $v_\text{rms}$ data within $\sim 3.5''$ and the Einstein mass $\pm10\%$.
 These estimates correspond to the mean and standard deviation of the pdf in Figure \ref{fig:modelB4_triangle}.
@@
 %--------------------------------------------
-In Section \ref{sec:results_lensing} we found from lensing constraints, that the light distribution might drop faster with radius than the mass distribution.
+In Section \ref{sec:results_lensing_compare} we found from lensing constraints, that the light distribution might drop faster with radius than the mass distribution.
 This could correspond to a radially increasing total mass-to-light ratio.
-As velocity anisotropy alone cannot explain the observed kinematics in a simple a mass-follows-light model, we now allow for a mass-to-light ratio gradient in the JAM modelling.
-We therefore generate a mass model from the light distribution in Table \ref{tab:MGEF814W} by assigning each of the five Gaussians in the MGE its own total mass-to-light ratio $\Upsilon_{\text{I,tot,}i}$ and replace the total luminosity in Equation \eqref{eq:centralItotalL} $L_i$ with the Gaussians total Mass $M_i = \Upsilon_{\text{I,tot,}i} L_i$.
+As velocity anisotropy alone cannot explain the observed kinematics in a simple mass-follows-light model, we now allow for a mass-to-light ratio gradient in the JAM modelling.
+We therefore generate a mass model from the light distribution in Table \ref{tab:MGEF814W} by assigning each of the five Gaussians in the MGE its own total mass-to-light ratio $\Upsilon_{\text{I,tot,}i}$ and replace the total luminosity in Equation \eqref{eq:centralItotalL} $L_i$ with the Gaussians total mass $M_i = \Upsilon_{\text{I,tot,}i} \cdot L_i$.
 We treat the five $\Upsilon_{\text{I,tot,}i}$ as free fit parameters and only require that $\Upsilon_{\text{I,tot,}j} \geq \Upsilon_{\text{I,tot,}i}$ when the corresponding $\sigma_j \geq \sigma_i$ to ensure that the overall mass-to-light ratio is increasing with radius.
@@
 Figure \ref{fig:JAM_modelG} shows that the best fit model nicely reproduces the central dip in the $v_\text{rms}$ curve, even though it has difficulties fitting the drop around $R' \sim 4''$.
-The latter might be because we only allowed the $\Upsilon_\text{I,tot}(R')$ to rise.
+The latter is because we only allowed the $\Upsilon_\text{I,tot}(R')$ to rise.
 A slight drop could be expected when the reddish bulge turns into the bluish disk and the contribution of the stellar component becomes less due to a lower $\Upsilon_\text{I,*}$ for younger and bluer populations.
@@
 %--------------------------------------------
-
-%--------------------------------------------
-\subsubsection{Including a DM halo}
-%--------------------------------------------
-
-%--------------------------------------------
-We therefore proceed by modelling the mass distribution with (i) a stellar component, which we get from the light MGE in Table \ref{tab:MGEF814W} (deprojected to the intrinsic $\nu(R,z)$) times a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and (ii) a spherical NFW DM component (see Section \ref{sec:model_JAM}) with halo scale length $r_s$ and circular velocity at the virial radius $v_{200}$ as free parameters.
-In the JAM modelling we use a 10-Gaussian MGE fit to the classical NFW profile in Equation \eqref{eq:NFWprofile}.
 
@@
 %--------------------------------------------
+We proceed by modelling the mass distribution with (i) a stellar component, which we get from the light MGE in Table \ref{tab:MGEF814W} (deprojected to the intrinsic $\nu(R,z)$) times a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and (ii) a spherical NFW DM component (see Section \ref{sec:model_JAM_NFW}) with halo scale length $r_s$ and circular velocity $v_{200}$ at the virial radius as free parameters.
+In the JAM modelling we use a 10-Gaussian MGE fit to the classical NFW profile from Equation \eqref{eq:NFWprofile}.
+
 The full set of fit parameters is $(\Upsilon_\text{I,*},r_s,v_{200},\beta_z)$, where $\beta_z$ is again the constant velocity anisotropy parameter.
-We will investigate this parameter space with a MCMC\footnote{The Python code package for \emph{emcee}, a Monte Carlo Markov Chain implementation by \citet{emcee} is available online at \url{http://dan.iel.fm/emcee/current/}.
+We will investigate this parameter space with a Monte Carlo Markov Chain (MCMC)\footnote{The Python code package for \emph{emcee}, a Monte Carlo Markov Chain implementation by \citet{emcee} is available online at \url{http://dan.iel.fm/emcee/current/}.
 The version from October 2013 was used in this work.} \citep{emcee} and use priors for the halo parameters to guide the fit to a realistic NFW halo shape.
@@
 stellar mass for late-type galaxies.
-Using the stellar mass estimate for J1331 from \citet{SWELLSI}, $m_* = (1.06 \pm 0.25) \cdot 10^{11} M_\odot$ for the Chabrier IMF estimate, we find ${v_{200}} = (202_{-33}^{+44})_{-13}^{+12}$.
+Using the stellar mass estimate for J1331 from \citet{SWELLSI}, $m_* = (1.06 \pm 0.25) \cdot 10^{11} M_\odot$ (with generous error; see also Table \ref{tab:previousresults}) for the Chabrier IMF estimate, we find ${v_{200}} = (202_{-33}^{+44})_{-13}^{+12}$.
 The first error is due to the $2\sigma$ scatter in the relation by \citet{Dutton10}.
@@
 \end{eqnarray*}
-where the factor $1/\ln\left( 10 r_s\right)$ is the Jacobian of the transformation from the halo parameters $(v_{200},\log c_{200})$ to $(v_{200},r_s)$.
+where the factor $1/\ln\left( 10 r_s\right)$ is the Jacobian of the transformation from the halo parameters $(v_{200},\log c_{200})$ to the fit parameters $(v_{200},r_s)$.
 
@@
 %--------------------------------------------
-\subsubsection{Result} \label{sec:results_JAM_NFW_results}
+\subsubsection{Best fit JAM modelt} \label{sec:results_JAM_NFW_results}
 %--------------------------------------------
@@
 The transformation from AB magnitudes to the Johnson-Cousins I-Band used the relation $I[\text{mag}] = I[\text{ABmag}] - 0.309$ from \citet{FG1994} (their table 2).
-For the conversion from apparent magnitude to total luminosity the redshift $z=0.113$ \citet{SWELLSIII} was turned into a luminosity distance using the cosmology by \citet{WMAP5cosm}.
+For the conversion from apparent magnitude to total luminosity the redshift $z=0.113$ \citet{SWELLSIII} was turned into a luminosity distance using the WMAP5 cosmology by \citet{WMAP5cosm}.
 }
@@
 We generate a rotation curve from the best fit mean model in Table \ref{tab:modelB4_bestfit}, whose $v_\text{rms}$ curve is shown in the first panel of Figure \ref{fig:modelB4_vrot}.
-Following the procedure in Section \ref{sec:model_JAM}, we find the rotation curve by fitting the rotation parameter $\kappa'$ to the symmetrized $v_\text{rot}$ data within $R' = 3.5''$.
+Following the procedure in Section \ref{sec:model_JAM_rotation}, we find the rotation curve by fitting the rotation parameter $\kappa'$ to the symmetrized $v_\text{rot}$ data within $R' = 3.5''$.
 The best fit with $\kappa' = 0.76$ is given in the second panel of Figure \ref{fig:modelB4_vrot}.
@@
 While the dispersion $\sigma$ in the center fits by construction quite good, the predicted dispersion is much larger than the data.
-We would expect the disk rotationally supported and therefore have a low velocity dispersion; especially dispersions as high as $\sim 200~\text{km s}^{-1}$ are more likely to be observed in the pressure supported bulges of galaxies.
-There might be something unexpected with the $\sigma$ measurements around $\sim 5''$, but at large radii the the best fit model NFW halo is simply too massive.
+We would expect the disk to be rotationally supported and therefore have a low velocity dispersion.
+Especially dispersions as high as $\sim 200~\text{km s}^{-1}$ are more likely to be observed in the pressure supported bulges of galaxies.
+There might be something unexpected with the $\sigma$ measurements around $\sim 5''$, but at large radii the best fit model NFW halo is simply too massive.
 %--------------------------------------------
@@
 %--------------------------------------------
-We've presented different dynamical models for the central region of J1331.
+We have presented different dynamical models for the central region of J1331.
 Some of them capture the observed kinematics, but none of them work at both small and large radii.
@@
 
-\citet{Ferreras} found a relation between the central stellar velocity dispersion $\sigma_0$ in early-type galaxies and the IMF slope $x$; a higher $\sigma_0$ suggests a more bottom-heavy IMF.
-For a unimodal (Salpeter-like) IMF and $\sigma_0 \simeq 200~\text{km s}^{-1}$ in J1331 (see Figure \ref{fig:kinematics}) they predict $x \approx 2.33$, which is close to the standard Salpeter slope, also supported by \citet{2014MNRAS.438.1483S}.
+\citet{Ferreras} found a relation between the central stellar velocity dispersion $\sigma_0$ in early-type galaxies and the IMF slope $x$, where a higher $\sigma_0$ suggests a more bottom-heavy IMF.
+For a unimodal (Salpeter-like) IMF and $\sigma_0 \simeq 200~\text{km s}^{-1}$ in J1331 (see Figure \ref{fig:kinematics}) this relation predicts $x \approx 2.33$, which is close to the standard Salpeter slope, also supported by \citet{2014MNRAS.438.1483S}.
 When assuming a bi-modal (Kroupa-equivalent-like) IMF, \citet{Ferreras} predict $x \approx 2.85$ for J1331's central velocity dispersion.
@@
 When \citet{SWELLSI} assumed a Chabrier IMF, their result translates to $\Upsilon_\text{I,*}^\text{chab} = 2.5 \pm 0.6$ (see Table \ref{tab:previousresults}).
-In Section \ref{sec:results_JAM_SB} we created a dynamical model from only the surface brightness distribution and an increasing mass-to-light ratio profile without additional DM halo.
+In Section \ref{sec:results_JAM_SB_gradient} we created a dynamical model from only the surface brightness distribution and an increasing mass-to-light ratio profile without additional DM halo.
 We found that such a model would be perfectly consistent with the Einstein mass, predict a total $\Upsilon_\text{I,tot}(R'\sim0) = 2.53$---being consistent with the Chabrier IMF estimate by \citet{SWELLSI}---and rise quickly to $\Upsilon_\text{I,tot}(R'\gtrsim R_\text{ein}) \gtrsim 6$.
@@
 We also compare our results from Section \ref{sec:results_JAM_NFW} with the study by \citet{SWELLSV}.
-They found that the bulge of J1331 has an IMF \emph{more} bottom-heavy than the Salpeter IMF from fitting a NFW halo to (1) the Einstein mass and (2) gas kinematics at larger radii $\gtrsim 8''$.
-In Section we fitted a mass model with NFW halo to (1) the Einstein mass and (2) stellar kinematics within $\sim 3.5''$.
+They found that the bulge of J1331 has an IMF \emph{more} bottom-heavy than the Salpeter IMF from fitting a NFW halo to (i) the Einstein mass and (ii) gas kinematics at larger radii $\gtrsim 8''$.
+In Section \ref{sec:results_JAM_NFW} we fitted a mass model with NFW halo to (i) the Einstein mass and (ii) stellar kinematics within $\sim 3.5''$.
 Our best fit $\Upsilon_\text{I,*} = 4.2 \pm 0.2$ (see Table \ref{tab:modelB4_bestfit}) indicates a \emph{less} bottom-heavy IMF than the Salpeter IMF.
-\cite{SWELLSV} found systematically lower NFW halo masses ($v_\text{circ,halo}(5'') \sim 120~\text{km s}^{-1}$ according to their Figure 2) than we did ($v_\text{circ,halo}(5'') \sim 200~\text{km s}^{-1}$).
+\cite{SWELLSV} found systematically lower NFW halo masses ($v_\text{circ,halo}(5'') \sim 120~\text{km s}^{-1}$ according to their Figure 2) than we did ($v_\text{circ,halo}(R'=5'') \sim 200~\text{km s}^{-1}$).
 %--------------------------------------------
@@
 %--------------------------------------------
-In Figure \ref{fig:vcirc_comparison} we compare the circular velocity curve found by \citet{SWELLSV} with a mass-follows-light model scaled to fit our Einstein mass (by multiplying the light distribution in Table \ref{tab:MGEF814W} with $\Upsilon_\text{I,tot}^\text{ein} = 5.56$).
+In Figure \ref{fig:vcirc_comparison} we compare the circular velocity curve found by \citet{SWELLSV} with a mass-follows-light model scaled to fit our Einstein mass (by multiplying the light distribution in Table \ref{tab:MGEF814W} by $\Upsilon_\text{I,tot}^\text{ein} = 5.56$, analogous to Figure \ref{fig:lenscomparelight}).
 Within $R < 5''$ they agree with each other.
@@
 We compare the lens mass model's $v_\text{circ}$ (for $\alpha=1.0\pm 0.1$) with the NFW JAM model (Table \ref{tab:modelB4_bestfit}) in Figure \ref{fig:vcirc_comparison} as well.
-Within and around $R_\text{ein}$ they are consistent with each other, even though they where independently derived.
-They do not agree with the result by \citet{SWELLSV} and in Section \ref{sec:results_JAM_SB} we showed, that ``mass-follows-light'' is not a good model for J1331.
+Within and around $R_\text{ein}$ they are consistent with each other, even though they were independently derived.
+They do not agree with the mass-follows-light-like result by \citet{SWELLSV} and in Section \ref{sec:results_JAM_SB_MfL} we showed that ``mass-follows-light'' is not a good model for J1331.
 
 Overall, we were not able to find a consistent explanation for J1331's central $v_\text{rms}$ dip.
-It cannot be due to tangential velocity anisotropy in the center alone (see Section \ref{sec:results_JAM_SB}, Figure \ref{fig:JAM_modelA2}).
-It also cannot be explained by a strong contribution of DM inside the bulge together with a moderate tagential velocity anisotropy, because the corresponding DM halos would still be too massive to fit the data in the outer regions (see Section \ref{sec:results_JAM_NFW}, Figure \ref{fig:modelB4_vrms}]).e
-
-Another feature in the stellar kinematics, that none of our JAM models was able to reproduce in the slightest and which we therefore excluded in the modelling, was the dip in $v_\text{rms}$ around $\sim 6''$, which occurs around the transition from bulge to disk (see Figures \ref{fig:F814W} and \ref{fig:kinematics}).
+It cannot be due to tangential velocity anisotropy in the center alone (see Section \ref{sec:results_JAM_SB_MfL}, Figure \ref{fig:JAM_modelA2}).
+It also cannot be explained by a strong contribution of DM inside the bulge together with a moderate tagential velocity anisotropy, because the corresponding DM halos would still be too massive to fit the data in the outer regions (see Section \ref{sec:results_JAM_NFW}, Figure \ref{fig:modelB4_vrms}).
+
+Another feature in the stellar kinematics that none of our JAM models was able to reproduce in the slightest and which we therefore excluded in the modelling, was the dip in $v_\text{rms}$ around $\sim 6''$, which occurs around the transition from bulge to disk (see Figures \ref{fig:F814W} and \ref{fig:kinematics}).
 %--------------------------------------------
@@
 %--------------------------------------------
-%Why we think that J1331 had a merger
 J1331 has a large counter-rotating stellar core within $\sim 2''$. This suggests a process in J1331's past in which two components with angular momenta oriented in opposite directions were involved.
 
-%Gas accretion - no!
 Accretion of gas on retrograde orbits and subsequent star formation could lead to a younger and counter-rotating stellar population.
@@
 
-%Mergers - yes!
 Galaxy mergers are another possible scenario.
 Major mergers can form kinematically decoupled cores (KDCs) (e.g., \citealt{2011MNRAS.414.2923K,2015ApJ...802L...3T}), if they include large amounts of gas \citep{2010ApJ...723..818H}.
-During a minor merger, the dense nucleus of a satellite galaxy on a retrograde orbit could survive the dissipationless accretion and spiral to the core due to tidal friction (e.g., \citealt{1984ApJ...287..577K,1988ApJ...327L..55F}).
-
-%Merger + color gradient
-Usually ellipticals and the bulges of massive spirals appear reddest in their center and getting increasingly bluer with larger radii.
+During a minor merger, the dense nucleus of a satellite galaxy on a retrograde orbit could survive the dissipationless accretion and spiral to the galaxy's core due to tidal friction (e.g., \citealt{1984ApJ...287..577K,1988ApJ...327L..55F}).
+
+Usually ellipticals and the bulges of massive spirals appear reddest in their center and get increasingly bluer with larger radii.
 Mergers can reverse this behaviour by inducing the creation of young stellar populations in the remnant's center.
 Major mergers can trigger star formation bursts (e.g., \citealt{2008gady.book.....B}, \S 8.5.5).
-After a minor merger the satellite's stellar population now residing in the remnant's core is in general younger than the progenitor's bulge \citep{1996AJ....112..839C,2010MNRAS.404.1775T} .
-The different stellar populations in a merger remnant can be associated with different $\Upsilon_*$ and in special cases they even show up as a reverse colour gradient within the bulge in photometry \citep{1990ApJ...361..381B, 1997ApJ...481..710C}.
-
-%Color gradient in J1331
+After a minor merger the satellite's stellar population now residing in the remnant's core is in general younger than the massive progenitor's bulge \citep{1996AJ....112..839C,2010MNRAS.404.1775T}.
+The different stellar populations in a merger remnant can be associated with different $\Upsilon_*$ and in rare cases they even show up as a reverse colour gradient within the bulge in photometry \citep{1990ApJ...361..381B, 1997ApJ...481..710C}.
+
 Even though investigation of the photometry of J1331 did not reveal a distinct blue core in J1331, we cannot fully exclude the possibility that J1331 has such a $\Upsilon_*$ gradient (see discussion in Sections \ref{sec:results_JAM_SB_MfL} and \ref{sec:results_JAM_SB_gradient}).
@@
 
-Another way how galaxy encounters can can modify the structure of galaxies is the excitation of warps \citep{1991wdir.book.....C,2013pss5.book..923S}.
+Another way how galaxy encounters can modify the structure of galaxies is the excitation of warps \citep{1991wdir.book.....C,2013pss5.book..923S}.
 Warps lead to a twist in the projected kinematic major axis with radius, which is then also misaligned with the photometric major axis (\citealt{1998gaas.book.....B}, \S 8.2.4).
@@
 Furthermore, learning more about different stellar populations in J1331 would lead to valuable constraints for the modelling.
-While a quick investigation of the photometric colour profile did not reveal obvious colour gradients in J1331's bulge, there could be still stellar $\Upsilon_{I,*}$ variations due to age of metallicity differences.
+While a quick investigation of the photometric colour profile did not reveal obvious colour gradients in J1331's bulge, there could be still stellar $\Upsilon_{I,*}$ variations due to age or metallicity differences.
 Existing major axis spectroscopy and/or future IFU data could be employed (i) to investigate absorption line indices to confirm (or contradict) the existence of $\Upsilon_{I,*}$ gradients and (ii) to perform stellar population analyses to constrain $\Upsilon_{I,*}$ reliably and independently of kinematics.
 
-Future modelling approaches should fit dynamics (stellar and gas kinematics from) simultaneously with the gravitational lensing (image positions, shape and even flux ratios) in a similar fashion to \citet{SWELLSIV}.
+Future modelling approaches should fit dynamics (stellar and gas kinematics) simultaneously with the gravitational lensing (image positions, shape and even flux ratios) in a similar fashion to \citet{SWELLSIV}.
 To also model the extent, shape and flux of the lensing images, the method by \citet{2004ApJ...611..739T,2003ApJ...590..673W} could be employed, which models the surface brightness distribution of the images and source on a pixelated grid.
@@
 
-All of the would lead to a much better understanding of J1331's structure and mass distribution and therefore answer questions on how mergers might modify spiral galaxies.
+All of the above would lead to a much better understanding of J1331's structure and mass distribution and therefore answer questions on how mergers might modify spiral galaxies.
 %--------------------------------------------
@@
 In our lensing approach we fitted a scale-free galaxy model to the lensing image position.
-This constrained the Einstein radius to within 2\% ($R_\text{ein}=(0.91\pm0.02)''\simeq(1.83\pm0.04)~\text{kpc}$), and the Einstein mass to within 4\% ($M_\text{ein} = (7.8\pm0.3) \cdot 10^{10} M_\odot$), consistent with results by \citet{SWELLSIII}.
+This constrained the Einstein radius to within 2\% ($R_\text{ein}=(0.91\pm0.02)'' \hat{=}(1.83\pm0.04)~\text{kpc}$), and the Einstein mass to within 4\% ($M_\text{ein} = (7.8\pm0.3) \cdot 10^{10} M_\odot$), consistent with results by \citet{SWELLSIII}.
 The recovered mass distribution agrees also very well with the shape of the observed lensing images.
@@
 We also fitted mass models with and without NFW halo to the stellar kinematics within $R'=3.5~\text{kpc}$.
-From this we deduced that a mass-follows-light model with constant total mass-to-light ratio is not a good model for J1331---not even in the inner regions.
+From this we deduced that a mass-follows-light model with constant total mass-to-light ratio and velocity anisotropy is not a good model for J1331---not even in the inner regions.
 To describe the observed stellar kinematics we either require a strong contribution of a DM halo already in the bulge, or a strongly varying stellar mass-to-light ratio.
@@
 While both our independent mass models are consistent with each other within $\sim R_\text{eff}$, they do not agree with previous findings by \citet{SWELLSV}, nor the data at large radii.
-We attribute this to the fact \citet{SWELLSV} derived mass constraints from kinematics in the outer regions only, while we focussed on the inner regions in detail.
+We attribute this to the fact that \citet{SWELLSV} derived mass constraints from kinematics in the outer regions only, while we focussed on the inner regions in detail.
 We speculate that a merger might have modified the kinematic structure and/or mass distribution of J1331 such that crucial model assumptions are not valid anymore.

### 2016-01-29 archive/v3/docs_v3/data_v3.02.tex
Cleaned up (files are moved to archive now)

--- 2015-11-20 docs/data_v3.02.tex
@@
 They obtained long-slit spectra along J1331's major-axis with the Low Resolution Imaging Spectrograph (LRIS) on the Keck I 10m telescope.
-The width of the slot was $1''$ and the seeing conditions had a FWHM of $\sim 1.1''$.
-Spectra for spatial bins of different widths along the major axis were extracted.
-They measured line-of-sight stellar rotation velocities ($v_\text{rot}$) and stellar velocity dispersion ($\sigma$) by fitting Gaussian line profiles to emission \Wilma{[TO DO: Check if really emission lines or, more likely, absorption lines]} lines in these spectra \Wilma{[TO DO: Find out which lines]}.
-Gas kinematics were extracted from fits to H$\alpha$ and NII lines, as tracers for ionized gas.
-\\The stellar kinematics, $v_\text{rot}$, $\sigma$ and $v_\text{rms}^2=v_\text{rot}^2 + \sigma^2$ are shown in Figure \ref{fig:kinematics}.
+The width of the slit was $1''$ and the seeing conditions had a FWHM of $\sim 1.1''$.
+1D Spectra for spatial bins of different widths along the major axis were extracted.
+They measured line-of-sight stellar rotation velocities ($v_\text{rot}$) and stellar velocity dispersion ($\sigma$) from the spectrum containing the absorption lines Mgb (5177 \AA) and FeII (5270, 5335 and 5406 \AA) (analogous to \citealt{SWELLSII}).
+Gas kinematics were extracted from Gaussian line profile fits to H$\alpha$ (6563 \AA) and [NII] (6583 and 6548 \AA) emission lines, as tracers for ionized gas.
+
+The stellar kinematics, $v_\text{rot}$, $\sigma$ and $v_\text{rms}^2=v_\text{rot}^2 + \sigma^2$ are shown in Figure \ref{fig:kinematics}.
 The rotation curve reveals a counter-rotating core within $2''\simeq$ 4 kpc.
-Outside of $\sim 3.5''$ there is a steep drop in the dispersion, which is expected at the boundary between the pressure supported bulge and the rotationally supported disk, which appears around this radius in the F450W filter in Figure \ref{fig:F450W}.
+Outside of $\sim 3.5''$ there is a steep drop in the dispersion.
+This could indicate the boundary between the pressure supported bulge and the rotationally supported disk, which appears around this radius in the F450W filter in Figure \ref{fig:F450W}.
 However, in the brighter F814W filter in Figure \ref{fig:F814W} the large reddish bulge extends out to $\sim5''$.
-\\Inside of $\sim 4''$, the data appears to be symmetric, outside of this the assumption of axisymmetry seems not to be valid anymore, considering the data.
+
+Inside of $\sim 4''$, the data appears to be symmetric, outside of this the assumption of axisymmetry seems not to be valid anymore, considering the data.
 We add $-2.3~\text{km s}^{-1}$ to the $v_\text{rot}$ to ensure $v_\text{rot}(R'=0) \sim 0$ as a possible correction term for a misjudgement of the systemic velocity.
@@
 Another reason to restrict to modelling on the bulge region is that our MGE in Table \ref{tab:MGEF814W} is only a good representation of J1331's F814W light distribution inside $\sim 5''$.
-
- \Wilma{[TO DO: Maybe mention the following details better in the data section....
-"Sufficiently inclined galaxies were picked by eye.
-Follow-up high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) was performed to confirm their lensing status \citep{SWELLSI}."]}

### 2016-01-29 archive/v3/docs_v3/discussion_ML_v3.03.tex
Cleaned up (files are moved to archive now)

--- 2015-12-10 docs/discussion_ML_v3.03.tex
@@
 Some of the ambiguities in recovering J1331's matter distribution could be resolved by learning more about stellar populations with different IMFs in J1331.
-In particular, a sophisticated guess for the stellar mass-to-light ratio in the bulge could be compared to our very reliable measurement of the total mass-to-light ratio inside the Einstein radius (see Table \ref{tab:einsteinML}).
+In particular, a sophisticated guess for the stellar mass-to-light ratio in the bulge could be compared to our very reliable measurement of the total mass-to-light ratio inside the Einstein radius $\Upsilon_\text{I,tot}^\text{ein} = 5.56 \Upsilon_{I,\odot}$.
 This would then either support or contradict the presence of a significant amount of DM in the bulge.
@@
 Transformed to a stellar I-band mass-to-light ratio, their results would correspond to $\Upsilon_\text{I,*}^\text{sal} = 4.7 \pm 1.2$ (see Table \ref{tab:previousresults}).
-This is not too far from $\Upsilon_\text{I,*} = 4.2 \pm 0.2$ (see Table \Wilma{[TO DO]}), which we found when including a NFW halo in the JAM modelling.
+This is not too far from $\Upsilon_\text{I,*} = 4.2 \pm 0.2$ (see Table \ref{tab:modelB4_bestfit}), which we found when including a NFW halo in the JAM modelling.
 

### 2016-01-29 archive/v3/docs_v3/discussion_kinematics_v3.03.tex
Cleaned up (files are moved to archive now)

--- 2015-12-10 docs/discussion_kinematics_v3.03.tex
@@
 (c) Mass-follows-light model, which uses the F814W surface brightness in Table \ref{tab:MGEF814W} and the mass-to-light ratio in the Einstein radius, $\Upsilon^\text{ein}_\text{I,tot} = 5.56$, to generate a mass distribution, as in Figure \ref{fig:lenscomparelight} (orange line).
-(d) Model from gas kinematics and Einstein mass found by \citet{SWELLSV} (their Figure 2, best model with 68\% confidence region) (blue lines).
-\Wilma{[TO DO: In Plot, change symbol for M/L einstein and use full number.
-Mass follows light curve orange.
-Dutton blue.]}}
+(d) Model from gas kinematics and Einstein mass found by \citet{SWELLSV} (their Figure 2, best model with 68\% confidence region) (blue lines).}
   \label{fig:vcirc_comparison}
@@
 
-In Figure \ref{fig:vcirc_comparison} we compare the circular velocity curve found by \citet{SWELLSV} with a mass-follows-light model scaled to fit our Einstein mass (by multiplying the light distribution in Table \Wilma{[TO DO]} with $\Upsilon_\text{I,tot}^\text{ein} = 5.6$).
+In Figure \ref{fig:vcirc_comparison} we compare the circular velocity curve found by \citet{SWELLSV} with a mass-follows-light model scaled to fit our Einstein mass (by multiplying the light distribution in Table \ref{tab:MGEF814W} with $\Upsilon_\text{I,tot}^\text{ein} = 5.56$).
 Within $R < 5''$ they agree with each other.
@@
 The dynamical models used stellar kinematics inside $R' \simeq 3.5''$ \Wilma{[TO DO: Check]}.
-We compare the lens mass model's $v_\text{circ}$ (for $\alpha=1.0\pm 0.1$) with the NFW JAM model (Table \Wilma{[TO DO]}) in Figure \ref{fig:vcirc_comparison} as well.
+We compare the lens mass model's $v_\text{circ}$ (for $\alpha=1.0\pm 0.1$) with the NFW JAM model (Table \ref{tab:modelB4_bestfit}) in Figure \ref{fig:vcirc_comparison} as well.
 Within and around $R_\text{ein}$ they are consistent with each other, even though they where independently derived.

### 2016-01-29 archive/v3/docs_v3/discussion_merger_v3.04.tex
Cleaned up (files are moved to archive now)

--- 2016-01-28 LensingPaper_draft_v3.05.tex
@@
-\documentclass[useAMS,usenatbib]{mnras}
+\subsection{On J1331's possible merger history and modelling failures}
 
-%_____GENERAL PACKAGES_____
-\usepackage{amsmath}	%for \text{} in math mode
-\usepackage{amssymb}	%for symbols
-
-%_____FIGURES_____
-\usepackage{graphicx}	%for including images
-\usepackage{float}	%for [Hhtb] etc of figures
-\usepackage{grffile}    %for using underscores in figure filenames
-\usepackage{subcaption} %for having sub-captions in figures with multiple panels
-\usepackage{placeins} %for \FloatBarrier, which forces all figures to be printed before continuing
-
-%_____SYMBOLS_____
-\usepackage{ mathrsfs } %for slanted letters in math mode
-
-%_____FORMAT_____
-%\setcounter{secnumdepth}{3}	%depth of section numbering
-\usepackage{hyperref} %ready-to-lick referencing
-
-%_____MACROS______
-\newcommand*\diff{\mathop{}\!\mathrm{d}}
-\newcommand*\Diff[1]{\mathop{}\!\mathrm{d^#1}}
-%\newcommand{\vect}[1]{\boldsymbol{#1}} % Uncomment for BOLD vectors.
-\newcommand{\vect}[1]{\vec{#1}} % Uncomment for ARROW vectors.
-\usepackage[usenames,dvipsnames]{xcolor}
-\newcommand{\Wilma}[1]{\textcolor{Magenta}{#1}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\title[A spiral galaxy's mass distribution uncovered]{A spiral galaxy's mass distribution uncovered through lensing and dynamics}
-\author[W.H. Trick, G. van de Ven and A.A. Dutton]{Wilma H. Trick$^{1}$\thanks{E-mail:
-trick@mpia.de}, Glenn van de Ven$^{1}$ and Aaron A. Dutton$^{1}$\\
-$^{1}$Max-Planck-Institute for Astronomy, K\"{o}nigstuhl 17, 69117 Heidelberg, Germany}
-\begin{document}
-
-\date{Accepted ???. Received ???; in original form ???}
-
-\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2015}
-
-\maketitle
-
-\label{firstpage}
-
-%--------------------------------------------
-\begin{abstract}
-We investigate the matter distribution of a spiral galaxy with counter-rotating stellar core, SDSS J1331+3628 (J1331), independently with gravitational lensing and stellar dynamical modelling.
-By fitting a gravitational potential model to a quadruplet of lensing images around J1331's bulge, we tightly constrain the mass inside the Einstein radius $R_\text{ein}=(0.91\pm0.02)''(\simeq1.83\pm0.04~\text{kpc})$ to within 4\%: $M_\text{ein} = (7.8\pm0.3) \cdot 10^{10} M_\odot$.
-We model observed long-slit major axis stellar kinematics in J1331's central regions by finding Multi-Gaussian Expansion (MGE) models for the stellar and dark matter distribution that solve the axisymmetric Jeans equations.
-The lens and dynamical model are independently derived, but in very good agreement with each other around $\sim R_\text{ein}$.
-We find that J1331's center requires a steep total mass-to-light ratio gradient.
-A dynamical model including a NFW halo (with virial velocity $v_{200} \simeq 240 \pm 40~\text{km s}^{-1}$ and concentration $c_{200} \simeq 8 \pm 2$) and moderate tangential velocity anisotropy ($\beta_z \simeq -0.4 \pm 0.1$) can reproduce the signatures of J1331's counter-rotating core and predict the stellar and gas rotation curve at larger radii.
-However, our models do not agree with the observed velocity dispersion at large radii.
-We speculate that the reason could be a non-trivial change in structure and kinematics due to a possible merger event in J1331's recent past.
-\end{abstract}
-%--------------------------------------------
-
-\begin{keywords}
-gravitational lensing: strong -- stars: kinematics and dynamics -- galaxies: kinematics and dynamics -- galaxies: photometry -- galaxies: structure
-\end{keywords}
-
-%--------------------------------------------
-\section{Introduction}
-%--------------------------------------------
-
-%--------------------------------------------
-Gravitational lensing and dynamical modelling provide independent constraints on the mass distribution of galaxies.
-Combining them allows for valuable cross-checking opportunities to disentangle the galactic stellar and dark matter (DM) content.
-
-Cosmological simulations suggest that cold DM forms cuspy halos following a Navarro-Frenk-White (NFW) profile \citep{1996ApJ...462..563N}.
-However, the existence of central DM density cusps in massive galaxies depends strongly on the stellar mass-to-light ratio (e.g., \citealt{2011MNRAS.416..322D}) and DM dominated dwarf galaxies even favour DM halos with cores (e.g., \citealt{1994Natur.370..629M,2001ApJ...552L..23D}).
-This discrepancy, known as the core-cusp problem, might be resolved by galaxy formation processes such as mergers and outflows (e.g., \citealt{2001ApJ...560..636E,2012MNRAS.421.3464P}).
-
-Determining the overall mass distribution in massive galaxies and separating the DM from the stellar mass components is therefore a crucial step in better understanding the structure and formation of galaxies and nature of DM.
-
-Massive galaxies can act as gravitational lenses, deflect the light of background sources and give rise to multiple images.
-This strong gravitational lensing tightly constrains the projected total mass of the lens galaxy inside $\sim 1''$ (e.g., \citealt{2010ARA&A..48...87T}).
-
-The mass profile at larger galactocentric radii can be probed by gas rotation curves that directly measure the galaxy's circular velocity profile (e.g., \citealt{1980ApJ...238..471R}).
-However, due to its dissipative nature gas motions are very sensitive to disturbances by, e.g., spiral arms and bars (e.g., \citealt{2004dad..book.....S}).
-
-Because stars are dissipationless dynamical tracers and present almost everywhere in the galaxy, stellar dynamical modelling can complement mass constraints from lensing at small and gas motions at large radii.
-As stellar motions are complex---a bulk rotation around one principal axis combined with random motions in all coordinate directions---\citep{2008gady.book.....B}, full dynamical modelling of rotation, dispersion and velocity anisotropies is needed to deduce the matter distribution.
-
-The Sloan WFC Edge-on Late-type Lens Survey (SWELLS, WFC = Wide field camera) \citep{SWELLSI,SWELLSII,SWELLSIII,SWELLSIV,SWELLSV,SWELLSVI} is dedicated to find and investigate spiral galaxies, which are (i) strong gravitational lenses and (ii) observed almost edge-on, such that rotation curves can be easily measured.
-By combining lensing and dynamical modelling, degeneracies inherent in both methods can be broken.
-
-One of the SWELLS galaxies is the massive spiral SDSS J1331+3628, to which we refer as J1331 in the remainder of this work.
-It has bluish spiral arms and a large reddish bulge (see Figures \ref{fig:F450W} and \ref{fig:F814W}), which is superimposed by a quadruplet of extended bluish images approximately at a distance of $1''$ from the galaxy center (see Figure \ref{fig:lens_just_imgpos}).
-The lensed object might be a star-forming blob of a background galaxy.
-J1331 stands out of the SWELLS sample because of its large counter-rotating core (see Figure \ref{fig:kinematics}), which might be an indication that J1331 underwent a merger in its recent past.
-
-\citet{SWELLSI} confirmed that J1331 is a strong gravitational lens, measured its apparent brightness and estimated the stellar masses of disk and bulge.
-The lensing properties of J1331 were first analysed by \citet{SWELLSIII}.
-\citet{SWELLSV} measured the gas and stellar kinematics along the major axis and deduced J1331's mass profile from the gas rotation curve at large radii and total mass inside the Einstein radius from gravitational lensing, focusing mostly on the outer regions of J1331.
-
-The goal of this work is to complement the previous studies of J1331 by an in-depth analysis of the matter distribution in J1331's inner regions.
-We use stellar dynamical modelling in addition to lensing constraints, similar to a study of the Einstein Cross by \citet{GlennEC}.
-We attempt to disentangle the stellar and DM components and test if employed axisymmetric Jeans models work also in the presence of a counter-rotating core.
-Ideally, this work on J1331 could also help understanding how mergers modify the mass distribution of a galaxy.
-
-This paper is organized as follows: Section \ref{sec:data} summarizes the data, Section \ref{sec:Modelling} gives an overview of the modelling techniques used in this work, and Section \ref{sec:Results} presents our results on the surface photometry of J1331 using Multi-Gaussian expansions (Section \ref{sec:MGE_results}), constraints from lensing (Section \ref{sec:results_lensing}) and Jeans modelling based on the surface brightness only (Section \ref{sec:results_JAM_SB}) and including a NFW DM halo (Section \ref{sec:results_JAM_NFW}).
-Finally, Section \ref{sec:Discussion} uses these results to discuss J1331's stellar mass-to-light ratio, central kinematics, possible merger history and starting points for future work.
-%--------------------------------------------
-
-%============================================
-\begin{figure*}
-\centering
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[width=.9\linewidth]{fig/first_glimpse_450.ps}
-  \caption{J1331 in the F450W filter.}
-  \label{fig:F450W}
-\end{subfigure}%
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[width=.9\linewidth]{fig/first_glimpse_814.ps}
-  \caption{J1331 in the F814W filter.}
-  \label{fig:F814W}
-\end{subfigure}
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[width=.9\linewidth]{fig/lens_imgpos.ps}
-  \caption{Lensing images around the galaxy center.}
-  \label{fig:lens_just_imgpos}
-\end{subfigure}%
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[width=.9\linewidth]{fig/stellar_kinematics_data.ps}
-  \caption{Stellar kinematics by \citet{SWELLSV}.}
-  \label{fig:kinematics}
-\end{subfigure}
-\caption{Hubble Space Telescope (HST) images and stellar kinematics of the galaxy SDSS J1331+3628 (J1331), which has a large counter-rotating core and whose bulge acts as a strong lens for a bluish background source.
-\emph{Panel (a) and (b):} HST/WFPC2/WFC3 images of J1331 by \citet{SWELLSI} in two filters, F450W in panel (a) and F814W in panel (b).
-The black solid line in panel (b) shows the orientation of the major axis.
-Its length is $10''$ and it marks approximately the region within which we carry out the dynamical modelling.
-\emph{Panel (c):} Lensing images in the central region of J1331.
-An IRAF \emph{ellipse} model was fitted to and then subtracted from the galaxy's F450W surface brightness in panel (a).
-The (smoothed) residuals within the white square in panel (a) are shown in panel (c).
-The four bright blobs (A, B, C and D), which are visible in the residuals, are arranged in a typical strong lensing configuration around the center of the galaxy (G).
-(The configuration of the two additional blobs which lie approximately on a line with A, B and G does not suggest that these blobs are a lensing doublet.
-They might rather be star-forming regions of a background galaxy.) \emph{Panel (d):} Stellar kinematics along the galaxy's major axis as measured by \citet{SWELLSV}.
-Shown are line-of-sight rotation velocity $v_\text{rot}$ (top), line-of-sight velocity dispersion $\sigma$ (middle) and the root mean-square (rms) velocity $v_\text{rms} = \sqrt{v_\text{rot}^2 + \sigma^2}$ (bottom).
-The dashed line indicates the galaxy's effective half-light radius (in the F814W filter), $R_\text{eff} = 2.6'' \hat{=} 5.2~\text{kpc}$.
-The $v_\text{rot}$ curve reveals that J1331 has a counter-rotating core within $R_\text{eff}$.}
-\label{fig:specialJ1331}
-\end{figure*}
-%============================================
-
-%--------------------------------------------
-\section{Data} \label{sec:data}
-%--------------------------------------------
-
-%--------------------------------------------
-\subsection{Redshift and position}
-%--------------------------------------------
-
-%--------------------------------------------
-J1331 is located at right ascension = 202.91800$^\circ$ and declination = 36.46999$^\circ$ (epoch J2000).
-\citet{SWELLSI} found from SDSS spectra that J1331 has two redshifts inside $R'=1''$: J1331 itself has $z_d = 0.113$ and $z_s = 0.254$ is the redshift of the lensed background source \citep{SWELLSIII}.
-According to the WMAP5 cosmology \citep{WMAP5cosm}, J1331 has an angular diameter distance of 414 Mpc, which translates into a transverse scaling of $1'' \hat{=} 2.01~\text{kpc}$.
-
-%--------------------------------------------
-\subsection{HST imaging}
-%--------------------------------------------
-
-%--------------------------------------------
-We use HST imaging of J1331 by \citet{SWELLSI}.
-They performed high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) and its WF3 CCD chip.
-The images are a combination of four exposures with each an exposure time of $400~\text{sec}$ and were drizzled to a pixel scale of 1 pixel = $0.05''$.
-In particular, we use the images in the filters F450W, to identify the positions of the bluish lensing images, and F814W (I-band) to create a surface brightness model of the reddish bulge.
-
-%--------------------------------------------
-\subsection{Stellar kinematics} \label{sec:data_kinematics}
-%--------------------------------------------
-
-%--------------------------------------------
-For the dynamical modelling we use the stellar kinematics for J1331 measured by \citet{SWELLSV}.
-They obtained long-slit spectra along J1331's major-axis with the Low Resolution Imaging Spectrograph (LRIS) on the Keck I 10m telescope.
-The width of the slit was $1''$ and the seeing conditions had a FWHM of $\sim 1.1''$.
-1D spectra for spatial bins of different widths along the major axis were extracted.
-Line-of-sight stellar rotation velocities ($v_\text{rot}$) and stellar velocity dispersions ($\sigma$) were determined from the spectral region containing the absorption lines Mgb (5177 \AA) and FeII (5270, 5335 and 5406 \AA) (analogous to \citealt{SWELLSII}).
-Gas kinematics were extracted from Gaussian line profile fits to H$\alpha$ (6563 \AA) and [NII] (6583 and 6548 \AA) emission lines as tracers for ionized gas.
-
-The stellar kinematics, $v_\text{rot}$, $\sigma$ and the root-mean-square velocity $v_\text{rms}^2=v_\text{rot}^2 + \sigma^2$ are shown in Figure \ref{fig:kinematics}.
-The rotation curve reveals a counter-rotating core within $2''\hat{=}4~\text{kpc}$.
-Outside of $\sim 3.5''$ there is a drop in the dispersion.
-This could indicate the boundary between the pressure supported bulge and the rotationally supported disk, which appears around this radius in the F450W filter in Figure \ref{fig:F450W}.
-However, in the brighter F814W filter in Figure \ref{fig:F814W} the smooth reddish bulge extends out to $\sim5''$.
-
-Inside of $\sim 4''$ the data appears to be symmetric; outside of it the data suggests that the assumption of axisymmetry seems not to be valid anymore.
-We subtract $2.3~\text{km s}^{-1}$ from $v_\text{rot}$ to ensure $v_\text{rot}(R'=0) \sim 0$ as a possible correction term for a misjudgement of the systemic velocity.
-We also symmetrize the data within $4''$ and asign a minimum error of $\delta v_\text{rms} \geq 5~\text{km s}^{-1}$ to the $v_\text{rms}$ data.
-In our dynamical Jeans modelling approach, which is based on the assumption of axisymmetry, only stellar kinematics with either $R'  \lesssim 3.5''$ or $R' \lesssim 4''$ are used.
-Another reason to restrict the modelling to the bulge region is that our surface brightness model (Table \ref{tab:MGEF814W} and Figure \ref{fig:MGEinnerRegions}) is only a good representation of J1331's F814W light distribution inside $\sim 5''$.
-%--------------------------------------------
-
-%--------------------------------------------
-\section{Modelling} \label{sec:Modelling}
-%--------------------------------------------
-
-%--------------------------------------------
-\subsection{Surface brightness model} \label{sec:MGE_theo}
-%--------------------------------------------
-
-%--------------------------------------------
-\subsubsection{Multi-Gaussian Expansion (MGE)}
-%--------------------------------------------
-
-%--------------------------------------------
-MGEs are used to parametrize the observed surface brightness (or projected total mass) of a galaxy as a sum of $N$ 2-dimensional, elliptical Gaussians \citep{1991ApJ...366..599B,1992A&A...253..366M,1994A&A...285..723E,1999MNRAS.303..495E}.
-This work makes use of the algorithm and code\footnote{The IDL code package for fitting MGEs to images by \citet{Cap02} is available online at \url{http://www-astro.physics.ox.ac.uk/~mxc/software}.
-The version from June 2012 was used in this work.} by \citet{Cap02}.
-We assume all Gaussians to have the same center and position angle $\phi$, i.e., the orientation of the Gaussians' major axis measured from North through East in the polar coordinate system $(R',\theta')$ on the plane of the sky.
-Then a surface brightness model can be expressed as
-\begin{eqnarray}
-I(R',\theta') &=& \sum_{i=1}^{N} I_{0,i} \exp\left[ - \frac{1}{2\sigma_i^2} \left(x^{'2} + \frac{y^{'2}}{q_i^{'2}}\right)\right]\label{eq:MGEgeneral}\\
-\text{with } I_{0,i} &=& \frac{L_i}{2\pi \sigma_i^2 q'_i}\label{eq:centralItotalL}\\
-\text{and } x'_i &=& R' \cos(\theta' - \phi)\nonumber\\
-y'_i &=& R' \sin(\theta' - \phi),\nonumber
-\end{eqnarray}
-where $I_{0,i}$ is the central surface brightness of each Gaussian, $L_i$ its total luminosity, $\sigma_i$ its dispersion along the major axis and $q'_i$ the axis ratio between the elliptical Gaussian's major and minor axis.
-
-\subsubsection{Convolution with the point spread function (PSF)}
-
-We can also expand the telescope's PSF as a sum of circular Gaussians,
-\begin{equation}
-\text{PSF}(x',y') = \sum_j \frac{G_j}{2 \pi \delta_j^2} \exp\left[- \frac{1}{2 \delta_j^2} \left({x'}^2 + {y'}^2 \right)\right], \label{eq:PSFgeneral}
-\end{equation}
-where $\sum_j G_j = 1$ and $\delta_j$ are the dispersions of the circular PSF Gaussians.
-
-The observed surface brightness distribution is a convolution of the intrinsic surface brightness in Equation \eqref{eq:MGEgeneral} with the PSF in Equation \eqref{eq:PSFgeneral}: $(I \ast \text{PSF}) (x',y')$ is then again a sum of Gaussians and can be directly fitted to an image of the galaxy in question.
-
-\subsubsection{Deprojection}
-
-$I(R',\theta')$ describes the intrinsic, to 2D projected light distribution or surface density of the galaxy.
-Under the assumption that the galaxy is oblate and axisymmetric, and given the inclination angle $i$ of the galaxy with respect to the observer, MGEs allow an analytic deprojection of the 2-dimensional MGE to get a 3-dimensional axisymmetric light distribution or density $\nu(R,z)$ for the galaxy,
-\begin{equation}
-\nu(R,z) = \sum_i \nu_{0,i} \exp \left[-\frac{1}{2\sigma_i}\left(R^2 + \frac{z^2}{q_i^2} \right) \right], \label{eq:deprojMGE}
-\end{equation}
-where $R$ is the distance from the galaxy's short axis and $z$ the height above the galactic plane.
-The flattening $q_i$ of each axisymmetric 3D Gaussian and its central density $\nu_{0,i}$ follow from the observed 2D axis ratio $q'_i$ and surface density $I_{0,i}$ as
-\begin{eqnarray*}
-q_i^2 &=& \frac{q_i'^2 - \cos^2 i}{\sin^2 i}\\
-\nu_{0,i} &=& \frac{q_i' I_{0,i}}{q_i \sqrt{2 \pi \sigma_i^2}}.
-\end{eqnarray*}
-%--------------------------------------------
-
-%--------------------------------------------
-\subsection{Strong gravitational lens model} \label{sec:lensing_theo}
-%--------------------------------------------
-
-%--------------------------------------------
-\subsubsection{Strong lensing formalism}
-%--------------------------------------------
-
-%--------------------------------------------
-A gravitational lens is a mass distribution whose gravitational potential $\Phi$ acts as a lens for light coming from a source positioned somewhere on a plane behind the lens.
-We summarize the basic formalism (see also \citealt{1992grle.book.....S,1996astro.ph..6001N,2006glsw.conf....1S,2006glsw.conf...91K,2010ARA&A..48...87T}).
-The angular diameter distance from the observer to the lens is $D_d$, to the source plane $D_s$, and the distance between the lens and source plane is $D_{ds}$.
-The deflection potential of the lens is its potential projected along the line of sight $z'$ and rescaled to
-\begin{equation}
-\psi(\vect{\theta}) := \frac{D_{ds}}{D_d D_s} \frac{2}{c^2} \int \Phi(\vect{r}=D_d \vect{\theta},z') {\ \mathrm d} z', \label{eq:psidef}
-\end{equation}
-where $\vect{\theta}\equiv(x',y')$ is a 2-dimensional vector on the plane of the sky. The light from the source at $\vect{\beta} \equiv (x_s',y_s')$ is deflected according to the lens equation
-\begin{equation}
-\vect{\beta} = \vect{\theta}_i - \left.\vect{\nabla}_\theta \psi(\vect{\theta})\right|_{\vect{\theta}_i} \label{eq:lenseqpot}
-\end{equation}
-into an image $\vect{\theta}_i = (x_i',y_i')$.
-The gradient of the deflection potential, $\vect{\nabla}_\theta \psi(\vect{\theta})$, is equal to the angle by which the light is deflected multiplied by $D_{ds}/D_{s}$.
-
-The total time delay of a deflected light path through $\vect{\theta}$ with respect to the unperturbed light path is given by 
-\begin{equation}
-\Delta t(\vect{\theta}) = \frac{(1+z_d)}{c} \frac{D_d D_s}{D_{ds}} \left[ \frac 12 (\vect{\theta} - \vect{\beta})^2 - \psi(\vect{\theta})\right]. \label{eq:timedelay}
-\end{equation}
- According to Fermat's principle the image positions will be observed at the extrema of $\Delta t(\vect{\theta})$.
-
-The inverse magnification tensor
-\begin{equation}
-\mathscr{M}^{-1} \equiv \frac{\partial \vect{\beta}}{\partial \vect{\theta}} \overset{(\ref{eq:lenseqpot})}{=} \left(\delta_{ij} - \frac{\partial^2 \psi}{\partial \theta_i \partial \theta_j} \right)\label{eq:magnificationtensor}
-\end{equation}
-describes how the source position changes with image position. It also describes the distortion of the image shape for an extended source and its magnification $\mu$ due to lensing according to
-$$\mu \equiv \frac{\text{image area}}{\text{source area}} = \det \mathscr{M}.$$
-Lines in the image plane for which the magnification becomes infinite, i.e., $\det \mathscr{M}^{-1} = 0$, are called critical curves.
-The corresponding lines in the source plane are called caustics.
-The position of the source with respect to the caustic detemines the number of images and their configuration and shape with respect to each other.
-
-The Einstein mass $M_\text{ein}$ and Einstein radius $R_\text{ein}$ are defined via the relation
-\begin{equation*}
-M_\text{ein} \equiv M(<R_\text{ein}) \overset{!}{=} \pi \Sigma_\text{crit} R_\text{ein}^2,
-\end{equation*}
-where $\Sigma_\text{crit} \equiv \frac{c^2}{4\pi G} \frac{D_s}{D_d D_{ds}}$ is the critical density and $M(<R_\text{ein})$ is the mass projected along the line-of-sight within $R'=R_\text{ein}$.
-$M_\text{ein}$ is similar to the projected mass within the critical curve $M_\text{crit}$.
-
-%--------------------------------------------
-\subsubsection{Lens model} 
-%--------------------------------------------
-
-%--------------------------------------------
-Following \citet{EvansWitt} we assume a scale-free model
-\begin{equation}
-\psi(R',\theta') = R^{'\alpha} F(\theta') \label{eq:scalefreemodel}
-\end{equation}
-for the lensing potential, consisting of an angular part $F(\theta')$ and a radial power-law part, with $(R',\theta')$ being again polar coordinates on the plane of the sky.
-$\alpha$ denotes the rotation curve slope of the lens and the case $\alpha = 1$ corresponds to a flat rotation curve.
-The surface density of this model is
-\begin{equation*}
-\Sigma(R',\theta')= \frac{ \Sigma_\text{crit}}{2} \left(\alpha^2 F(\theta') + \frac{\partial^2}{\partial \theta^{'2}}F(\theta')\right) R^{'\alpha-2}.
-\end{equation*}
-We expand $F(\theta')$ into a Fourier series,
-\begin{equation}
-F(\theta') = \frac{a_0}{2} + \sum_{k=1}^{\infty} \left(a_k \cos(k\theta') + b_k \sin (k\theta') \right). \label{eq:Fourieransatz}
-\end{equation}
-For this scale-free lens model the lens equation \eqref{eq:lenseqpot} becomes
-\begin{equation}
-\begin{pmatrix} x_s' \\ y_s' \end{pmatrix} = \begin{pmatrix} R'_i \cos \theta'_i - R_i^{'\alpha-1} \left(\alpha \cos \theta'_i F(\theta'_i) - \sin \theta'_i F'(\theta'_i) \right) \\ R'_i \sin \theta'_i - R_i^{'\alpha-1} \left(\alpha \sin \theta'_i F(\theta'_i + \cos \theta'_i F'(\theta'_i) \right)\end{pmatrix}\label{eq:Fourierlenseq}
-\end{equation}
-\citep{EvansWitt}, where $F'(\theta') \equiv \partial F(\theta') / \partial \theta'$.
-When we fix the slope $\alpha$, then the lens equation is a purely linear problem and can be solved numerically for the source position $(x_s',y_s')$ and the Fourier parameters $(a_k,b_k)$ given one observed image at position $(x'_i=R'_i \cos \theta'_i,y'_i=R'_i \sin \theta'_i)$.
-
-%--------------------------------------------
-\subsubsection{Model fitting}
-%--------------------------------------------
-
-%--------------------------------------------
-The free parameters of the lens model are: the source position $(x_s',y_s')$, the radial slope $\alpha$ and Fourier parameters $(a_k,b_k)$ of the lens mass distribution in Equations \eqref{eq:scalefreemodel}-\eqref{eq:Fourieransatz}.
-We want to minimize the distance between the observed image positions, $\vect{\theta}_{oi}$, and those predicted by the lensing model, $\vect{\theta}_{pi}$.
-To avoid having to solve the lens equation \eqref{eq:Fourierlenseq} for $\vect{\theta}_{pi}$, we follow \citet{1991ApJ...373..354K} and cast the calculation back to the source plane using the magnification tensor in Equation \eqref{eq:magnificationtensor} to approximate $\vect{\theta} \simeq (\partial \vect{\theta} / \partial \vect{\beta}) \vect{\beta} = \mathscr{M} \vect{\beta} $.
-The best fit lens model is then the one that minimizes
-\begin{eqnarray}
-\chi^2_\text{lens} &=& \sum_{i} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right) \left( \vect{\theta}_{pi} - \vect{\theta}_{oi} \right)\right|^2\nonumber\\
-&\simeq& \sum_{i} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right)  \left.\mathscr{M}\right|_{\vect{\theta}=\vect{\theta}_{oi}} \left( \begin{matrix} x_s' - \tilde{x}'_{si} \\ y_s' - \tilde{y}'_{si} \end{matrix} \right) \right|^2,\label{eq:chi2lens}
-\end{eqnarray}
-where $(\Delta_x,\Delta_y)$ are the measurement errors of the image positions $\vect{\theta}_{oi}$.
-$\left.\mathscr{M}\right|_{\vect{\theta}=\vect{\theta}_{oi}}$ is the magnification tensor and $(\tilde{x}'_{si},\tilde{y}'_{si})$ the source position according to the lens equation, both evaluated at the position of the $i$-th lensing image, $\vect{\theta}_{oi}$.
-Following \citet{GlennEC} we add a term
-\begin{equation}
-\chi^2_\text{shape} = \lambda \sum_{k \geq 3} \frac{\left(a_k^2 +b_k^2 \right)}{a_0^2} \label{eq:chi2shape}
-\end{equation}
-(with $\lambda$ being some weight factor) which forces the shape of the mass distribution to be close to an ellipse. The total $\chi^2$ to minimize is therefore
-\begin{equation}
-\chi^2 = \chi^2_\text{lens} + \chi^2_\text{shape} \label{eq:chi2total}
-\end{equation}
-We set $a_1 = b_1 = 0$, which corresponds to the choice of origin; in this case the center of the galaxy.
-
-To be able to constrain the slope $\alpha$ we would need flux ratios for the images as in \citet{GlennEC}.
-But the extent of the images, possible dust obscuration and surface brightness fluctuations due to microlensing events, as well as the uncertainty in surface brightness subtraction, make flux determination too unreliable and we do not include them in the fitting.
-%--------------------------------------------
-
-%--------------------------------------------
-\subsection{Axisymmetric dynamical model} \label{sec:model_JAM}
-%--------------------------------------------
-
-%--------------------------------------------
-\subsubsection{Jeans Anisotropic Models (JAM)} 
-%--------------------------------------------
-
-%--------------------------------------------
-JAM modelling assumes galaxies to be (i) collisionless (i.e., the collisionless Boltzmann equation for the distribution function $f(\vect{x},\vect{v},t)$ has to be satisfied, $\frac{\diff f(\vect{x},\vect{v},t)}{\diff t} = 0$), (ii) in a steady state ($\frac{\partial}{\partial t} = 0$), (iii) axisymmetric (best described in cylindrical coordinates $(R,z,\phi)$ and $\frac{\partial}{\partial \phi} = 0$).
-From this follow the axisymmetric Jeans equations as the vector-valued first moment of the Boltzmann equation, i.e.,
-\begin{equation*}
-\int \vect{v} \frac{\diff f}{\diff t} \Diff3 v = 0.
-\end{equation*}
-To be able to solve the Jeans equations, additional assumptions about the velocity ellipsoid tensor $\langle v_i v_j\rangle$ have to be made.
-We follow \citet{Cap08} and assume firstly that the galaxy's velocity ellipsoid is aligned with the cylindrical coordinate system, i.e., $\langle v_R v_z\rangle = \langle v_z v_\phi \rangle = \langle v_\phi v_R \rangle = 0$.
-Secondly, we assume a constant ratio between the radial and vertical second velocity moments,
-\begin{equation}
-\beta_z \equiv 1 - \langle v_z^2 \rangle / \langle v_R^2\rangle, \label{eq:bz}
-\end{equation}
-where $\beta_z$ is the velocity anisotropy parameter.
-This reduces the Jeans equations to two equations for $\langle v_z^2 \rangle$ and $\langle v_\phi^2 \rangle$ which can be solved by means of one integration,
-\begin{eqnarray}
-n \langle v_z^2 \rangle (R,z) &=& \int_0^\infty n \frac{\partial \Phi}{\partial z} \diff z \label{eq:Jeans1}\\
-n \langle v_\phi^2 \rangle (R,z) &=& R \frac{\partial}{\partial R} \left( \frac{n \langle v_z^2 \rangle}{1-\beta_z} \right) + \frac{n \langle v_z^2 \rangle}{1 - \beta_z} + R n \frac{\partial \Phi}{\partial R},\label{eq:Jeans2}
-\end{eqnarray}
-where $n(\vect{x}) \equiv \int f(\vect{x},\vect{v}) \Diff3 v$ is the number density of (stellar) tracers and $\Phi(\vect{x})$ the galaxy's gravitational potential generated by the mass density $\rho(\vect{x})$.
-
-The JAM modelling approach by \citet{Cap08} expresses the tracer and mass density in terms of MGEs (see also \citealt{1994A&A...285..723E}).
-The tracer density $n(\vect{x})$ is assumed to be proportional to the observed and deprojected brightness distribution $\nu(R,z)$ in Equation \eqref{eq:deprojMGE}.
-The mass density $\rho(R,z)$ can consist of several sets of MGEs, describing stellar and DM components.
-The MGE for $\Phi(R,z)$ is generated from the mass density MGE by integrating the Poisson equation \citep{1994A&A...285..723E}.
-Equations \eqref{eq:Jeans1} and \eqref{eq:Jeans2} together with \eqref{eq:bz} provide the velocity dispersion tensor $\langle v_i v_j \rangle(R,z) = \langle v_i^2 \rangle(R,z)$ (with $i,j \in \{ R,\phi, z\}$ and $\langle v_i v_j \rangle=0$ if $i\neq j$).
-$\langle v_i^2 \rangle$ is then rotated by the inclination angle $i$ to the coordinate system of the observer; $(x',y')$ is the plane of the sky and $z'$ the line-of-sight, where $x'$ is alinged with the galaxy's major axis.
-Taking a light-weighted projection along the line-of-sight gives a model prediction for the line-of-sight velocity second moment, which is comparable to actual spectroscopic measurements of the second velocity moment.
-Details of the derivation using the MGE formalism are given in \citet{Cap08} and in the appendix of \citet{GlennEC}.
-We therefore just give the result for the line-of-sight second velocity moment prediction from the Jeans equations,
-\begin{eqnarray}
-&&\left(I \langle v_\text{los}^2\rangle\right)(x',y')\nonumber\\
-&&= 4 \pi^{3/2} G \int_0^1 \sum_{i=1}^N \sum_{k=1}^M \nu_{0,i} \ q_k \ \rho_{0,k} \ u^2\nonumber\\
-&& \times \frac{\sigma_i^2 \ q^{2}_i \left( \cos^2 i + \frac{\sin^2 i}{1-\beta_{z,i}}\right) + \mathscr{D} \  {x'}^{2} \sin^2 i}{(1-\mathscr{C}u^2) \sqrt{(\mathscr{A} + \mathscr{B} \cos^2 i) \left[1-(1-q^{2}_k) u^2 \right]}}\nonumber\\
-&& \times \exp\left\{- \mathscr{A} \left[{x'}^{2} + \frac{(\mathscr{A}+\mathscr{B}) \ {y'}^{2}}{\mathscr{A}+\mathscr{B}\cos^2 i}\right] \right\} \diff u, \label{eq:explicitLOSvelCap}
-\end{eqnarray}
-with $N$ Gaussians describing the tracer distribution $\nu(R,z)$ and $M$ Gaussians describing the mass distribution $\rho(R,z)$, $\rho_{0,k}$ being the $k$-th mass density Gaussian evaluated at $(R=0,z=0)$ and
-\begin{eqnarray*}
-\mathscr{A} &=& \frac 12 \left(\frac{u^2}{\sigma_k^2} + \frac{1}{\sigma_i^2} \right)\nonumber\\
-\mathscr{B} &=& \frac 12 \left\{\frac{1-q^{2}_i}{\sigma_i^2 q^{2}_i} + \frac{(1-q^{2}_k)u^4}{\sigma_k^2 \left[1-(1-{q}_k^{2})u^2 \right]} \right\}\nonumber\\
-\mathscr{C} &=& 1- q^{2}_k - \frac{\sigma_i^2 q^{2}_i}{\sigma^2_k}\nonumber\\
-\mathscr{D} &=& 1 - \frac{q^{2}_i}{1-\beta_{z,i}} - \left[ \left(1-\frac{1}{1-\beta_{i,z}}\right)\mathscr{C} + \frac{1-q^{2}_k}{1-\beta_{z,i}}\right] u^2.\nonumber
-\end{eqnarray*}
-The JAM modelling code by \citet{Cap08} evaluates Equation \eqref{eq:explicitLOSvelCap} numerically for a given luminous tracer and mass distribution MGE and a given inclination.
-
-%--------------------------------------------
-\subsubsection{Data comparison} 
-%--------------------------------------------
-
-%--------------------------------------------
-As data we use stellar line-of-sight rotation velocities $v_\text{rot} \equiv \langle v_\text{los} \rangle$ and velocity dispersions $\sigma$ as described in Section \ref{sec:data_kinematics}.
-The JAM models give us a prediction for the second line-of-sight velocity moment $\langle v_\text{los}^2 \rangle$.
-The root-mean-square (rms) line-of-sight velocity $v_\text{rms}$ allows a data-model comparison by relating theses velocities according to
-\begin{equation*}
-v_\text{rms}^2 = \langle v_\text{los}^2 \rangle = v_\text{rot}^2 + \sigma^2.
-\end{equation*}
-The model in Equation \eqref{eq:explicitLOSvelCap} predicts the intrinsic $\langle v_\text{los}^2 \rangle$ at a given position on the sky, which needs then to be modified according to the mode of observation, to be comparable to the measurements.
-The measured $v_\text{rms}$ is a light-weighted mean for a pixel along the long-slit of the spectrograph, with width $L_y = 1''$ \citep{SWELLSV} and a certain given extent along the galaxy's major axis, $L_x$, i.e., for a rectangular aperture
-\begin{equation*}
-\text{AP}(x',y') \equiv \left\{ \begin{array}{ll} 1 & \text{for } -\frac{L_x}{2} \leq x' < + \frac{L_x}{2}\\
-& \text{and } - \frac{L_y}{2} \leq y' \leq + \frac{L_y}{2}  \\ 0 & \text{otherwise.} \end{array} \right.
-\end{equation*}
-The light arriving at the spectrograph itself was subject to seeing, i.e., a Gaussian with Full Width Half Maximum (FWHM) of $1.1''$ \citep{SWELLSV},
-\begin{equation*}
-\text{PSF}(x',y')\equiv\mathscr{N}(0,\text{FWHM}/2\sqrt{2\ln2}).
-\end{equation*}
-The model predictions for $\langle v_\text{los}^2 \rangle$ have therefore to be convolved with the convolution kernel
-\begin{eqnarray*}
-K(x',y') &\equiv& (\text{PSF} \ast \text{AP})(x',y') \\
-&=& \frac{1}{4} \prod_{u \in \{x',y'\}} \left[ \text{erf}\left( \frac{L_u/2 - u}{\sqrt{2}\sigma_\text{seeing}}\right) + \text{erf} \left( \frac{L_u/2 + u}{\sqrt{2} \sigma_\text{seeing}} \right) \right],
-\end{eqnarray*}
-and weighted by the surface brightness $I(x',y')$, i.e.,
-\begin{eqnarray*}
-I_\text{obs} &=& I \ast K\\
-\langle v_\text{los}^2 \rangle |_\text{obs} &=& \frac{(I \langle v_\text{los}^2\rangle) \ast K}{I_\text{obs}}.
-\end{eqnarray*}
-If provided with the convolution kernel, the JAM code\footnote{The IDL code package for Jeans Anisotropic Models (JAM) by \citet{Cap08} is available online at \url{http://www-astro.physics.ox.ac.uk/~mxc/software}.
-The version from June 2012 was used in this work.} by \citet{Cap08} performs the convolution numerically.
-We set $L_x = 0.21''$ as the width of the model pixel, and get a prediction for the actual measurements in bins of width $0.63''$, $1.26''$ and $1.89''$ \citep{SWELLSV} as light-weighted mean from each 3, 6 and 9 model pixels.
-
-%--------------------------------------------
-\subsubsection{Rotation curve}
-%--------------------------------------------
-
-%--------------------------------------------
-The intrinsic rotation curve is the first velocity moment $\langle v_\phi\rangle = \sqrt{\langle v_\phi^2 \rangle - \sigma_\phi^2}$.
-The observed rotation curve is the projection of the light-weighted contributions to $\langle v_\phi\rangle$ along the line-of-sight \citep{Cap08},
-\begin{equation*}
-I \langle v_\text{los}\rangle = \int_{-\infty}^{+\infty} \nu \langle v_\phi\rangle \cos \phi \sin i \diff z'.
-\end{equation*}
-The first velocity moments cannot be uniquely determined from the Jeans equations, which give only a prediction for the second velocity moments.
-Further assumptions are needed to separate the second velocity moments into ordered and random motion.
-\citet{Cap08} assumes that in a steady state there is no streaming velocity in $R$ direction, i.e., $\langle v_R \rangle = 0$ and therefore $\sigma_R^2 = \langle v_R^2 \rangle$.
-Then \citet{Cap08} relates the dispersions in $R$ and $\phi$ direction such that
-$$\langle v_\phi\rangle = \sqrt{\langle v_\phi^2 \rangle - \sigma_\phi^2} \equiv \kappa \sqrt{\langle v_\phi^2 \rangle - \langle v_R^2 \rangle},$$
-and the $\kappa$ parameter quantifies the rotation: $\kappa = 0$ means no rotation at all and $|\kappa| = 1$ describes a velocity dispersion ellipsoid that is a circle in the $R$-$\phi$ plane \citep{Cap08}.
-The sign of $\kappa$ determines the rotation direction.
-We can assign a constant $\kappa_k$ to every Gaussian in the MGE formalism and
-\begin{equation*}
-\nu \langle v_\phi\rangle = \left[\nu \sum_{k} \kappa_k^2 \left( [\nu\langle v_\phi^2 \rangle]_k - [\nu\langle v_R^2 \rangle]_k\right) \right]^{1/2}
-\end{equation*} 
-is then the light-weighted circular velocity curve, given the second velocity moments found from the Jeans equations.
-
-To model the counter-rotating core of J1331 with one free parameter, we employ the condition that the overall $\kappa(R)$ profile should smoothly and relatively steeply transit from $\kappa(R) = -\kappa' < 0$ at small $R$ through $\kappa(R_0) = 0$ and increase to $\kappa(R) = \kappa' > 0$ at large $R$.
-Our imposed profile is
-\begin{equation}
-\kappa(R) = \kappa' \frac{R^2 - R_0^2}{R^2 + R_0^2}. \label{eq:kappa_profile}
-\end{equation}
-We find $\kappa'$ by matching the model $\langle v_\text{los} \rangle$ with the symmetrized $v_\text{rot}$ data, where for a given $\kappa'$ the $\kappa_k$ are found from fitting the MGE generated profile $\kappa(R) = \sum_k \kappa_k \nu_k(r)/\sum_k \nu_k(r)$ to Equation \eqref{eq:kappa_profile}.
-The observed zero point is at $R'_0\approx 2''$.
-In the deprojected galactic plane the radius of zero rotation would be at a $R_0 \gtrsim 2''$, and we choose it to be at $2.2''$.
-
-%--------------------------------------------
-\subsubsection{Including a NFW halo} 
-%--------------------------------------------
-
-%--------------------------------------------
-As mentioned above, JAM modelling allows to incorporate an invisible matter component in addition to the luminous matter in the form of an MGE.
-In Section \ref{sec:results_JAM_NFW} we will include a spherical Navarro-Frenk-White (NFW) DM halo \citep{1996ApJ...462..563N} in the dynamical model.
-The classical NFW profile has the form
-\begin{equation}
-\rho_\text{NFW}(r) \propto r^{-1} \left( r+r_s \right)^{-2} \label{eq:NFWprofile}
-\end{equation}
-and two free parameters, the scale length $r_s$ and a parameter describing the total mass of the halo.
-We will use $v_\text{200}$, which is the circular velocity at the radius $r_\text{200}$ within which the mean density of the halo is 200 times the cosmological critical density $\rho_\text{crit} \equiv (2H^2)/(8\pi G)$, i.e.
-\begin{eqnarray*}
-M_\text{200} &=& M(<r_{200})\\
-\frac{M_{200}}{ \frac 43 \pi r_{200}^3} &=& 200 \rho_\text{crit}(z=0) \\
-v_\text{200} &=& \sqrt{\frac{GM_{200}}{r_\text{200}}}
-\end{eqnarray*}
-with $\rho_\text{crit}(z=0)=1.43 \cdot 10^{-7} M_\odot / \text{pc}^3$ in the WMAP5 cosmology by \citet{WMAP5cosm}.
-How much the mass is concentrated in the center of the NFW halo is given by the concentration of the NFW halo defined by
-\begin{equation}
-c_{200}\equiv r_{200} / r_s. \label{eq:NFW_c}
-\end{equation} 
-There is a close relation between the concentration and halo mass in simulations \citep{1996ApJ...462..563N}. \citet{Maccio08} found this relation for the WMAP5 cosmology to be
-\begin{equation}
-\langle \log c_{200} \rangle (M_{200}) = 0.830 - 0.098 \log \left(h \frac{M_{200}}{10^{12} M_\odot} \right) \label{eq:Maccio08}
-\end{equation}
-(their equation 10), with a Gaussian scatter of $\sigma_{\log c_{200}} = 0.105$ (their Table A2). 
-%--------------------------------------------
-
-%--------------------------------------------
-\section{Results} \label{sec:Results}
-%--------------------------------------------
-
-%============================================
-\begin{table}
-\centering
-\caption{General galaxy parameters of J1331.}
-\begin{tabular}{lllr}
-\hline
-redshift \citep{SWELLSIII}                 & $z_d$ & $0.113$ \\
-angular diameter distance & $D_d$ [Mpc] & $414$ \\
-scaling                   & $1~\text{kpc} / 1''$ & $2.006$ \\
-position angle from North          & $\phi$ [degrees] & $42.90^\circ$\\
-average axis ratio & $q'$ & $0.598$\\
-average ellipticity & $\epsilon = 1 - q'$ & $0.402$ \\
-estimated inclination & $i$ [degrees] & $70^\circ$\\
-apparent I-band magnitude & $m_\text{I}$ [mag] & $15.77$ \\
-total I-band luminosity & $L_\text{I,tot}$ [$10^{10} L_\odot$] & $5.6$ \\
-effective half-light radius & $R_\text{eff}$ [$''$] & $2.6$ \\
-& $R_\text{eff}$ [pc]& 5.2 & \\
-\hline
-\end{tabular}
-\label{tab:galaxyparameters}
-\end{table}
-%============================================
-
-%--------------------------------------------
-\subsection{Surface photometry for J1331 with MGEs} \label{sec:MGE_results}
-%--------------------------------------------
-
-%--------------------------------------------
-In this section we construct a model for the J1331's intrinsic light distribution in terms of MGEs (see Section \ref{sec:MGE_theo}).
-We use the HST image in the F814W (I-band) filter (Figure \ref{fig:F814W}) because J1331's central stellar component appears at longer wavelengths (i) smoother and more extended than in the F450W filter (Figure \ref{fig:F450W}), as it is less sensitive to young clumpy star-forming regions, (ii) much brighter than the bluish lensing images, and (iii) the imaging is less prone to extinction.
-
-%--------------------------------------------
-\subsubsection{PSF for the HST/F814W filter}
-%--------------------------------------------
-
-%--------------------------------------------
-The one-dimensional MGE in Equation \eqref{eq:PSFgeneral} is fitted to the radial profile of a synthetic image of the HST/F814W filter PSF, ignoring diffraction spikes and using the code by \citet{Cap02}.
-The MGE parameters of the normalized PSF model are given in Table \ref{tab:PSFMGEF814W}.
-
-%============================================
-\begin{table}
-\centering
-\caption{F814W PSF MGE: Parameters of the circular four-Gaussian MGE in Equation \eqref{eq:PSFgeneral} fitted to the radial profile of the synthetic HST/F814W PSF image.}
-\begin{tabular}{ccc}
-\hline
-$j$ & $G_j$ & $\delta_j$ [$''$] \\\hline
-1 & 0.184 & 0.038\\
-2 & 0.485 & 0.085\\
-3 & 0.222 & 0.169\\
-4 & 0.109 & 0.487\\\hline
-\end{tabular}
-\label{tab:PSFMGEF814W}
-\end{table}
-%============================================
-
-%--------------------------------------------
-\subsubsection{MGE for the inner regions.}
-%--------------------------------------------
-
-%--------------------------------------------
-We fit a MGE to J1331's smooth central region within $\sim 5''$ from the HST/WFPC2/WF3/F814W image (Figure \ref{fig:F814W}).
-Bright objects close to the bulge (blobs possibly belonging to the background galaxy and parts of the foreground spiral arm) were masked during the fit.
-J1331's galaxy center, position angle (with respect to North through East) and average apparent ellipticity (see Table \ref{tab:galaxyparameters}) are found from the images weighted first and second moment.
-The MGE fit splits the image in annuli with the given ellipticity and position angle and sectors of $5^\circ$ width and fits an 5-Gaussian MGE of the form in Equation \eqref{eq:MGEgeneral} convolved with the PSF MGE in Table \ref{tab:PSFMGEF814W} to it.
-The best fit MGE (PSF convolved) is compared to the data in Figure \ref{fig:MGEinnerRegions} and the corresponding parameters of the intrinsic surface brightness distribution are given in Table \ref{tab:MGEF814W}.
-The fit is a very good representation of the light distribution in the inner $5''$, but underestimates the light distribution outward.
-
-%--------------------------------------------
-\subsubsection{MGE for the outer regions}
-%--------------------------------------------
-
-%--------------------------------------------
-To get a handle on the light distribution also in the outer parts of J1331, where spiral arms dominate, we first fit a IRAF \citep{1993ASPC...52..173T} \emph{ellipse} model to the F814W image (masking the brightest blobs in the spiral arms and outer regions).
-Only then we fit a 7-Gaussian MGE to the smooth ellipse model.
-The MGE does not perfectly reproduce the flatness of the ellipse model at every radius (see Figure \ref{fig:MGEouterRegions}), but considering the spiral arm dominated outer regions of J1331, it is good enough for an approximate handling of the overall light distribution.
-
-%============================================
-\begin{figure*}
-\centering
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[width=.8\columnwidth]{fig/1331F814Wsci_MGE_M.ps}
-  \caption{MGE for J1331's inner regions.}
- \label{fig:MGEinnerRegions}
-\end{subfigure}%
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[width=.8\columnwidth]{fig/1331F814W_MGE_disk_L.ps}
-  \caption{MGE and IRAF \emph{ellipse} model for J1331's outer regions.}
- \label{fig:MGEouterRegions}
-\end{subfigure}%
-\caption{MGEs for J1331's surface brightness distribution.
-Comparison of contours with constant F814W surface brightness (orange lines) with the corresponding iso-brightness contours of the best fit MGE, convolved with the PSF in Table \ref{tab:MGEF814W}, (grey lines).
-The black line has a length of $10''$ and its orientation corresponds to the galaxy's position angle as found in Table \ref{tab:galaxyparameters}.
-For comparison the Einstein radius as found in Table \ref{tab:bestfitlensmodel}  is indicated as red dashed circle.
-\emph{Panel (a):} Central regions of J1331.
-The MGE model is a good representation of the galaxy's light distribution along the major axis within $\sim 5''$.
-Its parameters are given in Table \ref{tab:MGEF814W}.
-This MGE is used as model for the stellar tracer distribution in the dynamical Jeans modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}.
-\emph{Panel (b):} Outer regions of J1331.
-The orange lines indicate here contours of a smooth IRAF \emph{ellipse} fit to J1331 in the F814W filter; the grey lines are the corresponding best fit MGE.
-This MGE is not used for dynamical modelling, because the dynamics in the outer regions are strongly affected by non-axisymmetries (e.g., spiral arms).
-We use it, however, to estimate the galaxy's total luminosity and effective radius, and to get a prediction for the dynamics of the outer regions.}
-\end{figure*}
-%============================================
-
-%============================================
-\begin{table*}
-\centering
-\caption{Parameters of the best fit MGE to the F814W surface brightness of J1331 in Figure \ref{fig:MGEinnerRegions}.
-The fit is best inside an radius of $5''$.
-The position angle is given in Table \ref{tab:galaxyparameters}.
-This MGE is used in the dynamical modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}.
-The first column gives for each Gaussian the total F814W luminosity in Equation \eqref{eq:centralItotalL} in units of counts.
-The second column is the corresponding I-band peak surface brightness in Equation \eqref{eq:MGEgeneral} in units of a luminosity surface density.
-The third and fourth column give the dispersion and the last column the axis ratio of the Gaussian in Equation \eqref{eq:MGEgeneral}.}
-\begin{tabular}{cccccc}
-\hline
- & total luminosity  & surface density & \multicolumn{2}{c}{Gaussian dispersion} & axis ratio\\
-$i$  & $L_i$ [counts] & $I_{0,i}$ [$L_\odot$/pc$^2$] & $\sigma_i$ [$''$] & $\sigma_i$ [kpc] & $q'_i$\\\hline
-1  &     9425.96 &      20768.  &  0.051   & 0.103  & 1.00\\
-2  &    13173.0 &        3161.2 &  0.178   & 0.358  & 0.76\\
-3  &    40235.0 &        1588.2 &  0.503   & 1.008  & 0.58\\
-4  &    67755.2 &         502.25&  1.180   & 2.368  & 0.56\\
-5  &    203677. &         136.51&  3.891   & 7.805  & 0.57\\\hline
-\end{tabular}
-\label{tab:MGEF814W}
-\end{table*}
-%============================================
-
-%--------------------------------------------
-\subsubsection{Transformation into physical units}
-%--------------------------------------------
-
-%--------------------------------------------
-To transform the MGE in units of counts into physical units, we apply a simplified version of the procedure described in \citet{Holtzman}.
-
-The scaling of the drizzled HST/WFC3 images is  $S \equiv 0.05''/\text{pixel width}$ and the total exposure time $T = 1600$ sec.
-Each Gaussian in the MGE has a total F814W luminosity $L_i$ (in counts) and a central surface brightness (in counts per pixel) of
-\begin{equation*}
-C_{0,i}\text{[counts/pixel]} = \frac{L_i[\text{counts}]}{2\pi \sigma[\text{pixel}]^2 q}.
-\end{equation*}
-This is then transformed into an I-band surface brightness (in $\text{mag}\times(1'')^{-2}$) via
-\begin{equation}
-\mu_{I,0,i} \simeq -2.5 \log_{10}\left( \frac{C_{0,i}\text{[counts/pixel]}}{T[\text{sec}] \cdot S[''/\text{pixel width}]^2}\right) + Z + C + A_I, \label{eq:muI_}
-\end{equation}
-where $Z\simeq21.62~\text{mag}$ is a the zero-point from \citet{Holtzman}, updated according to \citet{Dolphin,DolphinNew}, for the photometric system of the HST/WFPC2 camera and the F814W filter, plus a correction for the difference in gain between calibration and observation.
-$C= 0.1~\text{mag}$ corrects for the finite aperture of the WFPC2; and $A_I =0.015~\text{mag}$ is the extinction in the (Landolt) I-band towards J1331, according to the NASA/IPAC Extragalactic Database (NED)\footnote{The NASA/IPAC Extragalactic Database (NED, \url{https://ned.ipac.caltech.edu/}) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.
-The data for J1331 (SDSS J133140.33+362811.9) was retrieved in October 2013.}.
-The color-dependent correction between the F814W filter and the I-band of the UBVRI photometric system is  small \citep{Holtzman} and we neglect it therefore.
-The last step is to transform the surface brightness $\mu_{I,0,i}$ (in mag) to the I-band surface density $I_{0,i}$ (in $L_\odot$/pc$^2$) of the Gaussian, i.e.,
-\begin{eqnarray*}
-I_{0,i}[L_\odot \text{pc}^{-2}] = \left( 64800/\pi\right)^2 \left(1+z_d \right)^4 10^{0.4\left(M_{\odot,I}-\mu_{I,0,i} \right)},
-\end{eqnarray*}
-where the term with $z_d$ accounts for redshift dimming and $M_{\odot,I}=4.08~\text{mag}$ is the Sun's absolute I-band magnitude \citep{1998gaas.book.....B}.
-The luminosity $L_i$[counts] and the corresponding surface brightness density $I_{0,i} [L_\odot \text{pc}^{-2}]$ of each Gaussian are given in Table \ref{fig:MGEinnerRegions}.
-
-%--------------------------------------------
-\subsubsection{Inclination}
-%--------------------------------------------
-
-%--------------------------------------------
-To estimate the inclination of J1331 with respect to the observer, we use the observed axis ratio of the flattest ellipse in the IRAF \emph{ellipse} model for J1331, which is $q'=0.42$.
-This is similar to the disk axis ratio of $q' = 0.40$ found by \citet{SWELLSI}.
-If a typical thickness of an oblate disk is around $q_0 \sim 0.2$ \citep{1958MeLu2.136....1H}, the inclination follows from
-\begin{equation*}
-\cos^2 i = \frac{q'^2 - q_0^2}{1 - q_0^2}
-\end{equation*}
-and a correction of $+3^\circ$ \citep{1988ngc..book.....T}.
-Our estimate for the inclination is therefore $i \approx 70^\circ$.
-Given this inclination, the 2D MGE models can be deprojected into three dimensions (see Section \ref{sec:MGE_theo}).
-
-%--------------------------------------------
-\subsubsection{Total luminosity and effective radius}
-%--------------------------------------------
-
-%--------------------------------------------
-J1331's total I-band luminosity is determined by summing up the luminosity contributions of all the MGE Gaussians for the outer regions (shown as grey lines in Figure \ref{fig:MGEouterRegions}).
-We find $L_\text{I,tot} \simeq 5.6 \cdot 10^{10} ~L_\odot$.
-This corresponds to an apparent magnitude of $m_I = 15.77~\text{mag}$.
-We determine the circularized effective radius $R_\text{eff}$ of J1331 from the definition $L(<R_\text{eff}) \equiv \frac 12 L_\text{tot}$ and the growth curve $L(<R')$ from the MGE model of the outer regions, where $R'$ is the projected radius on the sky.
-We find the effective radius to be $R_\text{eff} \simeq 2.6'' \hat{=} 5.2~\text{kpc}$.
-All values are summarized in Table \ref{tab:galaxyparameters}.
-%--------------------------------------------
-
-%============================================
-\begin{table}
-\centering
-\caption{Positions of the lensing images (A-D) and the galaxy center (G) in Figure \ref{fig:lens_just_imgpos}.
-The image positions were determined from the lens subtracted image for J1331 in Figure 4 of \citet{SWELLSIII}, rotated to the $(x,y)$ coordinate system in Figure \ref{fig:lens_just_imgpos}.
-The pixel scale is 1 pixel = $0.05''$ and the error of each image position is $\pm$ 1 pixel.}
-\begin{tabular}{r|rrrr|c}
-\hline
-  & A & B & C & D & G\\\hline
-$x_i$ [pixel] & 12.1 & -8.5 & 21.7 & -3.3 & 0.5 $\pm \sqrt{2}$ \\
-$y_i$ [pixel] & 16.6 & -10.4 & -0.5 & 19.2 & 0.5 $\pm \sqrt{2}$ \\
-\hline
-\end{tabular}
-\label{tab:lenspos}
-\end{table}
-%============================================
-
-%============================================
-\begin{figure}
-\centering
-  \includegraphics[width=\linewidth]{fig/lens_all_in_one.ps}
-\caption{Lensing model (Table \ref{tab:bestfitlensmodel}) found as best fit to the image positions.
-In the background we show the central region of J1331 in the F450W filter, subtracted by an IRAF \emph{ellipse} model of the F450W surface brightness and smoothed to remove noise smaller than the PSF.
-The brightness peaks of the four lensing images and the galaxy center (Table \ref{tab:lenspos}) are marked as red dots.
-For the best fit lens model we show the Einstein radius (red dotted circle) and the critical curve (red solid line), which are located in the lens plane.
-We also show the caustic (green solid line) corresponding to the critical curve and the best fit source position (green dot), which are located in the source plane.
-For $\alpha=1$ the critical curve is a contour of constant surface density of the mass model.
-The grey  lines show contours of the time delay surface given by Equation \eqref{eq:timedelay}.
-Not only the position of the extrema, but also their shape is consistent with the observed, extended images, even though we did not use information about the image shape in the analysis.}
-\label{fig:bestfitlensmodel}
-\end{figure}
-%============================================
-
-%--------------------------------------------
-\subsection{Mass distribution from lensing} \label{sec:results_lensing}
-%--------------------------------------------
-
-%--------------------------------------------
-In this section we use the gravitational lensing formalism summarized in Section \ref{sec:lensing_theo} to fit a scale-free galaxy mass model to the positions of the lensing images observed in J1331's central region.
-
-%============================================
-\begin{table*}
-\centering
-\caption{Best fit lens model (first column) found from the peak image positions in Table \ref{tab:lenspos} following the procedure described in Section \ref{sec:lensing_theo} and assuming a flat rotation curve ($\alpha = 1$).
-The second column gives the corresponding best fit mean and standard deviation derived from Monte Carlo sampling of the Gaussian uncertainties around the image positions, with the relative error given in parentheses.}
-\begin{tabular}{llrrclr}
-\hline
- &  & \multicolumn{1}{c}{lens model for} &\multicolumn{4}{c}{lens model from Monte Carlo sampling  } \\
- &  & \multicolumn{1}{c}{peak image positions}  & \multicolumn{4}{c}{of image position uncertainties}  \\ \hline
-Einstein radius      & $R_\text{ein}$ [$''$]             & $0.907$ & $0.91$  & $\pm$ & $     0.02$ & ($2\%$)\\
-Einstein mass        & $M_\text{ein}$ [$10^{10} M_\odot$]  & $7.72$  & $7.8 $  & $\pm$ & $      0.3$ & ($4\%$) \\
-Critical mass        & $M_\text{crit}$ [$10^{10} M_\odot$] & $7.87$  & $7.9$   & $\pm$ & $      0.3$ & ($4\%$)\\
-Source position      & $x_s'$ [$''$]                      & $0.095$ & $0.09 $ & $\pm$ & $     0.03$ & ($28\%$)\\
-                     & $y_s'$ [$''$]                     & $0.107$ & $0.10 $ & $\pm$ & $     0.03$ & ($27\%$)\\
-Fourier coefficients & $a_0$                               & $1.814$ & $1.82 $ & $\pm$ & $   0.04$ & (2\%)\\
-                     & $a_2$                               & $0.012$ & $ 0.011 $ & $\pm$ & $    0.004$ & (35\%)\\
-                     & $b_2$                               & $-0.057$ & $-0.06 $  & $\pm$ & $  0.01$ & (25\%)\\
-                     & $a_3$                               & $-0.0001$& $0.0000 $ & $\pm$ & $   0.0006$ & \\
-                     & $b_3$                               & $-0.0002$&$0.000 $   & $\pm$ & $  0.001$ & \\\hline
-\end{tabular}  
-\label{tab:bestfitlensmodel} 
-\end{table*}
-%============================================
-
-%============================================
-\begin{figure*}
-\centering
-\begin{subfigure}{.3\textwidth}
-  \centering
-  \includegraphics[width=.9\linewidth]{fig/lens_surface_brightness.ps}
-  \caption{Observed light distribution.}
-  \label{fig:lenscomparelight}
-\end{subfigure}%
-\begin{subfigure}{.3\textwidth}
-  \centering
-  \includegraphics[width=.9\linewidth]{fig/lens_surface_density.ps}
-  \caption{Lens model mass distribution.}
-  \label{fig:lenscomparemass}
-\end{subfigure}
-\begin{subfigure}{.3\textwidth}
-  \centering
-  \includegraphics[width=.9\linewidth]{fig/paper_lensmass_brightness_compare.ps}
-  \caption{Comparison of mass and light.}
-  \label{fig:lenscompareboth}
-\end{subfigure}
-\caption{Comparison of the observed F814W/I-band surface brightness distribution (panel (a) and orange contours) and derived mass distribution from lensing constraints (panel (b) and pink contours).
-To allow for a qualitative comparison of the contours in panel (c), the light distribution was turned into a mass distribution by multiplication with the total mass-to-light ratio inside the Einstein radius, $\Upsilon_\text{I,tot}^\text{ein} = 5.56 \Upsilon_{I,\odot}$.
-The Einstein radius is overplotted as red dotted circle.
-The uncertainties in the mass model in the second column of Table \ref{tab:bestfitlensmodel} were translated into random Monte Carlo noise in the mass contours.
-The smooth black contours correspond to the best fit model in the first column of Table \ref{tab:bestfitlensmodel}.
-We find, that the lens mass model is more roundish than the light distribution.
-The background in Panel (c) shows again the surface brightness subtracted center of the galaxy to make the lensing images visible.}
-\label{fig:lenslightcompareALL}
-\end{figure*}
-%============================================
-
-%--------------------------------------------
-\subsubsection{Image positions}
-%--------------------------------------------
-
-%--------------------------------------------
-We determine the positions of the lensing images by first subtracting a smooth model for the galaxy's surface brightness from the original image.
-As models we use MGE fits and IRAF \emph{ellipse} fits to J1331 in each the F450W and F814W filter.
-The lensing images become visible in the residuals (see Figure \ref{fig:lens_just_imgpos}).
-Because the images are extended, we use the position of the brightest pixel in each of the images.
-In addition, we consider the F450W-MGE subtracted residuals from \citet{SWELLSIII}.
-The lensing positions, as determined from the latter, are given in Table \ref{tab:lenspos}.
-The scatter of lensing positions, as determined from subtracting different brightness models from the galaxy in different filters, gives an error of $\pm 1$ pixel on the image positions.
-To the galaxy center, which we assume to be the surface brightness peak in the F450W image, we apply an error of $\pm \sqrt{2}$ pixel.
-
-Eight image position coordinates allow us to fit a lens mass model with only $<8$ free parameters.
-We therefore do not fit Fourier components $(a_k,b_k)$ with $k > 3$ in the lens mass model in Equations \eqref{eq:scalefreemodel}-\eqref{eq:Fourieransatz}.
-
-Even though the constraint from the image positions on $\alpha$ is very weak, we were however able to show that the image positions in Table \ref{tab:lenspos} are consistent with a model with flat rotation curve.
-In the following we therefore set $\alpha=1$.
-
-%--------------------------------------------
-\subsubsection{Best fit lens model} \label{sec:results_lensing_bestfit}
-%--------------------------------------------
-
-%--------------------------------------------
-We fit the lens mass model to the image positions in Table \ref{tab:lenspos} by minimizing $\chi^2 = \chi_\text{lens}^2 + \chi_\text{shape}^2$ (see Equations \eqref{eq:chi2lens}-\eqref{eq:chi2total}).
-The best fit parameters are given in the first column of Table \ref{tab:bestfitlensmodel}.
-Figure \ref{fig:bestfitlensmodel} shows the corresponding critical curve, caustic and Einstein radius, and the best fit source position.
-In this case, where $\alpha=1$, the (tangential) critical curve is also an equidensity contour of the galaxy model \citep{EvansWitt}, which appears to have an elliptical mass distribution.
-The source is located close to a cusp of the diamond-shaped caustic: a lensing configuration for which we indeed expect four images.
-Figure \ref{fig:bestfitlensmodel} also shows the (smoothed) residuals from the F450W image subtracted by an IRAF \emph{ellipse} brightness model and the contours of the best fit model's time delay surface.
-This demonstrates that, although we did not include any information about the shape of the lensing images in the fit, it is consistent with the predicted distortion for an extended source.
-
-To estimate how the uncertainties in the determination of image positions and galaxy center affect the results, we sample random positions from 2-dimensional Normal distributions with peaks and standard deviations according to Table \ref{tab:lenspos}.
-Model fits to many sampled image positions lead to probability distributions for the best fit shape parameters and Einstein quantities; peak and standard deviations are given in the second column of Table \ref{tab:bestfitlensmodel}.
-We constrain the Einstein radius to within 2\%, $R_\text{ein} = (0.91 \pm 0.02)''$ and the projected mass within the critical curve with a relative error of 4\%, $M_\text{crit} =(7.9\pm0.3)\cdot 10^{10} M_\odot$.
-Our measurement of $R_\text{ein}$ is consistent with that from \citet{SWELLSIII}, $R_\text{ein,SWELLS} = (0.96 \pm 0.04)''$ (which used a singular isothermal ellipsoid as lens mass model and the intermediate-axis convention of the critical curve as the Einstein radius).
-The relative difference between our critical mass and that of \citet{SWELLSIII}, $M_\text{crit,SWELLS} =(8.86\pm0.61)\cdot 10^{10} M_\odot$, is 13\%.
-%--------------------------------------------
-
-%============================================
-\begin{figure}
-  \centering
-  \includegraphics[height=6cm]{fig/lensing_JAM_comparision.ps}
-  \caption{Comparison (not a fit!) of the symmetrized stellar $v_\text{rms}$ data of J1331 (blue dots) with JAM models generated from mass distributions which were independently derived from lensing constraints in Section \ref{sec:results_lensing} (red lines).
-The red solid line corresponds to the lens model for a flat rotation curve ($\alpha = 1$) in Table \ref{tab:bestfitlensmodel}; the red dashed and dash-dotted lines are best fit lens models found analogously from the image positions, but for a fixed rotation curve slope of $\alpha = 1.1$ and $0.9$, respectively.
-For the JAM modelling a best fit MGE to the lens mass models were used, as well as the observed surface brightness MGE in Table \ref{tab:MGEF814W}, assuming velocity isotropy $\beta_z = 0$ and an inclination of $i = 70^\circ$.
-The most reliable constraints are around the Einstein radius (vertical red dotted line); outside of it the JAM model is just an extrapolation.}
-  \label{fig:JAM_modelL}
-\end{figure}
-%============================================
-
-%--------------------------------------------
-\subsubsection{Comparison with light distribution}
-%--------------------------------------------
-
-%--------------------------------------------
-The surface mass distribution as predicted by the best fit lens model (Table \ref{tab:bestfitlensmodel}) is shown in Figure \ref{fig:lenscomparemass}.
-We visualize the effect of the Fourier shape parameter uncertainties by introducing random noise to create a mock observation.
-From the mock image's second moment we find an average axis ratio for the lens mass model of $q_\text{lens} \simeq 0.695$, which is consistent with the one found by \citet{SWELLSIII}, $q_\text{lens,SWELLSIII} = 0.67 \pm 0.09$, while the light's average axis ratio is $q' = 0.598$ (see Table \ref{tab:galaxyparameters}).
-
-We estimate the total mass-to-light ratio within the Einstein radius $\Upsilon_\text{I,tot}^\text{ein} \equiv M_\text{ein} / L_\text{I,ein}$.
-For this, we integrate the MGE in Table \ref{tab:MGEF814W} to get the total I-band luminosity within the Einstein radius $L_\text{I,ein} = 1.40\cdot 10^{10} L_\odot$.
-The corresponding Einstein mass-to-light ratio is therefore $\Upsilon_\text{I,tot}^\text{ein} = 5.56 \Upsilon_{I,\odot}$.
-This is consistent with or slightly larger than the stellar mass-to-light ratio assuming a Salpeter initial mass function (IMF) $\Upsilon_\text{I,*}^\text{sal} = 4.7 \pm 1.2$ according to \citet{SWELLSI} and Table \ref{tab:previousresults} (see also discussion in Section \ref{sec:MLdiscussion}).
-
-We use $\Upsilon_\text{I,tot}^\text{ein}$ to transform the observed surface brightness in the F814W filter into a surface mass density (Figure \ref{fig:lenscomparelight}).
-Figure \ref{fig:lenscompareboth} then compares equidensity contours of both the predicted lens mass distribution and the observed surface brightness times $\Upsilon_\text{I,tot}^\text{ein}$.
-
-Figure \ref{fig:lenslightcompareALL} leads to the following three findings: (1)The mass predicted from lensing and the observed light distribution are oriented in the same direction (i.e., have the same position angle).
-(2) Within and around the Einstein radius, mass and light distribution have a similar elliptical shape, while further out the mass distribution is slightly rounder.
-(3) The light distribution drops faster than the mass with increasing radius (which is---at least partly---because of the assumption of a flat rotation curve).
-However, the mass distribution is only constraint around the Einstein radius and otherwise an extrapolation.
-%--------------------------------------------
-
-%============================================
-\begin{figure}
-  \centering
-  \includegraphics[height=6cm]{fig/jam_A2_vrms.ps}
-  \caption{Comparison of the symmetrized $v_\text{rms}$ data of J1331 (blue dots) with a best fit dynamical JAM model (orange line) assuming mass-follows-light and with two free parameters: $\Upsilon_\text{I,tot}^\text{dyn}$, the total constant I-band mass-to-light ratio which converts the observed surface brightness in Table \ref{tab:MGEF814W} into a mass distribution, and the velocity anisotropy parameter $\beta_z$.
-The ``best'' fit is $\Upsilon_\text{I,tot}^\text{dyn} = 4.8 \pm 0.1$ and $\beta_z = -0.5$, where the latter is however pegged at the lower limit of the allowed value range.
-This is obviously not a good model.}
-  \label{fig:JAM_modelA2}
-\end{figure}
-%============================================
-
-%--------------------------------------------
-\subsection{JAM based on surface brightness} \label{sec:results_JAM_SB}
-%--------------------------------------------
-
-%--------------------------------------------
-In this section we create dynamical models for J1331 following the procedure in Section \ref{sec:model_JAM}.
-We use the deprojected surface brightness MGE from Table \ref{tab:MGEF814W} for the tracer distribution $\nu(R,z)$ and to generate mass models $\rho(R,z)$.
-The only exception is the first test, where the mass model comes from lensing constraints.
-%--------------------------------------------
-
-%============================================
-\begin{figure*}
-\centering
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[height=6cm]{fig/jam_G_vrms.ps}
-  \caption{Comparison of $v_\text{rms}$ data and best fit model.}
-  \label{fig:JAM_modelG}
-\end{subfigure}%
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[height=6cm]{fig/jam_G_enclMass.ps}
-  \caption{Projected local mass-to-light ratio profile and enclosed mass.}
-  \label{fig:enclMass_modelG}
-\end{subfigure}
-\caption{JAM model found by fitting a galaxy model with increasing total mass-to-light ratio profile $\Upsilon_\text{I,tot}(R')$ to the symmetrized $v_\text{rms}$ data (blue dots).
-The mass distribution is generated by assigning a different mass-to-light ratio $\Upsilon_{\text{I,tot,}i}$ to each Gaussian $i$ in the light distribution MGE in Table \ref{tab:MGEF814W}.
-The $\Upsilon_{\text{I,tot,}i}$ were treated as free fit parameters.
-\emph{Panel (a):} Comparison between the stellar $v_\text{rms}$ data (blue dots) and the best fit model (green line).
-\emph{Panel (b):} Projected total mass-to-light profile $\Upsilon_\text{I,tot}(R')$ along the major axis (blue line, left axis) of the best fit model.
-The best fit mass-to-light ratios $\Upsilon_{\text{I,tot,}i}$ are plotted against $\sigma_i$ for each MGE Gaussian ($i<5$, yellow stars).
-(The Gaussians $i=4$ and $i=5$ have the same $\Upsilon_{\text{I,tot,}i}$.) Shown is also the enclosed mass inside the projected radius $R'$ on the sky, $M(<R')$ (green line, right axis).
-The enclosed mass curve is overplotted with the independent finding for the Einstein mass $\pm 4 \%$ in Table \ref{tab:bestfitlensmodel} (red dot) at the Einstein radius (red dotted line); the agreement is very good.}
-\label{fig:modelG}
-\end{figure*}
-%============================================
-
-%--------------------------------------------
-\subsubsection{JAM with lens mass model}
-%--------------------------------------------
-
-%--------------------------------------------
-We make an independent prediction for the $v_\text{rms}$ curve by evaluating Equation \ref{eq:explicitLOSvelCap} (with $\beta_z = 0$) for the lens mass model in Table \ref{tab:bestfitlensmodel} ($\alpha = 1$, flat rotation curve).
-In addition, we also calculate a  $v_\text{rms}$ curve for two lens models which were found analogously, but assumed a slightly rising (falling) rotation curve slope of $\alpha=1.1$ ($\alpha=0.9$).
-The predictions are compared with the data in Figure \ref{fig:JAM_modelL}.
-While the most reliable constraint is around $R_\text{ein}$, the agreement within $R' \sim 3''$ is still striking: The $\alpha > 1$ model recreates the observed central dip, while the $\alpha = 1$ model fits the wings around $R_\text{eff}$.
-This is in concordance with observations in other galaxies.
-For $R'> R_\text{eff}$ we would expect $\alpha<1$---and the lensing model for $\alpha=0.9$ has indeed a slightly dropping $v_\text{rms}$ around $R_\text{eff}$, like the data.
-A definite comparison in this regime is however difficult as the lens models are just extrapolations outside of $R_\text{ein}$.
-While our lensing model assumes $\alpha(R')=\text{const}$, Figure \ref{fig:JAM_modelL} suggests, that a model with variable $\alpha(R')$ could fit even better.
-Overall the lensing model is in very good agreement with the $v_\text{rms}$ data within $R' \sim 3''$---even though it was derived completely independently.
-%--------------------------------------------
-
-%--------------------------------------------
-\subsubsection{JAM with "mass-follows-light" and velocity anisotropy} \label{sec:results_JAM_SB_MfL}
-%--------------------------------------------
-
-%--------------------------------------------
-The first JAM model that we fit to the observed $v_\text{rms}$ within $R'<5''$ is a mass-follows-light model.
-Mass-follows-light models are often used in dynamical JAM modelling (e.g., \citealt{GlennEC,Cap06}) and generate a mass distribution by multiplying the intrinsic light distribution $\nu(R,z)$ by a constant total mass-to-light ratio  $\Upsilon_\text{I,tot}^\text{dyn}$.
-This assumes that the DM is always a constant fraction of the total matter distribution within the region covered by the kinematics.
-This simplified mass model sometimes gives good representations of the inner parts of galaxies, where the stellar component dominates.
-
-We also allow for a overall constant but non-zero velocity anisotropy $\beta_z$ in the model.
-The model parameters ($\Upsilon_\text{I,tot}^\text{dyn},\beta_z$) that fit the $v_\text{rms}$ data best are found using a $\chi^2$-fit and are demonstrated in Figure \ref{fig:JAM_modelA2}.
-
-For $\beta_z$ we imposed the fitting limits $\beta_z \in [-0.5,+0.5]$.
-While the outer parts of galaxies often show radially biased velocity anisotropy up to $\sim 0.5$ (from dynamical modelling of observed elliptical galaxies, e.g., \citet{Kronawitter2000}) and cosmological simulations (e.g., \citealt{2004MNRAS.352..535D,2001ApJ...557..533F}), the centers of galaxies are near-isotropic or have negative velocity anisotropy \citep{2003ApJ...583...92G}.
-Only in extreme models (e.g., around in-spiralling supermassive black holes, e.g., \citealt{1997NewA....2..533Q}) velocity anisotropies as low as $\sim -1$ have been found.
-
-The best fit in Figure \ref{fig:JAM_modelA2} however strives to very negative $\beta_z$ to be able to reproduce the deep central dip in the  $v_\text{rms}$ curve.\footnote{Without limiting the fitting range, the best fit would be a unrealistically low $\beta_z \sim -2$.} But $\beta_z = -0.5$ is not even a remotely agreeable fit and lower anisotropies are not to be expected or realistic.
-We also tested radial profiles for $\beta_z(R)$ of the form proposed by \citet{BaesVanHese}, which was however equally unable to reproduce the data.
-We conclude, that this is due to the well-known degeneracy between anisotropy and mass profile and the mass-follows-light model is \emph{not} a good representation of the mass distribution in J1331's inner regions.
-
-%============================================
-\begin{figure*}
-\centering
-\includegraphics[width=0.9\linewidth]{fig/B4_contour_plot_short.ps}
-\caption{Posterior probability distribution (pdf) sampled with an MCMC (red dots and histograms) for a JAM model fitted to the stellar $v_\text{rms}$ data, with NFW halo, parametrized by $r_s$ and $v_\text{200}$, a stellar mass distribution generated from the I-band MGE in Table \ref{tab:MGEF814W} and a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and constant velocity anisotropy $\beta_z$.
-Shown are also the priors used for J1331's NFW halo, $\mathscr{N}(200~\text{km s}^{-1},40~\text{km s}^{-1})$ (green, see Equation \eqref{eq:prior_v200}) and the concentration vs.
-halo mass relation by \citet{Maccio08} from Equation \eqref{eq:Maccio08} in terms of $v_{200}$ vs.
-$r_s$ with $1\sigma$ scatter (blue, see Equation \eqref{eq:prior_c200}).
-We find slight covariances between $\Upsilon_\text{I,*}$,  $r_s$ and $\beta_z$: The smaller the DM contribution in the center (i.e., the larger $\Upsilon_\text{I,*}$), the less concentrated is the halo (i.e., the larger $r_s$) and the more velocity anisotropy is needed to reproduce the central $v_\text{rms}$ dip.
-As the effect of $v_{200}$ is mostly at larger radii, this parameter doesn't show any covariances, but is also mostly constrained by the prior.\\The MCMC samples are colour coded according to their probability (darker red for higher probability); the sample point with the highest probability is marked by a black diamond.
-The black cross is the mean of the distribution and the ellipses are derived from the covariance matrix of the MCMC samples and correspond approximately to $1\sigma$ (black solid ellipse) and $2\sigma$ (black dotted ellipse) confidence.
-The histograms of the marginalized 1D distributions are overplotted by the mean (black solid lines) and $1\sigma$ error (black dashed lines), whose values are also quoted in the figure and in Table \ref{tab:modelB4_bestfit}.
-The grey diamonds mark a random sub-selection of 12 samples; the corresponding models are shown in Figure \ref{fig:modelB4_models}.}
-\label{fig:modelB4_triangle}
-\end{figure*}
-%============================================
-
-%============================================
-\begin{figure*}
-\centering
-\begin{subfigure}{.48\textwidth}
-  \centering
-  \includegraphics[width=0.9\linewidth]{fig/B4_rms_error_curves.ps}
-  \caption{Comparison of the $v_\text{rms}$ data with the best fit JAM models.}
-  \label{fig:modelB4_vrms}
-\end{subfigure}%
-\hspace{.02\textwidth}
-\begin{subfigure}{.48\textwidth}
-  \centering
-  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_projmass.ps}
-  \caption{Enclosed mass profiles for the best fit models.}
-  \label{fig:modelB4_enclMass}
-\end{subfigure}
-\caption{JAM model including a NFW halo and constant velocity anisotropy fitted to the stellar $v_\text{rms}$ data (blue solid dots) within $\sim3.5''$ and the Einstein mass (red solid dot).
-The 12 lines shown correspond to 12 models randomly drawn from the pdf (marked as grey diamonds in Figure \ref{fig:modelB4_triangle}) and demonstrate how tight the modelling constraints are.
-The mean and standard deviation of the pdf, i.e., the "best fit" parameters, are given in Table \ref{tab:modelB4_bestfit}.
-\emph{Panel (a):} At $R'\lesssim 3.5''$ the symmetrized $v_\text{rms}$ data used in the fit (solid blue points) is shown together with the best fit $v_\text{rms}$ models (red solid lines).
-At larger radii the non-symmetrized data (open blue dots) is compared to an extrapolation of the best fit models using the surface brightness MGE for the outer regions from Figure \ref{fig:MGEouterRegions} (red dashed lines).
-\emph{Panel (b):} Shown is the circular velocity curve of the total mass (green), and separately the contribution of the stellar mass (yellow, again generated from the MGE in Table \ref{tab:MGEF814W}) and DM (grey).
-At the Einstein radius $R_\text{ein}$ (red dotted line) the Einstein mass $M_\text{ein}$ is overplotted with a 10\% error, which was also included in the fit as additional constraint.
-Overplotted is also the effective half-light radius (black dotted line) and the blue dashed line marks the radius within which the data and model were fitted.}
-\label{fig:modelB4_models}
-\end{figure*}
-%============================================
-
-%============================================
-\begin{table*}
-\centering
-\begin{tabular}{llrcl}
-\hline
-stellar I-band mass-to-light ratio & $\Upsilon_\text{I,*}$ & 4.2 & $\pm$ & 0.2\\
-velocity anisotropy & $\beta_z$ & -0.4 & $\pm$ & 0.1 \\
-NFW halo scale length & $r_s$ [kpc] & 40 & $\pm$ & 20\\
-NFW halo virial velocity & $v_{200}$ [$\text{km s}^{-1}$] & 240 & $\pm$ & 40\\
-NFW halo concentration & $c_{200}$ & 8 & $\pm$ & 2 \\
-NFW halo mass & $M_{200}$ [$10^{12} M_\odot$] & 5 & $\pm$ & 2\\
-\hline
-\end{tabular}
-\caption{Summary of the best fit parameters of the JAM model with NFW halo and constant velocity anisotropy, fitted to the $v_\text{rms}$ data within $\sim 3.5''$ and the Einstein mass.
-These estimates correspond to the mean and standard deviation of the pdf in Figure \ref{fig:modelB4_triangle}.
-The halo mass and concentration are calculated from the the best fit $r_s$ and $v_{200}$.}
-\label{tab:modelB4_bestfit}
-\end{table*}
-%============================================
-
-%--------------------------------------------
-\subsubsection{JAM with increasing mass-to-light ratio} \label{sec:results_JAM_SB_gradient}
-%--------------------------------------------
-
-%--------------------------------------------
-In Section \ref{sec:results_lensing} we found from lensing constraints, that the light distribution might drop faster with radius than the mass distribution.
-This could correspond to a radially increasing total mass-to-light ratio.
-As velocity anisotropy alone cannot explain the observed kinematics in a simple a mass-follows-light model, we now allow for a mass-to-light ratio gradient in the JAM modelling.
-We therefore generate a mass model from the light distribution in Table \ref{tab:MGEF814W} by assigning each of the five Gaussians in the MGE its own total mass-to-light ratio $\Upsilon_{\text{I,tot,}i}$ and replace the total luminosity in Equation \eqref{eq:centralItotalL} $L_i$ with the Gaussians total Mass $M_i = \Upsilon_{\text{I,tot,}i} L_i$.
-We treat the five $\Upsilon_{\text{I,tot,}i}$ as free fit parameters and only require that $\Upsilon_{\text{I,tot,}j} \geq \Upsilon_{\text{I,tot,}i}$ when the corresponding $\sigma_j \geq \sigma_i$ to ensure that the overall mass-to-light ratio is increasing with radius.
-
-Figure \ref{fig:enclMass_modelG} shows the best fit (projected local) mass-to-light ratio profile, which rises from $\Upsilon_\text{I,tot} = 2.53$ in the center and approaches a value of $\Upsilon_\text{I,tot} = 7.60$ outside of the fitted region at $R'\gtrsim 3''$.
-The central mass-to-light ratio is in agreement with the mass-to-light ratio $\Upsilon_\text{I,*}^\text{chab} = 2.5 \pm 0.6$, given in Table \ref{tab:previousresults} based on the results of \citet{SWELLSI} assuming a stellar population with a \citet{Chabrier2003} IMF (see also Section \ref{sec:MLdiscussion}).
-When assuming that galaxy bulges are in general older and redder in the center, i.e., $\Upsilon_\text{I,*}$ is more likely to drop with radius than rise, the strong increase of $\Upsilon_\text{I,tot}(R')$ might be due to a strong contribution of DM in J1331.
-
-Figure \ref{fig:JAM_modelG} shows that the best fit model nicely reproduces the central dip in the $v_\text{rms}$ curve, even though it has difficulties fitting the drop around $R' \sim 4''$.
-The latter might be because we only allowed the $\Upsilon_\text{I,tot}(R')$ to rise.
-A slight drop could be expected when the reddish bulge turns into the bluish disk and the contribution of the stellar component becomes less due to a lower $\Upsilon_\text{I,*}$ for younger and bluer populations.
-
-In Figure \ref{fig:enclMass_modelG} we overplot the enclosed mass profile with the Einstein mass $M_\text{ein} = (7.77 \pm 0.33) \cdot 10^{10} M_\odot$ at the Einstein radius found from lensing in Table \ref{tab:bestfitlensmodel}.
-The agreement between the Einstein mass and the independently found $M(<R_\text{ein}) = 7.49 \cdot 10^{10} M_\odot$ from dynamical modelling is striking.
-%--------------------------------------------
-
-%--------------------------------------------
-\subsection{JAM with a NFW dark matter halo} \label{sec:results_JAM_NFW}
-%--------------------------------------------
-
-%--------------------------------------------
-The modelling attempts in the previous sections suggest that J1331's mass distribution could be more roundish in the inner regions and more massive at larger radii than expected from the distribution of stars alone.
-A DM halo in addition to the stellar component could explain these findings.
-%--------------------------------------------
-
-%--------------------------------------------
-\subsubsection{Including a DM halo}
-%--------------------------------------------
-
-%--------------------------------------------
-We therefore proceed by modelling the mass distribution with (i) a stellar component, which we get from the light MGE in Table \ref{tab:MGEF814W} (deprojected to the intrinsic $\nu(R,z)$) times a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and (ii) a spherical NFW DM component (see Section \ref{sec:model_JAM}) with halo scale length $r_s$ and circular velocity at the virial radius $v_{200}$ as free parameters.
-In the JAM modelling we use a 10-Gaussian MGE fit to the classical NFW profile in Equation \eqref{eq:NFWprofile}.
-
-%============================================
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{fig/B4_rms_rot_curves_best_model.ps}
-\caption{Generating the rotation curve $v_\text{rot}(R')$ (red solid line in middle panel) from the best fit JAM model with NFW halo by fitting the rotation parameter $\kappa'$ to the symmetrized $v_\text{rot}$ data within $R'\sim3.5''$ (solid blue dots in central panel).
-The first panel shows the $v_\text{rms}$ data and model analogous to Figure \ref{fig:modelB4_vrms} for the mean parameters in Table \ref{tab:modelB4_bestfit}.
-The second panel shows the corresponding $v_\text{rot}$ for the best fit rotation parameter $\kappa' = 0.76$ in Equation \eqref{eq:kappa_profile} (red solid lines).
-The third panel shows simply the velocity dispersion $\sigma = \sqrt{v_\text{rms}^2 - v_\text{rot}^2}$.
-At larger radii we compare the unsymmetrized data (open blue dots), the gas kinematics from \citet{SWELLSV} (green diamonds) and an extrapolation of the JAM model, using the light distribution MGE from Figure \ref{fig:MGEouterRegions} for the outer regions (red dashed lines).
-The central regions are very well reproduced and we can also nicely predict the rotation curve at larger radii.
-Only at larger radii the $v_\text{rms}$ and $v_\text{rot}$ overestimate the measurements, probably due to a too massive NFW halo.}
-\label{fig:modelB4_vrot}
-\end{figure}
-%============================================
-
-%--------------------------------------------
-\subsubsection{Modelling and priors}
-%--------------------------------------------
-
-%--------------------------------------------
-The full set of fit parameters is $(\Upsilon_\text{I,*},r_s,v_{200},\beta_z)$, where $\beta_z$ is again the constant velocity anisotropy parameter.
-We will investigate this parameter space with a MCMC\footnote{The Python code package for \emph{emcee}, a Monte Carlo Markov Chain implementation by \citet{emcee} is available online at \url{http://dan.iel.fm/emcee/current/}.
-The version from October 2013 was used in this work.} \citep{emcee} and use priors for the halo parameters to guide the fit to a realistic NFW halo shape.
-
-\citet{Dutton10} give a relation for halo vs.
-stellar mass for late-type galaxies.
-Using the stellar mass estimate for J1331 from \citet{SWELLSI}, $m_* = (1.06 \pm 0.25) \cdot 10^{11} M_\odot$ for the Chabrier IMF estimate, we find ${v_{200}} = (202_{-33}^{+44})_{-13}^{+12}$.
-The first error is due to the $2\sigma$ scatter in the relation by \citet{Dutton10}.
-The second error is the propagated error due to the uncertainty in the stellar mass.
-We use this as a rough estimate for the halo of J1331 and as Gaussian prior on $v_{200}$,
-\begin{equation}
-p(v_{200}) = \mathscr{N}(200~\text{km s}^{-1},40~\text{km s}^{-1}). \label{eq:prior_v200}
-\end{equation}
-
-We also use the concentration vs. halo mass relation by \citet{Maccio08} in Equation \eqref{eq:Maccio08} as a prior on the concentration, i.e.
-\begin{equation}
-p(\log c_{200} \mid v_{200}) = \mathscr{N}\left(\langle \log c_{200} \rangle (M_{200}) \mid 0.105 \right). \label{eq:prior_c200}
-\end{equation}
-
-For the velocity anisotropy parameter $\beta_z$ we will again employ a uniform prior 
-\begin{equation*}
-p(\beta_z) = \mathscr{U}(-0.5,+0.5)
-\end{equation*}
-to exclude very unrealistic anisotropies. The full prior used is then
-\begin{eqnarray*}
-&&p(\Upsilon_\text{I,*},r_s,v_{200},\beta_z) \\
-&&= \frac{1}{\ln\left( 10 r_s\right)} p(\log c_{200} \mid v_{200}) \cdot p(v_{200}) \cdot p(\beta_z), 
-\end{eqnarray*}
-where the factor $1/\ln\left( 10 r_s\right)$ is the Jacobian of the transformation from the halo parameters $(v_{200},\log c_{200})$ to $(v_{200},r_s)$.
-
-We restrict the $v_\text{rms}$ fit to a region $R' \lesssim 3.5''$, approximately within the effective half-light radius $R_\text{eff} = 2.6''$.
-We also include the Einstein mass $M(<R_\text{ein})$ with a 10\% error as an additional constraint in the fit.
-
-%--------------------------------------------
-\subsubsection{Result} \label{sec:results_JAM_NFW_results}
-%--------------------------------------------
-
-%--------------------------------------------
-Figure \ref{fig:modelB4_triangle} shows the posterior probability distribution (pdf) of the fit sampled with an MCMC.
-Overplotted are also the priors used to constrain the NFW halo.
-The mean parameters are summarized in Table \ref{tab:modelB4_bestfit}.
-We find that the best fit NFW halo strives to be more massive and with a higher concentration (due to a smaller $r_s$) than  proposed by the priors.
-The model also prefers  very negative velocity anisotropies.
-Both, the high halo concentration and low $\beta_z$, are needed to reproduce the central dip of the $v_\text{rms}$ curve.
-Figure \ref{fig:modelB4_models} illustrates the range of best fit models according to the extent of the pdf.
-The models fit the $v_\text{rms}$ data in the inner regions quite well (Figure \ref{fig:modelB4_vrms}) and are also consistent with the Einstein mass (see Figure \ref{fig:modelB4_enclMass}).
-The extrapolation of the model to larger radii however overestimates the data, does not exhibit a drop around $\sim 6''$ at all and seems to be therefore overall too massive.
-
-We also fitted a model with a cored logarithmic DM halo.
-The cored halo models are in general slightly less massive than the NFW halo and therefore fit the outer regions of J1331 better.
-However, the density profile of the cored halo as well as the I-band light distribution within the plane drop as $\rho(r) \propto r^{-2}$.
-There is therefore a strong degeneracy between the stellar mass and the DM.
-Overall, we were not able to obtain tight constraints on the cored logarithmic halo.
-
-%============================================
-\begin{table*}
-\centering
-\caption{Total I-band luminosity, stellar mass and mass-to-light ratio, calculated from the I-band AB magnitudes and stellar masses found for J133's bulge and disk by \citet{SWELLSI} (their table 2) for comparison with this work.
-The transformation from AB magnitudes to the Johnson-Cousins I-Band used the relation $I[\text{mag}] = I[\text{ABmag}] - 0.309$ from \citet{FG1994} (their table 2).
-For the conversion from apparent magnitude to total luminosity the redshift $z=0.113$ \citet{SWELLSIII} was turned into a luminosity distance using the cosmology by \citet{WMAP5cosm}.
-}
-\begin{tabular}{cccccc}
-\hline\hline
-& & \multicolumn{2}{c}{Chabrier IMF} & \multicolumn{2}{c}{Salpeter IMF}\\
-      &  $L$ [$10^{10}L_{\odot}$]                & $M_*$ [$10^{10}M_\odot$]               & $\Upsilon_\text{I,*}^\text{chab}$ & $M_*$ [$10^{10}M_\odot$] & $\Upsilon_\text{I,*}^\text{sal}$ \\\hline
-bulge &   $3.10 \pm 0.15 $  & $7.8 \pm 1.8$ & $2.5 \pm 0.6$ & $14.5 \pm 3.7 $ & $4.7 \pm 1.2$ \\
-disk  &   $2.35 \pm 0.11 $  & $2.9 \pm 0.7$ & $1.2 \pm 0.3$ & $5.2 \pm 1.1$ & $2.2 \pm 0.5$ \\
-total &   $5.45 \pm 0.19$ & $10.6 \pm 1.9$& & $19.7 \pm 3.9$&\\\hline
-\end{tabular}
-\label{tab:previousresults}
-\end{table*}
-%============================================
-
-%--------------------------------------------
-\subsubsection{Rotation curve}
-%--------------------------------------------
-
-%--------------------------------------------
-We generate a rotation curve from the best fit mean model in Table \ref{tab:modelB4_bestfit}, whose $v_\text{rms}$ curve is shown in the first panel of Figure \ref{fig:modelB4_vrot}.
-Following the procedure in Section \ref{sec:model_JAM}, we find the rotation curve by fitting the rotation parameter $\kappa'$ to the symmetrized $v_\text{rot}$ data within $R' = 3.5''$.
-The best fit with $\kappa' = 0.76$ is given in the second panel of Figure \ref{fig:modelB4_vrot}.
-The third panel shows the dispersion that follows from $\sigma = \sqrt{v_\text{rms}^2 - v_\text{rot}^2}$.
-Our assumptions for $\kappa(R)$ nicely reproduce a $v_\text{rot}$ model with counter-rotating core.
-Although we fitted $v_\text{rot}$ only to the inner regions, the extrapolation to large radii fits the data also very well.
-
-While the dispersion $\sigma$ in the center fits by construction quite good, the predicted dispersion is much larger than the data.
-We would expect the disk rotationally supported and therefore have a low velocity dispersion; especially dispersions as high as $\sim 200~\text{km s}^{-1}$ are more likely to be observed in the pressure supported bulges of galaxies.
-There might be something unexpected with the $\sigma$ measurements around $\sim 5''$, but at large radii the the best fit model NFW halo is simply too massive.
-%--------------------------------------------
-
-%--------------------------------------------
-\section{Discussion and Conclusion} \label{sec:Discussion}
-%--------------------------------------------
-
-%--------------------------------------------
-We've presented different dynamical models for the central region of J1331.
-Some of them capture the observed kinematics, but none of them work at both small and large radii.
-In the following we discuss possible reasons, also by comparing our results to previous work.
-%--------------------------------------------
-
-%--------------------------------------------
-\subsection{On J1331's central stellar mass-to-light ratio} \label{sec:MLdiscussion}
-%--------------------------------------------
-
-%--------------------------------------------
-Some of the ambiguities in recovering J1331's matter distribution could be resolved by learning more about stellar populations with different IMFs in J1331.
-In particular, a sophisticated guess for the stellar mass-to-light ratio in the bulge could be compared to our very reliable measurement of the total mass-to-light ratio inside the Einstein radius $\Upsilon_\text{I,tot}^\text{ein} = 5.56 \Upsilon_{I,\odot}$.
-This would then either support or contradict the presence of a significant amount of DM in the bulge.
-
-Traditional choices for the IMF are the bottom-heavy IMF by \citet{Salpeter1955},
-$$\xi(m) \propto m^{-x}, x=2.35,$$
-where $\xi(m) \diff m$ is the number of stars with mass $m$ in $[m,m+\diff m]$, and the IMFs by \citet{2002Sci...295...82K} and \citet{Chabrier2003}, which are in agreement with each other and predict less low-mass stars.
-
-\citet{Ferreras} found a relation between the central stellar velocity dispersion $\sigma_0$ in early-type galaxies and the IMF slope $x$; a higher $\sigma_0$ suggests a more bottom-heavy IMF.
-For a unimodal (Salpeter-like) IMF and $\sigma_0 \simeq 200~\text{km s}^{-1}$ in J1331 (see Figure \ref{fig:kinematics}) they predict $x \approx 2.33$, which is close to the standard Salpeter slope, also supported by \citet{2014MNRAS.438.1483S}.
-When assuming a bi-modal (Kroupa-equivalent-like) IMF, \citet{Ferreras} predict $x \approx 2.85$ for J1331's central velocity dispersion.
-This is more bottom-heavy than the standard \citet{2002Sci...295...82K} IMF.
-Overall, the central velocity dispersion suggests a rather bottom-heavy IMF in J1331's bulge and therefore large stellar mass-to-light ratio.
-
-\citet{SWELLSI} estimated J1331's stellar bulge mass given a Salpeter IMF and measured the I-band AB magnitude of the bulge.
-Transformed to a stellar I-band mass-to-light ratio, their results would correspond to $\Upsilon_\text{I,*}^\text{sal} = 4.7 \pm 1.2$ (see Table \ref{tab:previousresults}).
-This is not too far from $\Upsilon_\text{I,*} = 4.2 \pm 0.2$ (see Table \ref{tab:modelB4_bestfit}), which we found when including a NFW halo in the JAM modelling.
-
-When \citet{SWELLSI} assumed a Chabrier IMF, their result translates to $\Upsilon_\text{I,*}^\text{chab} = 2.5 \pm 0.6$ (see Table \ref{tab:previousresults}).
-In Section \ref{sec:results_JAM_SB} we created a dynamical model from only the surface brightness distribution and an increasing mass-to-light ratio profile without additional DM halo.
-We found that such a model would be perfectly consistent with the Einstein mass, predict a total $\Upsilon_\text{I,tot}(R'\sim0) = 2.53$---being consistent with the Chabrier IMF estimate by \citet{SWELLSI}---and rise quickly to $\Upsilon_\text{I,tot}(R'\gtrsim R_\text{ein}) \gtrsim 6$.
-
-We also compare our results from Section \ref{sec:results_JAM_NFW} with the study by \citet{SWELLSV}.
-They found that the bulge of J1331 has an IMF \emph{more} bottom-heavy than the Salpeter IMF from fitting a NFW halo to (1) the Einstein mass and (2) gas kinematics at larger radii $\gtrsim 8''$.
-In Section we fitted a mass model with NFW halo to (1) the Einstein mass and (2) stellar kinematics within $\sim 3.5''$.
-Our best fit $\Upsilon_\text{I,*} = 4.2 \pm 0.2$ (see Table \ref{tab:modelB4_bestfit}) indicates a \emph{less} bottom-heavy IMF than the Salpeter IMF.
-\cite{SWELLSV} found systematically lower NFW halo masses ($v_\text{circ,halo}(5'') \sim 120~\text{km s}^{-1}$ according to their Figure 2) than we did ($v_\text{circ,halo}(5'') \sim 200~\text{km s}^{-1}$).
-%--------------------------------------------
-
-%============================================
-\begin{figure}
-\centering
-\includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_vcirc.ps}
-\caption{Comparison of the circular velocity curve of J1331's inner regions for different models: (i) JAM model with NFW DM halo from Section \ref{sec:results_JAM_NFW_results} and Figure \ref{fig:modelB4_models} (green).
-(ii) Lens model from Section \ref{sec:results_lensing_bestfit} and Figure \ref{fig:JAM_modelL} with $\alpha = 1.1$ (red dashed line), $\alpha = 1$ (red solid line) and $\alpha=0.9$ (red dash-dotted line).
-(iii) Mass-follows-light model, which uses the F814W surface brightness in Table \ref{tab:MGEF814W} and the mass-to-light ratio in the Einstein radius, $\Upsilon^\text{ein}_\text{I,tot} = 5.56$, to generate a mass distribution, as in Figure \ref{fig:lenscomparelight} (orange line).
-(iv) Model from gas kinematics and Einstein mass found by \citet{SWELLSV} (their Figure 2, best model with 68\% confidence region) (blue lines).}
-\label{fig:vcirc_comparison}
-\end{figure}
-%============================================
-
-%--------------------------------------------
-\subsection{On J1331's central kinematics}
-%--------------------------------------------
-
-%--------------------------------------------
-In Figure \ref{fig:vcirc_comparison} we compare the circular velocity curve found by \citet{SWELLSV} with a mass-follows-light model scaled to fit our Einstein mass (by multiplying the light distribution in Table \ref{tab:MGEF814W} with $\Upsilon_\text{I,tot}^\text{ein} = 5.56$).
-Within $R < 5''$ they agree with each other.
-
-The models in this work used more than just the Einstein mass to constrain the matter distribution at small radii: The lens mass model constrained also the shape of the mass distribution within the lensing image configuration at $R_\text{ein} \sim 1''$.
-The dynamical models used stellar kinematics inside $R' \simeq 3.5''$.
-We compare the lens mass model's $v_\text{circ}$ (for $\alpha=1.0\pm 0.1$) with the NFW JAM model (Table \ref{tab:modelB4_bestfit}) in Figure \ref{fig:vcirc_comparison} as well.
-Within and around $R_\text{ein}$ they are consistent with each other, even though they where independently derived.
-They do not agree with the result by \citet{SWELLSV} and in Section \ref{sec:results_JAM_SB} we showed, that ``mass-follows-light'' is not a good model for J1331.
-
-Overall, we were not able to find a consistent explanation for J1331's central $v_\text{rms}$ dip.
-It cannot be due to tangential velocity anisotropy in the center alone (see Section \ref{sec:results_JAM_SB}, Figure \ref{fig:JAM_modelA2}).
-It also cannot be explained by a strong contribution of DM inside the bulge together with a moderate tagential velocity anisotropy, because the corresponding DM halos would still be too massive to fit the data in the outer regions (see Section \ref{sec:results_JAM_NFW}, Figure \ref{fig:modelB4_vrms}]).e
-
-Another feature in the stellar kinematics, that none of our JAM models was able to reproduce in the slightest and which we therefore excluded in the modelling, was the dip in $v_\text{rms}$ around $\sim 6''$, which occurs around the transition from bulge to disk (see Figures \ref{fig:F814W} and \ref{fig:kinematics}).
-%--------------------------------------------
-
-%--------------------------------------------
-\subsection{On J1331's possible merger history and modelling failures}
-%--------------------------------------------
-
-%--------------------------------------------
 %Why we think that J1331 had a merger
@@
 %Gas accretion - no!
-Accretion of gas on retrograde orbits and subsequent star formation could lead to a younger and counter-rotating stellar population.
+Accretion of gas on retrograde orbits and subsequent star formation could lead to a younger and counter-rotating stellar population \Wilma{[TO DO: REF]}.
 However, to form enough stars such that the net rotation of the large and massive core is retrograde, a very large amount of gas would have had to be accreted by J1331---which is not very likely.
@@
 %Mergers - yes!
-Galaxy mergers are another possible scenario.
+Another scenario are galaxy mergers.
 Major mergers can form kinematically decoupled cores (KDCs) (e.g., \citealt{2011MNRAS.414.2923K,2015ApJ...802L...3T}), if they include large amounts of gas \citep{2010ApJ...723..818H}.
-During a minor merger, the dense nucleus of a satellite galaxy on a retrograde orbit could survive the dissipationless accretion and spiral to the core due to tidal friction (e.g., \citealt{1984ApJ...287..577K,1988ApJ...327L..55F}).
+During a minor merger, the dense nucleus of a satellite galaxy on a retrograde orbit could survive the dissipationless accretion and spiral to the core due to tidal friction (e.g., \citealt{1984ApJ...287..577K}).
 
@@
 Mergers can reverse this behaviour by inducing the creation of young stellar populations in the remnant's center.
-Major mergers can trigger star formation bursts (e.g., \citealt{2008gady.book.....B}, \S 8.5.5).
-After a minor merger the satellite's stellar population now residing in the remnant's core is in general younger than the progenitor's bulge \citep{1996AJ....112..839C,2010MNRAS.404.1775T} .
-The different stellar populations in a merger remnant can be associated with different $\Upsilon_*$ and in special cases they even show up as a reverse colour gradient within the bulge in photometry \citep{1990ApJ...361..381B, 1997ApJ...481..710C}.
+Major mergers can trigger star formation bursts (e.g., \Wilma{[TO DO: REF, maybe http://arxiv.org/pdf/1409.5126v2.pdf???]}).
+After a minor merger the satellite's stellar population now residing in the remnant's core is in general younger than the progenitor's bulge \Wilma{[TO DO: REF]} .
+The different stellar populations in a merger remnant can be associated with different $\Upsilon_*$ and sometimes even show up as a reverse colour gradient within the bulge in photometry \Wilma{[TO DO: REF]}.
 
 %Color gradient in J1331
-Even though investigation of the photometry of J1331 did not reveal a distinct blue core in J1331, we cannot fully exclude the possibility that J1331 has such a $\Upsilon_*$ gradient (see discussion in Sections \ref{sec:results_JAM_SB_MfL} and \ref{sec:results_JAM_SB_gradient}).
+Even though investigation of the photometry of J1331 did not reveal a distinct blue core in J1331, we cannot fully exclude the possibility that J1331 has such a $\Upsilon_*$ gradient (see discussion in Section  \Wilma{[TO DO: Where???]}).
 In this case the restrictive assumption of a constant $\Upsilon_*$ in our JAM modelling could have lead to wrong conclusions about the DM distribution.
 
-Another way how galaxy encounters can can modify the structure of galaxies is the excitation of warps \citep{1991wdir.book.....C,2013pss5.book..923S}.
-Warps lead to a twist in the projected kinematic major axis with radius, which is then also misaligned with the photometric major axis (\citealt{1998gaas.book.....B}, \S 8.2.4).
-From kinematics along the photometric major axis only it cannot be determined if such a twist or misalignment is present in J1331.
+%Merger and kinematic twist
+Other ways how mergers can can modify the structure of galaxies are warps in the outer parts or kinematic twists in the center of the remnant galaxy \citep{2013pss5.book..923S}, which show up as misalignments of kinematic and photometric major axis.
+
+%Kinematic twist in J1331
+From kinematics along the photometric major axis only it cannot be determined if such a misalignement is present in J1331.
 But if it were, our modelling assumption of axisymmetry would not be satisfied anymore.
@@
 At large radii this could lead to an underestimation of the DM halo mass.
-%--------------------------------------------
-
-%--------------------------------------------
-\subsection{Future work}
-%--------------------------------------------
-
-%--------------------------------------------
-Standard JAM modelling approaches seem not to work for J1331.
-The existing data---photometry and major axis kinematics---is however not sufficient to decide which of our model assumptions lead to the failure to find an overall consistent mass model.
-
-2-dimensional stellar kinematics would greatly help to resolve this problem.
-The main future work would be therefore getting high-resolution integral-field spectroscopy for J1331.
-High spatial resolution would be required to clearly identify J1331's presumably complex kinematic structure.
-High spectral resolution would be important to be able to reliably measure the low velocity dispersion in the outer regions of J1331.
-
-Specifically 2D kinematics should help to answer the following questions: Is the drop in $v_\text{rms}$ around $R' \sim 3-6~\text{kpc}$ real?
-Did the long slit spectrograph maybe miss the major axis of the disk?
-And most importantly: Are the kinematics asymmetric?
-Is it possible that there even exists a kinematic twist due to the merger in J1331's past?
-
-Furthermore, learning more about different stellar populations in J1331 would lead to valuable constraints for the modelling.
-While a quick investigation of the photometric colour profile did not reveal obvious colour gradients in J1331's bulge, there could be still stellar $\Upsilon_{I,*}$ variations due to age of metallicity differences.
-Existing major axis spectroscopy and/or future IFU data could be employed (i) to investigate absorption line indices to confirm (or contradict) the existence of $\Upsilon_{I,*}$ gradients and (ii) to perform stellar population analyses to constrain $\Upsilon_{I,*}$ reliably and independently of kinematics.
-
-Future modelling approaches should fit dynamics (stellar and gas kinematics from) simultaneously with the gravitational lensing (image positions, shape and even flux ratios) in a similar fashion to \citet{SWELLSIV}.
-To also model the extent, shape and flux of the lensing images, the method by \citet{2004ApJ...611..739T,2003ApJ...590..673W} could be employed, which models the surface brightness distribution of the images and source on a pixelated grid.
-For this to work a good model for the galactic extinction would be needed---but 2D spectroscopy could also help with this.
-
-All of the would lead to a much better understanding of J1331's structure and mass distribution and therefore answer questions on how mergers might modify spiral galaxies.
-%--------------------------------------------
-
-%--------------------------------------------
-\subsection{Summary}
-%--------------------------------------------
-
-%--------------------------------------------
-The goal of this work was to constrain the matter distribution of the massive spiral galaxy J1331.
-J1331 is of special interest because it firstly has a large counter-rotating core and might therefore be a merger remnant and it secondly acts as strong gravitational lens for a background source.
-The latter allowed us to constrain the galaxy's mass from gravitational lensing.
-As second independent approach we used dynamical Jeans modelling to recover and disentangle the stellar and DM distribution.
-We focussed on the bulge region of J1331 to complement previous studies of J1331 by \citet{SWELLSIII} and \citet{SWELLSV}.
-The independent mass constraints which we derived from lensing and dynamics agree very well with each other within $R_\text{eff}$.
-
-In our lensing approach we fitted a scale-free galaxy model to the lensing image position.
-This constrained the Einstein radius to within 2\% ($R_\text{ein}=(0.91\pm0.02)''\simeq(1.83\pm0.04)~\text{kpc}$), and the Einstein mass to within 4\% ($M_\text{ein} = (7.8\pm0.3) \cdot 10^{10} M_\odot$), consistent with results by \citet{SWELLSIII}.
-The recovered mass distribution agrees also very well with the shape of the observed lensing images.
-
-To get a handle on J1331's light distribution we used a MGE fit to J1331's surface brightness in the F814W filter in HST imaging by \citet{SWELLSI}.
-Based on this we found J1331's effective radius to be $R_\text{eff} \simeq 2.6'' \hat{=} 5.2~\text{kpc}$ and its total I-band luminosity to be $L_\text{I,tot} \simeq 5.6 \cdot 10^{10} L_\odot$.
-
-We used axisymmetric JAM modelling to calculate the second velocity moment of a tracer and mass distribution given in terms of MGEs.
-The JAM model of the lens mass model gave an independent prediction which was consistent with observed stellar kinematics from major axis long slit spectroscopy by \citet{SWELLSV} within $R_\text{eff}$.
-We also fitted mass models with and without NFW halo to the stellar kinematics within $R'=3.5~\text{kpc}$.
-From this we deduced that a mass-follows-light model with constant total mass-to-light ratio is not a good model for J1331---not even in the inner regions.
-To describe the observed stellar kinematics we either require a strong contribution of a DM halo already in the bulge, or a strongly varying stellar mass-to-light ratio.
-We also showed that it is possible to construct a model which includes the counter-rotating core and fits the rotation curve at large radii.
-
-While both our independent mass models are consistent with each other within $\sim R_\text{eff}$, they do not agree with previous findings by \citet{SWELLSV}, nor the data at large radii.
-We attribute this to the fact \citet{SWELLSV} derived mass constraints from kinematics in the outer regions only, while we focussed on the inner regions in detail.
-We speculate that a merger might have modified the kinematic structure and/or mass distribution of J1331 such that crucial model assumptions are not valid anymore.
-To resolve the ambiguities in J1331's mass distribution 2-dimensional kinematic maps of J1331 from integral-field unit spectroscopy would be needed.
-%--------------------------------------------
-
-%--------------------------------------------
-\bibliographystyle{mnras}
-\bibliography{literaturelist}
-%--------------------------------------------
-
-\label{lastpage}
-
-\end{document}

### 2016-01-29 archive/v3/docs_v3/introduction_v3.02.tex
Cleaned up (files are moved to archive now)

--- 2016-01-05 docs/introduction_v3.02.tex
@@
   \includegraphics[width=.9\linewidth]{fig/first_glimpse_450.ps}
-  \caption{J1331 in F450W}
+  \caption{J1331 in the F450W filter.}
   \label{fig:F450W}
@@
   \includegraphics[width=.9\linewidth]{fig/first_glimpse_814.ps}
-  \caption{J1331 in F814W}
+  \caption{J1331 in the F814W filter.}
   \label{fig:F814W}
@@
   \includegraphics[width=.9\linewidth]{fig/lens_imgpos.ps}
-  \caption{The lensing images}
+  \caption{Lensing images around the galaxy center.}
   \label{fig:lens_just_imgpos}
@@
   \includegraphics[width=.9\linewidth]{fig/stellar_kinematics_data.ps}
-  \caption{Stellar Kinematics by \citet{SWELLSV}}
+  \caption{Stellar kinematics by \citet{SWELLSV}.}
   \label{fig:kinematics}
@@
 The black solid line in panel (b) shows the orientation of the major-axis.
-Its length is $10''$ and it indicates approximately where we carry out the dynamical modelling.
+Its length is $10''$ and it marks approximately the region within which we carry out the dynamical modelling.
 \emph{Panel (c):} Lensing images in the central region of J1331.
-An IRAF \emph{ellipse} fit to the F450W surface brightness in panel (a) was subtracted from the image.
+An IRAF \emph{ellipse} model was fitted to and then subtracted from the galaxy's F450W surface brightness in panel (a).
 The (smoothed) residuals within the white square in panel (a) are shown in panel (c).
-(The four bright blobs (A,B,C and D), that become visible, are arranged in a typical strong lensing configuration around the center of the galaxy (G).
-The configuration of the two additional blobs, that lie approximately on a line with A, B and G, does not suggest that they form a lensing doublet.
-They might be star forming regions of a background galaxy.) \emph{Panel (d):} Stellar Kinematics along the galaxy's major axis as measured by \citet{SWELLSV}, line-of-sight rotation velocity $v_\text{rot}$, line-of-sight velocity dispersion $\sigma$ and the rms-velocity $v_\text{rms} = \sqrt{v_\text{rot}^2 + \sigma^2}$.
-The dotted line in panel (b) indicates the galaxy's effective half-light radius (in the F814W filter), $R_\text{eff} = 2.6" = 5.2~\text{kpc}$.
+The four bright blobs (A, B, C and D) which are visible in the residuals are arranged in a typical strong lensing configuration around the center of the galaxy (G).
+(The configuration of the two additional blobs which lie approximately on a line with A, B and G does not suggest that these blobs are a lensing doublet.
+They might rather be star forming regions of a background galaxy.) \emph{Panel (d):} Stellar Kinematics along the galaxy's major axis as measured by \citet{SWELLSV}.
+Shown are line-of-sight rotation velocity $v_\text{rot}$ (top), line-of-sight velocity dispersion $\sigma$ (middle) and the rms-velocity $v_\text{rms} = \sqrt{v_\text{rot}^2 + \sigma^2}$ (bottom).
+The dashed line indicates the galaxy's effective half-light radius (in the F814W filter), $R_\text{eff} = 2.6'' = 5.2~\text{kpc}$.
 The $v_\text{rot}$ curve reveals that J1331 has a counter-rotating core within $R_\text{eff}$.}

### 2016-01-29 archive/v3/docs_v3/model_JAM_v3.02.tex
Cleaned up (files are moved to archive now)

--- 2015-11-18 docs/model_JAM_v3.02.tex
@@
 
-%============================================================================
-\begin{table*}
-\centering
-\caption{Galaxy Parameters of J1331}
-\begin{tabular}{lllrl}
-\hline
-redshift                  & $z_d$ & 0.113 & \citep{SWELLSIII}\\
-angular diameter distance & $D_d$ [Mpc] & 414 & \\
-scaling                   & 1 kpc / 1 $''$ & 2.006 & \\
-position angle            & $\phi$ [degrees] & \Wilma{[TO DO: wrt N through E]}\\
-average axis ratio & $q'$ & 0.598\\
-average ellipticity & $\epsilon = 1 - q'$ & 0.402 & \\
-apparent I-band magnitude & $m_\text{I}$ [mag] & 15.77 & \\
-total I-band luminosity & $L_\text{tot,I}$ [$10^{10} L_\odot$] & 5.6 & \\
-effective half-light radius & $R_\text{eff}$ [$''$] & 2.6 & \\
-& $R_\text{eff}$ [pc]& 5.2 & \\
-\hline
-\end{tabular}
-\label{tab:galaxyparameters}
-\end{table*}
-%============================================================================
-
 \paragraph{Including a NFW halo.} As mentioned above, JAM modelling allows to incorporate an invisible matter component in addition to the luminous matter in the form of an MGE.

### 2016-01-29 archive/v3/docs_v3/model_MGE_v3.02.tex
Cleaned up (files are moved to archive now)

--- 2015-11-18 archive/v3/docs/model_MGE_v3.01.tex
@@
 
-\paragraph{Multi-Gaussian Expansion (MGE).} MGEs are used to parametrize the observed surface brightness (or projected total mass) of a galaxy as a sum of $N$ two-dimensional, elliptical Gaussians \citep{1991ApJ...366..599B,1992A&A...253..366M,1994A&A...285..723E,1999MNRAS.303..495E}.
+\paragraph{Multi-Gaussian Expansion (MGE).} MGEs are used to parametrize the observed surface brightness (or projected total mass) of a galaxy as a sum of $N$ 2-dimensional, elliptical Gaussians \citep{1991ApJ...366..599B,1992A&A...253..366M,1994A&A...285..723E,1999MNRAS.303..495E}.
 This work makes use of the algorithm and code\footnote{The IDL code package for fitting MGEs to images by \citet{Cap02} is available online at \url{http://www-astro.physics.ox.ac.uk/~mxc/software}.
@@
 \end{eqnarray}
-where $I_{0,i}$ is the central surface brightness of each Gaussian, $L_i$ its total luminosity, $\sigma_i$ its dispersion along the major axis and $q'_i$ the axis ratio between the elliptical Gaussians major and minor axis.
+where $I_{0,i}$ is the central surface brightness of each Gaussian, $L_i$ its total luminosity, $\sigma_i$ its dispersion along the major axis and $q'_i$ the axis ratio between the elliptical Gaussian's major and minor axis.
 
-We can also expand the telescopes point-spread function (PSF) as a sum of circular Gaussians,
+We can also expand the telescope's point-spread function (PSF) as a sum of circular Gaussians,
 \begin{equation}
@@
 where $\sum_j G_j = 1$ and $\delta_j$ are in this case the dispersions of the circular PSF Gaussians.
-In this case the observed surface brightness distribution is a convolution of the intrinsic surface brightness in Equation \ref{eq:MGEgeneral} with the PSF in Equation \ref{eq:PSFgeneral}: $(I \ast \text{PSF}) (x',y')$ is then again a sum of Gaussians and can be directly fitted to an image of the galaxy in question.
+
+The observed surface brightness distribution is a convolution of the intrinsic surface brightness in Equation \eqref{eq:MGEgeneral} with the PSF in Equation \eqref{eq:PSFgeneral}: $(I \ast \text{PSF}) (x',y')$ is then again a sum of Gaussians and can be directly fitted to an image of the galaxy in question.
 

### 2016-01-29 archive/v3/docs_v3/model_lensing_v3.01.tex
Cleaned up (files are moved to archive now)

--- 2015-11-18 docs/model_lensing_v3.01.tex
@@
 The best fit lens model is then the one that minimizes
-\begin{eqnarray*}
-\chi^2_\text{lens} &=& \sum_{i} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right) \left( \vect{\theta}_{pi} - \vect{\theta}_{oi} \right)\right|^2\\
-&\simeq& \sum_{i} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right)  \left.\mathscr{M}\right|_{\vect{\theta}=\vect{\theta}_{oi}} \left( \begin{matrix} \xi - \tilde{\xi}_i \\ \eta - \tilde{\eta}_i \end{matrix} \right) \right|^2,
-\end{eqnarray*}
+\begin{eqnarray}
+\chi^2_\text{lens} &=& \sum_{i} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right) \left( \vect{\theta}_{pi} - \vect{\theta}_{oi} \right)\right|^2\nonumber\\
+&\simeq& \sum_{i} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right)  \left.\mathscr{M}\right|_{\vect{\theta}=\vect{\theta}_{oi}} \left( \begin{matrix} \xi - \tilde{\xi}_i \\ \eta - \tilde{\eta}_i \end{matrix} \right) \right|^2,\label{eq:chi2lens}
+\end{eqnarray}
 where $(\Delta_x,\Delta_y)$ are the measurement errors of the image positions $\vect{\theta}_{oi}$.
@@
 Following \citet{GlennEC} we add a term
-\begin{equation*}
-\chi^2_\text{shape} = \lambda \sum_{k \geq 3} \frac{\left(a_k^2 +b_k^2 \right)}{a_0^2} 
-\end{equation*}
+\begin{equation}
+\chi^2_\text{shape} = \lambda \sum_{k \geq 3} \frac{\left(a_k^2 +b_k^2 \right)}{a_0^2} \label{eq:chi2shape}
+\end{equation}
 which forces the shape of the mass distribution to be close to an ellipse. The total $\chi^2$ to minimize is therefore
-\begin{equation*}
-\chi^2 = \chi^2_\text{lens} + \chi^2_\text{shape}
-\end{equation*}
+\begin{equation}
+\chi^2 = \chi^2_\text{lens} + \chi^2_\text{shape} \label{eq:chi2total}
+\end{equation}
 We set $a_1 = b_1 = 0$, which corresponds to the choice of origin; in this case the center of the galaxy.

### 2016-01-29 archive/v3/docs_v3/results_JAMwithNFW_v3.02.tex
Cleaned up (files are moved to archive now)

--- 2016-01-07 docs/results_JAMwithNFW_v3.02.tex
@@
 \includegraphics[width=0.9\linewidth]{fig/B4_contour_plot_short.ps}
-\caption{Posterior probability distribution sampled with MCMC (red dots and histograms) for a JAM model with NFW halo, parametrized by $r_s$ and $v_\text{200}$, a stellar mass distribution generated from the I-band MGE in Table \ref{tab:MGEF814W} and a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and constant velocity anisotropy $\beta_z$.
-Shown are also the priors used for J1331's NFW halo, $\mathscr{N}(200~\text{km s}^{-1},40~\text{km s}^{-1})$ (green) and the concentration vs.
+\caption{Posterior probability distribution sampled with an MCMC (red dots and histograms) for a JAM model fitted to the stellar $v_\text{rms}$ data, with NFW halo, parametrized by $r_s$ and $v_\text{200}$, a stellar mass distribution generated from the I-band MGE in Table \ref{tab:MGEF814W} and a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and constant velocity anisotropy $\beta_z$.
+Shown are also the priors used for J1331's NFW halo, $\mathscr{N}(200~\text{km s}^{-1},40~\text{km s}^{-1})$ (green, see Equation \eqref{eq:prior_v200}) and the concentration vs.
 halo mass relation by \citet{Maccio08} from Equation \eqref{eq:Maccio08} in terms of $v_{200}$ vs.
-$r_s$ with $1\sigma$ scatter (blue).
-The MCMC samples are color coded according to their probability (darker red for higher probability); the sample point with the highest probability is marked by a black diamond.
-The black cross is the mean of the distribution and the ellipses are derived from the covariance of matrix of the sample set and correspond approximately to $1\sigma$ (black solid ellipse) and $2\sigma$ (black dotted ellipse).
+$r_s$ with $1\sigma$ scatter (blue, see Equation \eqref{eq:prior_c200}).
+We find slight covariances between $\Upsilon_\text{I,*}$,  $r_s$ and $\beta_z$: The smaller the DM contribution in the center (i.e., the larger $\Upsilon_\text{I,*}$), the less concentrated is the halo (i.e., the larger $r_s$) and the more velocity anisotropy is needed to reproduce the central $v_\text{rms}$ dip.
+As the effect of $v_{200}$ is mostly at larger radii, this parameter doesn't show any covariances, but is also mostly constrained by the prior.\\The MCMC samples are colour coded according to their probability (darker red for higher probability); the sample point with the highest probability is marked by a black diamond.
+The black cross is the mean of the distribution and the ellipses are derived from the covariance matrix of the MCMC samples and correspond approximately to $1\sigma$ (black solid ellipse) and $2\sigma$ (black dotted ellipse) confidence.
 The histograms of the marginalized 1D distributions are overplotted by the mean (black solid lines) and $1\sigma$ error (black dashed lines), whose values are also quoted in the figure and in Table \ref{tab:modelB4_bestfit}.
-The grey diamonds mark a random sub-selection of 12 samples; the corresponding models are shown in Figure \ref{fig:modelB4_models}.
-\Wilma{[TO DO: Maybe mention also: There are slight covariances between $\Upsilon_\text{I,*}$,  $r_s$ and $\beta_z$: The smaller the DM contribution in the center (i.e., the larger $\Upsilon_\text{I,*}$), the less concentrated is the halo (i.e., the larger $r_s$), the more velocity anisotropy is needed to reproduce the central dip.
-As the effect of $v_{200}$ is mostly at larger radii, this parameter doesn't show any covariances, but is also mostly constrained by the prior.
-]}}
+The grey diamonds mark a random sub-selection of 12 samples; the corresponding models are shown in Figure \ref{fig:modelB4_models}.}
 \label{fig:modelB4_triangle}
@@
 \end{subfigure}
-\caption{\Wilma{[TO DO: Rewrite caption]} Best fit JAM model including a NFW halo and velocity anisotropy with parameters given in Table \ref{tab:modelB4_bestfit}.
-The 12 lines shown correspond to the 12 models randomly drawn from the posterior probability distribution and marked as grey diamonds in Figure \ref{fig:modelB4_triangle}.
+\caption{JAM model including a NFW halo and velocity anisotropy with parameters given in Table \ref{tab:modelB4_bestfit} found as best fit to the stellar $v_\text{rms}$ data (blue dots) within $\sim3.5''$.
+\Wilma{[TO DO: Rewrite caption]}  The 12 lines shown correspond to the 12 models randomly drawn from the posterior probability distribution and marked as grey diamonds in Figure \ref{fig:modelB4_triangle}.
 Overplotted are the Einstein radius (red dotted line) and the effective half-light radius (black dotted line).
@@
 We use this as a rough estimate for the halo of J1331 and as Gaussian prior on $v_{200}$,
-\begin{equation*}
-p(v_{200}) = \mathscr{N}(200~\text{km s}^{-1},40~\text{km s}^{-1}).
-\end{equation*}
+\begin{equation}
+p(v_{200}) = \mathscr{N}(200~\text{km s}^{-1},40~\text{km s}^{-1}). \label{eq:prior_v200}
+\end{equation}
 
 We also use the concentration vs. halo mass relation by \citet{Maccio08} in Equation \eqref{eq:Maccio08} as a prior on the concentration, i.e.
-\begin{equation*}
-p(\log c_{200} \mid v_{200}) = \mathscr{N}\left(\langle \log c_{200} \rangle (M_{200}) \mid 0.105 \right).
-\end{equation*}
+\begin{equation}
+p(\log c_{200} \mid v_{200}) = \mathscr{N}\left(\langle \log c_{200} \rangle (M_{200}) \mid 0.105 \right). \label{eq:prior_c200}
+\end{equation}
 
@@
 \begin{equation*}
-p(\beta) = \mathscr{U}(-0.5,+0.5)
+p(\beta_z) = \mathscr{U}(-0.5,+0.5)
 \end{equation*}
@@
 \begin{eqnarray*}
-&&p(\Upsilon_\text{I,*},r_s,v_{200},\beta) \\
-&&= \frac{1}{\ln\left( 10 r_s\right)} p(\log c_{200} \mid v_{200}) \cdot p(v_{200}) \cdot p(\beta), 
+&&p(\Upsilon_\text{I,*},r_s,v_{200},\beta_z) \\
+&&= \frac{1}{\ln\left( 10 r_s\right)} p(\log c_{200} \mid v_{200}) \cdot p(v_{200}) \cdot p(\beta_z), 
 \end{eqnarray*}

### 2016-02-15 submitted_version_(v3.05)_16-02-15/Trick_J1331_modelling.tex
Paper is submitted.

--- 2016-01-29 LensingPaper_draft_v3.05.tex
@@
 \title[A spiral galaxy's mass distribution uncovered]{A spiral galaxy's mass distribution uncovered through lensing and dynamics}
-\author[W.H. Trick, G. van de Ven and A.A. Dutton]{Wilma H. Trick$^{1}$\thanks{E-mail:
-trick@mpia.de}, Glenn van de Ven$^{1}$ and Aaron A. Dutton$^{1}$\\
-$^{1}$Max-Planck-Institute for Astronomy, K\"{o}nigstuhl 17, 69117 Heidelberg, Germany}
+\author[W.H. Trick, G. van de Ven and A.A. Dutton]{Wilma H. Trick$^{1}$\thanks{E-mail: trick@mpia.de}, Glenn van de Ven$^{1}$ and Aaron A. Dutton$^{1,2}$\\
+$^{1}$Max-Planck-Institute for Astronomy, K\"{o}nigstuhl 17, 69117 Heidelberg, Germany\\
+$^{2}$New York University Abu Dhabi, PO Box 129188, Abu Dhabi, UAE\\}
 \begin{document}
@@
   \centering
-  \includegraphics[width=.9\linewidth]{fig/first_glimpse_450.ps}
+  \includegraphics[width=.9\linewidth]{first_glimpse_450.ps}
   \caption{J1331 in the F450W filter.}
@@
   \centering
-  \includegraphics[width=.9\linewidth]{fig/first_glimpse_814.ps}
+  \includegraphics[width=.9\linewidth]{first_glimpse_814.ps}
   \caption{J1331 in the F814W filter.}
@@
   \centering
-  \includegraphics[width=.9\linewidth]{fig/lens_imgpos.ps}
+  \includegraphics[width=.9\linewidth]{lens_imgpos.ps}
   \caption{Lensing images around the galaxy center.}
@@
   \centering
-  \includegraphics[width=.9\linewidth]{fig/stellar_kinematics_data.ps}
+  \includegraphics[width=.9\linewidth]{stellar_kinematics_data.ps}
   \caption{Stellar kinematics by \citet{SWELLSV}.}
@@
 According to the WMAP5 cosmology \citep{WMAP5cosm}, J1331 has an angular diameter distance of 414 Mpc, which translates into a transverse scaling of $1'' \hat{=} 2.01~\text{kpc}$.
+%--------------------------------------------
 
@@
 In particular, we use the images in the filters F450W, to identify the positions of the bluish lensing images, and F814W (I-band) to create a surface brightness model of the reddish bulge.
+%--------------------------------------------
 
@@
 where $I_{0,i}$ is the central surface brightness of each Gaussian, $L_i$ its total luminosity, $\sigma_i$ its dispersion along the major axis and $q'_i$ the axis ratio between the elliptical Gaussian's major and minor axis.
-
+%--------------------------------------------
+
+%--------------------------------------------
 \subsubsection{Convolution with the point spread function (PSF)}
-
+%--------------------------------------------
+
+%--------------------------------------------
 We can also expand the telescope's PSF as a sum of circular Gaussians,
@@
 The observed surface brightness distribution is a convolution of the intrinsic surface brightness in Equation \eqref{eq:MGEgeneral} with the PSF in Equation \eqref{eq:PSFgeneral}: $(I \ast \text{PSF}) (x',y')$ is then again a sum of Gaussians and can be directly fitted to an image of the galaxy in question.
-
+%--------------------------------------------
+
+%--------------------------------------------
 \subsubsection{Deprojection} \label{sec:MGE_theo_deprojection}
-
+%--------------------------------------------
+
+%--------------------------------------------
 $I(R',\theta')$ describes the intrinsic, to 2D projected light distribution or surface density of the galaxy.
@@
 $M_\text{ein}$ is similar to the projected mass within the critical curve $M_\text{crit}$.
+%--------------------------------------------
 
@@
 When we fix the slope $\alpha$, then the lens equation is a purely linear problem and can be solved numerically for the source position $(x_s',y_s')$ and the Fourier parameters $(a_k,b_k)$ given one observed image at position $(x'_i=R'_i \cos \theta'_i,y'_i=R'_i \sin \theta'_i)$.
+%--------------------------------------------
 
@@
 
-%--------------------------------------------
-\subsection{Surface photometry for J1331 with MGEs} \label{sec:MGE_results}
-%--------------------------------------------
-
-%--------------------------------------------
-In this section we construct a model for J1331's intrinsic light distribution in terms of MGEs (see Section \ref{sec:MGE_theo}).
-We use the HST image in the F814W (I-band) filter (Figure \ref{fig:F814W}) because J1331's central stellar component appears at longer wavelengths (i) smoother and more extended than in the F450W filter (Figure \ref{fig:F450W}), as it is less sensitive to young clumpy star-forming regions, (ii) much brighter than the bluish lensing images, and (iii) the imaging is less prone to extinction.
-
-%--------------------------------------------
-\subsubsection{PSF for the HST/F814W filter}
-%--------------------------------------------
-
-%--------------------------------------------
-The one-dimensional MGE in Equation \eqref{eq:PSFgeneral} is fitted to the radial profile of a synthetic image of the HST/F814W filter PSF, ignoring diffraction spikes and using the code by \citet{Cap02}.
-The MGE parameters of the normalized PSF model are given in Table \ref{tab:PSFMGEF814W}.
-
 %============================================
@@
 %--------------------------------------------
-\subsubsection{MGE for the inner and outer regions}
-%--------------------------------------------
-
-%--------------------------------------------
-We fit a MGE to J1331's smooth central region within $\sim 5''$ of the HST/WFPC2/WF3/F814W image (Figure \ref{fig:F814W}).
-Bright objects close to the bulge (blobs possibly belonging to the background galaxy and parts of the foreground spiral arm) were masked during the fit.
-J1331's galaxy center, position angle (with respect to North through East) and average apparent ellipticity (see Table \ref{tab:galaxyparameters}) are found from the images weighted first and second moment.
-The MGE fit splits the image in annuli with the given ellipticity and position angle and sectors of $5^\circ$ width and fits an 5-Gaussian MGE of the form in Equation \eqref{eq:MGEgeneral} convolved with the PSF MGE in Table \ref{tab:PSFMGEF814W} to it.
-The best fit MGE (PSF convolved) is compared to the data in Figure \ref{fig:MGEinnerRegions} and the corresponding parameters of the intrinsic surface brightness distribution are given in Table \ref{tab:MGEF814W}.
-The fit is a very good representation of the light distribution in the inner $5''$, but underestimates the light distribution further out.
-
-To get a handle on the light distribution also in the outer parts of J1331 where spiral arms dominate, we first fit a IRAF \citep{1993ASPC...52..173T} \emph{ellipse} model to the F814W image (masking the brightest blobs in the spiral arms and outer regions).
-Only then we fit a 7-Gaussian MGE to the smooth \emph{ellipse} model.
-The MGE does not perfectly reproduce the flatness of the \emph{ellipse} model at every radius (see Figure \ref{fig:MGEouterRegions}), but considering the spiral arm dominated outer regions of J1331 it is good enough for an approximate handling of the overall light distribution.
+\subsection{Surface photometry for J1331 with MGEs} \label{sec:MGE_results}
+%--------------------------------------------
+
+%--------------------------------------------
+In this section we construct a model for J1331's intrinsic light distribution in terms of MGEs (see Section \ref{sec:MGE_theo}).
+We use the HST image in the F814W (I-band) filter (Figure \ref{fig:F814W}) because J1331's central stellar component appears at longer wavelengths (i) smoother and more extended than in the F450W filter (Figure \ref{fig:F450W}), as it is less sensitive to young clumpy star-forming regions, (ii) much brighter than the bluish lensing images, and (iii) the imaging is less prone to extinction.
+
+%--------------------------------------------
+\subsubsection{PSF for the HST/F814W filter}
+%--------------------------------------------
+
+%--------------------------------------------
+The one-dimensional MGE in Equation \eqref{eq:PSFgeneral} is fitted to the radial profile of a synthetic image of the HST/F814W filter PSF, ignoring diffraction spikes and using the code by \citet{Cap02}.
+The MGE parameters of the normalized PSF model are given in Table \ref{tab:PSFMGEF814W}.
 %--------------------------------------------
@@
   \centering
-  \includegraphics[width=.8\columnwidth]{fig/1331F814Wsci_MGE_M.ps}
+  \includegraphics[width=.8\columnwidth]{1331F814Wsci_MGE_M.ps}
   \caption{MGE for J1331's inner regions.}
@@
   \centering
-  \includegraphics[width=.8\columnwidth]{fig/1331F814W_MGE_disk_L.ps}
+  \includegraphics[width=.8\columnwidth]{1331F814W_MGE_disk_L.ps}
   \caption{MGE and IRAF \emph{ellipse} model for J1331's outer regions.}
@@
 %--------------------------------------------
+\subsubsection{MGE for the inner and outer regions}
+%--------------------------------------------
+
+%--------------------------------------------
+We fit a MGE to J1331's smooth central region within $\sim 5''$ of the HST/WFPC2/WF3/F814W image (Figure \ref{fig:F814W}).
+Bright objects close to the bulge (blobs possibly belonging to the background galaxy and parts of the foreground spiral arm) were masked during the fit.
+J1331's galaxy center, position angle (with respect to North through East) and average apparent ellipticity (see Table \ref{tab:galaxyparameters}) are found from the images weighted first and second moment.
+The MGE fit splits the image in annuli with the given ellipticity and position angle and sectors of $5^\circ$ width and fits an 5-Gaussian MGE of the form in Equation \eqref{eq:MGEgeneral} convolved with the PSF MGE in Table \ref{tab:PSFMGEF814W} to it.
+The best fit MGE (PSF convolved) is compared to the data in Figure \ref{fig:MGEinnerRegions} and the corresponding parameters of the intrinsic surface brightness distribution are given in Table \ref{tab:MGEF814W}.
+The fit is a very good representation of the light distribution in the inner $5''$, but underestimates the light distribution further out.
+
+To get a handle on the light distribution also in the outer parts of J1331 where spiral arms dominate, we first fit a IRAF \citep{1993ASPC...52..173T} \emph{ellipse} model to the F814W image (masking the brightest blobs in the spiral arms and outer regions).
+Only then we fit a 7-Gaussian MGE to the smooth \emph{ellipse} model.
+The MGE does not perfectly reproduce the flatness of the \emph{ellipse} model at every radius (see Figure \ref{fig:MGEouterRegions}), but considering the spiral arm dominated outer regions of J1331 it is good enough for an approximate handling of the overall light distribution.
+%--------------------------------------------
+
+%--------------------------------------------
 \subsubsection{Transformation into physical units}
@@
 \centering
-  \includegraphics[width=\linewidth]{fig/lens_all_in_one.ps}
+  \includegraphics[width=\linewidth]{lens_all_in_one.ps}
 \caption{Lensing model (Table \ref{tab:bestfitlensmodel}) found as best fit to the lensing image positions.
@@
 In this section we use the gravitational lensing formalism summarized in Section \ref{sec:lensing_theo} to fit a scale-free galaxy mass model to the positions of the lensing images observed in J1331's central region.
+%--------------------------------------------
 
@@
   \centering
-  \includegraphics[width=.9\linewidth]{fig/lens_surface_brightness.ps}
+  \includegraphics[width=.9\linewidth]{lens_surface_brightness.ps}
   \caption{Observed light distribution.}
@@
   \centering
-  \includegraphics[width=.9\linewidth]{fig/lens_surface_density.ps}
+  \includegraphics[width=.9\linewidth]{lens_surface_density.ps}
   \caption{Lens model mass distribution.}
@@
   \centering
-  \includegraphics[width=.9\linewidth]{fig/paper_lensmass_brightness_compare.ps}
+  \includegraphics[width=.9\linewidth]{paper_lensmass_brightness_compare.ps}
   \caption{Comparison of mass and light.}
@@
 In the following we therefore set $\alpha=1$.
+%--------------------------------------------
 
@@
   \centering
-  \includegraphics[height=6cm]{fig/lensing_JAM_comparision.ps}
+  \includegraphics[height=6cm]{lensing_JAM_comparision.ps}
   \caption{Comparison (not a fit!) of the symmetrized stellar $v_\text{rms}$ data of J1331 (blue dots) with JAM models generated from mass distributions which were independently derived from lensing constraints in Section \ref{sec:results_lensing} (red lines).
@@
   \centering
-  \includegraphics[height=6cm]{fig/jam_A2_vrms.ps}
+  \includegraphics[height=6cm]{jam_A2_vrms.ps}
   \caption{Comparison of the symmetrized $v_\text{rms}$ data of J1331 (blue dots) with a best fit dynamical JAM model (orange line) assuming ``mass-follows-light'' and with two free parameters: $\Upsilon_\text{I,tot}^\text{dyn}$, the total constant I-band mass-to-light ratio which converts the observed surface brightness in Table \ref{tab:MGEF814W} into a mass distribution, and the velocity anisotropy parameter $\beta_z$.
@@
   \centering
-  \includegraphics[height=6cm]{fig/jam_G_vrms.ps}
+  \includegraphics[height=6cm]{jam_G_vrms.ps}
   \caption{Comparison of $v_\text{rms}$ data and best fit model.}
@@
   \centering
-  \includegraphics[height=6cm]{fig/jam_G_enclMass.ps}
+  \includegraphics[height=6cm]{jam_G_enclMass.ps}
   \caption{Projected local mass-to-light ratio profile and enclosed mass.}
@@
 We conclude that this is due to the well-known degeneracy between anisotropy and mass profile and the mass-follows-light model is \emph{not} a good representation of the mass distribution in J1331's inner regions.
+%--------------------------------------------
 
@@
 \centering
-\includegraphics[width=0.9\linewidth]{fig/B4_contour_plot_short.ps}
+\includegraphics[width=0.9\linewidth]{B4_contour_plot_short.ps}
 \caption{Posterior probability distribution (pdf) sampled with a Monte Carlo Markov Chain (MCMC) (red dots and histograms) for a JAM model fitted to the stellar $v_\text{rms}$ data, with NFW halo, parametrized by $r_s$ and $v_\text{200}$, a stellar mass distribution generated from the I-band MGE in Table \ref{tab:MGEF814W} and a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and constant velocity anisotropy $\beta_z$.
@@
   \centering
-  \includegraphics[width=0.9\linewidth]{fig/B4_rms_error_curves.ps}
+  \includegraphics[width=0.9\linewidth]{B4_rms_error_curves.ps}
   \caption{Comparison of the $v_\text{rms}$ data with the best fit JAM models.}
@@
   \centering
-  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_projmass.ps}
+  \includegraphics[width=0.9\linewidth]{B4_jam_profiles_errors_short_projmass.ps}
   \caption{Enclosed mass profiles for the best fit models.}
@@
 \centering
-\includegraphics[width=\linewidth]{fig/B4_rms_rot_curves_best_model.ps}
+\includegraphics[width=\linewidth]{B4_rms_rot_curves_best_model.ps}
 \caption{Generating the rotation curve $v_\text{rot}(R')$ (red solid line in middle panel) from the best fit JAM model with NFW halo by fitting the rotation parameter $\kappa'$ to the symmetrized $v_\text{rot}$ data within $R'\sim3.5''$ (solid blue dots in central panel).
@@
 We also include the Einstein mass $M(<R_\text{ein})$ with a 10\% error as an additional constraint in the fit.
+%--------------------------------------------
 
@@
 Overall, we were not able to obtain tight constraints on the cored logarithmic halo.
+%--------------------------------------------
 
@@
 \centering
-\includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_vcirc.ps}
+\includegraphics[width=0.9\linewidth]{B4_jam_profiles_errors_short_vcirc.ps}
 \caption{Comparison of the circular velocity curve of J1331's inner regions for different models: (i) JAM model with NFW DM halo from Section \ref{sec:results_JAM_NFW_results} and Figure \ref{fig:modelB4_models} (green).

### 2016-05-31 Answer_to_referee_report_LensingPaper.tex
Started including the referee comments.

\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{hyperref}	%for URLs
\usepackage[usenames,dvipsnames]{xcolor}	%for color text
\newcommand{\Comment}[1]{\textsl{\textcolor{Blue}{$\Longrightarrow$ {#1}}}}
\newcommand{\RM}{{\sl RoadMapping}}

\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\Wilma}[1]{\textcolor{Magenta}{#1}}
\newcommand{\Glenn}[1]{\textcolor{Green}{#1}}
\newcommand{\Aaron}[1]{\textcolor{Orange}{#1}}

\begin{document}

From:  	ae@ras.org.uk
Subject:  	MNRAS: MN-16-0473-MJ
Date:  	Mon, March 14, 2016 1:00 pm
To:  	trick@mpia.de
Cc:  	trick@mpia.de,glenn@mpia.de,dutton@nyu.edu

Dear Ms Trick

Copied below are the reviewer's comments on your manuscript entitled "A spiral
galaxy's mass distribution uncovered through lensing and dynamics", ref.
MN-16-0473-MJ, which you submitted to Monthly Notices of the Royal Astronomical
Society.

Minor revision of your manuscript is requested before it is reconsidered for
publication.

You should submit your revised version, together with your response to the
reviewer's comments via the Monthly Notices ScholarOne Manuscripts site
https://mc.manuscriptcentral.com/mnras.
Enter your Author Centre, where you will find your manuscript title listed under
"Manuscripts with Decisions." Under "Actions," click on "Create a Revision." Your
manuscript reference will be appended to denote a revision.

IMPORTANT: do not submit your revised manuscript as a new paper!

You will not be able to make your revisions to the originally submitted files of the
manuscript held on ScholarOne Manuscripts. Instead, you must delete the original
files and abstract and replace them with your revised files. Check that any requests
for colour publication or online-only publication are correct. Carefully proof read
the resulting PDF and HTML files that are generated. If you have used a .bib file to
generate your bibliography in Latex, please include this in your .tar archive along
with the .bbl and .tex files; this will aid the editing and typesetting process.

When submitting your revised manuscript, you will be able to respond to the comments
made by the reviewer in the space provided. You should also use this space to
document any changes you make to the original manuscript. In order to expedite the
processing of the revised manuscript, please be as specific as possible in your
response to the reviewer. Changes to the manuscript should be highlighted (e.g. in
bold or colour), to assist the referee and editor. Along with the highlighted
manuscript you should also upload clean files (remove any bold font/track changes)
for our publishers, as accepted manuscripts are now immediately published online
ahead of the proof-corrected version.

Because we are trying to facilitate timely publication of manuscripts submitted to
MNRAS, your revised manuscript should be uploaded promptly. If you do not submit
your revision within six months, we may consider it withdrawn and request it be
resubmitted as a new submission.

Please note that, due to the tight schedule, any post-acceptance changes notified
after the paper has gone into production (i.e. the day after the acceptance email is
sent) cannot be incorporated into the paper before it is typeset. Such changes will
therefore need to be made as part of the proof corrections. To avoid excessive proof
corrections and the delay that these can cause, you are strongly encouraged to
ensure that each version of your paper submitted to MNRAS is completely ready for
publication!

I look forward to receiving your revised manuscript.

Regards,

Anna

Anna Evripidou
Assistant Editor
"Monthly Notices" and "Geophysical Journal International"
Royal Astronomical Society
Email: ae@ras.org.uk
Tel: (+44) 0207 734 3307 Ext. 124 (except Wednesday)
Tel: (+44) 0207 734 3307 Ext. 117 (Wednesday)

This message is confidential and is intended solely for the use of the individual(s)
to whom it is addressed.  If you have received this message in error, do not open
any attachment but please notify the sender (above) and delete this message from
your system.

cc: all listed co-authors.

Reviewer's Comments:
Reviewer: 1

Comments to the Author

====================================
\begin{itemize}

\item This is an interesting paper which makes neat use of the combination of stellar
kinematics and strong lensing to investigate the mass structure of the spiral galaxy
J1331.

\item The introduction could be re-written slightly to emphasise the points that the study
wants to investigate; for instance, the opening paragraph talks about the methods
used rather than the astrophysics that the study is hoping to probe. This could
probably be removed altogether, and the second paragraph promoted to the beginning. \Comment{I understand the referee's point. I personally like the first paragraph however very much and I think the most interesting thing in this paper is to see that dynamical modelling and lensing can give independent and comparable results even in such a peculiar system. Our contribution to solving the "core-cusp" problem is actually rather weak, so I would not want to start my introduction with it. What do you think? On the other hand mentioning more astrophysics is always a good thing... Any idea how we could put that more in the foreground?}

\item It would also be nice to include some more discussion of the possibility of a recent
merger in the galaxy's past in the introduction, as this is a really interesting
feature of the galaxy in question and is also a very active topic of research.

\item The manuscript in its current form is also slightly longer than necessary at certain
points: for instance, in section 3.2.1, it is not really necessary to present all
the lensing equations (e.g. the time delay, equation 7), and similarly, section
3.3.1 contains a lot of material that is implicit in Cappellari's JAM code, and
therefore does not need to be explained equation by equation here. Section 3.3.4
also rather throws the book at the NFW profile relations – it probably isn't
necessary to include equation 22. \Aaron{What does that mean, "throw the book at something"?}

\item From a scientific perspective, in section 4.3.3, the authors comment that the
varying M/L JAM model is unable to reproduce the dynamics when M/L is forced to be
always rising as a function of radius, but it would be interesting to see if the
model could be improved by removing this constraint. Perhaps the authors could add
such a model to this section, or else comment on why they do not attempt it. \Comment{We have indeed tried a ``mass-follows-light'' JAM model with constant anisotropy and free M/L profile early on in our investigations of J1331. This was unsuccessful to a degree that showing the result in the paper would not be reasonable. 1. JAM modelling (without additional mass components) allows us to assign a separate (constant) M/L to each Gaussian of the light MGE model. With only 5 Gaussians in the light MGE model and all of them with Gaussian dispersions $< 4$ arcsec (see Table 3) our ability to create arbitrary M/L profiles---especially at larger radii---is very restricted. At large radii, $\sim$ 7 arcsec, we would have effectively a pure mass-follows-light model with constant M/L and very flattened matter structure, which is not expected to be the case considering the results from the lensing model. 2. When leaving all 5 Gaussian M/Ls free, we got a wiggly and difficult to interpret M/L profile in the inner regions of the galaxy, with a slight decrease from 0 to $\sim$ 0.7 arcsec, a sharp rise around 1 arcsec, and a sharp drop around 3 arcsec. While this could be of course physical, there is no clear indication in the photometry that would support such an extreme profile. We therefore rather think that this wiggly profile was the result of over-fitting. 3. With only 6 data points and 5 fit M/L parameters within 5 arcsec, the fit result is not very well constrained or reliable. 4. It would have been of course possible to impose more constraints on the M/L profile and forcing it to rise in the center and to allow to profile to drop in the disk again. But with the spiral arms' dynamics starting to dominate at radii R $\gtrsim 5$ arcsec and our MGE light model not being a good model anymore in the outer regions, we thought it would not be reasonable to force to fit too much, when we know that the model has only limited abilities and the information content of the data is limited as well. As we lay out in the discussion, constraints on a varying stellar M/L ratio should be motivated by stellar population analysis in the future---or use more kinematics measurements than just the ones along the major axis. }

\item In section 4.4.1, the NFW profile is fitted only to the inner data, and then is
shown to not provide a good model for the data beyond that point. This is not
entirely surprising, given that the outer data were not used to constrain the model!
What happens if the NFW profile is fitted to both small- and large- radius data at
once? (Perhaps it is impossible to find a good NFW model across the whole radius
range, but if this is the case, then it should be stated.) \Comment{??? We set out to investigate the rather peculiar kinematics in the center of J133, which is strongly affected by the merger. We investigate different possibilities (velocity anisotropy, strong dark matter contribution in the center...), but none gives a satisfying result that is also consistent with the outer regions.??? }

\item The discussion section is too non-committal and speculative in parts. For instance,
in section 5.1, the M/Ls inferred from a number of the different models are compared
with M/Ls from the literature, but the authors do not make any value judgement
between the different models to come to any firmer conclusions about what they
believe the most convincing description of the IMF to be. At the moment, this
section seems to just be trying to show that their various models can be made to
agree with previous models from the literature, but it would be much more
interesting if some attempt could be made to resolve all the different models (both
in this paper and in previous works) or at least present them in a more coherent
framework, to try to come up with a better picture of the nature of J1331's IMF. \Glenn{No idea how to tackle this!!!!!!!!}

\item In Section 5.2, the authors could make suggestions for what might be causing the two
$v_{rms}$ dips. Currently, they just state what cannot be the cause, but do not make any
more convincing suggestions – e.g. could it be associated with the possible recent
merger that is explored in Section 5.3? It would be more satisfying if some
suggestions like this could be put forward.

\item While the use of English is impressive given that it is not the main author's mother
tongue, I would also recommend giving the manuscript to a native speaker to correct
the number of grammatical errors that remain. \Aaron{Aaron, could you have another look at the paper, specifically for grammar errors? Or should I try to find a student who is willing to read the paper?}

\end{itemize}

\end{document}

### 2016-05-31 LensingPaper_draft_v4.01.tex
Started including the referee comments.

--- 2016-01-29 LensingPaper_draft_v3.05.tex
@@
 
+\usepackage[usenames,dvipsnames]{xcolor}
+\newcommand{\Wilma}[1]{\textcolor{Magenta}{#1}}
+\newcommand{\Glenn}[1]{\textcolor{Green}{#1}}
+\newcommand{\Aaron}[1]{\textcolor{Blue}{#1}}
+
+\usepackage[usenames,dvipsnames]{xcolor}
+\newcommand{\NOTE}[1]{\textcolor{Cyan}{#1}}
+\newcommand{\NEW}[1]{\textcolor{ForestGreen}{#1}}
+\newcommand{\OLD}[1]{\textcolor{Red}{#1}}
+%\newcommand{\OLD}[1]{}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %--------------------------------------------
+\Wilma{[Referee says: "The introduction could be re-written slightly to emphasise the points that the study wants to investigate; for instance, the opening paragraph talks about the methods used rather than the astrophysics that the study is hoping to probe.
+This could probably be removed altogether, and the second paragraph promoted to the beginning."]}
 Gravitational lensing and dynamical modelling provide independent constraints on the mass distribution of galaxies.
@@
 Finally, Section \ref{sec:Discussion} uses these results to discuss J1331's stellar mass-to-light ratio, central kinematics, possible merger history and starting points for future work.
+
+\Wilma{[Referee says: "It would also be nice to include some more discussion of the possibility of a recent
+merger in the galaxy's past in the introduction, as this is a really interesting
+feature of the galaxy in question and is also a very active topic of research."]}
 %--------------------------------------------
@@
 %--------------------------------------------
+\Wilma{[Referee says: "The manuscript in its current form is also slightly longer than necessary at certain
+points: for instance, in section 3.2.1, it is not really necessary to present all
+the lensing equations (e.g. the time delay, equation 7)"]}
 A gravitational lens is a mass distribution whose gravitational potential $\Phi$ acts as a lens for light coming from a source positioned somewhere on a plane behind the lens.
@@
 %--------------------------------------------
+\Wilma{[Referee says: "The manuscript in its current form is also slightly longer than necessary at certain
+points: [...] section
+3.3.1 contains a lot of material that is implicit in Cappellari's JAM code, and
+therefore does not need to be explained equation by equation here."]}
 JAM modelling assumes galaxies to be (i) collisionless (i.e., the collisionless Boltzmann equation for the distribution function $f(\vect{x},\vect{v},t)$ has to be satisfied, $\frac{\diff f(\vect{x},\vect{v},t)}{\diff t} = 0$), (ii) in a steady state ($\frac{\partial}{\partial t} = 0$), (iii) axisymmetric (best described in cylindrical coordinates $(R,z,\phi)$ and $\frac{\partial}{\partial \phi} = 0$).
@@
 %--------------------------------------------
+\Wilma{[Referee says: "The manuscript in its current form is also slightly longer than necessary at certain
+points: [...] Section 3.3.4
+also rather throws the book at the NFW profile relations – it probably isn't
+necessary to include equation 22."]}
 As mentioned above, JAM modelling allows to incorporate an invisible matter component in addition to the luminous matter in the form of an MGE.
@@
 The agreement between the Einstein mass and the independently found $M(<R_\text{ein}) = 7.49 \cdot 10^{10} M_\odot$ from dynamical modelling is striking.
+\Wilma{[TO DO: referee says: "From a scientific perspective, in section 4.3.3, the authors comment that the
+varying M/L JAM model is unable to reproduce the dynamics when M/L is forced to be
+always rising as a function of radius, but it would be interesting to see if the
+model could be improved by removing this constraint. Perhaps the authors could add
+such a model to this section, or else comment on why they do not attempt it." --> Add sentence that with 5 fit parameters and 6 data points within 5 arcsec and no additional information it is likely that we perform overfitting: The resulting best fit profile is wiggly and hard to interpret physically.]}
 %--------------------------------------------
@@
 %--------------------------------------------
+
+\Wilma{[TO DO: Referee says: "In section 4.4.1, the NFW profile is fitted only to the inner data, and then is
+shown to not provide a good model for the data beyond that point. This is not
+entirely surprising, given that the outer data were not used to constrain the model!
+What happens if the NFW profile is fitted to both small- and large- radius data at
+once? (Perhaps it is impossible to find a good NFW model across the whole radius
+range, but if this is the case, then it should be stated.)"]}
 
@@
 
+\Wilma{[TO DO: The referee says: "The discussion section is too non-committal and speculative in parts. For instance,
+in section 5.1, the M/Ls inferred from a number of the different models are compared
+with M/Ls from the literature, but the authors do not make any value judgement
+between the different models to come to any firmer conclusions about what they
+believe the most convincing description of the IMF to be. At the moment, this
+section seems to just be trying to show that their various models can be made to
+agree with previous models from the literature, but it would be much more
+interesting if some attempt could be made to resolve all the different models (both
+in this paper and in previous works) or at least present them in a more coherent
+framework, to try to come up with a better picture of the nature of J1331's IMF."]}
+
 %--------------------------------------------
@@
 
+\Wilma{[TO DO: The referee says: "In Section 5.2, the authors could make suggestions for what might be causing the two
+$v_{rms}$ dips. Currently, they just state what cannot be the cause, but do not make any
+more convincing suggestions – e.g. could it be associated with the possible recent
+merger that is explored in Section 5.3? It would be more satisfying if some
+suggestions like this could be put forward."]}
+
 %--------------------------------------------

### 2016-06-01 LensingPaper_draft_v4.01.tex
Started re-writing the introduction.

@@
 \newcommand{\NEW}[1]{\textcolor{ForestGreen}{#1}}
-\newcommand{\OLD}[1]{\textcolor{Red}{#1}}
-%\newcommand{\OLD}[1]{}
+%\newcommand{\OLD}[1]{\textcolor{Red}{#1}}
+\newcommand{\OLD}[1]{}
 
@@
 This could probably be removed altogether, and the second paragraph promoted to the beginning."]}
-Gravitational lensing and dynamical modelling provide independent constraints on the mass distribution of galaxies.
-Combining them allows for valuable cross-checking opportunities to disentangle the galactic stellar and dark matter (DM) content.
+
+\NEW{Determining the overall mass distribution of galaxies and separating the dark matter (DM) from the stellar mass components is a crucial step in better understanding the structure and formation of galaxies and the nature of DM.}
+
+\OLD{Gravitational lensing and dynamical modelling provide independent constraints on the mass distribution of galaxies.
+Combining them allows for valuable cross-checking opportunities to disentangle the galactic stellar and dark matter (DM) content.}
 
@@
 
-Determining the overall mass distribution in massive galaxies and separating the DM from the stellar mass components is therefore a crucial step in better understanding the structure and formation of galaxies and nature of DM.
+\OLD{Determining the overall mass distribution in massive galaxies and separating the DM from the stellar mass components is therefore a crucial step in better understanding the structure and formation of galaxies and nature of DM.}
+
+\NEW{The mass distribution of massive galaxies can be observationally measured in completely independent fashions by gravitational lensing and dynamical modelling.
+Combining these two methods allows for valuable cross-checking opportunities to disentangle the galactic stellar and DM content.}
 
@@
 
-\citet{SWELLSI} confirmed that J1331 is a strong gravitational lens, measured its apparent brightness and estimated the stellar masses of disk and bulge.
+\NEW{J1331 is therefore of special interest and a convenient candidate to investigate observationally if and how a merger might have modified the DM distribution of a massive galaxy.
+This would require in particular a precise disentanglement of stellar and DM components in the galaxy's inner regions.}
+
+\NEW{J1331 has already been the subject of several studies:} \citet{SWELLSI} confirmed that J1331 is a strong gravitational lens, measured its apparent brightness and estimated the stellar masses of disk and bulge.
 The lensing properties of J1331 were first analysed by \citet{SWELLSIII}.
@@
 
-The goal of this work is to complement the previous studies of J1331 by an in-depth analysis of the matter distribution in J1331's inner regions.
-We use stellar dynamical modelling in addition to lensing constraints, similar to a study of the Einstein Cross by \citet{GlennEC}.
+\OLD{The goal of this work is to complement the previous studies of J1331 by an in-depth analysis of the matter distribution in J1331's inner regions.}\NEW{The goal of this work is now the in-depth analysis of the matter distribution in J1331's inner regions.
+This will complement the previous studies of J1331 and is an important step in understanding J1331's merger-modified mass structure.} We use stellar dynamical modelling in addition to lensing constraints, similar to a study of the Einstein Cross by \citet{GlennEC}.
 We attempt to disentangle the stellar and DM components and test if employed axisymmetric Jeans models work also in the presence of a counter-rotating core.
-Ideally, this work on J1331 could also help understanding how mergers modify the mass distribution of a galaxy.
+\OLD{Ideally, this work on J1331 could also help understanding how mergers modify the mass distribution of a galaxy.}
 

### 2016-06-02 LensingPaper_draft_v4.01.tex
Started shortening the Lensing theory section.

@@
 
-\NEW{J1331 is therefore of special interest and a convenient candidate to investigate observationally if and how a merger might have modified the DM distribution of a massive galaxy.
+\NEW{J1331 is therefore of special interest and a convenient candidate to investigate observationally if and how a merger might have modified the DM and stellar distribution of a massive galaxy.
 This would require in particular a precise disentanglement of stellar and DM components in the galaxy's inner regions.}
@@
 
-The total time delay of a deflected light path through $\vect{\theta}$ with respect to the unperturbed light path is given by 
+\OLD{The total time delay of a deflected light path through $\vect{\theta}$ with respect to the unperturbed light path is given by 
 \begin{equation}
@@
 \end{equation}
- According to Fermat's principle the image positions will be observed at the extrema of $\Delta t(\vect{\theta})$.
+ According to Fermat's principle the image positions will be observed at the extrema of $\Delta t(\vect{\theta})$.}
 
@@
 For $\alpha=1$ the critical curve is a contour of constant surface density of the mass model.
-The grey  lines show contours of the time delay surface given by Equation \eqref{eq:timedelay}.
+The grey  lines show contours of the time delay surface given by Equation \OLD{\eqref{eq:timedelay}}\NEW{(63) in \citet{1996astro.ph..6001N}}.
 Not only the position of the extrema, but also their shape is consistent with the observed, extended images, even though we did not use information about the image shape in the analysis.}
@@
 The source is located close to a cusp of the diamond-shaped caustic: a lensing configuration for which we indeed expect four images.
-Figure \ref{fig:bestfitlensmodel} also shows the (smoothed) residuals from the F450W image subtracted by an IRAF \emph{ellipse} brightness model and the contours of the best fit model's time delay surface.
-This demonstrates that, although we did not include any information about the shape of the lensing images in the fit, it is consistent with the predicted distortion for an extended source.
+Figure \ref{fig:bestfitlensmodel} also shows the (smoothed) residuals from the F450W image subtracted by an IRAF \emph{ellipse} brightness model and the contours of the best fit model's time delay surface \NEW{(see \S 3.3.1 in \citet{1996astro.ph..6001N}).
+Fermat's principle states that the image positions are observed at the extrema of the time delay surface.
+And even though}\OLD{.
+This demonstrates that, although} we did not include any information about the shape of the lensing images in the fit, it is consistent with the predicted distortion for an extended source.
 

### 2016-06-03 LensingPaper_draft_v4.01.tex
Finished editing of section on lensing theory. Started editing section on JAM theory.

@@
 %--------------------------------------------
-\Wilma{[Referee says: "The manuscript in its current form is also slightly longer than necessary at certain
-points: for instance, in section 3.2.1, it is not really necessary to present all
-the lensing equations (e.g. the time delay, equation 7)"]}
 A gravitational lens is a mass distribution whose gravitational potential $\Phi$ acts as a lens for light coming from a source positioned somewhere on a plane behind the lens.
@@
 \begin{equation}
-\psi(\vect{\theta}) := \frac{D_{ds}}{D_d D_s} \frac{2}{c^2} \int \Phi(\vect{r}=D_d \vect{\theta},z') {\ \mathrm d} z', \label{eq:psidef}
+\psi(\vect{\theta}) \OLD{:=}\NEW{\equiv} \frac{D_{ds}}{D_d D_s} \frac{2}{c^2} \int \Phi(\vect{r}=D_d \vect{\theta},z') {\ \mathrm d} z', \label{eq:psidef}
 \end{equation}
@@
 \end{equation}
-describes how the source position changes with image position. It also describes the distortion of the image shape for an extended source and its magnification $\mu$ due to lensing according to
-$$\mu \equiv \frac{\text{image area}}{\text{source area}} = \det \mathscr{M}.$$
+describes how the source position changes with image position\OLD{.
+It also describes}\NEW{,} the distortion of the image shape for an extended source and its magnification \OLD{$\mu$ due to lensing according to}\NEW{$\mu \equiv \text{image area}/\text{source area} = \det \mathscr{M}$}.
+\OLD{$$\mu \equiv \frac{\text{image area}}{\text{source area}} = \det \mathscr{M}.$$}
 Lines in the image plane for which the magnification becomes infinite, i.e., $\det \mathscr{M}^{-1} = 0$, are called critical curves.
@@
 The Einstein mass $M_\text{ein}$ and Einstein radius $R_\text{ein}$ are defined via the relation
-\begin{equation*}
+\begin{equation}
 M_\text{ein} \equiv M(<R_\text{ein}) \overset{!}{=} \pi \Sigma_\text{crit} R_\text{ein}^2,
-\end{equation*}
-where $\Sigma_\text{crit} \equiv \frac{c^2}{4\pi G} \frac{D_s}{D_d D_{ds}}$ is the critical density and $M(<R_\text{ein})$ is the mass projected along the line-of-sight within $R'=R_\text{ein}$.
+\end{equation}
+where 
+\begin{equation}
+\Sigma_\text{crit} \equiv \frac{c^2}{4\pi G} \frac{D_s}{D_d D_{ds}}
+\end{equation}
+is the critical density and $M(<R_\text{ein})$ is the mass projected along the line-of-sight within $R'=R_\text{ein}$.
 $M_\text{ein}$ is similar to the projected mass within the critical curve $M_\text{crit}$.
@@
 therefore does not need to be explained equation by equation here."]}
-JAM modelling assumes galaxies to be (i) collisionless (i.e., the collisionless Boltzmann equation for the distribution function $f(\vect{x},\vect{v},t)$ has to be satisfied, $\frac{\diff f(\vect{x},\vect{v},t)}{\diff t} = 0$), (ii) in a steady state ($\frac{\partial}{\partial t} = 0$), (iii) axisymmetric (best described in cylindrical coordinates $(R,z,\phi)$ and $\frac{\partial}{\partial \phi} = 0$).
+\OLD{JAM modelling assumes galaxies to be (i) collisionless (i.e., the collisionless Boltzmann equation for the distribution function $f(\vect{x},\vect{v},t)$ has to be satisfied, $\frac{\diff f(\vect{x},\vect{v},t)}{\diff t} = 0$), (ii) in a steady state ($\frac{\partial}{\partial t} = 0$), (iii) axisymmetric (best described in cylindrical coordinates $(R,z,\phi)$ and $\frac{\partial}{\partial \phi} = 0$).
 From this follow the axisymmetric Jeans equations as the vector-valued first moment of the Boltzmann equation, i.e.,
@@
 \int \vect{v} \frac{\diff f}{\diff t} \Diff3 v = 0.
-\end{equation*}
-To be able to solve the Jeans equations, additional assumptions about the velocity ellipsoid tensor $\langle v_i v_j\rangle$ have to be made.
+\end{equation*}}
+\NEW{JAM modelling assumes galaxies to be (i) collisionless, (ii) in a steady state and (iii) axisymmetric.
+With these assumptions the axisymmetric Jeans equations follow from the vector-valued first moment of the collisionless Boltzmann equation (see Equations (4.221)-(4.222) in \Wilma{???}).
+The Jeans equations are functions of the second velocity moments $\langle v_i v_j\rangle$ (with $i,j\in(R,z,\phi)$), the stellar tracer number density \Wilma{Continue????????}} To be able to solve the Jeans equations, additional assumptions about the velocity ellipsoid tensor $\langle v_i v_j\rangle$ have to be made.
 We follow \citet{Cap08} and assume firstly that the galaxy's velocity ellipsoid is aligned with the cylindrical coordinate system, i.e., $\langle v_R v_z\rangle = \langle v_z v_\phi \rangle = \langle v_\phi v_R \rangle = 0$.

### 2016-06-04 LensingPaper_draft_v4.01.tex
Corrected typo.
Done editing section 3.3.1 on the theory behind JAM.

@@
 %_____FORMAT_____
-\usepackage{hyperref} %ready-to-lick referencing
+\usepackage{hyperref} %ready-to-click referencing
 
@@
 %--------------------------------------------
-\Wilma{[Referee says: "The manuscript in its current form is also slightly longer than necessary at certain
-points: [...] section
-3.3.1 contains a lot of material that is implicit in Cappellari's JAM code, and
-therefore does not need to be explained equation by equation here."]}
 \OLD{JAM modelling assumes galaxies to be (i) collisionless (i.e., the collisionless Boltzmann equation for the distribution function $f(\vect{x},\vect{v},t)$ has to be satisfied, $\frac{\diff f(\vect{x},\vect{v},t)}{\diff t} = 0$), (ii) in a steady state ($\frac{\partial}{\partial t} = 0$), (iii) axisymmetric (best described in cylindrical coordinates $(R,z,\phi)$ and $\frac{\partial}{\partial \phi} = 0$).
@@
 \NEW{JAM modelling assumes galaxies to be (i) collisionless, (ii) in a steady state and (iii) axisymmetric.
-With these assumptions the axisymmetric Jeans equations follow from the vector-valued first moment of the collisionless Boltzmann equation (see Equations (4.221)-(4.222) in \Wilma{???}).
-The Jeans equations are functions of the second velocity moments $\langle v_i v_j\rangle$ (with $i,j\in(R,z,\phi)$), the stellar tracer number density \Wilma{Continue????????}} To be able to solve the Jeans equations, additional assumptions about the velocity ellipsoid tensor $\langle v_i v_j\rangle$ have to be made.
+With these assumptions the axisymmetric Jeans equations follow from the vector-valued first moment of the collisionless Boltzmann equation (see Equations (4.221)-(4.222) in \citet{2008gady.book.....B}).
+The Jeans equations are functions of the second velocity moments $\langle v_i v_j\rangle$ (with $i,j\in(R,z,\phi)$), the number density of (stellar) tracers $n(\vect{x})$, and the galaxy's gravitational potential $\Phi(\vect{x})$ generated by the mass density $\rho(\vect{x})$.}
+
+To be able to solve the Jeans equations, additional assumptions about the velocity ellipsoid tensor $\langle v_i v_j\rangle$ have to be made.
 We follow \citet{Cap08} and assume firstly that the galaxy's velocity ellipsoid is aligned with the cylindrical coordinate system, i.e., $\langle v_R v_z\rangle = \langle v_z v_\phi \rangle = \langle v_\phi v_R \rangle = 0$.
@@
 where $\beta_z$ is the velocity anisotropy parameter.
-This reduces the Jeans equations to two equations for $\langle v_z^2 \rangle$ and $\langle v_\phi^2 \rangle$ which can be solved by means of one integration,
+\OLD{This reduces the Jeans equations to two equations for $\langle v_z^2 \rangle$ and $\langle v_\phi^2 \rangle$ which can be solved by means of one integration,
 \begin{eqnarray}
@@
 \end{eqnarray}
-where $n(\vect{x}) \equiv \int f(\vect{x},\vect{v}) \Diff3 v$ is the number density of (stellar) tracers and $\Phi(\vect{x})$ the galaxy's gravitational potential generated by the mass density $\rho(\vect{x})$.
+where $n(\vect{x}) \equiv \int f(\vect{x},\vect{v}) \Diff3 v$ is the number density of (stellar) tracers and $\Phi(\vect{x})$ the galaxy's gravitational potential generated by the mass density $\rho(\vect{x})$.}
 
@@
 The MGE for $\Phi(R,z)$ is generated from the mass density MGE by integrating the Poisson equation \citep{1994A&A...285..723E}.
-Equations \eqref{eq:Jeans1} and \eqref{eq:Jeans2} together with \eqref{eq:bz} provide the velocity dispersion tensor $\langle v_i v_j \rangle(R,z) = \langle v_i^2 \rangle(R,z)$ (with $i,j \in \{ R,\phi, z\}$ and $\langle v_i v_j \rangle=0$ if $i\neq j$).
-$\langle v_i^2 \rangle$ is then rotated by the inclination angle $i$ to the coordinate system of the observer; $(x',y')$ is the plane of the sky and $z'$ the line-of-sight, where $x'$ is alinged with the galaxy's major axis.
-Taking a light-weighted projection along the line-of-sight gives a model prediction for the line-of-sight velocity second moment, which is comparable to actual spectroscopic measurements of the second velocity moment.
-Details of the derivation using the MGE formalism are given in \citet{Cap08} and in the appendix of \citet{GlennEC}.
-We therefore just give the result for the line-of-sight second velocity moment prediction from the Jeans equations,
-\begin{eqnarray}
+\OLD{Equations \eqref{eq:Jeans1} and \eqref{eq:Jeans2} together with \eqref{eq:bz} provide the velocity dispersion tensor $\langle v_i v_j \rangle(R,z) = \langle v_i^2 \rangle(R,z)$ (with $i,j \in \{ R,\phi, z\}$ and $\langle v_i v_j \rangle=0$ if $i\neq j$).}
+
+\NEW{In this way one can now calculate an unambiguous model prediction for the velocity dispersion tensor $\langle v_i v_j \rangle(R,z) = \langle v_i^2 \rangle(R,z)$ (with $i,j \in \{ R,\phi, z\}$ and $\langle v_i v_j \rangle=0$ if $i\neq j$).
+To compare it with observations, $\langle v_i^2 \rangle(R,z)$ has to be}\OLD{$\langle v_i^2 \rangle$ is then} rotated by the inclination angle $i$ to the coordinate system of the observer; $(x',y')$ is the plane of the sky and $z'$ the line-of-sight, where $x'$ is alinged with the galaxy's major axis.
+Taking a light-weighted projection along the line-of-sight gives a model prediction for the line-of-sight velocity second moment \NEW{$\langle v_\text{los}^2\rangle(x',y')$}, which is comparable to actual spectroscopic measurements of the second velocity moment.
+Details of the derivation \NEW{from the Jeans equations} using the MGE formalism are \OLD{given}\NEW{laid out} in \citet{Cap08} and in the appendix of \citet{GlennEC}.
+\OLD{We therefore just give the result for the line-of-sight second velocity moment prediction from the Jeans equations,}\NEW{The result for $\langle v_\text{los}^2\rangle(x',y')$ in particular is given in Equation (28) and Equation (A18), respectively.}
+\OLD{\begin{eqnarray}
 &&\left(I \langle v_\text{los}^2\rangle\right)(x',y')\nonumber\\
@@
 \mathscr{D} &=& 1 - \frac{q^{2}_i}{1-\beta_{z,i}} - \left[ \left(1-\frac{1}{1-\beta_{i,z}}\right)\mathscr{C} + \frac{1-q^{2}_k}{1-\beta_{z,i}}\right] u^2.\nonumber
-\end{eqnarray*}
-The JAM modelling code by \citet{Cap08} evaluates Equation \eqref{eq:explicitLOSvelCap} numerically for a given luminous tracer and mass distribution MGE and a given inclination.
+\end{eqnarray*}}
+
+The JAM modelling code by \citet{Cap08} evaluates \OLD{Equation \eqref{eq:explicitLOSvelCap}}\NEW{this expression for $\langle v_\text{los}^2\rangle(x',y')$} numerically for a given luminous tracer and mass distribution MGE and a given inclination.
+\Wilma{[TO DO: MAke sure M and N are introduced somewhere.]}
 %--------------------------------------------

### 2016-06-06 LensingPaper_draft_v4.01.tex
Continued editing JAM theory section. References in introduction.

@@
 %--------------------------------------------
-\Wilma{[Referee says: "The introduction could be re-written slightly to emphasise the points that the study wants to investigate; for instance, the opening paragraph talks about the methods used rather than the astrophysics that the study is hoping to probe.
-This could probably be removed altogether, and the second paragraph promoted to the beginning."]}
-
 \NEW{Determining the overall mass distribution of galaxies and separating the dark matter (DM) from the stellar mass components is a crucial step in better understanding the structure and formation of galaxies and the nature of DM.}
@@
 This discrepancy, known as the core-cusp problem, might be resolved by galaxy formation processes such as mergers and outflows (e.g., \citealt{2001ApJ...560..636E,2012MNRAS.421.3464P}).
+\NEW{Especially the influence of mergers on the DM and baryonic structure of galaxies is currently an active field of research (e.g., \citealt{2009ApJ...697L..38J,2010ApJ...712...88L,2012MNRAS.425.3119H,2015MNRAS.453.2447D}).}
 
@@
 
-\NEW{J1331 is therefore of special interest and a convenient candidate to investigate observationally if and how a merger might have modified the DM and stellar distribution of a massive galaxy.
-This would require in particular a precise disentanglement of stellar and DM components in the galaxy's inner regions.}
+\NEW{J1331 is therefore of special interest and a convenient candidate to investigate observationally if and how a merger might have modified the DM and stellar distribution of a massive spiral galaxy.
+This requires in particular a precise disentanglement of stellar and DM components in the galaxy's inner regions.}
 
@@
 Finally, Section \ref{sec:Discussion} uses these results to discuss J1331's stellar mass-to-light ratio, central kinematics, possible merger history and starting points for future work.
-
-\Wilma{[Referee says: "It would also be nice to include some more discussion of the possibility of a recent
-merger in the galaxy's past in the introduction, as this is a really interesting
-feature of the galaxy in question and is also a very active topic of research."]}
 %--------------------------------------------
@@
 \end{equation*}
-The model in Equation \eqref{eq:explicitLOSvelCap} predicts the intrinsic $\langle v_\text{los}^2 \rangle_\text{intr}\equiv\langle v_\text{los}^2\rangle$ at a given position on the sky, which needs then to be modified to $\langle v_\text{los}^2 \rangle_\text{obs}$ according to the mode of observation to be comparable to the measurements.
+\OLD{The model in Equation \eqref{eq:explicitLOSvelCap}}\NEW{The model derived from the Jeans equations as outlined in Section \ref{sec:model_JAM_JAM}} predicts the intrinsic $\langle v_\text{los}^2 \rangle_\text{intr}\equiv\langle v_\text{los}^2\rangle$ at a given position on the sky, which needs then to be modified to $\langle v_\text{los}^2 \rangle_\text{obs}$ according to the mode of observation to be comparable to the measurements.
 The measured $v_\text{rms}$ is a light-weighted mean for a pixel along the long-slit of the spectrograph, with width $L_y = 1''$ \citep{SWELLSV} and a certain given extent along the galaxy's major axis, $L_x$, i.e., for a rectangular aperture
@@
 \end{eqnarray*}
-If provided with the convolution kernel, the JAM code\footnote{The IDL code package for Jeans Anisotropic Models (JAM) by \citet{Cap08} is available online at \url{http://www-astro.physics.ox.ac.uk/~mxc/software}.
-The version from June 2012 was used in this work.} by \citet{Cap08} performs the convolution numerically.
+\NEW{We modified the JAM code by \citet{Cap08} to use this convolution kernel with non-square pixels.
+The JAM code then}\OLD{If provided with the convolution kernel, the JAM code\footnote{The IDL code package for Jeans Anisotropic Models (JAM) by \citet{Cap08} is available online at \url{http://www-astro.physics.ox.ac.uk/~mxc/software}.
+The version from June 2012 was used in this work.} by \citet{Cap08}} performs the convolution numerically.
 We set $L_x = 0.21''$ as the width of the model pixel, and get a prediction for the actual measurements in bins of width $0.63''$, $1.26''$ and $1.89''$ \citep{SWELLSV} as light-weighted mean from each 3, 6 and 9 model pixels.
@@
 The intrinsic galaxy rotation curve is the first velocity moment $\langle v_\phi\rangle = \sqrt{\langle v_\phi^2 \rangle - \sigma_\phi^2}$.
-The observed rotation velocity is the projection of the light-weighted contributions to $\langle v_\phi\rangle$ along the line-of-sight \citep{Cap08},
+The observed rotation velocity is the projection of the light-weighted contributions to $\langle v_\phi\rangle$ along the line-of-sight \NEW{(Equation (31) in \citep{Cap08}).} \OLD{\citep{Cap08},
 \begin{equation*}
 I \langle v_\text{los}\rangle = \int_{-\infty}^{+\infty} \nu \langle v_\phi\rangle \cos \phi \sin i \diff z'.
-\end{equation*}
+\end{equation*}}
 The first velocity moments cannot be uniquely determined from the Jeans equations, which give only a prediction for the second velocity moments.
@@
 Then \citet{Cap08} relates the dispersions in $R$ and $\phi$ direction such that
-$$\langle v_\phi\rangle = \sqrt{\langle v_\phi^2 \rangle - \sigma_\phi^2} \equiv \kappa \sqrt{\langle v_\phi^2 \rangle - \langle v_R^2 \rangle},$$
+\begin{equation}
+\langle v_\phi\rangle = \sqrt{\langle v_\phi^2 \rangle - \sigma_\phi^2} \equiv \kappa \sqrt{\langle v_\phi^2 \rangle - \langle v_R^2 \rangle},
+\end{equation}
 and the $\kappa$ parameter quantifies the rotation: $\kappa = 0$ means no rotation at all and $|\kappa| = 1$ describes a velocity dispersion ellipsoid that is a circle in the $R$-$\phi$ plane \citep{Cap08}.
@@
 We can assign a constant $\kappa_i$ to every Gaussian in the MGE formalism and
-\begin{equation*}
+\OLD{\begin{equation*}
 \nu \langle v_\phi\rangle = \left[\nu \sum_{i=1}^N \kappa_i^2 \left( [\nu\langle v_\phi^2 \rangle]_i - [\nu\langle v_R^2 \rangle]_i\right) \right]^{1/2}
 \end{equation*} 
-is then the light-weighted circular velocity curve, given the second velocity moments found from the Jeans equations.
+is then}\NEW{calculate} the light-weighted circular velocity curve, given the second velocity moments found from the Jeans equations \NEW{(see Equations (37) and (38) in \citet{Cap08} for the intrinsic and observed rotation curves, respectively)}.
 
@@
 \begin{equation}
-\kappa(R) = \kappa' \frac{R^2 - R_0^2}{R^2 + R_0^2}. \label{eq:kappa_profile}
+\kappa(R) \OLD{=}\NEW{\equiv} \kappa' \frac{R^2 - R_0^2}{R^2 + R_0^2}. \label{eq:kappa_profile}
 \end{equation}
@@
 %--------------------------------------------
-We make an independent prediction for the $v_\text{rms}$ curve by evaluating Equation \eqref{eq:explicitLOSvelCap} (with $\beta_z = 0$) for the lens mass model in Table \ref{tab:bestfitlensmodel} ($\alpha = 1$, flat rotation curve).
+We make an independent prediction for the $v_\text{rms}$ curve by evaluating \OLD{Equation \eqref{eq:explicitLOSvelCap}}\NEW{the JAM equations} (with $\beta_z = 0$) for the lens mass model in Table \ref{tab:bestfitlensmodel} ($\alpha = 1$, flat rotation curve).
 In addition, we also calculate a  $v_\text{rms}$ curve for two lens models which were found analogously, but assumed a slightly rising (falling) rotation curve slope of $\alpha=1.1$ ($\alpha=0.9$).

### 2016-06-08 LensingPaper_draft_v4.01.tex
Wrote section that speculates on the matter distribution of J1331.

@@
 %--------------------------------------------
-\section{Introduction}
+\section{Introduction} \label{sec:intro}
 %--------------------------------------------
@@
 %--------------------------------------------
-\Wilma{[Referee says: "The manuscript in its current form is also slightly longer than necessary at certain
-points: [...] Section 3.3.4
-also rather throws the book at the NFW profile relations – it probably isn't
-necessary to include equation 22."]}
 As mentioned above, JAM modelling allows to incorporate an invisible matter component in addition to the luminous matter in the form of an MGE.
@@
 and two free parameters, the scale length $r_s$ and a parameter describing the total mass of the halo.
-We will use $v_\text{200}$, which is the circular velocity at the radius $r_\text{200}$ within which the mean density of the halo is 200 times the cosmological critical density $\rho_\text{crit} \equiv (2H^2)/(8\pi G)$, i.e.,
-\begin{eqnarray*}
+We will use $v_\text{200}\NEW{\equiv \sqrt{GM_{200}/r_{200}}}$, which is the circular velocity at the radius $r_\text{200}$ within which the mean density of the halo is 200 times the cosmological critical density $\rho_\text{crit} \equiv (2H^2)/(8\pi G)$, \OLD{i.e.,}\NEW{ and where $M_{200} \equiv M(<r_{200}) \stackrel{!}{=} \frac 43 \pi r_{200}^3 \cdot \rho_\text{crit}(z=0)$.}
+\OLD{\begin{eqnarray*}
 M_\text{200} &=& M(<r_{200})\\
@@
 v_\text{200} &=& \sqrt{\frac{GM_{200}}{r_\text{200}}}
-\end{eqnarray*}
+\end{eqnarray*}}
 with $\rho_\text{crit}(z=0)=1.43 \cdot 10^{-7} M_\odot / \text{pc}^3$ in the WMAP5 cosmology by \citet{WMAP5cosm}.
-How much the mass is concentrated in the center of the NFW halo is given by the concentration parameter
+\OLD{How much the mass is concentrated in the center of the NFW halo is given by the concentration parameter
 \begin{equation}
 c_{200}\equiv r_{200} / r_s. \label{eq:NFW_c}
-\end{equation} 
+\end{equation}}
+\NEW{The mass concentration of the NFW halo is quantified by $c_{200}\equiv r_{200} / r_s$.}
 There is a close relation between the concentration and halo mass in simulations \citep{1996ApJ...462..563N}. \citet{Maccio08} found this relation for the WMAP5 cosmology to be
@@
 (their equation 10), with a Gaussian scatter of $\sigma_{\log c_{200}} = 0.105$ (their Table A2).
+\NEW{In Section \Wilma{[TO DO ???]} we will use this relation as prior information to guide the modelling towards realistic NFW halo shapes.}
 %--------------------------------------------
@@
 A slight drop could be expected when the reddish bulge turns into the bluish disk and the contribution of the stellar component becomes less due to a lower $\Upsilon_\text{I,*}$ for younger and bluer populations.
-
-In Figure \ref{fig:enclMass_modelG} we overplot the enclosed mass profile with the Einstein mass $M_\text{ein} = (7.77 \pm 0.33) \cdot 10^{10} M_\odot$ at the Einstein radius found from lensing in Table \ref{tab:bestfitlensmodel}.
+\NEW{Corresponding fitting attempts with the matter model at hand were however unsuccessful: Leaving all five $\Upsilon_{\text{I,tot,}i}$ free lead to over-fitting in the central regions of J1331, while not allowing for sufficient flexibility further out at $R'\gtrsim4''$ (because four of the five $\sigma_i$ in the light MGE in Table \ref{tab:MGEF814W} are $< 1.2''$).}
+
+\NEW{For the inner regions the model with rising $\Upsilon(R')$ seems to be a very good model:} In Figure \ref{fig:enclMass_modelG} we overplot the enclosed mass profile with the Einstein mass $M_\text{ein} = (7.77 \pm 0.33) \cdot 10^{10} M_\odot$ at the Einstein radius found from lensing in Table \ref{tab:bestfitlensmodel}.
 The agreement between the Einstein mass and the independently found $M(<R_\text{ein}) = 7.49 \cdot 10^{10} M_\odot$ from dynamical modelling is striking.
-\Wilma{[TO DO: referee says: "From a scientific perspective, in section 4.3.3, the authors comment that the
-varying M/L JAM model is unable to reproduce the dynamics when M/L is forced to be
-always rising as a function of radius, but it would be interesting to see if the
-model could be improved by removing this constraint. Perhaps the authors could add
-such a model to this section, or else comment on why they do not attempt it." --> Add sentence that with 5 fit parameters and 6 data points within 5 arcsec and no additional information it is likely that we perform overfitting: The resulting best fit profile is wiggly and hard to interpret physically.]}
 %--------------------------------------------
@@
 
+\NEW{As we are particularly interested in the disentanglement of DM and stellar matter in the inner regions (see Section \ref{sec:intro}), we restrict the $v_\text{rms}$ fit to a region $R'\lesssim3.5''$, approximately within the effective half-light radius $R_\text{eff}=2.6''$.
+The constraints on a DM halo just from this data might be weak.
+To guide the fit towards a realistic halo, we therefore impose several priors on NFW halo.}
+
 \citet{Dutton10} give a relation for halo vs.
@@
 
-We restrict the $v_\text{rms}$ fit to a region $R' \lesssim 3.5''$, approximately within the effective half-light radius $R_\text{eff} = 2.6''$.
-We also include the Einstein mass $M(<R_\text{ein})$ with a 10\% error as an additional constraint in the fit.
+\OLD{We restrict the $v_\text{rms}$ fit to a region $R' \lesssim 3.5''$, approximately within the effective half-light radius $R_\text{eff} = 2.6''$.
+}We also include the Einstein mass $M(<R_\text{ein})$ with a 10\% error as an additional constraint in the fit.
 %--------------------------------------------
@@
 There might be something unexpected with the $\sigma$ measurements around $\sim 5''$, but at large radii the best fit model NFW halo is simply too massive.
+
+\subsubsection{\NEW{Discussion}}
+
+\NEW{A fit to all nine available $v_\text{rms}$ data points forces the DM halo to be less massive.
+But with decreasing DM contribution in the inner regions the model approaches the mass-follows-light model in the center, that we already ruled out in Section \ref{sec:results_JAM_SB_MfL}.
+Allowing for free $\Upsilon_{*}(R')$, $\beta_z(R')$ and/or non-NFW $\rho_\text{halo}(r)$ profiles would over-fit the data again.
+Without further priors on the stellar $\Upsilon_{*}(R')$ and/or more data points, we can make only the following statement: A model with constant $\Upsilon_*$, moderately tangential \Wilma{[TO DO: Check]} $\beta_z$ and a spherical and massive DM component with high concentration can explain the central kinematics of J1331 very well, we have however ruled out that in this case the DM halo will follow a NFW halo at both small and large radii.}
 %--------------------------------------------
@@
 It cannot be due to tangential velocity anisotropy in the center alone (see Section \ref{sec:results_JAM_SB_MfL}, Figure \ref{fig:JAM_modelA2}).
-It also cannot be explained by a strong contribution of DM inside the bulge together with a moderate tagential velocity anisotropy, because the corresponding DM halos would still be too massive to fit the data in the outer regions (see Section \ref{sec:results_JAM_NFW}, Figure \ref{fig:modelB4_vrms}).
+It also cannot be explained by a strong contribution of DM inside the bulge together with a moderate tagential velocity anisotropy, because the corresponding \NEW{NFW} DM halo\OLD{s} would still be too massive to fit the data in the outer regions (see Section \ref{sec:results_JAM_NFW}, Figure \ref{fig:modelB4_vrms}).
 
@@
 %--------------------------------------------
+
+\subsection{\NEW{Speculations on J1331's matter distribution}}
+
+\NEW{The kinematics of the merger remnant J1331 are peculiar and hard to explain with standard modelling techniques.
+We think that in the end the truth will be somewhere in between the results of the different modelling attempts.}
+
+\NEW{The central $v_\text{rms}$ is most likely a combination of the three different aspects that we investigated separately: We expect a bit of tangential \Wilma{???} velocity anisotropy (Sections \ref{sec:results_JAM_SB_MfL} and \ref{sec:results_JAM_NFW}), a moderate contribution of a roundish DM halo (Sections 4.2.3 \Wilma{???} and 4.4.2) and different stellar populations inside the bulge due to the merger (Section 5.3) with different $\Upsilon_{*}$ but overall bottom-heavy IMF (Section 5.1), which add to an overall rising $\Upsilon_\text{tot}(R')$ profile.}
+
+\NEW{The drop in $v_\text{rms}$ around $R'\sim4''$ is most likely due to a sharp drop in $\Upsilon_{*}(R')$ at the transition from red bulge to blue disk (compare bulge size in Figures \ref{fig:F450W} and \ref{fig:F814W}).
+Unfortunately the spiral arms make the disk of the galaxy difficult to model.
+At these larger radii a possible mis-alignment of long-slit and Galaxy major axis would also cause a stronger underestimation of the true $v_\text{rot}$ and would add to the drop in $v_\text{rms}$.}
+
+\NEW{Around $R'\sim7''$ the rotation curve and dispersion show some wiggles which lead to a spontaneous rise of the $v_\text{rms}$.
+As the spiral arms cross the major axis around this radius, we suspect they cause this disturbance of the axisymmetric kinematics.
+The DM halo should also start to dominate the kinematics at larger radii, whose total mass we expect more of the order of what \citep{Dutton paper} \Wilma{???} found---unless J1331 has a strong kinematic warp in its disk, which cannot be detected in long-slit kinematics only.}
+
+\NEW{All of these speculations should be easily testable with 2D kinematics.} \Wilma{[TO DO: Proper referencing.]}
 

### 2016-06-09 LensingPaper_draft_v4.01.tex
Edited section on merger slightly.

@@
 Some of them capture the observed kinematics, but none of them work at both small and large radii.
-In the following we discuss possible reasons, also by comparing our results to previous work.
+\NEW{In the following we try to resolve some of the ambiguities by discussing possible reasons, by comparing our results to previous work and by venturing some guesses on the true nature of J1331's matter distribution, which should be easily testable by future observations.}\OLD{In the following we discuss possible reasons, also by comparing our results to previous work.}
+%--------------------------------------------
+
+%--------------------------------------------
+\subsection{On J1331's possible merger history\OLD{ and modelling failures}}
+%--------------------------------------------
+\NOTE{[This subsection was moved from a later position to the beginning of this section.]}
+
+%--------------------------------------------
+J1331 has a large counter-rotating stellar core within $\sim 2''$. This suggests a process in J1331's past in which two components with angular momenta oriented in opposite directions were involved.
+
+Accretion of gas on retrograde orbits and subsequent star formation could lead to a younger and counter-rotating stellar population.
+However, to form enough stars such that the net rotation of the large and massive core is retrograde, a very large amount of gas would have had to be accreted by J1331---which is not very likely.
+
+Galaxy mergers are another possible scenario.
+Major mergers can form kinematically decoupled cores (KDCs) (e.g., \citealt{2011MNRAS.414.2923K,2015ApJ...802L...3T}), if they include large amounts of gas \citep{2010ApJ...723..818H}.
+During a minor merger, the dense nucleus of a satellite galaxy on a retrograde orbit could survive the dissipationless accretion and spiral to the galaxy's core due to tidal friction (e.g., \citealt{1984ApJ...287..577K,1988ApJ...327L..55F}).
+
+Usually ellipticals and the bulges of massive spirals appear reddest in their center and get increasingly bluer with larger radii.
+Mergers can reverse this behaviour by inducing the creation of young stellar populations in the remnant's center.
+Major mergers can trigger star formation bursts (e.g., \citealt{2008gady.book.....B}, \S 8.5.5).
+After a minor merger the satellite's stellar population now residing in the remnant's core is in general younger than the massive progenitor's bulge \citep{1996AJ....112..839C,2010MNRAS.404.1775T}.
+The different stellar populations in a merger remnant can be associated with different $\Upsilon_*$ and in rare cases they even show up as a reverse colour gradient within the bulge in photometry \citep{1990ApJ...361..381B, 1997ApJ...481..710C}.
+
+Even though investigation of the photometry of J1331 did not reveal a distinct blue core in J1331, we cannot fully exclude the possibility that J1331 has such a $\Upsilon_*$ gradient (see discussion in Sections \ref{sec:results_JAM_SB_MfL} and \ref{sec:results_JAM_SB_gradient}).
+\NEW{Stellar population analysis with spectra taken at different positions within the bulge could provide further information on the true $\Upsilon_*(R')$.}\OLD{In this case the restrictive assumption of a constant $\Upsilon_*$ in our JAM modelling could have lead to wrong conclusions about the DM distribution.}
+
+Another way how galaxy encounters can modify the structure of galaxies is the excitation of warps \citep{1991wdir.book.....C,2013pss5.book..923S}.
+Warps lead to a twist in the projected kinematic major axis with radius, which is then also misaligned with the photometric major axis (\citealt{1998gaas.book.....B}, \S 8.2.4).
+From kinematics along the photometric major axis only it cannot be determined if such a twist or misalignment is present in J1331\NEW{, but it should be immediately visible in a 2D kinematic map}.\OLD{ But if it were, our modelling assumption of axisymmetry would not be satisfied anymore.}
+\Wilma{[TO DO: Mention that warps would require other modelling techniques than the axisymmetric Jeans models.]}
+
+\Wilma{[More: "We note that kinematics measured along an axis different from the kinematic major axis would result in $v_\text{rot}$ measurements being lower than the actual maximum $v_\text{circ}$.
+At large radii this could lead to an underestimation of the DM halo mass." somewhere else.]}
 %--------------------------------------------
@@
 
-%--------------------------------------------
-\subsection{On J1331's possible merger history and modelling failures}
-%--------------------------------------------
-
-%--------------------------------------------
-J1331 has a large counter-rotating stellar core within $\sim 2''$. This suggests a process in J1331's past in which two components with angular momenta oriented in opposite directions were involved.
-
-Accretion of gas on retrograde orbits and subsequent star formation could lead to a younger and counter-rotating stellar population.
-However, to form enough stars such that the net rotation of the large and massive core is retrograde, a very large amount of gas would have had to be accreted by J1331---which is not very likely.
-
-Galaxy mergers are another possible scenario.
-Major mergers can form kinematically decoupled cores (KDCs) (e.g., \citealt{2011MNRAS.414.2923K,2015ApJ...802L...3T}), if they include large amounts of gas \citep{2010ApJ...723..818H}.
-During a minor merger, the dense nucleus of a satellite galaxy on a retrograde orbit could survive the dissipationless accretion and spiral to the galaxy's core due to tidal friction (e.g., \citealt{1984ApJ...287..577K,1988ApJ...327L..55F}).
-
-Usually ellipticals and the bulges of massive spirals appear reddest in their center and get increasingly bluer with larger radii.
-Mergers can reverse this behaviour by inducing the creation of young stellar populations in the remnant's center.
-Major mergers can trigger star formation bursts (e.g., \citealt{2008gady.book.....B}, \S 8.5.5).
-After a minor merger the satellite's stellar population now residing in the remnant's core is in general younger than the massive progenitor's bulge \citep{1996AJ....112..839C,2010MNRAS.404.1775T}.
-The different stellar populations in a merger remnant can be associated with different $\Upsilon_*$ and in rare cases they even show up as a reverse colour gradient within the bulge in photometry \citep{1990ApJ...361..381B, 1997ApJ...481..710C}.
-
-Even though investigation of the photometry of J1331 did not reveal a distinct blue core in J1331, we cannot fully exclude the possibility that J1331 has such a $\Upsilon_*$ gradient (see discussion in Sections \ref{sec:results_JAM_SB_MfL} and \ref{sec:results_JAM_SB_gradient}).
-In this case the restrictive assumption of a constant $\Upsilon_*$ in our JAM modelling could have lead to wrong conclusions about the DM distribution.
-
-Another way how galaxy encounters can modify the structure of galaxies is the excitation of warps \citep{1991wdir.book.....C,2013pss5.book..923S}.
-Warps lead to a twist in the projected kinematic major axis with radius, which is then also misaligned with the photometric major axis (\citealt{1998gaas.book.....B}, \S 8.2.4).
-From kinematics along the photometric major axis only it cannot be determined if such a twist or misalignment is present in J1331.
-But if it were, our modelling assumption of axisymmetry would not be satisfied anymore.
-
-We note that kinematics measured along an axis different from the kinematic major axis would result in $v_\text{rot}$ measurements being lower than the actual maximum $v_\text{circ}$.
-At large radii this could lead to an underestimation of the DM halo mass.
-%--------------------------------------------
-
 \subsection{\NEW{Speculations on J1331's matter distribution}}

### 2016-06-10 LensingPaper_draft_v4.01.tex
Tried to make the M/L section more definit.

@@
 
-\NEW{A fit to all nine available $v_\text{rms}$ data points forces the DM halo to be less massive.
+\NEW{A fit to all nine available $v_\text{rms}$ data points would force the DM halo to be less massive.
 But with decreasing DM contribution in the inner regions the model approaches the mass-follows-light model in the center, that we already ruled out in Section \ref{sec:results_JAM_SB_MfL}.
@@
 Even though investigation of the photometry of J1331 did not reveal a distinct blue core in J1331, we cannot fully exclude the possibility that J1331 has such a $\Upsilon_*$ gradient (see discussion in Sections \ref{sec:results_JAM_SB_MfL} and \ref{sec:results_JAM_SB_gradient}).
-\NEW{Stellar population analysis with spectra taken at different positions within the bulge could provide further information on the true $\Upsilon_*(R')$.}\OLD{In this case the restrictive assumption of a constant $\Upsilon_*$ in our JAM modelling could have lead to wrong conclusions about the DM distribution.}
+\NEW{Spatially resolved stellar population analysis based on integral-field spectroscopy of J1331's bulge could provide further information on the true $\Upsilon_*(R')$.}\OLD{In this case the restrictive assumption of a constant $\Upsilon_*$ in our JAM modelling could have lead to wrong conclusions about the DM distribution.}
 
@@
 
+\NEW{In the following we discuss why we think---based on our results and previous analyses---that J1331's bulge has an IMF slightly less bottom-heavy than the Salpeter-like IMF.}
+
+\NEW{\emph{(i) Indications for a Salpeter-like IMF in J1331's bulge:}}
+
 Traditional choices for the IMF are the bottom-heavy IMF by \citet{Salpeter1955},
@@
 
+\NEW{\emph{(ii) Indications for and arguments against a Chabrier-like IMF in J1331's bulge:}}
+
 When \citet{SWELLSI} assumed a Chabrier IMF, their result translates to $\Upsilon_\text{I,*}^\text{chab} = 2.5 \pm 0.6$ (see Table \ref{tab:previousresults}).
-In Section \ref{sec:results_JAM_SB_gradient} we created a dynamical model from only the surface brightness distribution and an increasing mass-to-light ratio profile without additional DM halo.
+In Section \ref{sec:results_JAM_SB_gradient} we created a dynamical model from only the surface brightness distribution and an increasing mass-to-light ratio profile without additional DM halo \NEW{and without velocity anisotropy}.
 We found that such a model would be perfectly consistent with the Einstein mass, predict a total $\Upsilon_\text{I,tot}(R'\sim0) = 2.53$---being consistent with the Chabrier IMF estimate by \citet{SWELLSI}---and rise quickly to $\Upsilon_\text{I,tot}(R'\gtrsim R_\text{ein}) \gtrsim 6$.
+
+\NEW{This rise could be either due to a cuspy DM halo (see Section \Wilma{4.4???}) or a very strong gradient in $\Upsilon_\text{I,*}$ (see Section \Wilma{5.1???}).
+However, we rule out that a DM cusp is the sole reason because a cuspy and therefore overall massive DM halo does not match the kinematics in J1331's outer regions.
+We also rule out that a very strong $\Upsilon_\text{I,*}$ gradient is the only reason, because---as mentioned in Section \Wilma{???}---photometry did not reveal the clear existence of a blue population in the very center of J1331's bulge.
+Also, our modelling attempts allowing for velocity anisotropy (Sections \Wilma{4.3.2} and \Wilma{4.4}) suggest that we do need some moderate $\beta_z<0$ to explain the central $v_\text{rms}$ dip.
+And lastly---as laid out in the previous paragraph---J1331's central velocity dispersion suggests a more bottom-heavy IMF.
+Overall it is therefore not very likely that the central regions of J1331 have such a low $\Upsilon_\text{I,*}^\text{chab} \sim 2.5$.}
+
+\NEW{\emph{(iii) Arguments against an IMF more bottom-heavy than the Salpeter IMF in J1331's bulge:}}
 
@@
 Our best fit $\Upsilon_\text{I,*} = 4.2 \pm 0.2$ (see Table \ref{tab:modelB4_bestfit}) indicates a \emph{less} bottom-heavy IMF than the Salpeter IMF.
-\cite{SWELLSV} found systematically lower NFW halo masses ($v_\text{circ,halo}(5'') \sim 120~\text{km s}^{-1}$ according to their Figure 2) than we did ($v_\text{circ,halo}(R'=5'') \sim 200~\text{km s}^{-1}$).
+\NEW{In the following section we will argue why we do not think that the \cite{SWELLSV} model is a good model for the central regions of J1331.
+We therefore also do not believe their findings that the central IMF is more bottom-heavy than Salpeter.} \Wilma{[TO DO: Find new place for: "\cite{SWELLSV} found systematically lower NFW halo masses ($v_\text{circ,halo}(5'') \sim 120~\text{km s}^{-1}$ according to their Figure 2) than we did ($v_\text{circ,halo}(R'=5'') \sim 200~\text{km s}^{-1}$)."]}
 %--------------------------------------------
@@
 
+\NEW{In conclusion we suspect that a moderate DM contribution in the center, with some tangential anisotropy and a $\Upsilon_\text{I,*}$ which is slightly lower than a Salpeter-like IMF is the most likely model for J1331's central bulge.}
+
 \subsection{\NEW{Speculations on J1331's matter distribution}}
@@
 As the spiral arms cross the major axis around this radius, we suspect they cause this disturbance of the axisymmetric kinematics.
-The DM halo should also start to dominate the kinematics at larger radii, whose total mass we expect more of the order of what \citep{Dutton paper} \Wilma{???} found---unless J1331 has a strong kinematic warp in its disk, which cannot be detected in long-slit kinematics only.}
+The DM halo should also start to dominate the kinematics at larger radii, whose total mass we expect more of the order of what \Wilma{[TO DO: Dutton paper]} found---unless J1331 has a strong kinematic warp in its disk, which cannot be detected in long-slit kinematics only.}
 

### 2016-06-13 LensingPaper_draft_v4.01.tex
Corrected some referencing.

@@
 (their equation 10), with a Gaussian scatter of $\sigma_{\log c_{200}} = 0.105$ (their Table A2).
-\NEW{In Section \Wilma{[TO DO ???]} we will use this relation as prior information to guide the modelling towards realistic NFW halo shapes.}
+\NEW{In Section \ref{sec:results_JAM_NFW} we will use this relation as prior information to guide the modelling towards realistic NFW halo shapes.}
 %--------------------------------------------
@@
 %--------------------------------------------
-\subsubsection{Best fit JAM modelt} \label{sec:results_JAM_NFW_results}
+\subsubsection{Best fit JAM model} \label{sec:results_JAM_NFW_results}
 %--------------------------------------------
@@
 Allowing for free $\Upsilon_{*}(R')$, $\beta_z(R')$ and/or non-NFW $\rho_\text{halo}(r)$ profiles would over-fit the data again.
-Without further priors on the stellar $\Upsilon_{*}(R')$ and/or more data points, we can make only the following statement: A model with constant $\Upsilon_*$, moderately tangential \Wilma{[TO DO: Check]} $\beta_z$ and a spherical and massive DM component with high concentration can explain the central kinematics of J1331 very well, we have however ruled out that in this case the DM halo will follow a NFW halo at both small and large radii.}
+Without further priors on the stellar $\Upsilon_{*}(R')$ and/or more data points, we can make only the following statement: A model with constant $\Upsilon_*$, moderately tangential $\beta_z$ and a spherical and massive DM component with high concentration can explain the central kinematics of J1331 very well, we have however ruled out that in this case the DM halo will follow a NFW halo profile at both small and large radii.}
 %--------------------------------------------
@@
 %--------------------------------------------
-\subsection{On J1331's possible merger history\OLD{ and modelling failures}}
+\subsection{On J1331's possible merger history\OLD{ and modelling failures}} \label{sec:discussion_merger}
 %--------------------------------------------
@@
 
-\NEW{In the following we discuss why we think---based on our results and previous analyses---that J1331's bulge has an IMF slightly less bottom-heavy than the Salpeter-like IMF.}
-
-\NEW{\emph{(i) Indications for a Salpeter-like IMF in J1331's bulge:}}
-
 Traditional choices for the IMF are the bottom-heavy IMF by \citet{Salpeter1955},
@@
 where $\xi(m) \diff m$ is the number of stars with mass $m$ in $[m,m+\diff m]$, and the IMFs by \citet{2002Sci...295...82K} and \citet{Chabrier2003}, which are in agreement with each other and predict less low-mass stars.
+
+\NEW{In the following we discuss why we think---based on our results and previous analyses---that J1331's bulge has an IMF slightly less bottom-heavy than the Salpeter-like IMF.}
+
+\NEW{\emph{(i) Indications for a slightly less bottom-heavy Salpeter-like IMF in J1331's bulge:}}
 
@@
 
-\NEW{This rise could be either due to a cuspy DM halo (see Section \Wilma{4.4???}) or a very strong gradient in $\Upsilon_\text{I,*}$ (see Section \Wilma{5.1???}).
+\NEW{This rise in $\Upsilon_\text{I,*}(R')$ could be either due to a cuspy DM halo (see Section \ref{sec:results_JAM_NFW}) or a very strong gradient in $\Upsilon_\text{I,*}$ (see Section \ref{sec:discussion_merger}).
 However, we rule out that a DM cusp is the sole reason because a cuspy and therefore overall massive DM halo does not match the kinematics in J1331's outer regions.
-We also rule out that a very strong $\Upsilon_\text{I,*}$ gradient is the only reason, because---as mentioned in Section \Wilma{???}---photometry did not reveal the clear existence of a blue population in the very center of J1331's bulge.
-Also, our modelling attempts allowing for velocity anisotropy (Sections \Wilma{4.3.2} and \Wilma{4.4}) suggest that we do need some moderate $\beta_z<0$ to explain the central $v_\text{rms}$ dip.
+We also rule out that a very strong $\Upsilon_\text{I,*}$ gradient is the only reason, because---as mentioned in Section \ref{sec:discussion_merger}---photometry did not reveal the clear existence of a blue population in the very center of J1331's bulge.
+Also, our modelling attempts allowing for velocity anisotropy (Sections \ref{sec:results_JAM_SB_MfL} and \ref{sec:results_JAM_NFW}) suggest that we do need some moderate $\beta_z<0$ to explain the central $v_\text{rms}$ dip.
 And lastly---as laid out in the previous paragraph---J1331's central velocity dispersion suggests a more bottom-heavy IMF.
@@
 
-\NEW{The central $v_\text{rms}$ is most likely a combination of the three different aspects that we investigated separately: We expect a bit of tangential \Wilma{???} velocity anisotropy (Sections \ref{sec:results_JAM_SB_MfL} and \ref{sec:results_JAM_NFW}), a moderate contribution of a roundish DM halo (Sections 4.2.3 \Wilma{???} and 4.4.2) and different stellar populations inside the bulge due to the merger (Section 5.3) with different $\Upsilon_{*}$ but overall bottom-heavy IMF (Section 5.1), which add to an overall rising $\Upsilon_\text{tot}(R')$ profile.}
+\NEW{The central $v_\text{rms}$ dip is most likely a combination of the three different aspects that we investigated separately: We expect a bit of tangential velocity anisotropy (Sections \ref{sec:results_JAM_SB_MfL} and \ref{sec:results_JAM_NFW}), a moderate contribution of a roundish DM halo (Sections \ref{sec:results_lensing_compare} and \ref{sec:results_JAM_NFW_results}) and different stellar populations inside the bulge due to the merger (Section \ref{sec:discussion_merger}) with different $\Upsilon_{*}$ but overall bottom-heavy IMF (Section \ref{sec:MLdiscussion}), which add to an overall rising $\Upsilon_\text{tot}(R')$ profile.}
 

### 2016-06-22 LensingPaper_draft_v4.01.tex
Continued rewriting the section on kinematic in the Discussion chapter.

@@
 Warps lead to a twist in the projected kinematic major axis with radius, which is then also misaligned with the photometric major axis (\citealt{1998gaas.book.....B}, \S 8.2.4).
-From kinematics along the photometric major axis only it cannot be determined if such a twist or misalignment is present in J1331\NEW{, but it should be immediately visible in a 2D kinematic map}.\OLD{ But if it were, our modelling assumption of axisymmetry would not be satisfied anymore.}
+\NEW{We note that kinematics measured along an axis different from the kinematic major axis would result in $v_\text{rot}$ measurements being lower than the actual maximum $v_\text{circ}$.
+At large radii this could lead to an underestimation of the DM halo mass.}
+
+From kinematics along the photometric major axis only it \OLD{cannot}\NEW{can however not} be determined if such a twist or misalignment is present in J1331\NEW{, but it should be immediately visible in a 2D kinematic map}.\OLD{ But if it were, our modelling assumption of axisymmetry would not be satisfied anymore.} \OLD{We note that kinematics measured along an axis different from the kinematic major axis would result in $v_\text{rot}$ measurements being lower than the actual maximum $v_\text{circ}$.
+At large radii this could lead to an underestimation of the DM halo mass.}
+
 \Wilma{[TO DO: Mention that warps would require other modelling techniques than the axisymmetric Jeans models.]}
-
-\Wilma{[More: "We note that kinematics measured along an axis different from the kinematic major axis would result in $v_\text{rot}$ measurements being lower than the actual maximum $v_\text{circ}$.
-At large radii this could lead to an underestimation of the DM halo mass." somewhere else.]}
 %--------------------------------------------
@@
 %--------------------------------------------
-\subsection{On J1331's central kinematics}
-%--------------------------------------------
-
-%--------------------------------------------
-In Figure \ref{fig:vcirc_comparison} we compare the circular velocity curve found by \citet{SWELLSV} with a mass-follows-light model scaled to fit our Einstein mass (by multiplying the light distribution in Table \ref{tab:MGEF814W} by $\Upsilon_\text{I,tot}^\text{ein} = 5.56$, analogous to Figure \ref{fig:lenscomparelight}).
+\subsection{On J1331's \OLD{central }kinematics}
+%--------------------------------------------
+
+%--------------------------------------------
+\NEW{Overall, the kinematics of the merger remnant J1331 are peculiar.
+In particular there are two features in the $v_\text{rms}$ curve that are hard to explain with standard modelling techniques.
+The first feature, the deep central $v_\text{rms}$ dip, was studied in detail in this work.
+The second feature, the drop and rise in $v_\text{rms}$ around \Wilma{[TO DO]}, is even harder to explain; below we will speculate about possible reasons that could cause such a signature.}
+
+\NEW{\emph{(i) The central $v_\text{rms}$ dip within $R'\lesssim1''$:}}
+
+\NEW{First, we will compare our modelling results with the modelling results by \citet{SWELLSV} within \Wilma{[TO DO]}.}
+
+\NEW{\citet{SWELLSV} fitted a stellar mass model and NFW halo to (i) the Einstein mass and (ii) gas kinematics at larger radii $\gtrsim8''$.
+} \OLD{In }Figure \ref{fig:vcirc_comparison} \OLD{we compare}\NEW{compares} the circular velocity curve found by \citet{SWELLSV} with a mass-follows-light model scaled to fit our Einstein mass (by multiplying the light distribution in Table \ref{tab:MGEF814W} by $\Upsilon_\text{I,tot}^\text{ein} = 5.56$, analogous to Figure \ref{fig:lenscomparelight}).
 Within $R < 5''$ they agree with each other.
@@
 
-Overall, we were not able to find a consistent explanation for J1331's central $v_\text{rms}$ dip.
+\NEW{Because we used more data constraints in the center than \citet{SWELLSV}, we think that our model for J1331's bulge is more reliable.
+In conclusion we suspect that the most likely model for J1331's central bulge is a moderate DM contribution in the center (Section \ref{sec:results_JAM_NFW_results}) with some tangential anisotropy (Sections \ref{sec:results_JAM_SB_MfL} and \ref{sec:results_JAM_NFW}) and an overall $\Upsilon_\text{*,I}$ in the bulge which is slightly lower than that of a Salpeter-like IMF (Section \ref{sec:MLdiscussion}).
+Different stellar populations inside the bulge due to the merger (Section \ref{sec:discussion_merger}) with different $\Upsilon_{*}$ could add to an overall rising $\Upsilon_\text{tot}(R')$ profile (Sections \ref{sec:results_lensing_compare} and \ref{sec:results_JAM_SB_gradient}).}
+
+\OLD{Overall, we were not able to find a consistent explanation for J1331's central $v_\text{rms}$ dip.
 It cannot be due to tangential velocity anisotropy in the center alone (see Section \ref{sec:results_JAM_SB_MfL}, Figure \ref{fig:JAM_modelA2}).
-It also cannot be explained by a strong contribution of DM inside the bulge together with a moderate tagential velocity anisotropy, because the corresponding \NEW{NFW} DM halo\OLD{s} would still be too massive to fit the data in the outer regions (see Section \ref{sec:results_JAM_NFW}, Figure \ref{fig:modelB4_vrms}).
-
-Another feature in the stellar kinematics that none of our JAM models was able to reproduce in the slightest and which we therefore excluded in the modelling, was the dip in $v_\text{rms}$ around $\sim 6''$, which occurs around the transition from bulge to disk (see Figures \ref{fig:F814W} and \ref{fig:kinematics}).
+It also cannot be explained by a strong contribution of DM inside the bulge together with a moderate tagential velocity anisotropy, because the corresponding \NEW{NFW} DM halo\OLD{s} would still be too massive to fit the data in the outer regions (see Section \ref{sec:results_JAM_NFW}, Figure \ref{fig:modelB4_vrms}).}
+
+\OLD{Another feature in the stellar kinematics that none of our JAM models was able to reproduce in the slightest and which we therefore excluded in the modelling, was the dip in $v_\text{rms}$ around $\sim 6''$, which occurs around the transition from bulge to disk (see Figures \ref{fig:F814W} and \ref{fig:kinematics}).}
+
+\Wilma{[TO DO: Mention somewhere else: "Overall, we were not able to find a consistent explanation for J1331's central $v_\text{rms}$ dip.
+It cannot be due to tangential velocity anisotropy in the center alone (see Section \ref{sec:results_JAM_SB_MfL}, Figure \ref{fig:JAM_modelA2}).
+It also cannot be explained by a strong contribution of DM inside the bulge together with a moderate tagential velocity anisotropy, because the corresponding \NEW{NFW} DM halo\OLD{s} would still be too massive to fit the data in the outer regions (see Section \ref{sec:results_JAM_NFW}, Figure \ref{fig:modelB4_vrms})."]}
+
 %--------------------------------------------
@@
 
-\NEW{In conclusion we suspect that a moderate DM contribution in the center, with some tangential anisotropy and a $\Upsilon_\text{I,*}$ which is slightly lower than a Salpeter-like IMF is the most likely model for J1331's central bulge.}
-
-\subsection{\NEW{Speculations on J1331's matter distribution}}
-
-\NEW{The kinematics of the merger remnant J1331 are peculiar and hard to explain with standard modelling techniques.
-We think that in the end the truth will be somewhere in between the results of the different modelling attempts.}
-
-\NEW{The central $v_\text{rms}$ dip is most likely a combination of the three different aspects that we investigated separately: We expect a bit of tangential velocity anisotropy (Sections \ref{sec:results_JAM_SB_MfL} and \ref{sec:results_JAM_NFW}), a moderate contribution of a roundish DM halo (Sections \ref{sec:results_lensing_compare} and \ref{sec:results_JAM_NFW_results}) and different stellar populations inside the bulge due to the merger (Section \ref{sec:discussion_merger}) with different $\Upsilon_{*}$ but overall bottom-heavy IMF (Section \ref{sec:MLdiscussion}), which add to an overall rising $\Upsilon_\text{tot}(R')$ profile.}
-
-\NEW{The drop in $v_\text{rms}$ around $R'\sim4''$ is most likely due to a sharp drop in $\Upsilon_{*}(R')$ at the transition from red bulge to blue disk (compare bulge size in Figures \ref{fig:F450W} and \ref{fig:F814W}).
+\NEW{\emph{(ii) The drop and rise of the $v_\text{rms}$ curve around $R'\sim 6''$:}}
+
+\NEW{The drop in $v_\text{rms}$ around $R'\sim4''$ (Figure \ref{fig:kinematics}) is most likely due to a sharp drop in $\Upsilon_{*}(R')$ at the transition from red bulge to blue disk (compare bulge size in Figures \ref{fig:F450W} and \ref{fig:F814W}).
 Unfortunately the spiral arms make the disk of the galaxy difficult to model.
-At these larger radii a possible mis-alignment of long-slit and Galaxy major axis would also cause a stronger underestimation of the true $v_\text{rot}$ and would add to the drop in $v_\text{rms}$.}
+At these larger radii a possible misalignment of long-slit and galaxy's kinematic major axis would also cause a stronger underestimation of the true $v_\text{rot}$ and would add to the drop in $v_\text{rms}$.}
 
@@
 As the spiral arms cross the major axis around this radius, we suspect they cause this disturbance of the axisymmetric kinematics.
-The DM halo should also start to dominate the kinematics at larger radii, whose total mass we expect more of the order of what \Wilma{[TO DO: Dutton paper]} found---unless J1331 has a strong kinematic warp in its disk, which cannot be detected in long-slit kinematics only.}
-
-\NEW{All of these speculations should be easily testable with 2D kinematics.} \Wilma{[TO DO: Proper referencing.]}
+The DM halo should also start to dominate the kinematics at larger radii, whose total mass we expect more of the order of what \citet{SWELLSV} found and which we suspect has a profile that deviates strongly from a NFW halo at both small and large radii.
+A more massive halo of NFW shape---as the one we found in this work---could however exist in J1331 if the galaxy had a strong kinematic warp in its disk due to the merger.}
+
+\NEW{All of these speculations should be easily testable with 2D kinematics.}
 
@@
 %--------------------------------------------
-
+\Wilma{[TO DO: Go through it and make it shorter.]}
 %--------------------------------------------

### 2016-06-23 LensingPaper_draft_v4.01.tex
Edited part of the Future Work and Central kinematics section in the Discussion.

@@
 
-\Wilma{[TO DO: Mention somewhere else: "Overall, we were not able to find a consistent explanation for J1331's central $v_\text{rms}$ dip.
-It cannot be due to tangential velocity anisotropy in the center alone (see Section \ref{sec:results_JAM_SB_MfL}, Figure \ref{fig:JAM_modelA2}).
-It also cannot be explained by a strong contribution of DM inside the bulge together with a moderate tagential velocity anisotropy, because the corresponding \NEW{NFW} DM halo\OLD{s} would still be too massive to fit the data in the outer regions (see Section \ref{sec:results_JAM_NFW}, Figure \ref{fig:modelB4_vrms})."]}
-
-%--------------------------------------------
-
-\Wilma{[TO DO: The referee says: "In Section 5.2, the authors could make suggestions for what might be causing the two
-$v_{rms}$ dips. Currently, they just state what cannot be the cause, but do not make any
-more convincing suggestions – e.g. could it be associated with the possible recent
-merger that is explored in Section 5.3? It would be more satisfying if some
-suggestions like this could be put forward."]}
+%--------------------------------------------
 
@@
 %--------------------------------------------
-\Wilma{[TO DO: Go through it and make it shorter.]}
-%--------------------------------------------
-Standard JAM modelling approaches seem not to work for J1331.
-The existing data---photometry and major axis kinematics---is however not sufficient to decide which of our model assumptions lead to the failure to find an overall consistent mass model.
-
-2-dimensional stellar kinematics would greatly help to resolve this problem.
-The main future work would be therefore getting high-resolution integral-field spectroscopy for J1331.
+
+%--------------------------------------------
+\OLD{Standard JAM modelling approaches seem not to work for J1331.
+The existing data---photometry and major axis kinematics---is however not sufficient to decide which of our model assumptions lead to the failure to find an overall consistent mass model.}
+\NEW{J1331's merging history and peculiar kinematics make it a valuable and exiting target to study merger remnants and a challenge for dynamical modelling techniques.
+We found however that the existing data alone---photometry and major axis kinematics---is not sufficient to resolve all the ambiguities we encountered in our modelling.}
+
+\OLD{2-dimensional stellar kinematics would greatly help to resolve this problem.
+}The main future work would be therefore getting high-resolution integral-field spectroscopy for J1331.
 High spatial resolution would be required to clearly identify J1331's presumably complex kinematic structure.
@@
 Is it possible that there even exists a kinematic twist due to the merger in J1331's past?
+\NEW{In the latter two cases we would need to apply non-axisymmetric Jeans models to J1331 as the assumption of axisymmetry of this work would not be valid anymore.}
 

### 2016-06-27 LensingPaper_draft_v4.01.tex
Rewrote the summary section.

@@
 
-\Wilma{[TO DO: The referee says: "The discussion section is too non-committal and speculative in parts. For instance,
-in section 5.1, the M/Ls inferred from a number of the different models are compared
-with M/Ls from the literature, but the authors do not make any value judgement
-between the different models to come to any firmer conclusions about what they
-believe the most convincing description of the IMF to be. At the moment, this
-section seems to just be trying to show that their various models can be made to
-agree with previous models from the literature, but it would be much more
-interesting if some attempt could be made to resolve all the different models (both
-in this paper and in previous works) or at least present them in a more coherent
-framework, to try to come up with a better picture of the nature of J1331's IMF."]}
-
 %--------------------------------------------
@@
 %--------------------------------------------
-\Wilma{[TO DO: Go through it and make it shorter.]}
-%--------------------------------------------
-The goal of this work was to constrain the matter distribution of the massive spiral galaxy J1331.
+
+%--------------------------------------------
+\NEW{We constrained the matter distribution of the massive spiral galaxy J1331, which has a large counter-rotating core, probably due to a merger in its past, and acts as a strong gravitational lens for a background source.
+We used two independent methods to model J1331: gravitational lensing and dynamical Jeans modelling.}\OLD{The goal of this work was to constrain the matter distribution of the massive spiral galaxy J1331.
 J1331 is of special interest because it firstly has a large counter-rotating core and might therefore be a merger remnant and it secondly acts as strong gravitational lens for a background source.
 The latter allowed us to constrain the galaxy's mass from gravitational lensing.
-As second independent approach we used dynamical Jeans modelling to recover and disentangle the stellar and DM distribution.
-We focussed on the bulge region of J1331 to complement previous studies of J1331 by \citet{SWELLSIII} and \citet{SWELLSV}.
-The independent mass constraints which we derived from lensing and dynamics agree very well with each other within $R_\text{eff}$.
+As second independent approach we used dynamical Jeans modelling to recover and disentangle the stellar and DM distribution.} We focussed on the bulge region of J1331 to complement previous studies of J1331 by \citet{SWELLSIII} and \citet{SWELLSV}.
+The \OLD{independent} mass constraints \OLD{which we derived} from lensing and dynamics agree very well with each other within $R_\text{eff}$.
 
 In our lensing approach we fitted a scale-free galaxy model to the lensing image position.
-This constrained the Einstein radius to within 2\% ($R_\text{ein}=(0.91\pm0.02)'' \hat{=}(1.83\pm0.04)~\text{kpc}$), and the Einstein mass to within 4\% ($M_\text{ein} = (7.8\pm0.3) \cdot 10^{10} M_\odot$), consistent with results by \citet{SWELLSIII}.
-The recovered mass distribution agrees also very well with the shape of the observed lensing images.
-
-To get a handle on J1331's light distribution we used a MGE fit to J1331's surface brightness in the F814W filter in HST imaging by \citet{SWELLSI}.
-Based on this we found J1331's effective radius to be $R_\text{eff} \simeq 2.6'' \hat{=} 5.2~\text{kpc}$ and its total I-band luminosity to be $L_\text{I,tot} \simeq 5.6 \cdot 10^{10} L_\odot$.
-
-We used axisymmetric JAM modelling to calculate the second velocity moment of a tracer and mass distribution given in terms of MGEs.
-The JAM model of the lens mass model gave an independent prediction which was consistent with observed stellar kinematics from major axis long slit spectroscopy by \citet{SWELLSV} within $R_\text{eff}$.
+This constrained the Einstein radius to within 2\% ($R_\text{ein}=(0.91\pm0.02)'' \hat{=}(1.83\pm0.04)~\text{kpc}$), and the Einstein mass to within 4\% ($M_\text{ein} = (7.8\pm0.3) \cdot 10^{10} M_\odot$), consistent with results by \citet{SWELLSIII}.\OLD{The recovered mass distribution agrees also very well with the shape of the observed lensing images.}
+
+\OLD{To get a handle on J1331's light distribution we used a MGE fit to J1331's surface brightness in the F814W filter in HST imaging by \citet{SWELLSI}.
+Based on this we found J1331's effective radius to be $R_\text{eff} \simeq 2.6'' \hat{=} 5.2~\text{kpc}$ and its total I-band luminosity to be $L_\text{I,tot} \simeq 5.6 \cdot 10^{10} L_\odot$.}\NEW{A MGE fit to J1331's surface brightness in the F814W filter in HST imaging by \citet{SWELLSI} helped us determining the effective radius, $R_\text{eff} \simeq 2.6'' \hat{=} 5.2~\text{kpc}$, and total I-band luminosity of the galaxy, $L_\text{I,tot} \simeq 5.6 \cdot 10^{10} L_\odot$.}
+
+\NEW{Axisymmetric JAM modelling allowed a comparison between model predictions for the second velocity moment given a tracer and mass distribution and the observed stellar kinematics from major axis long slit spectroscopy by \citet{SWELLSV}.} \OLD{We used axisymmetric JAM modelling to calculate the second velocity moment of a tracer and mass distribution given in terms of MGEs.} The \NEW{independent} JAM model of the lens mass model \OLD{gave an independent prediction which }was consistent with observed\OLD{ stellar} kinematics\OLD{ from major axis long slit spectroscopy by \citet{SWELLSV}} within $R_\text{eff}$.
 We also fitted mass models with and without NFW halo to the stellar kinematics within $R'=3.5~\text{kpc}$.
-From this we deduced that a mass-follows-light model with constant total mass-to-light ratio and velocity anisotropy is not a good model for J1331---not even in the inner regions.
-To describe the observed stellar kinematics we either require a strong contribution of a DM halo already in the bulge, or a strongly varying stellar mass-to-light ratio.
-We also showed that it is possible to construct a model which includes the counter-rotating core and fits the rotation curve at large radii.
-
-While both our independent mass models are consistent with each other within $\sim R_\text{eff}$, they do not agree with previous findings by \citet{SWELLSV}, nor the data at large radii.
-We attribute this to the fact that \citet{SWELLSV} derived mass constraints from kinematics in the outer regions only, while we focussed on the inner regions in detail.
-We speculate that a merger might have modified the kinematic structure and/or mass distribution of J1331 such that crucial model assumptions are not valid anymore.
+From this we deduced that a mass-follows-light model \NEW{(even} with \OLD{constant total mass-to-light ratio and }velocity anisotropy\NEW{)} is not a good model for J1331\OLD{---not even in the}\NEW{'s} inner regions.
+\NEW{This ruled out the previous findings of \citet{SWELLSV} for J1331's bulge.
+We discussed that, to}\OLD{ To} describe the observed stellar kinematics\NEW{,} we \OLD{either}\NEW{most likely} require a \OLD{strong}\NEW{moderate} contribution of a DM halo already in the bulge, \NEW{moderate tangential velocity anisotropy, $\beta_z \simeq -0.4\pm0.1$, }\OLD{or} \NEW{and possibly even} a \OLD{strongly} varying stellar mass-to-light ratio \NEW{within the bulge, which could be the result of the previous merger event}.
+\NEW{We argue that we expect the total stellar mass-to-light ratio within the bulge to be slightly less bottom-heavy than a Salpeter IMF, $\Upsilon_\text{I,*}\simeq 4.2\pm0.2$.} We also showed that it is possible to construct a model which includes the counter-rotating core and fits the rotation curve at large radii.
+
+While both our independent mass models are consistent with each other within $\sim R_\text{eff}$, they do not \OLD{agree with previous findings by \citet{SWELLSV}, nor the}\NEW{describe the} data at large radii \NEW{very well}.
+\OLD{We attribute this to the fact that \citet{SWELLSV} derived mass constraints from kinematics in the outer regions only, while we focussed on the inner regions in detail.} We speculate \OLD{that}\NEW{how} a merger \OLD{might}\NEW{could} have modified the kinematic structure and/or mass distribution of J1331\OLD{ such that crucial model assumptions are not valid anymore}.
 To resolve the ambiguities in J1331's mass distribution 2-dimensional kinematic maps of J1331 from integral-field unit spectroscopy would be needed.

### 2016-06-28 Answer_to_referee_report_LensingPaper.tex
Some corrections in the paper, a few comments in the referee report.

@@
 J1331. 
+\Comment{Thanks. It is a very exiting galaxy that's definitely worth exploring.}
 
@@
 probably be removed altogether, and the second paragraph promoted to the beginning. 
-\Comment{I understand the referee's point.
-I personally like the first paragraph however very much and I think the most interesting thing in this paper is to see that dynamical modelling and lensing can give independent and comparable results even in such a peculiar system.
-Our contribution to solving the "core-cusp" problem is actually rather weak, so I would not want to start my introduction with it.
-What do you think?
-On the other hand mentioning more astrophysics is always a good thing...
-Any idea how we could put that more in the foreground?}
+\Comment{That is a good point.
+We changed the opening paragraph to a general sentence why determining the matter distribution of galaxies is important.
+We mention the different methods now in the third paragraph.}
 
@@
 feature of the galaxy in question and is also a very active topic of research.
+\Comment{Good point.
+1.) We added a sentence mentioning the important role of mergers in modifying the matter distribution and added some recent references.
+2.) We added a short paragraph later in the introduction that points out that J1331 is a special and very interesting galaxy for researching mergers.
+We also explain better that this merger is one of the reasons why we especially focus on the inner regions of J1331 in our study.}
 
@@
 also rather throws the book at the NFW profile relations – it probably isn't
-necessary to include equation 22. \Aaron{What does that mean, "throw the book at something"?}
+necessary to include equation 22.
+\Comment{We made an effort to remove unnecessary equations in Section 3.2.1, tighten the explanation of the derivation of the Jeans equations in Section 3.3.1 and 3.3.3 and removed big and clumsy mathematical expressions by referring to the explicit equations in the literature instead.
+In 3.3.2 we refer stronger to the changes we made to Capellari's JAM code and kept the corresponding equations.
+In Section 3.3.4 we moved equations that are definitions and therefore needed inline to make it shorter; we kept the Maccio concentration vs.
+halo mass relation and explicitely mention that we will use this later as a prior in our modelling.
+In general we include a lot of equations and a big theory introduction because it is a paper that is potentially interesting for two communities, the lensing and the dynamics community.
+We wanted to make the paper understandable for both.}
 

### 2016-06-28 LensingPaper_draft_v4.01.tex
Some corrections in the paper, a few comments in the referee report.

@@
 Then a surface brightness model can be expressed as
-\begin{eqnarray}
-I(R',\theta') &=& \sum_{i=1}^{N} I_{0,i} \exp\left[ - \frac{1}{2\sigma_i^2} \left(x^{'2} + \frac{y^{'2}}{q_i^{'2}}\right)\right]\label{eq:MGEgeneral}\\
-\text{with } I_{0,i} &=& \frac{L_i}{2\pi \sigma_i^2 q'_i}\label{eq:centralItotalL}\\
-\text{and } x'_i &=& R' \cos(\theta' - \phi)\nonumber\\
-y'_i &=& R' \sin(\theta' - \phi),\nonumber
-\end{eqnarray}
+\begin{align}
+I(R',\theta') &= \sum_{i=1}^{N} I_{0,i} \exp\left[ - \frac{1}{2\sigma_i^2} \left(x^{'2} + \frac{y^{'2}}{q_i^{'2}}\right)\right]\label{eq:MGEgeneral}\\
+\text{with } I_{0,i} &= \frac{L_i}{2\pi \sigma_i^2 q'_i}\label{eq:centralItotalL}\\
+\begin{split}
+\text{and } x'_i &= R' \cos(\theta' - \phi)\\
+y'_i &= R' \sin(\theta' - \phi),
+\end{split}
+\end{align}
 where $I_{0,i}$ is the central surface brightness of each Gaussian, $L_i$ its total luminosity, $\sigma_i$ its dispersion along the major axis and $q'_i$ the axis ratio between the elliptical Gaussian's major and minor axis.
@@
 The flattening $q_i$ of each axisymmetric 3D Gaussian and its central density $\nu_{0,i}$ follow from the observed 2D axis ratio $q'_i$ and surface density $I_{0,i}$ as
-\begin{eqnarray*}
+\begin{eqnarray}
 q_i^2 &=& \frac{q_i'^2 - \cos^2 i}{\sin^2 i}\\
 \nu_{0,i} &=& \frac{q_i' I_{0,i}}{q_i \sqrt{2 \pi \sigma_i^2}}.
-\end{eqnarray*}
+\end{eqnarray}
 %--------------------------------------------
@@
 The best fit lens model is then the one that minimizes
-\begin{eqnarray}
-\chi^2_\text{lens} &=& \sum_{i} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right) \left( \vect{\theta}_{pi} - \vect{\theta}_{oi} \right)\right|^2\nonumber\\
-&\simeq& \sum_{i} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right)  \left.\mathscr{M}\right|_{\vect{\theta}=\vect{\theta}_{oi}} \left( \begin{matrix} x_s' - \tilde{x}'_{si} \\ y_s' - \tilde{y}'_{si} \end{matrix} \right) \right|^2,\label{eq:chi2lens}
-\end{eqnarray}
+\begin{align}
+\begin{split}
+\chi^2_\text{lens} &= \sum_{i} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right) \left( \vect{\theta}_{pi} - \vect{\theta}_{oi} \right)\right|^2\label{eq:chi2lens}\\
+&\simeq \sum_{i} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right)  \left.\mathscr{M}\right|_{\vect{\theta}=\vect{\theta}_{oi}} \left( \begin{matrix} x_s' - \tilde{x}'_{si} \\ y_s' - \tilde{y}'_{si} \end{matrix} \right) \right|^2,
+\end{split}
+\end{align}
 where $(\Delta_x,\Delta_y)$ are the measurement errors of the image positions $\vect{\theta}_{oi}$.
@@
 The root-mean-square (rms) line-of-sight velocity $v_\text{rms}$ allows a data-model comparison by relating theses velocities according to
-\begin{equation*}
+\begin{equation}
  v_\text{rms}^2 = v_\text{rot}^2 + \sigma^2  \stackrel{!}{=} \langle v_\text{los}^2 \rangle_\text{obs}.
-\end{equation*}
+\end{equation}
 \OLD{The model in Equation \eqref{eq:explicitLOSvelCap}}\NEW{The model derived from the Jeans equations as outlined in Section \ref{sec:model_JAM_JAM}} predicts the intrinsic $\langle v_\text{los}^2 \rangle_\text{intr}\equiv\langle v_\text{los}^2\rangle$ at a given position on the sky, which needs then to be modified to $\langle v_\text{los}^2 \rangle_\text{obs}$ according to the mode of observation to be comparable to the measurements.
 The measured $v_\text{rms}$ is a light-weighted mean for a pixel along the long-slit of the spectrograph, with width $L_y = 1''$ \citep{SWELLSV} and a certain given extent along the galaxy's major axis, $L_x$, i.e., for a rectangular aperture
-\begin{equation*}
+\begin{equation}
 \text{AP}(x',y') \equiv \left\{ \begin{array}{ll} 1 & \text{for } -\frac{L_x}{2} \leq x' < + \frac{L_x}{2}\\
 & \text{and } - \frac{L_y}{2} \leq y' \leq + \frac{L_y}{2}  \\ 0 & \text{otherwise.} \end{array} \right.
-\end{equation*}
+\end{equation}
 The light arriving at the spectrograph itself was subject to seeing, i.e., a Gaussian with Full Width Half Maximum (FWHM) of $1.1''$ \citep{SWELLSV},
-\begin{equation*}
+\begin{equation}
 \text{PSF}(x',y')\equiv\mathscr{N}(0,\sigma_\text{seeing}=\text{FWHM}/2\sqrt{2\ln2}).
-\end{equation*}
+\end{equation}
 The model predictions for $\langle v_\text{los}^2 \rangle_\text{intr}$ have therefore to be convolved with the convolution kernel
-\begin{eqnarray*}
-K(x',y') &\equiv& (\text{PSF} \ast \text{AP})(x',y') \\
+\begin{eqnarray}
+K(x',y') &\equiv& (\text{PSF} \ast \text{AP})(x',y') \nonumber\\
 &=& \frac{1}{4} \prod_{u \in \{x',y'\}} \left[ \text{erf}\left( \frac{L_u/2 - u}{\sqrt{2}\sigma_\text{seeing}}\right) + \text{erf} \left( \frac{L_u/2 + u}{\sqrt{2} \sigma_\text{seeing}} \right) \right],
-\end{eqnarray*}
+\end{eqnarray}
 and weighted by the surface brightness $I(x',y')$, i.e.,
-\begin{eqnarray*}
+\begin{eqnarray}
 I_\text{obs} &=& I \ast K\\
 \langle v_\text{los}^2 \rangle_\text{obs} &=& \frac{(I \langle v_\text{los}^2\rangle_\text{intr}) \ast K}{I_\text{obs}}.
-\end{eqnarray*}
+\end{eqnarray}
 \NEW{We modified the JAM code by \citet{Cap08} to use this convolution kernel with non-square pixels.
@@
 and two free parameters, the scale length $r_s$ and a parameter describing the total mass of the halo.
-We will use $v_\text{200}\NEW{\equiv \sqrt{GM_{200}/r_{200}}}$, which is the circular velocity at the radius $r_\text{200}$ within which the mean density of the halo is 200 times the cosmological critical density $\rho_\text{crit} \equiv (2H^2)/(8\pi G)$, \OLD{i.e.,}\NEW{ and where $M_{200} \equiv M(<r_{200}) \stackrel{!}{=} \frac 43 \pi r_{200}^3 \cdot \rho_\text{crit}(z=0)$.}
+We will use $v_\text{200}\NEW{\equiv \sqrt{GM_{200}/r_{200}}}$, which is the circular velocity at the radius $r_\text{200}$ within which the mean density of the halo is 200 times the cosmological critical density $\rho_\text{crit} \equiv (2H^2)/(8\pi G)$, \OLD{i.e.,}\NEW{ and where $M_{200} \equiv M(<r_{200}) \stackrel{!}{=} \frac 43 \pi r_{200}^3 \cdot 200\rho_\text{crit}(z=0)$.}
 \OLD{\begin{eqnarray*}
@@
 Each Gaussian in the MGE has a total F814W luminosity $L_i$ (in counts) and a central surface brightness (in counts per pixel) of
-\begin{equation*}
+\begin{equation}
 C_{0,i}\text{[counts/pixel]} = \frac{L_i[\text{counts}]}{2\pi \sigma_i[\text{pixel}]^2 q_i}.
-\end{equation*}
+\end{equation}
 This is then transformed into an I-band surface brightness (in $\text{mag}\times(1'')^{-2}$) via
@@
 The last step is to transform the surface brightness $\mu_{I,0,i}$ (in mag) to the I-band surface density $I_{0,i}$ (in $L_\odot$/pc$^2$) of the Gaussian, i.e.,
-\begin{eqnarray*}
+\begin{eqnarray}
 I_{0,i}[L_\odot \text{pc}^{-2}] = \left( 64800/\pi\right)^2 \left(1+z_d \right)^4 10^{0.4\left(M_{\odot,I}-\mu_{I,0,i} \right)},
-\end{eqnarray*}
+\end{eqnarray}
 where the term with $z_d$ accounts for redshift dimming and $M_{\odot,I}=4.08~\text{mag}$ is the Sun's absolute I-band magnitude \citep{1998gaas.book.....B}.
@@
 If a typical thickness of an oblate disk is around $q_0 \sim 0.2$ \citep{1958MeLu2.136....1H}, the inclination follows from
-\begin{equation*}
+\begin{equation}
 \cos^2 i = \frac{q'^2 - q_0^2}{1 - q_0^2}
-\end{equation*}
+\end{equation}
 and a correction of $+3^\circ$ \citep{1988ngc..book.....T}.
@@
 For the velocity anisotropy parameter $\beta_z$ we will again employ a uniform prior 
-\begin{equation*}
+\begin{equation}
 p(\beta_z) = \mathscr{U}(-0.5,+0.5)
-\end{equation*}
+\end{equation}
 to exclude very unrealistic anisotropies. The full prior used is then
-\begin{eqnarray*}
-&&p(\Upsilon_\text{I,*},r_s,v_{200},\beta_z) \\
-&&= \frac{1}{\ln\left( 10 r_s\right)} p(\log c_{200} \mid v_{200}) \cdot p(v_{200}) \cdot p(\beta_z), 
-\end{eqnarray*}
+\begin{align}
+\begin{split}
+&p(\Upsilon_\text{I,*},r_s,v_{200},\beta_z) \\
+&= \frac{1}{\ln\left( 10 r_s\right)} p(\log c_{200} \mid v_{200}) \cdot p(v_{200}) \cdot p(\beta_z), 
+\end{split}
+\end{align}
 where the factor $1/\ln\left( 10 r_s\right)$ is the Jacobian of the transformation from the halo parameters $(v_{200},\log c_{200})$ to the fit parameters $(v_{200},r_s)$.

### 2016-06-29 Answer_to_referee_report_LensingPaper.tex
Added one comment to referee report.

@@
 This was unsuccessful to a degree that showing the result in the paper would not be reasonable.
-1.
-JAM modelling (without additional mass components) allows us to assign a separate (constant) M/L to each Gaussian of the light MGE model.
-With only 5 Gaussians in the light MGE model and all of them with Gaussian dispersions $< 4$ arcsec (see Table 3) our ability to create arbitrary M/L profiles---especially at larger radii---is very restricted.
-At large radii, $\sim$ 7 arcsec, we would have effectively a pure mass-follows-light model with constant M/L and very flattened matter structure, which is not expected to be the case considering the results from the lensing model.
-2.
-When leaving all 5 Gaussian M/Ls free, we got a wiggly and difficult to interpret M/L profile in the inner regions of the galaxy, with a slight decrease from 0 to $\sim$ 0.7 arcsec, a sharp rise around 1 arcsec, and a sharp drop around 3 arcsec.
-While this could be of course physical, there is no clear indication in the photometry that would support such an extreme profile.
-We therefore rather think that this wiggly profile was the result of over-fitting.
-3.
-With only 6 data points and 5 fit M/L parameters within 5 arcsec, the fit result is not very well constrained or reliable.
-4.
-It would have been of course possible to impose more constraints on the M/L profile and forcing it to rise in the center and to allow to profile to drop in the disk again.
-But with the spiral arms' dynamics starting to dominate at radii R $\gtrsim 5$ arcsec and our MGE light model not being a good model anymore in the outer regions, we thought it would not be reasonable to force to fit too much, when we know that the model has only limited abilities and the information content of the data is limited as well.
-As we lay out in the discussion, constraints on a varying stellar M/L ratio should be motivated by stellar population analysis in the future---or use more kinematics measurements than just the ones along the major axis.
-}
+The way how we can generate variable M/L profiles with our MGE mass model is restricted.
+We have 6 data points and 5 fit M/L parameter within 5 arcsec.
+This lead to an over-fitting in the inner regions where most of the Gaussians are, while not having enough flexibility at larger radii.
+(We added a sentence mentioning that in the paper.) The resulting profile was very wiggly, difficult to interpret and most likely unphysical.
+As we lay out in the discussion, constraints on a varying stellar M/L ratio should be motivated by stellar population analysis in the future.}
 

### 2016-06-30 Answer_to_referee_report_LensingPaper.tex
Finished referee report (almost) and removed all TO DOs from the Paper.

@@
 once? (Perhaps it is impossible to find a good NFW model across the whole radius
-range, but if this is the case, then it should be stated.) \Comment{???
-We set out to investigate the rather peculiar kinematics in the center of J133, which is strongly affected by the merger.
-We investigate different possibilities (velocity anisotropy, strong dark matter contribution in the center...), but none gives a satisfying result that is also consistent with the outer regions.???
-}
+range, but if this is the case, then it should be stated.) \Comment{Yes, you are completely right.
+Our initial tests tried of course to fit the whole range of data, but failed.
+The problem is that we were never able to fit both the central $v_\text{rms}$ dip and the dip around $R'\sim 6''$ with any of the models we tried.
+If you think this is frustrating, we definitely feel the same way.
+Our best explanation was, that the spiral arms do weird things to the kinematics around $R'\sim 5-7''$ that cannot be captured by the axisymmtric Jeans models.
+In this region our MGE models also were not a good fit to the galaxy anymore.
+Considering also that there are other studies focussing on the outer regions and the counter-rotating core is the most interesting feature, we decided to focus our efforts on the inner regions and to try to explain the central kinematics only.
+We added however a small new section 4.4.4 that discusses that and why modelling attempts to the whole data range fail and what possible next modelling steps should be.}
 
@@
 in this paper and in previous works) or at least present them in a more coherent
-framework, to try to come up with a better picture of the nature of J1331's IMF. \Glenn{No idea how to tackle this!!!!!!!!}
+framework, to try to come up with a better picture of the nature of J1331's IMF.
+\Comment{This is a valid point of criticism.
+We thought again about the different models and indications for different IMFs that we collected and came to the conclusion that an IMF slightly less bottom-beavy than the Salpeter IMF is the most likely model for J1331's bulge.
+We tried to give Section 5.1 (now 5.2) more structure and tweaked the discussion to present arguments for $\Upsilon_{I,*} \sim 4.2$ and and to argue against the alternative models.\\We also moved the section that discusses J1331's merger history to the beginning to the discussion section, focussed more on the what the merger could have done to J1331's mass distribution and less on modelling failures.
+All following sections use the background information about mergers to discuss our models.\\Our scientific honesty is however, that without further data, we cannot be more commital and some of our statements have to stay in the "speculation regime".}
 
@@
 suggestions like this could be put forward.
+\Comment{Good point.
+We admit that the text was formulated a bit too negative, and that we can do better in explaining J1331 based on our models than just ruling out things.
+Also, some of the effects that mergers can have on galaxies \emph{could}, if they occured in J1331, actually explain some of the peculiar kinematic features of J1331.
+We tried to re-formulate section 5.2 (now 5.3) and discuss several aspects of the kinematics with respect to the merger history.}
 

### 2016-06-30 LensingPaper_draft_v4.01.tex
Added one comment to referee report.
Finished referee report (almost) and removed all TO DOs from the Paper.

@@
 The JAM modelling code by \citet{Cap08} evaluates \OLD{Equation \eqref{eq:explicitLOSvelCap}}\NEW{this expression for $\langle v_\text{los}^2\rangle(x',y')$} numerically for a given luminous tracer and mass distribution MGE and a given inclination.
-\Wilma{[TO DO: MAke sure M and N are introduced somewhere.]}
 %--------------------------------------------
@@
 
-\Wilma{[TO DO: Referee says: "In section 4.4.1, the NFW profile is fitted only to the inner data, and then is
-shown to not provide a good model for the data beyond that point. This is not
-entirely surprising, given that the outer data were not used to constrain the model!
-What happens if the NFW profile is fitted to both small- and large- radius data at
-once? (Perhaps it is impossible to find a good NFW model across the whole radius
-range, but if this is the case, then it should be stated.)"]}
-
 %============================================
@@
 The extrapolation of the model to larger radii however overestimates the data, does not exhibit a drop around $\sim 6''$ at all and seems to be therefore overall too massive.
-
-We also fitted a model with a cored logarithmic DM halo.
-The cored halo models are in general slightly less massive than the NFW halo and therefore fit the outer regions of J1331 better.
-However, the density profile of the cored halo as well as the I-band light distribution within the plane drop as $\rho(r) \propto r^{-2}$.
-There is therefore a strong degeneracy between the stellar mass and the DM.
-Overall, we were not able to obtain tight constraints on the cored logarithmic halo.
 %--------------------------------------------
@@
 
-\subsubsection{\NEW{Discussion}}
-
-\NEW{A fit to all nine available $v_\text{rms}$ data points would force the DM halo to be less massive.
+%--------------------------------------------
+
+\subsubsection{\NEW{Further tests and discussion}}
+
+We also fitted a model with a cored logarithmic DM halo.
+The cored halo models are in general slightly less massive than the NFW halo and therefore fit the outer regions of J1331 better.
+However, the density profile of the cored halo as well as the I-band light distribution within the plane drop as $\rho(r) \propto r^{-2}$.
+There is therefore a strong degeneracy between the stellar mass and the DM.
+Overall, we were not able to obtain tight constraints on the cored logarithmic halo.
+\NOTE{[NOTE: this paragraph was moved from 4.4.2 to 4.4.4.]}
+
+\NEW{As we only fitted the halo models to the inner regions, it is not surprising that they do not fit at larger radii.
+A fit to all nine available $v_\text{rms}$ data points would force the DM halo to be less massive.
 But with decreasing DM contribution in the inner regions the model approaches the mass-follows-light model in the center, that we already ruled out in Section \ref{sec:results_JAM_SB_MfL}.
-Allowing for free $\Upsilon_{*}(R')$, $\beta_z(R')$ and/or non-NFW $\rho_\text{halo}(r)$ profiles would over-fit the data again.
-Without further priors on the stellar $\Upsilon_{*}(R')$ and/or more data points, we can make only the following statement: A model with constant $\Upsilon_*$, moderately tangential $\beta_z$ and a spherical and massive DM component with high concentration can explain the central kinematics of J1331 very well, we have however ruled out that in this case the DM halo will follow a NFW halo profile at both small and large radii.}
-%--------------------------------------------
+Allowing for free $\Upsilon_{*}(R')$, $\beta_z(R')$ and/or more flexible $\rho_\text{halo}(r)$ profiles, which would be the reasonable next step, would over-fit the data again.
+Without further priors on the stellar $\Upsilon_{*}(R')$ and/or more data points, we can make only the following statement: A model with constant $\Upsilon_*$, moderately tangential $\beta_z$ and a spherical and massive DM component with high concentration can explain the central kinematics of J1331 very well.
+We have however ruled out that in this case the DM halo will follow a NFW halo profile at both small and large radii.}
+
+\NEW{We will also discuss the kinematics at larger radii in more depth in the discussion section \ref{sec:discussion_kinematics}.}
 
@@
 At large radii this could lead to an underestimation of the DM halo mass.}
-
-\Wilma{[TO DO: Mention that warps would require other modelling techniques than the axisymmetric Jeans models.]}
 %--------------------------------------------
@@
 \NEW{In the following section we will argue why we do not think that the \cite{SWELLSV} model is a good model for the central regions of J1331.
-We therefore also do not believe their findings that the central IMF is more bottom-heavy than Salpeter.} \Wilma{[TO DO: Find new place for: "\cite{SWELLSV} found systematically lower NFW halo masses ($v_\text{circ,halo}(5'') \sim 120~\text{km s}^{-1}$ according to their Figure 2) than we did ($v_\text{circ,halo}(R'=5'') \sim 200~\text{km s}^{-1}$)."]}
+We therefore also do not believe their findings that the central IMF is more bottom-heavy than Salpeter.}
 %--------------------------------------------
@@
 %--------------------------------------------
-\subsection{On J1331's \OLD{central }kinematics}
+\subsection{On J1331's \OLD{central }kinematics} \label{sec:discussion_kinematics}
 %--------------------------------------------
@@
 The first feature, the deep central $v_\text{rms}$ dip, was studied in detail in this work.
-The second feature, the drop and rise in $v_\text{rms}$ around \Wilma{[TO DO]}, is even harder to explain; below we will speculate about possible reasons that could cause such a signature.}
+The second feature, the drop and rise in $v_\text{rms}$ around $R'\sim6''$, is even harder to explain; below we will speculate about possible reasons that could cause such a signature.}
 
@@
 
-\NEW{First, we will compare our modelling results with the modelling results by \citet{SWELLSV} within \Wilma{[TO DO]}.}
+\NEW{First, we will compare our modelling results with the modelling results by \citet{SWELLSV} within $R_\text{eff}$.}
 
@@
 \NEW{Around $R'\sim7''$ the rotation curve and dispersion show some wiggles which lead to a spontaneous rise of the $v_\text{rms}$.
-As the spiral arms cross the major axis around this radius, we suspect they cause this disturbance of the axisymmetric kinematics.
-The DM halo should also start to dominate the kinematics at larger radii, whose total mass we expect more of the order of what \citet{SWELLSV} found and which we suspect has a profile that deviates strongly from a NFW halo at both small and large radii.
+As the spiral arms cross the major axis around this radius, we suspect they cause this disturbance of the axisymmetric kinematics.}
+
+\NEW{\emph{(iii) The profile of the DM halo at $R'\gtrsim 5''$:}}
+
+\NEW{The DM halo should start to dominate the kinematics at larger radii.
+\cite{SWELLSV}, who fitted a NFW halo to the gas kinematics in the outer regions, found lower halo masses ($v_\text{circ,halo}(5'') \sim 120~\text{km s}^{-1}$ according to their Figure 2) than we did ($v_\text{circ,halo}(5'') \sim 200~\text{km s}^{-1}$, Figure \ref{fig:vcirc_comparison}).
+As we did not fit the outer regions and only used a prior for $v_\text{200}$, their result in this regime is more reliable.
+Given our findings that a NFW halo does not fit the kinematics at both small and large radii, we suspect that the true halo has a profile that deviates strongly from a NFW halo.
 A more massive halo of NFW shape---as the one we found in this work---could however exist in J1331 if the galaxy had a strong kinematic warp in its disk due to the merger.}

### 2016-07-01 Answer_to_referee_report_LensingPaper.tex
Included all corrections that I wanted to. Now I sent it to Glenn and Aaron.

@@
 \begin{document}
+\begin{flushright}
+Wilma H. Trick\\
+Max-Planck-Institut f\"{u}r Astronomie\\
+K\"{o}nigstuhl 17\\
+69117 Heidelberg, Germany
+\end{flushright}
 
-From:  	ae@ras.org.uk
-Subject:  	MNRAS: MN-16-0473-MJ
-Date:  	Mon, March 14, 2016 1:00 pm
-To:  	trick@mpia.de
-Cc:  	trick@mpia.de,glenn@mpia.de,dutton@nyu.edu
+\noindent Anna Evripidou\\
+Assistant Editor\\
+"Monthly Notices" and "Geophysical Journal International"\\
+Royal Astronomical Society\\
 
-Dear Ms Trick
+\begin{flushright}
+Heidelberg, 4th of July 2016
+\end{flushright}
+
+\textbf{Subject:} Answer to the Referee Report on "A spiral galaxy's mass distribution uncovered through lensing and dynamics"\\\\
+
+Dear Ms. Evripidou,
+
+Dear anonymous referee,\\
+
+thank you very much for having a detailed look at our paper draft and preparing this helpful report.
+We made an effort to account for all the referee's comments and to make some of the sections a bit more understandable---we hope you agree.
+We attach the original letter and report below to which we added our answers to the referee's comments in blue and italics.
+\\\\
+Kind regards,\\
+Wilma Trick\\\\\\
+
+\noindent\textbf{Attachments:}
+\begin{itemize}
+\item \texttt{Trick{\_}J1331{\_}Modelling{\_}revised.tex/.pdf} - revised paper file ready for publishing (without any marked text or annotations), if the referee agrees.
+\item \texttt{Trick{\_}J1331{\_}Modelling{\_}revised{\_}all{\_}changes.pdf} - file in which all changes with respect to the previous version of the paper are marked (new text = green, deleted text = red, annotations = blue).
+\item \texttt{Trick{\_}J1331{\_}Modelling{\_}revised{\_}for{\_}referee.pdf} - file for the referee with the deleted text excluded to be more readable (new text = green, annotations = blue).
+\end{itemize}
+
+\newpage
+
+\noindent From:  	ae@ras.org.uk\\
+Subject:  	MNRAS: MN-16-0473-MJ\\
+Date:  	Mon, March 14, 2016 1:00 pm\\
+To:  	trick@mpia.de\\
+Cc:  	trick@mpia.de,glenn@mpia.de,dutton@nyu.edu\\\\
+
+Dear Ms Trick\\
 
@@
 MN-16-0473-MJ, which you submitted to Monthly Notices of the Royal Astronomical
-Society.
+Society.\\
 
 Minor revision of your manuscript is requested before it is reconsidered for
-publication.
+publication.\\
 
@@
 "Manuscripts with Decisions." Under "Actions," click on "Create a Revision." Your
-manuscript reference will be appended to denote a revision.
+manuscript reference will be appended to denote a revision.\\
 
-IMPORTANT: do not submit your revised manuscript as a new paper!
+IMPORTANT: do not submit your revised manuscript as a new paper!\\
 
@@
 generate your bibliography in Latex, please include this in your .tar archive along
-with the .bbl and .tex files; this will aid the editing and typesetting process.
+with the .bbl and .tex files; this will aid the editing and typesetting process.\\
 
@@
 for our publishers, as accepted manuscripts are now immediately published online
-ahead of the proof-corrected version.
+ahead of the proof-corrected version.\\
 
@@
 your revision within six months, we may consider it withdrawn and request it be
-resubmitted as a new submission.
+resubmitted as a new submission.\\
 
@@
 ensure that each version of your paper submitted to MNRAS is completely ready for
-publication!
+publication!\\
 
-I look forward to receiving your revised manuscript.
+I look forward to receiving your revised manuscript.\\
 
-Regards,
+Regards,\\
 
-Anna
+Anna\\
 
-Anna Evripidou
-Assistant Editor
-"Monthly Notices" and "Geophysical Journal International"
-Royal Astronomical Society
-Email: ae@ras.org.uk
-Tel: (+44) 0207 734 3307 Ext. 124 (except Wednesday)
-Tel: (+44) 0207 734 3307 Ext. 117 (Wednesday)
+\noindent Anna Evripidou\\
+Assistant Editor\\
+"Monthly Notices" and "Geophysical Journal International"\\
+Royal Astronomical Society\\
+Email: ae@ras.org.uk\\
+Tel: (+44) 0207 734 3307 Ext. 124 (except Wednesday)\\
+Tel: (+44) 0207 734 3307 Ext. 117 (Wednesday)\\
 
@@
 any attachment but please notify the sender (above) and delete this message from
-your system.
+your system.\\
 
-cc: all listed co-authors.
+cc: all listed co-authors.\\
 
-Reviewer's Comments:
-Reviewer: 1
+\noindent Reviewer's Comments:\\
+Reviewer: 1\\
 
-Comments to the Author
+Comments to the Author\\
 
@@
 kinematics and strong lensing to investigate the mass structure of the spiral galaxy
-J1331. 
-\Comment{Thanks. It is a very exiting galaxy that's definitely worth exploring.}
+J1331. \\\Comment{Thanks. It is a very exiting galaxy that's definitely worth exploring.}
 
@@
 probably be removed altogether, and the second paragraph promoted to the beginning.
-\Comment{That is a good point.
+\\\Comment{That is a good point.
 We changed the opening paragraph to a general sentence why determining the matter distribution of galaxies is important.
@@
 feature of the galaxy in question and is also a very active topic of research.
-\Comment{Good point.
+\\\Comment{Good point.
 1.) We added a sentence mentioning the important role of mergers in modifying the matter distribution and added some recent references.
@@
 necessary to include equation 22.
-\Comment{We made an effort to remove unnecessary equations in Section 3.2.1, tighten the explanation of the derivation of the Jeans equations in Section 3.3.1 and 3.3.3 and removed big and clumsy mathematical expressions by referring to the explicit equations in the literature instead.
+\\\Comment{We made an effort to remove unnecessary equations in Section 3.2.1, tighten the explanation of the derivation of the Jeans equations in Section 3.3.1 and 3.3.3 and removed big and clumsy mathematical expressions by referring to the explicit equations in the literature instead.
 In 3.3.2 we refer stronger to the changes we made to Capellari's JAM code and kept the corresponding equations.
@@
 such a model to this section, or else comment on why they do not attempt it.
-\Comment{We have indeed tried a ``mass-follows-light'' JAM model with constant anisotropy and free M/L profile early on in our investigations of J1331.
+\\\Comment{We have indeed tried a ``mass-follows-light'' JAM model with constant anisotropy and free M/L profile early on in our investigations of J1331.
 This was unsuccessful to a degree that showing the result in the paper would not be reasonable.
@@
 once? (Perhaps it is impossible to find a good NFW model across the whole radius
-range, but if this is the case, then it should be stated.) \Comment{Yes, you are completely right.
+range, but if this is the case, then it should be stated.) \\\Comment{Yes, you are completely right.
 Our initial tests tried of course to fit the whole range of data, but failed.
@@
 framework, to try to come up with a better picture of the nature of J1331's IMF.
-\Comment{This is a valid point of criticism.
+\\\Comment{This is a valid point of criticism.
 We thought again about the different models and indications for different IMFs that we collected and came to the conclusion that an IMF slightly less bottom-beavy than the Salpeter IMF is the most likely model for J1331's bulge.
@@
 suggestions like this could be put forward.
-\Comment{Good point.
+\\\Comment{Good point.
 We admit that the text was formulated a bit too negative, and that we can do better in explaining J1331 based on our models than just ruling out things.

### 2016-07-01 LensingPaper_draft_v4.02.tex
Included all corrections that I wanted to. Now I sent it to Glenn and Aaron.

--- 2016-06-30 LensingPaper_draft_v4.01.tex
@@
 \newcommand{\NEW}[1]{\textcolor{ForestGreen}{#1}}
-%\newcommand{\OLD}[1]{\textcolor{Red}{#1}}
-\newcommand{\OLD}[1]{}
+\newcommand{\OLD}[1]{\textcolor{Red}{#1}}
+%\newcommand{\OLD}[1]{}
 
@@
 
-\NEW{The mass distribution of massive galaxies can be observationally measured in completely independent fashions by gravitational lensing and dynamical modelling.
+\NEW{The mass distribution of massive galaxies can be measured in completely independent fashions by gravitational lensing and dynamical modelling.
 Combining these two methods allows for valuable cross-checking opportunities to disentangle the galactic stellar and DM content.}
@@
 Taking a light-weighted projection along the line-of-sight gives a model prediction for the line-of-sight velocity second moment \NEW{$\langle v_\text{los}^2\rangle(x',y')$}, which is comparable to actual spectroscopic measurements of the second velocity moment.
-Details of the derivation \NEW{from the Jeans equations} using the MGE formalism are \OLD{given}\NEW{laid out} in \citet{Cap08} and in the appendix of \citet{GlennEC}.
+Details of the derivation \NEW{of $\langle v_\text{los}^2\rangle(x',y')$ from the Jeans equations} using the MGE formalism are \OLD{given}\NEW{laid out} in \citet{Cap08} and in the appendix of \citet{GlennEC}.
 \OLD{We therefore just give the result for the line-of-sight second velocity moment prediction from the Jeans equations,}\NEW{The result for $\langle v_\text{los}^2\rangle(x',y')$ in particular is given in Equation (28) and Equation (A18), respectively.}
@@
 \OLD{The model in Equation \eqref{eq:explicitLOSvelCap}}\NEW{The model derived from the Jeans equations as outlined in Section \ref{sec:model_JAM_JAM}} predicts the intrinsic $\langle v_\text{los}^2 \rangle_\text{intr}\equiv\langle v_\text{los}^2\rangle$ at a given position on the sky, which needs then to be modified to $\langle v_\text{los}^2 \rangle_\text{obs}$ according to the mode of observation to be comparable to the measurements.
-The measured $v_\text{rms}$ is a light-weighted mean for a pixel along the long-slit of the spectrograph, with width $L_y = 1''$ \citep{SWELLSV} and a certain given extent along the galaxy's major axis, $L_x$, i.e., for a rectangular aperture
+The measured $v_\text{rms}$ \NEW{in this work} is a light-weighted mean for a pixel along the long-slit of the spectrograph, with width $L_y = 1''$ \citep{SWELLSV} and a certain given extent along the galaxy's major axis, $L_x$, i.e., for a rectangular aperture
 \begin{equation}
@@
 The intrinsic galaxy rotation curve is the first velocity moment $\langle v_\phi\rangle = \sqrt{\langle v_\phi^2 \rangle - \sigma_\phi^2}$.
-The observed rotation velocity is the projection of the light-weighted contributions to $\langle v_\phi\rangle$ along the line-of-sight \NEW{(Equation (31) in \citep{Cap08}).} \OLD{\citep{Cap08},
+The observed rotation velocity is the projection of the light-weighted contributions to $\langle v_\phi\rangle$ along the line-of-sight \NEW{(Equation (31) in \citet{Cap08}).} \OLD{\citep{Cap08},
 \begin{equation*}
@@
 \end{equation}
-(their equation 10), with a Gaussian scatter of $\sigma_{\log c_{200}} = 0.105$ (their Table A2).
+(their \OLD{e}\NEW{E}quation 10), with a Gaussian scatter of $\sigma_{\log c_{200}} = 0.105$ (their Table A2).
 \NEW{In Section \ref{sec:results_JAM_NFW} we will use this relation as prior information to guide the modelling towards realistic NFW halo shapes.}
@@
 A slight drop could be expected when the reddish bulge turns into the bluish disk and the contribution of the stellar component becomes less due to a lower $\Upsilon_\text{I,*}$ for younger and bluer populations.
-\NEW{Corresponding fitting attempts with the matter model at hand were however unsuccessful: Leaving all five $\Upsilon_{\text{I,tot,}i}$ free lead to over-fitting in the central regions of J1331, while not allowing for sufficient flexibility further out at $R'\gtrsim4''$ (because four of the five $\sigma_i$ in the light MGE in Table \ref{tab:MGEF814W} are $< 1.2''$).}
-
-\NEW{For the inner regions the model with rising $\Upsilon(R')$ seems to be a very good model:} In Figure \ref{fig:enclMass_modelG} we overplot the enclosed mass profile with the Einstein mass $M_\text{ein} = (7.77 \pm 0.33) \cdot 10^{10} M_\odot$ at the Einstein radius found from lensing in Table \ref{tab:bestfitlensmodel}.
+\NEW{Corresponding fitting attempts with the matter model at hand were however unsuccessful: Leaving all five $\Upsilon_{\text{I,tot,}i}$ free lead to over-fitting in the central regions of J1331, while not allowing for sufficient flexibility further out at $R'\gtrsim4''$ (because four of the five $\sigma_i$ in the light MGE in Table \ref{tab:MGEF814W} are $< 1.2''$) to properly model the transition from bulge to disk.}
+
+\NEW{For the inner regions the model with rising $\Upsilon(R')$ seems however to be a very good model:} In Figure \ref{fig:enclMass_modelG} we overplot the enclosed mass profile with the Einstein mass $M_\text{ein} = (7.77 \pm 0.33) \cdot 10^{10} M_\odot$ at the Einstein radius found from lensing in Table \ref{tab:bestfitlensmodel}.
 The agreement between the Einstein mass and the independently found $M(<R_\text{ein}) = 7.49 \cdot 10^{10} M_\odot$ from dynamical modelling is striking.
@@
 
-\NEW{As we only fitted the halo models to the inner regions, it is not surprising that they do not fit at larger radii.
+\NEW{As we only fitted the halo models to the inner regions, it is not surprising that they do not fit the kinematics at larger radii.
 A fit to all nine available $v_\text{rms}$ data points would force the DM halo to be less massive.
 But with decreasing DM contribution in the inner regions the model approaches the mass-follows-light model in the center, that we already ruled out in Section \ref{sec:results_JAM_SB_MfL}.
-Allowing for free $\Upsilon_{*}(R')$, $\beta_z(R')$ and/or more flexible $\rho_\text{halo}(r)$ profiles, which would be the reasonable next step, would over-fit the data again.
-Without further priors on the stellar $\Upsilon_{*}(R')$ and/or more data points, we can make only the following statement: A model with constant $\Upsilon_*$, moderately tangential $\beta_z$ and a spherical and massive DM component with high concentration can explain the central kinematics of J1331 very well.
+Allowing for free $\Upsilon_\text{I,*}(R')$, $\beta_z(R')$ and more flexible $\rho_\text{halo}(r)$ profiles, which would be the reasonable next step, would over-fit the data.
+Without further priors on the stellar $\Upsilon_\text{I,*}(R')$ or more data points, we can make only the following statement: A model with constant $\Upsilon_\text{I,*} = 4.2\pm 0.2$, moderately tangential $\beta_z = -0.4\pm 0.1$ and a spherical and massive DM component with high concentration ($c_\text{200}=8\pm 2$) can explain the central kinematics of J1331 very well.
 We have however ruled out that in this case the DM halo will follow a NFW halo profile at both small and large radii.}
 
-\NEW{We will also discuss the kinematics at larger radii in more depth in the discussion section \ref{sec:discussion_kinematics}.}
+\NEW{We will also discuss the kinematics at larger radii in more depth in the discussion Section \ref{sec:discussion_kinematics}.}
 
@@
 Some of them capture the observed kinematics, but none of them work at both small and large radii.
-\NEW{In the following we try to resolve some of the ambiguities by discussing possible reasons, by comparing our results to previous work and by venturing some guesses on the true nature of J1331's matter distribution, which should be easily testable by future observations.}\OLD{In the following we discuss possible reasons, also by comparing our results to previous work.}
+\NEW{In the following we try to resolve some of the ambiguities by discussing possible reasons, by comparing our results to previous work and by hazarding some guesses on the true nature of J1331's matter distribution, which should be easily testable by future observations.}\OLD{In the following we discuss possible reasons, also by comparing our results to previous work.}
 %--------------------------------------------
@@
 Warps lead to a twist in the projected kinematic major axis with radius, which is then also misaligned with the photometric major axis (\citealt{1998gaas.book.....B}, \S 8.2.4).
-\NEW{We note that kinematics measured along an axis different from the kinematic major axis would result in $v_\text{rot}$ measurements being lower than the actual maximum $v_\text{circ}$.
-At large radii this could lead to an underestimation of the DM halo mass.}
 
@@
 We also compare our results from Section \ref{sec:results_JAM_NFW} with the study by \citet{SWELLSV}.
-They found that the bulge of J1331 has an IMF \emph{more} bottom-heavy than the Salpeter IMF from fitting a NFW halo to (i) the Einstein mass and (ii) gas kinematics at larger radii $\gtrsim 8''$.
-In Section \ref{sec:results_JAM_NFW} we fitted a mass model with NFW halo to (i) the Einstein mass and (ii) stellar kinematics within $\sim 3.5''$.
-Our best fit $\Upsilon_\text{I,*} = 4.2 \pm 0.2$ (see Table \ref{tab:modelB4_bestfit}) indicates a \emph{less} bottom-heavy IMF than the Salpeter IMF.
-\NEW{In the following section we will argue why we do not think that the \cite{SWELLSV} model is a good model for the central regions of J1331.
+They found that the bulge of J1331 has an IMF \emph{more} bottom-heavy than the Salpeter IMF\OLD{ from fitting a NFW halo to (i) the Einstein mass and (ii) gas kinematics at larger radii $\gtrsim 8''$}.
+\NEW{Our fitting attempt---using more data within $\sim 3.5''$ than \citet{SWELLSV}---in}\OLD{ In} Section \ref{sec:results_JAM_NFW} \OLD{we fitted a mass model with NFW halo to (i) the Einstein mass and (ii) stellar kinematics within $\sim 3.5''$.
+Our best fit }\NEW{gave} $\Upsilon_\text{I,*} = 4.2 \pm 0.2$ \NEW{as best fit} (see Table \ref{tab:modelB4_bestfit})\NEW{, which} indicates a \emph{less} bottom-heavy IMF than the Salpeter IMF.
+\NEW{In Section \ref{sec:discussion_kinematics} we will argue why we do not think that the \cite{SWELLSV} model is a good model for the central regions of J1331.
 We therefore also do not believe their findings that the central IMF is more bottom-heavy than Salpeter.}
@@
 Unfortunately the spiral arms make the disk of the galaxy difficult to model.
-At these larger radii a possible misalignment of long-slit and galaxy's kinematic major axis would also cause a stronger underestimation of the true $v_\text{rot}$ and would add to the drop in $v_\text{rms}$.}
+At these larger radii a possible misalignment of long-slit and galaxy's kinematic major axis---be it the result of a slightly faulty mode of observation or due to a kinematic twist caused by the merger---would also measure a lower $v_\text{rot}$, cause therefore a stronger underestimation of the true $v_\text{circ}$ and would add to the drop in $v_\text{rms}$.}
 
@@
 Given our findings that a NFW halo does not fit the kinematics at both small and large radii, we suspect that the true halo has a profile that deviates strongly from a NFW halo.
-A more massive halo of NFW shape---as the one we found in this work---could however exist in J1331 if the galaxy had a strong kinematic warp in its disk due to the merger.}
+A more massive halo of NFW shape---as the one we found in this work---could however exist in J1331 if the galaxy had a strong kinematic twist in its disk due to the merger.}
 
@@
 \NEW{This ruled out the previous findings of \citet{SWELLSV} for J1331's bulge.
-We discussed that, to}\OLD{ To} describe the observed stellar kinematics\NEW{,} we \OLD{either}\NEW{most likely} require a \OLD{strong}\NEW{moderate} contribution of a DM halo already in the bulge, \NEW{moderate tangential velocity anisotropy, $\beta_z \simeq -0.4\pm0.1$, }\OLD{or} \NEW{and possibly even} a \OLD{strongly} varying stellar mass-to-light ratio \NEW{within the bulge, which could be the result of the previous merger event}.
+We discussed that, to}\OLD{ To} describe the observed stellar kinematics\NEW{,} we \OLD{either}\NEW{most likely} require a \OLD{strong}\NEW{moderate} contribution of a DM halo already in the bulge, \NEW{moderate tangential velocity anisotropy, $\beta_z \simeq -0.4\pm0.1$, }\OLD{or} \NEW{and possibly even} a \OLD{strongly} varying stellar mass-to-light ratio\NEW{, which could be the result of the previous merger event}.
 \NEW{We argue that we expect the total stellar mass-to-light ratio within the bulge to be slightly less bottom-heavy than a Salpeter IMF, $\Upsilon_\text{I,*}\simeq 4.2\pm0.2$.} We also showed that it is possible to construct a model which includes the counter-rotating core and fits the rotation curve at large radii.

### 2016-07-19 LensingPaper_draft_v4.02.tex
Included changes from Aaron.

@@
 \begin{abstract}
-We investigate the matter distribution of a spiral galaxy with counter-rotating stellar core, SDSS J1331+3628 (J1331), independently with gravitational lensing and stellar dynamical modelling.
-By fitting a gravitational potential model to a quadruplet of lensing images around J1331's bulge, we tightly constrain the mass inside the Einstein radius $R_\text{ein}=(0.91\pm0.02)''(\simeq1.83\pm0.04~\text{kpc})$ to within 4\%: $M_\text{ein} = (7.8\pm0.3) \cdot 10^{10} M_\odot$.
+We investigate the matter distribution of a spiral galaxy with \NEW{a} counter-rotating stellar core, SDSS J1331+3628 (J1331), independently with gravitational lensing and stellar dynamical modelling.
+By fitting a gravitational potential model to a quadruplet of lensing images around J1331's bulge, we tightly constrain the mass inside the Einstein radius $R_\text{ein}=(0.91\pm0.02)''(\simeq1.83\pm0.04~\text{kpc})$ to within 4\%: $M_\text{ein} = (7.8\pm0.3) \OLD{\cdot}\NEW{\times} 10^{10} \text{M}_\odot$.
 We model observed long-slit major axis stellar kinematics in J1331's central regions by finding Multi-Gaussian Expansion (MGE) models for the stellar and dark matter distribution that solve the axisymmetric Jeans equations.
@@
 \NEW{The mass distribution of massive galaxies can be measured in completely independent fashions by gravitational lensing and dynamical modelling.
-Combining these two methods allows for valuable cross-checking opportunities to disentangle the galactic stellar and DM content.}
-
-Massive galaxies can act as gravitational lenses, deflect the light of background sources and give rise to multiple images.
+Combining these two methods allows for valuable cross-checking opportunities to disentangle the galactic stellar and DM content.} Massive galaxies can act as gravitational lenses, deflect the light of background sources and give rise to multiple images.
 This strong gravitational lensing tightly constrains the projected total mass of the lens galaxy inside $\sim 1''$ (e.g., \citealt{2010ARA&A..48...87T}).
@@
 However, due to its dissipative nature gas motions are very sensitive to disturbances by, e.g., spiral arms and bars (e.g., \citealt{2004dad..book.....S}).
-
 Because stars are dissipationless dynamical tracers and present almost everywhere in the galaxy, stellar dynamical modelling can complement mass constraints from lensing at small and gas motions at large radii.
@@
 
-The Sloan WFC Edge-on Late-type Lens Survey (SWELLS, WFC = Wide field camera) \citep{SWELLSI,SWELLSII,SWELLSIII,SWELLSIV,SWELLSV,SWELLSVI} is dedicated to find and investigate spiral galaxies, which are (i) strong gravitational lenses and (ii) observed almost edge-on, such that rotation curves can be easily measured.
+The Sloan WFC Edge-on Late-type Lens Survey (SWELLS, WFC = Wide field camera) \citep{SWELLSI,SWELLSII,SWELLSIII,SWELLSIV,SWELLSV,SWELLSVI} is dedicated to \OLD{find}\NEW{finding} and \OLD{investigate}\NEW{investigating} spiral galaxies, which are (i) strong gravitational lenses and (ii) observed almost edge-on, such that rotation curves can be easily measured.
 By combining lensing and dynamical modelling, degeneracies inherent in both methods can be broken.
@@
 J1331 is located at right ascension = 202.91800$^\circ$ and declination = 36.46999$^\circ$ (epoch J2000).
-\citet{SWELLSI} found from SDSS spectra that J1331 has two redshifts inside $R'=1''$: J1331 itself has $z_d = 0.113$ and $z_s = 0.254$ is the redshift of the lensed background source \citep{SWELLSIII}.
+\citet{SWELLSI} found from SDSS spectra that J1331 has two redshifts inside \NEW{the projected radius on the sky} $R'=1''$: J1331 itself has $z_d = 0.113$ and $z_s = 0.254$ is the redshift of the lensed background source \citep{SWELLSIII}.
 According to the WMAP5 cosmology \citep{WMAP5cosm}, J1331 has an angular diameter distance of 414 Mpc, which translates into a transverse scaling of $1'' \hat{=} 2.01~\text{kpc}$.
+\NEW{We summarize all galaxy parameters also in Table \ref{tab:galaxyparameters}.}
 %--------------------------------------------
@@
 We use HST imaging of J1331 by \citet{SWELLSI}.
-They performed high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) and its WF3 CCD chip.
+They \OLD{performed}\NEW{obtained} high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) and its WF3 CCD chip.
 The images are a combination of four exposures with each an exposure time of $400~\text{sec}$ and were drizzled to a pixel scale of 1 pixel = $0.05''$.
@@
 We subtract $2.3~\text{km s}^{-1}$ from $v_\text{rot}$ to ensure $v_\text{rot}(R'=0) \sim 0$ as a possible correction term for a misjudgement of the systemic velocity.
-We also symmetrize the data within $4''$ and asign a minimum error of $\delta v_\text{rms} \geq 5~\text{km s}^{-1}$ to the $v_\text{rms}$ data.
+We also symmetrize the data within $4''$ and asign a minimum error of $\delta v_\text{rms} \OLD{\geq}\NEW{=} 5~\text{km s}^{-1}$ to the $v_\text{rms}$ data.
 In our dynamical Jeans modelling approach, which is based on the assumption of axisymmetry, only stellar kinematics with either $R'  \lesssim 3.5''$ or $R' \lesssim 4''$ are used.
@@
 %--------------------------------------------
-$I(R',\theta')$ describes the intrinsic, to 2D projected light distribution or surface density of the galaxy.
-Under the assumption that the galaxy is oblate and axisymmetric, and given the inclination angle $i$ of the galaxy with respect to the observer, MGEs allow an analytic deprojection of the 2-dimensional MGE to get a 3-dimensional axisymmetric light distribution or density $\nu(R,z)$ for the galaxy,
+$I(R',\theta')$ describes the intrinsic\OLD{, to} \NEW{and} 2D projected light distribution or surface density of the galaxy.
+Under the assumption that the galaxy is oblate and axisymmetric, and given the inclination angle $\OLD{i}\NEW{inc}$ of the galaxy with respect to the observer, MGEs allow an analytic deprojection of the 2-dimensional MGE to get a 3-dimensional axisymmetric light distribution or density $\nu(R,z)$ for the galaxy,
 \begin{equation}
@@
 \end{equation}
-where $R$ is the distance from the galaxy's short axis and $z$ the height above the galactic plane.
-The flattening $q_i$ of each axisymmetric 3D Gaussian and its central density $\nu_{0,i}$ follow from the observed 2D axis ratio $q'_i$ and surface density $I_{0,i}$ as
+where $R$ is the distance from the galaxy's short axis and $z$ the height above the galactic plane.\footnote{\NEW{$(R,z)$ are cylindrical coordinates aligned with the galactic plane.
+The primed $(R',z')$ denote polar coordinates on the plane of the sky.}} The flattening $q_i$ of each axisymmetric 3D Gaussian and its central density $\nu_{0,i}$ follow from the observed 2D axis ratio $q'_i$ and surface density $I_{0,i}$ as
 \begin{eqnarray}
-q_i^2 &=& \frac{q_i'^2 - \cos^2 i}{\sin^2 i}\\
+q_i^2 &=& \frac{q_i'^2 - \cos^2 \OLD{i}\NEW{(inc)}}{\sin^2 \OLD{i}\NEW{(inc)}}\\
 \nu_{0,i} &=& \frac{q_i' I_{0,i}}{q_i \sqrt{2 \pi \sigma_i^2}}.
@@
 We summarize the basic formalism (see also \citealt{1992grle.book.....S,1996astro.ph..6001N,2006glsw.conf....1S,2006glsw.conf...91K,2010ARA&A..48...87T}).
-The angular diameter distance from the observer to the lens is $D_d$, to the source plane $D_s$, and the distance between the lens and source plane is $D_{ds}$.
+The angular diameter distance from the observer to the lens is $D_\text{d}$, to the source plane $D_\text{s}$, and the distance between the lens and source plane is $D_\text{ds}$.
 The deflection potential of the lens is its potential projected along the line of sight $z'$ and rescaled to
 \begin{equation}
-\psi(\vect{\theta}) \OLD{:=}\NEW{\equiv} \frac{D_{ds}}{D_d D_s} \frac{2}{c^2} \int \Phi(\vect{r}=D_d \vect{\theta},z') {\ \mathrm d} z', \label{eq:psidef}
+\psi(\vect{\theta}) \OLD{:=}\NEW{\equiv} \frac{D_\text{ds}}{D_\text{d} D_\text{s}} \frac{2}{c^2} \int \Phi(\vect{r}=D_\text{d} \vect{\theta},z') {\ \mathrm d} z', \label{eq:psidef}
 \end{equation}
@@
 into an image $\vect{\theta}_i = (x_i',y_i')$.
-The gradient of the deflection potential, $\vect{\nabla}_\theta \psi(\vect{\theta})$, is equal to the angle by which the light is deflected multiplied by $D_{ds}/D_{s}$.
+The gradient of the deflection potential, $\vect{\nabla}_\theta \psi(\vect{\theta})$, is equal to the angle by which the light is deflected multiplied by $D_\text{ds}/D_\text{s}$.
 
@@
 \begin{equation}
-\Delta t(\vect{\theta}) = \frac{(1+z_d)}{c} \frac{D_d D_s}{D_{ds}} \left[ \frac 12 (\vect{\theta} - \vect{\beta})^2 - \psi(\vect{\theta})\right]. \label{eq:timedelay}
+\Delta t(\vect{\theta}) = \frac{(1+z_d)}{c} \frac{D_\text{d} D_\text{s}}{D_\text{ds}} \left[ \frac 12 (\vect{\theta} - \vect{\beta})^2 - \psi(\vect{\theta})\right]. \label{eq:timedelay}
 \end{equation}
@@
 \begin{equation}
-\Sigma_\text{crit} \equiv \frac{c^2}{4\pi G} \frac{D_s}{D_d D_{ds}}
+\Sigma_\text{crit} \equiv \frac{c^2}{4\pi G} \frac{D_\text{s}}{D_\text{d} D_\text{ds}}
 \end{equation}
@@
 \NEW{In this way one can now calculate an unambiguous model prediction for the velocity dispersion tensor $\langle v_i v_j \rangle(R,z) = \langle v_i^2 \rangle(R,z)$ (with $i,j \in \{ R,\phi, z\}$ and $\langle v_i v_j \rangle=0$ if $i\neq j$).
-To compare it with observations, $\langle v_i^2 \rangle(R,z)$ has to be}\OLD{$\langle v_i^2 \rangle$ is then} rotated by the inclination angle $i$ to the coordinate system of the observer; $(x',y')$ is the plane of the sky and $z'$ the line-of-sight, where $x'$ is alinged with the galaxy's major axis.
+To compare it with observations, $\langle v_i^2 \rangle(R,z)$ has to be}\OLD{$\langle v_i^2 \rangle$ is then} rotated by the inclination angle $\OLD{i}\NEW{inc}$ to the coordinate system of the observer; $(x',y')$ is the plane of the sky and $z'$ the line-of-sight, where $x'$ is alinged with the galaxy's major axis.
 Taking a light-weighted projection along the line-of-sight gives a model prediction for the line-of-sight velocity second moment \NEW{$\langle v_\text{los}^2\rangle(x',y')$}, which is comparable to actual spectroscopic measurements of the second velocity moment.
@@
 K(x',y') &\equiv& (\text{PSF} \ast \text{AP})(x',y') \nonumber\\
-&=& \frac{1}{4} \prod_{u \in \{x',y'\}} \left[ \text{erf}\left( \frac{L_u/2 - u}{\sqrt{2}\sigma_\text{seeing}}\right) + \text{erf} \left( \frac{L_u/2 + u}{\sqrt{2} \sigma_\text{seeing}} \right) \right],
+&=& \frac{1}{4} \prod_{u \in \{x',y'\}} \left[\text{erf}\left( \frac{L_u/2 - u}{\sqrt{2}\sigma_\text{seeing}}\right) \right.\nonumber\\
+ && + \left. \text{erf} \left( \frac{L_u/2 + u}{\sqrt{2} \sigma_\text{seeing}} \right) \right],
  \end{eqnarray}
@@
 \begin{equation*}
-I \langle v_\text{los}\rangle = \int_{-\infty}^{+\infty} \nu \langle v_\phi\rangle \cos \phi \sin i \diff z'.
+I \langle v_\text{los}\rangle = \int_{-\infty}^{+\infty} \nu \langle v_\phi\rangle \cos \phi \sin \OLD{i}\NEW{inc} \diff z'.
 \end{equation*}}
@@
 and two free parameters, the scale length $r_s$ and a parameter describing the total mass of the halo.
-We will use $v_\text{200}\NEW{\equiv \sqrt{GM_{200}/r_{200}}}$, which is the circular velocity at the radius $r_\text{200}$ within which the mean density of the halo is 200 times the cosmological critical density $\rho_\text{crit} \equiv (2H^2)/(8\pi G)$, \OLD{i.e.,}\NEW{ and where $M_{200} \equiv M(<r_{200}) \stackrel{!}{=} \frac 43 \pi r_{200}^3 \cdot 200\rho_\text{crit}(z=0)$.}
+We will use $v_\text{200}\NEW{\equiv \sqrt{GM_{200}/r_{200}}}$, which is the circular velocity at the radius $r_\text{200}$ within which the mean density of the halo is 200 times the cosmological critical density $\rho_\text{crit} \equiv (2H^2)/(8\pi G)$, \OLD{i.e.,}\NEW{ and where $M_{200} \equiv M(<r_{200}) \stackrel{!}{=} \frac 43 \pi r_{200}^3 \times 200\rho_\text{crit}(z=0)$.}
 \OLD{\begin{eqnarray*}
@@
 \end{eqnarray*}}
-with $\rho_\text{crit}(z=0)=1.43 \cdot 10^{-7} M_\odot / \text{pc}^3$ in the WMAP5 cosmology by \citet{WMAP5cosm}.
+with $\rho_\text{crit}(z=0)=1.43 \OLD{\cdot}\NEW{\times} 10^{-7} \text{M}_\odot / \text{pc}^3$ in the WMAP5 cosmology by \citet{WMAP5cosm}.
 \OLD{How much the mass is concentrated in the center of the NFW halo is given by the concentration parameter
@@
 \begin{equation}
-\langle \log c_{200} \rangle (M_{200}) = 0.830 - 0.098 \log \left(h \frac{M_{200}}{10^{12} M_\odot} \right) \label{eq:Maccio08}
+\langle \log c_{200} \rangle (M_{200}) = 0.830 - 0.098 \log \left(h \frac{M_{200}}{10^{12} \text{M}_\odot} \right) \label{eq:Maccio08}
 \end{equation}
@@
 redshift \citep{SWELLSIII}                 & $z_d$ & $0.113$ \\
-angular diameter distance & $D_d$ [Mpc] & $414$ \\
+angular diameter distance & $D_\text{d}$ [Mpc] & $414$ \\
 scaling                   & $1~\text{kpc} / 1''$ & $2.006$ \\
@@
 average ellipticity & $\epsilon = 1 - q'$ & $0.402$ \\
-estimated inclination & $i$ [$^\circ$] & $70$\\
+estimated inclination & $\OLD{i}\NEW{inc}$ [$^\circ$] & $70$\\
 apparent I-band magnitude & $m_\text{I}$ [mag] & $15.77$ \\
@@
 The orange lines indicate here contours of a smooth IRAF \emph{ellipse} fit to J1331 in the F814W filter; the grey lines are the corresponding best fit MGE.
-This MGE is not used for dynamical modelling because the dynamics in the outer regions are strongly affected by non-axisymmetries (e.g., spiral arms).
-We use it, however, to estimate the galaxy's total luminosity and effective radius, and to get a prediction for the dynamics of the outer regions.}
+This MGE is not used for dynamical \OLD{modelling}\NEW{model fitting} because the dynamics in the outer regions are strongly affected by non-axisymmetries (e.g., spiral arms).
+We use it, however, to estimate the galaxy's total luminosity and effective radius, and to get \OLD{a prediction}\NEW{an estimate} for the dynamics of the outer regions.}
 \end{figure*}
@@
 \begin{equation}
-\mu_{I,0,i} \simeq -2.5 \log_{10}\left( \frac{C_{0,i}\text{[counts/pixel]}}{T[\text{sec}] \cdot S[''/\text{pixel width}]^2}\right) + Z + C + A_I, \label{eq:muI_}
+\mu_{I,0,i} \simeq -2.5 \log_{10}\left( \frac{C_{0,i}\text{[counts/pixel]}}{T[\text{sec}] \OLD{\cdot}\NEW{\times} S[''/\text{pixel width}]^2}\right) + Z + C + A_I, \label{eq:muI_}
 \end{equation}
@@
 \begin{equation}
-\cos^2 i = \frac{q'^2 - q_0^2}{1 - q_0^2}
+\cos^2 \OLD{i}\NEW{(inc)} = \frac{q'^2 - q_0^2}{1 - q_0^2}
 \end{equation}
 and a correction of $+3^\circ$ \citep{1988ngc..book.....T}.
-Our estimate for the inclination is therefore $i \approx 70^\circ$.
+Our estimate for the inclination is therefore $\OLD{i}\NEW{inc} \approx 70^\circ$.
 Given this inclination, the 2-dimensional MGE models can be deprojected into three dimensions (see Section \ref{sec:MGE_theo_deprojection}).
@@
 J1331's total I-band luminosity is determined by summing up the luminosity contributions of all the MGE Gaussians for the outer regions (shown as grey lines in Figure \ref{fig:MGEouterRegions}).
-We find $L_\text{I,tot} \simeq 5.6 \cdot 10^{10} ~L_\odot$.
+We find $L_\text{I,tot} \simeq 5.6 \OLD{\cdot}\NEW{\times} 10^{10} ~L_\odot$.
 This corresponds to an apparent magnitude of $m_I = 15.77~\text{mag}$.
@@
 Einstein radius      & $R_\text{ein}$ [$''$]             & $0.907$ & $0.91$  & $\pm$ & $     0.02$ & ($2\%$)\\
-Einstein mass        & $M_\text{ein}$ [$10^{10} M_\odot$]  & $7.72$  & $7.8 $  & $\pm$ & $      0.3$ & ($4\%$) \\
-Critical mass        & $M_\text{crit}$ [$10^{10} M_\odot$] & $7.87$  & $7.9$   & $\pm$ & $      0.3$ & ($4\%$)\\
+Einstein mass        & $M_\text{ein}$ [$10^{10} \text{M}_\odot$]  & $7.72$  & $7.8 $  & $\pm$ & $      0.3$ & ($4\%$) \\
+Critical mass        & $M_\text{crit}$ [$10^{10} \text{M}_\odot$] & $7.87$  & $7.9$   & $\pm$ & $      0.3$ & ($4\%$)\\
 Source position      & $x_s'$ [$''$]                      & $0.095$ & $0.09 $ & $\pm$ & $     0.03$ & ($28\%$)\\
@@
 The source is located close to a cusp of the diamond-shaped caustic: a lensing configuration for which we indeed expect four images.
-Figure \ref{fig:bestfitlensmodel} also shows the (smoothed) residuals from the F450W image subtracted by an IRAF \emph{ellipse} brightness model and the contours of the best fit model's time delay surface \NEW{(see \S 3.3.1 in \citet{1996astro.ph..6001N}).
+Figure \ref{fig:bestfitlensmodel} also shows the (smoothed) residuals from the F450W image subtracted by an IRAF \emph{ellipse} brightness model and the contours of the best fit model's time delay surface \NEW{(see \S 3.3.1 in \citealt{1996astro.ph..6001N}).
 Fermat's principle states that the image positions are observed at the extrema of the time delay surface.
@@
 Model fits to many sampled image positions lead to probability distributions for the best fit shape parameters and Einstein quantities; peak and standard deviations are given in the second column of Table \ref{tab:bestfitlensmodel}.
-We constrain the Einstein radius to within 2\%, $R_\text{ein} = (0.91 \pm 0.02)'' \hat{=}(1.83\pm0.04)~\text{kpc}$, and the projected mass within the critical curve with a relative error of 4\%, $M_\text{crit} =(7.9\pm0.3)\cdot 10^{10} M_\odot$.
+We constrain the Einstein radius to within 2\%, $R_\text{ein} = (0.91 \pm 0.02)'' \hat{=}(1.83\pm0.04)~\text{kpc}$, and the projected mass within the critical curve with a relative error of 4\%, $M_\text{crit} =(7.9\pm0.3) \OLD{\cdot}\NEW{\times} 10^{10} \text{M}_\odot$.
 Our measurement of $R_\text{ein}$ is consistent with that from \citet{SWELLSIII}, $R_\text{ein,SWELLS} = (0.96 \pm 0.04)''$ (which used a singular isothermal ellipsoid as lens mass model and the intermediate-axis convention of the critical curve as the Einstein radius).
-The relative difference between our critical mass and that of \citet{SWELLSIII}, $M_\text{crit,SWELLS} =(8.86\pm0.61)\cdot 10^{10} M_\odot$, is 13\%.
+The relative difference between our critical mass and that of \citet{SWELLSIII}, $M_\text{crit,SWELLS} =(8.86\pm0.61) \OLD{\cdot}\NEW{\times} 10^{10} \text{M}_\odot$, is 13\%.
 %--------------------------------------------
@@
 The red solid line corresponds to the lens model for a flat rotation curve ($\alpha = 1$) in Table \ref{tab:bestfitlensmodel}; the red dashed and dash-dotted lines are best fit lens models found analogously from the image positions, but for a fixed rotation curve slope of $\alpha = 1.1$ and $0.9$, respectively.
-For the JAM modelling best fit MGEs to the lens mass models were used, as well as the observed surface brightness MGE in Table \ref{tab:MGEF814W}, assuming velocity isotropy $\beta_z = 0$ and an inclination of $i = 70^\circ$.
+For the JAM modelling best fit MGEs to the lens mass models were used, as well as the observed surface brightness MGE in Table \ref{tab:MGEF814W}, assuming velocity isotropy $\beta_z = 0$ and an inclination of $\OLD{i}\NEW{inc} = 70^\circ$.
 The most reliable constraints are around the Einstein radius (vertical red dotted line); outside of it the model is just an extrapolation.}
@@
 
-We estimate the total mass-to-light ratio within the Einstein radius $\Upsilon_\text{I,tot}^\text{ein} \equiv M_\text{ein} / L_\text{I,ein}$.
-For this, we integrate the MGE in Table \ref{tab:MGEF814W} to get the total I-band luminosity within the Einstein radius $L_\text{I,ein} = 1.40\cdot 10^{10} L_\odot$.
+We estimate the total \NEW{(projected)} mass-to-light ratio within the Einstein radius $\Upsilon_\text{I,tot}^\text{ein} \equiv M_\text{ein} / L_\text{I,ein}$.
+For this, we integrate the MGE in Table \ref{tab:MGEF814W} to get the total I-band luminosity within the Einstein radius $L_\text{I,ein} = 1.40 \OLD{\cdot}\NEW{\times} 10^{10} L_\odot$.
 The corresponding Einstein mass-to-light ratio is therefore $\Upsilon_\text{I,tot}^\text{ein} = 5.56 \Upsilon_{I,\odot}$.
@@
 (iii) The light distribution drops faster than the mass with increasing radius (which is---at least partly---because of the assumption of a flat rotation curve).
-However, the mass distribution is only constrained around the Einstein radius and otherwise an extrapolation.
+However, the mass distribution is only constrained around the Einstein radius and otherwise \NEW{is} an extrapolation.
 %--------------------------------------------
@@
 We find slight covariances between $\Upsilon_\text{I,*}$,  $r_s$ and $\beta_z$: The smaller the DM contribution in the center (i.e., the larger $\Upsilon_\text{I,*}$), the less concentrated is the halo (i.e., the larger $r_s$) and the more velocity anisotropy is needed to reproduce the central $v_\text{rms}$ dip.
-As the effect of $v_{200}$ is mostly at larger radii, this parameter doesn't show any covariances, but is also mostly constrained by the prior.\\The MCMC samples are colour coded according to their probability (darker red for higher probability); the sample point with the highest probability is marked by a black diamond.
+As the effect of $v_{200}$ is mostly at larger radii, this parameter doesn't show any covariances, but is also mostly constrained by the prior.
+The MCMC samples are colour coded according to their probability (darker red for higher probability); the sample point with the highest probability is marked by a black diamond.
 The black cross is the mean of the distribution and the ellipses are derived from the covariance matrix of the MCMC samples and correspond approximately to $1\sigma$ (black solid ellipse) and $2\sigma$ (black dotted ellipse) confidence.
@@
 NFW halo concentration & $c_{200}$ & 8 & $\pm$ & 2 \\
-NFW halo mass & $M_{200}$ [$10^{12} M_\odot$] & 5 & $\pm$ & 2\\
+NFW halo mass & $M_{200}$ [$10^{12} \text{M}_\odot$] & 5 & $\pm$ & 2\\
 \hline
@@
 As velocity anisotropy alone cannot explain the observed kinematics in a simple mass-follows-light model, we now allow for a mass-to-light ratio gradient in the JAM modelling.
-We therefore generate a mass model from the light distribution in Table \ref{tab:MGEF814W} by assigning each of the five Gaussians in the MGE its own total mass-to-light ratio $\Upsilon_{\text{I,tot,}i}$ and replace the total luminosity in Equation \eqref{eq:centralItotalL} $L_i$ with the Gaussians total mass $M_i = \Upsilon_{\text{I,tot,}i} \cdot L_i$.
+We therefore generate a mass model from the light distribution in Table \ref{tab:MGEF814W} by assigning each of the five Gaussians in the MGE its own total mass-to-light ratio $\Upsilon_{\text{I,tot,}i}$ and replace the total luminosity in Equation \eqref{eq:centralItotalL} $L_i$ with the Gaussians total mass $M_i = \Upsilon_{\text{I,tot,}i} \OLD{\cdot}\NEW{\times} L_i$.
 We treat the five $\Upsilon_{\text{I,tot,}i}$ as free fit parameters and only require that $\Upsilon_{\text{I,tot,}j} \geq \Upsilon_{\text{I,tot,}i}$ when the corresponding $\sigma_j \geq \sigma_i$ to ensure that the overall mass-to-light ratio is increasing with radius.
@@
 
-\NEW{For the inner regions the model with rising $\Upsilon(R')$ seems however to be a very good model:} In Figure \ref{fig:enclMass_modelG} we overplot the enclosed mass profile with the Einstein mass $M_\text{ein} = (7.77 \pm 0.33) \cdot 10^{10} M_\odot$ at the Einstein radius found from lensing in Table \ref{tab:bestfitlensmodel}.
-The agreement between the Einstein mass and the independently found $M(<R_\text{ein}) = 7.49 \cdot 10^{10} M_\odot$ from dynamical modelling is striking.
+\NEW{For the inner regions the model with rising $\Upsilon(R')$ seems however to be a very good model:} In Figure \ref{fig:enclMass_modelG} we overplot the enclosed mass profile with the Einstein mass $M_\text{ein} = (7.77 \pm 0.33) \OLD{\cdot}\NEW{\times} 10^{10} \text{M}_\odot$ at the Einstein radius found from lensing in Table \ref{tab:bestfitlensmodel}.
+The agreement between the Einstein mass and the independently found $M(<R_\text{ein}) = 7.49 \OLD{\cdot}\NEW{\times} 10^{10} \text{M}_\odot$ from dynamical modelling is striking.
 %--------------------------------------------
@@
 stellar mass for late-type galaxies.
-Using the stellar mass estimate for J1331 from \citet{SWELLSI}, $m_* = (1.06 \pm 0.25) \cdot 10^{11} M_\odot$ (with generous error; see also Table \ref{tab:previousresults}) for the Chabrier IMF estimate, we find ${v_{200}} = (202_{-33}^{+44})_{-13}^{+12}$.
+Using the stellar mass estimate for J1331 from \citet{SWELLSI}, $m_* = (1.06 \pm 0.25) \OLD{\cdot}\NEW{\times} 10^{11} \text{M}_\odot$ (with generous error; see also Table \ref{tab:previousresults}) for the Chabrier IMF estimate, we find ${v_{200}} = (202_{-33}^{+44})_{-13}^{+12}$.
 The first error is due to the $2\sigma$ scatter in the relation by \citet{Dutton10}.
@@
 &p(\Upsilon_\text{I,*},r_s,v_{200},\beta_z) \\
-&= \frac{1}{\ln\left( 10 r_s\right)} p(\log c_{200} \mid v_{200}) \cdot p(v_{200}) \cdot p(\beta_z), 
+&= \frac{1}{\ln\left( 10 r_s\right)} p(\log c_{200} \mid v_{200}) \OLD{\cdot}\NEW{\times} p(v_{200}) \OLD{\cdot}\NEW{\times} p(\beta_z), 
 \end{split}
@@
 & & \multicolumn{2}{c}{Chabrier IMF} & \multicolumn{2}{c}{Salpeter IMF}\\
-      &  $L$ [$10^{10}L_{\odot}$]                & $M_*$ [$10^{10}M_\odot$]               & $\Upsilon_\text{I,*}^\text{chab}$ & $M_*$ [$10^{10}M_\odot$] & $\Upsilon_\text{I,*}^\text{sal}$ \\\hline
+      &  $L$ [$10^{10}L_{\odot}$]                & $M_*$ [$10^{10}\text{M}_\odot$]               & $\Upsilon_\text{I,*}^\text{chab}$ & $M_*$ [$10^{10}\text{M}_\odot$] & $\Upsilon_\text{I,*}^\text{sal}$ \\\hline
 bulge &   $3.10 \pm 0.15 $  & $7.8 \pm 1.8$ & $2.5 \pm 0.6$ & $14.5 \pm 3.7 $ & $4.7 \pm 1.2$ \\
@@
 Our assumptions for $\kappa(R)$ nicely reproduce a $v_\text{rot}$ model with counter-rotating core.
-Although we fitted $v_\text{rot}$ only to the inner regions, the extrapolation to large radii fits the data also very well.
+Although we fitted $v_\text{rot}$ only to the inner regions, the extrapolation to large radii \OLD{fits}\NEW{matches} the data also very well.
 
@@
 
-Traditional choices for the IMF are the bottom-heavy IMF by \citet{Salpeter1955},
-$$\xi(m) \propto m^{-x}, x=2.35,$$
-where $\xi(m) \diff m$ is the number of stars with mass $m$ in $[m,m+\diff m]$, and the IMFs by \citet{2002Sci...295...82K} and \citet{Chabrier2003}, which are in agreement with each other and predict less low-mass stars.
+Traditional choices for the IMF are the bottom-heavy IMF by \citet{Salpeter1955}, $\xi(m) \propto m^{-x}$ with $x=2.35$, where $\xi(m) \diff m$ is the number of stars with mass $m$ in $[m,m+\diff m]$, and the IMFs by \citet{2002Sci...295...82K} and \citet{Chabrier2003}, which are in agreement with each other and predict less low-mass stars.
 
@@
 Our best fit }\NEW{gave} $\Upsilon_\text{I,*} = 4.2 \pm 0.2$ \NEW{as best fit} (see Table \ref{tab:modelB4_bestfit})\NEW{, which} indicates a \emph{less} bottom-heavy IMF than the Salpeter IMF.
-\NEW{In Section \ref{sec:discussion_kinematics} we will argue why we do not think that the \cite{SWELLSV} model is a good model for the central regions of J1331.
-We therefore also do not believe their findings that the central IMF is more bottom-heavy than Salpeter.}
+\NEW{In Section \ref{sec:discussion_kinematics} we will argue why we do not think that the \cite{SWELLSV} model is a good model for the central regions of J1331.}
 %--------------------------------------------
@@
 
-\NEW{First, we will compare our modelling results with the modelling results by \citet{SWELLSV} within $R_\text{eff}$.}
-
-\NEW{\citet{SWELLSV} fitted a stellar mass model and NFW halo to (i) the Einstein mass and (ii) gas kinematics at larger radii $\gtrsim8''$.
+\NEW{First, we will compare our modelling results with the modelling results by \citet{SWELLSV} within $R_\text{eff}$.
+\citet{SWELLSV} fitted a stellar mass model and NFW halo to (i) the Einstein mass and (ii) gas kinematics at larger radii $\gtrsim8''$.
 } \OLD{In }Figure \ref{fig:vcirc_comparison} \OLD{we compare}\NEW{compares} the circular velocity curve found by \citet{SWELLSV} with a mass-follows-light model scaled to fit our Einstein mass (by multiplying the light distribution in Table \ref{tab:MGEF814W} by $\Upsilon_\text{I,tot}^\text{ein} = 5.56$, analogous to Figure \ref{fig:lenscomparelight}).
-Within $R < 5''$ they agree with each other.
+Within \OLD{$R < 5''$}\NEW{$0''.5 < R < 5''$} they agree with each other.
 
@@
 
-\NEW{The drop in $v_\text{rms}$ around $R'\sim4''$ (Figure \ref{fig:kinematics}) is most likely due to a sharp drop in $\Upsilon_{*}(R')$ at the transition from red bulge to blue disk (compare bulge size in Figures \ref{fig:F450W} and \ref{fig:F814W}).
-Unfortunately the spiral arms make the disk of the galaxy difficult to model.
-At these larger radii a possible misalignment of long-slit and galaxy's kinematic major axis---be it the result of a slightly faulty mode of observation or due to a kinematic twist caused by the merger---would also measure a lower $v_\text{rot}$, cause therefore a stronger underestimation of the true $v_\text{circ}$ and would add to the drop in $v_\text{rms}$.}
+\NEW{The drop in $v_\text{rms}$ around $R'\sim4''$ (Figure \ref{fig:kinematics}) is most likely due to the transition from bulge to disk (compare bulge size in Figures \ref{fig:F450W} and \ref{fig:F814W}).
+Non-circular motions due to the spiral arms and patchy star-forming regions are expected to strongly affect the measured kinematics.
+Also, a mix of different stellar populations in the disk could make the modelling difficult: The smooth light distribution was derived from the F814W filter and is therefore dominated by older stars, while the measured light-weighted stellar kinematics in the disk are dominated by luminous young stars with their lower velocity dispersion.
+As the merger could have caused a warp in J1331's disk, it is possible that bulge and disk have different inclination angles and a kinematic twist.
+The latter could have lead to a misalignment of the long-slit and the galaxy's kinematic major axis at larger radii, to measurements of lower $v_\text{rot}$ and therefore to a stronger underestimation of the true $v_\text{circ}$, which would add to the drop in $v_\text{rms}$.}
 
@@
 In our lensing approach we fitted a scale-free galaxy model to the lensing image position.
-This constrained the Einstein radius to within 2\% ($R_\text{ein}=(0.91\pm0.02)'' \hat{=}(1.83\pm0.04)~\text{kpc}$), and the Einstein mass to within 4\% ($M_\text{ein} = (7.8\pm0.3) \cdot 10^{10} M_\odot$), consistent with results by \citet{SWELLSIII}.\OLD{The recovered mass distribution agrees also very well with the shape of the observed lensing images.}
+This constrained the Einstein radius to within 2\% [$R_\text{ein}=(0.91\pm0.02)'' \hat{=}(1.83\pm0.04)~\text{kpc}$], and the Einstein mass to within 4\% ($M_\text{ein} = (7.8\pm0.3) \OLD{\cdot}\NEW{\times} 10^{10} \text{M}_\odot$), consistent with results by \citet{SWELLSIII}.\OLD{The recovered mass distribution agrees also very well with the shape of the observed lensing images.}
 
 \OLD{To get a handle on J1331's light distribution we used a MGE fit to J1331's surface brightness in the F814W filter in HST imaging by \citet{SWELLSI}.
-Based on this we found J1331's effective radius to be $R_\text{eff} \simeq 2.6'' \hat{=} 5.2~\text{kpc}$ and its total I-band luminosity to be $L_\text{I,tot} \simeq 5.6 \cdot 10^{10} L_\odot$.}\NEW{A MGE fit to J1331's surface brightness in the F814W filter in HST imaging by \citet{SWELLSI} helped us determining the effective radius, $R_\text{eff} \simeq 2.6'' \hat{=} 5.2~\text{kpc}$, and total I-band luminosity of the galaxy, $L_\text{I,tot} \simeq 5.6 \cdot 10^{10} L_\odot$.}
+Based on this we found J1331's effective radius to be $R_\text{eff} \simeq 2.6'' \hat{=} 5.2~\text{kpc}$ and its total I-band luminosity to be $L_\text{I,tot} \simeq 5.6 \OLD{\cdot}\NEW{\times} 10^{10} L_\odot$.}\NEW{A MGE fit to J1331's surface brightness in the F814W filter in HST imaging by \citet{SWELLSI} helped us determining the effective radius, $R_\text{eff} \simeq 2.6'' \hat{=} 5.2~\text{kpc}$, and total I-band luminosity of the galaxy, $L_\text{I,tot} \simeq 5.6 \OLD{\cdot}\NEW{\times} 10^{10} L_\odot$.}
 
@@
 We discussed that, to}\OLD{ To} describe the observed stellar kinematics\NEW{,} we \OLD{either}\NEW{most likely} require a \OLD{strong}\NEW{moderate} contribution of a DM halo already in the bulge, \NEW{moderate tangential velocity anisotropy, $\beta_z \simeq -0.4\pm0.1$, }\OLD{or} \NEW{and possibly even} a \OLD{strongly} varying stellar mass-to-light ratio\NEW{, which could be the result of the previous merger event}.
-\NEW{We argue that we expect the total stellar mass-to-light ratio within the bulge to be slightly less bottom-heavy than a Salpeter IMF, $\Upsilon_\text{I,*}\simeq 4.2\pm0.2$.} We also showed that it is possible to construct a model which includes the counter-rotating core and fits the rotation curve at large radii.
+\NEW{We argue that we expect the total stellar mass-to-light ratio within the bulge to be $\Upsilon_\text{I,*}\simeq 4.2\pm0.2$, which is slightly less bottom-heavy than a Salpeter IMF ($\Upsilon_\text{I,*}^\text{sal}\sim 4.7$).} We also showed that it is possible to construct a model which includes the counter-rotating core and fits the rotation curve at large radii.
 

### 2016-07-20 Answer_to_referee_report_LensingPaper.tex
Paper is re-submitted.

@@
 In 3.3.2 we refer stronger to the changes we made to Capellari's JAM code and kept the corresponding equations.
-In Section 3.3.4 we moved equations that are definitions and therefore needed inline to make it shorter; we kept the Maccio concentration vs.
-halo mass relation and explicitely mention that we will use this later as a prior in our modelling.
-In general we include a lot of equations and a big theory introduction because it is a paper that is potentially interesting for two communities, the lensing and the dynamics community.
+In Section 3.3.4 we moved equations that are definitions and therefore needed inline to make it shorter; we kept the concentration vs.
+halo mass relation (former equation 22) and explicitely mention that we will use this later as a prior in our modelling.
+In general we include a lot of equations and a substantial theory introduction because it is a paper that is potentially interesting for two communities, the lensing and the dynamics community.
 We wanted to make the paper understandable for both.}
@@
 In this region our MGE models also were not a good fit to the galaxy anymore.
-Considering also that there are other studies focussing on the outer regions and the counter-rotating core is the most interesting feature, we decided to focus our efforts on the inner regions and to try to explain the central kinematics only.
+Considering also that there are other studies focussing on the outer regions and the counter-rotating core is the most interesting feature, we decided to focus our efforts on the inner regions and try to explain the central kinematics only.
 We added however a small new section 4.4.4 that discusses that and why modelling attempts to the whole data range fail and what possible next modelling steps should be.}
@@
 We thought again about the different models and indications for different IMFs that we collected and came to the conclusion that an IMF slightly less bottom-beavy than the Salpeter IMF is the most likely model for J1331's bulge.
-We tried to give Section 5.1 (now 5.2) more structure and tweaked the discussion to present arguments for $\Upsilon_{I,*} \sim 4.2$ and and to argue against the alternative models.\\We also moved the section that discusses J1331's merger history to the beginning to the discussion section, focussed more on the what the merger could have done to J1331's mass distribution and less on modelling failures.
+We tried to give Section 5.2 (former 5.1) more structure and tweaked the discussion to present arguments for $\Upsilon_{I,*} \sim 4.2$ and and to argue against the alternative models.\\We also moved the section that discusses J1331's merger history to the beginning to the discussion section, focussed more on what the merger could have done to J1331's mass distribution and less on modelling failures.
 All following sections use the background information about mergers to discuss our models.\\Our scientific honesty is however, that without further data, we cannot be more commital and some of our statements have to stay in the "speculation regime".}
@@
 Also, some of the effects that mergers can have on galaxies \emph{could}, if they occured in J1331, actually explain some of the peculiar kinematic features of J1331.
-We tried to re-formulate section 5.2 (now 5.3) and discuss several aspects of the kinematics with respect to the merger history.}
+We tried to re-formulate section 5.3 (former 5.2) and discuss several aspects of the kinematics with respect to the merger history.}
 
@@
 the number of grammatical errors that remain.
-\Aaron{Aaron, could you have another look at the paper, specifically for grammar errors?
-Or should I try to find a student who is willing to read the paper?}
+\\\Comment{One of the authors is a native speaker and he had a look at the language again.
+We corrected everything he thought should be corrected.
+Hopefully it is fine now.}
 

### 2016-07-20 revised_version_(4.02)_16-07-20/Trick_J1331_Modelling_revised.tex
Paper is re-submitted.

--- 2016-07-19 LensingPaper_draft_v4.02.tex
@@
 
-\usepackage[usenames,dvipsnames]{xcolor}
-\newcommand{\Wilma}[1]{\textcolor{Magenta}{#1}}
-\newcommand{\Glenn}[1]{\textcolor{Green}{#1}}
-\newcommand{\Aaron}[1]{\textcolor{Blue}{#1}}
-
-\usepackage[usenames,dvipsnames]{xcolor}
-\newcommand{\NOTE}[1]{\textcolor{Cyan}{#1}}
-\newcommand{\NEW}[1]{\textcolor{ForestGreen}{#1}}
-%\newcommand{\OLD}[1]{\textcolor{Red}{#1}}
-\newcommand{\OLD}[1]{}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{abstract}
-We investigate the matter distribution of a spiral galaxy with \NEW{a} counter-rotating stellar core, SDSS J1331+3628 (J1331), independently with gravitational lensing and stellar dynamical modelling.
-By fitting a gravitational potential model to a quadruplet of lensing images around J1331's bulge, we tightly constrain the mass inside the Einstein radius $R_\text{ein}=(0.91\pm0.02)''(\simeq1.83\pm0.04~\text{kpc})$ to within 4\%: $M_\text{ein} = (7.8\pm0.3) \OLD{\cdot}\NEW{\times} 10^{10} \text{M}_\odot$.
+We investigate the matter distribution of a spiral galaxy with a counter-rotating stellar core, SDSS J1331+3628 (J1331), independently with gravitational lensing and stellar dynamical modelling.
+By fitting a gravitational potential model to a quadruplet of lensing images around J1331's bulge, we tightly constrain the mass inside the Einstein radius $R_\text{ein}=(0.91\pm0.02)''(\simeq1.83\pm0.04~\text{kpc})$ to within 4\%: $M_\text{ein} = (7.8\pm0.3) \times 10^{10} \text{M}_\odot$.
 We model observed long-slit major axis stellar kinematics in J1331's central regions by finding Multi-Gaussian Expansion (MGE) models for the stellar and dark matter distribution that solve the axisymmetric Jeans equations.
@@
 %--------------------------------------------
-\NEW{Determining the overall mass distribution of galaxies and separating the dark matter (DM) from the stellar mass components is a crucial step in better understanding the structure and formation of galaxies and the nature of DM.}
-
-\OLD{Gravitational lensing and dynamical modelling provide independent constraints on the mass distribution of galaxies.
-Combining them allows for valuable cross-checking opportunities to disentangle the galactic stellar and dark matter (DM) content.}
+Determining the overall mass distribution of galaxies and separating the dark matter (DM) from the stellar mass components is a crucial step in better understanding the structure and formation of galaxies and the nature of DM.
 
@@
 This discrepancy, known as the core-cusp problem, might be resolved by galaxy formation processes such as mergers and outflows (e.g., \citealt{2001ApJ...560..636E,2012MNRAS.421.3464P}).
-\NEW{Especially the influence of mergers on the DM and baryonic structure of galaxies is currently an active field of research (e.g., \citealt{2009ApJ...697L..38J,2010ApJ...712...88L,2012MNRAS.425.3119H,2015MNRAS.453.2447D}).}
-
-\OLD{Determining the overall mass distribution in massive galaxies and separating the DM from the stellar mass components is therefore a crucial step in better understanding the structure and formation of galaxies and nature of DM.}
-
-\NEW{The mass distribution of massive galaxies can be measured in completely independent fashions by gravitational lensing and dynamical modelling.
-Combining these two methods allows for valuable cross-checking opportunities to disentangle the galactic stellar and DM content.} Massive galaxies can act as gravitational lenses, deflect the light of background sources and give rise to multiple images.
+Especially the influence of mergers on the DM and baryonic structure of galaxies is currently an active field of research (e.g., \citealt{2009ApJ...697L..38J,2010ApJ...712...88L,2012MNRAS.425.3119H,2015MNRAS.453.2447D}).
+
+The mass distribution of massive galaxies can be measured in completely independent fashions by gravitational lensing and dynamical modelling.
+Combining these two methods allows for valuable cross-checking opportunities to disentangle the galactic stellar and DM content.
+Massive galaxies can act as gravitational lenses, deflect the light of background sources and give rise to multiple images.
 This strong gravitational lensing tightly constrains the projected total mass of the lens galaxy inside $\sim 1''$ (e.g., \citealt{2010ARA&A..48...87T}).
@@
 
-The Sloan WFC Edge-on Late-type Lens Survey (SWELLS, WFC = Wide field camera) \citep{SWELLSI,SWELLSII,SWELLSIII,SWELLSIV,SWELLSV,SWELLSVI} is dedicated to \OLD{find}\NEW{finding} and \OLD{investigate}\NEW{investigating} spiral galaxies, which are (i) strong gravitational lenses and (ii) observed almost edge-on, such that rotation curves can be easily measured.
+The Sloan WFC Edge-on Late-type Lens Survey (SWELLS, WFC = Wide field camera) \citep{SWELLSI,SWELLSII,SWELLSIII,SWELLSIV,SWELLSV,SWELLSVI} is dedicated to finding and investigating spiral galaxies, which are (i) strong gravitational lenses and (ii) observed almost edge-on, such that rotation curves can be easily measured.
 By combining lensing and dynamical modelling, degeneracies inherent in both methods can be broken.
@@
 
-\NEW{J1331 is therefore of special interest and a convenient candidate to investigate observationally if and how a merger might have modified the DM and stellar distribution of a massive spiral galaxy.
-This requires in particular a precise disentanglement of stellar and DM components in the galaxy's inner regions.}
-
-\NEW{J1331 has already been the subject of several studies:} \citet{SWELLSI} confirmed that J1331 is a strong gravitational lens, measured its apparent brightness and estimated the stellar masses of disk and bulge.
+J1331 is therefore of special interest and a convenient candidate to investigate observationally if and how a merger might have modified the DM and stellar distribution of a massive spiral galaxy.
+This requires in particular a precise disentanglement of stellar and DM components in the galaxy's inner regions.
+
+J1331 has already been the subject of several studies: \citet{SWELLSI} confirmed that J1331 is a strong gravitational lens, measured its apparent brightness and estimated the stellar masses of disk and bulge.
 The lensing properties of J1331 were first analysed by \citet{SWELLSIII}.
@@
 
-\OLD{The goal of this work is to complement the previous studies of J1331 by an in-depth analysis of the matter distribution in J1331's inner regions.}\NEW{The goal of this work is now the in-depth analysis of the matter distribution in J1331's inner regions.
-This will complement the previous studies of J1331 and is an important step in understanding J1331's merger-modified mass structure.} We use stellar dynamical modelling in addition to lensing constraints, similar to a study of the Einstein Cross by \citet{GlennEC}.
+The goal of this work is now the in-depth analysis of the matter distribution in J1331's inner regions.
+This will complement the previous studies of J1331 and is an important step in understanding J1331's merger-modified mass structure.
+We use stellar dynamical modelling in addition to lensing constraints, similar to a study of the Einstein Cross by \citet{GlennEC}.
 We attempt to disentangle the stellar and DM components and test if employed axisymmetric Jeans models work also in the presence of a counter-rotating core.
-\OLD{Ideally, this work on J1331 could also help understanding how mergers modify the mass distribution of a galaxy.}
 
@@
 J1331 is located at right ascension = 202.91800$^\circ$ and declination = 36.46999$^\circ$ (epoch J2000).
-\citet{SWELLSI} found from SDSS spectra that J1331 has two redshifts inside \NEW{the projected radius on the sky} $R'=1''$: J1331 itself has $z_d = 0.113$ and $z_s = 0.254$ is the redshift of the lensed background source \citep{SWELLSIII}.
+\citet{SWELLSI} found from SDSS spectra that J1331 has two redshifts inside the projected radius on the sky $R'=1''$: J1331 itself has $z_d = 0.113$ and $z_s = 0.254$ is the redshift of the lensed background source \citep{SWELLSIII}.
 According to the WMAP5 cosmology \citep{WMAP5cosm}, J1331 has an angular diameter distance of 414 Mpc, which translates into a transverse scaling of $1'' \hat{=} 2.01~\text{kpc}$.
-\NEW{We summarize all galaxy parameters also in Table \ref{tab:galaxyparameters}.}
+We summarize all galaxy parameters also in Table \ref{tab:galaxyparameters}.
 %--------------------------------------------
@@
 We use HST imaging of J1331 by \citet{SWELLSI}.
-They \OLD{performed}\NEW{obtained} high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) and its WF3 CCD chip.
+They obtained high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) and its WF3 CCD chip.
 The images are a combination of four exposures with each an exposure time of $400~\text{sec}$ and were drizzled to a pixel scale of 1 pixel = $0.05''$.
@@
 We subtract $2.3~\text{km s}^{-1}$ from $v_\text{rot}$ to ensure $v_\text{rot}(R'=0) \sim 0$ as a possible correction term for a misjudgement of the systemic velocity.
-We also symmetrize the data within $4''$ and asign a minimum error of $\delta v_\text{rms} \OLD{\geq}\NEW{=} 5~\text{km s}^{-1}$ to the $v_\text{rms}$ data.
+We also symmetrize the data within $4''$ and asign a minimum error of $\delta v_\text{rms} = 5~\text{km s}^{-1}$ to the $v_\text{rms}$ data.
 In our dynamical Jeans modelling approach, which is based on the assumption of axisymmetry, only stellar kinematics with either $R'  \lesssim 3.5''$ or $R' \lesssim 4''$ are used.
@@
 %--------------------------------------------
-$I(R',\theta')$ describes the intrinsic\OLD{, to} \NEW{and} 2D projected light distribution or surface density of the galaxy.
-Under the assumption that the galaxy is oblate and axisymmetric, and given the inclination angle $\OLD{i}\NEW{inc}$ of the galaxy with respect to the observer, MGEs allow an analytic deprojection of the 2-dimensional MGE to get a 3-dimensional axisymmetric light distribution or density $\nu(R,z)$ for the galaxy,
+$I(R',\theta')$ describes the intrinsic and 2D projected light distribution or surface density of the galaxy.
+Under the assumption that the galaxy is oblate and axisymmetric, and given the inclination angle $inc$ of the galaxy with respect to the observer, MGEs allow an analytic deprojection of the 2-dimensional MGE to get a 3-dimensional axisymmetric light distribution or density $\nu(R,z)$ for the galaxy,
 \begin{equation}
@@
 \end{equation}
-where $R$ is the distance from the galaxy's short axis and $z$ the height above the galactic plane.\footnote{\NEW{$(R,z)$ are cylindrical coordinates aligned with the galactic plane.
-The primed $(R',z')$ denote polar coordinates on the plane of the sky.}} The flattening $q_i$ of each axisymmetric 3D Gaussian and its central density $\nu_{0,i}$ follow from the observed 2D axis ratio $q'_i$ and surface density $I_{0,i}$ as
+where $R$ is the distance from the galaxy's short axis and $z$ the height above the galactic plane.\footnote{$(R,z)$ are cylindrical coordinates aligned with the galactic plane.
+The primed $(R',z')$ denote polar coordinates on the plane of the sky.} The flattening $q_i$ of each axisymmetric 3D Gaussian and its central density $\nu_{0,i}$ follow from the observed 2D axis ratio $q'_i$ and surface density $I_{0,i}$ as
 \begin{eqnarray}
-q_i^2 &=& \frac{q_i'^2 - \cos^2 \OLD{i}\NEW{(inc)}}{\sin^2 \OLD{i}\NEW{(inc)}}\\
+q_i^2 &=& \frac{q_i'^2 - \cos^2 (inc)}{\sin^2 (inc)}\\
 \nu_{0,i} &=& \frac{q_i' I_{0,i}}{q_i \sqrt{2 \pi \sigma_i^2}}.
@@
 \begin{equation}
-\psi(\vect{\theta}) \OLD{:=}\NEW{\equiv} \frac{D_\text{ds}}{D_\text{d} D_\text{s}} \frac{2}{c^2} \int \Phi(\vect{r}=D_\text{d} \vect{\theta},z') {\ \mathrm d} z', \label{eq:psidef}
+\psi(\vect{\theta}) \equiv \frac{D_\text{ds}}{D_\text{d} D_\text{s}} \frac{2}{c^2} \int \Phi(\vect{r}=D_\text{d} \vect{\theta},z') {\ \mathrm d} z', \label{eq:psidef}
 \end{equation}
@@
 
-\OLD{The total time delay of a deflected light path through $\vect{\theta}$ with respect to the unperturbed light path is given by 
-\begin{equation}
-\Delta t(\vect{\theta}) = \frac{(1+z_d)}{c} \frac{D_\text{d} D_\text{s}}{D_\text{ds}} \left[ \frac 12 (\vect{\theta} - \vect{\beta})^2 - \psi(\vect{\theta})\right]. \label{eq:timedelay}
-\end{equation}
- According to Fermat's principle the image positions will be observed at the extrema of $\Delta t(\vect{\theta})$.}
-
 The inverse magnification tensor
@@
 \end{equation}
-describes how the source position changes with image position\OLD{.
-It also describes}\NEW{,} the distortion of the image shape for an extended source and its magnification \OLD{$\mu$ due to lensing according to}\NEW{$\mu \equiv \text{image area}/\text{source area} = \det \mathscr{M}$}.
-\OLD{$$\mu \equiv \frac{\text{image area}}{\text{source area}} = \det \mathscr{M}.$$}
+describes how the source position changes with image position, the distortion of the image shape for an extended source and its magnification $\mu \equiv \text{image area}/\text{source area} = \det \mathscr{M}$.
 Lines in the image plane for which the magnification becomes infinite, i.e., $\det \mathscr{M}^{-1} = 0$, are called critical curves.
@@
 %--------------------------------------------
-\OLD{JAM modelling assumes galaxies to be (i) collisionless (i.e., the collisionless Boltzmann equation for the distribution function $f(\vect{x},\vect{v},t)$ has to be satisfied, $\frac{\diff f(\vect{x},\vect{v},t)}{\diff t} = 0$), (ii) in a steady state ($\frac{\partial}{\partial t} = 0$), (iii) axisymmetric (best described in cylindrical coordinates $(R,z,\phi)$ and $\frac{\partial}{\partial \phi} = 0$).
-From this follow the axisymmetric Jeans equations as the vector-valued first moment of the Boltzmann equation, i.e.,
-\begin{equation*}
-\int \vect{v} \frac{\diff f}{\diff t} \Diff3 v = 0.
-\end{equation*}}
-\NEW{JAM modelling assumes galaxies to be (i) collisionless, (ii) in a steady state and (iii) axisymmetric.
+JAM modelling assumes galaxies to be (i) collisionless, (ii) in a steady state and (iii) axisymmetric.
 With these assumptions the axisymmetric Jeans equations follow from the vector-valued first moment of the collisionless Boltzmann equation (see Equations (4.221)-(4.222) in \citet{2008gady.book.....B}).
-The Jeans equations are functions of the second velocity moments $\langle v_i v_j\rangle$ (with $i,j\in(R,z,\phi)$), the number density of (stellar) tracers $n(\vect{x})$, and the galaxy's gravitational potential $\Phi(\vect{x})$ generated by the mass density $\rho(\vect{x})$.}
+The Jeans equations are functions of the second velocity moments $\langle v_i v_j\rangle$ (with $i,j\in(R,z,\phi)$), the number density of (stellar) tracers $n(\vect{x})$, and the galaxy's gravitational potential $\Phi(\vect{x})$ generated by the mass density $\rho(\vect{x})$.
 
@@
 where $\beta_z$ is the velocity anisotropy parameter.
-\OLD{This reduces the Jeans equations to two equations for $\langle v_z^2 \rangle$ and $\langle v_\phi^2 \rangle$ which can be solved by means of one integration,
-\begin{eqnarray}
-n \langle v_z^2 \rangle (R,z) &=& \int_0^\infty n \frac{\partial \Phi}{\partial z} \diff z \label{eq:Jeans1}\\
-n \langle v_\phi^2 \rangle (R,z) &=& R \frac{\partial}{\partial R} \left( \frac{n \langle v_z^2 \rangle}{1-\beta_z} \right) + \frac{n \langle v_z^2 \rangle}{1 - \beta_z} + R n \frac{\partial \Phi}{\partial R},\label{eq:Jeans2}
-\end{eqnarray}
-where $n(\vect{x}) \equiv \int f(\vect{x},\vect{v}) \Diff3 v$ is the number density of (stellar) tracers and $\Phi(\vect{x})$ the galaxy's gravitational potential generated by the mass density $\rho(\vect{x})$.}
 
@@
 The MGE for $\Phi(R,z)$ is generated from the mass density MGE by integrating the Poisson equation \citep{1994A&A...285..723E}.
-\OLD{Equations \eqref{eq:Jeans1} and \eqref{eq:Jeans2} together with \eqref{eq:bz} provide the velocity dispersion tensor $\langle v_i v_j \rangle(R,z) = \langle v_i^2 \rangle(R,z)$ (with $i,j \in \{ R,\phi, z\}$ and $\langle v_i v_j \rangle=0$ if $i\neq j$).}
-
-\NEW{In this way one can now calculate an unambiguous model prediction for the velocity dispersion tensor $\langle v_i v_j \rangle(R,z) = \langle v_i^2 \rangle(R,z)$ (with $i,j \in \{ R,\phi, z\}$ and $\langle v_i v_j \rangle=0$ if $i\neq j$).
-To compare it with observations, $\langle v_i^2 \rangle(R,z)$ has to be}\OLD{$\langle v_i^2 \rangle$ is then} rotated by the inclination angle $\OLD{i}\NEW{inc}$ to the coordinate system of the observer; $(x',y')$ is the plane of the sky and $z'$ the line-of-sight, where $x'$ is alinged with the galaxy's major axis.
-Taking a light-weighted projection along the line-of-sight gives a model prediction for the line-of-sight velocity second moment \NEW{$\langle v_\text{los}^2\rangle(x',y')$}, which is comparable to actual spectroscopic measurements of the second velocity moment.
-Details of the derivation \NEW{of $\langle v_\text{los}^2\rangle(x',y')$ from the Jeans equations} using the MGE formalism are \OLD{given}\NEW{laid out} in \citet{Cap08} and in the appendix of \citet{GlennEC}.
-\OLD{We therefore just give the result for the line-of-sight second velocity moment prediction from the Jeans equations,}\NEW{The result for $\langle v_\text{los}^2\rangle(x',y')$ in particular is given in Equation (28) and Equation (A18), respectively.}
-\OLD{\begin{eqnarray}
-&&\left(I \langle v_\text{los}^2\rangle\right)(x',y')\nonumber\\
-&&= 4 \pi^{3/2} G \int_0^1 \sum_{i=1}^N \sum_{k=1}^M \nu_{0,i} \ q_k \ \rho_{0,k} \ u^2\nonumber\\
-&& \times \frac{\sigma_i^2 \ q^{2}_i \left( \cos^2 i + \frac{\sin^2 i}{1-\beta_{z,i}}\right) + \mathscr{D} \  {x'}^{2} \sin^2 i}{(1-\mathscr{C}u^2) \sqrt{(\mathscr{A} + \mathscr{B} \cos^2 i) \left[1-(1-q^{2}_k) u^2 \right]}}\nonumber\\
-&& \times \exp\left\{- \mathscr{A} \left[{x'}^{2} + \frac{(\mathscr{A}+\mathscr{B}) \ {y'}^{2}}{\mathscr{A}+\mathscr{B}\cos^2 i}\right] \right\} \diff u, \label{eq:explicitLOSvelCap}
-\end{eqnarray}
-with $N$ Gaussians describing the tracer distribution $\nu(R,z)$ and $M$ Gaussians describing the mass distribution $\rho(R,z)$, $\rho_{0,k}$ being the $k$-th mass density Gaussian evaluated at $(R=0,z=0)$ and
-\begin{eqnarray*}
-\mathscr{A} &=& \frac 12 \left(\frac{u^2}{\sigma_k^2} + \frac{1}{\sigma_i^2} \right)\nonumber\\
-\mathscr{B} &=& \frac 12 \left\{\frac{1-q^{2}_i}{\sigma_i^2 q^{2}_i} + \frac{(1-q^{2}_k)u^4}{\sigma_k^2 \left[1-(1-{q}_k^{2})u^2 \right]} \right\}\nonumber\\
-\mathscr{C} &=& 1- q^{2}_k - \frac{\sigma_i^2 q^{2}_i}{\sigma^2_k}\nonumber\\
-\mathscr{D} &=& 1 - \frac{q^{2}_i}{1-\beta_{z,i}} - \left[ \left(1-\frac{1}{1-\beta_{i,z}}\right)\mathscr{C} + \frac{1-q^{2}_k}{1-\beta_{z,i}}\right] u^2.\nonumber
-\end{eqnarray*}}
-
-The JAM modelling code by \citet{Cap08} evaluates \OLD{Equation \eqref{eq:explicitLOSvelCap}}\NEW{this expression for $\langle v_\text{los}^2\rangle(x',y')$} numerically for a given luminous tracer and mass distribution MGE and a given inclination.
+
+In this way one can now calculate an unambiguous model prediction for the velocity dispersion tensor $\langle v_i v_j \rangle(R,z) = \langle v_i^2 \rangle(R,z)$ (with $i,j \in \{ R,\phi, z\}$ and $\langle v_i v_j \rangle=0$ if $i\neq j$).
+To compare it with observations, $\langle v_i^2 \rangle(R,z)$ has to be rotated by the inclination angle $inc$ to the coordinate system of the observer; $(x',y')$ is the plane of the sky and $z'$ the line-of-sight, where $x'$ is alinged with the galaxy's major axis.
+Taking a light-weighted projection along the line-of-sight gives a model prediction for the line-of-sight velocity second moment $\langle v_\text{los}^2\rangle(x',y')$, which is comparable to actual spectroscopic measurements of the second velocity moment.
+Details of the derivation of $\langle v_\text{los}^2\rangle(x',y')$ from the Jeans equations using the MGE formalism are laid out in \citet{Cap08} and in the appendix of \citet{GlennEC}.
+The result for $\langle v_\text{los}^2\rangle(x',y')$ in particular is given in Equation (28) and Equation (A18), respectively.
+
+The JAM modelling code by \citet{Cap08} evaluates this expression for $\langle v_\text{los}^2\rangle(x',y')$ numerically for a given luminous tracer and mass distribution MGE and a given inclination.
 %--------------------------------------------
@@
 \end{equation}
-\OLD{The model in Equation \eqref{eq:explicitLOSvelCap}}\NEW{The model derived from the Jeans equations as outlined in Section \ref{sec:model_JAM_JAM}} predicts the intrinsic $\langle v_\text{los}^2 \rangle_\text{intr}\equiv\langle v_\text{los}^2\rangle$ at a given position on the sky, which needs then to be modified to $\langle v_\text{los}^2 \rangle_\text{obs}$ according to the mode of observation to be comparable to the measurements.
-The measured $v_\text{rms}$ \NEW{in this work} is a light-weighted mean for a pixel along the long-slit of the spectrograph, with width $L_y = 1''$ \citep{SWELLSV} and a certain given extent along the galaxy's major axis, $L_x$, i.e., for a rectangular aperture
+The model derived from the Jeans equations as outlined in Section \ref{sec:model_JAM_JAM} predicts the intrinsic $\langle v_\text{los}^2 \rangle_\text{intr}\equiv\langle v_\text{los}^2\rangle$ at a given position on the sky, which needs then to be modified to $\langle v_\text{los}^2 \rangle_\text{obs}$ according to the mode of observation to be comparable to the measurements.
+The measured $v_\text{rms}$ in this work is a light-weighted mean for a pixel along the long-slit of the spectrograph, with width $L_y = 1''$ \citep{SWELLSV} and a certain given extent along the galaxy's major axis, $L_x$, i.e., for a rectangular aperture
 \begin{equation}
@@
 \end{eqnarray}
-\NEW{We modified the JAM code by \citet{Cap08} to use this convolution kernel with non-square pixels.
-The JAM code then}\OLD{If provided with the convolution kernel, the JAM code\footnote{The IDL code package for Jeans Anisotropic Models (JAM) by \citet{Cap08} is available online at \url{http://www-astro.physics.ox.ac.uk/~mxc/software}.
-The version from June 2012 was used in this work.} by \citet{Cap08}} performs the convolution numerically.
+We modified the JAM code\footnote{The IDL code package for Jeans Anisotropic Models (JAM) by \citet{Cap08} is available online at \url{http://www-astro.physics.ox.ac.uk/~mxc/software}.
+The version from June 2012 was used in this work.} by \citet{Cap08} to use this convolution kernel with non-square pixels.
+The JAM code then performs the convolution numerically.
 We set $L_x = 0.21''$ as the width of the model pixel, and get a prediction for the actual measurements in bins of width $0.63''$, $1.26''$ and $1.89''$ \citep{SWELLSV} as light-weighted mean from each 3, 6 and 9 model pixels.
@@
 The intrinsic galaxy rotation curve is the first velocity moment $\langle v_\phi\rangle = \sqrt{\langle v_\phi^2 \rangle - \sigma_\phi^2}$.
-The observed rotation velocity is the projection of the light-weighted contributions to $\langle v_\phi\rangle$ along the line-of-sight \NEW{(Equation (31) in \citet{Cap08}).} \OLD{\citep{Cap08},
-\begin{equation*}
-I \langle v_\text{los}\rangle = \int_{-\infty}^{+\infty} \nu \langle v_\phi\rangle \cos \phi \sin \OLD{i}\NEW{inc} \diff z'.
-\end{equation*}}
+The observed rotation velocity is the projection of the light-weighted contributions to $\langle v_\phi\rangle$ along the line-of-sight (Equation (31) in \citet{Cap08}).
+
 The first velocity moments cannot be uniquely determined from the Jeans equations, which give only a prediction for the second velocity moments.
@@
 The sign of $\kappa$ determines the rotation direction.
-We can assign a constant $\kappa_i$ to every Gaussian in the MGE formalism and
-\OLD{\begin{equation*}
-\nu \langle v_\phi\rangle = \left[\nu \sum_{i=1}^N \kappa_i^2 \left( [\nu\langle v_\phi^2 \rangle]_i - [\nu\langle v_R^2 \rangle]_i\right) \right]^{1/2}
-\end{equation*} 
-is then}\NEW{calculate} the light-weighted circular velocity curve, given the second velocity moments found from the Jeans equations \NEW{(see Equations (37) and (38) in \citet{Cap08} for the intrinsic and observed rotation curves, respectively)}.
+We can assign a constant $\kappa_i$ to every Gaussian in the MGE formalism and calculate the light-weighted circular velocity curve, given the second velocity moments found from the Jeans equations (see Equations (37) and (38) in \citet{Cap08} for the intrinsic and observed rotation curves, respectively).
 
@@
 \begin{equation}
-\kappa(R) \OLD{=}\NEW{\equiv} \kappa' \frac{R^2 - R_0^2}{R^2 + R_0^2}. \label{eq:kappa_profile}
+\kappa(R) \equiv \kappa' \frac{R^2 - R_0^2}{R^2 + R_0^2}. \label{eq:kappa_profile}
 \end{equation}
@@
 and two free parameters, the scale length $r_s$ and a parameter describing the total mass of the halo.
-We will use $v_\text{200}\NEW{\equiv \sqrt{GM_{200}/r_{200}}}$, which is the circular velocity at the radius $r_\text{200}$ within which the mean density of the halo is 200 times the cosmological critical density $\rho_\text{crit} \equiv (2H^2)/(8\pi G)$, \OLD{i.e.,}\NEW{ and where $M_{200} \equiv M(<r_{200}) \stackrel{!}{=} \frac 43 \pi r_{200}^3 \times 200\rho_\text{crit}(z=0)$.}
-\OLD{\begin{eqnarray*}
-M_\text{200} &=& M(<r_{200})\\
-\frac{M_{200}}{ \frac 43 \pi r_{200}^3} &=& 200 \rho_\text{crit}(z=0) \\
-v_\text{200} &=& \sqrt{\frac{GM_{200}}{r_\text{200}}}
-\end{eqnarray*}}
-with $\rho_\text{crit}(z=0)=1.43 \OLD{\cdot}\NEW{\times} 10^{-7} \text{M}_\odot / \text{pc}^3$ in the WMAP5 cosmology by \citet{WMAP5cosm}.
-\OLD{How much the mass is concentrated in the center of the NFW halo is given by the concentration parameter
-\begin{equation}
-c_{200}\equiv r_{200} / r_s. \label{eq:NFW_c}
-\end{equation}}
-\NEW{The mass concentration of the NFW halo is quantified by $c_{200}\equiv r_{200} / r_s$.}
+We will use $v_\text{200}\equiv \sqrt{GM_{200}/r_{200}}$, which is the circular velocity at the radius $r_\text{200}$ within which the mean density of the halo is 200 times the cosmological critical density $\rho_\text{crit} \equiv (2H^2)/(8\pi G)$, and where $M_{200} \equiv M(<r_{200}) \stackrel{!}{=} \frac 43 \pi r_{200}^3 \times 200\rho_\text{crit}(z=0)$, with $\rho_\text{crit}(z=0)=1.43 \times 10^{-7} \text{M}_\odot / \text{pc}^3$ in the WMAP5 cosmology by \citet{WMAP5cosm}.
+The mass concentration of the NFW halo is quantified by $c_{200}\equiv r_{200} / r_s$.
 There is a close relation between the concentration and halo mass in simulations \citep{1996ApJ...462..563N}. \citet{Maccio08} found this relation for the WMAP5 cosmology to be
@@
 \end{equation}
-(their \OLD{e}\NEW{E}quation 10), with a Gaussian scatter of $\sigma_{\log c_{200}} = 0.105$ (their Table A2).
-\NEW{In Section \ref{sec:results_JAM_NFW} we will use this relation as prior information to guide the modelling towards realistic NFW halo shapes.}
+(their Equation 10), with a Gaussian scatter of $\sigma_{\log c_{200}} = 0.105$ (their Table A2).
+In Section \ref{sec:results_JAM_NFW} we will use this relation as prior information to guide the modelling towards realistic NFW halo shapes.
 %--------------------------------------------
@@
 average ellipticity & $\epsilon = 1 - q'$ & $0.402$ \\
-estimated inclination & $\OLD{i}\NEW{inc}$ [$^\circ$] & $70$\\
+estimated inclination & $inc$ [$^\circ$] & $70$\\
 apparent I-band magnitude & $m_\text{I}$ [mag] & $15.77$ \\
@@
 The orange lines indicate here contours of a smooth IRAF \emph{ellipse} fit to J1331 in the F814W filter; the grey lines are the corresponding best fit MGE.
-This MGE is not used for dynamical \OLD{modelling}\NEW{model fitting} because the dynamics in the outer regions are strongly affected by non-axisymmetries (e.g., spiral arms).
-We use it, however, to estimate the galaxy's total luminosity and effective radius, and to get \OLD{a prediction}\NEW{an estimate} for the dynamics of the outer regions.}
+This MGE is not used for dynamical model fitting because the dynamics in the outer regions are strongly affected by non-axisymmetries (e.g., spiral arms).
+We use it, however, to estimate the galaxy's total luminosity and effective radius, and to get an estimate for the dynamics of the outer regions.}
 \end{figure*}
@@
 \begin{equation}
-\mu_{I,0,i} \simeq -2.5 \log_{10}\left( \frac{C_{0,i}\text{[counts/pixel]}}{T[\text{sec}] \OLD{\cdot}\NEW{\times} S[''/\text{pixel width}]^2}\right) + Z + C + A_I, \label{eq:muI_}
+\mu_{I,0,i} \simeq -2.5 \log_{10}\left( \frac{C_{0,i}\text{[counts/pixel]}}{T[\text{sec}] \times S[''/\text{pixel width}]^2}\right) + Z + C + A_I, \label{eq:muI_}
 \end{equation}
@@
 The luminosity $L_i$[counts] and the corresponding surface brightness density $I_{0,i} [L_\odot \text{pc}^{-2}]$ of each Gaussian are given in Table \ref{fig:MGEinnerRegions}.
+%--------------------------------------------
+
+%--------------------------------------------
+\subsubsection{Inclination, total luminosity and effective radius}
+%--------------------------------------------
+
+%--------------------------------------------
+To estimate the inclination of J1331 with respect to the observer, we use the observed axis ratio of the flattest ellipse in the IRAF \emph{ellipse} model for J1331, which is $q'=0.42$.
+This is similar to the disk axis ratio of $q' = 0.40$ found by \citet{SWELLSI}.
+If a typical thickness of an oblate disk is around $q_0 \sim 0.2$ \citep{1958MeLu2.136....1H}, the inclination follows from
+\begin{equation}
+\cos^2 (inc) = \frac{q'^2 - q_0^2}{1 - q_0^2}
+\end{equation}
+and a correction of $+3^\circ$ \citep{1988ngc..book.....T}.
+Our estimate for the inclination is therefore $inc \approx 70^\circ$.
+Given this inclination, the 2-dimensional MGE models can be deprojected into three dimensions (see Section \ref{sec:MGE_theo_deprojection}).
+
+J1331's total I-band luminosity is determined by summing up the luminosity contributions of all the MGE Gaussians for the outer regions (shown as grey lines in Figure \ref{fig:MGEouterRegions}).
+We find $L_\text{I,tot} \simeq 5.6 \times 10^{10} ~L_\odot$.
+This corresponds to an apparent magnitude of $m_I = 15.77~\text{mag}$.
+We determine the circularized effective radius $R_\text{eff}$ of J1331 from the definition $L(<R_\text{eff}) \equiv \frac 12 L_\text{tot}$ and the growth curve $L(<R')$ from the MGE model of the outer regions, where $R'$ is the projected radius on the sky.
+We find the effective radius to be $R_\text{eff} \simeq 2.6'' \hat{=} 5.2~\text{kpc}$.
+All values are summarized in Table \ref{tab:galaxyparameters}.
 %--------------------------------------------
@@
 
-%--------------------------------------------
-\subsubsection{Inclination, total luminosity and effective radius}
-%--------------------------------------------
-
-%--------------------------------------------
-To estimate the inclination of J1331 with respect to the observer, we use the observed axis ratio of the flattest ellipse in the IRAF \emph{ellipse} model for J1331, which is $q'=0.42$.
-This is similar to the disk axis ratio of $q' = 0.40$ found by \citet{SWELLSI}.
-If a typical thickness of an oblate disk is around $q_0 \sim 0.2$ \citep{1958MeLu2.136....1H}, the inclination follows from
-\begin{equation}
-\cos^2 \OLD{i}\NEW{(inc)} = \frac{q'^2 - q_0^2}{1 - q_0^2}
-\end{equation}
-and a correction of $+3^\circ$ \citep{1988ngc..book.....T}.
-Our estimate for the inclination is therefore $\OLD{i}\NEW{inc} \approx 70^\circ$.
-Given this inclination, the 2-dimensional MGE models can be deprojected into three dimensions (see Section \ref{sec:MGE_theo_deprojection}).
-
-J1331's total I-band luminosity is determined by summing up the luminosity contributions of all the MGE Gaussians for the outer regions (shown as grey lines in Figure \ref{fig:MGEouterRegions}).
-We find $L_\text{I,tot} \simeq 5.6 \OLD{\cdot}\NEW{\times} 10^{10} ~L_\odot$.
-This corresponds to an apparent magnitude of $m_I = 15.77~\text{mag}$.
-We determine the circularized effective radius $R_\text{eff}$ of J1331 from the definition $L(<R_\text{eff}) \equiv \frac 12 L_\text{tot}$ and the growth curve $L(<R')$ from the MGE model of the outer regions, where $R'$ is the projected radius on the sky.
-We find the effective radius to be $R_\text{eff} \simeq 2.6'' \hat{=} 5.2~\text{kpc}$.
-All values are summarized in Table \ref{tab:galaxyparameters}.
-%--------------------------------------------
-
 %============================================
@@
 For $\alpha=1$ the critical curve is a contour of constant surface density of the mass model.
-The grey  lines show contours of the time delay surface given by Equation \OLD{\eqref{eq:timedelay}}\NEW{(63) in \citet{1996astro.ph..6001N}}.
+The grey  lines show contours of the time delay surface given by Equation (63) in \citet{1996astro.ph..6001N}.
 Not only the position of the extrema, but also their shape is consistent with the observed, extended images, even though we did not use information about the image shape in the analysis.}
@@
 The source is located close to a cusp of the diamond-shaped caustic: a lensing configuration for which we indeed expect four images.
-Figure \ref{fig:bestfitlensmodel} also shows the (smoothed) residuals from the F450W image subtracted by an IRAF \emph{ellipse} brightness model and the contours of the best fit model's time delay surface \NEW{(see \S 3.3.1 in \citealt{1996astro.ph..6001N}).
+Figure \ref{fig:bestfitlensmodel} also shows the (smoothed) residuals from the F450W image subtracted by an IRAF \emph{ellipse} brightness model and the contours of the best fit model's time delay surface (see \S 3.3.1 in \citealt{1996astro.ph..6001N}).
 Fermat's principle states that the image positions are observed at the extrema of the time delay surface.
-And even though}\OLD{.
-This demonstrates that, although} we did not include any information about the shape of the lensing images in the fit, it is consistent with the predicted distortion for an extended source.
+And even though we did not include any information about the shape of the lensing images in the fit, it is consistent with the predicted distortion for an extended source.
 
@@
 Model fits to many sampled image positions lead to probability distributions for the best fit shape parameters and Einstein quantities; peak and standard deviations are given in the second column of Table \ref{tab:bestfitlensmodel}.
-We constrain the Einstein radius to within 2\%, $R_\text{ein} = (0.91 \pm 0.02)'' \hat{=}(1.83\pm0.04)~\text{kpc}$, and the projected mass within the critical curve with a relative error of 4\%, $M_\text{crit} =(7.9\pm0.3) \OLD{\cdot}\NEW{\times} 10^{10} \text{M}_\odot$.
+We constrain the Einstein radius to within 2\%, $R_\text{ein} = (0.91 \pm 0.02)'' \hat{=}(1.83\pm0.04)~\text{kpc}$, and the projected mass within the critical curve with a relative error of 4\%, $M_\text{crit} =(7.9\pm0.3) \times 10^{10} \text{M}_\odot$.
 Our measurement of $R_\text{ein}$ is consistent with that from \citet{SWELLSIII}, $R_\text{ein,SWELLS} = (0.96 \pm 0.04)''$ (which used a singular isothermal ellipsoid as lens mass model and the intermediate-axis convention of the critical curve as the Einstein radius).
-The relative difference between our critical mass and that of \citet{SWELLSIII}, $M_\text{crit,SWELLS} =(8.86\pm0.61) \OLD{\cdot}\NEW{\times} 10^{10} \text{M}_\odot$, is 13\%.
+The relative difference between our critical mass and that of \citet{SWELLSIII}, $M_\text{crit,SWELLS} =(8.86\pm0.61) \times 10^{10} \text{M}_\odot$, is 13\%.
 %--------------------------------------------
@@
 The red solid line corresponds to the lens model for a flat rotation curve ($\alpha = 1$) in Table \ref{tab:bestfitlensmodel}; the red dashed and dash-dotted lines are best fit lens models found analogously from the image positions, but for a fixed rotation curve slope of $\alpha = 1.1$ and $0.9$, respectively.
-For the JAM modelling best fit MGEs to the lens mass models were used, as well as the observed surface brightness MGE in Table \ref{tab:MGEF814W}, assuming velocity isotropy $\beta_z = 0$ and an inclination of $\OLD{i}\NEW{inc} = 70^\circ$.
+For the JAM modelling best fit MGEs to the lens mass models were used, as well as the observed surface brightness MGE in Table \ref{tab:MGEF814W}, assuming velocity isotropy $\beta_z = 0$ and an inclination of $inc = 70^\circ$.
 The most reliable constraints are around the Einstein radius (vertical red dotted line); outside of it the model is just an extrapolation.}
@@
 
-We estimate the total \NEW{(projected)} mass-to-light ratio within the Einstein radius $\Upsilon_\text{I,tot}^\text{ein} \equiv M_\text{ein} / L_\text{I,ein}$.
-For this, we integrate the MGE in Table \ref{tab:MGEF814W} to get the total I-band luminosity within the Einstein radius $L_\text{I,ein} = 1.40 \OLD{\cdot}\NEW{\times} 10^{10} L_\odot$.
+We estimate the total (projected) mass-to-light ratio within the Einstein radius $\Upsilon_\text{I,tot}^\text{ein} \equiv M_\text{ein} / L_\text{I,ein}$.
+For this, we integrate the MGE in Table \ref{tab:MGEF814W} to get the total I-band luminosity within the Einstein radius $L_\text{I,ein} = 1.40 \times 10^{10} L_\odot$.
 The corresponding Einstein mass-to-light ratio is therefore $\Upsilon_\text{I,tot}^\text{ein} = 5.56 \Upsilon_{I,\odot}$.
@@
 (iii) The light distribution drops faster than the mass with increasing radius (which is---at least partly---because of the assumption of a flat rotation curve).
-However, the mass distribution is only constrained around the Einstein radius and otherwise \NEW{is} an extrapolation.
+However, the mass distribution is only constrained around the Einstein radius and otherwise is an extrapolation.
 %--------------------------------------------
@@
 %--------------------------------------------
-We make an independent prediction for the $v_\text{rms}$ curve by evaluating \OLD{Equation \eqref{eq:explicitLOSvelCap}}\NEW{the JAM equations} (with $\beta_z = 0$) for the lens mass model in Table \ref{tab:bestfitlensmodel} ($\alpha = 1$, flat rotation curve).
+We make an independent prediction for the $v_\text{rms}$ curve by evaluating the JAM equations (with $\beta_z = 0$) for the lens mass model in Table \ref{tab:bestfitlensmodel} ($\alpha = 1$, flat rotation curve).
 In addition, we also calculate a  $v_\text{rms}$ curve for two lens models which were found analogously, but assumed a slightly rising (falling) rotation curve slope of $\alpha=1.1$ ($\alpha=0.9$).
@@
 As velocity anisotropy alone cannot explain the observed kinematics in a simple mass-follows-light model, we now allow for a mass-to-light ratio gradient in the JAM modelling.
-We therefore generate a mass model from the light distribution in Table \ref{tab:MGEF814W} by assigning each of the five Gaussians in the MGE its own total mass-to-light ratio $\Upsilon_{\text{I,tot,}i}$ and replace the total luminosity in Equation \eqref{eq:centralItotalL} $L_i$ with the Gaussians total mass $M_i = \Upsilon_{\text{I,tot,}i} \OLD{\cdot}\NEW{\times} L_i$.
+We therefore generate a mass model from the light distribution in Table \ref{tab:MGEF814W} by assigning each of the five Gaussians in the MGE its own total mass-to-light ratio $\Upsilon_{\text{I,tot,}i}$ and replace the total luminosity in Equation \eqref{eq:centralItotalL} $L_i$ with the Gaussians total mass $M_i = \Upsilon_{\text{I,tot,}i} \times L_i$.
 We treat the five $\Upsilon_{\text{I,tot,}i}$ as free fit parameters and only require that $\Upsilon_{\text{I,tot,}j} \geq \Upsilon_{\text{I,tot,}i}$ when the corresponding $\sigma_j \geq \sigma_i$ to ensure that the overall mass-to-light ratio is increasing with radius.
@@
 A slight drop could be expected when the reddish bulge turns into the bluish disk and the contribution of the stellar component becomes less due to a lower $\Upsilon_\text{I,*}$ for younger and bluer populations.
-\NEW{Corresponding fitting attempts with the matter model at hand were however unsuccessful: Leaving all five $\Upsilon_{\text{I,tot,}i}$ free lead to over-fitting in the central regions of J1331, while not allowing for sufficient flexibility further out at $R'\gtrsim4''$ (because four of the five $\sigma_i$ in the light MGE in Table \ref{tab:MGEF814W} are $< 1.2''$) to properly model the transition from bulge to disk.}
-
-\NEW{For the inner regions the model with rising $\Upsilon(R')$ seems however to be a very good model:} In Figure \ref{fig:enclMass_modelG} we overplot the enclosed mass profile with the Einstein mass $M_\text{ein} = (7.77 \pm 0.33) \OLD{\cdot}\NEW{\times} 10^{10} \text{M}_\odot$ at the Einstein radius found from lensing in Table \ref{tab:bestfitlensmodel}.
-The agreement between the Einstein mass and the independently found $M(<R_\text{ein}) = 7.49 \OLD{\cdot}\NEW{\times} 10^{10} \text{M}_\odot$ from dynamical modelling is striking.
+Corresponding fitting attempts with the matter model at hand were however unsuccessful: Leaving all five $\Upsilon_{\text{I,tot,}i}$ free lead to over-fitting in the central regions of J1331, while not allowing for sufficient flexibility further out at $R'\gtrsim4''$ (because four of the five $\sigma_i$ in the light MGE in Table \ref{tab:MGEF814W} are $< 1.2''$) to properly model the transition from bulge to disk.
+
+For the inner regions the model with rising $\Upsilon(R')$ seems however to be a very good model: In Figure \ref{fig:enclMass_modelG} we overplot the enclosed mass profile with the Einstein mass $M_\text{ein} = (7.77 \pm 0.33) \times 10^{10} \text{M}_\odot$ at the Einstein radius found from lensing in Table \ref{tab:bestfitlensmodel}.
+The agreement between the Einstein mass and the independently found $M(<R_\text{ein}) = 7.49 \times 10^{10} \text{M}_\odot$ from dynamical modelling is striking.
 %--------------------------------------------
@@
 
-\NEW{As we are particularly interested in the disentanglement of DM and stellar matter in the inner regions (see Section \ref{sec:intro}), we restrict the $v_\text{rms}$ fit to a region $R'\lesssim3.5''$, approximately within the effective half-light radius $R_\text{eff}=2.6''$.
+As we are particularly interested in the disentanglement of DM and stellar matter in the inner regions (see Section \ref{sec:intro}), we restrict the $v_\text{rms}$ fit to a region $R'\lesssim3.5''$, approximately within the effective half-light radius $R_\text{eff}=2.6''$.
 The constraints on a DM halo just from this data might be weak.
-To guide the fit towards a realistic halo, we therefore impose several priors on NFW halo.}
+To guide the fit towards a realistic halo, we therefore impose several priors on NFW halo.
 
@@
 stellar mass for late-type galaxies.
-Using the stellar mass estimate for J1331 from \citet{SWELLSI}, $m_* = (1.06 \pm 0.25) \OLD{\cdot}\NEW{\times} 10^{11} \text{M}_\odot$ (with generous error; see also Table \ref{tab:previousresults}) for the Chabrier IMF estimate, we find ${v_{200}} = (202_{-33}^{+44})_{-13}^{+12}$.
+Using the stellar mass estimate for J1331 from \citet{SWELLSI}, $m_* = (1.06 \pm 0.25) \times 10^{11} \text{M}_\odot$ (with generous error; see also Table \ref{tab:previousresults}) for the Chabrier IMF estimate, we find ${v_{200}} = (202_{-33}^{+44})_{-13}^{+12}$.
 The first error is due to the $2\sigma$ scatter in the relation by \citet{Dutton10}.
@@
 &p(\Upsilon_\text{I,*},r_s,v_{200},\beta_z) \\
-&= \frac{1}{\ln\left( 10 r_s\right)} p(\log c_{200} \mid v_{200}) \OLD{\cdot}\NEW{\times} p(v_{200}) \OLD{\cdot}\NEW{\times} p(\beta_z), 
+&= \frac{1}{\ln\left( 10 r_s\right)} p(\log c_{200} \mid v_{200}) \times p(v_{200}) \times p(\beta_z), 
 \end{split}
@@
 
-\OLD{We restrict the $v_\text{rms}$ fit to a region $R' \lesssim 3.5''$, approximately within the effective half-light radius $R_\text{eff} = 2.6''$.
-}We also include the Einstein mass $M(<R_\text{ein})$ with a 10\% error as an additional constraint in the fit.
+We also include the Einstein mass $M(<R_\text{ein})$ with a 10\% error as an additional constraint in the fit.
 %--------------------------------------------
@@
 Our assumptions for $\kappa(R)$ nicely reproduce a $v_\text{rot}$ model with counter-rotating core.
-Although we fitted $v_\text{rot}$ only to the inner regions, the extrapolation to large radii \OLD{fits}\NEW{matches} the data also very well.
+Although we fitted $v_\text{rot}$ only to the inner regions, the extrapolation to large radii matches the data also very well.
 
@@
 
-\subsubsection{\NEW{Further tests and discussion}}
+\subsubsection{Further tests and discussion}
 
@@
 Overall, we were not able to obtain tight constraints on the cored logarithmic halo.
-\NOTE{[NOTE: this paragraph was moved from 4.4.2 to 4.4.4.]}
-
-\NEW{As we only fitted the halo models to the inner regions, it is not surprising that they do not fit the kinematics at larger radii.
+
+As we only fitted the halo models to the inner regions, it is not surprising that they do not fit the kinematics at larger radii.
 A fit to all nine available $v_\text{rms}$ data points would force the DM halo to be less massive.
@@
 Without further priors on the stellar $\Upsilon_\text{I,*}(R')$ or more data points, we can make only the following statement: A model with constant $\Upsilon_\text{I,*} = 4.2\pm 0.2$, moderately tangential $\beta_z = -0.4\pm 0.1$ and a spherical and massive DM component with high concentration ($c_\text{200}=8\pm 2$) can explain the central kinematics of J1331 very well.
-We have however ruled out that in this case the DM halo will follow a NFW halo profile at both small and large radii.}
-
-\NEW{We will also discuss the kinematics at larger radii in more depth in the discussion Section \ref{sec:discussion_kinematics}.}
+We have however ruled out that in this case the DM halo will follow a NFW halo profile at both small and large radii.
+
+We will also discuss the kinematics at larger radii in more depth in the discussion Section \ref{sec:discussion_kinematics}.
 
@@
 Some of them capture the observed kinematics, but none of them work at both small and large radii.
-\NEW{In the following we try to resolve some of the ambiguities by discussing possible reasons, by comparing our results to previous work and by hazarding some guesses on the true nature of J1331's matter distribution, which should be easily testable by future observations.}\OLD{In the following we discuss possible reasons, also by comparing our results to previous work.}
-%--------------------------------------------
-
-%--------------------------------------------
-\subsection{On J1331's possible merger history\OLD{ and modelling failures}} \label{sec:discussion_merger}
-%--------------------------------------------
-\NOTE{[This subsection was moved from a later position to the beginning of this section.]}
+In the following we try to resolve some of the ambiguities by discussing possible reasons, by comparing our results to previous work and by hazarding some guesses on the true nature of J1331's matter distribution, which should be easily testable by future observations.
+%--------------------------------------------
+
+%--------------------------------------------
+\subsection{On J1331's possible merger history} \label{sec:discussion_merger}
+%--------------------------------------------
 
@@
 Even though investigation of the photometry of J1331 did not reveal a distinct blue core in J1331, we cannot fully exclude the possibility that J1331 has such a $\Upsilon_*$ gradient (see discussion in Sections \ref{sec:results_JAM_SB_MfL} and \ref{sec:results_JAM_SB_gradient}).
-\NEW{Spatially resolved stellar population analysis based on integral-field spectroscopy of J1331's bulge could provide further information on the true $\Upsilon_*(R')$.}\OLD{In this case the restrictive assumption of a constant $\Upsilon_*$ in our JAM modelling could have lead to wrong conclusions about the DM distribution.}
+Spatially resolved stellar population analysis based on integral-field spectroscopy of J1331's bulge could provide further information on the true $\Upsilon_*(R')$.
 
@@
 
-From kinematics along the photometric major axis only it \OLD{cannot}\NEW{can however not} be determined if such a twist or misalignment is present in J1331\NEW{, but it should be immediately visible in a 2D kinematic map}.\OLD{ But if it were, our modelling assumption of axisymmetry would not be satisfied anymore.} \OLD{We note that kinematics measured along an axis different from the kinematic major axis would result in $v_\text{rot}$ measurements being lower than the actual maximum $v_\text{circ}$.
-At large radii this could lead to an underestimation of the DM halo mass.}
+From kinematics along the photometric major axis only it can however not be determined if such a twist or misalignment is present in J1331, but it should be immediately visible in a 2D kinematic map.
 %--------------------------------------------
@@
 
-\NEW{In the following we discuss why we think---based on our results and previous analyses---that J1331's bulge has an IMF slightly less bottom-heavy than the Salpeter-like IMF.}
-
-\NEW{\emph{(i) Indications for a slightly less bottom-heavy Salpeter-like IMF in J1331's bulge:}}
+In the following we discuss why we think---based on our results and previous analyses---that J1331's bulge has an IMF slightly less bottom-heavy than the Salpeter-like IMF.
+
+\emph{(i) Indications for a slightly less bottom-heavy Salpeter-like IMF in J1331's bulge:}
 
@@
 
-\NEW{\emph{(ii) Indications for and arguments against a Chabrier-like IMF in J1331's bulge:}}
+\emph{(ii) Indications for and arguments against a Chabrier-like IMF in J1331's bulge:}
 
 When \citet{SWELLSI} assumed a Chabrier IMF, their result translates to $\Upsilon_\text{I,*}^\text{chab} = 2.5 \pm 0.6$ (see Table \ref{tab:previousresults}).
-In Section \ref{sec:results_JAM_SB_gradient} we created a dynamical model from only the surface brightness distribution and an increasing mass-to-light ratio profile without additional DM halo \NEW{and without velocity anisotropy}.
+In Section \ref{sec:results_JAM_SB_gradient} we created a dynamical model from only the surface brightness distribution and an increasing mass-to-light ratio profile without additional DM halo and without velocity anisotropy.
 We found that such a model would be perfectly consistent with the Einstein mass, predict a total $\Upsilon_\text{I,tot}(R'\sim0) = 2.53$---being consistent with the Chabrier IMF estimate by \citet{SWELLSI}---and rise quickly to $\Upsilon_\text{I,tot}(R'\gtrsim R_\text{ein}) \gtrsim 6$.
 
-\NEW{This rise in $\Upsilon_\text{I,*}(R')$ could be either due to a cuspy DM halo (see Section \ref{sec:results_JAM_NFW}) or a very strong gradient in $\Upsilon_\text{I,*}$ (see Section \ref{sec:discussion_merger}).
+This rise in $\Upsilon_\text{I,*}(R')$ could be either due to a cuspy DM halo (see Section \ref{sec:results_JAM_NFW}) or a very strong gradient in $\Upsilon_\text{I,*}$ (see Section \ref{sec:discussion_merger}).
 However, we rule out that a DM cusp is the sole reason because a cuspy and therefore overall massive DM halo does not match the kinematics in J1331's outer regions.
@@
 And lastly---as laid out in the previous paragraph---J1331's central velocity dispersion suggests a more bottom-heavy IMF.
-Overall it is therefore not very likely that the central regions of J1331 have such a low $\Upsilon_\text{I,*}^\text{chab} \sim 2.5$.}
-
-\NEW{\emph{(iii) Arguments against an IMF more bottom-heavy than the Salpeter IMF in J1331's bulge:}}
+Overall it is therefore not very likely that the central regions of J1331 have such a low $\Upsilon_\text{I,*}^\text{chab} \sim 2.5$.
+
+\emph{(iii) Arguments against an IMF more bottom-heavy than the Salpeter IMF in J1331's bulge:}
 
 We also compare our results from Section \ref{sec:results_JAM_NFW} with the study by \citet{SWELLSV}.
-They found that the bulge of J1331 has an IMF \emph{more} bottom-heavy than the Salpeter IMF\OLD{ from fitting a NFW halo to (i) the Einstein mass and (ii) gas kinematics at larger radii $\gtrsim 8''$}.
-\NEW{Our fitting attempt---using more data within $\sim 3.5''$ than \citet{SWELLSV}---in}\OLD{ In} Section \ref{sec:results_JAM_NFW} \OLD{we fitted a mass model with NFW halo to (i) the Einstein mass and (ii) stellar kinematics within $\sim 3.5''$.
-Our best fit }\NEW{gave} $\Upsilon_\text{I,*} = 4.2 \pm 0.2$ \NEW{as best fit} (see Table \ref{tab:modelB4_bestfit})\NEW{, which} indicates a \emph{less} bottom-heavy IMF than the Salpeter IMF.
-\NEW{In Section \ref{sec:discussion_kinematics} we will argue why we do not think that the \cite{SWELLSV} model is a good model for the central regions of J1331.}
+They found that the bulge of J1331 has an IMF \emph{more} bottom-heavy than the Salpeter IMF.
+Our fitting attempt---using more data within $\sim 3.5''$ than \citet{SWELLSV}---in Section \ref{sec:results_JAM_NFW} gave $\Upsilon_\text{I,*} = 4.2 \pm 0.2$ as best fit (see Table \ref{tab:modelB4_bestfit}), which indicates a \emph{less} bottom-heavy IMF than the Salpeter IMF.
+In Section \ref{sec:discussion_kinematics} we will argue why we do not think that the \cite{SWELLSV} model is a good model for the central regions of J1331.
 %--------------------------------------------
@@
 %--------------------------------------------
-\subsection{On J1331's \OLD{central }kinematics} \label{sec:discussion_kinematics}
-%--------------------------------------------
-
-%--------------------------------------------
-\NEW{Overall, the kinematics of the merger remnant J1331 are peculiar.
+\subsection{On J1331's kinematics} \label{sec:discussion_kinematics}
+%--------------------------------------------
+
+%--------------------------------------------
+Overall, the kinematics of the merger remnant J1331 are peculiar.
 In particular there are two features in the $v_\text{rms}$ curve that are hard to explain with standard modelling techniques.
 The first feature, the deep central $v_\text{rms}$ dip, was studied in detail in this work.
-The second feature, the drop and rise in $v_\text{rms}$ around $R'\sim6''$, is even harder to explain; below we will speculate about possible reasons that could cause such a signature.}
-
-\NEW{\emph{(i) The central $v_\text{rms}$ dip within $R'\lesssim1''$:}}
-
-\NEW{First, we will compare our modelling results with the modelling results by \citet{SWELLSV} within $R_\text{eff}$.
+The second feature, the drop and rise in $v_\text{rms}$ around $R'\sim6''$, is even harder to explain; below we will speculate about possible reasons that could cause such a signature.
+
+\emph{(i) The central $v_\text{rms}$ dip within $R'\lesssim1''$:}
+
+First, we will compare our modelling results with the modelling results by \citet{SWELLSV} within $R_\text{eff}$.
 \citet{SWELLSV} fitted a stellar mass model and NFW halo to (i) the Einstein mass and (ii) gas kinematics at larger radii $\gtrsim8''$.
-} \OLD{In }Figure \ref{fig:vcirc_comparison} \OLD{we compare}\NEW{compares} the circular velocity curve found by \citet{SWELLSV} with a mass-follows-light model scaled to fit our Einstein mass (by multiplying the light distribution in Table \ref{tab:MGEF814W} by $\Upsilon_\text{I,tot}^\text{ein} = 5.56$, analogous to Figure \ref{fig:lenscomparelight}).
-Within \OLD{$R < 5''$}\NEW{$0''.5 < R < 5''$} they agree with each other.
+Figure \ref{fig:vcirc_comparison} compares the circular velocity curve found by \citet{SWELLSV} with a mass-follows-light model scaled to fit our Einstein mass (by multiplying the light distribution in Table \ref{tab:MGEF814W} by $\Upsilon_\text{I,tot}^\text{ein} = 5.56$, analogous to Figure \ref{fig:lenscomparelight}).
+Within $0''.5 < R < 5''$ they agree with each other.
 
@@
 
-\NEW{Because we used more data constraints in the center than \citet{SWELLSV}, we think that our model for J1331's bulge is more reliable.
-In conclusion we suspect that the most likely model for J1331's central bulge is a moderate DM contribution in the center (Section \ref{sec:results_JAM_NFW_results}) with some tangential anisotropy (Sections \ref{sec:results_JAM_SB_MfL} and \ref{sec:results_JAM_NFW}) and an overall $\Upsilon_\text{*,I}$ in the bulge which is slightly lower than that of a Salpeter-like IMF (Section \ref{sec:MLdiscussion}).
-Different stellar populations inside the bulge due to the merger (Section \ref{sec:discussion_merger}) with different $\Upsilon_{*}$ could add to an overall rising $\Upsilon_\text{tot}(R')$ profile (Sections \ref{sec:results_lensing_compare} and \ref{sec:results_JAM_SB_gradient}).}
-
-\OLD{Overall, we were not able to find a consistent explanation for J1331's central $v_\text{rms}$ dip.
-It cannot be due to tangential velocity anisotropy in the center alone (see Section \ref{sec:results_JAM_SB_MfL}, Figure \ref{fig:JAM_modelA2}).
-It also cannot be explained by a strong contribution of DM inside the bulge together with a moderate tagential velocity anisotropy, because the corresponding \NEW{NFW} DM halo\OLD{s} would still be too massive to fit the data in the outer regions (see Section \ref{sec:results_JAM_NFW}, Figure \ref{fig:modelB4_vrms}).}
-
-\OLD{Another feature in the stellar kinematics that none of our JAM models was able to reproduce in the slightest and which we therefore excluded in the modelling, was the dip in $v_\text{rms}$ around $\sim 6''$, which occurs around the transition from bulge to disk (see Figures \ref{fig:F814W} and \ref{fig:kinematics}).}
-
-%--------------------------------------------
-
-\NEW{\emph{(ii) The drop and rise of the $v_\text{rms}$ curve around $R'\sim 6''$:}}
-
-\NEW{The drop in $v_\text{rms}$ around $R'\sim4''$ (Figure \ref{fig:kinematics}) is most likely due to the transition from bulge to disk (compare bulge size in Figures \ref{fig:F450W} and \ref{fig:F814W}).
-Non-circular motions due to the spiral arms and patchy star-forming regions are expected to strongly affect the measured kinematics.
-Also, a mix of different stellar populations in the disk could make the modelling difficult: The smooth light distribution was derived from the F814W filter and is therefore dominated by older stars, while the measured light-weighted stellar kinematics in the disk are dominated by luminous young stars with their lower velocity dispersion.
+Because we used more data constraints in the center than \citet{SWELLSV}, we think that our model for J1331's bulge is more reliable.
+In conclusion we suspect that the most likely model for J1331's central bulge is a moderate DM contribution in the center (Section \ref{sec:results_JAM_NFW_results}) with some tangential anisotropy (Sections \ref{sec:results_JAM_SB_MfL} and \ref{sec:results_JAM_NFW}, which would be also consistent with the counter-rotation in the bulge) and an overall $\Upsilon_\text{*,I}$ in the bulge which is slightly lower than that of a Salpeter-like IMF (Section \ref{sec:MLdiscussion}).
+Different stellar populations inside the bulge due to the merger (Section \ref{sec:discussion_merger}) with different $\Upsilon_{*}$ could add to an overall rising $\Upsilon_\text{tot}(R')$ profile (Sections \ref{sec:results_lensing_compare} and \ref{sec:results_JAM_SB_gradient}).
+
+%--------------------------------------------
+
+\emph{(ii) The drop and rise of the $v_\text{rms}$ curve around $R'\sim 6''$:}
+
+The drop in $v_\text{rms}$ around $R'\sim4''$ (Figure \ref{fig:kinematics}) is most likely due to the transition from red bulge to blue disk (compare bulge size in Figures \ref{fig:F450W} and \ref{fig:F814W}).
+A mix of different stellar populations in the disk could make the modelling difficult: The smooth light distribution was derived from the F814W filter and is therefore dominated by older stars, while the measured light-weighted stellar kinematics in the disk are dominated by luminous young stars with their lower velocity dispersion.
 As the merger could have caused a warp in J1331's disk, it is possible that bulge and disk have different inclination angles and a kinematic twist.
-The latter could have lead to a misalignment of the long-slit and the galaxy's kinematic major axis at larger radii, to measurements of lower $v_\text{rot}$ and therefore to a stronger underestimation of the true $v_\text{circ}$, which would add to the drop in $v_\text{rms}$.}
-
-\NEW{Around $R'\sim7''$ the rotation curve and dispersion show some wiggles which lead to a spontaneous rise of the $v_\text{rms}$.
-As the spiral arms cross the major axis around this radius, we suspect they cause this disturbance of the axisymmetric kinematics.}
-
-\NEW{\emph{(iii) The profile of the DM halo at $R'\gtrsim 5''$:}}
-
-\NEW{The DM halo should start to dominate the kinematics at larger radii.
+The latter could have lead to a misalignment of the long-slit and the galaxy's kinematic major axis at larger radii, therefore to measurements of lower $v_\text{rot}$ and consequently to a stronger underestimation of the true $v_\text{circ}$, which would add to the drop in $v_\text{rms}$.
+
+Around $R'\sim7''$ the rotation curve and dispersion show some wiggles which lead to a spontaneous rise of the $v_\text{rms}$.
+As the spiral arms with their non-circular motions and patchy star-forming regions cross the major axis around this radius, we suspect they cause this disturbance of the axisymmetric kinematics.
+
+\emph{(iii) The profile of the DM halo at $R'\gtrsim 5''$:}
+
+The DM halo should start to dominate the kinematics at larger radii.
 \cite{SWELLSV}, who fitted a NFW halo to the gas kinematics in the outer regions, found lower halo masses ($v_\text{circ,halo}(5'') \sim 120~\text{km s}^{-1}$ according to their Figure 2) than we did ($v_\text{circ,halo}(5'') \sim 200~\text{km s}^{-1}$, Figure \ref{fig:vcirc_comparison}).
 As we did not fit the outer regions and only used a prior for $v_\text{200}$, their result in this regime is more reliable.
-Given our findings that a NFW halo does not fit the kinematics at both small and large radii, we suspect that the true halo has a profile that deviates strongly from a NFW halo.
-A more massive halo of NFW shape---as the one we found in this work---could however exist in J1331 if the galaxy had a strong kinematic twist in its disk due to the merger.}
-
-\NEW{All of these speculations should be easily testable with 2D kinematics.}
+Given our findings that a NFW halo does not fit the kinematics at both small and large radii, we suspect that the true halo has a profile that deviates strongly from a NFW halo, possibly as a result of the merger.
+
+All of these speculations should be easily testable with 2D kinematics.
 
@@
 %--------------------------------------------
-\OLD{Standard JAM modelling approaches seem not to work for J1331.
-The existing data---photometry and major axis kinematics---is however not sufficient to decide which of our model assumptions lead to the failure to find an overall consistent mass model.}
-\NEW{J1331's merging history and peculiar kinematics make it a valuable and exiting target to study merger remnants and a challenge for dynamical modelling techniques.
-We found however that the existing data alone---photometry and major axis kinematics---is not sufficient to resolve all the ambiguities we encountered in our modelling.}
-
-\OLD{2-dimensional stellar kinematics would greatly help to resolve this problem.
-}The main future work would be therefore getting high-resolution integral-field spectroscopy for J1331.
+J1331's merging history and peculiar kinematics make it a valuable and exiting target to study merger remnants and a challenge for dynamical modelling techniques.
+We found however that the existing data alone---photometry and major axis kinematics---is not sufficient to resolve all the ambiguities we encountered in our modelling.
+
+The main future work would be therefore getting high-resolution integral-field spectroscopy for J1331.
 High spatial resolution would be required to clearly identify J1331's presumably complex kinematic structure.
@@
 Is it possible that there even exists a kinematic twist due to the merger in J1331's past?
-\NEW{In the latter two cases we would need to apply non-axisymmetric Jeans models to J1331 as the assumption of axisymmetry of this work would not be valid anymore.}
+In the latter two cases we would need to apply non-axisymmetric Jeans models to J1331 as the assumption of axisymmetry of this work would not be valid anymore.
 
@@
 %--------------------------------------------
-\NEW{We constrained the matter distribution of the massive spiral galaxy J1331, which has a large counter-rotating core, probably due to a merger in its past, and acts as a strong gravitational lens for a background source.
-We used two independent methods to model J1331: gravitational lensing and dynamical Jeans modelling.}\OLD{The goal of this work was to constrain the matter distribution of the massive spiral galaxy J1331.
-J1331 is of special interest because it firstly has a large counter-rotating core and might therefore be a merger remnant and it secondly acts as strong gravitational lens for a background source.
-The latter allowed us to constrain the galaxy's mass from gravitational lensing.
-As second independent approach we used dynamical Jeans modelling to recover and disentangle the stellar and DM distribution.} We focussed on the bulge region of J1331 to complement previous studies of J1331 by \citet{SWELLSIII} and \citet{SWELLSV}.
-The \OLD{independent} mass constraints \OLD{which we derived} from lensing and dynamics agree very well with each other within $R_\text{eff}$.
+We constrained the matter distribution of the massive spiral galaxy J1331, which has a large counter-rotating core, probably due to a merger in its past, and acts as a strong gravitational lens for a background source.
+We used two independent methods to model J1331: gravitational lensing and dynamical Jeans modelling.
+We focussed on the bulge region of J1331 to complement previous studies of J1331 by \citet{SWELLSIII} and \citet{SWELLSV}.
+The mass constraints from lensing and dynamics agree very well with each other within $R_\text{eff}$.
 
 In our lensing approach we fitted a scale-free galaxy model to the lensing image position.
-This constrained the Einstein radius to within 2\% [$R_\text{ein}=(0.91\pm0.02)'' \hat{=}(1.83\pm0.04)~\text{kpc}$], and the Einstein mass to within 4\% ($M_\text{ein} = (7.8\pm0.3) \OLD{\cdot}\NEW{\times} 10^{10} \text{M}_\odot$), consistent with results by \citet{SWELLSIII}.\OLD{The recovered mass distribution agrees also very well with the shape of the observed lensing images.}
-
-\OLD{To get a handle on J1331's light distribution we used a MGE fit to J1331's surface brightness in the F814W filter in HST imaging by \citet{SWELLSI}.
-Based on this we found J1331's effective radius to be $R_\text{eff} \simeq 2.6'' \hat{=} 5.2~\text{kpc}$ and its total I-band luminosity to be $L_\text{I,tot} \simeq 5.6 \OLD{\cdot}\NEW{\times} 10^{10} L_\odot$.}\NEW{A MGE fit to J1331's surface brightness in the F814W filter in HST imaging by \citet{SWELLSI} helped us determining the effective radius, $R_\text{eff} \simeq 2.6'' \hat{=} 5.2~\text{kpc}$, and total I-band luminosity of the galaxy, $L_\text{I,tot} \simeq 5.6 \OLD{\cdot}\NEW{\times} 10^{10} L_\odot$.}
-
-\NEW{Axisymmetric JAM modelling allowed a comparison between model predictions for the second velocity moment given a tracer and mass distribution and the observed stellar kinematics from major axis long slit spectroscopy by \citet{SWELLSV}.} \OLD{We used axisymmetric JAM modelling to calculate the second velocity moment of a tracer and mass distribution given in terms of MGEs.} The \NEW{independent} JAM model of the lens mass model \OLD{gave an independent prediction which }was consistent with observed\OLD{ stellar} kinematics\OLD{ from major axis long slit spectroscopy by \citet{SWELLSV}} within $R_\text{eff}$.
+This constrained the Einstein radius to within 2\% [$R_\text{ein}=(0.91\pm0.02)'' \hat{=}(1.83\pm0.04)~\text{kpc}$], and the Einstein mass to within 4\% ($M_\text{ein} = (7.8\pm0.3) \times 10^{10} \text{M}_\odot$), consistent with results by \citet{SWELLSIII}.
+
+A MGE fit to J1331's surface brightness in the F814W filter in HST imaging by \citet{SWELLSI} helped us determining the effective radius, $R_\text{eff} \simeq 2.6'' \hat{=} 5.2~\text{kpc}$, and total I-band luminosity of the galaxy, $L_\text{I,tot} \simeq 5.6 \times 10^{10} L_\odot$.
+
+Axisymmetric JAM modelling allowed a comparison between model predictions for the second velocity moment given a tracer and mass distribution and the observed stellar kinematics from major axis long slit spectroscopy by \citet{SWELLSV}.
+The independent JAM model of the lens mass model was consistent with observed kinematics within $R_\text{eff}$.
 We also fitted mass models with and without NFW halo to the stellar kinematics within $R'=3.5~\text{kpc}$.
-From this we deduced that a mass-follows-light model \NEW{(even} with \OLD{constant total mass-to-light ratio and }velocity anisotropy\NEW{)} is not a good model for J1331\OLD{---not even in the}\NEW{'s} inner regions.
-\NEW{This ruled out the previous findings of \citet{SWELLSV} for J1331's bulge.
-We discussed that, to}\OLD{ To} describe the observed stellar kinematics\NEW{,} we \OLD{either}\NEW{most likely} require a \OLD{strong}\NEW{moderate} contribution of a DM halo already in the bulge, \NEW{moderate tangential velocity anisotropy, $\beta_z \simeq -0.4\pm0.1$, }\OLD{or} \NEW{and possibly even} a \OLD{strongly} varying stellar mass-to-light ratio\NEW{, which could be the result of the previous merger event}.
-\NEW{We argue that we expect the total stellar mass-to-light ratio within the bulge to be $\Upsilon_\text{I,*}\simeq 4.2\pm0.2$, which is slightly less bottom-heavy than a Salpeter IMF ($\Upsilon_\text{I,*}^\text{sal}\sim 4.7$).} We also showed that it is possible to construct a model which includes the counter-rotating core and fits the rotation curve at large radii.
-
-While both our independent mass models are consistent with each other within $\sim R_\text{eff}$, they do not \OLD{agree with previous findings by \citet{SWELLSV}, nor the}\NEW{describe the} data at large radii \NEW{very well}.
-\OLD{We attribute this to the fact that \citet{SWELLSV} derived mass constraints from kinematics in the outer regions only, while we focussed on the inner regions in detail.} We speculate \OLD{that}\NEW{how} a merger \OLD{might}\NEW{could} have modified the kinematic structure and/or mass distribution of J1331\OLD{ such that crucial model assumptions are not valid anymore}.
-To resolve the ambiguities in J1331's mass distribution 2-dimensional kinematic maps of J1331 from integral-field unit spectroscopy would be needed.
+From this we deduced that a mass-follows-light model (even with velocity anisotropy) is not a good model for J1331's inner regions.
+This ruled out the previous findings of \citet{SWELLSV} for J1331's bulge.
+We discussed that, to describe the observed stellar kinematics, we most likely require a moderate contribution of a DM halo already in the bulge, moderate tangential velocity anisotropy, $\beta_z \simeq -0.4\pm0.1$, and possibly even a varying stellar mass-to-light ratio, which could be the result of the previous merger event.
+We argue that we expect the total stellar mass-to-light ratio within the bulge to be $\Upsilon_\text{I,*}\simeq 4.2\pm0.2$, which is slightly less bottom-heavy than a Salpeter IMF ($\Upsilon_\text{I,*}^\text{sal}\sim 4.7$).
+We also showed that it is possible to construct a model which includes the counter-rotating core and fits the rotation curve at large radii.
+
+While both our independent mass models are consistent with each other within $\sim R_\text{eff}$, they do not describe the data at large radii very well.
+We speculate how a merger could have modified the kinematic structure and/or mass distribution of J1331.
+To resolve the ambiguities in J1331's mass distribution 2-dimensional kinematic maps of J1331 from integral-field unit spectroscopy are needed.
 %--------------------------------------------

### 2016-08-19 revised_version_(4.02)_16-07-20/Answer_to_the_referee.txt
Uploaded revised version.

--- 2016-07-20 Answer_to_referee_report_LensingPaper.tex
@@
-\documentclass[10pt,a4paper]{article}
-\usepackage[utf8]{inputenc}
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{amssymb}
-\usepackage{hyperref}	%for URLs
-\usepackage[usenames,dvipsnames]{xcolor}	%for color text
-\newcommand{\Comment}[1]{\textsl{\textcolor{Blue}{$\Longrightarrow$ {#1}}}}
-\newcommand{\RM}{{\sl RoadMapping}}
-
-\usepackage[usenames,dvipsnames]{xcolor}
-\newcommand{\Wilma}[1]{\textcolor{Magenta}{#1}}
-\newcommand{\Glenn}[1]{\textcolor{Green}{#1}}
-\newcommand{\Aaron}[1]{\textcolor{Orange}{#1}}
-
-\begin{document}
-\begin{flushright}
-Wilma H. Trick\\
-Max-Planck-Institut f\"{u}r Astronomie\\
-K\"{o}nigstuhl 17\\
-69117 Heidelberg, Germany
-\end{flushright}
-
-\noindent Anna Evripidou\\
-Assistant Editor\\
-"Monthly Notices" and "Geophysical Journal International"\\
-Royal Astronomical Society\\
-
-\begin{flushright}
-Heidelberg, 4th of July 2016
-\end{flushright}
-
-\textbf{Subject:} Answer to the Referee Report on "A spiral galaxy's mass distribution uncovered through lensing and dynamics"\\\\
-
 Dear Ms. Evripidou,
-
-Dear anonymous referee,\\
+Dear anonymous referee,
 
@@
 We made an effort to account for all the referee's comments and to make some of the sections a bit more understandable---we hope you agree.
-We attach the original letter and report below to which we added our answers to the referee's comments in blue and italics.
-\\\\
-Kind regards,\\
-Wilma Trick\\\\\\
+We attach the original referee report below to which we added our answers.
 
-\noindent\textbf{Attachments:}
-\begin{itemize}
-\item \texttt{Trick{\_}J1331{\_}Modelling{\_}revised.tex/.pdf} - revised paper file ready for publishing (without any marked text or annotations), if the referee agrees.
-\item \texttt{Trick{\_}J1331{\_}Modelling{\_}revised{\_}all{\_}changes.pdf} - file in which all changes with respect to the previous version of the paper are marked (new text = green, deleted text = red, annotations = blue).
-\item \texttt{Trick{\_}J1331{\_}Modelling{\_}revised{\_}for{\_}referee.pdf} - file for the referee with the deleted text excluded to be more readable (new text = green, annotations = blue).
-\end{itemize}
+Kind regards,
+Wilma Trick
 
-\newpage
-
-\noindent From:  	ae@ras.org.uk\\
-Subject:  	MNRAS: MN-16-0473-MJ\\
-Date:  	Mon, March 14, 2016 1:00 pm\\
-To:  	trick@mpia.de\\
-Cc:  	trick@mpia.de,glenn@mpia.de,dutton@nyu.edu\\\\
-
-Dear Ms Trick\\
-
-Copied below are the reviewer's comments on your manuscript entitled "A spiral
-galaxy's mass distribution uncovered through lensing and dynamics", ref.
-MN-16-0473-MJ, which you submitted to Monthly Notices of the Royal Astronomical
-Society.\\
-
-Minor revision of your manuscript is requested before it is reconsidered for
-publication.\\
-
-You should submit your revised version, together with your response to the
-reviewer's comments via the Monthly Notices ScholarOne Manuscripts site
-https://mc.manuscriptcentral.com/mnras.
-Enter your Author Centre, where you will find your manuscript title listed under
-"Manuscripts with Decisions." Under "Actions," click on "Create a Revision." Your
-manuscript reference will be appended to denote a revision.\\
-
-IMPORTANT: do not submit your revised manuscript as a new paper!\\
-
-You will not be able to make your revisions to the originally submitted files of the
-manuscript held on ScholarOne Manuscripts. Instead, you must delete the original
-files and abstract and replace them with your revised files. Check that any requests
-for colour publication or online-only publication are correct. Carefully proof read
-the resulting PDF and HTML files that are generated. If you have used a .bib file to
-generate your bibliography in Latex, please include this in your .tar archive along
-with the .bbl and .tex files; this will aid the editing and typesetting process.\\
-
-When submitting your revised manuscript, you will be able to respond to the comments
-made by the reviewer in the space provided. You should also use this space to
-document any changes you make to the original manuscript. In order to expedite the
-processing of the revised manuscript, please be as specific as possible in your
-response to the reviewer. Changes to the manuscript should be highlighted (e.g. in
-bold or colour), to assist the referee and editor. Along with the highlighted
-manuscript you should also upload clean files (remove any bold font/track changes)
-for our publishers, as accepted manuscripts are now immediately published online
-ahead of the proof-corrected version.\\
-
-Because we are trying to facilitate timely publication of manuscripts submitted to
-MNRAS, your revised manuscript should be uploaded promptly. If you do not submit
-your revision within six months, we may consider it withdrawn and request it be
-resubmitted as a new submission.\\
-
-Please note that, due to the tight schedule, any post-acceptance changes notified
-after the paper has gone into production (i.e. the day after the acceptance email is
-sent) cannot be incorporated into the paper before it is typeset. Such changes will
-therefore need to be made as part of the proof corrections. To avoid excessive proof
-corrections and the delay that these can cause, you are strongly encouraged to
-ensure that each version of your paper submitted to MNRAS is completely ready for
-publication!\\
-
-I look forward to receiving your revised manuscript.\\
-
-Regards,\\
-
-Anna\\
-
-\noindent Anna Evripidou\\
-Assistant Editor\\
-"Monthly Notices" and "Geophysical Journal International"\\
-Royal Astronomical Society\\
-Email: ae@ras.org.uk\\
-Tel: (+44) 0207 734 3307 Ext. 124 (except Wednesday)\\
-Tel: (+44) 0207 734 3307 Ext. 117 (Wednesday)\\
-
-This message is confidential and is intended solely for the use of the individual(s)
-to whom it is addressed.  If you have received this message in error, do not open
-any attachment but please notify the sender (above) and delete this message from
-your system.\\
-
-cc: all listed co-authors.\\
-
-\noindent Reviewer's Comments:\\
-Reviewer: 1\\
-
-Comments to the Author\\
+Attachments:
+Trick_J1331_Modelling_revised.tex/.pdf - revised paper file ready for publishing (without any marked text or annotations), if the referee agrees.
+Trick_J1331_Modelling_revised_all_changes.pdf - file in which all changes with respect to the previous version of the paper are marked (new text = green, deleted text = red, annotations = blue).
+Trick_J1331_Modelling_revised_for_referee.pdf - file for the referee with the deleted text excluded to be more readable (new text = green, annotations = blue).
 
 ====================================
-\begin{itemize}
 
-\item This is an interesting paper which makes neat use of the combination of stellar
+This is an interesting paper which makes neat use of the combination of stellar
 kinematics and strong lensing to investigate the mass structure of the spiral galaxy
-J1331. \\\Comment{Thanks. It is a very exiting galaxy that's definitely worth exploring.}
+J1331.
 
-\item The introduction could be re-written slightly to emphasise the points that the study
+--> ANSWER: Thanks. It is a very exiting galaxy that's definitely worth exploring.
+
+----------
+
+The introduction could be re-written slightly to emphasise the points that the study
 wants to investigate; for instance, the opening paragraph talks about the methods
@@
 probably be removed altogether, and the second paragraph promoted to the beginning.
-\\\Comment{That is a good point.
+
+--> ANSWER: That is a good point.
 We changed the opening paragraph to a general sentence why determining the matter distribution of galaxies is important.
-We mention the different methods now in the third paragraph.}
+We mention the different methods now in the third paragraph.
 
-\item It would also be nice to include some more discussion of the possibility of a recent
+----------
+
+It would also be nice to include some more discussion of the possibility of a recent
 merger in the galaxy's past in the introduction, as this is a really interesting
 feature of the galaxy in question and is also a very active topic of research.
-\\\Comment{Good point.
+
+--> ANSWER: Good point.
 1.) We added a sentence mentioning the important role of mergers in modifying the matter distribution and added some recent references.
 2.) We added a short paragraph later in the introduction that points out that J1331 is a special and very interesting galaxy for researching mergers.
-We also explain better that this merger is one of the reasons why we especially focus on the inner regions of J1331 in our study.}
+We also explain better that this merger is one of the reasons why we especially focus on the inner regions of J1331 in our study.
 
-\item The manuscript in its current form is also slightly longer than necessary at certain
+----------
+
+The manuscript in its current form is also slightly longer than necessary at certain
 points: for instance, in section 3.2.1, it is not really necessary to present all
@@
 necessary to include equation 22.
-\\\Comment{We made an effort to remove unnecessary equations in Section 3.2.1, tighten the explanation of the derivation of the Jeans equations in Section 3.3.1 and 3.3.3 and removed big and clumsy mathematical expressions by referring to the explicit equations in the literature instead.
+
+--> ANSWER: We made an effort to remove unnecessary equations in Section 3.2.1, tighten the explanation of the derivation of the Jeans equations in Section 3.3.1 and 3.3.3 and removed big and clumsy mathematical expressions by referring to the explicit equations in the literature instead.
 In 3.3.2 we refer stronger to the changes we made to Capellari's JAM code and kept the corresponding equations.
@@
 In general we include a lot of equations and a substantial theory introduction because it is a paper that is potentially interesting for two communities, the lensing and the dynamics community.
-We wanted to make the paper understandable for both.}
+We wanted to make the paper understandable for both.
 
-\item From a scientific perspective, in section 4.3.3, the authors comment that the
+----------
+
+From a scientific perspective, in section 4.3.3, the authors comment that the
 varying M/L JAM model is unable to reproduce the dynamics when M/L is forced to be
@@
 such a model to this section, or else comment on why they do not attempt it.
-\\\Comment{We have indeed tried a ``mass-follows-light'' JAM model with constant anisotropy and free M/L profile early on in our investigations of J1331.
+
+--> ANSWER: We have indeed tried a ``mass-follows-light'' JAM model with constant anisotropy and free M/L profile early on in our investigations of J1331.
 This was unsuccessful to a degree that showing the result in the paper would not be reasonable.
@@
 (We added a sentence mentioning that in the paper.) The resulting profile was very wiggly, difficult to interpret and most likely unphysical.
-As we lay out in the discussion, constraints on a varying stellar M/L ratio should be motivated by stellar population analysis in the future.}
+As we lay out in the discussion, constraints on a varying stellar M/L ratio should be motivated by stellar population analysis in the future.
 
-\item In section 4.4.1, the NFW profile is fitted only to the inner data, and then is
+----------
+
+In section 4.4.1, the NFW profile is fitted only to the inner data, and then is
 shown to not provide a good model for the data beyond that point. This is not
@@
 once? (Perhaps it is impossible to find a good NFW model across the whole radius
-range, but if this is the case, then it should be stated.) \\\Comment{Yes, you are completely right.
+range, but if this is the case, then it should be stated.)
+
+--> ANSWER: Yes, you are completely right.
 Our initial tests tried of course to fit the whole range of data, but failed.
@@
 Considering also that there are other studies focussing on the outer regions and the counter-rotating core is the most interesting feature, we decided to focus our efforts on the inner regions and try to explain the central kinematics only.
-We added however a small new section 4.4.4 that discusses that and why modelling attempts to the whole data range fail and what possible next modelling steps should be.}
+We added however a small new section 4.4.4 that discusses that and why modelling attempts to the whole data range fail and what possible next modelling steps should be.
 
-\item The discussion section is too non-committal and speculative in parts. For instance,
+----------
+
+The discussion section is too non-committal and speculative in parts. For instance,
 in section 5.1, the M/Ls inferred from a number of the different models are compared
@@
 framework, to try to come up with a better picture of the nature of J1331's IMF.
-\\\Comment{This is a valid point of criticism.
+
+--> ANSWER: This is a valid point of criticism.
 We thought again about the different models and indications for different IMFs that we collected and came to the conclusion that an IMF slightly less bottom-beavy than the Salpeter IMF is the most likely model for J1331's bulge.
-We tried to give Section 5.2 (former 5.1) more structure and tweaked the discussion to present arguments for $\Upsilon_{I,*} \sim 4.2$ and and to argue against the alternative models.\\We also moved the section that discusses J1331's merger history to the beginning to the discussion section, focussed more on what the merger could have done to J1331's mass distribution and less on modelling failures.
-All following sections use the background information about mergers to discuss our models.\\Our scientific honesty is however, that without further data, we cannot be more commital and some of our statements have to stay in the "speculation regime".}
+We tried to give Section 5.2 (former 5.1) more structure and tweaked the discussion to present arguments for $\Upsilon_{I,*} \sim 4.2$ and and to argue against the alternative models.
+We also moved the section that discusses J1331's merger history to the beginning to the discussion section, focussed more on what the merger could have done to J1331's mass distribution and less on modelling failures.
+All following sections use the background information about mergers to discuss our models.
+Our scientific honesty is however, that without further data, we cannot be more commital and some of our statements have to stay in the "speculation regime".
 
-\item In Section 5.2, the authors could make suggestions for what might be causing the two
+----------
+
+In Section 5.2, the authors could make suggestions for what might be causing the two
 $v_{rms}$ dips. Currently, they just state what cannot be the cause, but do not make any
@@
 suggestions like this could be put forward.
-\\\Comment{Good point.
+
+--> ANSWER: Good point.
 We admit that the text was formulated a bit too negative, and that we can do better in explaining J1331 based on our models than just ruling out things.
-Also, some of the effects that mergers can have on galaxies \emph{could}, if they occured in J1331, actually explain some of the peculiar kinematic features of J1331.
-We tried to re-formulate section 5.3 (former 5.2) and discuss several aspects of the kinematics with respect to the merger history.}
+Also, some of the effects that mergers can have on galaxies could, if they occured in J1331, actually explain some of the peculiar kinematic features of J1331.
+We tried to re-formulate section 5.3 (former 5.2) and discuss several aspects of the kinematics with respect to the merger history.
 
-\item While the use of English is impressive given that it is not the main author's mother
+----------
+
+While the use of English is impressive given that it is not the main author's mother
 tongue, I would also recommend giving the manuscript to a native speaker to correct
 the number of grammatical errors that remain.
-\\\Comment{One of the authors is a native speaker and he had a look at the language again.
-We corrected everything he thought should be corrected.
-Hopefully it is fine now.}
 
-\end{itemize}
-
-\end{document}
+--> ANSWER: One of the authors is a native speaker and he had a look at the language again. We corrected everything he thought should be corrected. Hopefully it is fine now.

### 2016-09-18 LensingPaper_draft_v4.03.tex
Started version to be uploaded to arXiv

--- 2016-07-20 revised_version_(4.02)_16-07-20/Trick_J1331_Modelling_revised.tex
@@
 
-\title[A spiral galaxy's mass distribution uncovered]{A spiral galaxy's mass distribution uncovered through lensing and dynamics}
-\author[W.H. Trick, G. van de Ven and A.A. Dutton]{Wilma H. Trick$^{1}$\thanks{E-mail: trick@mpia.de}, Glenn van de Ven$^{1}$ and Aaron A. Dutton$^{1,2}$\\
+\title[Galaxy mass distribution via lensing \& dynamics]{A spiral galaxy's mass distribution uncovered through lensing and dynamics}
+\author[W.H. Trick, G. van de Ven, and A.A. Dutton]{Wilma H. Trick$^{1}$\thanks{E-mail: trick@mpia.de}, Glenn van de Ven$^{1}$ and Aaron A. Dutton$^{1,2}$\\
 $^{1}$Max-Planck-Institute for Astronomy, K\"{o}nigstuhl 17, 69117 Heidelberg, Germany\\
@@
 %--------------------------------------------
+\subsection{Strong gravitational lens model} \label{sec:lensing_theo}
+%--------------------------------------------
+
+%--------------------------------------------
+\subsubsection{Strong lensing formalism}
+%--------------------------------------------
+
+%--------------------------------------------
+A gravitational lens is a mass distribution whose gravitational potential $\Phi$ acts as a lens for light coming from a source positioned somewhere on a plane behind the lens.
+We summarize the basic formalism (see also \citealt{1992grle.book.....S,1996astro.ph..6001N,2006glsw.conf....1S,2006glsw.conf...91K,2010ARA&A..48...87T}).
+The angular diameter distance from the observer to the lens is $D_\text{d}$, to the source plane $D_\text{s}$, and the distance between the lens and source plane is $D_\text{ds}$.
+The deflection potential of the lens is its potential projected along the line of sight $z'$ and rescaled to
+\begin{equation}
+\psi(\vect{\theta}) \equiv \frac{D_\text{ds}}{D_\text{d} D_\text{s}} \frac{2}{c^2} \int \Phi(\vect{r}=D_\text{d} \vect{\theta},z') {\ \mathrm d} z', \label{eq:psidef}
+\end{equation}
+where $\vect{\theta}\equiv(x',y')$ is a 2-dimensional vector on the plane of the sky. The light from the source at $\vect{\beta} \equiv (x_s',y_s')$ is deflected according to the lens equation
+\begin{equation}
+\vect{\beta} = \vect{\theta}_i - \left.\vect{\nabla}_\theta \psi(\vect{\theta})\right|_{\vect{\theta}_i} \label{eq:lenseqpot}
+\end{equation}
+into an image $\vect{\theta}_i = (x_i',y_i')$.
+The gradient of the deflection potential, $\vect{\nabla}_\theta \psi(\vect{\theta})$, is equal to the angle by which the light is deflected multiplied by $D_\text{ds}/D_\text{s}$.
+
+The inverse magnification tensor
+\begin{equation}
+\mathscr{M}^{-1} \equiv \frac{\partial \vect{\beta}}{\partial \vect{\theta}} \overset{(\ref{eq:lenseqpot})}{=} \left(\delta_{ij} - \frac{\partial^2 \psi}{\partial \theta_i \partial \theta_j} \right)\label{eq:magnificationtensor}
+\end{equation}
+describes how the source position changes with image position, the distortion of the image shape for an extended source and its magnification $\mu \equiv \text{image area}/\text{source area} = \det \mathscr{M}$.
+Lines in the image plane for which the magnification becomes infinite, i.e., $\det \mathscr{M}^{-1} = 0$, are called critical curves.
+The corresponding lines in the source plane are called caustics.
+The position of the source with respect to the caustic detemines the number of images and their configuration and shape with respect to each other.
+
+The Einstein mass $M_\text{ein}$ and Einstein radius $R_\text{ein}$ are defined via the relation
+\begin{equation}
+M_\text{ein} \equiv M(<R_\text{ein}) \overset{!}{=} \pi \Sigma_\text{crit} R_\text{ein}^2,
+\end{equation}
+where 
+\begin{equation}
+\Sigma_\text{crit} \equiv \frac{c^2}{4\pi G} \frac{D_\text{s}}{D_\text{d} D_\text{ds}}
+\end{equation}
+is the critical density and $M(<R_\text{ein})$ is the mass projected along the line-of-sight within $R'=R_\text{ein}$.
+$M_\text{ein}$ is similar to the projected mass within the critical curve $M_\text{crit}$.
+%--------------------------------------------
+
+%--------------------------------------------
+\subsubsection{Lens model} 
+%--------------------------------------------
+
+%--------------------------------------------
+Following \citet{EvansWitt} we assume a scale-free model
+\begin{equation}
+\psi(R',\theta') = R^{'\alpha} F(\theta') \label{eq:scalefreemodel}
+\end{equation}
+for the lensing potential, consisting of an angular part $F(\theta')$ and a radial power-law part, with $(R',\theta')$ being again polar coordinates on the plane of the sky.
+$\alpha$ denotes the rotation curve slope of the lens and the case $\alpha = 1$ corresponds to a flat rotation curve.
+The surface density of this model is
+\begin{equation*}
+\Sigma(R',\theta')= \frac{ \Sigma_\text{crit}}{2} \left(\alpha^2 F(\theta') + \frac{\partial^2}{\partial \theta^{'2}}F(\theta')\right) R^{'\alpha-2}.
+\end{equation*}
+We expand $F(\theta')$ into a Fourier series,
+\begin{equation}
+F(\theta') = \frac{a_0}{2} + \sum_{k=1}^{\infty} \left(a_k \cos(k\theta') + b_k \sin (k\theta') \right). \label{eq:Fourieransatz}
+\end{equation}
+For this scale-free lens model the lens equation \eqref{eq:lenseqpot} becomes
+\begin{equation}
+\begin{pmatrix} x_s' \\ y_s' \end{pmatrix} = \begin{pmatrix} R'_i \cos \theta'_i - R_i^{'\alpha-1} \left(\alpha \cos \theta'_i F(\theta'_i) - \sin \theta'_i F'(\theta'_i) \right) \\ R'_i \sin \theta'_i - R_i^{'\alpha-1} \left(\alpha \sin \theta'_i F(\theta'_i + \cos \theta'_i F'(\theta'_i) \right)\end{pmatrix}\label{eq:Fourierlenseq}
+\end{equation}
+\citep{EvansWitt}, where $F'(\theta') \equiv \partial F(\theta') / \partial \theta'$.
+When we fix the slope $\alpha$, then the lens equation is a purely linear problem and can be solved numerically for the source position $(x_s',y_s')$ and the Fourier parameters $(a_k,b_k)$ given one observed image at position $(x'_i=R'_i \cos \theta'_i,y'_i=R'_i \sin \theta'_i)$.
+%--------------------------------------------
+
+%--------------------------------------------
+\subsubsection{Model fitting}
+%--------------------------------------------
+
+%--------------------------------------------
+The free parameters of the lens model are: the source position $(x_s',y_s')$, the radial slope $\alpha$ and Fourier parameters $(a_k,b_k)$ of the lens mass distribution in Equations \eqref{eq:scalefreemodel}-\eqref{eq:Fourieransatz}.
+We want to minimize the distance between the observed image positions, $\vect{\theta}_{oi}$, and those predicted by the lensing model, $\vect{\theta}_{pi}$.
+To avoid having to solve the lens equation \eqref{eq:Fourierlenseq} for $\vect{\theta}_{pi}$, we follow \citet{1991ApJ...373..354K} and cast the calculation back to the source plane using the magnification tensor in Equation \eqref{eq:magnificationtensor} to approximate $\vect{\theta} \simeq (\partial \vect{\theta} / \partial \vect{\beta}) \vect{\beta} = \mathscr{M} \vect{\beta} $.
+The best fit lens model is then the one that minimizes
+\begin{align}
+\begin{split}
+\chi^2_\text{lens} &= \sum_{i} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right) \left( \vect{\theta}_{pi} - \vect{\theta}_{oi} \right)\right|^2\label{eq:chi2lens}\\
+&\simeq \sum_{i} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right)  \left.\mathscr{M}\right|_{\vect{\theta}=\vect{\theta}_{oi}} \left( \begin{matrix} x_s' - \tilde{x}'_{si} \\ y_s' - \tilde{y}'_{si} \end{matrix} \right) \right|^2,
+\end{split}
+\end{align}
+where $(\Delta_x,\Delta_y)$ are the measurement errors of the image positions $\vect{\theta}_{oi}$.
+$\left.\mathscr{M}\right|_{\vect{\theta}=\vect{\theta}_{oi}}$ is the magnification tensor and $(\tilde{x}'_{si},\tilde{y}'_{si})$ the source position according to the lens equation, both evaluated at the position of the $i$-th lensing image, $\vect{\theta}_{oi}$.
+Following \citet{GlennEC} we add a term
+\begin{equation}
+\chi^2_\text{shape} = \lambda \sum_{k \geq 3} \frac{\left(a_k^2 +b_k^2 \right)}{a_0^2} \label{eq:chi2shape}
+\end{equation}
+(with $\lambda$ being some weight factor) which forces the shape of the mass distribution to be close to an ellipse. The total $\chi^2$ to minimize is therefore
+\begin{equation}
+\chi^2 = \chi^2_\text{lens} + \chi^2_\text{shape} \label{eq:chi2total}
+\end{equation}
+We set $a_1 = b_1 = 0$, which corresponds to the choice of origin; in this case the center of the galaxy.
+
+To be able to constrain the slope $\alpha$ we would need flux ratios for the images as in \citet{GlennEC}.
+But the extent of the images, possible dust obscuration and surface brightness fluctuations due to microlensing events, as well as the uncertainty in surface brightness subtraction, make flux determination too unreliable and we do not include them in the fitting.
+%--------------------------------------------
+
+%--------------------------------------------
 \subsection{Surface brightness model} \label{sec:MGE_theo}
@@
 $I(R',\theta')$ describes the intrinsic and 2D projected light distribution or surface density of the galaxy.
-Under the assumption that the galaxy is oblate and axisymmetric, and given the inclination angle $inc$ of the galaxy with respect to the observer, MGEs allow an analytic deprojection of the 2-dimensional MGE to get a 3-dimensional axisymmetric light distribution or density $\nu(R,z)$ for the galaxy,
+Under the assumption that the galaxy is oblate and axisymmetric, and given the inclination angle $\iota$ of the galaxy with respect to the observer, MGEs allow an analytic deprojection of the 2-dimensional MGE to get a 3-dimensional axisymmetric light distribution or density $\nu(R,z)$ for the galaxy,
 \begin{equation}
@@
 \begin{eqnarray}
-q_i^2 &=& \frac{q_i'^2 - \cos^2 (inc)}{\sin^2 (inc)}\\
+q_i^2 &=& \frac{q_i'^2 - \cos^2 \iota}{\sin^2 \iota}\\
 \nu_{0,i} &=& \frac{q_i' I_{0,i}}{q_i \sqrt{2 \pi \sigma_i^2}}.
 \end{eqnarray}
-%--------------------------------------------
-
-%--------------------------------------------
-\subsection{Strong gravitational lens model} \label{sec:lensing_theo}
-%--------------------------------------------
-
-%--------------------------------------------
-\subsubsection{Strong lensing formalism}
-%--------------------------------------------
-
-%--------------------------------------------
-A gravitational lens is a mass distribution whose gravitational potential $\Phi$ acts as a lens for light coming from a source positioned somewhere on a plane behind the lens.
-We summarize the basic formalism (see also \citealt{1992grle.book.....S,1996astro.ph..6001N,2006glsw.conf....1S,2006glsw.conf...91K,2010ARA&A..48...87T}).
-The angular diameter distance from the observer to the lens is $D_\text{d}$, to the source plane $D_\text{s}$, and the distance between the lens and source plane is $D_\text{ds}$.
-The deflection potential of the lens is its potential projected along the line of sight $z'$ and rescaled to
-\begin{equation}
-\psi(\vect{\theta}) \equiv \frac{D_\text{ds}}{D_\text{d} D_\text{s}} \frac{2}{c^2} \int \Phi(\vect{r}=D_\text{d} \vect{\theta},z') {\ \mathrm d} z', \label{eq:psidef}
-\end{equation}
-where $\vect{\theta}\equiv(x',y')$ is a 2-dimensional vector on the plane of the sky. The light from the source at $\vect{\beta} \equiv (x_s',y_s')$ is deflected according to the lens equation
-\begin{equation}
-\vect{\beta} = \vect{\theta}_i - \left.\vect{\nabla}_\theta \psi(\vect{\theta})\right|_{\vect{\theta}_i} \label{eq:lenseqpot}
-\end{equation}
-into an image $\vect{\theta}_i = (x_i',y_i')$.
-The gradient of the deflection potential, $\vect{\nabla}_\theta \psi(\vect{\theta})$, is equal to the angle by which the light is deflected multiplied by $D_\text{ds}/D_\text{s}$.
-
-The inverse magnification tensor
-\begin{equation}
-\mathscr{M}^{-1} \equiv \frac{\partial \vect{\beta}}{\partial \vect{\theta}} \overset{(\ref{eq:lenseqpot})}{=} \left(\delta_{ij} - \frac{\partial^2 \psi}{\partial \theta_i \partial \theta_j} \right)\label{eq:magnificationtensor}
-\end{equation}
-describes how the source position changes with image position, the distortion of the image shape for an extended source and its magnification $\mu \equiv \text{image area}/\text{source area} = \det \mathscr{M}$.
-Lines in the image plane for which the magnification becomes infinite, i.e., $\det \mathscr{M}^{-1} = 0$, are called critical curves.
-The corresponding lines in the source plane are called caustics.
-The position of the source with respect to the caustic detemines the number of images and their configuration and shape with respect to each other.
-
-The Einstein mass $M_\text{ein}$ and Einstein radius $R_\text{ein}$ are defined via the relation
-\begin{equation}
-M_\text{ein} \equiv M(<R_\text{ein}) \overset{!}{=} \pi \Sigma_\text{crit} R_\text{ein}^2,
-\end{equation}
-where 
-\begin{equation}
-\Sigma_\text{crit} \equiv \frac{c^2}{4\pi G} \frac{D_\text{s}}{D_\text{d} D_\text{ds}}
-\end{equation}
-is the critical density and $M(<R_\text{ein})$ is the mass projected along the line-of-sight within $R'=R_\text{ein}$.
-$M_\text{ein}$ is similar to the projected mass within the critical curve $M_\text{crit}$.
-%--------------------------------------------
-
-%--------------------------------------------
-\subsubsection{Lens model} 
-%--------------------------------------------
-
-%--------------------------------------------
-Following \citet{EvansWitt} we assume a scale-free model
-\begin{equation}
-\psi(R',\theta') = R^{'\alpha} F(\theta') \label{eq:scalefreemodel}
-\end{equation}
-for the lensing potential, consisting of an angular part $F(\theta')$ and a radial power-law part, with $(R',\theta')$ being again polar coordinates on the plane of the sky.
-$\alpha$ denotes the rotation curve slope of the lens and the case $\alpha = 1$ corresponds to a flat rotation curve.
-The surface density of this model is
-\begin{equation*}
-\Sigma(R',\theta')= \frac{ \Sigma_\text{crit}}{2} \left(\alpha^2 F(\theta') + \frac{\partial^2}{\partial \theta^{'2}}F(\theta')\right) R^{'\alpha-2}.
-\end{equation*}
-We expand $F(\theta')$ into a Fourier series,
-\begin{equation}
-F(\theta') = \frac{a_0}{2} + \sum_{k=1}^{\infty} \left(a_k \cos(k\theta') + b_k \sin (k\theta') \right). \label{eq:Fourieransatz}
-\end{equation}
-For this scale-free lens model the lens equation \eqref{eq:lenseqpot} becomes
-\begin{equation}
-\begin{pmatrix} x_s' \\ y_s' \end{pmatrix} = \begin{pmatrix} R'_i \cos \theta'_i - R_i^{'\alpha-1} \left(\alpha \cos \theta'_i F(\theta'_i) - \sin \theta'_i F'(\theta'_i) \right) \\ R'_i \sin \theta'_i - R_i^{'\alpha-1} \left(\alpha \sin \theta'_i F(\theta'_i + \cos \theta'_i F'(\theta'_i) \right)\end{pmatrix}\label{eq:Fourierlenseq}
-\end{equation}
-\citep{EvansWitt}, where $F'(\theta') \equiv \partial F(\theta') / \partial \theta'$.
-When we fix the slope $\alpha$, then the lens equation is a purely linear problem and can be solved numerically for the source position $(x_s',y_s')$ and the Fourier parameters $(a_k,b_k)$ given one observed image at position $(x'_i=R'_i \cos \theta'_i,y'_i=R'_i \sin \theta'_i)$.
-%--------------------------------------------
-
-%--------------------------------------------
-\subsubsection{Model fitting}
-%--------------------------------------------
-
-%--------------------------------------------
-The free parameters of the lens model are: the source position $(x_s',y_s')$, the radial slope $\alpha$ and Fourier parameters $(a_k,b_k)$ of the lens mass distribution in Equations \eqref{eq:scalefreemodel}-\eqref{eq:Fourieransatz}.
-We want to minimize the distance between the observed image positions, $\vect{\theta}_{oi}$, and those predicted by the lensing model, $\vect{\theta}_{pi}$.
-To avoid having to solve the lens equation \eqref{eq:Fourierlenseq} for $\vect{\theta}_{pi}$, we follow \citet{1991ApJ...373..354K} and cast the calculation back to the source plane using the magnification tensor in Equation \eqref{eq:magnificationtensor} to approximate $\vect{\theta} \simeq (\partial \vect{\theta} / \partial \vect{\beta}) \vect{\beta} = \mathscr{M} \vect{\beta} $.
-The best fit lens model is then the one that minimizes
-\begin{align}
-\begin{split}
-\chi^2_\text{lens} &= \sum_{i} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right) \left( \vect{\theta}_{pi} - \vect{\theta}_{oi} \right)\right|^2\label{eq:chi2lens}\\
-&\simeq \sum_{i} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right)  \left.\mathscr{M}\right|_{\vect{\theta}=\vect{\theta}_{oi}} \left( \begin{matrix} x_s' - \tilde{x}'_{si} \\ y_s' - \tilde{y}'_{si} \end{matrix} \right) \right|^2,
-\end{split}
-\end{align}
-where $(\Delta_x,\Delta_y)$ are the measurement errors of the image positions $\vect{\theta}_{oi}$.
-$\left.\mathscr{M}\right|_{\vect{\theta}=\vect{\theta}_{oi}}$ is the magnification tensor and $(\tilde{x}'_{si},\tilde{y}'_{si})$ the source position according to the lens equation, both evaluated at the position of the $i$-th lensing image, $\vect{\theta}_{oi}$.
-Following \citet{GlennEC} we add a term
-\begin{equation}
-\chi^2_\text{shape} = \lambda \sum_{k \geq 3} \frac{\left(a_k^2 +b_k^2 \right)}{a_0^2} \label{eq:chi2shape}
-\end{equation}
-(with $\lambda$ being some weight factor) which forces the shape of the mass distribution to be close to an ellipse. The total $\chi^2$ to minimize is therefore
-\begin{equation}
-\chi^2 = \chi^2_\text{lens} + \chi^2_\text{shape} \label{eq:chi2total}
-\end{equation}
-We set $a_1 = b_1 = 0$, which corresponds to the choice of origin; in this case the center of the galaxy.
-
-To be able to constrain the slope $\alpha$ we would need flux ratios for the images as in \citet{GlennEC}.
-But the extent of the images, possible dust obscuration and surface brightness fluctuations due to microlensing events, as well as the uncertainty in surface brightness subtraction, make flux determination too unreliable and we do not include them in the fitting.
 %--------------------------------------------
@@
 In this way one can now calculate an unambiguous model prediction for the velocity dispersion tensor $\langle v_i v_j \rangle(R,z) = \langle v_i^2 \rangle(R,z)$ (with $i,j \in \{ R,\phi, z\}$ and $\langle v_i v_j \rangle=0$ if $i\neq j$).
-To compare it with observations, $\langle v_i^2 \rangle(R,z)$ has to be rotated by the inclination angle $inc$ to the coordinate system of the observer; $(x',y')$ is the plane of the sky and $z'$ the line-of-sight, where $x'$ is alinged with the galaxy's major axis.
+To compare it with observations, $\langle v_i^2 \rangle(R,z)$ has to be rotated by the inclination angle $\iota$ to the coordinate system of the observer; $(x',y')$ is the plane of the sky and $z'$ the line-of-sight, where $x'$ is alinged with the galaxy's major axis.
 Taking a light-weighted projection along the line-of-sight gives a model prediction for the line-of-sight velocity second moment $\langle v_\text{los}^2\rangle(x',y')$, which is comparable to actual spectroscopic measurements of the second velocity moment.
@@
 average ellipticity & $\epsilon = 1 - q'$ & $0.402$ \\
-estimated inclination & $inc$ [$^\circ$] & $70$\\
+estimated inclination & $\iota$ [$^\circ$] & $70$\\
 apparent I-band magnitude & $m_\text{I}$ [mag] & $15.77$ \\
@@
 where the term with $z_d$ accounts for redshift dimming and $M_{\odot,I}=4.08~\text{mag}$ is the Sun's absolute I-band magnitude \citep{1998gaas.book.....B}.
-The luminosity $L_i$[counts] and the corresponding surface brightness density $I_{0,i} [L_\odot \text{pc}^{-2}]$ of each Gaussian are given in Table \ref{fig:MGEinnerRegions}.
-%--------------------------------------------
-
-%--------------------------------------------
-\subsubsection{Inclination, total luminosity and effective radius}
+The luminosity $L_i$[counts] and the corresponding surface brightness density $I_{0,i} [L_\odot \text{pc}^{-2}]$ of each Gaussian are given in Table \ref{tab:MGEF814W}.
+%--------------------------------------------
+
+%--------------------------------------------
+\subsubsection{Inclination, total luminosity and effective radius} \label{sec:incl_Ltot_Reff}
 %--------------------------------------------
@@
 \begin{equation}
-\cos^2 (inc) = \frac{q'^2 - q_0^2}{1 - q_0^2}
+\cos^2 \iota = \frac{q'^2 - q_0^2}{1 - q_0^2}
 \end{equation}
 and a correction of $+3^\circ$ \citep{1988ngc..book.....T}.
-Our estimate for the inclination is therefore $inc \approx 70^\circ$.
+Our estimate for the inclination is therefore $\iota \approx 70^\circ$.
 Given this inclination, the 2-dimensional MGE models can be deprojected into three dimensions (see Section \ref{sec:MGE_theo_deprojection}).
+We also assume the inclination angle to be known and fixed to this value in the dynamical modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}.
 
@@
 We find the effective radius to be $R_\text{eff} \simeq 2.6'' \hat{=} 5.2~\text{kpc}$.
-All values are summarized in Table \ref{tab:galaxyparameters}.
+
+All galaxy parameters are summarized in Table \ref{tab:galaxyparameters}.
 %--------------------------------------------
@@
 The red solid line corresponds to the lens model for a flat rotation curve ($\alpha = 1$) in Table \ref{tab:bestfitlensmodel}; the red dashed and dash-dotted lines are best fit lens models found analogously from the image positions, but for a fixed rotation curve slope of $\alpha = 1.1$ and $0.9$, respectively.
-For the JAM modelling best fit MGEs to the lens mass models were used, as well as the observed surface brightness MGE in Table \ref{tab:MGEF814W}, assuming velocity isotropy $\beta_z = 0$ and an inclination of $inc = 70^\circ$.
+For the JAM modelling best fit MGEs to the lens mass models were used, as well as the observed surface brightness MGE in Table \ref{tab:MGEF814W}, assuming velocity isotropy $\beta_z = 0$ and an inclination of $\iota = 70^\circ$.
 The most reliable constraints are around the Einstein radius (vertical red dotted line); outside of it the model is just an extrapolation.}
@@
 In this section we create dynamical models for J1331 following the procedure in Sections \ref{sec:model_JAM_JAM}-\ref{sec:model_JAM_compare}.
-We use the deprojected surface brightness MGE from Table \ref{tab:MGEF814W} for the tracer distribution $\nu(R,z)$ and to generate mass models $\rho(R,z)$.
+We use the deprojected surface brightness MGE from Table \ref{tab:MGEF814W} for the tracer distribution $\nu(R,z)$ and to generate mass models $\rho(R,z)$ (assuming the galaxy's inclination angle to be $\iota=70^\circ$; see Table \ref{tab:galaxyparameters} and Section \ref{sec:incl_Ltot_Reff}).
 The only exception is the first test, where the mass model comes from lensing constraints.
@@
 %--------------------------------------------
-We proceed by modelling the mass distribution with (i) a stellar component, which we get from the light MGE in Table \ref{tab:MGEF814W} (deprojected to the intrinsic $\nu(R,z)$) times a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and (ii) a spherical NFW DM component (see Section \ref{sec:model_JAM_NFW}) with halo scale length $r_s$ and circular velocity $v_{200}$ at the virial radius as free parameters.
+We proceed by modelling the mass distribution with (i) a stellar component, which we get from the light MGE in Table \ref{tab:MGEF814W} (deprojected to the intrinsic $\nu(R,z)$ using the fixed inclination angle $\iota=70^\circ$ in Table \ref{tab:galaxyparameters}) times a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and (ii) a spherical NFW DM component (see Section \ref{sec:model_JAM_NFW}) with halo scale length $r_s$ and circular velocity $v_{200}$ at the virial radius as free parameters.
 In the JAM modelling we use a 10-Gaussian MGE fit to the classical NFW profile from Equation \eqref{eq:NFWprofile}.

### 2016-09-18 LensingPaper_draft_v4.04.tex
Started version to be uploaded to arXiv

--- 2016-09-18 LensingPaper_draft_v4.03.tex
@@
 
-\title[Galaxy mass distribution via lensing \& dynamics]{A spiral galaxy's mass distribution uncovered through lensing and dynamics}
-\author[W.H. Trick, G. van de Ven, and A.A. Dutton]{Wilma H. Trick$^{1}$\thanks{E-mail: trick@mpia.de}, Glenn van de Ven$^{1}$ and Aaron A. Dutton$^{1,2}$\\
+\title[Galaxy mass via lensing \& dynamics]{A spiral galaxy's mass distribution uncovered through lensing and dynamics}
+\author[W.H. Trick, G. van de Ven, and A.A. Dutton]{Wilma H. Trick$^{1}$\thanks{E-mail: trick@mpia.de}, Glenn van de Ven$^{1}$, and Aaron A. Dutton$^{1,2}$\\
 $^{1}$Max-Planck-Institute for Astronomy, K\"{o}nigstuhl 17, 69117 Heidelberg, Germany\\
@@
 
-\date{Accepted ???. Received ???; in original form ???}
+\date{Accepted xxx. Received xxx; in original form xxx}
 
@@
 We investigate the matter distribution of a spiral galaxy with a counter-rotating stellar core, SDSS J1331+3628 (J1331), independently with gravitational lensing and stellar dynamical modelling.
-By fitting a gravitational potential model to a quadruplet of lensing images around J1331's bulge, we tightly constrain the mass inside the Einstein radius $R_\text{ein}=(0.91\pm0.02)''(\simeq1.83\pm0.04~\text{kpc})$ to within 4\%: $M_\text{ein} = (7.8\pm0.3) \times 10^{10} \text{M}_\odot$.
+By fitting a gravitational potential model to a quadruplet of lensing images around J1331's bulge, we tightly constrain the mass inside the Einstein radius $R_\text{ein}=(0.91\pm0.02)''$ $(\simeq1.83\pm0.04~\text{kpc})$ to within 4\%: $M_\text{ein} = (7.8\pm0.3) \times 10^{10} \text{M}_\odot$.
 We model observed long-slit major axis stellar kinematics in J1331's central regions by finding Multi-Gaussian Expansion (MGE) models for the stellar and dark matter distribution that solve the axisymmetric Jeans equations.
@@
 We find that J1331's center requires a steep total mass-to-light ratio gradient.
-A dynamical model including a NFW halo (with virial velocity $v_{200} \simeq 240 \pm 40~\text{km s}^{-1}$ and concentration $c_{200} \simeq 8 \pm 2$) and moderate tangential velocity anisotropy ($\beta_z \simeq -0.4 \pm 0.1$) can reproduce the signatures of J1331's counter-rotating core and predict the stellar and gas rotation curve at larger radii.
+A dynamical model including an NFW halo (with virial velocity $v_{200} \simeq 240 \pm 40~\text{km s}^{-1}$ and concentration $c_{200} \simeq 8 \pm 2$) and moderate tangential velocity anisotropy ($\beta_z \simeq -0.4 \pm 0.1$) can reproduce the signatures of J1331's counter-rotating core and predict the stellar and gas rotation curve at larger radii.
 However, our models do not agree with the observed velocity dispersion at large radii.
@@
 Cosmological simulations suggest that cold DM forms cuspy halos following a Navarro-Frenk-White (NFW) profile \citep{1996ApJ...462..563N}.
-However, the existence of central DM density cusps in massive galaxies depends strongly on the stellar mass-to-light ratio (e.g., \citealt{2011MNRAS.416..322D}) and DM dominated dwarf galaxies even favour DM halos with cores (e.g., \citealt{1994Natur.370..629M,2001ApJ...552L..23D}).
+However, the existence of central DM density cusps in massive galaxies depends strongly on the stellar mass-to-light ratio (e.g., \citealt{2011MNRAS.416..322D}), and DM dominated dwarf galaxies even favour DM halos with cores (e.g., \citealt{1994Natur.370..629M,2001ApJ...552L..23D}).
 This discrepancy, known as the core-cusp problem, might be resolved by galaxy formation processes such as mergers and outflows (e.g., \citealt{2001ApJ...560..636E,2012MNRAS.421.3464P}).
@@
 Combining these two methods allows for valuable cross-checking opportunities to disentangle the galactic stellar and DM content.
-Massive galaxies can act as gravitational lenses, deflect the light of background sources and give rise to multiple images.
+Massive galaxies can act as gravitational lenses, deflect the light of background sources, and give rise to multiple images.
 This strong gravitational lensing tightly constrains the projected total mass of the lens galaxy inside $\sim 1''$ (e.g., \citealt{2010ARA&A..48...87T}).
@@
 Because stars are dissipationless dynamical tracers and present almost everywhere in the galaxy, stellar dynamical modelling can complement mass constraints from lensing at small and gas motions at large radii.
-As stellar motions are complex---a bulk rotation around one principal axis combined with random motions in all coordinate directions---\citep{2008gady.book.....B}, full dynamical modelling of rotation, dispersion and velocity anisotropies is needed to deduce the matter distribution.
+As stellar motions are complex---a bulk rotation around one principal axis combined with random motions in all coordinate directions---\citep{2008gady.book.....B}, full dynamical modelling of rotation, dispersion, and velocity anisotropies is needed to deduce the matter distribution.
 
@@
 
-J1331 has already been the subject of several studies: \citet{SWELLSI} confirmed that J1331 is a strong gravitational lens, measured its apparent brightness and estimated the stellar masses of disk and bulge.
+J1331 has already been the subject of several studies: \citet{SWELLSI} confirmed that J1331 is a strong gravitational lens, measured its apparent brightness, and estimated the stellar masses of disk and bulge.
 The lensing properties of J1331 were first analysed by \citet{SWELLSIII}.
-\citet{SWELLSV} measured the gas and stellar kinematics along the major axis and deduced J1331's mass profile from the gas rotation curve at large radii and total mass inside the Einstein radius from gravitational lensing, focusing mostly on the outer regions of J1331.
+\citet{SWELLSV} measured the gas and stellar kinematics along the major axis, and deduced J1331's mass profile from the gas rotation curve at large radii and total mass inside the Einstein radius from gravitational lensing, focusing mostly on the outer regions of J1331.
 
@@
 
-This paper is organized as follows: Section \ref{sec:data} summarizes the data, Section \ref{sec:Modelling} gives an overview of the modelling techniques used in this work, and Section \ref{sec:Results} presents our results on the surface photometry of J1331 using Multi-Gaussian expansions (Section \ref{sec:MGE_results}), constraints from lensing (Section \ref{sec:results_lensing}) and Jeans modelling based on the surface brightness only (Section \ref{sec:results_JAM_SB}) and including a NFW DM halo (Section \ref{sec:results_JAM_NFW}).
-Finally, Section \ref{sec:Discussion} uses these results to discuss J1331's stellar mass-to-light ratio, central kinematics, possible merger history and starting points for future work.
+This paper is organized as follows: Section \ref{sec:data} summarizes the data, Section \ref{sec:Modelling} gives an overview of the modelling techniques used in this work, and Section \ref{sec:Results} presents our results on the surface photometry of J1331 using Multi-Gaussian expansions (Section \ref{sec:MGE_results}), constraints from lensing (Section \ref{sec:results_lensing}) and Jeans modelling based on the surface brightness only (Section \ref{sec:results_JAM_SB}) and including an NFW DM halo (Section \ref{sec:results_JAM_NFW}).
+Finally, Section \ref{sec:Discussion} uses these results to discuss J1331's possible merger history, stellar mass-to-light ratio, central kinematics, and starting points for future work.
 %--------------------------------------------
@@
 The (smoothed) residuals within the white square in panel (a) are shown in panel (c).
-The four bright blobs (A, B, C and D), which are visible in the residuals, are arranged in a typical strong lensing configuration around the center of the galaxy (G).
-(The configuration of the two additional blobs which lie approximately on a line with A, B and G does not suggest that these blobs are a lensing doublet.
+The four bright blobs (A, B, C, and D), which are visible in the residuals, are arranged in a typical strong lensing configuration around the center of the galaxy (G).
+(The configuration of the two additional blobs which lie approximately on a line with A, B, and G does not suggest that these blobs are a lensing doublet.
 They might rather be star-forming regions of a background galaxy.) \emph{Panel (d):} Stellar kinematics along the galaxy's major axis as measured by \citet{SWELLSV}.
@@
 J1331 is located at right ascension = 202.91800$^\circ$ and declination = 36.46999$^\circ$ (epoch J2000).
-\citet{SWELLSI} found from SDSS spectra that J1331 has two redshifts inside the projected radius on the sky $R'=1''$: J1331 itself has $z_d = 0.113$ and $z_s = 0.254$ is the redshift of the lensed background source \citep{SWELLSIII}.
+\citet{SWELLSI} found from SDSS spectra that J1331 has two redshifts inside the projected radius on the sky $R'=1''$: J1331 itself has $z_{\rm d} = 0.113$, and $z_{\rm s} = 0.254$ is the redshift of the lensed background source \citep{SWELLSIII}.
 According to the WMAP5 cosmology \citep{WMAP5cosm}, J1331 has an angular diameter distance of 414 Mpc, which translates into a transverse scaling of $1'' \hat{=} 2.01~\text{kpc}$.
@@
 The images are a combination of four exposures with each an exposure time of $400~\text{sec}$ and were drizzled to a pixel scale of 1 pixel = $0.05''$.
-In particular, we use the images in the filters F450W, to identify the positions of the bluish lensing images, and F814W (I-band) to create a surface brightness model of the reddish bulge.
+In particular, we use the images in the filters F450W, to identify the positions of the bluish lensing images, and F814W ($I$-band) to create a surface brightness model of the reddish bulge.
 %--------------------------------------------
@@
 
-The stellar kinematics, $v_\text{rot}$, $\sigma$ and the root-mean-square velocity $v_\text{rms}^2=v_\text{rot}^2 + \sigma^2$ are shown in Figure \ref{fig:kinematics}.
+The stellar kinematics, $v_\text{rot}$, $\sigma$, and the root-mean-square velocity $v_\text{rms}^2=v_\text{rot}^2 + \sigma^2$, are shown in Figure \ref{fig:kinematics}.
 The rotation curve reveals a counter-rotating core within $2''\hat{=}4~\text{kpc}$.
@@
 We subtract $2.3~\text{km s}^{-1}$ from $v_\text{rot}$ to ensure $v_\text{rot}(R'=0) \sim 0$ as a possible correction term for a misjudgement of the systemic velocity.
-We also symmetrize the data within $4''$ and asign a minimum error of $\delta v_\text{rms} = 5~\text{km s}^{-1}$ to the $v_\text{rms}$ data.
+We also symmetrize the data within $4''$ and assign a minimum error of $\delta v_\text{rms} = 5~\text{km s}^{-1}$ to the $v_\text{rms}$ data.
 In our dynamical Jeans modelling approach, which is based on the assumption of axisymmetry, only stellar kinematics with either $R'  \lesssim 3.5''$ or $R' \lesssim 4''$ are used.
@@
 \end{equation}
-where $\vect{\theta}\equiv(x',y')$ is a 2-dimensional vector on the plane of the sky. The light from the source at $\vect{\beta} \equiv (x_s',y_s')$ is deflected according to the lens equation
+where $\vect{\theta}\equiv(x',y')$ is a two-dimensional vector on the plane of the sky.
+The light from the source at $\vect{\beta} \equiv (x_{\rm s}',y_{\rm s}')$ is deflected according to the lens equation
 \begin{equation}
@@
 \begin{equation}
-\begin{pmatrix} x_s' \\ y_s' \end{pmatrix} = \begin{pmatrix} R'_i \cos \theta'_i - R_i^{'\alpha-1} \left(\alpha \cos \theta'_i F(\theta'_i) - \sin \theta'_i F'(\theta'_i) \right) \\ R'_i \sin \theta'_i - R_i^{'\alpha-1} \left(\alpha \sin \theta'_i F(\theta'_i + \cos \theta'_i F'(\theta'_i) \right)\end{pmatrix}\label{eq:Fourierlenseq}
+\begin{pmatrix} x_{\rm s}' \\ y_{\rm s}' \end{pmatrix} = \begin{pmatrix} R'_i \cos \theta'_i - R_i^{'\alpha-1} \left(\alpha \cos \theta'_i F(\theta'_i) - \sin \theta'_i F'(\theta'_i) \right) \\ R'_i \sin \theta'_i - R_i^{'\alpha-1} \left(\alpha \sin \theta'_i F(\theta'_i + \cos \theta'_i F'(\theta'_i) \right)\end{pmatrix}\label{eq:Fourierlenseq}
 \end{equation}
 \citep{EvansWitt}, where $F'(\theta') \equiv \partial F(\theta') / \partial \theta'$.
-When we fix the slope $\alpha$, then the lens equation is a purely linear problem and can be solved numerically for the source position $(x_s',y_s')$ and the Fourier parameters $(a_k,b_k)$ given one observed image at position $(x'_i=R'_i \cos \theta'_i,y'_i=R'_i \sin \theta'_i)$.
+When we fix the slope $\alpha$, then the lens equation is a purely linear problem and can be solved numerically for the source position $(x_{\rm s}',y_{\rm s}')$ and the Fourier parameters $(a_k,b_k)$ given one observed image at position $(x'_i=R'_i \cos \theta'_i,y'_i=R'_i \sin \theta'_i)$.
 %--------------------------------------------
@@
 %--------------------------------------------
-The free parameters of the lens model are: the source position $(x_s',y_s')$, the radial slope $\alpha$ and Fourier parameters $(a_k,b_k)$ of the lens mass distribution in Equations \eqref{eq:scalefreemodel}-\eqref{eq:Fourieransatz}.
-We want to minimize the distance between the observed image positions, $\vect{\theta}_{oi}$, and those predicted by the lensing model, $\vect{\theta}_{pi}$.
-To avoid having to solve the lens equation \eqref{eq:Fourierlenseq} for $\vect{\theta}_{pi}$, we follow \citet{1991ApJ...373..354K} and cast the calculation back to the source plane using the magnification tensor in Equation \eqref{eq:magnificationtensor} to approximate $\vect{\theta} \simeq (\partial \vect{\theta} / \partial \vect{\beta}) \vect{\beta} = \mathscr{M} \vect{\beta} $.
-The best fit lens model is then the one that minimizes
+The free parameters of the lens model are: the source position $(x_{\rm s}',y_{\rm s}')$, the radial slope $\alpha$ and Fourier parameters $(a_k,b_k)$ of the lens mass distribution in Equations \eqref{eq:scalefreemodel}-\eqref{eq:Fourieransatz}.
+We want to minimize the distance between the observed image positions, $\vect{\theta}_{{\rm o}i}$, and those predicted by the lensing model, $\vect{\theta}_{{\rm p}i}$.
+To avoid having to solve the lens equation \eqref{eq:Fourierlenseq} for $\vect{\theta}_{{\rm p}i}$, we follow \citet{1991ApJ...373..354K} and cast the calculation back to the source plane using the magnification tensor in Equation \eqref{eq:magnificationtensor} to approximate $\vect{\theta} \simeq (\partial \vect{\theta} / \partial \vect{\beta}) \vect{\beta} = \mathscr{M} \vect{\beta} $.
+The best-fitting lens model is then the one that minimizes
 \begin{align}
 \begin{split}
-\chi^2_\text{lens} &= \sum_{i} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right) \left( \vect{\theta}_{pi} - \vect{\theta}_{oi} \right)\right|^2\label{eq:chi2lens}\\
-&\simeq \sum_{i} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right)  \left.\mathscr{M}\right|_{\vect{\theta}=\vect{\theta}_{oi}} \left( \begin{matrix} x_s' - \tilde{x}'_{si} \\ y_s' - \tilde{y}'_{si} \end{matrix} \right) \right|^2,
+\chi^2_\text{lens} &= \sum_{i} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right) \left( \vect{\theta}_{{\rm p}i} - \vect{\theta}_{{\rm o}i} \right)\right|^2\label{eq:chi2lens}\\
+&\simeq \sum_{i} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right)  \left.\mathscr{M}\right|_{\vect{\theta}=\vect{\theta}_{{\rm o}i}} \left( \begin{matrix} x_{\rm s}' - \tilde{x}'_{si} \\ y_{\rm s}' - \tilde{y}'_{si} \end{matrix} \right) \right|^2,
 \end{split}
 \end{align}
-where $(\Delta_x,\Delta_y)$ are the measurement errors of the image positions $\vect{\theta}_{oi}$.
-$\left.\mathscr{M}\right|_{\vect{\theta}=\vect{\theta}_{oi}}$ is the magnification tensor and $(\tilde{x}'_{si},\tilde{y}'_{si})$ the source position according to the lens equation, both evaluated at the position of the $i$-th lensing image, $\vect{\theta}_{oi}$.
+where $(\Delta_x,\Delta_y)$ are the measurement errors of the image positions $\vect{\theta}_{{\rm o}i}$.
+$\left.\mathscr{M}\right|_{\vect{\theta}=\vect{\theta}_{{\rm o}i}}$ is the magnification tensor and $(\tilde{x}'_{si},\tilde{y}'_{si})$ the source position according to the lens equation, both evaluated at the position of the $i$-th lensing image, $\vect{\theta}_{{\rm o}i}$.
 Following \citet{GlennEC} we add a term
@@
 %--------------------------------------------
-MGEs are used to parametrize the observed surface brightness (or projected total mass) of a galaxy as a sum of $N$ 2-dimensional, elliptical Gaussians \citep{1991ApJ...366..599B,1992A&A...253..366M,1994A&A...285..723E,1999MNRAS.303..495E}.
+MGEs are used to parametrize the observed surface brightness (or projected total mass) of a galaxy as a sum of $N$ two-dimensional, elliptical Gaussians \citep{1991ApJ...366..599B,1992A&A...253..366M,1994A&A...285..723E,1999MNRAS.303..495E}.
 This work makes use of the algorithm and code\footnote{The IDL code package for fitting MGEs to images by \citet{Cap02} is available online at \url{http://www-astro.physics.ox.ac.uk/~mxc/software}.
@@
 \end{equation}
-where $\sum_j G_j = 1$ and $\delta_j$ are the dispersions of the circular PSF Gaussians.
+where $\sum_j G_j = 1$, and $\delta_j$ are the dispersions of the circular PSF Gaussians.
 
@@
 $I(R',\theta')$ describes the intrinsic and 2D projected light distribution or surface density of the galaxy.
-Under the assumption that the galaxy is oblate and axisymmetric, and given the inclination angle $\iota$ of the galaxy with respect to the observer, MGEs allow an analytic deprojection of the 2-dimensional MGE to get a 3-dimensional axisymmetric light distribution or density $\nu(R,z)$ for the galaxy,
+Under the assumption that the galaxy is oblate and axisymmetric, and given the inclination angle $\iota$ of the galaxy with respect to the observer, MGEs allow an analytic deprojection of the two-dimensional MGE to get a three-dimensional axisymmetric light distribution or density $\nu(R,z)$ for the galaxy,
 \begin{equation}
@@
 %--------------------------------------------
-JAM modelling assumes galaxies to be (i) collisionless, (ii) in a steady state and (iii) axisymmetric.
+JAM modelling assumes galaxies to be (i) collisionless, (ii) in a steady state, and (iii) axisymmetric.
 With these assumptions the axisymmetric Jeans equations follow from the vector-valued first moment of the collisionless Boltzmann equation (see Equations (4.221)-(4.222) in \citet{2008gady.book.....B}).
@@
 To be able to solve the Jeans equations, additional assumptions about the velocity ellipsoid tensor $\langle v_i v_j\rangle$ have to be made.
-We follow \citet{Cap08} and assume firstly that the galaxy's velocity ellipsoid is aligned with the cylindrical coordinate system, i.e., $\langle v_R v_z\rangle = \langle v_z v_\phi \rangle = \langle v_\phi v_R \rangle = 0$.
+We follow \citet{Cap08} and assume first that the galaxy's velocity ellipsoid is aligned with the cylindrical coordinate system, i.e., $\langle v_R v_z\rangle = \langle v_z v_\phi \rangle = \langle v_\phi v_R \rangle = 0$.
 Secondly, we assume a constant ratio between the radial and vertical second velocity moments,
@@
 In this way one can now calculate an unambiguous model prediction for the velocity dispersion tensor $\langle v_i v_j \rangle(R,z) = \langle v_i^2 \rangle(R,z)$ (with $i,j \in \{ R,\phi, z\}$ and $\langle v_i v_j \rangle=0$ if $i\neq j$).
-To compare it with observations, $\langle v_i^2 \rangle(R,z)$ has to be rotated by the inclination angle $\iota$ to the coordinate system of the observer; $(x',y')$ is the plane of the sky and $z'$ the line-of-sight, where $x'$ is alinged with the galaxy's major axis.
+To compare it with observations, $\langle v_i^2 \rangle(R,z)$ has to be rotated by the inclination angle $\iota$ to the coordinate system of the observer; $(x',y')$ is the plane of the sky and $z'$ the line-of-sight, where $x'$ is aligned with the galaxy's major axis.
 Taking a light-weighted projection along the line-of-sight gives a model prediction for the line-of-sight velocity second moment $\langle v_\text{los}^2\rangle(x',y')$, which is comparable to actual spectroscopic measurements of the second velocity moment.
@@
 
-The JAM modelling code by \citet{Cap08} evaluates this expression for $\langle v_\text{los}^2\rangle(x',y')$ numerically for a given luminous tracer and mass distribution MGE and a given inclination.
+The JAM modelling code\footnote{The IDL code package for Jeans Anisotropic Models (JAM) by \citet{Cap08} is available online at \url{http://www-astro.physics.ox.ac.uk/~mxc/software}.
+The version from June 2012 was used in this work.} by \citet{Cap08} evaluates this expression for $\langle v_\text{los}^2\rangle(x',y')$ numerically for a given luminous tracer and mass distribution MGE and a given inclination.
 %--------------------------------------------
@@
 \begin{eqnarray}
-I_\text{obs} &=& I \ast K\\
+I_\text{obs} &=& I \ast K,\\
 \langle v_\text{los}^2 \rangle_\text{obs} &=& \frac{(I \langle v_\text{los}^2\rangle_\text{intr}) \ast K}{I_\text{obs}}.
 \end{eqnarray}
-We modified the JAM code\footnote{The IDL code package for Jeans Anisotropic Models (JAM) by \citet{Cap08} is available online at \url{http://www-astro.physics.ox.ac.uk/~mxc/software}.
-The version from June 2012 was used in this work.} by \citet{Cap08} to use this convolution kernel with non-square pixels.
+We modified the JAM code by \citet{Cap08} to use this convolution kernel with non-square pixels.
 The JAM code then performs the convolution numerically.
@@
 Further assumptions are needed to separate the second velocity moments into ordered and random motion.
-\citet{Cap08} assumes that in a steady state there is no streaming velocity in $R$ direction, i.e., $\langle v_R \rangle = 0$ and therefore $\sigma_R^2 = \langle v_R^2 \rangle$.
+\citet{Cap08} assumes that in a steady state there is no streaming velocity in $R$ direction, i.e., $\langle v_R \rangle = 0$, and therefore $\sigma_R^2 = \langle v_R^2 \rangle$.
 Then \citet{Cap08} relates the dispersions in $R$ and $\phi$ direction such that
@@
 \end{equation}
-and the $\kappa$ parameter quantifies the rotation: $\kappa = 0$ means no rotation at all and $|\kappa| = 1$ describes a velocity dispersion ellipsoid that is a circle in the $R$-$\phi$ plane \citep{Cap08}.
+and the $\kappa$ parameter quantifies the rotation: $\kappa = 0$ means no rotation at all, and $|\kappa| = 1$ describes a velocity dispersion ellipsoid that is a circle in the $R$-$\phi$ plane \citep{Cap08}.
 The sign of $\kappa$ determines the rotation direction.
@@
 We find $\kappa'$ by matching the model $\langle v_\text{los} \rangle_\text{obs}$ with the symmetrized $v_\text{rot}$ data, where for a given $\kappa'$ the $\kappa_i$ are found from fitting the MGE generated profile $\kappa(R) = \sum_i \kappa_i \nu_i(r)/\sum_i \nu_i(r)$ to Equation \eqref{eq:kappa_profile}.
-The observed zero point is at $R'_0\approx 2''$.
+The observed zero-point is at $R'_0\approx 2''$.
 In the deprojected galactic plane the radius of zero rotation would be at a $R_0 \gtrsim 2''$, and we choose it to be at $2.2''$.
@@
 %--------------------------------------------
-\subsubsection{Including a NFW halo} \label{sec:model_JAM_NFW}
-%--------------------------------------------
-
-%--------------------------------------------
-As mentioned above, JAM modelling allows to incorporate an invisible matter component in addition to the luminous matter in the form of an MGE.
-In Section \ref{sec:results_JAM_NFW} we will include a spherical Navarro-Frenk-White (NFW) DM halo \citep{1996ApJ...462..563N} in the dynamical model.
+\subsubsection{Including an NFW halo} \label{sec:model_JAM_NFW}
+%--------------------------------------------
+
+%--------------------------------------------
+As mentioned above, JAM modelling allows us to incorporate an invisible matter component in addition to the luminous matter in the form of an MGE.
+In Section \ref{sec:results_JAM_NFW}, we will include a spherical Navarro-Frenk-White (NFW) DM halo \citep{1996ApJ...462..563N} in the dynamical model.
 The classical NFW profile has the form
 \begin{equation}
-\rho_\text{NFW}(r) \propto r^{-1} \left( r+r_s \right)^{-2} \label{eq:NFWprofile}
-\end{equation}
-and two free parameters, the scale length $r_s$ and a parameter describing the total mass of the halo.
+\rho_\text{NFW}(r) \propto r^{-1} \left( r+r_{\rm s} \right)^{-2} \label{eq:NFWprofile}
+\end{equation}
+and two free parameters, the scale length $r_{\rm s}$ and a parameter describing the total mass of the halo.
 We will use $v_\text{200}\equiv \sqrt{GM_{200}/r_{200}}$, which is the circular velocity at the radius $r_\text{200}$ within which the mean density of the halo is 200 times the cosmological critical density $\rho_\text{crit} \equiv (2H^2)/(8\pi G)$, and where $M_{200} \equiv M(<r_{200}) \stackrel{!}{=} \frac 43 \pi r_{200}^3 \times 200\rho_\text{crit}(z=0)$, with $\rho_\text{crit}(z=0)=1.43 \times 10^{-7} \text{M}_\odot / \text{pc}^3$ in the WMAP5 cosmology by \citet{WMAP5cosm}.
-The mass concentration of the NFW halo is quantified by $c_{200}\equiv r_{200} / r_s$.
+The mass concentration of the NFW halo is quantified by $c_{200}\equiv r_{200} / r_{\rm s}$.
 There is a close relation between the concentration and halo mass in simulations \citep{1996ApJ...462..563N}. \citet{Maccio08} found this relation for the WMAP5 cosmology to be
@@
 (their Equation 10), with a Gaussian scatter of $\sigma_{\log c_{200}} = 0.105$ (their Table A2).
-In Section \ref{sec:results_JAM_NFW} we will use this relation as prior information to guide the modelling towards realistic NFW halo shapes.
+In Section \ref{sec:results_JAM_NFW}, we will use this relation as prior information to guide the modelling towards realistic NFW halo shapes.
 %--------------------------------------------
@@
 \hline
-redshift \citep{SWELLSIII}                 & $z_d$ & $0.113$ \\
+redshift \citep{SWELLSIII}                 & $z_{\rm d}$ & $0.113$ \\
 angular diameter distance & $D_\text{d}$ [Mpc] & $414$ \\
@@
 estimated inclination & $\iota$ [$^\circ$] & $70$\\
-apparent I-band magnitude & $m_\text{I}$ [mag] & $15.77$ \\
-total I-band luminosity & $L_\text{I,tot}$ [$10^{10} L_\odot$] & $5.6$ \\
+apparent $I$-band magnitude & $m_\text{I}$ [mag] & $15.77$ \\
+total $I$-band luminosity & $L_\text{I,tot}$ [$10^{10} L_\odot$] & $5.6$ \\
 effective half-light radius & $R_\text{eff}$ [$''$] & $2.6$ \\
@@
 In this section we construct a model for J1331's intrinsic light distribution in terms of MGEs (see Section \ref{sec:MGE_theo}).
-We use the HST image in the F814W (I-band) filter (Figure \ref{fig:F814W}) because J1331's central stellar component appears at longer wavelengths (i) smoother and more extended than in the F450W filter (Figure \ref{fig:F450W}), as it is less sensitive to young clumpy star-forming regions, (ii) much brighter than the bluish lensing images, and (iii) the imaging is less prone to extinction.
+We use the HST image in the F814W ($I$-band) filter (Figure \ref{fig:F814W}) because J1331's central stellar component appears at longer wavelengths (i) smoother and more extended than in the F450W filter (Figure \ref{fig:F450W}), as it is less sensitive to young clumpy star-forming regions, (ii) much brighter than the bluish lensing images, and (iii) the imaging is less prone to extinction.
 
@@
 \caption{MGEs for J1331's surface brightness distribution.
-Comparison of contours with constant F814W surface brightness (orange lines) with the corresponding iso-brightness contours of the best fit MGE, convolved with the PSF in Table \ref{tab:MGEF814W}, (grey lines).
+Comparison of contours with constant F814W surface brightness (orange lines) with the corresponding iso-brightness contours of the best-fitting MGE, convolved with the PSF in Table \ref{tab:MGEF814W}, (grey lines).
 The black line has a length of $10''$ and its orientation corresponds to the galaxy's position angle as found in Table \ref{tab:galaxyparameters}.
-For comparison the Einstein radius as found in Table \ref{tab:bestfitlensmodel}  is indicated as red dashed circle.
+For comparison, the Einstein radius as found in Table \ref{tab:bestfitlensmodel} is indicated as red dashed circle.
 \emph{Panel (a):} Central regions of J1331.
@@
 \emph{Panel (b):} Outer regions of J1331.
-The orange lines indicate here contours of a smooth IRAF \emph{ellipse} fit to J1331 in the F814W filter; the grey lines are the corresponding best fit MGE.
+The orange lines indicate here contours of a smooth IRAF \emph{ellipse} fit to J1331 in the F814W filter; the grey lines are the corresponding best-fitting MGE.
 This MGE is not used for dynamical model fitting because the dynamics in the outer regions are strongly affected by non-axisymmetries (e.g., spiral arms).
@@
 \centering
-\caption{Parameters of the best fit MGE to the F814W surface brightness of J1331 in Figure \ref{fig:MGEinnerRegions}.
+\caption{Parameters of the best-fitting MGE to the F814W surface brightness of J1331 in Figure \ref{fig:MGEinnerRegions}.
 The fit is best inside a radius of $5''$.
@@
 The first column gives for each Gaussian the total F814W luminosity in Equation \eqref{eq:centralItotalL} in units of counts.
-The second column is the corresponding I-band peak surface brightness in Equation \eqref{eq:MGEgeneral} in units of a luminosity surface density.
+The second column is the corresponding $I$-band peak surface brightness in Equation \eqref{eq:MGEgeneral} in units of a luminosity surface density.
 The third and fourth column give the dispersion and the last column the axis ratio of the Gaussian in Equation \eqref{eq:MGEgeneral}.}
@@
 Bright objects close to the bulge (blobs possibly belonging to the background galaxy and parts of the foreground spiral arm) were masked during the fit.
-J1331's galaxy center, position angle (with respect to North through East) and average apparent ellipticity (see Table \ref{tab:galaxyparameters}) are found from the images weighted first and second moment.
+J1331's galaxy center, position angle (with respect to North through East), and average apparent ellipticity (see Table \ref{tab:galaxyparameters}) are found from the images weighted first and second moment.
 The MGE fit splits the image in annuli with the given ellipticity and position angle and sectors of $5^\circ$ width and fits an 5-Gaussian MGE of the form in Equation \eqref{eq:MGEgeneral} convolved with the PSF MGE in Table \ref{tab:PSFMGEF814W} to it.
-The best fit MGE (PSF convolved) is compared to the data in Figure \ref{fig:MGEinnerRegions} and the corresponding parameters of the intrinsic surface brightness distribution are given in Table \ref{tab:MGEF814W}.
+The best-fitting MGE (PSF convolved) is compared to the data in Figure \ref{fig:MGEinnerRegions}, and the corresponding parameters of the intrinsic surface brightness distribution are given in Table \ref{tab:MGEF814W}.
 The fit is a very good representation of the light distribution in the inner $5''$, but underestimates the light distribution further out.
@@
 \end{equation}
-This is then transformed into an I-band surface brightness (in $\text{mag}\times(1'')^{-2}$) via
+This is then transformed into an $I$-band surface brightness (in $\text{mag}\times(1'')^{-2}$) via
 \begin{equation}
@@
 \end{equation}
-where $Z\simeq21.62~\text{mag}$ is the zero-point from \citet{Holtzman}, updated according to \citet{Dolphin,DolphinNew}, for the photometric system of the HST/WFPC2 camera and the F814W filter, plus a correction for the difference in gain between calibration and observation.
-$C= 0.1~\text{mag}$ corrects for the finite aperture of the WFPC2; and $A_I =0.015~\text{mag}$ is the extinction in the (Landolt) I-band towards J1331, according to the NASA/IPAC Extragalactic Database (NED)\footnote{The NASA/IPAC Extragalactic Database (NED, \url{https://ned.ipac.caltech.edu/}) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.
+where $Z\simeq21.62~\text{mag}$ is the zero-point from \citet{Holtzman}, updated according to \citet{Dolphin}\footnote{We used the updated zero points by Andrew E.
+Dolphin, "Zero Points relative to Holtzman et al.
+(1995)" from \url{http://americano.dolphinsim.com/wfpc2_calib/2008_07_19.html}.
+The data was retrieved on September 20th, 2013.}, for the photometric system of the HST/WFPC2 camera and the F814W filter, plus a correction for the difference in gain between calibration and observation.
+$C= 0.1~\text{mag}$ corrects for the finite aperture of the WFPC2; and $A_I =0.015~\text{mag}$ is the extinction in the (Landolt) $I$-band towards J1331, according to the NASA/IPAC Extragalactic Database (NED)\footnote{The NASA/IPAC Extragalactic Database (NED, \url{https://ned.ipac.caltech.edu/}) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.
 The data for J1331 (SDSS J133140.33+362811.9) was retrieved in October 2013.}.
-The colour-dependent correction between the F814W filter and the I-band of the UBVRI photometric system is  small \citep{Holtzman} and we neglect it therefore.
-The last step is to transform the surface brightness $\mu_{I,0,i}$ (in mag) to the I-band surface density $I_{0,i}$ (in $L_\odot$/pc$^2$) of the Gaussian, i.e.,
+The colour-dependent correction between the F814W filter and the $I$-band of the UBVRI photometric system is  small \citep{Holtzman} and we neglect it therefore.
+The last step is to transform the surface brightness $\mu_{I,0,i}$ (in mag) to the $I$-band surface density $I_{0,i}$ (in $L_\odot$/pc$^2$) of the Gaussian, i.e.,
 \begin{eqnarray}
-I_{0,i}[L_\odot \text{pc}^{-2}] = \left( 64800/\pi\right)^2 \left(1+z_d \right)^4 10^{0.4\left(M_{\odot,I}-\mu_{I,0,i} \right)},
+I_{0,i}[L_\odot \text{pc}^{-2}] = \left( 64800/\pi\right)^2 \left(1+z_{\rm d} \right)^4 10^{0.4\left(M_{\odot,I}-\mu_{I,0,i} \right)},
 \end{eqnarray}
-where the term with $z_d$ accounts for redshift dimming and $M_{\odot,I}=4.08~\text{mag}$ is the Sun's absolute I-band magnitude \citep{1998gaas.book.....B}.
+where the term with $z_{\rm d}$ accounts for redshift dimming, and $M_{\odot,I}=4.08~\text{mag}$ is the Sun's absolute $I$-band magnitude \citep{1998gaas.book.....B}.
 The luminosity $L_i$[counts] and the corresponding surface brightness density $I_{0,i} [L_\odot \text{pc}^{-2}]$ of each Gaussian are given in Table \ref{tab:MGEF814W}.
@@
 %--------------------------------------------
-\subsubsection{Inclination, total luminosity and effective radius} \label{sec:incl_Ltot_Reff}
+\subsubsection{Inclination, total luminosity, and effective radius} \label{sec:incl_Ltot_Reff}
 %--------------------------------------------
@@
 Our estimate for the inclination is therefore $\iota \approx 70^\circ$.
-Given this inclination, the 2-dimensional MGE models can be deprojected into three dimensions (see Section \ref{sec:MGE_theo_deprojection}).
+Given this inclination, the two-dimensional MGE models can be deprojected into three dimensions (see Section \ref{sec:MGE_theo_deprojection}).
 We also assume the inclination angle to be known and fixed to this value in the dynamical modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}.
 
-J1331's total I-band luminosity is determined by summing up the luminosity contributions of all the MGE Gaussians for the outer regions (shown as grey lines in Figure \ref{fig:MGEouterRegions}).
+J1331's total $I$-band luminosity is determined by summing up the luminosity contributions of all the MGE Gaussians for the outer regions (shown as grey lines in Figure \ref{fig:MGEouterRegions}).
 We find $L_\text{I,tot} \simeq 5.6 \times 10^{10} ~L_\odot$.
@@
 \caption{Positions of the lensing images (A-D) and the galaxy center (G) in Figure \ref{fig:lens_just_imgpos}.
-The image positions were determined from the lens-MGE subtracted F450W image for J1331by \citet{SWELLSIII} (their Figure 4), rotated to the $(x',y')$ coordinate system in Figure \ref{fig:lens_just_imgpos}.
+The image positions were determined from the lens-MGE subtracted F450W image for J1331 by \citet{SWELLSIII} (their Figure 4), rotated to the $(x',y')$ coordinate system in Figure \ref{fig:lens_just_imgpos}.
 The pixel scale is 1 pixel = $0.05''$ and the error of the image positions A-D is $\pm$ 1 pixel.}
@@
   \includegraphics[width=\linewidth]{fig/lens_all_in_one.ps}
-\caption{Lensing model (Table \ref{tab:bestfitlensmodel}) found as best fit to the lensing image positions.
+\caption{Lensing model (in Table \ref{tab:bestfitlensmodel}) found as best fit to the lensing image positions.
 In the background we show the central region of J1331 in the F450W filter, subtracted by an IRAF \emph{ellipse} model of the F450W surface brightness and smoothed to remove noise smaller than the PSF.
 The brightness peaks of the four lensing images and the galaxy center (Table \ref{tab:lenspos}) are marked as red dots.
-For the best fit lens model we show the Einstein radius (red dotted circle) and the critical curve (red solid line), which are located in the lens plane.
-We also show the caustic (green solid line) corresponding to the critical curve and the best fit source position (green dot), which are located in the source plane.
-For $\alpha=1$ the critical curve is a contour of constant surface density of the mass model.
+For the best-fitting lens model we show the Einstein radius (red dotted circle) and the critical curve (red solid line), which are located in the lens plane.
+We also show the caustic (green solid line) corresponding to the critical curve and the best-fitting source position (green dot), which are located in the source plane.
+For $\alpha=1$, the critical curve is a contour of constant surface density of the mass model.
 The grey  lines show contours of the time delay surface given by Equation (63) in \citet{1996astro.ph..6001N}.
@@
 \centering
-\caption{Best fit lens model (first column) found from the peak image positions in Table \ref{tab:lenspos} following the procedure described in Section \ref{sec:lensing_theo} and assuming a flat rotation curve ($\alpha = 1$).
-The second column gives the corresponding best fit mean and standard deviation derived from Monte Carlo sampling of the Gaussian uncertainties around the image positions, with the relative error given in parentheses.}
+\caption{Best-fitting lens model (first column) found from the peak image positions in Table \ref{tab:lenspos} following the procedure described in Section \ref{sec:lensing_theo} and assuming a flat rotation curve ($\alpha = 1$).
+The second column gives the corresponding best-fitting mean and standard deviation derived from Monte Carlo sampling of the Gaussian uncertainties around the image positions, with the relative error given in parentheses.}
 \begin{tabular}{llrrclr}
@@
 Critical mass        & $M_\text{crit}$ [$10^{10} \text{M}_\odot$] & $7.87$  & $7.9$   & $\pm$ & $      0.3$ & ($4\%$)\\
-Source position      & $x_s'$ [$''$]                      & $0.095$ & $0.09 $ & $\pm$ & $     0.03$ & ($28\%$)\\
-                     & $y_s'$ [$''$]                     & $0.107$ & $0.10 $ & $\pm$ & $     0.03$ & ($27\%$)\\
+Source position      & $x_{\rm s}'$ [$''$]                      & $0.095$ & $0.09 $ & $\pm$ & $     0.03$ & ($28\%$)\\
+                     & $y_{\rm s}'$ [$''$]                     & $0.107$ & $0.10 $ & $\pm$ & $     0.03$ & ($27\%$)\\
 Fourier coefficients & $a_0$                               & $1.814$ & $1.82 $ & $\pm$ & $   0.04$ & (2\%)\\
@@
 \end{subfigure}
-\caption{Comparison of the observed F814W/I-band surface brightness distribution (panel (a) and orange contours) and derived mass distribution from lensing constraints (panel (b) and pink contours).
+\caption{Comparison of the observed F814W/$I$-band surface brightness distribution (panel (a) and orange contours) and derived mass distribution from lensing constraints (panel (b) and pink contours).
 To allow for a qualitative comparison of the contours in panel (c), the light distribution was turned into a mass distribution by multiplication with the total mass-to-light ratio inside the Einstein radius, $\Upsilon_\text{I,tot}^\text{ein} = 5.56 \Upsilon_{I,\odot}$.
@@
 The uncertainties in the mass model in the second column of Table \ref{tab:bestfitlensmodel} were translated into random Monte Carlo noise in the mass contours.
-The smooth black contours correspond to the best fit model in the first column of Table \ref{tab:bestfitlensmodel}.
-We find, that the lens mass model is more roundish than the light distribution.
-The background in Panel (c) shows again the surface brightness subtracted center of the galaxy to make the lensing images visible.}
+The smooth black contours correspond to the best-fitting model in the first column of Table \ref{tab:bestfitlensmodel}.
+We find that the lens mass model is more roundish than the light distribution.
+The background in panel (c) shows again the surface brightness subtracted center of the galaxy to make the lensing images visible.}
 \label{fig:lenslightcompareALL}
@@
 %--------------------------------------------
-\subsubsection{Best fit lens model} \label{sec:results_lensing_bestfit}
+\subsubsection{Best-fitting lens model} \label{sec:results_lensing_bestfit}
 %--------------------------------------------
@@
 We fit the lens mass model to the image positions in Table \ref{tab:lenspos} by minimizing $\chi^2 = \chi_\text{lens}^2 + \chi_\text{shape}^2$ (see Equations \eqref{eq:chi2lens}-\eqref{eq:chi2total}).
-The best fit parameters are given in the first column of Table \ref{tab:bestfitlensmodel}.
-Figure \ref{fig:bestfitlensmodel} shows the corresponding critical curve, caustic and Einstein radius, and the best fit source position.
+The best-fitting parameters are given in the first column of Table \ref{tab:bestfitlensmodel}.
+Figure \ref{fig:bestfitlensmodel} shows the corresponding critical curve, caustic and Einstein radius, and the best-fitting source position.
 In this case, where $\alpha=1$, the (tangential) critical curve is also an equidensity contour of the galaxy model \citep{EvansWitt}, which appears to have an elliptical mass distribution.
 The source is located close to a cusp of the diamond-shaped caustic: a lensing configuration for which we indeed expect four images.
-Figure \ref{fig:bestfitlensmodel} also shows the (smoothed) residuals from the F450W image subtracted by an IRAF \emph{ellipse} brightness model and the contours of the best fit model's time delay surface (see \S 3.3.1 in \citealt{1996astro.ph..6001N}).
+Figure \ref{fig:bestfitlensmodel} also shows the (smoothed) residuals from the F450W image subtracted by an IRAF \emph{ellipse} brightness model and the contours of the best-fitting model's time delay surface (see \S 3.3.1 in \citealt{1996astro.ph..6001N}).
 Fermat's principle states that the image positions are observed at the extrema of the time delay surface.
@@
 
-To estimate how the uncertainties in the determination of image positions and galaxy center affect the results, we sample random positions from 2-dimensional Normal distributions with peaks and standard deviations according to Table \ref{tab:lenspos}.
-Model fits to many sampled image positions lead to probability distributions for the best fit shape parameters and Einstein quantities; peak and standard deviations are given in the second column of Table \ref{tab:bestfitlensmodel}.
+To estimate how the uncertainties in the determination of image positions and galaxy center affect the results, we sample random positions from two-dimensional Normal distributions with peaks and standard deviations according to Table \ref{tab:lenspos}.
+Model fits to many sampled image positions lead to probability distributions for the best-fitting shape parameters and Einstein quantities; peak and standard deviations are given in the second column of Table \ref{tab:bestfitlensmodel}.
 We constrain the Einstein radius to within 2\%, $R_\text{ein} = (0.91 \pm 0.02)'' \hat{=}(1.83\pm0.04)~\text{kpc}$, and the projected mass within the critical curve with a relative error of 4\%, $M_\text{crit} =(7.9\pm0.3) \times 10^{10} \text{M}_\odot$.
@@
   \caption{Comparison (not a fit!) of the symmetrized stellar $v_\text{rms}$ data of J1331 (blue dots) with JAM models generated from mass distributions which were independently derived from lensing constraints in Section \ref{sec:results_lensing} (red lines).
-The red solid line corresponds to the lens model for a flat rotation curve ($\alpha = 1$) in Table \ref{tab:bestfitlensmodel}; the red dashed and dash-dotted lines are best fit lens models found analogously from the image positions, but for a fixed rotation curve slope of $\alpha = 1.1$ and $0.9$, respectively.
-For the JAM modelling best fit MGEs to the lens mass models were used, as well as the observed surface brightness MGE in Table \ref{tab:MGEF814W}, assuming velocity isotropy $\beta_z = 0$ and an inclination of $\iota = 70^\circ$.
+The red solid line corresponds to the lens model for a flat rotation curve ($\alpha = 1$) in Table \ref{tab:bestfitlensmodel}; the red dashed and dash-dotted lines are the best-fitting lens models found analogously from the image positions, but for a fixed rotation curve slope of $\alpha = 1.1$ and $0.9$, respectively.
+For the JAM modelling, best-fitting MGEs to the lens mass models were used, as well as the observed surface brightness MGE in Table \ref{tab:MGEF814W}, assuming velocity isotropy $\beta_z = 0$ and an inclination of $\iota = 70^\circ$.
 The most reliable constraints are around the Einstein radius (vertical red dotted line); outside of it the model is just an extrapolation.}
@@
 %--------------------------------------------
-\subsubsection{Comparison with light distribution} \label{sec:results_lensing_compare}
-%--------------------------------------------
-
-%--------------------------------------------
-The surface mass distribution as predicted by the best fit lens model (Table \ref{tab:bestfitlensmodel}) is shown in Figure \ref{fig:lenscomparemass}.
+\subsubsection{Comparison with the light distribution} \label{sec:results_lensing_compare}
+%--------------------------------------------
+
+%--------------------------------------------
+The surface mass distribution as predicted by the best-fitting lens model (Table \ref{tab:bestfitlensmodel}) is shown in Figure \ref{fig:lenscomparemass}.
 We visualize the effect of the Fourier shape parameter uncertainties by introducing random noise to create a mock observation.
@@
 We estimate the total (projected) mass-to-light ratio within the Einstein radius $\Upsilon_\text{I,tot}^\text{ein} \equiv M_\text{ein} / L_\text{I,ein}$.
-For this, we integrate the MGE in Table \ref{tab:MGEF814W} to get the total I-band luminosity within the Einstein radius $L_\text{I,ein} = 1.40 \times 10^{10} L_\odot$.
+For this, we integrate the MGE in Table \ref{tab:MGEF814W} to get the total $I$-band luminosity within the Einstein radius $L_\text{I,ein} = 1.40 \times 10^{10} L_\odot$.
 The corresponding Einstein mass-to-light ratio is therefore $\Upsilon_\text{I,tot}^\text{ein} = 5.56 \Upsilon_{I,\odot}$.
@@
   \includegraphics[height=6cm]{fig/jam_A2_vrms.ps}
-  \caption{Comparison of the symmetrized $v_\text{rms}$ data of J1331 (blue dots) with a best fit dynamical JAM model (orange line) assuming ``mass-follows-light'' and with two free parameters: $\Upsilon_\text{I,tot}^\text{dyn}$, the total constant I-band mass-to-light ratio which converts the observed surface brightness in Table \ref{tab:MGEF814W} into a mass distribution, and the velocity anisotropy parameter $\beta_z$.
+  \caption{Comparison of the symmetrized $v_\text{rms}$ data of J1331 (blue dots) with a best-fitting dynamical JAM model (orange line) assuming ``mass-follows-light'' and with two free parameters: $\Upsilon_\text{I,tot}^\text{dyn}$, the total constant $I$-band mass-to-light ratio which converts the observed surface brightness in Table \ref{tab:MGEF814W} into a mass distribution, and the velocity anisotropy parameter $\beta_z$.
 The ``best'' fit is $\Upsilon_\text{I,tot}^\text{dyn} = 4.8 \pm 0.1$ and $\beta_z = -0.5$, where the latter is however pegged at the lower limit of the allowed value range.
@@
   \includegraphics[height=6cm]{fig/jam_G_vrms.ps}
-  \caption{Comparison of $v_\text{rms}$ data and best fit model.}
+  \caption{Comparison of $v_\text{rms}$ data and best-fitting model.}
   \label{fig:JAM_modelG}
@@
 The $\Upsilon_{\text{I,tot,}i}$ were treated as free fit parameters.
-\emph{Panel (a):} Comparison between the stellar $v_\text{rms}$ data (blue dots) and the best fit model (green line).
-\emph{Panel (b):} Projected total mass-to-light profile $\Upsilon_\text{I,tot}(R')$ along the major axis (blue line, left axis) of the best fit model.
-The best fit mass-to-light ratios $\Upsilon_{\text{I,tot,}i}$ are plotted against $\sigma_i$ for each MGE Gaussian ($i<5$, yellow stars).
+\emph{Panel (a):} Comparison between the stellar $v_\text{rms}$ data (blue dots) and the best-fitting model (green line).
+\emph{Panel (b):} Projected total mass-to-light profile $\Upsilon_\text{I,tot}(R')$ along the major axis (blue line, left axis) of the best-fitting model.
+The best-fitting mass-to-light ratios $\Upsilon_{\text{I,tot,}i}$ are plotted against $\sigma_i$ for each MGE Gaussian ($i<5$, yellow stars).
 (The Gaussians $i=4$ and $i=5$ have the same $\Upsilon_{\text{I,tot,}i}$.) Shown is also the enclosed mass inside the projected radius $R'$ on the sky, $M(<R')$ (green line, right axis).
@@
 \includegraphics[width=0.9\linewidth]{fig/B4_contour_plot_short.ps}
-\caption{Posterior probability distribution (pdf) sampled with a Monte Carlo Markov Chain (MCMC) (red dots and histograms) for a JAM model fitted to the stellar $v_\text{rms}$ data, with NFW halo, parametrized by $r_s$ and $v_\text{200}$, a stellar mass distribution generated from the I-band MGE in Table \ref{tab:MGEF814W} and a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and constant velocity anisotropy $\beta_z$.
+\caption{Posterior probability distribution (pdf) sampled with a Monte Carlo Markov Chain (MCMC) (red dots and histograms) for a JAM model fitted to the stellar $v_\text{rms}$ data, with NFW halo, parametrized by $r_{\rm s}$ and $v_\text{200}$, a stellar mass distribution generated from the $I$-band MGE in Table \ref{tab:MGEF814W} and a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and constant velocity anisotropy $\beta_z$.
 Shown are also the priors used for J1331's NFW halo, $\mathscr{N}(200~\text{km s}^{-1},40~\text{km s}^{-1})$ (green, see Equation \eqref{eq:prior_v200}) and the concentration vs.
 halo mass relation by \citet{Maccio08} from Equation \eqref{eq:Maccio08} in terms of $v_{200}$ vs.
-$r_s$ with $1\sigma$ scatter (blue, see Equation \eqref{eq:prior_c200}).
-We find slight covariances between $\Upsilon_\text{I,*}$,  $r_s$ and $\beta_z$: The smaller the DM contribution in the center (i.e., the larger $\Upsilon_\text{I,*}$), the less concentrated is the halo (i.e., the larger $r_s$) and the more velocity anisotropy is needed to reproduce the central $v_\text{rms}$ dip.
-As the effect of $v_{200}$ is mostly at larger radii, this parameter doesn't show any covariances, but is also mostly constrained by the prior.
+$r_{\rm s}$ with $1\sigma$ scatter (blue, see Equation \eqref{eq:prior_c200}).
+We find slight covariances between $\Upsilon_\text{I,*}$,  $r_{\rm s}$ and $\beta_z$: The smaller the DM contribution in the center (i.e., the larger $\Upsilon_\text{I,*}$), the less concentrated is the halo (i.e., the larger $r_{\rm s}$) and the more velocity anisotropy is needed to reproduce the central $v_\text{rms}$ dip.
+As the effect of $v_{200}$ is mostly at larger radii, this parameter does not show any covariances, but is also mostly constrained by the prior.
 The MCMC samples are colour coded according to their probability (darker red for higher probability); the sample point with the highest probability is marked by a black diamond.
@@
   \includegraphics[width=0.9\linewidth]{fig/B4_rms_error_curves.ps}
-  \caption{Comparison of the $v_\text{rms}$ data with the best fit JAM models.}
+  \caption{Comparison of the $v_\text{rms}$ data with the best-fitting JAM models.}
   \label{fig:modelB4_vrms}
@@
   \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_projmass.ps}
-  \caption{Enclosed mass profiles for the best fit models.}
+  \caption{Enclosed mass profiles for the best-fitting models.}
   \label{fig:modelB4_enclMass}
 \end{subfigure}
-\caption{JAM model including a NFW halo and constant velocity anisotropy fitted to the stellar $v_\text{rms}$ data (blue solid dots) within $\sim3.5''$ and the Einstein mass (red solid dot).
+\caption{JAM model including an NFW halo and constant velocity anisotropy fitted to the stellar $v_\text{rms}$ data (blue solid dots) within $\sim3.5''$ and the Einstein mass (red solid dot).
 The 12 lines shown correspond to 12 models randomly drawn from the pdf (marked as grey diamonds in Figure \ref{fig:modelB4_triangle}) and their range demonstrates how tight the modelling constraints are.
 The mean and standard deviation of the pdf, i.e., the "best fit" parameters, are given in Table \ref{tab:modelB4_bestfit}.
-\emph{Panel (a):} At $R'\lesssim 3.5''$ the symmetrized $v_\text{rms}$ data used in the fit (solid blue points) is shown together with the best fit $v_\text{rms}$ models (red solid lines).
-At larger radii the non-symmetrized data (open blue dots) is compared to an extrapolation of the best fit models using the surface brightness MGE for the outer regions from Figure \ref{fig:MGEouterRegions} (red dashed lines).
+\emph{Panel (a):} At $R'\lesssim 3.5''$ the symmetrized $v_\text{rms}$ data used in the fit (solid blue points) is shown together with the best-fitting $v_\text{rms}$ models (red solid lines).
+At larger radii the non-symmetrized data (open blue dots) is compared to an extrapolation of the best-fitting models using the surface brightness MGE for the outer regions from Figure \ref{fig:MGEouterRegions} (red dashed lines).
 \emph{Panel (b):} Shown is the projected enclosed mass profile of the total mass (green), and separately the contribution of the stellar mass (yellow, again generated from the MGE in Table \ref{tab:MGEF814W}) and DM (grey).
@@
 \hline
-stellar I-band mass-to-light ratio & $\Upsilon_\text{I,*}$ & 4.2 & $\pm$ & 0.2\\
+stellar $I$-band mass-to-light ratio & $\Upsilon_\text{I,*}$ & 4.2 & $\pm$ & 0.2\\
 velocity anisotropy & $\beta_z$ & -0.4 & $\pm$ & 0.1 \\
-NFW halo scale length & $r_s$ [kpc] & 40 & $\pm$ & 20\\
+NFW halo scale length & $r_{\rm s}$ [kpc] & 40 & $\pm$ & 20\\
 NFW halo virial velocity & $v_{200}$ [$\text{km s}^{-1}$] & 240 & $\pm$ & 40\\
@@
 \end{tabular}
-\caption{Summary of the best fit parameters of the JAM model with NFW halo and constant velocity anisotropy, fitted to the $v_\text{rms}$ data within $\sim 3.5''$ and the Einstein mass $\pm10\%$.
+\caption{Summary of the best-fitting parameters of the JAM model with NFW halo and constant velocity anisotropy, fitted to the $v_\text{rms}$ data within $\sim 3.5''$ and the Einstein mass $\pm10\%$.
 These estimates correspond to the mean and standard deviation of the pdf in Figure \ref{fig:modelB4_triangle}.
-The halo mass and concentration are calculated from the the best fit $r_s$ and $v_{200}$.}
+The halo mass and concentration are calculated from the the best-fitting $r_{\rm s}$ and $v_{200}$.}
 \label{tab:modelB4_bestfit}
@@
 %--------------------------------------------
-In Section \ref{sec:results_lensing_compare} we found from lensing constraints, that the light distribution might drop faster with radius than the mass distribution.
+In Section \ref{sec:results_lensing_compare} we found from lensing constraints that the light distribution might drop faster with radius than the mass distribution.
 This could correspond to a radially increasing total mass-to-light ratio.
 As velocity anisotropy alone cannot explain the observed kinematics in a simple mass-follows-light model, we now allow for a mass-to-light ratio gradient in the JAM modelling.
-We therefore generate a mass model from the light distribution in Table \ref{tab:MGEF814W} by assigning each of the five Gaussians in the MGE its own total mass-to-light ratio $\Upsilon_{\text{I,tot,}i}$ and replace the total luminosity in Equation \eqref{eq:centralItotalL} $L_i$ with the Gaussians total mass $M_i = \Upsilon_{\text{I,tot,}i} \times L_i$.
+We therefore generate a mass model from the light distribution in Table \ref{tab:MGEF814W} by assigning each of the five Gaussians in the MGE its own total mass-to-light ratio $\Upsilon_{\text{I,tot,}i}$ and replace the total luminosity in Equation \eqref{eq:centralItotalL}, $L_i$, with the Gaussians total mass $M_i = \Upsilon_{\text{I,tot,}i} \times L_i$.
 We treat the five $\Upsilon_{\text{I,tot,}i}$ as free fit parameters and only require that $\Upsilon_{\text{I,tot,}j} \geq \Upsilon_{\text{I,tot,}i}$ when the corresponding $\sigma_j \geq \sigma_i$ to ensure that the overall mass-to-light ratio is increasing with radius.
 
-Figure \ref{fig:enclMass_modelG} shows the best fit (projected local) mass-to-light ratio profile, which rises from $\Upsilon_\text{I,tot} = 2.53$ in the center and approaches a value of $\Upsilon_\text{I,tot} = 7.60$ outside of the fitted region at $R'\gtrsim 3''$.
+Figure \ref{fig:enclMass_modelG} shows the best-fitting (projected local) mass-to-light ratio profile, which rises from $\Upsilon_\text{I,tot} = 2.53$ in the center and approaches a value of $\Upsilon_\text{I,tot} = 7.60$ outside of the fitted region at $R'\gtrsim 3''$.
 The central mass-to-light ratio is in agreement with the mass-to-light ratio $\Upsilon_\text{I,*}^\text{chab} = 2.5 \pm 0.6$, given in Table \ref{tab:previousresults} based on the results of \citet{SWELLSI} assuming a stellar population with a \citet{Chabrier2003} IMF (see also Section \ref{sec:MLdiscussion}).
@@
 
-Figure \ref{fig:JAM_modelG} shows that the best fit model nicely reproduces the central dip in the $v_\text{rms}$ curve, even though it has difficulties fitting the drop around $R' \sim 4''$.
+Figure \ref{fig:JAM_modelG} shows that the best-fitting model nicely reproduces the central dip in the $v_\text{rms}$ curve, even though it has difficulties fitting the drop around $R' \sim 4''$.
 The latter is because we only allowed the $\Upsilon_\text{I,tot}(R')$ to rise.
 A slight drop could be expected when the reddish bulge turns into the bluish disk and the contribution of the stellar component becomes less due to a lower $\Upsilon_\text{I,*}$ for younger and bluer populations.
-Corresponding fitting attempts with the matter model at hand were however unsuccessful: Leaving all five $\Upsilon_{\text{I,tot,}i}$ free lead to over-fitting in the central regions of J1331, while not allowing for sufficient flexibility further out at $R'\gtrsim4''$ (because four of the five $\sigma_i$ in the light MGE in Table \ref{tab:MGEF814W} are $< 1.2''$) to properly model the transition from bulge to disk.
+Corresponding fitting attempts with the matter model at hand were however unsuccessful: Leaving all five $\Upsilon_{\text{I,tot,}i}$ free lead to over-fitting in the central regions of J1331, while not allowing for sufficient flexibility further out at $R'\gtrsim4''$ to properly model the transition from bulge to disk (because four of the five $\sigma_i$ in the light MGE in Table \ref{tab:MGEF814W} are $< 1.2''$).
 
@@
 %--------------------------------------------
-\subsection{JAM with a NFW dark matter halo} \label{sec:results_JAM_NFW}
+\subsection{JAM with an NFW dark matter halo} \label{sec:results_JAM_NFW}
 %--------------------------------------------
@@
 \includegraphics[width=\linewidth]{fig/B4_rms_rot_curves_best_model.ps}
-\caption{Generating the rotation curve $v_\text{rot}(R')$ (red solid line in middle panel) from the best fit JAM model with NFW halo by fitting the rotation parameter $\kappa'$ to the symmetrized $v_\text{rot}$ data within $R'\sim3.5''$ (solid blue dots in central panel).
+\caption{Generating the rotation curve $v_\text{rot}(R')$ (red solid line in middle panel) from the best-fitting JAM model with NFW halo by fitting the rotation parameter $\kappa'$ to the symmetrized $v_\text{rot}$ data within $R'\sim3.5''$ (solid blue dots in central panel).
 The first panel shows the $v_\text{rms}$ data and model analogous to Figure \ref{fig:modelB4_vrms} for the mean parameters in Table \ref{tab:modelB4_bestfit}.
-The second panel shows the corresponding $v_\text{rot}$ for the best fit rotation parameter $\kappa' = 0.76$ in Equation \eqref{eq:kappa_profile} (red solid lines).
+The second panel shows the corresponding $v_\text{rot}$ for the best-fitting rotation parameter $\kappa' = 0.76$ in Equation \eqref{eq:kappa_profile} (red solid lines).
 The third panel shows simply the velocity dispersion $\sigma = \sqrt{v_\text{rms}^2 - v_\text{rot}^2}$.
@@
 %--------------------------------------------
-We proceed by modelling the mass distribution with (i) a stellar component, which we get from the light MGE in Table \ref{tab:MGEF814W} (deprojected to the intrinsic $\nu(R,z)$ using the fixed inclination angle $\iota=70^\circ$ in Table \ref{tab:galaxyparameters}) times a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and (ii) a spherical NFW DM component (see Section \ref{sec:model_JAM_NFW}) with halo scale length $r_s$ and circular velocity $v_{200}$ at the virial radius as free parameters.
+We proceed by modelling the mass distribution with (i) a stellar component, which we get from the light MGE in Table \ref{tab:MGEF814W} (deprojected to the intrinsic $\nu(R,z)$ using the fixed inclination angle $\iota=70^\circ$ in Table \ref{tab:galaxyparameters}) times a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and (ii) a spherical NFW DM component (see Section \ref{sec:model_JAM_NFW}) with halo scale length $r_{\rm s}$ and circular velocity $v_{200}$ at the virial radius as free parameters.
 In the JAM modelling we use a 10-Gaussian MGE fit to the classical NFW profile from Equation \eqref{eq:NFWprofile}.
 
-The full set of fit parameters is $(\Upsilon_\text{I,*},r_s,v_{200},\beta_z)$, where $\beta_z$ is again the constant velocity anisotropy parameter.
-We will investigate this parameter space with a Monte Carlo Markov Chain (MCMC)\footnote{The Python code package for \emph{emcee}, a Monte Carlo Markov Chain implementation by \citet{emcee} is available online at \url{http://dan.iel.fm/emcee/current/}.
-The version from October 2013 was used in this work.} \citep{emcee} and use priors for the halo parameters to guide the fit to a realistic NFW halo shape.
+The full set of fit parameters is $(\Upsilon_\text{I,*},r_{\rm s},v_{200},\beta_z)$, where $\beta_z$ is again the constant velocity anisotropy parameter.
+We will investigate this parameter space with a Monte Carlo Markov Chain (MCMC; using code\footnote{The Python code package for \emph{emcee}, a Monte Carlo Markov Chain implementation by \citet{emcee}, is available online at \url{http://dan.iel.fm/emcee/current/}.
+The version from October 2013 was used in this work.} by\citealt{emcee}).
 
@@
 The constraints on a DM halo just from this data might be weak.
-To guide the fit towards a realistic halo, we therefore impose several priors on NFW halo.
+To guide the fit towards a realistic NFW halo shape, we therefore impose several priors on the NFW halo.
 
@@
 \begin{equation}
-p(\log c_{200} \mid v_{200}) = \mathscr{N}\left(\langle \log c_{200} \rangle (M_{200}) \mid 0.105 \right). \label{eq:prior_c200}
+p(\log c_{200} \mid v_{200}) = \mathscr{N}\left(\langle \log c_{200} \rangle (M_{200}) , 0.105 \right). \label{eq:prior_c200}
 \end{equation}
@@
 \begin{split}
-&p(\Upsilon_\text{I,*},r_s,v_{200},\beta_z) \\
-&= \frac{1}{\ln\left( 10 r_s\right)} p(\log c_{200} \mid v_{200}) \times p(v_{200}) \times p(\beta_z), 
+&p(\Upsilon_\text{I,*},r_{\rm s},v_{200},\beta_z) \\
+&= \frac{1}{\ln\left( 10 r_{\rm s}\right)} p(\log c_{200} \mid v_{200}) \times p(v_{200}) \times p(\beta_z), 
 \end{split}
 \end{align}
-where the factor $1/\ln\left( 10 r_s\right)$ is the Jacobian of the transformation from the halo parameters $(v_{200},\log c_{200})$ to the fit parameters $(v_{200},r_s)$.
+where the factor $1/\ln\left( 10 r_{\rm s}\right)$ is the Jacobian of the transformation from the halo parameters $(v_{200},\log c_{200})$ to the fit parameters $(v_{200},r_{\rm s})$.
 
@@
 %--------------------------------------------
-\subsubsection{Best fit JAM model} \label{sec:results_JAM_NFW_results}
+\subsubsection{Best-fitting JAM model} \label{sec:results_JAM_NFW_results}
 %--------------------------------------------
@@
 The mean parameters are summarized in Table \ref{tab:modelB4_bestfit}.
-We find that the best fit NFW halo strives to be more massive and with a higher concentration (due to a smaller $r_s$) than  proposed by the priors.
+We find that the best-fitting NFW halo strives to be more massive and with a higher concentration (due to a smaller $r_{\rm s}$) than  proposed by the priors.
 The model also prefers  very negative velocity anisotropies.
 Both, the high halo concentration and low $\beta_z$, are needed to reproduce the central dip of the $v_\text{rms}$ curve.
-Figure \ref{fig:modelB4_models} illustrates the range of best fit models according to the extent of the pdf.
+Figure \ref{fig:modelB4_models} illustrates the range of best-fitting models according to the extent of the pdf.
 The models fit the $v_\text{rms}$ data in the inner regions quite well (Figure \ref{fig:modelB4_vrms}) and are also consistent with the Einstein mass (see Figure \ref{fig:modelB4_enclMass}).
@@
 \centering
-\caption{Total I-band luminosity, stellar mass and mass-to-light ratio, calculated from the I-band AB magnitudes and stellar masses found for J133's bulge and disk by \citet{SWELLSI} (their table 2) for comparison with this work.
-The transformation from AB magnitudes to the Johnson-Cousins I-Band used the relation $I[\text{mag}] = I[\text{ABmag}] - 0.309$ from \citet{FG1994} (their table 2).
+\caption{Total $I$-band luminosity, stellar mass and mass-to-light ratio, calculated from the $I$-band AB magnitudes and stellar masses found for J1331's bulge and disk by \citet{SWELLSI} (their table 2) for comparison with this work.
+The transformation from AB magnitudes to the Johnson-Cousins $I$-band used the relation $I[\text{mag}] = I[\text{ABmag}] - 0.309$ from \citet{FG1994} (their table 2).
 For the conversion from apparent magnitude to total luminosity the redshift $z=0.113$ \citet{SWELLSIII} was turned into a luminosity distance using the WMAP5 cosmology by \citet{WMAP5cosm}.
@@
 %--------------------------------------------
-We generate a rotation curve from the best fit mean model in Table \ref{tab:modelB4_bestfit}, whose $v_\text{rms}$ curve is shown in the first panel of Figure \ref{fig:modelB4_vrot}.
+We generate a rotation curve from the best-fitting mean model in Table \ref{tab:modelB4_bestfit}, whose $v_\text{rms}$ curve is shown in the first panel of Figure \ref{fig:modelB4_vrot}.
 Following the procedure in Section \ref{sec:model_JAM_rotation}, we find the rotation curve by fitting the rotation parameter $\kappa'$ to the symmetrized $v_\text{rot}$ data within $R' = 3.5''$.
@@
 
-While the dispersion $\sigma$ in the center fits by construction quite good, the predicted dispersion is much larger than the data.
+While the dispersion $\sigma$ in the center fits by construction quite good, the extrapolated dispersion is much larger than the data.
 We would expect the disk to be rotationally supported and therefore have a low velocity dispersion.
 Especially dispersions as high as $\sim 200~\text{km s}^{-1}$ are more likely to be observed in the pressure supported bulges of galaxies.
-There might be something unexpected with the $\sigma$ measurements around $\sim 5''$, but at large radii the best fit model NFW halo is simply too massive.
+There might be something unexpected with the $\sigma$ measurements around $\sim 5''$, but at large radii the best-fitting model NFW halo is simply too massive.
 
@@
 The cored halo models are in general slightly less massive than the NFW halo and therefore fit the outer regions of J1331 better.
-However, the density profile of the cored halo as well as the I-band light distribution within the plane drop as $\rho(r) \propto r^{-2}$.
+However, the density profile of the cored halo as well as the $I$-band light distribution within the plane drop as $\rho(r) \propto r^{-2}$.
 There is therefore a strong degeneracy between the stellar mass and the DM.
@@
 A fit to all nine available $v_\text{rms}$ data points would force the DM halo to be less massive.
-But with decreasing DM contribution in the inner regions the model approaches the mass-follows-light model in the center, that we already ruled out in Section \ref{sec:results_JAM_SB_MfL}.
-Allowing for free $\Upsilon_\text{I,*}(R')$, $\beta_z(R')$ and more flexible $\rho_\text{halo}(r)$ profiles, which would be the reasonable next step, would over-fit the data.
+But with decreasing DM contribution in the inner regions the model approaches the mass-follows-light model in the center that we already ruled out in Section \ref{sec:results_JAM_SB_MfL}.
+Allowing for free $\Upsilon_\text{I,*}(R')$, $\beta_z(R')$, and more flexible $\rho_\text{halo}(r)$ profiles, which would be the reasonable next step, would over fit the data.
 Without further priors on the stellar $\Upsilon_\text{I,*}(R')$ or more data points, we can make only the following statement: A model with constant $\Upsilon_\text{I,*} = 4.2\pm 0.2$, moderately tangential $\beta_z = -0.4\pm 0.1$ and a spherical and massive DM component with high concentration ($c_\text{200}=8\pm 2$) can explain the central kinematics of J1331 very well.
-We have however ruled out that in this case the DM halo will follow a NFW halo profile at both small and large radii.
+We have however ruled out that in this case the DM halo will follow an NFW halo profile at both small and large radii.
 
@@
 \citet{Ferreras} found a relation between the central stellar velocity dispersion $\sigma_0$ in early-type galaxies and the IMF slope $x$, where a higher $\sigma_0$ suggests a more bottom-heavy IMF.
-For a unimodal (Salpeter-like) IMF and $\sigma_0 \simeq 200~\text{km s}^{-1}$ in J1331 (see Figure \ref{fig:kinematics}) this relation predicts $x \approx 2.33$, which is close to the standard Salpeter slope, also supported by \citet{2014MNRAS.438.1483S}.
+For a unimodal (Salpeter-like) IMF and $\sigma_0 \simeq 200~\text{km s}^{-1}$ in J1331 (see Figure \ref{fig:kinematics}), this relation predicts $x \approx 2.33$, which is close to the standard Salpeter slope, also supported by \citet{2014MNRAS.438.1483S}.
 When assuming a bi-modal (Kroupa-equivalent-like) IMF, \citet{Ferreras} predict $x \approx 2.85$ for J1331's central velocity dispersion.
@@
 
-\citet{SWELLSI} estimated J1331's stellar bulge mass given a Salpeter IMF and measured the I-band AB magnitude of the bulge.
-Transformed to a stellar I-band mass-to-light ratio, their results would correspond to $\Upsilon_\text{I,*}^\text{sal} = 4.7 \pm 1.2$ (see Table \ref{tab:previousresults}).
-This is not too far from $\Upsilon_\text{I,*} = 4.2 \pm 0.2$ (see Table \ref{tab:modelB4_bestfit}), which we found when including a NFW halo in the JAM modelling.
+\citet{SWELLSI} estimated J1331's stellar bulge mass given a Salpeter IMF and measured the $I$-band AB magnitude of the bulge.
+Transformed to a stellar $I$-band mass-to-light ratio, their results would correspond to $\Upsilon_\text{I,*}^\text{sal} = 4.7 \pm 1.2$ (see Table \ref{tab:previousresults}).
+This is not too far from $\Upsilon_\text{I,*} = 4.2 \pm 0.2$ (see Table \ref{tab:modelB4_bestfit}), which we found when including an NFW halo in the JAM modelling.
 
@@
 When \citet{SWELLSI} assumed a Chabrier IMF, their result translates to $\Upsilon_\text{I,*}^\text{chab} = 2.5 \pm 0.6$ (see Table \ref{tab:previousresults}).
-In Section \ref{sec:results_JAM_SB_gradient} we created a dynamical model from only the surface brightness distribution and an increasing mass-to-light ratio profile without additional DM halo and without velocity anisotropy.
+In Section \ref{sec:results_JAM_SB_gradient}, we created a dynamical model from only the surface brightness distribution and an increasing mass-to-light ratio profile without additional DM halo and without velocity anisotropy.
 We found that such a model would be perfectly consistent with the Einstein mass, predict a total $\Upsilon_\text{I,tot}(R'\sim0) = 2.53$---being consistent with the Chabrier IMF estimate by \citet{SWELLSI}---and rise quickly to $\Upsilon_\text{I,tot}(R'\gtrsim R_\text{ein}) \gtrsim 6$.
@@
 Our fitting attempt---using more data within $\sim 3.5''$ than \citet{SWELLSV}---in Section \ref{sec:results_JAM_NFW} gave $\Upsilon_\text{I,*} = 4.2 \pm 0.2$ as best fit (see Table \ref{tab:modelB4_bestfit}), which indicates a \emph{less} bottom-heavy IMF than the Salpeter IMF.
-In Section \ref{sec:discussion_kinematics} we will argue why we do not think that the \cite{SWELLSV} model is a good model for the central regions of J1331.
+In Section \ref{sec:discussion_kinematics}, we will argue why we do not think that the \cite{SWELLSV} model is a good model for the central regions of J1331.
 %--------------------------------------------
@@
 Overall, the kinematics of the merger remnant J1331 are peculiar.
-In particular there are two features in the $v_\text{rms}$ curve that are hard to explain with standard modelling techniques.
+In particular, there are two features in the $v_\text{rms}$ curve that are hard to explain with standard modelling techniques.
 The first feature, the deep central $v_\text{rms}$ dip, was studied in detail in this work.
@@
 Because we used more data constraints in the center than \citet{SWELLSV}, we think that our model for J1331's bulge is more reliable.
-In conclusion we suspect that the most likely model for J1331's central bulge is a moderate DM contribution in the center (Section \ref{sec:results_JAM_NFW_results}) with some tangential anisotropy (Sections \ref{sec:results_JAM_SB_MfL} and \ref{sec:results_JAM_NFW}, which would be also consistent with the counter-rotation in the bulge) and an overall $\Upsilon_\text{*,I}$ in the bulge which is slightly lower than that of a Salpeter-like IMF (Section \ref{sec:MLdiscussion}).
+In conclusion, we suspect that the most likely model for J1331's central bulge is a moderate DM contribution in the center (Section \ref{sec:results_JAM_NFW_results}) with some tangential anisotropy (Sections \ref{sec:results_JAM_SB_MfL} and \ref{sec:results_JAM_NFW}, which would be also consistent with the counter-rotation in the bulge) and an overall $\Upsilon_\text{*,I}$ in the bulge which is slightly lower than that of a Salpeter-like IMF (Section \ref{sec:MLdiscussion}).
 Different stellar populations inside the bulge due to the merger (Section \ref{sec:discussion_merger}) with different $\Upsilon_{*}$ could add to an overall rising $\Upsilon_\text{tot}(R')$ profile (Sections \ref{sec:results_lensing_compare} and \ref{sec:results_JAM_SB_gradient}).
@@
 The DM halo should start to dominate the kinematics at larger radii.
-\cite{SWELLSV}, who fitted a NFW halo to the gas kinematics in the outer regions, found lower halo masses ($v_\text{circ,halo}(5'') \sim 120~\text{km s}^{-1}$ according to their Figure 2) than we did ($v_\text{circ,halo}(5'') \sim 200~\text{km s}^{-1}$, Figure \ref{fig:vcirc_comparison}).
+\cite{SWELLSV}, who fitted an NFW halo to the gas kinematics in the outer regions, found lower halo masses ($v_\text{circ,halo}(5'') \sim 120~\text{km s}^{-1}$ according to their Figure 2) than we did ($v_\text{circ,halo}(5'') \sim 200~\text{km s}^{-1}$, Figure \ref{fig:vcirc_comparison}).
 As we did not fit the outer regions and only used a prior for $v_\text{200}$, their result in this regime is more reliable.
-Given our findings that a NFW halo does not fit the kinematics at both small and large radii, we suspect that the true halo has a profile that deviates strongly from a NFW halo, possibly as a result of the merger.
+Given our findings that an NFW halo does not fit the kinematics at both small and large radii, we suspect that the true halo has a profile that deviates strongly from an NFW halo, possibly as a result of the merger.
 
@@
 To also model the extent, shape and flux of the lensing images, the method by \citet{2004ApJ...611..739T,2003ApJ...590..673W} could be employed, which models the surface brightness distribution of the images and source on a pixelated grid.
-For this to work a good model for the galactic extinction would be needed---but 2D spectroscopy could also help with this.
+For this to work, a good model for the galactic extinction would be needed---but 2D spectroscopy could also help with this.
 
@@
 We used two independent methods to model J1331: gravitational lensing and dynamical Jeans modelling.
-We focussed on the bulge region of J1331 to complement previous studies of J1331 by \citet{SWELLSIII} and \citet{SWELLSV}.
+We focused on the bulge region of J1331 to complement previous studies of J1331 by \citet{SWELLSIII} and \citet{SWELLSV}.
 The mass constraints from lensing and dynamics agree very well with each other within $R_\text{eff}$.
@@
 
-A MGE fit to J1331's surface brightness in the F814W filter in HST imaging by \citet{SWELLSI} helped us determining the effective radius, $R_\text{eff} \simeq 2.6'' \hat{=} 5.2~\text{kpc}$, and total I-band luminosity of the galaxy, $L_\text{I,tot} \simeq 5.6 \times 10^{10} L_\odot$.
+A MGE fit to J1331's surface brightness in the F814W filter in HST imaging by \citet{SWELLSI} helped us determining the effective radius, $R_\text{eff} \simeq 2.6'' \hat{=} 5.2~\text{kpc}$, and total $I$-band luminosity of the galaxy, $L_\text{I,tot} \simeq 5.6 \times 10^{10} L_\odot$.
 
@@
 We speculate how a merger could have modified the kinematic structure and/or mass distribution of J1331.
-To resolve the ambiguities in J1331's mass distribution 2-dimensional kinematic maps of J1331 from integral-field unit spectroscopy are needed.
-%--------------------------------------------
+To resolve the ambiguities in J1331's mass distribution two-dimensional kinematic maps of J1331 from integral-field unit spectroscopy are needed.
+%--------------------------------------------
+
+\section*{Acknowledgements}
+
+The authors thank Tommaso Treu and the SWELLS team for their support, and the anonymous referee for their helpful comments.
+WHT thanks the Department of Physics and Astronomy at the University of Heidelberg for awarding this research with the Otto-Haxel-Prize for an outstanding master's thesis.
+GvdV acknowledges partial support from Sonderforschungsbereich SFB 881 "The Milky Way System" (subproject A7 and A8) funded by the German Research Foundation, and from the DAGAL network from the People Programme (Marie Curie Actions) of the European Union's Seventh Framework Programme FP7/2007-2013/ under REA grant agreement number PITN-GA-2011-289313.
 

### 2016-09-18 uploaded_to_arXiv_16-09-18/Trick_J1331_Modelling_ARXIV.tex
Started version to be uploaded to arXiv

--- 2016-09-18 LensingPaper_draft_v4.04.tex
@@
 \centering
-  \includegraphics[width=\linewidth]{fig/lens_all_in_one.ps}
+  \includegraphics[width=\linewidth]{lens_all_in_one.ps}
 \caption{Lensing model (in Table \ref{tab:bestfitlensmodel}) found as best fit to the lensing image positions.
@@
   \centering
-  \includegraphics[height=6cm]{fig/jam_A2_vrms.ps}
+  \includegraphics[height=6cm]{jam_A2_vrms.ps}
   \caption{Comparison of the symmetrized $v_\text{rms}$ data of J1331 (blue dots) with a best-fitting dynamical JAM model (orange line) assuming ``mass-follows-light'' and with two free parameters: $\Upsilon_\text{I,tot}^\text{dyn}$, the total constant $I$-band mass-to-light ratio which converts the observed surface brightness in Table \ref{tab:MGEF814W} into a mass distribution, and the velocity anisotropy parameter $\beta_z$.
@@
   \centering
-  \includegraphics[height=6cm]{fig/jam_G_vrms.ps}
+  \includegraphics[height=6cm]{jam_G_vrms.ps}
   \caption{Comparison of $v_\text{rms}$ data and best-fitting model.}
@@
 \centering
-\includegraphics[width=0.9\linewidth]{fig/B4_contour_plot_short.ps}
+\includegraphics[width=0.9\linewidth]{B4_contour_plot_short.ps}
 \caption{Posterior probability distribution (pdf) sampled with a Monte Carlo Markov Chain (MCMC) (red dots and histograms) for a JAM model fitted to the stellar $v_\text{rms}$ data, with NFW halo, parametrized by $r_{\rm s}$ and $v_\text{200}$, a stellar mass distribution generated from the $I$-band MGE in Table \ref{tab:MGEF814W} and a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and constant velocity anisotropy $\beta_z$.
@@
   \centering
-  \includegraphics[width=0.9\linewidth]{fig/B4_rms_error_curves.ps}
+  \includegraphics[width=0.9\linewidth]{B4_rms_error_curves.ps}
   \caption{Comparison of the $v_\text{rms}$ data with the best-fitting JAM models.}
@@
   \centering
-  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_projmass.ps}
+  \includegraphics[width=0.9\linewidth]{B4_jam_profiles_errors_short_projmass.ps}
   \caption{Enclosed mass profiles for the best-fitting models.}
@@
 \centering
-\includegraphics[width=\linewidth]{fig/B4_rms_rot_curves_best_model.ps}
+\includegraphics[width=\linewidth]{B4_rms_rot_curves_best_model.ps}
 \caption{Generating the rotation curve $v_\text{rot}(R')$ (red solid line in middle panel) from the best-fitting JAM model with NFW halo by fitting the rotation parameter $\kappa'$ to the symmetrized $v_\text{rot}$ data within $R'\sim3.5''$ (solid blue dots in central panel).

### 2016-09-18 uploaded_to_arXiv_16-09-18/Trick_J1331_Modelling_ARXIV.tex
Merging problems....

@@
 
+%--------------------------------------------
+\subsection{Surface photometry for J1331 with MGEs} \label{sec:MGE_results}
+%--------------------------------------------
+
+%--------------------------------------------
+In this section we construct a model for J1331's intrinsic light distribution in terms of MGEs (see Section \ref{sec:MGE_theo}).
+We use the HST image in the F814W ($I$-band) filter (Figure \ref{fig:F814W}) because J1331's central stellar component appears at longer wavelengths (i) smoother and more extended than in the F450W filter (Figure \ref{fig:F450W}), as it is less sensitive to young clumpy star-forming regions, (ii) much brighter than the bluish lensing images, and (iii) the imaging is less prone to extinction.
+
 %============================================
@@
 %============================================
-
-%--------------------------------------------
-\subsection{Surface photometry for J1331 with MGEs} \label{sec:MGE_results}
-%--------------------------------------------
-
-%--------------------------------------------
-In this section we construct a model for J1331's intrinsic light distribution in terms of MGEs (see Section \ref{sec:MGE_theo}).
-We use the HST image in the F814W ($I$-band) filter (Figure \ref{fig:F814W}) because J1331's central stellar component appears at longer wavelengths (i) smoother and more extended than in the F450W filter (Figure \ref{fig:F450W}), as it is less sensitive to young clumpy star-forming regions, (ii) much brighter than the bluish lensing images, and (iii) the imaging is less prone to extinction.
 
@@
 
+%--------------------------------------------
+\subsubsection{JAM with increasing mass-to-light ratio} \label{sec:results_JAM_SB_gradient}
+%--------------------------------------------
+
+%--------------------------------------------
+In Section \ref{sec:results_lensing_compare} we found from lensing constraints that the light distribution might drop faster with radius than the mass distribution.
+This could correspond to a radially increasing total mass-to-light ratio.
+As velocity anisotropy alone cannot explain the observed kinematics in a simple mass-follows-light model, we now allow for a mass-to-light ratio gradient in the JAM modelling.
+We therefore generate a mass model from the light distribution in Table \ref{tab:MGEF814W} by assigning each of the five Gaussians in the MGE its own total mass-to-light ratio $\Upsilon_{\text{I,tot,}i}$ and replace the total luminosity in Equation \eqref{eq:centralItotalL}, $L_i$, with the Gaussians total mass $M_i = \Upsilon_{\text{I,tot,}i} \times L_i$.
+We treat the five $\Upsilon_{\text{I,tot,}i}$ as free fit parameters and only require that $\Upsilon_{\text{I,tot,}j} \geq \Upsilon_{\text{I,tot,}i}$ when the corresponding $\sigma_j \geq \sigma_i$ to ensure that the overall mass-to-light ratio is increasing with radius.
+
+Figure \ref{fig:enclMass_modelG} shows the best-fitting (projected local) mass-to-light ratio profile, which rises from $\Upsilon_\text{I,tot} = 2.53$ in the center and approaches a value of $\Upsilon_\text{I,tot} = 7.60$ outside of the fitted region at $R'\gtrsim 3''$.
+The central mass-to-light ratio is in agreement with the mass-to-light ratio $\Upsilon_\text{I,*}^\text{chab} = 2.5 \pm 0.6$, given in Table \ref{tab:previousresults} based on the results of \citet{SWELLSI} assuming a stellar population with a \citet{Chabrier2003} IMF (see also Section \ref{sec:MLdiscussion}).
+When assuming that galaxy bulges are in general older and redder in the center, i.e., $\Upsilon_\text{I,*}$ is more likely to drop with radius than rise, the strong increase of $\Upsilon_\text{I,tot}(R')$ might be due to a strong contribution of DM in J1331.
+
+Figure \ref{fig:JAM_modelG} shows that the best-fitting model nicely reproduces the central dip in the $v_\text{rms}$ curve, even though it has difficulties fitting the drop around $R' \sim 4''$.
+The latter is because we only allowed the $\Upsilon_\text{I,tot}(R')$ to rise.
+A slight drop could be expected when the reddish bulge turns into the bluish disk and the contribution of the stellar component becomes less due to a lower $\Upsilon_\text{I,*}$ for younger and bluer populations.
+Corresponding fitting attempts with the matter model at hand were however unsuccessful: Leaving all five $\Upsilon_{\text{I,tot,}i}$ free lead to over-fitting in the central regions of J1331, while not allowing for sufficient flexibility further out at $R'\gtrsim4''$ to properly model the transition from bulge to disk (because four of the five $\sigma_i$ in the light MGE in Table \ref{tab:MGEF814W} are $< 1.2''$).
+
+For the inner regions the model with rising $\Upsilon(R')$ seems however to be a very good model: In Figure \ref{fig:enclMass_modelG} we overplot the enclosed mass profile with the Einstein mass $M_\text{ein} = (7.77 \pm 0.33) \times 10^{10} \text{M}_\odot$ at the Einstein radius found from lensing in Table \ref{tab:bestfitlensmodel}.
+The agreement between the Einstein mass and the independently found $M(<R_\text{ein}) = 7.49 \times 10^{10} \text{M}_\odot$ from dynamical modelling is striking.
+%--------------------------------------------
+
 %============================================
@@
 %--------------------------------------------
-\subsubsection{JAM with increasing mass-to-light ratio} \label{sec:results_JAM_SB_gradient}
-%--------------------------------------------
-
-%--------------------------------------------
-In Section \ref{sec:results_lensing_compare} we found from lensing constraints that the light distribution might drop faster with radius than the mass distribution.
-This could correspond to a radially increasing total mass-to-light ratio.
-As velocity anisotropy alone cannot explain the observed kinematics in a simple mass-follows-light model, we now allow for a mass-to-light ratio gradient in the JAM modelling.
-We therefore generate a mass model from the light distribution in Table \ref{tab:MGEF814W} by assigning each of the five Gaussians in the MGE its own total mass-to-light ratio $\Upsilon_{\text{I,tot,}i}$ and replace the total luminosity in Equation \eqref{eq:centralItotalL}, $L_i$, with the Gaussians total mass $M_i = \Upsilon_{\text{I,tot,}i} \times L_i$.
-We treat the five $\Upsilon_{\text{I,tot,}i}$ as free fit parameters and only require that $\Upsilon_{\text{I,tot,}j} \geq \Upsilon_{\text{I,tot,}i}$ when the corresponding $\sigma_j \geq \sigma_i$ to ensure that the overall mass-to-light ratio is increasing with radius.
-
-Figure \ref{fig:enclMass_modelG} shows the best-fitting (projected local) mass-to-light ratio profile, which rises from $\Upsilon_\text{I,tot} = 2.53$ in the center and approaches a value of $\Upsilon_\text{I,tot} = 7.60$ outside of the fitted region at $R'\gtrsim 3''$.
-The central mass-to-light ratio is in agreement with the mass-to-light ratio $\Upsilon_\text{I,*}^\text{chab} = 2.5 \pm 0.6$, given in Table \ref{tab:previousresults} based on the results of \citet{SWELLSI} assuming a stellar population with a \citet{Chabrier2003} IMF (see also Section \ref{sec:MLdiscussion}).
-When assuming that galaxy bulges are in general older and redder in the center, i.e., $\Upsilon_\text{I,*}$ is more likely to drop with radius than rise, the strong increase of $\Upsilon_\text{I,tot}(R')$ might be due to a strong contribution of DM in J1331.
-
-Figure \ref{fig:JAM_modelG} shows that the best-fitting model nicely reproduces the central dip in the $v_\text{rms}$ curve, even though it has difficulties fitting the drop around $R' \sim 4''$.
-The latter is because we only allowed the $\Upsilon_\text{I,tot}(R')$ to rise.
-A slight drop could be expected when the reddish bulge turns into the bluish disk and the contribution of the stellar component becomes less due to a lower $\Upsilon_\text{I,*}$ for younger and bluer populations.
-Corresponding fitting attempts with the matter model at hand were however unsuccessful: Leaving all five $\Upsilon_{\text{I,tot,}i}$ free lead to over-fitting in the central regions of J1331, while not allowing for sufficient flexibility further out at $R'\gtrsim4''$ to properly model the transition from bulge to disk (because four of the five $\sigma_i$ in the light MGE in Table \ref{tab:MGEF814W} are $< 1.2''$).
-
-For the inner regions the model with rising $\Upsilon(R')$ seems however to be a very good model: In Figure \ref{fig:enclMass_modelG} we overplot the enclosed mass profile with the Einstein mass $M_\text{ein} = (7.77 \pm 0.33) \times 10^{10} \text{M}_\odot$ at the Einstein radius found from lensing in Table \ref{tab:bestfitlensmodel}.
-The agreement between the Einstein mass and the independently found $M(<R_\text{ein}) = 7.49 \times 10^{10} \text{M}_\odot$ from dynamical modelling is striking.
-%--------------------------------------------
-
-%--------------------------------------------
 \subsection{JAM with an NFW dark matter halo} \label{sec:results_JAM_NFW}
@@
 
+%--------------------------------------------
+\subsubsection{Rotation curve}
+%--------------------------------------------
+
+%--------------------------------------------
+We generate a rotation curve from the best-fitting mean model in Table \ref{tab:modelB4_bestfit}, whose $v_\text{rms}$ curve is shown in the first panel of Figure \ref{fig:modelB4_vrot}.
+Following the procedure in Section \ref{sec:model_JAM_rotation}, we find the rotation curve by fitting the rotation parameter $\kappa'$ to the symmetrized $v_\text{rot}$ data within $R' = 3.5''$.
+The best fit with $\kappa' = 0.76$ is given in the second panel of Figure \ref{fig:modelB4_vrot}.
+The third panel shows the dispersion that follows from $\sigma = \sqrt{v_\text{rms}^2 - v_\text{rot}^2}$.
+Our assumptions for $\kappa(R)$ nicely reproduce a $v_\text{rot}$ model with counter-rotating core.
+Although we fitted $v_\text{rot}$ only to the inner regions, the extrapolation to large radii matches the data also very well.
+
+While the dispersion $\sigma$ in the center fits by construction quite good, the extrapolated dispersion is much larger than the data.
+We would expect the disk to be rotationally supported and therefore have a low velocity dispersion.
+Especially dispersions as high as $\sim 200~\text{km s}^{-1}$ are more likely to be observed in the pressure supported bulges of galaxies.
+There might be something unexpected with the $\sigma$ measurements around $\sim 5''$, but at large radii the best-fitting model NFW halo is simply too massive.
+
+%--------------------------------------------
+
+\subsubsection{Further tests and discussion}
+
+We also fitted a model with a cored logarithmic DM halo.
+The cored halo models are in general slightly less massive than the NFW halo and therefore fit the outer regions of J1331 better.
+However, the density profile of the cored halo as well as the $I$-band light distribution within the plane drop as $\rho(r) \propto r^{-2}$.
+There is therefore a strong degeneracy between the stellar mass and the DM.
+Overall, we were not able to obtain tight constraints on the cored logarithmic halo.
+
+As we only fitted the halo models to the inner regions, it is not surprising that they do not fit the kinematics at larger radii.
+A fit to all nine available $v_\text{rms}$ data points would force the DM halo to be less massive.
+But with decreasing DM contribution in the inner regions the model approaches the mass-follows-light model in the center that we already ruled out in Section \ref{sec:results_JAM_SB_MfL}.
+Allowing for free $\Upsilon_\text{I,*}(R')$, $\beta_z(R')$, and more flexible $\rho_\text{halo}(r)$ profiles, which would be the reasonable next step, would over fit the data.
+Without further priors on the stellar $\Upsilon_\text{I,*}(R')$ or more data points, we can make only the following statement: A model with constant $\Upsilon_\text{I,*} = 4.2\pm 0.2$, moderately tangential $\beta_z = -0.4\pm 0.1$ and a spherical and massive DM component with high concentration ($c_\text{200}=8\pm 2$) can explain the central kinematics of J1331 very well.
+We have however ruled out that in this case the DM halo will follow an NFW halo profile at both small and large radii.
+
+We will also discuss the kinematics at larger radii in more depth in the discussion Section \ref{sec:discussion_kinematics}.
+
+%--------------------------------------------
+\section{Discussion and Conclusion} \label{sec:Discussion}
+%--------------------------------------------
+
+%--------------------------------------------
+We have presented different dynamical models for the central region of J1331.
+Some of them capture the observed kinematics, but none of them work at both small and large radii.
+In the following we try to resolve some of the ambiguities by discussing possible reasons, by comparing our results to previous work and by hazarding some guesses on the true nature of J1331's matter distribution, which should be easily testable by future observations.
+%--------------------------------------------
+
 %============================================
@@
 \centering
-\caption{Total $I$-band luminosity, stellar mass and mass-to-light ratio, calculated from the $I$-band AB magnitudes and stellar masses found for J1331's bulge and disk by \citet{SWELLSI} (their table 2) for comparison with this work.
+\caption{Total $I$-band luminosity, stellar mass, and mass-to-light ratio, calculated from the $I$-band AB magnitudes and stellar masses found for J1331's bulge and disk by \citet{SWELLSI} (their table 2) for comparison with this work.
 The transformation from AB magnitudes to the Johnson-Cousins $I$-band used the relation $I[\text{mag}] = I[\text{ABmag}] - 0.309$ from \citet{FG1994} (their table 2).
@@
 %--------------------------------------------
-\subsubsection{Rotation curve}
-%--------------------------------------------
-
-%--------------------------------------------
-We generate a rotation curve from the best-fitting mean model in Table \ref{tab:modelB4_bestfit}, whose $v_\text{rms}$ curve is shown in the first panel of Figure \ref{fig:modelB4_vrot}.
-Following the procedure in Section \ref{sec:model_JAM_rotation}, we find the rotation curve by fitting the rotation parameter $\kappa'$ to the symmetrized $v_\text{rot}$ data within $R' = 3.5''$.
-The best fit with $\kappa' = 0.76$ is given in the second panel of Figure \ref{fig:modelB4_vrot}.
-The third panel shows the dispersion that follows from $\sigma = \sqrt{v_\text{rms}^2 - v_\text{rot}^2}$.
-Our assumptions for $\kappa(R)$ nicely reproduce a $v_\text{rot}$ model with counter-rotating core.
-Although we fitted $v_\text{rot}$ only to the inner regions, the extrapolation to large radii matches the data also very well.
-
-While the dispersion $\sigma$ in the center fits by construction quite good, the extrapolated dispersion is much larger than the data.
-We would expect the disk to be rotationally supported and therefore have a low velocity dispersion.
-Especially dispersions as high as $\sim 200~\text{km s}^{-1}$ are more likely to be observed in the pressure supported bulges of galaxies.
-There might be something unexpected with the $\sigma$ measurements around $\sim 5''$, but at large radii the best-fitting model NFW halo is simply too massive.
-
-%--------------------------------------------
-
-\subsubsection{Further tests and discussion}
-
-We also fitted a model with a cored logarithmic DM halo.
-The cored halo models are in general slightly less massive than the NFW halo and therefore fit the outer regions of J1331 better.
-However, the density profile of the cored halo as well as the $I$-band light distribution within the plane drop as $\rho(r) \propto r^{-2}$.
-There is therefore a strong degeneracy between the stellar mass and the DM.
-Overall, we were not able to obtain tight constraints on the cored logarithmic halo.
-
-As we only fitted the halo models to the inner regions, it is not surprising that they do not fit the kinematics at larger radii.
-A fit to all nine available $v_\text{rms}$ data points would force the DM halo to be less massive.
-But with decreasing DM contribution in the inner regions the model approaches the mass-follows-light model in the center that we already ruled out in Section \ref{sec:results_JAM_SB_MfL}.
-Allowing for free $\Upsilon_\text{I,*}(R')$, $\beta_z(R')$, and more flexible $\rho_\text{halo}(r)$ profiles, which would be the reasonable next step, would over fit the data.
-Without further priors on the stellar $\Upsilon_\text{I,*}(R')$ or more data points, we can make only the following statement: A model with constant $\Upsilon_\text{I,*} = 4.2\pm 0.2$, moderately tangential $\beta_z = -0.4\pm 0.1$ and a spherical and massive DM component with high concentration ($c_\text{200}=8\pm 2$) can explain the central kinematics of J1331 very well.
-We have however ruled out that in this case the DM halo will follow an NFW halo profile at both small and large radii.
-
-We will also discuss the kinematics at larger radii in more depth in the discussion Section \ref{sec:discussion_kinematics}.
-
-%--------------------------------------------
-\section{Discussion and Conclusion} \label{sec:Discussion}
-%--------------------------------------------
-
-%--------------------------------------------
-We have presented different dynamical models for the central region of J1331.
-Some of them capture the observed kinematics, but none of them work at both small and large radii.
-In the following we try to resolve some of the ambiguities by discussing possible reasons, by comparing our results to previous work and by hazarding some guesses on the true nature of J1331's matter distribution, which should be easily testable by future observations.
-%--------------------------------------------
-
-%--------------------------------------------
 \subsection{On J1331's possible merger history} \label{sec:discussion_merger}
@@
 %--------------------------------------------
+
+%--------------------------------------------
+\subsection{On J1331's kinematics} \label{sec:discussion_kinematics}
+%--------------------------------------------
+
+%--------------------------------------------
+Overall, the kinematics of the merger remnant J1331 are peculiar.
+In particular, there are two features in the $v_\text{rms}$ curve that are hard to explain with standard modelling techniques.
+The first feature, the deep central $v_\text{rms}$ dip, was studied in detail in this work.
+The second feature, the drop and rise in $v_\text{rms}$ around $R'\sim6''$, is even harder to explain; below we will speculate about possible reasons that could cause such a signature.
+
+\emph{(i) The central $v_\text{rms}$ dip within $R'\lesssim1''$:}
+
+First, we will compare our modelling results with the modelling results by \citet{SWELLSV} within $R_\text{eff}$.
+\citet{SWELLSV} fitted a stellar mass model and NFW halo to (i) the Einstein mass and (ii) gas kinematics at larger radii $\gtrsim8''$.
+Figure \ref{fig:vcirc_comparison} compares the circular velocity curve found by \citet{SWELLSV} with a mass-follows-light model scaled to fit our Einstein mass (by multiplying the light distribution in Table \ref{tab:MGEF814W} by $\Upsilon_\text{I,tot}^\text{ein} = 5.56$, analogous to Figure \ref{fig:lenscomparelight}).
+Within $0''.5 < R < 5''$ they agree with each other.
+
+The models in this work used more than just the Einstein mass to constrain the matter distribution at small radii: The lens mass model constrained also the shape of the mass distribution within the lensing image configuration at $R_\text{ein} \sim 1''$.
+The dynamical models used stellar kinematics inside $R' \simeq 3.5''$.
+We compare the lens mass model's $v_\text{circ}$ (for $\alpha=1.0\pm 0.1$) with the NFW JAM model (Table \ref{tab:modelB4_bestfit}) in Figure \ref{fig:vcirc_comparison} as well.
+Within and around $R_\text{ein}$ they are consistent with each other, even though they were independently derived.
+They do not agree with the mass-follows-light-like result by \citet{SWELLSV} and in Section \ref{sec:results_JAM_SB_MfL} we showed that ``mass-follows-light'' is not a good model for J1331.
 
@@
 %============================================
-
-%--------------------------------------------
-\subsection{On J1331's kinematics} \label{sec:discussion_kinematics}
-%--------------------------------------------
-
-%--------------------------------------------
-Overall, the kinematics of the merger remnant J1331 are peculiar.
-In particular, there are two features in the $v_\text{rms}$ curve that are hard to explain with standard modelling techniques.
-The first feature, the deep central $v_\text{rms}$ dip, was studied in detail in this work.
-The second feature, the drop and rise in $v_\text{rms}$ around $R'\sim6''$, is even harder to explain; below we will speculate about possible reasons that could cause such a signature.
-
-\emph{(i) The central $v_\text{rms}$ dip within $R'\lesssim1''$:}
-
-First, we will compare our modelling results with the modelling results by \citet{SWELLSV} within $R_\text{eff}$.
-\citet{SWELLSV} fitted a stellar mass model and NFW halo to (i) the Einstein mass and (ii) gas kinematics at larger radii $\gtrsim8''$.
-Figure \ref{fig:vcirc_comparison} compares the circular velocity curve found by \citet{SWELLSV} with a mass-follows-light model scaled to fit our Einstein mass (by multiplying the light distribution in Table \ref{tab:MGEF814W} by $\Upsilon_\text{I,tot}^\text{ein} = 5.56$, analogous to Figure \ref{fig:lenscomparelight}).
-Within $0''.5 < R < 5''$ they agree with each other.
-
-The models in this work used more than just the Einstein mass to constrain the matter distribution at small radii: The lens mass model constrained also the shape of the mass distribution within the lensing image configuration at $R_\text{ein} \sim 1''$.
-The dynamical models used stellar kinematics inside $R' \simeq 3.5''$.
-We compare the lens mass model's $v_\text{circ}$ (for $\alpha=1.0\pm 0.1$) with the NFW JAM model (Table \ref{tab:modelB4_bestfit}) in Figure \ref{fig:vcirc_comparison} as well.
-Within and around $R_\text{ein}$ they are consistent with each other, even though they were independently derived.
-They do not agree with the mass-follows-light-like result by \citet{SWELLSV} and in Section \ref{sec:results_JAM_SB_MfL} we showed that ``mass-follows-light'' is not a good model for J1331.
 
@@
 %--------------------------------------------
+\bibliography{literaturelist}{}
 \bibliographystyle{mnras}
-\bibliography{literaturelist}
 %--------------------------------------------
